### 2020-03-04 README.Rmd
First commit

---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  eval = TRUE 
)

mypath <- rprojroot::find_package_root_file
source(mypath("R", "misc.R"))
data_dir <- mypath("data")

library(tidyverse)
library(magrittr)
library(jmotif)
```
# Analyse desassembly and assembly processes in fish communities

<!-- badges: start -->
<!-- badges: end -->

The goal of this project is to analyze the links between the biomass dynamics
and community structure dynamics.

## Data

data about communities are located in `data` folder.

```{r load dataset, include = FALSE}
myload(community_metrics, op_analysis, dir = data_dir)
community_metrics %<>% left_join(select(op_analysis, opcod, station, date))
```

```{r}
ts_biomass  <- community_metrics %>%
  select(station, date, biomass) %>%
  mutate(station = as.character(station)) %>%
  group_by(station) %>%
  arrange(date) %>%
  nest()

ts_biomass %<>%
  mutate(
    zts = map(data, function(x) znorm(x$biomass, threshold = 0.01)),
    paa = map(zts, ~paa(., 3)),
    sax = map_chr(paa, ~series_to_string(., 3))
  )
```

```{r}
pattern_dist <- ts_biomass %>%
  group_by(sax) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
ggplot(ts_biomass, aes(x = sax)) +
  geom_histogram(stat = "count")

filter(pattern_dist, count > 10)
```

```{r}
test <- ts_biomass %>%
  filter(sax %in% c("cba", "bbb", "cab", "abc", "acb", "bca", "bac", "cbb")) %>%
  group_by(sax) %>%
  sample_n(10) %>%
  mutate(
    paa2 = map2(data, zts, function (x, zts) {
      cbind(x[,1], zts)
  }),
    id_sta = as.character(seq(1,n()))

  ) %>%
  unnest(paa2)

ggplot(test, aes(x = date, y = zts)) +
  geom_line(aes(color = id_sta)) +
  facet_wrap(~ sax)

```

### 2020-03-04 analysis/intro.Rmd
First commit

---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = TRUE
)
library(datasets)
```

```{r}
library(tidyverse)
library(magrittr)

data(iris)
head(iris)
```

```{r}
# I do not like uppercase:
iris %<>% rename_all(tolower)
head(iris)

# I prefer tibble format:
iris %<>% as.tibble 
iris

```

We want to compute the mean value for each variable for each species. We will
use the functions of the `dplyr` package.

```{r}
iris_species <- iris %>%
  gather(variable, value, sepal.length:petal.width) %>%
  group_by(species, variable) %>%
  summarise(avg = mean(value)) %>%
  spread(variable, avg)
```

## Tables

You can generate tables in markdown with `kable()` but you can also generate it
in LaTeX.

```{r}
knitr::kable(iris_species)

```

```{r}
library(xtable)
xtable(iris_species)

```

Let's tweak a bit the table by removing row numbering, reduce digit number,
etc... See `r ?xtable` and `r ?print.xtable`

```{r}
iris_species_xtable <- xtable(iris_species, 
  caption = "Average flower phenology (in cm) of different species of the
  \textit{Iris} genus.",
  label = "tab:iris_species",
  align = c("c","l", "|", "r", "r", "r", "r"),
  digits = 1
  )
print(iris_species_xtable, include.rownames = FALSE)

```

## Figures

```{r}
iris_petall <- select(iris, species, petal.length)
p <- ggplot(iris_petall, aes(y = petal.length, x = species)) + 
  geom_violin()
p
```

This plot is not ready to be put in a paper (grey area, bad axes, font not
ajusted). The package `cowplot` load a theme with better default. See the
cowplot
[vignette](https://cran.r-project.org/web/packages/cowplot/vignettes/introduction.html).

```{r}
library(cowplot)
p

```

You can also arrange plots in a grid:

```{r}
p2 <- ggplot(mpg, aes(x = cty, y = hwy, colour = factor(cyl))) + 
  geom_point(size=2.5)
p2

```
```{r, fig.dim = c(7, 5)}
plot_grid(p, p2, labels = "AUTO")
```

### 2020-08-20 R/data_frame_manipulation.R
Add plot and proto-report

@@ -19,9 +19,16 @@ add_relative_biomass_to_start <- function (.data = NULL) {
   output <- .data %>%
     dplyr::group_by(station) %>%
     dplyr::arrange(nb_year) %>%
-    dplyr::mutate(rel_bm = (biomass - first(biomass)) / first(biomass)) %>%
-    dplyr::ungroup()
-  return(output)
+    dplyr::mutate(rel_bm = (biomass - first(biomass)) / first(biomass)) 
+  
+  if ("log_bm" %in% names(output)) {
+
+    output %<>% 
+      dplyr::mutate(rel_log_bm = (log_bm - first(log_bm)) / first(log_bm))
+  
+  }
+
+  return(ungroup(output))
 }
 
 #' Compute derivate variables
@@ -29,7 +36,9 @@ add_relative_biomass_to_start <- function (.data = NULL) {
 #' @inheritParams add_relative_biomass_to_start 
 add_to_full_data <- function (.data = NULL) {
 
-  output <- add_nb_year_station(.data)  
+  output <- add_nb_year_station(.data)
+  output <- output %>% 
+    mutate(log_bm = log(biomass))
   output <- add_relative_biomass_to_start(output) 
 
   return(output)

### 2020-08-20 R/packages.R

@@ -4,3 +4,4 @@ library(drake)
 library(tibble)
 library(tidyverse)
 library(magrittr)
+library(ggeffects)

### 2020-08-20 make.R

@@ -11,21 +11,34 @@ source("R/plan.R")      # Create your drake plan.
 # Call make() to run your work.
 # Your targets will be stored in a hidden .drake/ cache,
 make(plan)
+vis_drake_graph(plan)
 
 # If you do not change any code or data,
 # subsequent make()'s do not build targets.
 
 # Load your targets back into your session with loadd() and readd().
-loadd(temporal_dynamics_coef)
-temporal_dynamics_coef$value[[1]]
-debug(compute_lm_temporal_trends)
-library(tibble)
-test <- compute_lm_temporal_trends(.data = temporal_dynamics_coef,
-    y = c("biomass", "rel_bm"), x = c("connectance", "w_trph_lvl_avg", "richness"))
-test <- extract_xy_slope_from_coeff(x = "biomass", y = "rel_bm", .data = temporal_dynamics_coef)
+plan
 
-loadd(correlation_temporal_dynamics)
-correlation_temporal_dynamics$x
-correlation_temporal_dynamics$y
-get_lm_coeff(.data = correlation_temporal_dynamics, col_names = "model")
-temporal_dynamics
+loadd(net_dyn_lm_plot)
+cowplot::plot_grid(plotlist = net_dyn_lm_plot$plot)
+loadd(temporal_dynamics_plot)
+temporal_dynamics_plot %<>%
+  arrange(variable, station)
+to_plot <- temporal_dynamics_plot %>%
+  filter(variable == "rel_bm") %>%
+  slice(1:9)
+cowplot::plot_grid(plotlist = to_plot$plot, labels = to_plot$station)
+
+
+loadd(temporal_dynamics)
+loadd(data)
+data %>%
+  filter(station == 190)
+test <- temporal_dynamics[temporal_dynamics$station == 190, ]$rel_bm[[1]]
+
+lm(rel_bm ~ nb_year + surface, temporal_dynamics[temporal_dynamics$station == 190, ]$data[[1]])
+lm(rel_bm ~ nb_year, temporal_dynamics[temporal_dynamics$station == 190, ]$data[[1]])
+
+get_lm_station(.data = data, 
+    var_name = c("biomass", "rel_bm", "connectance", "w_trph_lvl_avg", "richness"),
+    rhs = " ~ nb_year + offset(surface)")

### 2020-08-21 report.Rmd
Add report of the preliminary results

---
title: "Report"
author: "Alain Danet"
output: html_document
---

```{r}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE 
)

library(drake)
library(tidyverse)
library(magrittr)
library(cowplot)
#theme_set(theme_cowplot())
```

## Temporal dynamics

```{r p-tmp-dyn, cache = FALSE}
loadd(temporal_dynamics_plot)

p <- vector(mode = "list", length = 10)
for (i in seq_len(length(p))) {
  to_plot <- temporal_dynamics_plot %>% 
    filter(station == sample(temporal_dynamics_plot$station, 1))
  p[[i]] <- cowplot::plot_grid(plotlist = to_plot$plot, labels = to_plot$station)
} 
p
```

## Links betwenn temporal dynamics

```{r p-bivar, cache = FALSE}
loadd(net_dyn_lm_plot)

cowplot::plot_grid(plotlist = net_dyn_lm_plot$plot[1:9], ncol = 3)

cowplot::plot_grid(plotlist = net_dyn_lm_plot$plot[10:18], ncol = 3)

```

```{r}
loadd(temporal_dynamics_coef)
loadd(data)
first_year_biomass <- 
  data %>%
  filter(nb_year == 0) %>%
  select(station, biomass, rel_bm, log_bm, rel_log_bm) %>%
  pivot_longer(-station, names_to = "coeff", values_to = "first_year")

temporal_dynamics_coef %>%
  filter(term %in% "slope", coeff %in% c("biomass", "rel_bm", "log_bm", "rel_log_bm")) %>%
  select(1:4) %>%
  pivot_wider(names_from = "term", values_from = estimate) %>%
  left_join(first_year_biomass, by = c("station", "coeff")) %>%
  ggplot(aes(x = first_year, y = slope)) +
  geom_point() +
  facet_wrap(~coeff, scales = "free")
```

```{r}
data %>%
  group_by(station) %>%
  summarise(med_bm = median(biomass)) %>%
  ggplot(aes(x = med_bm)) +
  geom_histogram() +
  labs(x = "Median total biomass over time by station (g)")
```

```{r}
slope_com_net <- temporal_dynamics_coef %>%
  filter(!coeff %in% get_biomass_var(), term == "slope") %>%
  select(station, coeff, estimate) %>%
  pivot_wider(names_from = "coeff", values_from = estimate)

absolute_slope_biomass <- temporal_dynamics_coef %>%
  filter(coeff %in% get_biomass_var(), term == "slope") %>%
  select(station, coeff, estimate) %>%
  mutate(
    absolute_slope =  abs(estimate),
    trend_sign = if_else(estimate > 0, "positive", "negative")
  ) %>%
  left_join(slope_com_net, by = "station")

metrics <- unique(temporal_dynamics_coef$coeff)[!unique(temporal_dynamics_coef$coeff) %in% get_biomass_var()]

p <- vector("list", length = length(metrics))
for (i in seq_along(metrics)) {
  p[[i]] <- 
    absolute_slope_biomass %>%
    ggplot(aes_string(x = "absolute_slope", y = metrics[i])) +
    geom_point(aes(color = trend_sign)) +
    facet_wrap(facets = ~ coeff, scales = "free") +
    labs(title = metrics[i])
}
p
```

### 2020-08-21 R/get_model_plot.R

@@ -5,7 +5,8 @@ get_temporal_dynamics_plot <- function (temporal_dynamics = NULL) {
   temporal_dynamics %>%
     select(-data) %>%
     pivot_longer(-station, names_to = "variable", values_to = "model") %>%
-    mutate(plot = map(model, plot_data_slope_lm))
+    mutate(plot = map(model, plot_data_slope_lm)) %>%
+    select(-model)
 
 
 }
@@ -14,7 +15,8 @@ get_temporal_dynamics_plot <- function (temporal_dynamics = NULL) {
 get_net_dyn_lm_plot <- function (net_dyn_lm = NULL) {
 
   net_dyn_lm %>%
-    mutate(plot = map(model, plot_data_slope_lm))
+    mutate(plot = map(model, plot_data_slope_lm)) %>%
+    select(-model)
   
 }
 
@@ -31,8 +33,8 @@ plot_data_slope_lm <- function (fit) {
     geom_line(data = prediction) +
     geom_ribbon(data = prediction, aes(ymin = conf.low, ymax = conf.high), alpha = .1) +
     #geom_line(method = "lm", col = "red") +
-    labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
-	"Intercept =",signif(fit$coef[[1]],5 ),
-	" Slope =",signif(fit$coef[[2]], 5),
-	" P =",signif(summary(fit)$coef[2,4], 5)))
+    labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 2),
+	"Intercept =",signif(fit$coef[[1]],2),
+	" Slope =",signif(fit$coef[[2]], 2),
+	" P =",signif(summary(fit)$coef[2,4], 3)))
 }

### 2020-08-21 R/statistical_model.R

@@ -76,8 +76,11 @@ extract_xy_slope_from_coeff <- function (y = NULL, x = NULL, .data = NULL) {
 compute_lm_temporal_trends <- function (.data = NULL, y = "biomass", x = "connectance") {
   
   output <- list(y = y, x = x) %>%
-    expand.grid() %>% 
-    mutate_all(as.character)
+    expand.grid() %>%
+    mutate_all(as.character) %>%
+    distinct(x, y) %>%
+    filter_at(vars(x, y), any_vars((. != x))) %>%
+    as_tibble
 
 
   output$data <- purrr::map2(output$y, output$x, extract_xy_slope_from_coeff, .data = .data)

### 2020-08-21 R/variable_shortcut.R

@@ -1,0 +1,3 @@
+get_biomass_var <- function () {
+  c("biomass", "rel_bm", "log_bm", "rel_log_bm")
+}

### 2020-09-01 report.Rmd
Big/little communities + test stan

@@
 
+# Research questions
+
+## State of the art
+
+- Report of community biomass (or number of individual) collapses in many
+  ecosystems
+- Modification of community are linked to modification in network structure 
+- Studies have been interested in how network assembles or disassembles
+  themselves.
+- However, the lack of availability of such empirical dataset have prevented the
+answering to this question.
+
+- Questions:
+  1. Are assembly and disassembly of networks symmetric processes ?
+
+# Results
+
 ## Temporal dynamics
+
+```{r}
+p_cap <- paste0(
+  "Temporal dynamics of biomass and temporal dynamics of
+  metrics for 10 randomly selected communities."
+)
+```
 
@@
 
-```{r p-bivar, cache = FALSE}
+```{r b-bivar-cap}
+bivar_cap <- paste0(
+  "Links between temporal dynamics of biomass and temporal dynamics of
+  metrics for the communities which have a median biomass across time inferior
+  to the median of the station (little) and the other (big)"
+)
+```
+
+```{r p-bivar, cache = FALSE, fig.cap = bivar_cap, fig.height = 10}
+loadd(net_dyn_lm)
 loadd(net_dyn_lm_plot)
 
-cowplot::plot_grid(plotlist = net_dyn_lm_plot$plot[1:9], ncol = 3)
+cowplot::plot_grid(
+  cowplot::plot_grid(plotlist = net_dyn_lm_plot$plot[1:4], ncol = 2),
+  cowplot::plot_grid(plotlist = filter(net_dyn_lm_plot, group == "big")$plot[1:4], ncol = 2),
+  ncol = 1, 
+  axis = "rlbt",
+  align = "hv",
+  label_y = 1.01,
+  label_x = .40,
+  labels = c("Little community", "Big community")
+)
 
-cowplot::plot_grid(plotlist = net_dyn_lm_plot$plot[10:18], ncol = 3)
+cowplot::plot_grid(
+  cowplot::plot_grid(plotlist = net_dyn_lm_plot$plot[5:8], ncol = 2),
+  cowplot::plot_grid(plotlist = filter(net_dyn_lm_plot, group == "big")$plot[5:8], ncol = 2),
+  ncol = 1, 
+  axis = "rlbt",
+  align = "hv",
+  label_y = 1.01,
+  label_x = .40,
+  labels = c("Little community", "Big community")
+)
+```
 
-```
+- Intercept close to 0 for all but richness in big communities 
+- Same slope between big and little communities except for connectance
 
@@
   select(station, biomass, rel_bm, log_bm, rel_log_bm) %>%
-  pivot_longer(-station, names_to = "coeff", values_to = "first_year")
+  pivot_longer(-station, names_to = "coeff", values_to = "first_year") %>%
+  group_by(coeff) %>%
+  mutate(com_size = ifelse(first_year < median(first_year, na.rm = TRUE), "little", "big"))
+median_biomass <- 
+  data %>%
+  select(station, biomass, log_bm) %>%
+  pivot_longer(-station, names_to = "coeff", values_to = "biomass") %>%
+  group_by(station, coeff) %>%
+  summarise(bm_med = median(biomass, na.rm = TRUE)) %>%
+  ungroup()
 
 temporal_dynamics_coef %>%
-  filter(term %in% "slope", coeff %in% c("biomass", "rel_bm", "log_bm", "rel_log_bm")) %>%
+  filter(term %in% "slope", coeff %in% c("biomass", "log_bm")) %>%
   select(1:4) %>%
@@
   ggplot(aes(x = first_year, y = slope)) +
-  geom_point() +
-  facet_wrap(~coeff, scales = "free")
+  geom_point(aes(color = com_size)) +
+  facet_wrap(~coeff, scales = "free") +
+  labs(x = "First year biomass (g)", y = "Slope (g.y^-1)")
+
+loadd(biomass_group)
+temporal_dynamics_coef %>%
+  filter(term %in% "slope", coeff %in% c("biomass", "log_bm")) %>%
+  select(1:4) %>%
+  pivot_wider(names_from = "term", values_from = estimate) %>%
+  left_join(median_biomass, by = c("station", "coeff")) %>%
+  left_join(biomass_group, by = c("station")) %>%
+  ggplot(aes(x = bm_med, y = slope)) +
+  geom_point(aes(color = com_size)) +
+  facet_wrap(~coeff, scales = "free") +
+  labs(x = "Median biomass (g)", y = "Slope (g.y^-1)")
 ```
@@
 
-```{r}
+```{r, eval = FALSE}
 slope_com_net <- temporal_dynamics_coef %>%
@@
 ```
+
+# Methods

### 2020-09-01 R/data_frame_manipulation.R

@@ -43,3 +43,15 @@ add_to_full_data <- function (.data = NULL) {
 
   return(output)
 }
+
+#' Add group to data according to station
+#'
+#'
+add_group_station <- function (.data = NULL, group = NULL) {
+
+  output <- .data %>%
+    left_join(group, by = "station")
+
+  return(output)
+
+}

### 2020-09-01 R/get_data.R

@@ -1,9 +1,12 @@
 #' Get community metrics
 #'
 #' @param dir path to the data
-get_community_data <- function (dir = get_mypath("data")) {
+get_community_data <- function (
+  path = get_mypath("data", "community_metrics.rda"),
+  community_metrics = NULL
+  ) {
 
-  myload(community_metrics, dir = dir, envir = environment())
+  load(path, envir = environment())
 
   com <- community_metrics %>% 
     dplyr::select(opcod, biomass, richness) %>%
@@ -16,10 +19,12 @@ get_community_data <- function (dir = get_mypath("data")) {
 #' Get network metrics
 #'
 #' @param dir path to the data
-get_network_data <- function (dir = get_mypath("data", "classes"), metrics = NULL) {
+get_network_data <- function (network_metrics = NULL, 
+  path = get_mypath("data", "classes", "network_metrics.rda"), 
+metrics = NULL) {
 
   
-  myload(network_metrics, dir = dir, envir = environment())
+  load(path, envir = environment())
 
   if (is.null(metrics)) {
     metrics <- c(
@@ -39,9 +44,9 @@ get_network_data <- function (dir = get_mypath("data", "classes"), metrics = NUL
 #' Get fishing operation data
 #'
 #'
-get_op_data <- function (dir = get_mypath("data")) {
+get_op_data <- function (path = get_mypath("data", "op_analysis.rda")) {
 
-  myload(op_analysis, dir = dir, envir = environment())
+  load(path, envir = environment())
 
   col_to_keep <- c("opcod", "station", "year", "surface")
   op <- op_analysis[, colnames(op_analysis) %in% col_to_keep]
@@ -70,6 +75,23 @@ get_full_data <- function (net = NULL, com = NULL, op = NULL) {
 
   return(full)
 
+}
+
+#' Get group of community based on median biomass 
+#'
+#'
+get_biomass_group <- function(.data = data) {
+ 
+  .data %>%
+  select(station, biomass, log_bm) %>%
+  pivot_longer(-station, names_to = "coeff", values_to = "biomass") %>%
+  group_by(station, coeff) %>%
+  summarise(bm_med = median(biomass, na.rm = TRUE)) %>%
+  ungroup() %>%
+  filter(coeff == "biomass") %>%
+  mutate(com_size = ifelse(bm_med < median(bm_med, na.rm = TRUE), "little", "big")) %>%
+  ungroup() %>%
+  select(station, com_size)
 }
 
 update_files <- function () {

### 2020-09-01 R/statistical_model.R

@@ -73,24 +73,39 @@ extract_xy_slope_from_coeff <- function (y = NULL, x = NULL, .data = NULL) {
   return(output)
 }
 
-compute_lm_temporal_trends <- function (.data = NULL, y = "biomass", x = "connectance") {
+compute_lm_temporal_trends <- function (.data = NULL, y = "biomass", x = "connectance", group = NULL) {
   
-  output <- list(y = y, x = x) %>%
+  group_var <- enquo(group)
+  group_var_chr <- quo_name(group_var)
+
+
+  if (rlang::quo_is_null(group_var)) {
+    output <- list(y = y, x = x)
+  } else {
+    output <- list(y = y, x = x, group = unique(.data[[group_var_chr]]))
+  }
+  output <- 
+    output %>%
     expand.grid() %>%
     mutate_all(as.character) %>%
-    distinct(x, y) %>%
+    distinct() %>%
     filter_at(vars(x, y), any_vars((. != x))) %>%
     as_tibble
 
-
-  output$data <- purrr::map2(output$y, output$x, extract_xy_slope_from_coeff, .data = .data)
+  if (rlang::quo_is_null(group_var)) {
+    output$data <- purrr::map2(output$y, output$x, extract_xy_slope_from_coeff, .data = .data)
+  } else {
+    output$data <- purrr::pmap(
+      list(output$y, output$x, output$group),
+      ~extract_xy_slope_from_coeff(y = ..1, x = ..2, .data = filter(.data, !!group_var == ..3)))
+  }
 
   output %<>%
     mutate(
       formulas = paste(y, "~", x ),
       model = purrr::map2(data, formulas, ~lm(formula = .y, weights = weight, data =.x))
       ) %>%
-    select(y, x, model)
+    select(-formulas)
   return(output)
 }
 

### 2020-09-16 report.Rmd
Add a proper statistical model

@@
 library(cowplot)
+source("R/misc.R") # Define your custom code as a bunch of functions.
+source_dir(get_mypath("R")) # Define your custom code as a bunch of functions.
+
 #theme_set(theme_cowplot())
@@
 - Questions:
-  1. Are assembly and disassembly of networks symmetric processes ?
+  1. Is a decrease or a increase in biomass related to a network
+     structure modification?
+     1.1 Is a contant decrease/increase in biomass correspond the same dynamic
+     in network? Or there are non linear dynamics ?
+  2. Are assembly and disassembly of networks symmetric processes?
 
@@
 
-## Temporal dynamics
+## Links betwenn temporal dynamics
 
 ```{r}
-p_cap <- paste0(
-  "Temporal dynamics of biomass and temporal dynamics of
-  metrics for 10 randomly selected communities."
-)
+loadd(net_dyn_lm)
+loadd(net_dyn_lm_plot)
 ```
-
-```{r p-tmp-dyn, cache = FALSE}
-loadd(temporal_dynamics_plot)
-
-p <- vector(mode = "list", length = 10)
-for (i in seq_len(length(p))) {
-  to_plot <- temporal_dynamics_plot %>% 
-    filter(station == sample(temporal_dynamics_plot$station, 1))
-  p[[i]] <- cowplot::plot_grid(plotlist = to_plot$plot, labels = to_plot$station)
-} 
-p
-```
-
-## Links betwenn temporal dynamics
 
@@
 
-```{r p-bivar, cache = FALSE, fig.cap = bivar_cap, fig.height = 10}
-loadd(net_dyn_lm)
-loadd(net_dyn_lm_plot)
+```{r p-bivar, cache = TRUE, fig.cap = bivar_cap, fig.height = 10}
 
@@
 loadd(temporal_dynamics_coef)
-loadd(data)
+loadd(temporal_dynamics_plot)
+loadd(full_data2)
+```
+
+```{r}
 first_year_biomass <-
-  data %>%
+  full_data2 %>%
   filter(nb_year == 0) %>%
@@
   group_by(coeff) %>%
-  mutate(com_size = ifelse(first_year < median(first_year, na.rm = TRUE), "little", "big"))
+  mutate(com_size = ifelse(first_year < median(first_year, na.rm = TRUE), "little", "big")) %>%
+  ungroup()
+
 median_biomass <- 
-  data %>%
+  full_data2 %>%
   select(station, biomass, log_bm) %>%
@@
   summarise(bm_med = median(biomass, na.rm = TRUE)) %>%
+  ungroup()
+three_first_year_biomass <-
+  full_data2 %>%
+  filter(nb_year <= 2) %>%
+  select(station, nb_year, biomass, rel_bm, log_bm, rel_log_bm) %>%
+  pivot_longer(cols = biomass:rel_log_bm, names_to = "coeff", values_to = "first_year") %>%
+  group_by(station, coeff) %>%
+  summarise(first_3_year = median(first_year, na.rm = TRUE)) %>%
+  group_by(coeff) %>%
+  mutate(com_size = ifelse(first_3_year < median(first_3_year, na.rm = TRUE), "little", "big")) %>%
   ungroup()
@@
 ```{r}
-data %>%
+full_data2 %>%
   group_by(station) %>%
@@
 ```
+
+##
 
@@
 # Methods
+
+## Biomass classification
+
+```{r}
+loadd(rigal_classification)
+myload(biomass_ts_sax, envir = globalenv(),dir = get_mypath("data"))
+
+biomass_classif_rigal <- rigal_classification %>%
+  filter(variable %in% c("biomass", "log_bm")) %>%
+  unnest(classif) %>%
+  mutate(station = as.character(station)) %>%
+  select(station, variable,shape_class)
+
+p_biomass_classif_rigal <- biomass_classif_rigal %>%
+  ggplot(aes(x = shape_class)) +
+  geom_bar() +
+  facet_wrap(~variable) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+```
+
+## Temporal dynamics
+
+```{r}
+p_cap <- paste0(
+  "Temporal dynamics of biomass and temporal dynamics of
+  metrics for 10 randomly selected communities."
+)
+```
+
+```{r p-tmp-dyn, cache = TRUE}
+
+p <- vector(mode = "list", length = 10)
+for (i in seq_len(length(p))) {
+  to_plot <- temporal_dynamics_plot %>% 
+    filter(station == sample(temporal_dynamics_plot$station, 1))
+  p[[i]] <- cowplot::plot_grid(plotlist = to_plot$plot, labels = to_plot$station)
+}
+p
+```
+
+## Temporal dynamics decrease/increase constant
+
+### Log biomass
+
+```{r, fig.height = 45}
+st_decrease_increase_rigal <- biomass_classif_rigal %>%
+  filter(shape_class %in% c("increase_constant", "decrease_constant"))
+data_decrease_increase <- full_data2 %>%
+  filter(station %in% st_decrease_increase_rigal$station)
+
+log_bm_min_max <- map_dbl(c(min, max),
+  ~.x(data_decrease_increase$log_bm, na.rm = TRUE))
+nb_year_min_max <- map_dbl(c(min, max),
+  ~.x(data_decrease_increase$nb_year, na.rm = TRUE))
+temporal_dynamics_plot$plot %<>%
+  map(., ~ .x + lims(y = log_bm_min_max, x = nb_year_min_max))
+
+temporal_dynamics_plot %>%
+  filter(variable == "log_bm", station %in% st_decrease_increase_rigal$station) %>%
+  plot_grid(plotlist = .$plot, ncol = 3, labels = st_decrease_increase_rigal$station)
+```
+
+### Raw Biomass
+
+```{r, fig.height = 45}
+st_decrease_increase_rigal_biomass <- rigal_classification %>%
+  filter(variable == "bm_std") %>%
+  unnest(classif) %>%
+  filter(shape_class %in% c("increase_constant", "decrease_constant"))
+
+bm_min_max <- map_dbl(
+  c(min, max),
+  ~.x(data_decrease_increase$biomass, na.rm = TRUE))
+nb_year_min_max <- map_dbl(
+  c(min, max),
+  ~.x(data_decrease_increase$nb_year, na.rm = TRUE))
+temporal_dynamics_plot[temporal_dynamics_plot$variable == "biomass",]$plot %<>%
+  map(., ~ .x + lims(y = bm_min_max, x = nb_year_min_max))
+
+temporal_dynamics_plot %>%
+  filter(variable == "biomass", station %in% st_decrease_increase_rigal_biomass$station) %>%
+  plot_grid(plotlist = .$plot, ncol = 3, labels = st_decrease_increase_rigal_biomass$station)
+```
+
+## Station grouping
+
+### Rigal station increase / decrease
+
+Les stations ont moins de 40 kilos au départ ont l'air comparable en terme de
+dynamique.
+
+```{r}
+
+station_summary_biomass <- full_data2 %>%
+  group_by(station) %>%
+  summarise(bm_med = median(biomass, na.rm = TRUE)) %>%
+  left_join(
+    filter(three_first_year_biomass, coeff == "biomass") %>%
+      select(station, first_3_year)
+    , by =
+    "station") %>%
+  left_join(
+    filter(first_year_biomass, coeff == "biomass") %>%
+      select(station, first_year)
+      , by =
+    "station")
+
+p_rigal_decrease_increase_slope_st <- 
+  st_decrease_increase_rigal_biomass %>%
+  left_join(station_summary_biomass, by = "station") %>%
+  select(station, shape_class, linear_slope, linear_intercept, first_3_year, bm_med, first_year) %>%
+  pivot_longer(cols = first_3_year:first_year, names_to = "variable",
+    values_to = "value") %>%
+  ggplot(aes(y = linear_slope, x = value, color = shape_class)) +
+  geom_point() +
+  facet_wrap(~variable)
+p_rigal_decrease_increase_slope_st
+```
+
+### Tendancies in rigal increase / decrease
+
+```{r}
+rigal_biomass_coeff_dynamics <- st_decrease_increase_rigal_biomass %>%
+  select(station, linear_slope, strd_error) %>%
+  left_join(temporal_dynamics_coef, by = "station") %>%
+  filter(!coeff %in% get_biomass_var(), term == "slope") %>%
+  select(station, coeff, estimate, std.error, linear_slope, bm_std_error = strd_error) %>%
+  mutate(reg_weight = (abs(estimate / std.error) + abs(linear_slope / bm_std_error))/2)
+rigal_biomass_coeff_dynamics %>%
+  ggplot(aes(x = reg_weight)) +
+  geom_histogram() +
+  facet_wrap(~coeff)
+
+rigal_biomass_coeff_dynamics %>%
+  ggplot(aes(x = linear_slope, y = estimate, size = reg_weight, weight = reg_weight)) +
+  geom_point() +
+  geom_smooth() +
+  facet_wrap(~coeff, scales = "free_y")
+rigal_biomass_coeff_dynamics %>%
+  ggplot(aes(x = linear_slope, y = estimate, size = reg_weight)) +
+  geom_point() +
+  geom_smooth() +
+  facet_wrap(~coeff, scales = "free_y")
+```
+
+### With group
+
+#### Median
+
+```{r}
+group_results <- rigal_biomass_coeff_dynamics %>%
+  left_join(station_summary_biomass, by = "station") %>%
+  pivot_longer(cols = bm_med:first_year, names_to = "bm_summary_type", values_to = "bm_summary") %>%
+  group_by(bm_summary_type) %>%
+  mutate(
+    median_group = ifelse(bm_summary < median(bm_summary, na.rm = TRUE), "little", "big"),
+    first_quartile = map_chr(bm_summary, function (x, y) {
+      if (is.na(x)) return(NA)
+
+      if (x < y[1])
+	output <- "first_quartile"
+      else if (x > y[2])
+	output <- "third_quartile"
+      else
+	output <- NA
+      return(output)
+}, y = quantile(bm_summary, probs = c(.25, .75), na.rm = TRUE))
+  ) %>%
+  ungroup()
+
+##Summary of group 
+group_results %>%
+  ggplot(aes(x = bm_summary)) +
+  geom_histogram() +
+  facet_wrap(~bm_summary_type, scales = "free_x")
+
+p1 <- group_results  %>%
+  filter(bm_summary_type == "first_3_year") %>%
+  ggplot(aes(x = linear_slope, y = estimate, color = median_group, size = reg_weight, weight = reg_weight)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  facet_wrap(~coeff, scales = "free_y")
+
+p2 <- group_results  %>%
+  filter(bm_summary_type == "first_3_year") %>%
+  ggplot(aes(x = linear_slope, y = estimate, color = first_quartile, size = reg_weight, weight = reg_weight)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  facet_wrap(~coeff, scales = "free_y")
+
+p3 <- group_results  %>%
+  filter(bm_summary_type == "bm_med") %>%
+  ggplot(aes(x = linear_slope, y = estimate, color = median_group, size = reg_weight, weight = reg_weight)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  facet_wrap(~coeff, scales = "free_y")
+
+p1
+p2
+p3
+```
+
+#### Little and big rivers
+
+```{r}
+#grandes/petites rivières
+myload(habitat_press, habitat_pressure, op_analysis, envir = environment(),
+  dir = get_mypath("data"))
+width_classif_mean <- habitat_press %>%
+    mutate(width_classif_mean  = if_else(width_river_mean < mean(width_river_mean, na.rm = TRUE), "little",
+      "big")) %>%
+    select(station, width_river_mean, width_classif_mean)
+habitat_press %>%
+  ggplot(aes(x = width_river_mean)) +
+  geom_histogram()
+
+habitat_pressure %>%
+  pivot_longer(cols = c(RC1, RC2), names_to = "PCA_axis", values_to = "value") %>%
+  ggplot(aes(x = value)) +
+  geom_histogram() +
+  facet_wrap(~PCA_axis)
+protocol_station <- op_analysis %>%
+  group_by(station) %>%
+  summarise(protocol_type = unique(protocol_type))
+
+habitat_press %>%
+  left_join(protocol_station, by = "station") %>%
+  ggplot(aes(x = width_river_mean, fill = protocol_type)) +
+  geom_histogram()
+
+group_results_stream_size <-
+  group_results %>%
+  left_join(
+    habitat_pressure %>%
+    mutate(RC1_med = if_else(RC1 < median(RC1, na.rm = TRUE), "little",
+      "big")) %>%
+    select(station, RC1, RC1_med),
+  by = "station"
+  ) %>%
+  left_join(protocol_station, by = "station") %>%
+  left_join(width_classif_mean, by = "station")
+
+group_results_stream_size %>%
+  filter(bm_summary_type == "first_3_year", linear_slope < 8) %>%
+  ggplot(aes(x = linear_slope, y = estimate, color = protocol_type, size = reg_weight, weight = reg_weight)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  facet_wrap(~coeff, scales = "free_y") +
+  labs(title = "Group as protocol type")
+
+group_results_stream_size %>%
+  filter(bm_summary_type == "first_3_year", linear_slope < 8) %>%
+  ggplot(aes(x = linear_slope, y = estimate, color = protocol_type, size = reg_weight, weight = reg_weight)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  facet_wrap(~coeff, scales = "free_y") +
+  labs(title = "Group as mean river size")
+
+group_results_stream_size %>%
+  filter(bm_summary_type == "first_3_year", linear_slope < 8) %>%
+  ggplot(aes(x = linear_slope, y = estimate, color = width_classif_mean, size = reg_weight, weight = reg_weight)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  facet_wrap(~coeff, scales = "free_y") +
+  labs(title = "Group as mean river size")
+
+group_results_stream_size %>%
+  filter(bm_summary_type == "bm_med", linear_slope < 8) %>%
+  ggplot(aes(x = linear_slope, y = estimate, color = median_group, size = reg_weight, weight = reg_weight)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  facet_wrap(~coeff, scales = "free_y") +
+  labs(title = "Group as mean biomass")
+
+# Quelle est la compo des dynamique dans RC1
+group_results_stream_size %>%
+  filter(bm_summary_type == "first_3_year") %>%
+  ggplot(aes(x = RC1)) +
+  geom_histogram() +
+  facet_wrap(~protocol_type)
+
+group_results_stream_size %>%
+  filter(bm_summary_type == "first_3_year") %>%
+  ggplot(aes(x = bm_summary)) +
+  geom_histogram() +
+  facet_wrap(~protocol_type)
+```
+
+```{r}
+model_int <- group_results_stream_size %>%
+  filter(bm_summary_type == "first_3_year", linear_slope < 5000) %>%
+  group_by(coeff) %>%
+  nest() %>%
+  mutate(model = map(data, ~lm(estimate ~ linear_slope * width_river_mean,.x)))
+
+test <- model_int$model[[3]]
+car::vif(test)
+
+```
+
+```{r}
+group_results_stream_size %>%
+  filter(bm_summary_type == "bm_med", linear_slope < 8) %>%
+  ggplot(aes(x = linear_slope, y = estimate, color = median_group, size = reg_weight, weight = reg_weight)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  facet_wrap(~coeff, scales = "free") +
+  labs(title = "Group as mean biomass")
+```
+
+```{r}
+model_int <- group_results_stream_size %>%
+  filter(bm_summary_type == "bm_med", linear_slope < 8) %>%
+  mutate(
+    increasing = linear_slope > 0,
+    inc_f = as.factor(increasing) 
+    ) %>%
+  group_by(coeff) %>%
+  nest() %>%
+  mutate(
+    mod1 = map(data, ~lm(estimate ~ linear_slope:(linear_slope <0) + linear_slope:(linear_slope >0),.x)),
+    mod2 = map(data, ~lm(estimate ~ linear_slope:increasing,.x)),
+    mod3 = map(data, ~lm(estimate ~ linear_slope:increasing:median_group,.x)),
+    mod4 = map(data, ~lm(estimate ~ linear_slope:increasing:median_group, .x, weights = reg_weight)),
+    mod5 = map(data, ~lm(estimate ~ linear_slope:inc_f:median_group, .x, weights = reg_weight)),
+  )
+
+model_out <- map(model_int$mod5, summary)
+model_vif <- map(model_int$mod4, car::vif)
+names(model_out) <- model_int$coeff 
+model_out
+```
+
+```{r}
+library(ggeffects)
+mydf <- ggpredict(model_int$mod5[[1]], terms = c("linear_slope", "inc_f",
+    "median_group"))
+plot(mydf, add.data = TRUE)
+
+plot_final_model <- function (ggpred = NULL, rawdata = NULL) {
+  ggpred %<>%
+    as_tibble %>%
+    rename(increasing = group, bm_group = facet)
+
+  ggpred %<>%
+    filter(increasing == FALSE & x < 0 | increasing == TRUE & x > 0)
+
+  if (is.null(rawdata)) {
+  rawdata <- attr(ggpred, "rawdata")
+  }
+
+  p <- ggplot(ggpred, aes(x = x , y = predicted, color = bm_group)) +
+    geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = bm_group), alpha =
+      .1) +
+    geom_line()
+  p + geom_point(data = rawdata, aes(y = estimate, x = linear_slope, color =
+      median_group))
+
+}
+```
+
+```{r}
+model_int %<>%
+  mutate(
+    pred5 = map(mod5, ~ggpredict(.x,
+	terms = c("linear_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2,3, 4, 6]", "inc_f", "median_group"))),
+    plot = map(pred5, ~plot(.x, add.data = TRUE)),
+    myplot = map2(pred5, data, ~plot_final_model(ggpred = .x, rawdata = .y))
+  )
+plot_grid(plotlist = model_int$myplot, labels = model_int$coeff)
+```
+
+```{r}
+library(segmented)
+
+mod_tlvl <- lm(estimate ~ linear_slope, model_int$data[[2]])
+mod_tlvl <- lm(
+  estimate ~ linear_slope*decreasing*median_group,#(linear_slope < 0)*linear_slope + (linear_slope >= 0)*linear_slope,
+  mutate(model_int$data[[2]], decreasing = linear_slope < 0)
+)
+seg_tlvl <- segmented(mod_tlvl, seg.Z=~linear_slope)
+plot(seg_tlvl)
+
+mod_richness <- lm(estimate ~ linear_slope, model_int$data[[2]])
+test <- segmented(mod_richness, seg.Z=~linear_slope)
+plot(test)
+
+car::vif(test)
+```
+
+```{r}
+#keep only complete protocol
+group_results_stream_size %>%
+  filter(protocol_type == "complete") %>%
+  filter(bm_summary_type == "bm_med", linear_slope < 8) %>%
+  ggplot(aes(x = linear_slope, y = estimate, color = median_group)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  facet_wrap(~coeff, scales = "free") +
+  labs(title = "Group as mean biomass")
+
+```
+
+## Richness
+
+```{r}
+```
+
+```{r}
+st_big_bm_tendancies <- group_results %>%
+  filter(abs(linear_slope) > 5000) %>%
+  .$station %>%
+  unique
+plot_big_bm_tendancies <- temporal_dynamics_plot %>%
+  filter(variable == "biomass", station %in% st_big_bm_tendancies) %>%
+  .$plot
+plot_grid(
+  plotlist = map(plot_big_bm_tendancies, 
+    ~.x + lims(x = c(0, 10), y = c(0, 155000)))
+)
+```
+
+```{r}
+rigal_shape_var <- rigal_classification %>%
+  unnest(classif) %>%
+  select(station, variable, shape_class) %>%
+  mutate(station = as.character(station))
+
+rigal_shape_var %>%
+  filter(station %in% st_decrease_increase_rigal_biomass$station) %>%
+  ggplot(aes(x = shape_class)) +
+  geom_bar() +
+  facet_wrap(~ variable) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+```
+
+```{r}
+
+```
+
+## SAX
+
+```{r, eval = FALSE}
+library(jmotif)
+loadd(full_data2)
+sax_all_variable <- full_data2 %>%
+  select(station, nb_year, biomass:log_bm) %>%
+  pivot_longer(cols = biomass:log_bm, names_to = "variable", values_to = "value") %>%
+  group_by(station, variable) %>%
+  arrange(nb_year) %>%
+  nest() %>%
+  mutate(
+    zts = map(data, function(x) znorm(x$value, threshold = 0.01)),
+    paa = map(zts, ~paa(., 3)),
+    sax = map_chr(paa, ~series_to_string(., 3))
+  ) %>%
+  ungroup()
+
+# CBA:
+sax_all_variable %>%
+  filter(station %in% cba_rigal_sax$station, !variable %in% c("biomass", "nbnode")) %>%
+  ggplot(aes(x = sax)) +
+  geom_bar() +
+  facet_wrap(facets = ~variable)
+
+sax_all_variable %>%
+  filter(
+    station %in% cba_rigal_sax$station,
+    !variable %in% c("biomass", "nbnode")
+    ) %>%
+  ggplot(aes(x = sax)) +
+  geom_bar() +
+  facet_wrap(facets = ~variable)
+
+```

### 2020-09-16 R/misc.R

@@ -3,25 +3,25 @@
 #' As devtools::use_data but choosing dest_dir 
 #'  
 #' @export
-mysave <- function (..., dir = ".", overwrite = FALSE,
-    compress = "bzip2") {
+#mysave <- function (..., dir = ".", overwrite = FALSE,
+    #compress = "bzip2") {
 
-  objs <- eval(substitute(alist(...)))
-  objs <- vapply(objs, as.character, character(1))
-  paths <- file.path(dir, paste0(objs, ".rda"))
+  #objs <- eval(substitute(alist(...)))
+  #objs <- vapply(objs, as.character, character(1))
+  #paths <- file.path(dir, paste0(objs, ".rda"))
 
-  if (any(file.exists(paths)) & !overwrite) {
-    existing_file <- objs[file.exists(paths)]
-    stop(paste0(existing_file, " already exists.\n", "Use overwrite = TRUE."))
-  }
-  message("Saving ", paste(unlist(objs), collapse = ", "),
-    " as ", paste(basename(paths), collapse = ", "), " to ",
-    dir)
-  envir <- parent.frame()
-  mapply(save, list = objs, file = paths, MoreArgs = list(envir = envir,
-      compress = compress))
-  invisible()
-}
+  #if (any(file.exists(paths)) & !overwrite) {
+    #existing_file <- objs[file.exists(paths)]
+    #stop(paste0(existing_file, " already exists.\n", "Use overwrite = TRUE."))
+  #}
+  #message("Saving ", paste(unlist(objs), collapse = ", "),
+    #" as ", paste(basename(paths), collapse = ", "), " to ",
+    #dir)
+  #envir <- parent.frame()
+  #mapply(save, list = objs, file = paths, MoreArgs = list(envir = envir,
+      #compress = compress))
+  #invisible()
+#}
 myload <- function (..., dir = ".", envir = environment()) {
 
   objs <- eval(substitute(alist(...)))

### 2020-09-16 R/plan.R

@@ -5,12 +5,14 @@ plan <- drake_plan(
   com_data = get_community_data(path = file_in(!!get_mypath("data", "community_metrics.rda"))),
   op_data = get_op_data(path = file_in(!!get_mypath("data", "op_analysis.rda"))),
   full_data = get_full_data(net = net_data, com = com_data, op = op_data),
-  filtered_time_series = get_monotonous_station(.data = full_data),
-  data = add_to_full_data(.data = filtered_time_series),
-  biomass_group = get_biomass_group(.data = data),
-  temporal_dynamics = get_lm_station(.data = data, 
+  full_data2 = add_to_full_data(.data = full_data),
+  monotonous_data = get_monotonous_station(.data = full_data2),
+  biomass_group = get_biomass_group(.data = monotonous_data),
+  temporal_dynamics = get_lm_station(.data = monotonous_data, 
     var_name = c("biomass", "log_bm", "connectance", "w_trph_lvl_avg", "richness", "weighted_connectance"),
     rhs = " ~ nb_year + surface"),
+  rigal_classification = compute_rigal_classif(data = full_data2, 
+    variable = c("biomass", "bm_std", "log_bm", "connectance", "w_trph_lvl_avg", "richness", "weighted_connectance")),
   temporal_dynamics_plot = get_temporal_dynamics_plot(temporal_dynamics = temporal_dynamics),
   temporal_dynamics_coef = get_lm_coeff(
     .data = temporal_dynamics,
@@ -27,4 +29,3 @@ plan <- drake_plan(
     output_file = file_out("report.html")
   )
 )
-

### 2020-09-17 report.Rmd
Put analysis in drake plan

@@
 ```{r}
-first_year_biomass <-
-  full_data2 %>%
-  filter(nb_year == 0) %>%
-  select(station, biomass, rel_bm, log_bm, rel_log_bm) %>%
-  pivot_longer(-station, names_to = "coeff", values_to = "first_year") %>%
-  group_by(coeff) %>%
-  mutate(com_size = ifelse(first_year < median(first_year, na.rm = TRUE), "little", "big")) %>%
-  ungroup()
-
-median_biomass <- 
-  full_data2 %>%
-  select(station, biomass, log_bm) %>%
-  pivot_longer(-station, names_to = "coeff", values_to = "biomass") %>%
-  group_by(station, coeff) %>%
-  summarise(bm_med = median(biomass, na.rm = TRUE)) %>%
-  ungroup()
-three_first_year_biomass <-
-  full_data2 %>%
-  filter(nb_year <= 2) %>%
-  select(station, nb_year, biomass, rel_bm, log_bm, rel_log_bm) %>%
-  pivot_longer(cols = biomass:rel_log_bm, names_to = "coeff", values_to = "first_year") %>%
-  group_by(station, coeff) %>%
-  summarise(first_3_year = median(first_year, na.rm = TRUE)) %>%
-  group_by(coeff) %>%
-  mutate(com_size = ifelse(first_3_year < median(first_3_year, na.rm = TRUE), "little", "big")) %>%
-  ungroup()
+loadd(full_data2)
 
@@
 
-loadd(biomass_group)
 temporal_dynamics_coef %>%
@@
 ```{r}
-
 station_summary_biomass <- full_data2 %>%
@@
 ```{r}
+get_stream_group <- function (op_analysis_path = NULL, habitat_press_path = NULL) {
+  load(file = op_analysis_path, envir = environment())
+  load(file = habitat_press_path, envir = environment())
+
+  width_classif_mean <- habitat_press %>%
+    mutate(
+      avg = if_else(width_river_mean < mean(width_river_mean, na.rm = TRUE),
+	"little", "big"),
+      median = if_else(width_river_mean < median(
+	  width_river_mean, na.rm = TRUE), "little", "big")) %>%
+  pivot_longer(cols = c(avg, median), names_to = "group_type", values_to =
+    "group") %>%
+  select(station, width_river_mean, group_type, group)
+
+protocol_station <- op_analysis %>%
+  group_by(station) %>%
+  summarise(protocol_type = unique(protocol_type))
+
+output <- width_classif_mean %>% 
+  left_join(protocol_station, by = "station")
+
+return(output)
+
+}
 #grandes/petites rivières
-myload(habitat_press, habitat_pressure, op_analysis, envir = environment(),
-  dir = get_mypath("data"))
-width_classif_mean <- habitat_press %>%
-    mutate(width_classif_mean  = if_else(width_river_mean < mean(width_river_mean, na.rm = TRUE), "little",
-      "big")) %>%
-    select(station, width_river_mean, width_classif_mean)
 habitat_press %>%
@@
 
-test <- model_int$model[[3]]
-car::vif(test)
-
 ```
@@
 
-plot_final_model <- function (ggpred = NULL, rawdata = NULL) {
+plot_final_model <- function (ggpred = NULL, rawdata = NULL, facet = FALSE) {
   ggpred %<>%
     as_tibble %>%
-    rename(increasing = group, bm_group = facet)
+    rename(increasing = group, median_group = facet)
 
@@
 
-  p <- ggplot(ggpred, aes(x = x , y = predicted, color = bm_group)) +
-    geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = bm_group), alpha =
+  if (!facet) {
+  p <- ggplot(ggpred, aes(x = x , y = predicted, color = median_group)) +
+    geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = median_group), alpha =
       .1) +
@@
       median_group))
+  } else {
+    p <- ggplot(ggpred, aes(x = x , y = predicted)) +
+      geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha =
+	.1) +
+      geom_line() 
+    p + geom_point(data = rawdata, aes(y = estimate, x = linear_slope)) +
+      facet_grid(cols = vars(median_group), scales = "free_x")
+
+  }
 
@@
 	terms = c("linear_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2,3, 4, 6]", "inc_f", "median_group"))),
+    pred5_df = map(pred5, as_tibble),
     plot = map(pred5, ~plot(.x, add.data = TRUE)),
@@
 plot_grid(plotlist = model_int$myplot, labels = model_int$coeff)
+```
+
+```{r}
+model_int$pred5_df[[1]] %>%
+  ggplot()
+
+plot_final_model(model_int$pred5[[1]], rawdata = model_int$data[[1]], facet =
+  TRUE)
 ```

### 2020-09-17 R/data_frame_manipulation.R

@@ -40,7 +40,8 @@ add_to_full_data <- function (.data = NULL) {
   output <- output %>% 
     mutate(
       log_bm = log(biomass),
-      bm_std = biomass / surface
+      bm_std = biomass / surface,
+      log_bm_std = log(bm_std)
     )
   output <- add_relative_biomass_to_start(output) 
 
@@ -56,5 +57,79 @@ add_group_station <- function (.data = NULL, group = NULL) {
     left_join(group, by = "station")
 
   return(output)
+
+}
+
+get_bm_vs_network_trends <- function (classif = NULL, bm_var = NULL,
+  coeff = c("connectance", "w_trph_lvl_avg", "richness", "weighted_connectance")
+  ) {
+
+  var_to_keep <- c("station", "linear_slope", "strd_error")
+
+  bm <- classif[classif$variable == bm_var,] %>%
+    unnest(classif) %>%
+    select(!!!var_to_keep) %>%
+    rename(bm_slope = linear_slope, bm_slope_strd_error = strd_error)
+
+  network <- classif %>%
+    filter(!variable %in% get_biomass_var()) %>%
+    unnest(classif) %>%
+    select(!!!c("variable", var_to_keep))
+
+  output <- bm %>%
+    left_join(network, by = "station")
+
+  # Add regression weight
+  output  %<>%
+    mutate(reg_weight = mean(c(abs(bm_slope / bm_slope_strd_error), abs(linear_slope / strd_error))))
+
+  return(output)
+}
+
+get_station_biomass_summary <- function (.data = NULL, bm_var = c("bm_std", "log_bm_std")) {
+
+  var_to_keep <- c("station", "nb_year", bm_var)
+  # Prepare
+  .data %<>%
+    select(!!!var_to_keep) %>%
+    pivot_longer(cols = -c(station, nb_year), names_to = "bm_var", values_to = "bm") %>%
+    group_by(station, variable)
+
+  # Summarise and make it tidy
+  bm_summary <- .data %>% 
+    summarise(
+      first_year = bm[nb_year == 0],
+      last_year = bm[nb_year == max(nb_year)],
+      first_3_year = mean(bm[nb_year %in% c(0:2)], na.rm = TRUE),
+      last_3_year = mean(bm[nb_year %in% c(max(nb_year) - 2:max(nb_year))], na.rm = TRUE),
+      median = median(bm, na.rm = TRUE),
[…]

### 2020-10-01 report.Rmd
Multi-models with various spec: try to understand multicollinearity

--- 2020-09-01 report.Rmd
@@
 library(cowplot)
+library(viridis)
+source("R/misc.R") # Define your custom code as a bunch of functions.
+source_dir(get_mypath("R")) # Define your custom code as a bunch of functions.
+
 #theme_set(theme_cowplot())
@@
 loadd(temporal_dynamics_coef)
-loadd(data)
-first_year_biomass <-
-  data %>%
-  filter(nb_year == 0) %>%
-  select(station, biomass, rel_bm, log_bm, rel_log_bm) %>%
-  pivot_longer(-station, names_to = "coeff", values_to = "first_year") %>%
-  group_by(coeff) %>%
-  mutate(com_size = ifelse(first_year < median(first_year, na.rm = TRUE), "little", "big"))
-median_biomass <- 
-  data %>%
-  select(station, biomass, log_bm) %>%
-  pivot_longer(-station, names_to = "coeff", values_to = "biomass") %>%
-  group_by(station, coeff) %>%
-  summarise(bm_med = median(biomass, na.rm = TRUE)) %>%
-  ungroup()
-
-temporal_dynamics_coef %>%
-  filter(term %in% "slope", coeff %in% c("biomass", "log_bm")) %>%
-  select(1:4) %>%
-  pivot_wider(names_from = "term", values_from = estimate) %>%
-  left_join(first_year_biomass, by = c("station", "coeff")) %>%
-  ggplot(aes(x = first_year, y = slope)) +
-  geom_point(aes(color = com_size)) +
-  facet_wrap(~coeff, scales = "free") +
-  labs(x = "First year biomass (g)", y = "Slope (g.y^-1)")
-
+loadd(temporal_dynamics_plot)
+loadd(full_data2)
 loadd(biomass_group)
-temporal_dynamics_coef %>%
-  filter(term %in% "slope", coeff %in% c("biomass", "log_bm")) %>%
-  select(1:4) %>%
-  pivot_wider(names_from = "term", values_from = estimate) %>%
-  left_join(median_biomass, by = c("station", "coeff")) %>%
-  left_join(biomass_group, by = c("station")) %>%
-  ggplot(aes(x = bm_med, y = slope)) +
-  geom_point(aes(color = com_size)) +
-  facet_wrap(~coeff, scales = "free") +
-  labs(x = "Median biomass (g)", y = "Slope (g.y^-1)")
 ```
@@
 ```{r}
-data %>%
+temporal_dynamics_coef %>%
+  filter(term %in% "slope", coeff %in% c("bm_std", "log_bm_std")) %>%
+  select(1:4) %>%
+  pivot_wider(names_from = "term", values_from = estimate) %>%
+  left_join(biomass_group, by = c("station", "coeff" = "bm_var")) %>%
+  filter(group_type == "median", summary_type %in% c("first_3_year", "median")) %>%
+  ggplot(aes(x = bm, y = slope)) +
+  geom_point(aes(color = group)) +
+  facet_wrap(coeff~summary_type, scales = "free") +
+  labs(x = "Summary of biomass (g)", y = "Slope (g.y^-1)")
+```
+
+```{r}
+full_data2 %>%
   group_by(station) %>%
@@
 # Methods
+
+## Biomass classification
+
+```{r}
+loadd(rigal_classification)
+myload(biomass_ts_sax, envir = globalenv(),dir = get_mypath("data"))
+
+biomass_classif_rigal <- rigal_classification %>%
+  filter(variable %in% c("bm_std", "log_bm_std")) %>%
+  unnest(classif) %>%
+  mutate(station = as.character(station)) %>%
+  select(station, variable,shape_class)
+
+p_biomass_classif_rigal <- biomass_classif_rigal %>%
+  ggplot(aes(x = shape_class)) +
+  geom_bar() +
+  facet_wrap(~variable) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+```
+
+## Temporal dynamics
+
+```{r}
+p_cap <- paste0(
+  "Temporal dynamics of biomass and temporal dynamics of
+  metrics for 10 randomly selected communities."
+)
+```
+
+```{r p-tmp-dyn, cache = TRUE}
+
+p <- vector(mode = "list", length = 10)
+for (i in seq_len(length(p))) {
+  to_plot <- temporal_dynamics_plot %>% 
+    filter(station == sample(temporal_dynamics_plot$station, 1))
+  p[[i]] <- cowplot::plot_grid(plotlist = to_plot$plot, labels = to_plot$station)
+}
+p
+```
+
+## Temporal dynamics decrease/increase constant
+
+### Log biomass
+
+```{r, fig.height = 45}
+st_decrease_increase_rigal <- biomass_classif_rigal %>%
+  filter(variable == "log_bm_std") %>%
+  filter(shape_class %in% c("increase_constant", "decrease_constant"))
+data_decrease_increase <- full_data2 %>%
+  filter(station %in% st_decrease_increase_rigal$station)
+
+log_bm_min_max <- map_dbl(c(min, max),
+  ~.x(data_decrease_increase$log_bm, na.rm = TRUE))
+nb_year_min_max <- map_dbl(c(min, max),
+  ~.x(data_decrease_increase$nb_year, na.rm = TRUE))
+temporal_dynamics_plot$plot %<>%
+  map(., ~ .x + lims(y = log_bm_min_max, x = nb_year_min_max))
+
+temporal_dynamics_plot %>%
+  filter(variable == "bm_std", station %in% st_decrease_increase_rigal$station) %>%
+  plot_grid(plotlist = .$plot, ncol = 3, labels = st_decrease_increase_rigal$station)
+```
+
+### Raw Biomass
+
+```{r, fig.height = 45}
+st_decrease_increase_rigal_biomass <- rigal_classification %>%
+  filter(variable == "bm_std") %>%
+  unnest(classif) %>%
+  filter(shape_class %in% c("increase_constant", "decrease_constant"))
+
+bm_min_max <- map_dbl(
+  c(min, max),
+  ~.x(data_decrease_increase$biomass, na.rm = TRUE))
+nb_year_min_max <- map_dbl(
+  c(min, max),
+  ~.x(data_decrease_increase$nb_year, na.rm = TRUE))
+temporal_dynamics_plot[temporal_dynamics_plot$variable == "biomass",]$plot %<>%
+  map(., ~ .x + lims(y = bm_min_max, x = nb_year_min_max))
+
+temporal_dynamics_plot %>%
+  filter(variable == "bm_std", station %in% st_decrease_increase_rigal_biomass$station) %>%
+  plot_grid(plotlist = .$plot, ncol = 3, labels = st_decrease_increase_rigal_biomass$station)
+```
+
+## Station grouping
+
+### Rigal station increase / decrease
+
+Les stations ont moins de 40 kilos au départ ont l'air comparable en terme de
+dynamique.
+
+```{r, eval=FALSE}
+loadd(biomass_group)
+
+p_rigal_decrease_increase_slope_st <- 
+  st_decrease_increase_rigal_biomass %>%
+  left_join(biomass_group, by = "station") %>%
+  ggplot(aes(y = linear_slope, x = value, color = shape_class)) +
+  geom_point() +
+  facet_wrap(~variable)
+p_rigal_decrease_increase_slope_st
+```
+
+### Tendancies in rigal increase / decrease
+
+```{r}
+rigal_biomass_coeff_dynamics <- st_decrease_increase_rigal_biomass %>%
+  select(station, linear_slope, strd_error) %>%
+  left_join(temporal_dynamics_coef, by = "station") %>%
+  filter(!coeff %in% get_biomass_var(), term == "slope") %>%
+  select(station, coeff, estimate, std.error, linear_slope, bm_std_error = strd_error) %>%
+  mutate(reg_weight = (abs(estimate / std.error) + abs(linear_slope / bm_std_error))/2)
+rigal_biomass_coeff_dynamics %>%
+  ggplot(aes(x = reg_weight)) +
+  geom_histogram() +
+  facet_wrap(~coeff)
+
+rigal_biomass_coeff_dynamics %>%
+  ggplot(aes(x = linear_slope, y = estimate, size = reg_weight, weight = reg_weight)) +
+  geom_point() +
+  geom_smooth() +
+  facet_wrap(~coeff, scales = "free_y")
+rigal_biomass_coeff_dynamics %>%
+  ggplot(aes(x = linear_slope, y = estimate, size = reg_weight)) +
+  geom_point() +
+  geom_smooth() +
+  facet_wrap(~coeff, scales = "free_y")
+```
+
+### With group
+
+#### Median
+
+```{r}
+##Summary of group 
+biomass_group %>%
+  filter(group_type == "median") %>%
+  ggplot(aes(x = bm)) +
+  geom_histogram() +
+  facet_wrap(bm_var~summary_type, scales = "free_x")
+
+group_results <- 
+  rigal_biomass_coeff_dynamics %>%
+  left_join(biomass_group, by = "station") %>% 
+  filter(group_type == "median", bm_var == "bm_std")
+
+p1 <- group_results %>%
+  filter(summary_type == "first_3_year") %>%
+  ggplot(aes(x = linear_slope, y = estimate, color = group,
+      size = reg_weight, weight = reg_weight)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  facet_wrap(~coeff, scales = "free_y")
+
+p3 <- group_results  %>%
+  filter(summary_type == "median") %>%
+  ggplot(aes(x = linear_slope, y = estimate, color = group, size = reg_weight, weight = reg_weight)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  facet_wrap(~coeff, scales = "free_y")
+
+p1
+p3
+```
+
+#### Little and big rivers
+
+```{r}
+loadd(stream_group)
+#grandes/petites rivières
+stream_group %>%
+  ggplot(aes(x = width_river_mean, fill = group)) +
+  geom_histogram() +
+  facet_grid(~group_type)
+
+stream_group %>%
+  filter(group_type == "median") %>%
+  ggplot(aes(x = width_river_mean, fill = protocol_type)) +
+  geom_histogram()
+
+stream_group %>%
+  filter(group_type == "median") %>%
+  left_join(
+    biomass_group %>%
+    filter(group_type == "median", summary_type == "median") %>%
+    select(-group_type, -summary_type, -group),
+  by = "station"
+  ) %>%
+  filter(!is.na(protocol_type)) %>%
+  ggplot(aes(x = bm, fill = protocol_type)) +
+  geom_histogram() +
+  facet_wrap(~bm_var, scales = "free_x")
+```
+
+```{r}
+group_results_stream_size <- 
+  group_results %>%
+  left_join(
+    filter(stream_group, group_type == "median") %>%
+      rename(stream_group = group) %>% select(-group_type)
+    , by = "station")
+
+group_results_stream_size %>%
+  filter(summary_type == "first_3_year", linear_slope < 8) %>%
+  ggplot(aes(x = linear_slope, y = estimate, color = protocol_type, size = reg_weight, weight = reg_weight)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  facet_wrap(~coeff, scales = "free_y") +
+  labs(title = "Group as protocol type")
+
+group_results_stream_size %>%
+  filter(summary_type == "first_3_year", linear_slope < 8) %>%
+  ggplot(aes(x = linear_slope, y = estimate, color = protocol_type, size = reg_weight, weight = reg_weight)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  facet_wrap(~coeff, scales = "free_y") +
+  labs(title = "Group as mean river size")
+
+group_results_stream_size %>%
+  filter(summary_type == "first_3_year", linear_slope < 8) %>%
+  ggplot(aes(x = linear_slope, y = estimate, color = group, size = reg_weight, weight = reg_weight)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  facet_wrap(~coeff, scales = "free_y") +
+  labs(title = "Group as mean river size")
+
+group_results_stream_size %>%
+  filter(summary_type == "median", linear_slope < 8) %>%
+  ggplot(aes(x = linear_slope, y = estimate, color = group, size = reg_weight, weight = reg_weight)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  facet_wrap(~coeff, scales = "free_y") +
+  labs(title = "Group as mean biomass")
+```
+
+# Patterns
+
+```{r}
+loadd(bm_net_group)
+loadd(log_bm_net_group)
+
+bm_net_group %>%
+  filter(!is.na(protocol_type)) %>%
+  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm), size = reg_weight, weight = reg_weight)) +
+  geom_point() +
+  scale_color_viridis() +
+  #geom_smooth(method = "lm") +
+  facet_grid(variable~protocol_type, scales = "free") +
+  labs(title = "Group as mean biomass")
+
+```
+
+# Correlation
+
+```{r}
+cor_bm_net <- bm_net_group %>%
+  select(bm_slope, variable, linear_slope, bm, width_river_mean) %>%
+  pivot_wider(names_from = variable, values_from = linear_slope) 
+corrplot::corrplot(cor(na.omit(cor_bm_net)), type = "upper")
+
+library(ade4)
+library(factoextra)
+res.pca <- dudi.pca(na.omit(cor_bm_net),
+                    scannf = FALSE,   # Cacher le scree plot
+                    nf = 3            # Nombre d'axes gardés
+                    )
+screeplot(res.pca, main = "Screeplot - Eigenvalues")
+p1 <- fviz_pca_var(res.pca,
+  col.var = "contrib", 
+  gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
+  repel = TRUE     
+)
+p2 <- fviz_pca_var(res.pca,
+  axes = c(1, 3),
+  col.var = "contrib", 
+  gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
+  repel = TRUE     
+)
+
+p3 <- fviz_pca_var(res.pca,
+  axes = c(2, 3),
+  col.var = "contrib", 
+  gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
+  repel = TRUE     
+)
+plot_grid(p1, p2, p3)
+```
+
+# Statistical models
+
+## Raw bm
+
+```{r, eval = FALSE}
+model_int <- compute_my_lm_vs_net_model(bm_net_group, var_to_group = c("variable"))
+model_vif <- get_vif(model_int, model_cols = c("mod3", "mod5",
+    "mod6", "mod8", "mod9"))
+model_vif %>%
+  ggplot(aes(y = vif, x = term)) +
+  geom_hline(yintercept = 10) +
+  geom_bar(stat = "identity") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  facet_grid(model_type~variable)
+```
+
+```{r, eval = FALSE}
+library(yhat)
+test <- model_int$mod3[[1]]
+CCData <- commonalityCoefficients(model_int$data[[1]],
+  "linear_slope",
+  list("bm_slope", "inc_f", "bm"), "F")
+CCData
+
+test_data <- model_int$data[[1]]
+lm_test <- lm(
+  formula = linear_slope ~ bm_slope*inc_f*bm,
+  weights = reg_weight
+)
+test <- regr(lm_test)
+```
+
+### Effect of protocol type on the model validity
+
+```{r}
+model_by_protocol <- compute_my_lm_vs_net_model(
+  filter(bm_net_group, !is.na(protocol_type)),
+  var_to_group = c("variable", "protocol_type"),
+  #var_to_scale = c("log_bm") 
+)
+model_var <- tidyselect::vars_select(names(model_by_protocol), starts_with("mod"))
+model_vif <- get_vif(model_by_protocol,
+  model_cols = model_var)
+protocol_vec <- model_vif$protocol_type %>% unique
+p_vif_protocol <- map(protocol_vec, function (x) {
+  model_vif %>%
+    filter(protocol_type == x) %>%
+    ggplot(aes(y= vif, x = term)) +
+    geom_hline(yintercept = 10) +
+    geom_bar(stat = "identity") +
+    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+    labs(title = paste0("Protocol type: ", x)) +
+    facet_grid(model_type~variable, scales = "free_y")
+  })
+p_vif_protocol[[1]]
+p_vif_protocol[[2]]
+```
+```{r}
+bm_net_group %>%
+  filter(variable == "connectance") %>%
+  ggplot(aes(x = bm_slope, y = bm)) +
+  geom_point()
+
+```
+
+### Current best model
+
+$$
+Y = \alpha + \beta_1D_b + \beta_2D_bI_b + \beta_3D_bI_bB
+$$
+
+```{r, eval = FALSE}
+res_mod <- model_by_protocol %>%
+  filter(protocol_type == "complete") %>%
+  select(-data) %>%
+  pivot_longer(cols = c(mod1:last_col()),
+    names_to = "model", values_to = "model_obj") %>%
+  mutate(
+    resume = map(model_obj, summary),
+    anova = map(model_obj, anova)
+  )
+```
+
+```{r, eval = FALSE}
+filter(res_mod, model == "mod_inc_bm")[["resume"]]
+filter(res_mod, model == "mod_inc_bm")[["anova"]]
+
+filter(res_mod, model == "mod_bm_inc")[["resume"]]
+filter(res_mod, model == "mod_bm_inc")[["anova"]]
+```
+
+```{r, eval = FALSE}
+pred <- res_mod %>%
+  filter(model == "mod4") %>%
+  mutate(
+    pred = map(model_obj, ~ggpredict(.x,
+	terms = c("bm_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2, 3, 4, 6]", "bm [quart2]"))),
+    pred_df = map(pred, as_tibble),
+    plot = map(pred, ~plot(.x, add.data = FALSE)),
+    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
+    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
+  )
+plot_grid(plotlist = pred$plot)
+```
+
+```{r, eval = FALSE}
+res_mod7 %<>%
+  mutate(
+    pred7 = map(mod7, ~ggpredict(.x,
+	terms = c("bm_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2, 3, 4, 6]", "bm [quart2]", "inc_f"))),
+    pred7_df = map(pred7, as_tibble),
+    plot = map(pred7, ~plot(.x, add.data = FALSE)),
+    plot_data = map(pred7, ~plot(.x, add.data = TRUE)),
+    myplot = map2(pred7, data, ~plot_final_model(ggpred = .x, rawdata = .y))
+  )
+
+#plot_final_model(model_int$pred5[[1]], model_int$data[[1]])
+plot_grid(plotlist = res_mod7$plot, labels = res_mod7$variable)
+plot_grid(plotlist = res_mod7$plot_data, labels = res_mod7$variable)
+
+test <- model_int$data[[1]]
+res_mod7$pred7_df[[1]]
+test %>%
+  ggplot(aes(x = bm_slope, y = linear_slope, weight = reg_weight, size = reg_weight)) +
+  geom_smooth(method = "lm") +
+  geom_point()
+
+#pred_test <-
+  #model_int$pred5_df[[1]] %>%
+  #as_tibble %>%
+  #rename(increasing = group, group = facet) %>%
+  #filter(increasing == FALSE & x < 0 | increasing == TRUE & x > 0)
+
+#p <- ggplot(pred_test, aes(x = x , y = predicted, color = group)) +
+  #geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group), alpha =
+    #.1) +
+  #geom_line() +
+  #geom_point(data = rename(test,
+      #predicted = linear_slope, x = bm_slope),
+    #aes(x = x, y = predicted),
+    #inherit.aes = FALSE)
+```
+
+### Is the model valid with log_bm ?
+
+```{r}
+log_bm_net_group %>%
+  filter(!is.na(protocol_type)) %>%
+  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm), size = reg_weight, weight = reg_weight)) +
+  geom_point() +
+  scale_color_viridis() +
+  #geom_smooth(method = "lm") +
+  facet_grid(variable~protocol_type, scales = "free") +
+  labs(title = "Log biomass")
+
+log_bm_net_group %>%
+  filter(variable == "connectance") %>%
+  ggplot(aes(x = bm_slope, y = bm)) +
+  geom_point()
+```
+
+```{r}
+loadd(log_bm_net_group)
+model_log <- compute_my_lm_vs_net_model(
+  log_bm_net_group, var_to_group = c("variable"),
+)
+
+model_var <- tidyselect::vars_select(names(model_by_protocol), starts_with("mod"))
+model_log_vif <- get_vif(model_log, model_cols = model_var)
+
+model_log_vif %>%
+  ggplot(aes(y= vif, x = term)) +
+  geom_hline(yintercept = 10) +
+  geom_bar(stat = "identity") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  facet_grid(model_type~variable)
+```
+
+```{r}
+model_by_protocol <- compute_my_lm_vs_net_model(
+  filter(log_bm_net_group, !is.na(protocol_type)),
+  var_to_group = c("variable", "protocol_type")
+)
+
+model_var <- tidyselect::vars_select(names(model_by_protocol), starts_with("mod"))
+model_vif <- get_vif(model_by_protocol,
+  model_cols = model_var)
+
+protocol_vec <- model_vif$protocol_type %>% unique
+p_vif_protocol <- map(protocol_vec, function (x) {
+  model_vif %>%
+    filter(protocol_type == x) %>%
+    ggplot(aes(y= vif, x = term)) +
+    geom_hline(yintercept = 10) +
+    geom_bar(stat = "identity") +
+    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+    labs(title = paste0("Protocol type: ", x)) +
+    facet_grid(model_type~variable, scales = "free_y")
+  })
+p_vif_protocol[[1]]
+p_vif_protocol[[2]]
+```
+
+```{r}
+res_mod <- model_by_protocol %>%
+  filter(protocol_type == "complete") %>%
+  select(-data) %>%
+  pivot_longer(cols = all_of(model_var),
+    names_to = "model", values_to = "model_obj") %>%
+  mutate(
+    resume = map(model_obj, summary),
+    anova = map(model_obj, anova)
+  )
+```
+
+```{r}
+filter(res_mod, model == "mod_inc_log_bm")[["resume"]]
+filter(res_mod, model == "mod_inc_log_bm")[["anova"]]
+```
+
+```{r}
+filter(res_mod, model == "mod_log_bm_inc")[["resume"]]
+filter(res_mod, model == "mod_log_bm_inc")[["anova"]]
+```
+
+```{r, eval = FALSE}
+pred <- res_mod %>%
+  filter(model == "mod4") %>%
+  mutate(
+    pred = map(model_obj, ~ggpredict(.x,
+	terms = c("bm_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2, 3, 4, 6]", "bm [quart2]"))),
+    pred_df = map(pred, as_tibble),
+    plot = map(pred, ~plot(.x, add.data = FALSE)),
+    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
+  )
+plot_grid(plotlist = pred$plot)
+```
+
+### Can we predict the model without all simple effects?
+
+```{r, eval = FALSE}
+# Perform a valid model 
+pred <- model_int %>%
+  select(-data, -mod4) %>%
+  pivot_longer(cols = c(mod1:mod5), names_to = "model_type", values_to =
+    "mod_obj") %>%
+  mutate(
+    pred_ref = map2(mod_obj, model_type, function (x, y) {
+       if (y %in% c("mod3", "mod5"))
+	 terms_spec <- c("bm_slope", "inc_f", "bm")
+       else
+	 terms_spec <- c("bm_slope", "inc_f", "bm_group") 
+      ggpredict(x, terms = terms_spec)
+      }
+    ),
+    pred_cte = map2(mod_obj, model_type, function (x, y) {
+       if (y %in% c("mod3", "mod5"))
+	 terms_spec <- c("linear_slope", "inc_f", "bm")
+       else
+	 terms_spec <- c("linear_slope", "inc_f", "bm_group") 
+      ggeffect(x, terms = terms_spec)
+      }
+    )
+  )
+
+pred %<>%
+  mutate(
+  plot_pred_ref = map(pred_ref, plot, add.data = TRUE),
+  plot_pred_cte = map(pred_cte, plot, add.data = TRUE)
+  )
+pred_richness <- pred %>%
+  filter(variable == "richness", model_type == "mod3")
+
+pred$plot_pred_ref[[1]]
+pred$plot_pred_cte[[1]]
+pred$plot_pred[[2]]
+pred$plot_pred[[3]]
+pred$plot_pred_ref[[4]]
+```
+
+```{r, eval = FALSE}
+library(ggeffects)
+mydf <- ggpredict(model_int$mod3[[1]], terms = c("linear_slope", "inc_f",
+    "bm"))
+plot(mydf, add.data = TRUE)
+
+```
+
+```{r, eval = FALSE}
+model_log %<>%
+  mutate(
+    pred5 = map(mod3, ~ggpredict(.x,
+	terms = c("linear_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2, 3, 4, 6]", "inc_f", "bm"))),
+    pred5_df = map(pred5, as_tibble),
+    plot = map(pred5, ~plot(.x, add.data = TRUE)),
+    myplot = map2(pred5, data, ~plot_final_model(ggpred = .x, rawdata = .y))
+  )
+
+#plot_final_model(model_int$pred5[[1]], model_int$data[[1]])
+plot_grid(plotlist = model_int$plot, labels = model_int$variable)
+model_int$plot[[1]]
+summary(model_int$mod3[[1]])
+test <- model_int$data[[1]]
+model_int$pred5_df[[1]]
+test %>%
+  ggplot(aes(x = bm_slope, y = linear_slope, weight = reg_weight, size = reg_weight)) +
+  geom_smooth(method = "lm") +
+  geom_point()
+
+pred_test <-
+  model_int$pred5_df[[1]] %>%
+  as_tibble %>%
+  rename(increasing = group, group = facet) %>%
+  filter(increasing == FALSE & x < 0 | increasing == TRUE & x > 0)
+
+p <- ggplot(pred_test, aes(x = x , y = predicted, color = group)) +
+  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group), alpha =
+    .1) +
+  geom_line() +
+  geom_point(data = rename(test,
+      predicted = linear_slope, x = bm_slope),
+    aes(x = x, y = predicted),
+    inherit.aes = FALSE)
+```
+
+```{r, eval = FALSE}
+model_int$pred5_df[[1]] %>%
+  ggplot()
+
+plot_final_model(model_int$pred5[[1]], rawdata = model_int$data[[1]], facet =
+  TRUE)
+```
+
+```{r, eval = FALSE}
+library(segmented)
+
+mod_tlvl <- lm(estimate ~ linear_slope, model_int$data[[2]])
+mod_tlvl <- lm(
+  estimate ~ linear_slope*decreasing*group,#(linear_slope < 0)*linear_slope + (linear_slope >= 0)*linear_slope,
+  mutate(model_int$data[[2]], decreasing = linear_slope < 0)
+)
+seg_tlvl <- segmented(mod_tlvl, seg.Z=~linear_slope)
+plot(seg_tlvl)
+
+mod_richness <- lm(estimate ~ linear_slope, model_int$data[[2]])
+test <- segmented(mod_richness, seg.Z=~linear_slope)
+plot(test)
+
+car::vif(test)
+```
+
+## Richness
+
+```{r}
+knitr::opts_chunk$set(
+  eval = FALSE 
+)
+```
+
+```{r}
+st_big_bm_tendancies <- group_results %>%
+  filter(abs(linear_slope) > 5000) %>%
+  .$station %>%
+  unique
+plot_big_bm_tendancies <- temporal_dynamics_plot %>%
+  filter(variable == "biomass", station %in% st_big_bm_tendancies) %>%
+  .$plot
+plot_grid(
+  plotlist = map(plot_big_bm_tendancies, 
+    ~.x + lims(x = c(0, 10), y = c(0, 155000)))
+)
+```
+
+```{r}
+rigal_shape_var <- rigal_classification %>%
+  unnest(classif) %>%
+  select(station, variable, shape_class) %>%
+  mutate(station = as.character(station))
+
+rigal_shape_var %>%
+  filter(station %in% st_decrease_increase_rigal_biomass$station) %>%
+  ggplot(aes(x = shape_class)) +
+  geom_bar() +
+  facet_wrap(~ variable) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+```
+
+```{r}
+
+```
+
+## SAX
+
+```{r, eval = FALSE}
+library(jmotif)
+loadd(full_data2)
+sax_all_variable <- full_data2 %>%
+  select(station, nb_year, biomass:log_bm) %>%
+  pivot_longer(cols = biomass:log_bm, names_to = "variable", values_to = "value") %>%
+  group_by(station, variable) %>%
+  arrange(nb_year) %>%
+  nest() %>%
+  mutate(
+    zts = map(data, function(x) znorm(x$value, threshold = 0.01)),
+    paa = map(zts, ~paa(., 3)),
+    sax = map_chr(paa, ~series_to_string(., 3))
+  ) %>%
+  ungroup()
+
+# CBA:
+sax_all_variable %>%
+  filter(station %in% cba_rigal_sax$station, !variable %in% c("biomass", "nbnode")) %>%
+  ggplot(aes(x = sax)) +
+  geom_bar() +
+  facet_wrap(facets = ~variable)
+
+sax_all_variable %>%
+  filter(
+    station %in% cba_rigal_sax$station,
+    !variable %in% c("biomass", "nbnode")
+    ) %>%
+  ggplot(aes(x = sax)) +
+  geom_bar() +
+  facet_wrap(facets = ~variable)
+
+```

### 2020-10-01 R/statistical_model.R

@@ -109,3 +109,53 @@ compute_lm_temporal_trends <- function (.data = NULL, y = "biomass", x = "connec
   return(output)
 }
 
+#' Linear models bm versus network 
+
+compute_my_lm_vs_net_model <- function (
+  .df = NULL,
+  var_to_group = c("variable", "protocol_type"),
+  var_to_scale = NULL
+  ) {
+
+  .df %<>%
+    mutate(
+      increasing = linear_slope > 0,
+      inc_f = as.factor(increasing),
+      log_bm = log(bm)
+    ) 
+
+  if (!is.null(var_to_scale)) {
+    .df %<>%
+      mutate_at(vars(all_of(var_to_scale)), scale)
+  }
+  
+  .df %<>%
+  group_by_at(vars(all_of(var_to_group))) %>%
+  nest() %>%
+    mutate(
+      mod_all_group = map(data, ~lm(linear_slope ~ bm_slope*inc_f*bm_group, .x, weights = reg_weight)),
+      mod_medium_group = map(data, ~lm(
+	   linear_slope~ bm_slope + bm_slope:inc_f + bm_slope:bm_group +
+	    bm_slope:inc_f:bm_group,
+	  .x, weights = reg_weight)),
+     mod_medium_bm = map(data, ~lm(
+	   linear_slope ~ bm_slope + bm_slope:inc_f + bm_slope:bm +
+	    bm_slope:inc_f:bm,
+	  .x, weights = reg_weight)),
+      mod_min_bm = map(data, ~lm(
+	  linear_slope ~ bm_slope:inc_f + bm_slope:bm +
+	    bm_slope:inc_f:bm,
+	  .x, weights = reg_weight)),
+      mod_all_bm = map(data, ~lm(linear_slope ~ bm_slope*inc_f*bm, .x, weights = reg_weight)),
+      mod_all_log_bm = map(data, ~lm(linear_slope ~ bm_slope*inc_f*log_bm, .x, weights = reg_weight)),
+      mod_bm = map(data, ~lm(linear_slope ~ bm_slope*bm, .x, weights = reg_weight)),
+      mod_bm_inc = map(data, ~lm(linear_slope ~ bm_slope*bm + inc_f, .x, weights = reg_weight)),
+      mod_log_bm = map(data, ~lm(linear_slope ~ bm_slope*log_bm, .x, weights = reg_weight)),
[…]

### 2020-10-05 report.Rmd
Fix regression weigth + plot of prediction + data

@@
 author: "Alain Danet"
-output: html_document
+date: "`r Sys.Date()`"
+output:
+  prettydoc::html_pretty:
+    theme: cayman
+    highlight: github
+    math: katex
 ---
@@
 ```{r p-bivar, cache = TRUE, fig.cap = bivar_cap, fig.height = 10}
-
 cowplot::plot_grid(
@@
 log_bm_min_max <- map_dbl(c(min, max),
-  ~.x(data_decrease_increase$log_bm, na.rm = TRUE))
+  ~.x(data_decrease_increase$log_bm_std, na.rm = TRUE))
 nb_year_min_max <- map_dbl(c(min, max),
@@
 temporal_dynamics_plot %>%
-  filter(variable == "bm_std", station %in% st_decrease_increase_rigal$station) %>%
+  filter(variable == "log_bm_std", station %in% st_decrease_increase_rigal$station) %>%
   plot_grid(plotlist = .$plot, ncol = 3, labels = st_decrease_increase_rigal$station)
@@
   c(min, max),
-  ~.x(data_decrease_increase$biomass, na.rm = TRUE))
+  ~.x(data_decrease_increase$bm_std, na.rm = TRUE))
 nb_year_min_max <- map_dbl(
@@
   ~.x(data_decrease_increase$nb_year, na.rm = TRUE))
-temporal_dynamics_plot[temporal_dynamics_plot$variable == "biomass",]$plot %<>%
+temporal_dynamics_plot[temporal_dynamics_plot$variable == "bm_std",]$plot %<>%
   map(., ~ .x + lims(y = bm_min_max, x = nb_year_min_max))
@@
   left_join(biomass_group, by = "station") %>%
-  ggplot(aes(y = linear_slope, x = value, color = shape_class)) +
+  ggplot(aes(y = linear_slope, x = bm_slope, color = shape_class)) +
   geom_point() +
@@
 ```{r}
-rigal_biomass_coeff_dynamics <- st_decrease_increase_rigal_biomass %>%
-  select(station, linear_slope, strd_error) %>%
-  left_join(temporal_dynamics_coef, by = "station") %>%
-  filter(!coeff %in% get_biomass_var(), term == "slope") %>%
-  select(station, coeff, estimate, std.error, linear_slope, bm_std_error = strd_error) %>%
-  mutate(reg_weight = (abs(estimate / std.error) + abs(linear_slope / bm_std_error))/2)
-rigal_biomass_coeff_dynamics %>%
+loadd(bm_net_group, log_bm_net_group, bm_vs_net_trends)
+bm_vs_net_trends %>%
   ggplot(aes(x = reg_weight)) +
   geom_histogram() +
-  facet_wrap(~coeff)
+  facet_wrap(~variable)
 
-rigal_biomass_coeff_dynamics %>%
-  ggplot(aes(x = linear_slope, y = estimate, size = reg_weight, weight = reg_weight)) +
+bm_net_group %>%
+  ggplot(aes(x = bm_slope, y = linear_slope, size = reg_weight, weight = reg_weight, color = log(bm))) +
   geom_point() +
+  scale_color_viridis() +
+  geom_vline(xintercept = 0, color = "red") +
   geom_smooth() +
-  facet_wrap(~coeff, scales = "free_y")
-rigal_biomass_coeff_dynamics %>%
-  ggplot(aes(x = linear_slope, y = estimate, size = reg_weight)) +
+  facet_wrap(~variable, scales = "free_y") +
+  labs(x = "Biomass trend (g.m-1.y-1)", y = "Network trend (U.y-1)")
+
+log_bm_net_group %>%
+  ggplot(aes(x = bm_slope, y = linear_slope, size = reg_weight, weight = reg_weight, color = log(bm))) +
   geom_point() +
+  scale_color_viridis() +
+  geom_vline(xintercept = 0, color = "red") +
   geom_smooth() +
-  facet_wrap(~coeff, scales = "free_y")
+  facet_wrap(~variable, scales = "free_y") +
+  labs(x = "Log Biomass trend (g.m-1.y-1)", y = "Network trend (U.y-1)")
 ```
@@
   facet_wrap(bm_var~summary_type, scales = "free_x")
-
+```
+```{r, eval = FALSE}
 group_results <- 
@@
 
-```{r}
-group_results_stream_size <- 
-  group_results %>%
-  left_join(
-    filter(stream_group, group_type == "median") %>%
-      rename(stream_group = group) %>% select(-group_type)
-    , by = "station")
-
-group_results_stream_size %>%
-  filter(summary_type == "first_3_year", linear_slope < 8) %>%
-  ggplot(aes(x = linear_slope, y = estimate, color = protocol_type, size = reg_weight, weight = reg_weight)) +
-  geom_point() +
-  geom_smooth(method = "lm") +
-  facet_wrap(~coeff, scales = "free_y") +
-  labs(title = "Group as protocol type")
-
-group_results_stream_size %>%
-  filter(summary_type == "first_3_year", linear_slope < 8) %>%
-  ggplot(aes(x = linear_slope, y = estimate, color = protocol_type, size = reg_weight, weight = reg_weight)) +
-  geom_point() +
-  geom_smooth(method = "lm") +
-  facet_wrap(~coeff, scales = "free_y") +
-  labs(title = "Group as mean river size")
-
-group_results_stream_size %>%
-  filter(summary_type == "first_3_year", linear_slope < 8) %>%
-  ggplot(aes(x = linear_slope, y = estimate, color = group, size = reg_weight, weight = reg_weight)) +
-  geom_point() +
-  geom_smooth(method = "lm") +
-  facet_wrap(~coeff, scales = "free_y") +
-  labs(title = "Group as mean river size")
-
-group_results_stream_size %>%
-  filter(summary_type == "median", linear_slope < 8) %>%
-  ggplot(aes(x = linear_slope, y = estimate, color = group, size = reg_weight, weight = reg_weight)) +
-  geom_point() +
-  geom_smooth(method = "lm") +
-  facet_wrap(~coeff, scales = "free_y") +
-  labs(title = "Group as mean biomass")
-```
-
 # Patterns
@@
 loadd(log_bm_net_group)
+
+bm_net_group %>%
+  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm), size = reg_weight, weight = reg_weight)) +
+  geom_point() +
+  scale_color_viridis() +
+  #geom_smooth(method = "lm") +
+  facet_wrap(~variable, scales = "free") +
+  labs(title = "Group as mean biomass")
+
+bm_net_group %>%
+  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
+  geom_point() +
+  scale_color_viridis() +
+  geom_errorbar(aes(
+      xmin = bm_slope - bm_slope_strd_error,
+      xmax = bm_slope + bm_slope_strd_error),
+    alpha = .2
+    ) +
+  geom_errorbar(aes(
+      ymin = linear_slope - linear_slope_strd_error,
+      ymax = linear_slope + linear_slope_strd_error),
+    alpha = .2
+    ) +
+  facet_wrap(~variable, scales = "free") +
+  labs(title = "Group as mean biomass")
 
@@
   labs(title = "Group as mean biomass")
-
 ```
@@
 
-```{r, eval = FALSE}
-model_int <- compute_my_lm_vs_net_model(bm_net_group, var_to_group = c("variable"))
-model_vif <- get_vif(model_int, model_cols = c("mod3", "mod5",
-    "mod6", "mod8", "mod9"))
-model_vif %>%
+```{r, eval = TRUE}
+loadd(model_bm, model_bm_vif)
+
+model_bm_vif %>%
   ggplot(aes(y = vif, x = term)) +
@@
   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  facet_grid(model_type~variable)
+  facet_grid(model_type~variable, scales = "free_x")
 ```
@@
 ```{r}
-model_by_protocol <- compute_my_lm_vs_net_model(
-  filter(bm_net_group, !is.na(protocol_type)),
-  var_to_group = c("variable", "protocol_type"),
-  #var_to_scale = c("log_bm") 
-)
-model_var <- tidyselect::vars_select(names(model_by_protocol), starts_with("mod"))
-model_vif <- get_vif(model_by_protocol,
-  model_cols = model_var)
-protocol_vec <- model_vif$protocol_type %>% unique
+loadd(model_bm_by_protocol, model_bm_by_protocol_vif)
+
+protocol_vec <- model_bm_by_protocol_vif$protocol_type %>% unique
 p_vif_protocol <- map(protocol_vec, function (x) {
-  model_vif %>%
+  model_bm_by_protocol_vif %>%
     filter(protocol_type == x) %>%
@@
 ```
+
+```{r, eval = FALSE}
+filter(model_bm_by_protocol_vif, model_type == "mod_bm_quad")
+```
+
 ```{r}
@@
   geom_point()
-
 ```
@@
 
-```{r, eval = FALSE}
-res_mod <- model_by_protocol %>%
-  filter(protocol_type == "complete") %>%
-  select(-data) %>%
-  pivot_longer(cols = c(mod1:last_col()),
-    names_to = "model", values_to = "model_obj") %>%
-  mutate(
-    resume = map(model_obj, summary),
-    anova = map(model_obj, anova)
-  )
+```{r, eval = TRUE}
+loadd(model_bm_by_protocol_summary)
+model_bm_by_protocol_summary %<>%
+  filter(protocol_type == "complete")
 ```
 
-```{r, eval = FALSE}
-filter(res_mod, model == "mod_inc_bm")[["resume"]]
-filter(res_mod, model == "mod_inc_bm")[["anova"]]
+```{r, eval = TRUE}
+filter(model_bm_by_protocol_summary, model == "mod_inc_bm")[["resume"]]
+filter(model_bm_by_protocol_summary, model == "mod_inc_bm")[["anova"]]
 
-filter(res_mod, model == "mod_bm_inc")[["resume"]]
-filter(res_mod, model == "mod_bm_inc")[["anova"]]
+filter(model_bm_by_protocol_summary, model == "mod_bm_inc")[["resume"]]
+filter(model_bm_by_protocol_summary, model == "mod_bm_inc")[["anova"]]
+
+filter(model_bm_by_protocol_summary, model == "mod_bm_quad")[["resume"]]
+filter(model_bm_by_protocol_summary, model == "mod_bm_quad")[["anova"]]
+
+filter(model_bm_by_protocol_summary, model == "mod_bm_quad2")[["resume"]]
+filter(model_bm_by_protocol_summary, model == "mod_bm_quad2")[["anova"]]
 ```
 
-```{r, eval = FALSE}
-pred <- res_mod %>%
-  filter(model == "mod4") %>%
+```{r, eval = TRUE}
+pred <- model_bm_by_protocol_summary %>%
+  filter(model == "mod_bm_inc") %>%
+  mutate(
+    pred = map(model_obj, ~ggpredict(.x,
+	terms = c("bm_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2, 3, 4, 6]", "bm [quart2]", "inc_f"))),
+    pred_df = map(pred, as_tibble),
+    plot = map(pred, ~plot(.x, add.data = FALSE)),
+    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
+    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
+  )
+plot_grid(plotlist = pred$plot, labels = pred$variable)
+```
+
+```{r}
+pred <- model_bm_by_protocol_summary %>%
+  filter(model == "mod_bm_quad2") %>%
   mutate(
@@
   )
-plot_grid(plotlist = pred$plot)
+plot_grid(plotlist = pred$plot_data, labels = pred$variable)
 ```
 
-```{r, eval = FALSE}
-res_mod7 %<>%
+#### All protocol
+
+```{r}
+loadd(model_bm_summary)
+```
+
+```{r}
+filter(model_bm_summary, model == "mod_inc_bm")[["resume"]]
+filter(model_bm_summary, model == "mod_inc_bm")[["anova"]]
+
+filter(model_bm_summary, model == "mod_bm_inc")[["resume"]]
+filter(model_bm_summary, model == "mod_bm_inc")[["anova"]]
+
+filter(model_bm_summary, model == "mod_bm_quad")[["resume"]]
+filter(model_bm_summary, model == "mod_bm_quad")[["anova"]]
+
+filter(model_bm_summary, model == "mod_bm_quad2")[["resume"]]
+filter(model_bm_summary, model == "mod_bm_quad2")[["anova"]]
+```
+
+```{r}
+pred_bm_quad2 <- model_bm_summary %>%
+  filter(model == "mod_bm_quad2") %>%
   mutate(
-    pred7 = map(mod7, ~ggpredict(.x,
-	terms = c("bm_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2, 3, 4, 6]", "bm [quart2]", "inc_f"))),
-    pred7_df = map(pred7, as_tibble),
-    plot = map(pred7, ~plot(.x, add.data = FALSE)),
-    plot_data = map(pred7, ~plot(.x, add.data = TRUE)),
-    myplot = map2(pred7, data, ~plot_final_model(ggpred = .x, rawdata = .y))
+    pred = map(model_obj, ~ggpredict(.x,
+	terms = c("bm_slope", "bm [quart2]"))),
+    pred_df = map(pred, as_tibble),
+    plot = map(pred, ~plot(.x, add.data = FALSE)),
+    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
+    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
+  )
+plot_grid(plotlist = pred_bm_quad2$plot, labels = pred_bm_quad2$variable)
+pred_bm_quad2_plot <- map2(model_bm$data, pred_bm_quad2$pred_df, plot_pred_data)
+
+plot_grid(plotlist = pred_bm_quad2_plot, labels = pred_bm_quad2$variable)
+
+pred_bm_quad <- model_bm_summary %>%
+  filter(model == "mod_bm_quad") %>%
+  mutate(
+    pred = map(model_obj, ~ggpredict(.x,
+	terms = c("bm_slope", "bm [quart2]"))),
+    pred_df = map(pred, as_tibble),
+    plot = map(pred, ~plot(.x, add.data = FALSE)),
+    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
+    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
   )
 
-#plot_final_model(model_int$pred5[[1]], model_int$data[[1]])
-plot_grid(plotlist = res_mod7$plot, labels = res_mod7$variable)
-plot_grid(plotlist = res_mod7$plot_data, labels = res_mod7$variable)
+pred_bm_quad_plot <- map2(model_bm$data, pred_bm_quad$pred_df, plot_pred_data)
+plot_grid(plotlist = pred_bm_quad_plot, labels = pred_bm_quad2$variable)
+```
 
-test <- model_int$data[[1]]
-res_mod7$pred7_df[[1]]
-test %>%
-  ggplot(aes(x = bm_slope, y = linear_slope, weight = reg_weight, size = reg_weight)) +
-  geom_smooth(method = "lm") +
-  geom_point()
+#### Quadratic two
 
-#pred_test <-
-  #model_int$pred5_df[[1]] %>%
-  #as_tibble %>%
-  #rename(increasing = group, group = facet) %>%
-  #filter(increasing == FALSE & x < 0 | increasing == TRUE & x > 0)
+```{r}
+#model_bm$data[[1]] %>%
+  #ggplot(aes(x = bm_slope, y = linear_slope, fill = log(bm)), shape = 23, size = 4) +
+  #scale_fill_viridis() +
+  #geom_point() +
+  #geom_line(
+    #data = pred_bm_quad2$pred_df[[1]] %>%
+      #rename(bm_f = group, bm_slope = x, linear_slope = predicted),
+    #aes(y = linear_slope, x = bm_slope, color = bm_f),
+    #inherit.aes = FALSE)
 
-#p <- ggplot(pred_test, aes(x = x , y = predicted, color = group)) +
-  #geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group), alpha =
-    #.1) +
-  #geom_line() +
-  #geom_point(data = rename(test,
-      #predicted = linear_slope, x = bm_slope),
-    #aes(x = x, y = predicted),
-    #inherit.aes = FALSE)
+test <- map2(model_bm$data, pred_bm_quad2$pred_df, function (.data, pred) {
+
+  .data %>%
+    ggplot(aes(x = bm_slope, y = linear_slope, fill = log(bm)), shape = 23, size = 4) +
+    scale_fill_viridis() +
+    geom_point() +
+    geom_line(
+      data = pred %>%
+	rename(bm_f = group, bm_slope = x, linear_slope = predicted),
+      aes(y = linear_slope, x = bm_slope, color = bm_f),
+      inherit.aes = FALSE)
+
+    })
+plot_grid(plotlist = test)
+```
+
+#### Quadratic one
+
+```{r}
+test <- map2(model_bm$data, pred_bm_quad$pred_df, function (.data, pred) {
+
+  .data %>%
+    ggplot(aes(x = bm_slope, y = linear_slope, fill = log(bm)), shape = 23, size = 4) +
+    scale_fill_viridis() +
+    geom_point() +
+    geom_line(
+      data = pred %>%
+	rename(bm_f = group, bm_slope = x, linear_slope = predicted),
+      aes(y = linear_slope, x = bm_slope, color = bm_f),
+      inherit.aes = FALSE)
+
+    })
+plot_grid(plotlist = test, labels = model_bm$variable)
 ```
@@
 
+#### All protocol
+
 ```{r}
-loadd(log_bm_net_group)
-model_log <- compute_my_lm_vs_net_model(
-  log_bm_net_group, var_to_group = c("variable"),
+loadd(model_log_bm, model_log_bm_summary)
+```
+
+```{r}
+filter(model_log_bm_summary, model == "mod_inc_bm")[["resume"]]
+filter(model_log_bm_summary, model == "mod_inc_bm")[["anova"]]
+
+filter(model_log_bm_summary, model == "mod_bm_inc")[["resume"]]
+filter(model_log_bm_summary, model == "mod_bm_inc")[["anova"]]
+
+filter(model_log_bm_summary, model == "mod_bm_quad")[["resume"]]
+filter(model_log_bm_summary, model == "mod_bm_quad")[["resume"]] %>%
+  map(., ~ .x$r.squared)
+filter(model_log_bm_summary, model == "mod_bm_quad")[["anova"]]
+
+filter(model_log_bm_summary, model == "mod_bm_quad2")[["resume"]]
+filter(model_log_bm_summary, model == "mod_bm_quad2")[["resume"]] %>%
+  map_dbl(., ~ .x$r.squared)
+
+filter(model_log_bm_summary, model == "mod_bm_quad2")[["anova"]]
+
+filter(model_log_bm_summary, model == "mod_log_bm_quad2")[["anova"]]
+filter(model_log_bm_summary, model == "mod_log_bm_quad2")[["resume"]] %>%
+  map_dbl(., ~ .x$r.squared)
+```
+
+#### Quadratic two
+
+```{r}
+pred_log_bm_quad2 <- model_log_bm_summary %>%
+  filter(model == "mod_bm_quad2") %>%
+  mutate(
+    pred = map(model_obj, ~ggpredict(.x,
+	terms = c("bm_slope", "bm [quart2]"))),
+    pred_df = map(pred, as_tibble),
+    plot = map(pred, ~plot(.x, add.data = FALSE)),
+    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
+    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
   )
 
-model_var <- tidyselect::vars_select(names(model_by_protocol), starts_with("mod"))
-model_log_vif <- get_vif(model_log, model_cols = model_var)
+pred_log_bm_quad2_plot <- map2(model_log_bm$data, pred_log_bm_quad2$pred_df,
+  plot_pred_data)
+plot_grid(plotlist = pred_log_bm_quad2_plot, labels = model_log_bm$variable)
+```
 
-model_log_vif %>%
+#### Quadratic one
+
+```{r}
+pred_log_bm_quad <- model_log_bm_summary %>%
+  filter(model == "mod_bm_quad") %>%
+  mutate(
+    pred = map(model_obj, ~ggpredict(.x,
+	terms = c("bm_slope", "bm [quart2]"))),
+    pred_df = map(pred, as_tibble),
+    plot = map(pred, ~plot(.x, add.data = FALSE)),
+    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
+    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
+  )
+
+test <- map2(model_log_bm$data, pred_log_bm_quad$pred_df, plot_pred_data,
+  std_error = TRUE)
+plot_grid(plotlist = test, labels = model_log_bm$variable)
+```
+
+```{r}
+loadd(log_bm_net_group, model_log_bm_vif)
+
+model_log_bm_vif %>%
   ggplot(aes(y= vif, x = term)) +
@@
   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  facet_grid(model_type~variable)
+  facet_grid(model_type~variable, scales = "free")
 ```
 
+### By protocol
+
 ```{r}
-model_by_protocol <- compute_my_lm_vs_net_model(
-  filter(log_bm_net_group, !is.na(protocol_type)),
-  var_to_group = c("variable", "protocol_type")
-)
+loadd(model_log_bm_by_protocol_vif)
 
-model_var <- tidyselect::vars_select(names(model_by_protocol), starts_with("mod"))
-model_vif <- get_vif(model_by_protocol,
-  model_cols = model_var)
-
-protocol_vec <- model_vif$protocol_type %>% unique
+protocol_vec <- model_log_bm_by_protocol_vif$protocol_type %>% unique
 p_vif_protocol <- map(protocol_vec, function (x) {
-  model_vif %>%
+  model_log_bm_by_protocol_vif %>%
     filter(protocol_type == x) %>%
@@
 ```{r}
-res_mod <- model_by_protocol %>%
-  filter(protocol_type == "complete") %>%
-  select(-data) %>%
-  pivot_longer(cols = all_of(model_var),
-    names_to = "model", values_to = "model_obj") %>%
-  mutate(
-    resume = map(model_obj, summary),
-    anova = map(model_obj, anova)
-  )
+loadd(model_log_bm_by_protocol, model_log_bm_by_protocol_summary)
 ```
@@
 ```{r}
-filter(res_mod, model == "mod_inc_log_bm")[["resume"]]
-filter(res_mod, model == "mod_inc_log_bm")[["anova"]]
+filter(model_log_bm_by_protocol_summary, model == "mod_inc_log_bm")[["resume"]]
+filter(model_log_bm_by_protocol_summary, model == "mod_inc_log_bm")[["anova"]]
 ```
@@
 ```{r}
-filter(res_mod, model == "mod_log_bm_inc")[["resume"]]
-filter(res_mod, model == "mod_log_bm_inc")[["anova"]]
+filter(model_log_bm_by_protocol_summary, model == "mod_log_bm_inc")[["resume"]]
+filter(model_log_bm_by_protocol_summary, model == "mod_log_bm_inc")[["anova"]]
+
+filter(model_log_bm_by_protocol_summary, model == "mod_bm_quad")[["resume"]]
+filter(model_log_bm_by_protocol_summary, model == "mod_log_bm_inc")[["anova"]]
+```
+
+#### Quadratic two
+
+```{r}
+pred_log_bm_quad2 <- model_log_bm_by_protocol_summary %>%
+  filter(model == "mod_bm_quad2", protocol_type == "complete") %>%
+  mutate(
+    pred = map(model_obj, ~ggpredict(.x,
+	terms = c("bm_slope", "bm [quart2]"))),
+    pred_df = map(pred, as_tibble),
+    plot = map(pred, ~plot(.x, add.data = FALSE)),
+    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
+    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
+  )
+model_log_bm_by_protocol %<>% filter(protocol_type == "complete")
+
+pred_log_bm_quad2_plot <- map2(model_log_bm_by_protocol$data, pred_log_bm_quad2$pred_df,
+  plot_pred_data)
+plot_grid(plotlist = pred_log_bm_quad2_plot, labels = model_log_bm$variable)
+```
+
+#### Quadratic one
+
+```{r}
+pred_log_bm_quad <- model_log_bm_by_protocol_summary %>%
+  filter(model == "mod_bm_quad", protocol_type == "complete") %>%
+  mutate(
+    pred = map(model_obj, ~ggpredict(.x,
+	terms = c("bm_slope", "bm [quart2]"))),
+    pred_df = map(pred, as_tibble),
+    plot = map(pred, ~plot(.x, add.data = FALSE)),
+    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
+    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
+  )
+model_log_bm_by_protocol %<>% filter(protocol_type == "complete")
+
+pred_log_bm_quad_plot <- map2(model_log_bm$data, pred_log_bm_quad$pred_df, plot_pred_data,
+  std_error = TRUE)
+plot_grid(plotlist = pred_log_bm_quad_plot, labels = model_log_bm$variable)
 ```
@@
 ```{r, eval = FALSE}
-pred <- res_mod %>%
-  filter(model == "mod4") %>%
+pred <- model_log_bm_by_protocol_summary %>%
+  filter(model == "mod_log_bm_inc") %>%
   mutate(
     pred = map(model_obj, ~ggpredict(.x,
-	terms = c("bm_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2, 3, 4, 6]", "bm [quart2]"))),
+	terms = c("bm_slope", "log_bm [quart2]", "inc_f"))),
     pred_df = map(pred, as_tibble),
@@
   )
-plot_grid(plotlist = pred$plot)
+plot_grid(plotlist = pred$plot, labels = pred$variable)
+```
+
+```{r}
+pred <- model_log_bm_by_protocol_summary %>%
+  filter(model == "mod_log_bm_inc") %>%
+  mutate(
+    pred = map(model_obj, ~ggpredict(.x,
+	terms = c("bm_slope", "log_bm [quart2]", "inc_f"))),
+    pred_df = map(pred, as_tibble),
+    plot = map(pred, ~plot(.x, add.data = FALSE)),
+    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
+  )
+plot_grid(plotlist = pred$plot, labels = pred$variable)
 ```

### 2020-10-05 R/data_frame_manipulation.R

@@ -64,12 +64,12 @@ get_bm_vs_network_trends <- function (classif = NULL, bm_var = NULL,
   coeff = c("connectance", "w_trph_lvl_avg", "richness", "weighted_connectance")
   ) {
 
-  var_to_keep <- c("station", "linear_slope", "strd_error")
+  var_to_keep <- c("station", "linear_slope", "linear_slope_strd_error")
 
   bm <- classif[classif$variable == bm_var,] %>%
     unnest(classif) %>%
     select(!!!var_to_keep) %>%
-    rename(bm_slope = linear_slope, bm_slope_strd_error = strd_error)
+    rename(bm_slope = linear_slope, bm_slope_strd_error = linear_slope_strd_error)
 
   network <- classif %>%
     filter(!variable %in% get_biomass_var()) %>%
@@ -81,7 +81,8 @@ get_bm_vs_network_trends <- function (classif = NULL, bm_var = NULL,
 
   # Add regression weight
   output %<>%
-    mutate(reg_weight = (abs(bm_slope) / bm_slope_strd_error + abs(linear_slope) / strd_error) / 2)
+    mutate( reg_weight = (1 / bm_slope_strd_error +
+	1 / linear_slope_strd_error) / 2)
 
   return(output)
 }

### 2020-10-05 R/get_model_plot.R

@@ -72,3 +72,34 @@ plot_final_model <- function (ggpred = NULL, rawdata = NULL, facet = FALSE) {
   }
 
 }
+
+plot_pred_data <- function(.data = NULL, pred = NULL, std_error = TRUE) {
+
+  p <- .data %>%
+    ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
+    scale_color_viridis() +
+    geom_point() +
+    geom_line(
+      data = pred %>%
+	rename(bm_f = group, bm_slope = x, linear_slope = predicted),
+      aes(y = linear_slope, x = bm_slope, linetype = bm_f),
+      inherit.aes = FALSE)
+
+    if (std_error) {
+    
+      p <- p +
+	geom_errorbar(data = .data, 
+	  aes(xmin = bm_slope - bm_slope_strd_error,
+	    xmax = bm_slope + bm_slope_strd_error),
+	  alpha = .3
+	  ) +
+	geom_errorbar(data = .data, 
+	  aes(ymin = linear_slope - linear_slope_strd_error,
+	    ymax = linear_slope + linear_slope_strd_error), alpha = .3)
+
+    
+    }
+
+  return(p)
+
+}

### 2020-10-05 R/plan.R

@@ -18,6 +18,16 @@ plan <- drake_plan(
     habitat_press_path = file_in(!!get_mypath("data", "habitat_press.rda"))),
   bm_vs_net_trends = get_bm_vs_network_trends(classif = rigal_classification, bm_var = "bm_std"),
   log_bm_vs_net_trends = get_bm_vs_network_trends(classif = rigal_classification, bm_var = "log_bm_std"),
+
+  bm_std_st_decrease_increase = rigal_classification %>%
+    unnest(classif) %>%
+    filter(variable == "bm_std", shape_class %in% c("increase_constant", "decrease_constant")) %>%
+    select(station, shape_class),
+  log_bm_std_st_decrease_increase = rigal_classification %>%
+    unnest(classif) %>%
+    filter(variable == "log_bm_std", shape_class %in% c("increase_constant", "decrease_constant")) %>%
+    select(station, shape_class),
+
   bm_net_group = 
     add_stream_bm_caract_to_model(bm_vs_network_df = bm_vs_net_trends,
       stream_caract = stream_group, bm_caract = biomass_group,
@@ -28,15 +38,29 @@ plan <- drake_plan(
       stream_caract = stream_group, bm_caract = biomass_group,
       bm_group_var = "bm_std", group_type_caract = "median") %>%
   filter(station %in% log_bm_std_st_decrease_increase$station),
-  , 
-  bm_std_st_decrease_increase = rigal_classification %>%
-    unnest(classif) %>%
-    filter(variable == "bm_std", shape_class %in% c("increase_constant", "decrease_constant")) %>%
-    select(station, shape_class),
-  log_bm_std_st_decrease_increase = rigal_classification %>%
-    unnest(classif) %>%
-    filter(variable == "log_bm_std", shape_class %in% c("increase_constant", "decrease_constant")) %>%
-    select(station, shape_class),
+  
+  model_bm = compute_my_lm_vs_net_model(bm_net_group, var_to_group = c("variable")),
+  model_bm_vif = get_vif(model_bm,
+    model_cols = all_of(tidyselect::vars_select(names(model_bm), starts_with("mod")))),
+  model_bm_summary = model_summary(model_bm),
+  model_bm_by_protocol = compute_my_lm_vs_net_model(
+    filter(bm_net_group, !is.na(protocol_type)),
+    var_to_group = c("variable", "protocol_type")),
[…]

### 2020-10-05 make.R

@@ -9,7 +9,8 @@ source_dir("R") # Define your custom code as a bunch of functions.
 source("R/plan.R")      # Create your drake plan.
 # Call make() to run your work.
 # Your targets will be stored in a hidden .drake/ cache,
-make(plan)
+drake::r_make(plan)
+drake::make(plan)
 vis_drake_graph(plan)
 
 # If you do not change any code or data,

### 2020-10-06 report.Rmd
Add nbnode + standardized richness

@@
 
-```{r p-bivar, cache = TRUE, fig.cap = bivar_cap, fig.height = 10}
-cowplot::plot_grid(
-  cowplot::plot_grid(plotlist = net_dyn_lm_plot$plot[1:4], ncol = 2),
-  cowplot::plot_grid(plotlist = filter(net_dyn_lm_plot, group == "big")$plot[1:4], ncol = 2),
-  ncol = 1, 
-  axis = "rlbt",
-  align = "hv",
-  label_y = 1.01,
-  label_x = .40,
-  labels = c("Little community", "Big community")
-)
-
-cowplot::plot_grid(
-  cowplot::plot_grid(plotlist = net_dyn_lm_plot$plot[5:8], ncol = 2),
-  cowplot::plot_grid(plotlist = filter(net_dyn_lm_plot, group == "big")$plot[5:8], ncol = 2),
-  ncol = 1, 
-  axis = "rlbt",
-  align = "hv",
-  label_y = 1.01,
-  label_x = .40,
-  labels = c("Little community", "Big community")
-)
-```
-
-- Intercept close to 0 for all but richness in big communities 
-- Same slope between big and little communities except for connectance
-
 ```{r}
@@
 
-##
-
-```{r, eval = FALSE}
-slope_com_net <- temporal_dynamics_coef %>%
-  filter(!coeff %in% get_biomass_var(), term == "slope") %>%
-  select(station, coeff, estimate) %>%
-  pivot_wider(names_from = "coeff", values_from = estimate)
-
-absolute_slope_biomass <- temporal_dynamics_coef %>%
-  filter(coeff %in% get_biomass_var(), term == "slope") %>%
-  select(station, coeff, estimate) %>%
-  mutate(
-    absolute_slope =  abs(estimate),
-    trend_sign = if_else(estimate > 0, "positive", "negative")
-  ) %>%
-  left_join(slope_com_net, by = "station")
-
-metrics <- unique(temporal_dynamics_coef$coeff)[!unique(temporal_dynamics_coef$coeff) %in% get_biomass_var()]
-
-p <- vector("list", length = length(metrics))
-for (i in seq_along(metrics)) {
-  p[[i]] <- 
-    absolute_slope_biomass %>%
-    ggplot(aes_string(x = "absolute_slope", y = metrics[i])) +
-    geom_point(aes(color = trend_sign)) +
-    facet_wrap(facets = ~ coeff, scales = "free") +
-    labs(title = metrics[i])
+# Statistical models
+
+## Raw bm
+
+```{r, eval = TRUE}
+loadd(model_bm, model_bm_vif)
+
+model_bm_vif %>%
+  ggplot(aes(y = vif, x = term)) +
+  geom_hline(yintercept = 10) +
+  geom_bar(stat = "identity") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  facet_grid(model_type~variable, scales = "free")
+```
+
+```{r, eval = FALSE}
+library(yhat)
+test <- model_int$mod3[[1]]
+CCData <- commonalityCoefficients(model_int$data[[1]],
+  "linear_slope",
+  list("bm_slope", "inc_f", "bm"), "F")
+CCData
+
+test_data <- model_int$data[[1]]
+lm_test <- lm(
+  formula = linear_slope ~ bm_slope*inc_f*bm,
+  weights = reg_weight
+)
+test <- regr(lm_test)
+```
+
+### Effect of protocol type on the model validity
+
+```{r}
+loadd(model_bm_by_protocol, model_bm_by_protocol_vif)
+
+protocol_vec <- model_bm_by_protocol_vif$protocol_type %>% unique
+p_vif_protocol <- map(protocol_vec, function (x) {
+  model_bm_by_protocol_vif %>%
+    filter(protocol_type == x) %>%
+    ggplot(aes(y= vif, x = term)) +
+    geom_hline(yintercept = 10) +
+    geom_bar(stat = "identity") +
+    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+    labs(title = paste0("Protocol type: ", x)) +
+    facet_grid(model_type~variable, scales = "free_y")
+  })
+p_vif_protocol[[1]]
+p_vif_protocol[[2]]
+```
+
+```{r, eval = FALSE}
+filter(model_bm_by_protocol_vif, model_type == "mod_bm_quad")
+```
+
+```{r}
+loadd(bm_net_group)
+bm_net_group %>%
+  filter(variable == "connectance") %>%
+  ggplot(aes(x = bm_slope, y = bm)) +
+  geom_point()
+```
+
+### Current best model
+
+$$
+Y = \alpha + \beta_1D_b + \beta_2D_bI_b + \beta_3D_bI_bB
+$$
+
+```{r, eval = TRUE}
+loadd(model_bm_by_protocol_summary)
+model_bm_by_protocol_summary %<>%
+  filter(protocol_type == "complete")
+```
+
+```{r, eval = FALSE}
+filter(model_bm_by_protocol_summary, model == "mod_inc_bm")[["resume"]]
+filter(model_bm_by_protocol_summary, model == "mod_inc_bm")[["anova"]]
+
+filter(model_bm_by_protocol_summary, model == "mod_bm_inc")[["resume"]]
+filter(model_bm_by_protocol_summary, model == "mod_bm_inc")[["anova"]]
+
+filter(model_bm_by_protocol_summary, model == "mod_bm_quad")[["resume"]]
+filter(model_bm_by_protocol_summary, model == "mod_bm_quad")[["anova"]]
+
+filter(model_bm_by_protocol_summary, model == "mod_bm_quad2")[["resume"]]
+filter(model_bm_by_protocol_summary, model == "mod_bm_quad2")[["anova"]]
+```
+
+```{r, eval = TRUE}
+pred <- model_bm_by_protocol_summary %>%
+  filter(model == "mod_bm_inc") %>%
+  mutate(
+    pred = map(model_obj, ~ggpredict(.x,
+	terms = c("bm_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2, 3, 4, 6]", "bm [quart2]", "inc_f"))),
+    pred_df = map(pred, as_tibble),
+    plot = map(pred, ~plot(.x, add.data = FALSE)),
+    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
+    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
+  )
+plot_grid(plotlist = pred$plot, labels = pred$variable)
+```
+
+```{r}
+pred <- model_bm_by_protocol_summary %>%
+  filter(model == "mod_bm_quad2") %>%
+  mutate(
+    pred = map(model_obj, ~ggpredict(.x,
+	terms = c("bm_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2, 3, 4, 6]", "bm [quart2]"))),
+    pred_df = map(pred, as_tibble),
+    plot = map(pred, ~plot(.x, add.data = FALSE)),
+    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
+    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
+  )
+plot_grid(plotlist = pred$plot_data, labels = pred$variable)
+```
+
+#### All protocol
+
+```{r}
+loadd(model_bm_summary)
+```
+
+```{r, eval = FALSE}
+filter(model_bm_summary, model == "mod_inc_bm")[["resume"]]
+filter(model_bm_summary, model == "mod_inc_bm")[["anova"]]
+
+filter(model_bm_summary, model == "mod_bm_inc")[["resume"]]
+filter(model_bm_summary, model == "mod_bm_inc")[["anova"]]
+
+filter(model_bm_summary, model == "mod_bm_quad")[["resume"]]
+filter(model_bm_summary, model == "mod_bm_quad")[["anova"]]
+
+filter(model_bm_summary, model == "mod_bm_quad2")[["resume"]]
+filter(model_bm_summary, model == "mod_bm_quad2")[["anova"]]
+```
+
+```{r}
+pred_bm_quad2 <- model_bm_summary %>%
+  filter(model == "mod_bm_quad2") %>%
+  mutate(
+    pred = map(model_obj, ~ggpredict(.x,
+	terms = c("bm_slope", "bm [quart2]"))),
+    pred_df = map(pred, as_tibble),
+    plot = map(pred, ~plot(.x, add.data = FALSE)),
+    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
+    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
+  )
+plot_grid(plotlist = pred_bm_quad2$plot, labels = pred_bm_quad2$variable)
+pred_bm_quad2_plot <- map2(model_bm$data, pred_bm_quad2$pred_df, plot_pred_data)
+
+plot_grid(plotlist = pred_bm_quad2_plot, labels = pred_bm_quad2$variable)
+
+pred_bm_quad <- model_bm_summary %>%
+  filter(model == "mod_bm_quad") %>%
+  mutate(
+    pred = map(model_obj, ~ggpredict(.x,
+	terms = c("bm_slope", "bm [quart2]"))),
+    pred_df = map(pred, as_tibble),
+    plot = map(pred, ~plot(.x, add.data = FALSE)),
+    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
+    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
+  )
+
+pred_bm_quad_plot <- map2(model_bm$data, pred_bm_quad$pred_df, plot_pred_data)
+plot_grid(plotlist = pred_bm_quad_plot, labels = pred_bm_quad2$variable)
+```
+
+#### Quadratic two
+
+```{r}
+#model_bm$data[[1]] %>%
+  #ggplot(aes(x = bm_slope, y = linear_slope, fill = log(bm)), shape = 23, size = 4) +
+  #scale_fill_viridis() +
+  #geom_point() +
+  #geom_line(
+    #data = pred_bm_quad2$pred_df[[1]] %>%
+      #rename(bm_f = group, bm_slope = x, linear_slope = predicted),
+    #aes(y = linear_slope, x = bm_slope, color = bm_f),
+    #inherit.aes = FALSE)
+
+test <- map2(model_bm$data, pred_bm_quad2$pred_df, function (.data, pred) {
+
+  .data %>%
+    ggplot(aes(x = bm_slope, y = linear_slope, fill = log(bm)), shape = 23, size = 4) +
+    scale_fill_viridis() +
+    geom_point() +
+    geom_line(
+      data = pred %>%
+	rename(bm_f = group, bm_slope = x, linear_slope = predicted),
+      aes(y = linear_slope, x = bm_slope, color = bm_f),
+      inherit.aes = FALSE)
+
+    })
+plot_grid(plotlist = test)
+```
+
+#### Quadratic one
+
+```{r}
+test <- map2(model_bm$data, pred_bm_quad$pred_df, function (.data, pred) {
+
+  .data %>%
+    ggplot(aes(x = bm_slope, y = linear_slope, fill = log(bm)), shape = 23, size = 4) +
+    scale_fill_viridis() +
+    geom_point() +
+    geom_line(
+      data = pred %>%
+	rename(bm_f = group, bm_slope = x, linear_slope = predicted),
+      aes(y = linear_slope, x = bm_slope, color = bm_f),
+      inherit.aes = FALSE)
+
+    })
+plot_grid(plotlist = test, labels = model_bm$variable)
+```
+
+### Is the model valid with log_bm ?
+
+```{r}
+loadd(log_bm_net_group)
+```
+
+```{r}
+log_bm_net_group %>%
+  filter(!is.na(protocol_type)) %>%
+  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm), size = reg_weight, weight = reg_weight)) +
+  geom_point() +
+  scale_color_viridis() +
+  #geom_smooth(method = "lm") +
+  facet_grid(variable~protocol_type, scales = "free") +
+  labs(title = "Log biomass")
+
+log_bm_net_group %>%
+  filter(variable == "connectance") %>%
+  ggplot(aes(x = bm_slope, y = bm)) +
+  geom_point()
+```
+
+#### All protocol
+
+```{r}
+loadd(model_log_bm, model_log_bm_summary)
+```
+
+```{r, eval = FALSE}
+filter(model_log_bm_summary, model == "mod_inc_bm")[["resume"]]
+filter(model_log_bm_summary, model == "mod_inc_bm")[["anova"]]
+
+filter(model_log_bm_summary, model == "mod_bm_inc")[["resume"]]
+filter(model_log_bm_summary, model == "mod_bm_inc")[["anova"]]
+
+filter(model_log_bm_summary, model == "mod_bm_quad")[["resume"]]
+filter(model_log_bm_summary, model == "mod_bm_quad")[["resume"]] %>%
+  map(., ~ .x$r.squared)
+filter(model_log_bm_summary, model == "mod_bm_quad")[["anova"]]
+
+filter(model_log_bm_summary, model == "mod_bm_quad2")[["resume"]]
+filter(model_log_bm_summary, model == "mod_bm_quad2")[["resume"]] %>%
+  map_dbl(., ~ .x$r.squared)
+
+filter(model_log_bm_summary, model == "mod_bm_quad2")[["anova"]]
+filter(model_log_bm_summary, model == "mod_bm_quad2")[["resume"]]
+
+filter(model_log_bm_summary, model == "mod_log_bm_quad2")[["anova"]]
+filter(model_log_bm_summary, model == "mod_log_bm_quad2")[["resume"]] %>%
+  map_dbl(., ~ .x$r.squared)
+```
+
+#### Quadratic two
+
+```{r}
+pred_log_bm_quad2 <- model_log_bm_summary %>%
+  filter(model == "mod_bm_quad2") %>%
+  mutate(
+    pred = map(model_obj, ~ggpredict(.x,
+	terms = c("bm_slope", "bm [quart2]"))),
+    pred_df = map(pred, as_tibble),
+    plot = map(pred, ~plot(.x, add.data = FALSE)),
+    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
+    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
+  )
+
+pred_log_bm_quad2_plot <- map2(model_log_bm$data, pred_log_bm_quad2$pred_df,
+  plot_pred_data)
+plot_grid(plotlist = pred_log_bm_quad2_plot, labels = model_log_bm$variable)
+```
+
+#### Quadratic one
+
+```{r}
+pred_log_bm_quad <- model_log_bm_summary %>%
+  filter(model == "mod_bm_quad") %>%
+  mutate(
+    pred = map(model_obj, ~ggpredict(.x,
+	terms = c("bm_slope", "bm [quart2]"))),
+    pred_df = map(pred, as_tibble),
+    plot = map(pred, ~plot(.x, add.data = FALSE)),
+    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
+    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
+  )
+
+test <- map2(model_log_bm$data, pred_log_bm_quad$pred_df, plot_pred_data,
+  std_error = TRUE)
+plot_grid(plotlist = test, labels = model_log_bm$variable)
+```
+
+```{r}
+loadd(log_bm_net_group, model_log_bm_vif)
+
+model_log_bm_vif %>%
+  ggplot(aes(y= vif, x = term)) +
+  geom_hline(yintercept = 10) +
+  geom_bar(stat = "identity") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  facet_grid(model_type~variable, scales = "free")
+```
+
+### By protocol
+
+```{r}
+loadd(model_log_bm_by_protocol_vif)
+
+protocol_vec <- model_log_bm_by_protocol_vif$protocol_type %>% unique
+p_vif_protocol <- map(protocol_vec, function (x) {
+  model_log_bm_by_protocol_vif %>%
+    filter(protocol_type == x) %>%
+    ggplot(aes(y= vif, x = term)) +
+    geom_hline(yintercept = 10) +
+    geom_bar(stat = "identity") +
+    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+    labs(title = paste0("Protocol type: ", x)) +
+    facet_grid(model_type~variable, scales = "free_y")
+  })
+p_vif_protocol[[1]]
+p_vif_protocol[[2]]
+```
+
+```{r}
+loadd(model_log_bm_by_protocol, model_log_bm_by_protocol_summary)
+```
+
+```{r, eval = FALSE}
+filter(model_log_bm_by_protocol_summary, model == "mod_inc_log_bm")[["resume"]]
+filter(model_log_bm_by_protocol_summary, model == "mod_inc_log_bm")[["anova"]]
+```
+
+```{r, eval = FALSE}
+filter(model_log_bm_by_protocol_summary, model == "mod_log_bm_inc")[["resume"]]
+filter(model_log_bm_by_protocol_summary, model == "mod_log_bm_inc")[["anova"]]
+
+filter(model_log_bm_by_protocol_summary, model == "mod_bm_quad")[["resume"]]
+filter(model_log_bm_by_protocol_summary, model == "mod_log_bm_inc")[["anova"]]
+```
+
+#### Quadratic two
+
+```{r}
+pred_log_bm_quad2 <- model_log_bm_by_protocol_summary %>%
+  filter(model == "mod_bm_quad2", protocol_type == "complete") %>%
+  mutate(
+    pred = map(model_obj, ~ggpredict(.x,
+	terms = c("bm_slope", "bm [quart2]"))),
+    pred_df = map(pred, as_tibble),
+    plot = map(pred, ~plot(.x, add.data = FALSE)),
+    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
+    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
+  )
+model_log_bm_by_protocol %<>% filter(protocol_type == "complete")
+
+pred_log_bm_quad2_plot <- map2(model_log_bm_by_protocol$data, pred_log_bm_quad2$pred_df,
+  plot_pred_data)
+plot_grid(plotlist = pred_log_bm_quad2_plot, labels = model_log_bm$variable)
+```
+
+#### Quadratic one
+
+```{r}
+pred_log_bm_quad <- model_log_bm_by_protocol_summary %>%
+  filter(model == "mod_bm_quad", protocol_type == "complete") %>%
+  mutate(
+    pred = map(model_obj, ~ggpredict(.x,
+	terms = c("bm_slope", "bm [quart2]"))),
+    pred_df = map(pred, as_tibble),
+    plot = map(pred, ~plot(.x, add.data = FALSE)),
+    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
+    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
+  )
+model_log_bm_by_protocol %<>% filter(protocol_type == "complete")
+
+pred_log_bm_quad_plot <- map2(model_log_bm$data, pred_log_bm_quad$pred_df, plot_pred_data,
+  std_error = TRUE)
+plot_grid(plotlist = pred_log_bm_quad_plot, labels = model_log_bm$variable)
+```
+
+```{r, eval = FALSE}
+pred <- model_log_bm_by_protocol_summary %>%
+  filter(model == "mod_log_bm_inc") %>%
+  mutate(
+    pred = map(model_obj, ~ggpredict(.x,
+	terms = c("bm_slope", "log_bm [quart2]", "inc_f"))),
+    pred_df = map(pred, as_tibble),
+    plot = map(pred, ~plot(.x, add.data = FALSE)),
+    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
+  )
+plot_grid(plotlist = pred$plot, labels = pred$variable)
+```
+
+```{r}
+pred <- model_log_bm_by_protocol_summary %>%
+  filter(model == "mod_log_bm_inc") %>%
+  mutate(
+    pred = map(model_obj, ~ggpredict(.x,
+	terms = c("bm_slope", "log_bm [quart2]", "inc_f"))),
+    pred_df = map(pred, as_tibble),
+    plot = map(pred, ~plot(.x, add.data = FALSE)),
+    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
+  )
+plot_grid(plotlist = pred$plot, labels = pred$variable)
+```
+
+### Can we predict the model without all simple effects?
+
+```{r, eval = FALSE}
+# Perform a valid model 
+pred <- model_int %>%
+  select(-data, -mod4) %>%
+  pivot_longer(cols = c(mod1:mod5), names_to = "model_type", values_to =
+    "mod_obj") %>%
+  mutate(
+    pred_ref = map2(mod_obj, model_type, function (x, y) {
+       if (y %in% c("mod3", "mod5"))
+	 terms_spec <- c("bm_slope", "inc_f", "bm")
+       else
+	 terms_spec <- c("bm_slope", "inc_f", "bm_group") 
+      ggpredict(x, terms = terms_spec)
       }
-p
+    ),
+    pred_cte = map2(mod_obj, model_type, function (x, y) {
+       if (y %in% c("mod3", "mod5"))
+	 terms_spec <- c("linear_slope", "inc_f", "bm")
+       else
+	 terms_spec <- c("linear_slope", "inc_f", "bm_group") 
+      ggeffect(x, terms = terms_spec)
+      }
+    )
+  )
+
+pred %<>%
+  mutate(
+  plot_pred_ref = map(pred_ref, plot, add.data = TRUE),
+  plot_pred_cte = map(pred_cte, plot, add.data = TRUE)
+  )
+pred_richness <- pred %>%
+  filter(variable == "richness", model_type == "mod3")
+
+pred$plot_pred_ref[[1]]
+pred$plot_pred_cte[[1]]
+pred$plot_pred[[2]]
+pred$plot_pred[[3]]
+pred$plot_pred_ref[[4]]
+```
+
+```{r, eval = FALSE}
+library(ggeffects)
+mydf <- ggpredict(model_int$mod3[[1]], terms = c("linear_slope", "inc_f",
+    "bm"))
+plot(mydf, add.data = TRUE)
+
+```
+
+```{r, eval = FALSE}
+model_log %<>%
+  mutate(
+    pred5 = map(mod3, ~ggpredict(.x,
+	terms = c("linear_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2, 3, 4, 6]", "inc_f", "bm"))),
+    pred5_df = map(pred5, as_tibble),
+    plot = map(pred5, ~plot(.x, add.data = TRUE)),
+    myplot = map2(pred5, data, ~plot_final_model(ggpred = .x, rawdata = .y))
+  )
+
+#plot_final_model(model_int$pred5[[1]], model_int$data[[1]])
+plot_grid(plotlist = model_int$plot, labels = model_int$variable)
+model_int$plot[[1]]
+summary(model_int$mod3[[1]])
+test <- model_int$data[[1]]
+model_int$pred5_df[[1]]
+test %>%
+  ggplot(aes(x = bm_slope, y = linear_slope, weight = reg_weight, size = reg_weight)) +
+  geom_smooth(method = "lm") +
+  geom_point()
+
+pred_test <-
+  model_int$pred5_df[[1]] %>%
+  as_tibble %>%
+  rename(increasing = group, group = facet) %>%
+  filter(increasing == FALSE & x < 0 | increasing == TRUE & x > 0)
+
+p <- ggplot(pred_test, aes(x = x , y = predicted, color = group)) +
+  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group), alpha =
+    .1) +
+  geom_line() +
+  geom_point(data = rename(test,
+      predicted = linear_slope, x = bm_slope),
+    aes(x = x, y = predicted),
+    inherit.aes = FALSE)
+```
+
+```{r, eval = FALSE}
+model_int$pred5_df[[1]] %>%
+  ggplot()
+
+plot_final_model(model_int$pred5[[1]], rawdata = model_int$data[[1]], facet =
+  TRUE)
 ```
@@
 
-```{r p-tmp-dyn, cache = TRUE}
+```{r p-tmp-dyn, cache = TRUE, eval = FALSE}
 
@@
 
-```{r, fig.height = 45}
+```{r, cache = TRUE, fig.height = 45}
 st_decrease_increase_rigal <- biomass_classif_rigal %>%
@@
 
-```{r, fig.height = 45}
+```{r, cache = TRUE, fig.height = 45}
 st_decrease_increase_rigal_biomass <- rigal_classification %>%
@@
   plot_grid(plotlist = .$plot, ncol = 3, labels = st_decrease_increase_rigal_biomass$station)
+```
+
+### Richness
+
+```{r, cache = TRUE, fig.height = 45}
+var_tmp <- "rich_std"
+st_decrease_increase_rigal <- rigal_classification %>%
+  filter(variable == var_tmp) %>%
+  unnest(classif) %>%
+  filter(shape_class %in% c("increase_constant", "decrease_constant"))
+
+min_max <- map_dbl(
+  c(min, max),
+  ~.x(data_decrease_increase[[var_tmp]], na.rm = TRUE))
+nb_year_min_max <- map_dbl(
+  c(min, max),
+  ~.x(data_decrease_increase$nb_year, na.rm = TRUE))
+temporal_dynamics_plot[temporal_dynamics_plot$variable == var_tmp,]$plot %<>%
+  map(., ~ .x + lims(y = min_max, x = nb_year_min_max))
+
+temporal_dynamics_plot %>%
+  filter(variable == var_tmp, station %in% st_decrease_increase_rigal$station) %>%
+  plot_grid(plotlist = .$plot, ncol = 3, labels = st_decrease_increase_rigal$station)
+```
+
+### Number of nodes
+
+```{r, cache = TRUE, fig.height = 45}
+var_tmp <- "nbnode_std"
+st_decrease_increase_rigal <- rigal_classification %>%
+  filter(variable == var_tmp) %>%
+  unnest(classif) %>%
+  filter(shape_class %in% c("increase_constant", "decrease_constant"))
+
+min_max <- map_dbl(
+  c(min, max),
+  ~.x(data_decrease_increase[[var_tmp]], na.rm = TRUE))
+nb_year_min_max <- map_dbl(
+  c(min, max),
+  ~.x(data_decrease_increase$nb_year, na.rm = TRUE))
+temporal_dynamics_plot[temporal_dynamics_plot$variable == var_tmp,]$plot %<>%
+  map(., ~ .x + lims(y = min_max, x = nb_year_min_max))
+
+temporal_dynamics_plot %>%
+  filter(variable == var_tmp, station %in% st_decrease_increase_rigal$station) %>%
+  plot_grid(plotlist = .$plot, ncol = 3, labels = st_decrease_increase_rigal$station)
 ```
@@
 
-# Statistical models
-
-## Raw bm
-
-```{r, eval = TRUE}
-loadd(model_bm, model_bm_vif)
-
-model_bm_vif %>%
-  ggplot(aes(y = vif, x = term)) +
-  geom_hline(yintercept = 10) +
-  geom_bar(stat = "identity") +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  facet_grid(model_type~variable, scales = "free_x")
-```
-
-```{r, eval = FALSE}
-library(yhat)
-test <- model_int$mod3[[1]]
-CCData <- commonalityCoefficients(model_int$data[[1]],
-  "linear_slope",
-  list("bm_slope", "inc_f", "bm"), "F")
-CCData
-
-test_data <- model_int$data[[1]]
-lm_test <- lm(
-  formula = linear_slope ~ bm_slope*inc_f*bm,
-  weights = reg_weight
-)
-test <- regr(lm_test)
-```
-
-### Effect of protocol type on the model validity
-
-```{r}
-loadd(model_bm_by_protocol, model_bm_by_protocol_vif)
-
-protocol_vec <- model_bm_by_protocol_vif$protocol_type %>% unique
-p_vif_protocol <- map(protocol_vec, function (x) {
-  model_bm_by_protocol_vif %>%
-    filter(protocol_type == x) %>%
-    ggplot(aes(y= vif, x = term)) +
-    geom_hline(yintercept = 10) +
-    geom_bar(stat = "identity") +
-    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-    labs(title = paste0("Protocol type: ", x)) +
-    facet_grid(model_type~variable, scales = "free_y")
-  })
-p_vif_protocol[[1]]
-p_vif_protocol[[2]]
-```
-
-```{r, eval = FALSE}
-filter(model_bm_by_protocol_vif, model_type == "mod_bm_quad")
-```
-
-```{r}
-bm_net_group %>%
-  filter(variable == "connectance") %>%
-  ggplot(aes(x = bm_slope, y = bm)) +
-  geom_point()
-```
-
-### Current best model
-
-$$
-Y = \alpha + \beta_1D_b + \beta_2D_bI_b + \beta_3D_bI_bB
-$$
-
-```{r, eval = TRUE}
-loadd(model_bm_by_protocol_summary)
-model_bm_by_protocol_summary %<>%
-  filter(protocol_type == "complete")
-```
-
-```{r, eval = TRUE}
-filter(model_bm_by_protocol_summary, model == "mod_inc_bm")[["resume"]]
-filter(model_bm_by_protocol_summary, model == "mod_inc_bm")[["anova"]]
-
-filter(model_bm_by_protocol_summary, model == "mod_bm_inc")[["resume"]]
-filter(model_bm_by_protocol_summary, model == "mod_bm_inc")[["anova"]]
-
-filter(model_bm_by_protocol_summary, model == "mod_bm_quad")[["resume"]]
-filter(model_bm_by_protocol_summary, model == "mod_bm_quad")[["anova"]]
-
-filter(model_bm_by_protocol_summary, model == "mod_bm_quad2")[["resume"]]
-filter(model_bm_by_protocol_summary, model == "mod_bm_quad2")[["anova"]]
-```
-
-```{r, eval = TRUE}
-pred <- model_bm_by_protocol_summary %>%
-  filter(model == "mod_bm_inc") %>%
-  mutate(
-    pred = map(model_obj, ~ggpredict(.x,
-	terms = c("bm_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2, 3, 4, 6]", "bm [quart2]", "inc_f"))),
-    pred_df = map(pred, as_tibble),
-    plot = map(pred, ~plot(.x, add.data = FALSE)),
-    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
-    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
-  )
-plot_grid(plotlist = pred$plot, labels = pred$variable)
-```
-
-```{r}
-pred <- model_bm_by_protocol_summary %>%
-  filter(model == "mod_bm_quad2") %>%
-  mutate(
-    pred = map(model_obj, ~ggpredict(.x,
-	terms = c("bm_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2, 3, 4, 6]", "bm [quart2]"))),
-    pred_df = map(pred, as_tibble),
-    plot = map(pred, ~plot(.x, add.data = FALSE)),
-    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
-    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
-  )
-plot_grid(plotlist = pred$plot_data, labels = pred$variable)
-```
-
-#### All protocol
-
-```{r}
-loadd(model_bm_summary)
-```
-
-```{r}
-filter(model_bm_summary, model == "mod_inc_bm")[["resume"]]
-filter(model_bm_summary, model == "mod_inc_bm")[["anova"]]
-
-filter(model_bm_summary, model == "mod_bm_inc")[["resume"]]
-filter(model_bm_summary, model == "mod_bm_inc")[["anova"]]
-
-filter(model_bm_summary, model == "mod_bm_quad")[["resume"]]
-filter(model_bm_summary, model == "mod_bm_quad")[["anova"]]
-
-filter(model_bm_summary, model == "mod_bm_quad2")[["resume"]]
-filter(model_bm_summary, model == "mod_bm_quad2")[["anova"]]
-```
-
-```{r}
-pred_bm_quad2 <- model_bm_summary %>%
-  filter(model == "mod_bm_quad2") %>%
-  mutate(
-    pred = map(model_obj, ~ggpredict(.x,
-	terms = c("bm_slope", "bm [quart2]"))),
-    pred_df = map(pred, as_tibble),
-    plot = map(pred, ~plot(.x, add.data = FALSE)),
-    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
-    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
-  )
-plot_grid(plotlist = pred_bm_quad2$plot, labels = pred_bm_quad2$variable)
-pred_bm_quad2_plot <- map2(model_bm$data, pred_bm_quad2$pred_df, plot_pred_data)
-
-plot_grid(plotlist = pred_bm_quad2_plot, labels = pred_bm_quad2$variable)
-
-pred_bm_quad <- model_bm_summary %>%
-  filter(model == "mod_bm_quad") %>%
-  mutate(
-    pred = map(model_obj, ~ggpredict(.x,
-	terms = c("bm_slope", "bm [quart2]"))),
-    pred_df = map(pred, as_tibble),
-    plot = map(pred, ~plot(.x, add.data = FALSE)),
-    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
-    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
-  )
-
-pred_bm_quad_plot <- map2(model_bm$data, pred_bm_quad$pred_df, plot_pred_data)
-plot_grid(plotlist = pred_bm_quad_plot, labels = pred_bm_quad2$variable)
-```
-
-#### Quadratic two
-
-```{r}
-#model_bm$data[[1]] %>%
-  #ggplot(aes(x = bm_slope, y = linear_slope, fill = log(bm)), shape = 23, size = 4) +
-  #scale_fill_viridis() +
-  #geom_point() +
-  #geom_line(
-    #data = pred_bm_quad2$pred_df[[1]] %>%
-      #rename(bm_f = group, bm_slope = x, linear_slope = predicted),
-    #aes(y = linear_slope, x = bm_slope, color = bm_f),
-    #inherit.aes = FALSE)
-
-test <- map2(model_bm$data, pred_bm_quad2$pred_df, function (.data, pred) {
-
-  .data %>%
-    ggplot(aes(x = bm_slope, y = linear_slope, fill = log(bm)), shape = 23, size = 4) +
-    scale_fill_viridis() +
-    geom_point() +
-    geom_line(
-      data = pred %>%
-	rename(bm_f = group, bm_slope = x, linear_slope = predicted),
-      aes(y = linear_slope, x = bm_slope, color = bm_f),
-      inherit.aes = FALSE)
-
-    })
-plot_grid(plotlist = test)
-```
-
-#### Quadratic one
-
-```{r}
-test <- map2(model_bm$data, pred_bm_quad$pred_df, function (.data, pred) {
-
-  .data %>%
-    ggplot(aes(x = bm_slope, y = linear_slope, fill = log(bm)), shape = 23, size = 4) +
-    scale_fill_viridis() +
-    geom_point() +
-    geom_line(
-      data = pred %>%
-	rename(bm_f = group, bm_slope = x, linear_slope = predicted),
-      aes(y = linear_slope, x = bm_slope, color = bm_f),
-      inherit.aes = FALSE)
-
-    })
-plot_grid(plotlist = test, labels = model_bm$variable)
-```
-
-### Is the model valid with log_bm ?
-
-```{r}
-log_bm_net_group %>%
-  filter(!is.na(protocol_type)) %>%
-  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm), size = reg_weight, weight = reg_weight)) +
-  geom_point() +
-  scale_color_viridis() +
-  #geom_smooth(method = "lm") +
-  facet_grid(variable~protocol_type, scales = "free") +
-  labs(title = "Log biomass")
-
-log_bm_net_group %>%
-  filter(variable == "connectance") %>%
-  ggplot(aes(x = bm_slope, y = bm)) +
-  geom_point()
-```
-
-#### All protocol
-
-```{r}
-loadd(model_log_bm, model_log_bm_summary)
-```
-
-```{r}
-filter(model_log_bm_summary, model == "mod_inc_bm")[["resume"]]
-filter(model_log_bm_summary, model == "mod_inc_bm")[["anova"]]
-
-filter(model_log_bm_summary, model == "mod_bm_inc")[["resume"]]
-filter(model_log_bm_summary, model == "mod_bm_inc")[["anova"]]
-
-filter(model_log_bm_summary, model == "mod_bm_quad")[["resume"]]
-filter(model_log_bm_summary, model == "mod_bm_quad")[["resume"]] %>%
-  map(., ~ .x$r.squared)
-filter(model_log_bm_summary, model == "mod_bm_quad")[["anova"]]
-
-filter(model_log_bm_summary, model == "mod_bm_quad2")[["resume"]]
-filter(model_log_bm_summary, model == "mod_bm_quad2")[["resume"]] %>%
-  map_dbl(., ~ .x$r.squared)
-
-filter(model_log_bm_summary, model == "mod_bm_quad2")[["anova"]]
-
-filter(model_log_bm_summary, model == "mod_log_bm_quad2")[["anova"]]
-filter(model_log_bm_summary, model == "mod_log_bm_quad2")[["resume"]] %>%
-  map_dbl(., ~ .x$r.squared)
-```
-
-#### Quadratic two
-
-```{r}
-pred_log_bm_quad2 <- model_log_bm_summary %>%
-  filter(model == "mod_bm_quad2") %>%
-  mutate(
-    pred = map(model_obj, ~ggpredict(.x,
-	terms = c("bm_slope", "bm [quart2]"))),
-    pred_df = map(pred, as_tibble),
-    plot = map(pred, ~plot(.x, add.data = FALSE)),
-    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
-    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
-  )
-
-pred_log_bm_quad2_plot <- map2(model_log_bm$data, pred_log_bm_quad2$pred_df,
-  plot_pred_data)
-plot_grid(plotlist = pred_log_bm_quad2_plot, labels = model_log_bm$variable)
-```
-
-#### Quadratic one
-
-```{r}
-pred_log_bm_quad <- model_log_bm_summary %>%
-  filter(model == "mod_bm_quad") %>%
-  mutate(
-    pred = map(model_obj, ~ggpredict(.x,
-	terms = c("bm_slope", "bm [quart2]"))),
-    pred_df = map(pred, as_tibble),
-    plot = map(pred, ~plot(.x, add.data = FALSE)),
-    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
-    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
-  )
-
-test <- map2(model_log_bm$data, pred_log_bm_quad$pred_df, plot_pred_data,
-  std_error = TRUE)
-plot_grid(plotlist = test, labels = model_log_bm$variable)
-```
-
-```{r}
-loadd(log_bm_net_group, model_log_bm_vif)
-
-model_log_bm_vif %>%
-  ggplot(aes(y= vif, x = term)) +
-  geom_hline(yintercept = 10) +
-  geom_bar(stat = "identity") +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  facet_grid(model_type~variable, scales = "free")
-```
-
-### By protocol
-
-```{r}
-loadd(model_log_bm_by_protocol_vif)
-
-protocol_vec <- model_log_bm_by_protocol_vif$protocol_type %>% unique
-p_vif_protocol <- map(protocol_vec, function (x) {
-  model_log_bm_by_protocol_vif %>%
-    filter(protocol_type == x) %>%
-    ggplot(aes(y= vif, x = term)) +
-    geom_hline(yintercept = 10) +
-    geom_bar(stat = "identity") +
-    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-    labs(title = paste0("Protocol type: ", x)) +
-    facet_grid(model_type~variable, scales = "free_y")
-  })
-p_vif_protocol[[1]]
-p_vif_protocol[[2]]
-```
-
-```{r}
-loadd(model_log_bm_by_protocol, model_log_bm_by_protocol_summary)
-```
-
-```{r}
-filter(model_log_bm_by_protocol_summary, model == "mod_inc_log_bm")[["resume"]]
-filter(model_log_bm_by_protocol_summary, model == "mod_inc_log_bm")[["anova"]]
-```
-
-```{r}
-filter(model_log_bm_by_protocol_summary, model == "mod_log_bm_inc")[["resume"]]
-filter(model_log_bm_by_protocol_summary, model == "mod_log_bm_inc")[["anova"]]
-
-filter(model_log_bm_by_protocol_summary, model == "mod_bm_quad")[["resume"]]
-filter(model_log_bm_by_protocol_summary, model == "mod_log_bm_inc")[["anova"]]
-```
-
-#### Quadratic two
-
-```{r}
-pred_log_bm_quad2 <- model_log_bm_by_protocol_summary %>%
-  filter(model == "mod_bm_quad2", protocol_type == "complete") %>%
-  mutate(
-    pred = map(model_obj, ~ggpredict(.x,
-	terms = c("bm_slope", "bm [quart2]"))),
-    pred_df = map(pred, as_tibble),
-    plot = map(pred, ~plot(.x, add.data = FALSE)),
-    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
-    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
-  )
-model_log_bm_by_protocol %<>% filter(protocol_type == "complete")
-
-pred_log_bm_quad2_plot <- map2(model_log_bm_by_protocol$data, pred_log_bm_quad2$pred_df,
-  plot_pred_data)
-plot_grid(plotlist = pred_log_bm_quad2_plot, labels = model_log_bm$variable)
-```
-
-#### Quadratic one
-
-```{r}
-pred_log_bm_quad <- model_log_bm_by_protocol_summary %>%
-  filter(model == "mod_bm_quad", protocol_type == "complete") %>%
-  mutate(
-    pred = map(model_obj, ~ggpredict(.x,
-	terms = c("bm_slope", "bm [quart2]"))),
-    pred_df = map(pred, as_tibble),
-    plot = map(pred, ~plot(.x, add.data = FALSE)),
-    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
-    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
-  )
-model_log_bm_by_protocol %<>% filter(protocol_type == "complete")
-
-pred_log_bm_quad_plot <- map2(model_log_bm$data, pred_log_bm_quad$pred_df, plot_pred_data,
-  std_error = TRUE)
-plot_grid(plotlist = pred_log_bm_quad_plot, labels = model_log_bm$variable)
-```
-
-```{r, eval = FALSE}
-pred <- model_log_bm_by_protocol_summary %>%
-  filter(model == "mod_log_bm_inc") %>%
-  mutate(
-    pred = map(model_obj, ~ggpredict(.x,
-	terms = c("bm_slope", "log_bm [quart2]", "inc_f"))),
-    pred_df = map(pred, as_tibble),
-    plot = map(pred, ~plot(.x, add.data = FALSE)),
-    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
-  )
-plot_grid(plotlist = pred$plot, labels = pred$variable)
-```
-
-```{r}
-pred <- model_log_bm_by_protocol_summary %>%
-  filter(model == "mod_log_bm_inc") %>%
-  mutate(
-    pred = map(model_obj, ~ggpredict(.x,
-	terms = c("bm_slope", "log_bm [quart2]", "inc_f"))),
-    pred_df = map(pred, as_tibble),
-    plot = map(pred, ~plot(.x, add.data = FALSE)),
-    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
-  )
-plot_grid(plotlist = pred$plot, labels = pred$variable)
-```
-
-### Can we predict the model without all simple effects?
-
-```{r, eval = FALSE}
-# Perform a valid model 
-pred <- model_int %>%
-  select(-data, -mod4) %>%
-  pivot_longer(cols = c(mod1:mod5), names_to = "model_type", values_to =
-    "mod_obj") %>%
-  mutate(
-    pred_ref = map2(mod_obj, model_type, function (x, y) {
-       if (y %in% c("mod3", "mod5"))
-	 terms_spec <- c("bm_slope", "inc_f", "bm")
-       else
-	 terms_spec <- c("bm_slope", "inc_f", "bm_group") 
-      ggpredict(x, terms = terms_spec)
-      }
-    ),
-    pred_cte = map2(mod_obj, model_type, function (x, y) {
-       if (y %in% c("mod3", "mod5"))
-	 terms_spec <- c("linear_slope", "inc_f", "bm")
-       else
-	 terms_spec <- c("linear_slope", "inc_f", "bm_group") 
-      ggeffect(x, terms = terms_spec)
-      }
-    )
-  )
-
-pred %<>%
-  mutate(
-  plot_pred_ref = map(pred_ref, plot, add.data = TRUE),
-  plot_pred_cte = map(pred_cte, plot, add.data = TRUE)
-  )
-pred_richness <- pred %>%
-  filter(variable == "richness", model_type == "mod3")
-
-pred$plot_pred_ref[[1]]
-pred$plot_pred_cte[[1]]
-pred$plot_pred[[2]]
-pred$plot_pred[[3]]
-pred$plot_pred_ref[[4]]
-```
-
-```{r, eval = FALSE}
-library(ggeffects)
-mydf <- ggpredict(model_int$mod3[[1]], terms = c("linear_slope", "inc_f",
-    "bm"))
-plot(mydf, add.data = TRUE)
-
-```
-
-```{r, eval = FALSE}
-model_log %<>%
-  mutate(
-    pred5 = map(mod3, ~ggpredict(.x,
-	terms = c("linear_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2, 3, 4, 6]", "inc_f", "bm"))),
-    pred5_df = map(pred5, as_tibble),
-    plot = map(pred5, ~plot(.x, add.data = TRUE)),
-    myplot = map2(pred5, data, ~plot_final_model(ggpred = .x, rawdata = .y))
-  )
-
-#plot_final_model(model_int$pred5[[1]], model_int$data[[1]])
-plot_grid(plotlist = model_int$plot, labels = model_int$variable)
-model_int$plot[[1]]
-summary(model_int$mod3[[1]])
-test <- model_int$data[[1]]
-model_int$pred5_df[[1]]
-test %>%
-  ggplot(aes(x = bm_slope, y = linear_slope, weight = reg_weight, size = reg_weight)) +
-  geom_smooth(method = "lm") +
-  geom_point()
-
-pred_test <-
-  model_int$pred5_df[[1]] %>%
-  as_tibble %>%
-  rename(increasing = group, group = facet) %>%
-  filter(increasing == FALSE & x < 0 | increasing == TRUE & x > 0)
-
-p <- ggplot(pred_test, aes(x = x , y = predicted, color = group)) +
-  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group), alpha =
-    .1) +
-  geom_line() +
-  geom_point(data = rename(test,
-      predicted = linear_slope, x = bm_slope),
-    aes(x = x, y = predicted),
-    inherit.aes = FALSE)
-```
-
-```{r, eval = FALSE}
-model_int$pred5_df[[1]] %>%
-  ggplot()
-
-plot_final_model(model_int$pred5[[1]], rawdata = model_int$data[[1]], facet =
-  TRUE)
-```
-
-```{r, eval = FALSE}
-library(segmented)
-
-mod_tlvl <- lm(estimate ~ linear_slope, model_int$data[[2]])
-mod_tlvl <- lm(
-  estimate ~ linear_slope*decreasing*group,#(linear_slope < 0)*linear_slope + (linear_slope >= 0)*linear_slope,
-  mutate(model_int$data[[2]], decreasing = linear_slope < 0)
-)
-seg_tlvl <- segmented(mod_tlvl, seg.Z=~linear_slope)
-plot(seg_tlvl)
-
-mod_richness <- lm(estimate ~ linear_slope, model_int$data[[2]])
-test <- segmented(mod_richness, seg.Z=~linear_slope)
-plot(test)
-
-car::vif(test)
-```
-
 ## Richness
@@
 
-```{r}
-
-```
-
 ## SAX
@@
   facet_wrap(facets = ~variable)
-
-```
+```

### 2020-10-06 R/statistical_model.R

@@ -133,7 +133,7 @@ compute_my_lm_vs_net_model <- function (
   group_by_at(vars(all_of(var_to_group))) %>%
   nest() %>%
     mutate(
-      mod_all_group = map(data, ~lm(linear_slope ~ bm_slope*inc_f*bm_group, .x, weights = reg_weight)),
+      #mod_all_group = map(data, ~lm(linear_slope ~ bm_slope*inc_f*bm_group, .x, weights = reg_weight)),
       #mod_medium_group = map(data, ~lm(
 	   #linear_slope~ bm_slope + bm_slope:inc_f + bm_slope:bm_group +
 	    #bm_slope:inc_f:bm_group,
@@ -148,17 +148,17 @@ compute_my_lm_vs_net_model <- function (
 	  #.x, weights = reg_weight)),
       mod_all_bm = map(data, ~lm(linear_slope ~ bm_slope*inc_f*bm, .x, weights = reg_weight)),
       mod_all_log_bm = map(data, ~lm(linear_slope ~ bm_slope*inc_f*log_bm, .x, weights = reg_weight)),
-      mod_bm = map(data, ~lm(linear_slope ~ bm_slope*bm, .x, weights = reg_weight)),
+      #mod_bm = map(data, ~lm(linear_slope ~ bm_slope*bm, .x, weights = reg_weight)),
       mod_bm_quad = map(data, ~lm(linear_slope ~ bm_slope*bm + I(bm_slope^2), .x, weights = reg_weight)),
       mod_bm_quad2 = map(data, ~lm(linear_slope ~ bm_slope*bm + I(bm_slope^2)*bm, .x, weights = reg_weight)),
       mod_log_bm_quad = map(data, ~lm(linear_slope ~ bm_slope*log_bm + I(bm_slope^2), .x, weights = reg_weight)),
       mod_log_bm_quad2 = map(data, ~lm(linear_slope ~ bm_slope*log_bm + I(bm_slope^2)*log_bm, .x, weights = reg_weight)),
-      mod_bm_inc = map(data, ~lm(linear_slope ~ bm_slope*bm + inc_f, .x, weights = reg_weight)),
-      mod_log_bm = map(data, ~lm(linear_slope ~ bm_slope*log_bm, .x, weights = reg_weight)),
-      mod_log_bm_inc = map(data, ~lm(linear_slope ~ bm_slope*log_bm + inc_f, .x, weights = reg_weight)),
[…]

### 2020-10-12 report.Rmd
Add piscivory statistics

@@
 date: "`r Sys.Date()`"
+tables: yes
 output:
@@
 library(viridis)
+library(kableExtra)
 source("R/misc.R") # Define your custom code as a bunch of functions.
@@
 
-# Statistical models
+# Results
 
-## Raw bm
-
-```{r, eval = TRUE}
-loadd(model_bm, model_bm_vif)
-
-model_bm_vif %>%
-  ggplot(aes(y = vif, x = term)) +
-  geom_hline(yintercept = 10) +
-  geom_bar(stat = "identity") +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  facet_grid(model_type~variable, scales = "free")
-```
-
-```{r, eval = FALSE}
-library(yhat)
-test <- model_int$mod3[[1]]
-CCData <- commonalityCoefficients(model_int$data[[1]],
-  "linear_slope",
-  list("bm_slope", "inc_f", "bm"), "F")
-CCData
-
-test_data <- model_int$data[[1]]
-lm_test <- lm(
-  formula = linear_slope ~ bm_slope*inc_f*bm,
-  weights = reg_weight
-)
-test <- regr(lm_test)
-```
-
-### Effect of protocol type on the model validity
-
-```{r}
-loadd(model_bm_by_protocol, model_bm_by_protocol_vif)
-
-protocol_vec <- model_bm_by_protocol_vif$protocol_type %>% unique
-p_vif_protocol <- map(protocol_vec, function (x) {
-  model_bm_by_protocol_vif %>%
-    filter(protocol_type == x) %>%
-    ggplot(aes(y= vif, x = term)) +
-    geom_hline(yintercept = 10) +
-    geom_bar(stat = "identity") +
-    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-    labs(title = paste0("Protocol type: ", x)) +
-    facet_grid(model_type~variable, scales = "free_y")
-  })
-p_vif_protocol[[1]]
-p_vif_protocol[[2]]
-```
-
-```{r, eval = FALSE}
-filter(model_bm_by_protocol_vif, model_type == "mod_bm_quad")
-```
-
-```{r}
-loadd(bm_net_group)
-bm_net_group %>%
-  filter(variable == "connectance") %>%
-  ggplot(aes(x = bm_slope, y = bm)) +
-  geom_point()
-```
-
-### Current best model
-
-$$
-Y = \alpha + \beta_1D_b + \beta_2D_bI_b + \beta_3D_bI_bB
-$$
-
-```{r, eval = TRUE}
-loadd(model_bm_by_protocol_summary)
-model_bm_by_protocol_summary %<>%
-  filter(protocol_type == "complete")
-```
-
-```{r, eval = FALSE}
-filter(model_bm_by_protocol_summary, model == "mod_inc_bm")[["resume"]]
-filter(model_bm_by_protocol_summary, model == "mod_inc_bm")[["anova"]]
-
-filter(model_bm_by_protocol_summary, model == "mod_bm_inc")[["resume"]]
-filter(model_bm_by_protocol_summary, model == "mod_bm_inc")[["anova"]]
-
-filter(model_bm_by_protocol_summary, model == "mod_bm_quad")[["resume"]]
-filter(model_bm_by_protocol_summary, model == "mod_bm_quad")[["anova"]]
-
-filter(model_bm_by_protocol_summary, model == "mod_bm_quad2")[["resume"]]
-filter(model_bm_by_protocol_summary, model == "mod_bm_quad2")[["anova"]]
-```
-
-```{r, eval = TRUE}
-pred <- model_bm_by_protocol_summary %>%
-  filter(model == "mod_bm_inc") %>%
-  mutate(
-    pred = map(model_obj, ~ggpredict(.x,
-	terms = c("bm_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2, 3, 4, 6]", "bm [quart2]", "inc_f"))),
-    pred_df = map(pred, as_tibble),
-    plot = map(pred, ~plot(.x, add.data = FALSE)),
-    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
-    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
-  )
-plot_grid(plotlist = pred$plot, labels = pred$variable)
-```
-
-```{r}
-pred <- model_bm_by_protocol_summary %>%
-  filter(model == "mod_bm_quad2") %>%
-  mutate(
-    pred = map(model_obj, ~ggpredict(.x,
-	terms = c("bm_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2, 3, 4, 6]", "bm [quart2]"))),
-    pred_df = map(pred, as_tibble),
-    plot = map(pred, ~plot(.x, add.data = FALSE)),
-    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
-    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
-  )
-plot_grid(plotlist = pred$plot_data, labels = pred$variable)
-```
-
-#### All protocol
-
-```{r}
-loadd(model_bm_summary)
-```
-
-```{r, eval = FALSE}
-filter(model_bm_summary, model == "mod_inc_bm")[["resume"]]
-filter(model_bm_summary, model == "mod_inc_bm")[["anova"]]
-
-filter(model_bm_summary, model == "mod_bm_inc")[["resume"]]
-filter(model_bm_summary, model == "mod_bm_inc")[["anova"]]
-
-filter(model_bm_summary, model == "mod_bm_quad")[["resume"]]
-filter(model_bm_summary, model == "mod_bm_quad")[["anova"]]
-
-filter(model_bm_summary, model == "mod_bm_quad2")[["resume"]]
-filter(model_bm_summary, model == "mod_bm_quad2")[["anova"]]
-```
-
-```{r}
-pred_bm_quad2 <- model_bm_summary %>%
-  filter(model == "mod_bm_quad2") %>%
-  mutate(
-    pred = map(model_obj, ~ggpredict(.x,
-	terms = c("bm_slope", "bm [quart2]"))),
-    pred_df = map(pred, as_tibble),
-    plot = map(pred, ~plot(.x, add.data = FALSE)),
-    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
-    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
-  )
-plot_grid(plotlist = pred_bm_quad2$plot, labels = pred_bm_quad2$variable)
-pred_bm_quad2_plot <- map2(model_bm$data, pred_bm_quad2$pred_df, plot_pred_data)
-
-plot_grid(plotlist = pred_bm_quad2_plot, labels = pred_bm_quad2$variable)
-
-pred_bm_quad <- model_bm_summary %>%
-  filter(model == "mod_bm_quad") %>%
-  mutate(
-    pred = map(model_obj, ~ggpredict(.x,
-	terms = c("bm_slope", "bm [quart2]"))),
-    pred_df = map(pred, as_tibble),
-    plot = map(pred, ~plot(.x, add.data = FALSE)),
-    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
-    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
-  )
-
-pred_bm_quad_plot <- map2(model_bm$data, pred_bm_quad$pred_df, plot_pred_data)
-plot_grid(plotlist = pred_bm_quad_plot, labels = pred_bm_quad2$variable)
-```
-
-#### Quadratic two
-
-```{r}
-#model_bm$data[[1]] %>%
-  #ggplot(aes(x = bm_slope, y = linear_slope, fill = log(bm)), shape = 23, size = 4) +
-  #scale_fill_viridis() +
-  #geom_point() +
-  #geom_line(
-    #data = pred_bm_quad2$pred_df[[1]] %>%
-      #rename(bm_f = group, bm_slope = x, linear_slope = predicted),
-    #aes(y = linear_slope, x = bm_slope, color = bm_f),
-    #inherit.aes = FALSE)
-
-test <- map2(model_bm$data, pred_bm_quad2$pred_df, function (.data, pred) {
-
-  .data %>%
-    ggplot(aes(x = bm_slope, y = linear_slope, fill = log(bm)), shape = 23, size = 4) +
-    scale_fill_viridis() +
-    geom_point() +
-    geom_line(
-      data = pred %>%
-	rename(bm_f = group, bm_slope = x, linear_slope = predicted),
-      aes(y = linear_slope, x = bm_slope, color = bm_f),
-      inherit.aes = FALSE)
-
-    })
-plot_grid(plotlist = test)
-```
-
-#### Quadratic one
-
-```{r}
-test <- map2(model_bm$data, pred_bm_quad$pred_df, function (.data, pred) {
-
-  .data %>%
-    ggplot(aes(x = bm_slope, y = linear_slope, fill = log(bm)), shape = 23, size = 4) +
-    scale_fill_viridis() +
-    geom_point() +
-    geom_line(
-      data = pred %>%
-	rename(bm_f = group, bm_slope = x, linear_slope = predicted),
-      aes(y = linear_slope, x = bm_slope, color = bm_f),
-      inherit.aes = FALSE)
-
-    })
-plot_grid(plotlist = test, labels = model_bm$variable)
-```
-
-### Is the model valid with log_bm ?
+- Methodological choice:
+  - Dynamics of log of the biomass: put big and little station on the same scale
+    (% of biomass gained or lost per year)
 
@@
 
-```{r}
+```{r, fig.height = 12, fig.width = 12}
+log_bm_net_group %>%
+  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
+  geom_point() +
+  scale_color_viridis() +
+  geom_errorbar(aes(xmin = bm_slope - bm_slope_strd_error,
+      xmax = bm_slope + bm_slope_strd_error), alpha = .3) +
+  geom_errorbar(aes(ymin = linear_slope - linear_slope_strd_error,
+      ymax = linear_slope + linear_slope_strd_error), alpha = .3) +
+  facet_wrap(~variable, scales = "free") +
+  labs_log_bm_net_trends()
+```
+
+```{r, fig.height = 12, fig.width = 12}
 log_bm_net_group %>%
   filter(!is.na(protocol_type)) %>%
-  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm), size = reg_weight, weight = reg_weight)) +
+  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
   geom_point() +
   scale_color_viridis() +
-  #geom_smooth(method = "lm") +
+  geom_errorbar(aes(xmin = bm_slope - bm_slope_strd_error,
+      xmax = bm_slope + bm_slope_strd_error), alpha = .3) +
+  geom_errorbar(aes(ymin = linear_slope - linear_slope_strd_error,
+      ymax = linear_slope + linear_slope_strd_error), alpha = .3) +
   facet_grid(variable~protocol_type, scales = "free") +
-  labs(title = "Log biomass")
+  labs_log_bm_net_trends()
 
@@
   geom_point()
+  labs(x = "Biomass trends (log biomass per year)", y = "Biomass")
 ```
@@
 
-```{r, eval = FALSE}
-filter(model_log_bm_summary, model == "mod_inc_bm")[["resume"]]
-filter(model_log_bm_summary, model == "mod_inc_bm")[["anova"]]
+```{r, eval = TRUE}
+#https://stackoverflow.com/questions/44457243/regression-tables-in-r-markdown-rmarkdown-html-pdf
 
-filter(model_log_bm_summary, model == "mod_bm_inc")[["resume"]]
-filter(model_log_bm_summary, model == "mod_bm_inc")[["anova"]]
+unique(model_log_bm_summary$variable)
+model_log_bm_table <- model_log_bm_summary %>%
+  filter(model == "mod_bm_quad2") %>%
+  filter(!variable %in% c("log_rich_std", "nbnode_std")) %>%
+  mutate(
+    reg_table = map(model_obj, broom::tidy),
+    anova_table = map(anova, broom::tidy)
+  )
 
-filter(model_log_bm_summary, model == "mod_bm_quad")[["resume"]]
-filter(model_log_bm_summary, model == "mod_bm_quad")[["resume"]] %>%
-  map(., ~ .x$r.squared)
-filter(model_log_bm_summary, model == "mod_bm_quad")[["anova"]]
+model_log_bm_table[["reg_table"]] %>% 
+  bind_rows(.) %>%
+  mutate(variable = rep(model_log_bm_table[["variable"]], each = 6)) %>%
+  select(variable, everything()) %>%
+  kable(.,
+    booktabs = TRUE, 
+    caption = 
+      paste0(
+      "Regression table for the model: dN =",
+      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
+    ) 
+  )
+```
 
-filter(model_log_bm_summary, model == "mod_bm_quad2")[["resume"]]
-filter(model_log_bm_summary, model == "mod_bm_quad2")[["resume"]] %>%
-  map_dbl(., ~ .x$r.squared)
+```{r}
+bind_rows(model_log_bm_table[["anova_table"]]) %>% 
+  mutate(variable = rep(model_log_bm_table[["variable"]], each = 6)) %>%
+  select(variable, everything()) %>%
+  kable(., booktabs = TRUE,
+    caption = 
+      paste0(
+      "ANOVA table for the model: dN =",
+      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
+    )
+  )
 
-filter(model_log_bm_summary, model == "mod_bm_quad2")[["anova"]]
-filter(model_log_bm_summary, model == "mod_bm_quad2")[["resume"]]
+```
 
-filter(model_log_bm_summary, model == "mod_log_bm_quad2")[["anova"]]
-filter(model_log_bm_summary, model == "mod_log_bm_quad2")[["resume"]] %>%
-  map_dbl(., ~ .x$r.squared)
+```{r}
+map_dfr(model_log_bm_table[["model_obj"]], broom::glance) %>%
+  mutate(variable = model_log_bm_table[["variable"]]) %>%
+  select(variable, everything()) %>%
+  kable(., booktabs = TRUE,
+    caption = 
+      paste0(
+      "Model summary for the model: dN =",
+      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
+    )
+  )
 ```
@@
 
-```{r}
+```{r, fig.height = 12, fig.width = 12}
 pred_log_bm_quad2 <- model_log_bm_summary %>%
@@
 
-#### Quadratic one
-
-```{r}
-pred_log_bm_quad <- model_log_bm_summary %>%
-  filter(model == "mod_bm_quad") %>%
-  mutate(
-    pred = map(model_obj, ~ggpredict(.x,
-	terms = c("bm_slope", "bm [quart2]"))),
-    pred_df = map(pred, as_tibble),
-    plot = map(pred, ~plot(.x, add.data = FALSE)),
-    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
-    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
-  )
-
-test <- map2(model_log_bm$data, pred_log_bm_quad$pred_df, plot_pred_data,
-  std_error = TRUE)
-plot_grid(plotlist = test, labels = model_log_bm$variable)
-```
-
-```{r}
-loadd(log_bm_net_group, model_log_bm_vif)
-
-model_log_bm_vif %>%
-  ggplot(aes(y= vif, x = term)) +
-  geom_hline(yintercept = 10) +
-  geom_bar(stat = "identity") +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  facet_grid(model_type~variable, scales = "free")
-```
-
-### By protocol
-
-```{r}
-loadd(model_log_bm_by_protocol_vif)
-
-protocol_vec <- model_log_bm_by_protocol_vif$protocol_type %>% unique
-p_vif_protocol <- map(protocol_vec, function (x) {
-  model_log_bm_by_protocol_vif %>%
-    filter(protocol_type == x) %>%
-    ggplot(aes(y= vif, x = term)) +
-    geom_hline(yintercept = 10) +
-    geom_bar(stat = "identity") +
-    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-    labs(title = paste0("Protocol type: ", x)) +
-    facet_grid(model_type~variable, scales = "free_y")
-  })
-p_vif_protocol[[1]]
-p_vif_protocol[[2]]
-```
-
-```{r}
-loadd(model_log_bm_by_protocol, model_log_bm_by_protocol_summary)
-```
-
-```{r, eval = FALSE}
-filter(model_log_bm_by_protocol_summary, model == "mod_inc_log_bm")[["resume"]]
-filter(model_log_bm_by_protocol_summary, model == "mod_inc_log_bm")[["anova"]]
-```
-
-```{r, eval = FALSE}
-filter(model_log_bm_by_protocol_summary, model == "mod_log_bm_inc")[["resume"]]
-filter(model_log_bm_by_protocol_summary, model == "mod_log_bm_inc")[["anova"]]
-
-filter(model_log_bm_by_protocol_summary, model == "mod_bm_quad")[["resume"]]
-filter(model_log_bm_by_protocol_summary, model == "mod_log_bm_inc")[["anova"]]
-```
-
-#### Quadratic two
-
-```{r}
-pred_log_bm_quad2 <- model_log_bm_by_protocol_summary %>%
-  filter(model == "mod_bm_quad2", protocol_type == "complete") %>%
-  mutate(
-    pred = map(model_obj, ~ggpredict(.x,
-	terms = c("bm_slope", "bm [quart2]"))),
-    pred_df = map(pred, as_tibble),
-    plot = map(pred, ~plot(.x, add.data = FALSE)),
-    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
-    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
-  )
-model_log_bm_by_protocol %<>% filter(protocol_type == "complete")
-
-pred_log_bm_quad2_plot <- map2(model_log_bm_by_protocol$data, pred_log_bm_quad2$pred_df,
-  plot_pred_data)
-plot_grid(plotlist = pred_log_bm_quad2_plot, labels = model_log_bm$variable)
-```
-
-#### Quadratic one
-
-```{r}
-pred_log_bm_quad <- model_log_bm_by_protocol_summary %>%
-  filter(model == "mod_bm_quad", protocol_type == "complete") %>%
-  mutate(
-    pred = map(model_obj, ~ggpredict(.x,
-	terms = c("bm_slope", "bm [quart2]"))),
-    pred_df = map(pred, as_tibble),
-    plot = map(pred, ~plot(.x, add.data = FALSE)),
-    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
-    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
-  )
-model_log_bm_by_protocol %<>% filter(protocol_type == "complete")
-
-pred_log_bm_quad_plot <- map2(model_log_bm$data, pred_log_bm_quad$pred_df, plot_pred_data,
-  std_error = TRUE)
-plot_grid(plotlist = pred_log_bm_quad_plot, labels = model_log_bm$variable)
-```
-
-```{r, eval = FALSE}
-pred <- model_log_bm_by_protocol_summary %>%
-  filter(model == "mod_log_bm_inc") %>%
-  mutate(
-    pred = map(model_obj, ~ggpredict(.x,
-	terms = c("bm_slope", "log_bm [quart2]", "inc_f"))),
-    pred_df = map(pred, as_tibble),
-    plot = map(pred, ~plot(.x, add.data = FALSE)),
-    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
-  )
-plot_grid(plotlist = pred$plot, labels = pred$variable)
-```
-
-```{r}
-pred <- model_log_bm_by_protocol_summary %>%
-  filter(model == "mod_log_bm_inc") %>%
-  mutate(
-    pred = map(model_obj, ~ggpredict(.x,
-	terms = c("bm_slope", "log_bm [quart2]", "inc_f"))),
-    pred_df = map(pred, as_tibble),
-    plot = map(pred, ~plot(.x, add.data = FALSE)),
-    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
-  )
-plot_grid(plotlist = pred$plot, labels = pred$variable)
-```
-
-### Can we predict the model without all simple effects?
-
-```{r, eval = FALSE}
-# Perform a valid model 
-pred <- model_int %>%
-  select(-data, -mod4) %>%
-  pivot_longer(cols = c(mod1:mod5), names_to = "model_type", values_to =
-    "mod_obj") %>%
-  mutate(
-    pred_ref = map2(mod_obj, model_type, function (x, y) {
-       if (y %in% c("mod3", "mod5"))
-	 terms_spec <- c("bm_slope", "inc_f", "bm")
-       else
-	 terms_spec <- c("bm_slope", "inc_f", "bm_group") 
-      ggpredict(x, terms = terms_spec)
-      }
-    ),
-    pred_cte = map2(mod_obj, model_type, function (x, y) {
-       if (y %in% c("mod3", "mod5"))
-	 terms_spec <- c("linear_slope", "inc_f", "bm")
-       else
-	 terms_spec <- c("linear_slope", "inc_f", "bm_group") 
-      ggeffect(x, terms = terms_spec)
-      }
-    )
-  )
-
-pred %<>%
-  mutate(
-  plot_pred_ref = map(pred_ref, plot, add.data = TRUE),
-  plot_pred_cte = map(pred_cte, plot, add.data = TRUE)
-  )
-pred_richness <- pred %>%
-  filter(variable == "richness", model_type == "mod3")
-
-pred$plot_pred_ref[[1]]
-pred$plot_pred_cte[[1]]
-pred$plot_pred[[2]]
-pred$plot_pred[[3]]
-pred$plot_pred_ref[[4]]
-```
-
-```{r, eval = FALSE}
-library(ggeffects)
-mydf <- ggpredict(model_int$mod3[[1]], terms = c("linear_slope", "inc_f",
-    "bm"))
-plot(mydf, add.data = TRUE)
-
-```
-
-```{r, eval = FALSE}
-model_log %<>%
-  mutate(
-    pred5 = map(mod3, ~ggpredict(.x,
-	terms = c("linear_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2, 3, 4, 6]", "inc_f", "bm"))),
-    pred5_df = map(pred5, as_tibble),
-    plot = map(pred5, ~plot(.x, add.data = TRUE)),
-    myplot = map2(pred5, data, ~plot_final_model(ggpred = .x, rawdata = .y))
-  )
-
-#plot_final_model(model_int$pred5[[1]], model_int$data[[1]])
-plot_grid(plotlist = model_int$plot, labels = model_int$variable)
-model_int$plot[[1]]
-summary(model_int$mod3[[1]])
-test <- model_int$data[[1]]
-model_int$pred5_df[[1]]
-test %>%
-  ggplot(aes(x = bm_slope, y = linear_slope, weight = reg_weight, size = reg_weight)) +
-  geom_smooth(method = "lm") +
-  geom_point()
-
-pred_test <-
-  model_int$pred5_df[[1]] %>%
-  as_tibble %>%
-  rename(increasing = group, group = facet) %>%
-  filter(increasing == FALSE & x < 0 | increasing == TRUE & x > 0)
-
-p <- ggplot(pred_test, aes(x = x , y = predicted, color = group)) +
-  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group), alpha =
-    .1) +
-  geom_line() +
-  geom_point(data = rename(test,
-      predicted = linear_slope, x = bm_slope),
-    aes(x = x, y = predicted),
-    inherit.aes = FALSE)
-```
-
-```{r, eval = FALSE}
-model_int$pred5_df[[1]] %>%
-  ggplot()
-
-plot_final_model(model_int$pred5[[1]], rawdata = model_int$data[[1]], facet =
-  TRUE)
-```
-
 # Methods
-
-## Biomass classification
-
-```{r}
-loadd(rigal_classification)
-myload(biomass_ts_sax, envir = globalenv(),dir = get_mypath("data"))
-
-biomass_classif_rigal <- rigal_classification %>%
-  filter(variable %in% c("bm_std", "log_bm_std")) %>%
-  unnest(classif) %>%
-  mutate(station = as.character(station)) %>%
-  select(station, variable,shape_class)
-
-p_biomass_classif_rigal <- biomass_classif_rigal %>%
-  ggplot(aes(x = shape_class)) +
-  geom_bar() +
-  facet_wrap(~variable) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-```
-
-## Temporal dynamics
-
-```{r}
-p_cap <- paste0(
-  "Temporal dynamics of biomass and temporal dynamics of
-  metrics for 10 randomly selected communities."
-)
-```
-
-```{r p-tmp-dyn, cache = TRUE, eval = FALSE}
-
-p <- vector(mode = "list", length = 10)
-for (i in seq_len(length(p))) {
-  to_plot <- temporal_dynamics_plot %>% 
-    filter(station == sample(temporal_dynamics_plot$station, 1))
-  p[[i]] <- cowplot::plot_grid(plotlist = to_plot$plot, labels = to_plot$station)
-}
-p
-```
-
-## Temporal dynamics decrease/increase constant
-
-### Log biomass
-
-```{r, cache = TRUE, fig.height = 45}
-st_decrease_increase_rigal <- biomass_classif_rigal %>%
-  filter(variable == "log_bm_std") %>%
-  filter(shape_class %in% c("increase_constant", "decrease_constant"))
-data_decrease_increase <- full_data2 %>%
-  filter(station %in% st_decrease_increase_rigal$station)
-
-log_bm_min_max <- map_dbl(c(min, max),
-  ~.x(data_decrease_increase$log_bm_std, na.rm = TRUE))
-nb_year_min_max <- map_dbl(c(min, max),
-  ~.x(data_decrease_increase$nb_year, na.rm = TRUE))
-temporal_dynamics_plot$plot %<>%
-  map(., ~ .x + lims(y = log_bm_min_max, x = nb_year_min_max))
-
-temporal_dynamics_plot %>%
-  filter(variable == "log_bm_std", station %in% st_decrease_increase_rigal$station) %>%
-  plot_grid(plotlist = .$plot, ncol = 3, labels = st_decrease_increase_rigal$station)
-```
-
-### Raw Biomass
-
-```{r, cache = TRUE, fig.height = 45}
-st_decrease_increase_rigal_biomass <- rigal_classification %>%
-  filter(variable == "bm_std") %>%
-  unnest(classif) %>%
-  filter(shape_class %in% c("increase_constant", "decrease_constant"))
-
-bm_min_max <- map_dbl(
-  c(min, max),
-  ~.x(data_decrease_increase$bm_std, na.rm = TRUE))
-nb_year_min_max <- map_dbl(
-  c(min, max),
-  ~.x(data_decrease_increase$nb_year, na.rm = TRUE))
-temporal_dynamics_plot[temporal_dynamics_plot$variable == "bm_std",]$plot %<>%
-  map(., ~ .x + lims(y = bm_min_max, x = nb_year_min_max))
-
-temporal_dynamics_plot %>%
-  filter(variable == "bm_std", station %in% st_decrease_increase_rigal_biomass$station) %>%
-  plot_grid(plotlist = .$plot, ncol = 3, labels = st_decrease_increase_rigal_biomass$station)
-```
-
-### Richness
-
-```{r, cache = TRUE, fig.height = 45}
-var_tmp <- "rich_std"
-st_decrease_increase_rigal <- rigal_classification %>%
-  filter(variable == var_tmp) %>%
-  unnest(classif) %>%
-  filter(shape_class %in% c("increase_constant", "decrease_constant"))
-
-min_max <- map_dbl(
-  c(min, max),
-  ~.x(data_decrease_increase[[var_tmp]], na.rm = TRUE))
-nb_year_min_max <- map_dbl(
-  c(min, max),
-  ~.x(data_decrease_increase$nb_year, na.rm = TRUE))
-temporal_dynamics_plot[temporal_dynamics_plot$variable == var_tmp,]$plot %<>%
-  map(., ~ .x + lims(y = min_max, x = nb_year_min_max))
-
-temporal_dynamics_plot %>%
-  filter(variable == var_tmp, station %in% st_decrease_increase_rigal$station) %>%
-  plot_grid(plotlist = .$plot, ncol = 3, labels = st_decrease_increase_rigal$station)
-```
-
-### Number of nodes
-
-```{r, cache = TRUE, fig.height = 45}
-var_tmp <- "nbnode_std"
-st_decrease_increase_rigal <- rigal_classification %>%
-  filter(variable == var_tmp) %>%
-  unnest(classif) %>%
-  filter(shape_class %in% c("increase_constant", "decrease_constant"))
-
-min_max <- map_dbl(
-  c(min, max),
-  ~.x(data_decrease_increase[[var_tmp]], na.rm = TRUE))
-nb_year_min_max <- map_dbl(
-  c(min, max),
-  ~.x(data_decrease_increase$nb_year, na.rm = TRUE))
-temporal_dynamics_plot[temporal_dynamics_plot$variable == var_tmp,]$plot %<>%
-  map(., ~ .x + lims(y = min_max, x = nb_year_min_max))
-
-temporal_dynamics_plot %>%
-  filter(variable == var_tmp, station %in% st_decrease_increase_rigal$station) %>%
-  plot_grid(plotlist = .$plot, ncol = 3, labels = st_decrease_increase_rigal$station)
-```
 
@@
 ```
-
 ### Tendancies in rigal increase / decrease
@@
 
+## Other Statistical model
+
+#### Quadratic one
+
+```{r}
+pred_log_bm_quad <- model_log_bm_summary %>%
+  filter(model == "mod_bm_quad") %>%
+  mutate(
+    pred = map(model_obj, ~ggpredict(.x,
+	terms = c("bm_slope", "bm [quart2]"))),
+    pred_df = map(pred, as_tibble),
+    plot = map(pred, ~plot(.x, add.data = FALSE)),
+    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
+    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
+  )
+
+test <- map2(model_log_bm$data, pred_log_bm_quad$pred_df, plot_pred_data,
+  std_error = TRUE)
+plot_grid(plotlist = test, labels = model_log_bm$variable)
+```
+
+```{r}
+loadd(log_bm_net_group, model_log_bm_vif)
+
+model_log_bm_vif %>%
+  ggplot(aes(y= vif, x = term)) +
+  geom_hline(yintercept = 10) +
+  geom_bar(stat = "identity") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  facet_grid(model_type~variable, scales = "free")
+```
+
+### By protocol
+
+```{r}
+loadd(model_log_bm_by_protocol_vif)
+
+protocol_vec <- model_log_bm_by_protocol_vif$protocol_type %>% unique
+p_vif_protocol <- map(protocol_vec, function (x) {
+  model_log_bm_by_protocol_vif %>%
+    filter(protocol_type == x) %>%
+    ggplot(aes(y= vif, x = term)) +
+    geom_hline(yintercept = 10) +
+    geom_bar(stat = "identity") +
+    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+    labs(title = paste0("Protocol type: ", x)) +
+    facet_grid(model_type~variable, scales = "free_y")
+  })
+p_vif_protocol[[1]]
+p_vif_protocol[[2]]
+```
+
+```{r}
+loadd(model_log_bm_by_protocol, model_log_bm_by_protocol_summary)
+```
+
+```{r, eval = FALSE}
+complete_log_quad2 <- model_log_bm_by_protocol_summary %>%
+  filter(model == "mod_bm_quad2", protocol_type == "complete") %>%
+  mutate(
+    reg_table = map(model_obj, broom::tidy),
+    anova_table = map(anova, broom::tidy)
+  )
+
+complete_log_quad2[["reg_table"]] %>% 
+  bind_rows(.) %>%
+  mutate(variable = rep(complete_log_quad2[["variable"]], each = 6)) %>%
+  select(variable, everything()) %>%
+  kable(.,
+    booktabs = TRUE, 
+    caption = 
+      paste0(
+      "Regression table for the model: dN =",
+      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
+    ) 
+  )
+
+complete_log_quad2[["anova_table"]] %>% 
+  bind_rows(.) %>%
+  mutate(variable = rep(complete_log_quad2[["variable"]], each = 6)) %>%
+  select(variable, everything()) %>%
+  kable(., booktabs = TRUE,
+    caption = 
+      paste0(
+      "ANOVA table for the model: dN =",
+      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
+    )
+  )
+```
+
+```{r, eval = FALSE}
+filter(model_log_bm_by_protocol_summary, model == "mod_log_bm_inc")[["resume"]]
+filter(model_log_bm_by_protocol_summary, model == "mod_log_bm_inc")[["anova"]]
+
+filter(model_log_bm_by_protocol_summary, model == "mod_bm_quad")[["resume"]]
+filter(model_log_bm_by_protocol_summary, model == "mod_log_bm_inc")[["anova"]]
+```
+
+#### Quadratic two
+
+```{r}
+pred_log_bm_quad2 <- model_log_bm_by_protocol_summary %>%
+  filter(model == "mod_bm_quad2", protocol_type == "complete") %>%
+  mutate(
+    pred = map(model_obj, ~ggpredict(.x,
+	terms = c("bm_slope", "bm [quart2]"))),
+    pred_df = map(pred, as_tibble),
+    plot = map(pred, ~plot(.x, add.data = FALSE)),
+    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
+    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
+  )
+model_log_bm_by_protocol %<>% filter(protocol_type == "complete")
+
+pred_log_bm_quad2_plot <- map2(model_log_bm_by_protocol$data, pred_log_bm_quad2$pred_df,
+  plot_pred_data)
+plot_grid(plotlist = pred_log_bm_quad2_plot, labels = model_log_bm$variable)
+```
+
+#### Quadratic one
+
+```{r}
+pred_log_bm_quad <- model_log_bm_by_protocol_summary %>%
+  filter(model == "mod_bm_quad", protocol_type == "complete") %>%
+  mutate(
+    pred = map(model_obj, ~ggpredict(.x,
+	terms = c("bm_slope", "bm [quart2]"))),
+    pred_df = map(pred, as_tibble),
+    plot = map(pred, ~plot(.x, add.data = FALSE)),
+    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
+    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
+  )
+model_log_bm_by_protocol %<>% filter(protocol_type == "complete")
+
+pred_log_bm_quad_plot <- map2(model_log_bm$data, pred_log_bm_quad$pred_df, plot_pred_data,
+  std_error = TRUE)
+plot_grid(plotlist = pred_log_bm_quad_plot, labels = model_log_bm$variable)
+```
+
+```{r, eval = FALSE}
+pred <- model_log_bm_by_protocol_summary %>%
+  filter(model == "mod_log_bm_inc") %>%
+  mutate(
+    pred = map(model_obj, ~ggpredict(.x,
+	terms = c("bm_slope", "log_bm [quart2]", "inc_f"))),
+    pred_df = map(pred, as_tibble),
+    plot = map(pred, ~plot(.x, add.data = FALSE)),
+    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
+  )
+plot_grid(plotlist = pred$plot, labels = pred$variable)
+```
+
+```{r, eval = FALSE}
+pred <- model_log_bm_by_protocol_summary %>%
+  filter(model == "mod_log_bm_inc") %>%
+  mutate(
+    pred = map(model_obj, ~ggpredict(.x,
+	terms = c("bm_slope", "log_bm [quart2]", "inc_f"))),
+    pred_df = map(pred, as_tibble),
+    plot = map(pred, ~plot(.x, add.data = FALSE)),
+    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
+  )
+plot_grid(plotlist = pred$plot, labels = pred$variable)
+```
+
+### Can we predict the model without all simple effects?
+
+```{r, eval = FALSE}
+# Perform a valid model 
+pred <- model_int %>%
+  select(-data, -mod4) %>%
+  pivot_longer(cols = c(mod1:mod5), names_to = "model_type", values_to =
+    "mod_obj") %>%
+  mutate(
+    pred_ref = map2(mod_obj, model_type, function (x, y) {
+       if (y %in% c("mod3", "mod5"))
+	 terms_spec <- c("bm_slope", "inc_f", "bm")
+       else
+	 terms_spec <- c("bm_slope", "inc_f", "bm_group") 
+      ggpredict(x, terms = terms_spec)
+      }
+    ),
+    pred_cte = map2(mod_obj, model_type, function (x, y) {
+       if (y %in% c("mod3", "mod5"))
+	 terms_spec <- c("linear_slope", "inc_f", "bm")
+       else
+	 terms_spec <- c("linear_slope", "inc_f", "bm_group") 
+      ggeffect(x, terms = terms_spec)
+      }
+    )
+  )
+
+pred %<>%
+  mutate(
+  plot_pred_ref = map(pred_ref, plot, add.data = TRUE),
+  plot_pred_cte = map(pred_cte, plot, add.data = TRUE)
+  )
+pred_richness <- pred %>%
+  filter(variable == "richness", model_type == "mod3")
+
+pred$plot_pred_ref[[1]]
+pred$plot_pred_cte[[1]]
+pred$plot_pred[[2]]
+pred$plot_pred[[3]]
+pred$plot_pred_ref[[4]]
+```
+
+```{r, eval = FALSE}
+library(ggeffects)
+mydf <- ggpredict(model_int$mod3[[1]], terms = c("linear_slope", "inc_f",
+    "bm"))
+plot(mydf, add.data = TRUE)
+
+```
+
+```{r, eval = FALSE}
+model_log %<>%
+  mutate(
+    pred5 = map(mod3, ~ggpredict(.x,
+	terms = c("linear_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2, 3, 4, 6]", "inc_f", "bm"))),
+    pred5_df = map(pred5, as_tibble),
+    plot = map(pred5, ~plot(.x, add.data = TRUE)),
+    myplot = map2(pred5, data, ~plot_final_model(ggpred = .x, rawdata = .y))
+  )
+
+#plot_final_model(model_int$pred5[[1]], model_int$data[[1]])
+plot_grid(plotlist = model_int$plot, labels = model_int$variable)
+model_int$plot[[1]]
+summary(model_int$mod3[[1]])
+test <- model_int$data[[1]]
+model_int$pred5_df[[1]]
+test %>%
+  ggplot(aes(x = bm_slope, y = linear_slope, weight = reg_weight, size = reg_weight)) +
+  geom_smooth(method = "lm") +
+  geom_point()
+
+pred_test <-
+  model_int$pred5_df[[1]] %>%
+  as_tibble %>%
+  rename(increasing = group, group = facet) %>%
+  filter(increasing == FALSE & x < 0 | increasing == TRUE & x > 0)
+
+p <- ggplot(pred_test, aes(x = x , y = predicted, color = group)) +
+  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group), alpha =
+    .1) +
+  geom_line() +
+  geom_point(data = rename(test,
+      predicted = linear_slope, x = bm_slope),
+    aes(x = x, y = predicted),
+    inherit.aes = FALSE)
+```
+
+```{r, eval = FALSE}
+model_int$pred5_df[[1]] %>%
+  ggplot()
+
+plot_final_model(model_int$pred5[[1]], rawdata = model_int$data[[1]], facet =
+  TRUE)
+```
+
 # Correlation

### 2020-10-12 R/get_data.R

@@ -22,18 +22,25 @@ get_community_data <- function (
 get_network_data <- function (network_metrics = NULL, 
   path = get_mypath("data", "classes", "network_metrics.rda"), 
 metrics = NULL) {
-
   
   load(path, envir = environment())
+
+  network_metrics %<>%
+    mutate(
+      pisc_stat = map(network, ~try(get_piscivory_stat_from_network(net = .x)))
+    )
 
   if (is.null(metrics)) {
     metrics <- c(
       "connectance", "weighted_connectance",
-      "nbnode", "w_trph_lvl_avg")
+      "nbnode", "w_trph_lvl_avg", "pisc_stat")
   }
 
   col_to_keep <- c("opcod", metrics)
   net <- network_metrics[, colnames(network_metrics) %in% col_to_keep]
+
+  net %<>%
+    unnest(cols = pisc_stat)
 
   net %<>%
     dplyr::filter(!is.na(opcod))

### 2020-10-12 R/misc.R

@@ -46,3 +46,4 @@ source_dir <- function(path, trace = TRUE, ...) {
     if(trace) cat("\n")
   }
 }
+

### 2020-10-12 make.R

@@ -9,7 +9,7 @@ source_dir("R") # Define your custom code as a bunch of functions.
 source("R/plan.R")      # Create your drake plan.
 # Call make() to run your work.
 # Your targets will be stored in a hidden .drake/ cache,
-drake::r_make(plan)
+#drake::r_make(plan)
 drake::make(plan)
 vis_drake_graph(plan)
 

### 2020-11-09 report.Rmd
Begin to concatenate analysis + few new plot

@@
   plot_pred_data)
-plot_grid(plotlist = pred_log_bm_quad2_plot, labels = model_log_bm$variable)
+legend_quad2 <- get_legend(pred_log_bm_quad2_plot[[1]])
+pred_log_bm_quad2_plot %<>% map(., ~.x + theme(legend.position = "none"))
+top <- plot_grid(plotlist = pred_log_bm_quad2_plot, labels = model_log_bm$variable)
+plot_grid(top, legend_quad2, rel_widths = c(1, .1))
+```
+-
+
+## Link biomass dynamic and environment
+
+```{r}
+myload(habitat_press, habitat_pressure,
+  envir = environment(),
+  dir = get_mypath("data"))
+#habitat_press
+```
+
+```{r}
+test <- log_bm_net_group %>%
+  filter(variable == "connectance") %>%
+  left_join(habitat_pressure, by = "station")
+test %>%
+  pivot_longer(
+    cols = c(bm, width_river_mean, temperature_med, alt , RC1, RC2),
+    names_to = "evt_var", values_to = "value") %>%
+ggplot(aes(y = bm_slope, x = value)) +
+geom_point() +
+facet_wrap(~evt_var, scales = "free_x")
+```
+
+```{r}
+library(sf)
+myload(region_polygon, envir = environment(), dir = get_mypath("data"))
+myload(station_analysis,
+  envir = environment(),
+  dir = "~/Documents/post-these/mnhn/fishcom/data")
+
+p <- ggplot() +
+  geom_sf(data = st_geometry(region_polygon)) 
+st_bm_slope <- station_analysis %>%
+  rename(station = id) %>%
+  left_join(select(test, station, bm_slope)) %>%
+  filter(!is.na(bm_slope))
+p + 
+  geom_sf(data = st_bm_slope, aes(color = bm_slope)) +
+  scale_color_viridis()
 ```

### 2020-11-09 R/variable_shortcut.R

@@ -14,3 +14,7 @@ get_species <- function(node_list) {
   species_resource_list
 
 }
+
+model_type_var <- function() {
+  c("model_bm", "model_bm_f3y", "model_log_bm", "model_log_bm_f3y")
+}

### 2020-11-09 make.R

@@ -10,11 +10,12 @@ source("R/plan.R")      # Create your drake plan.
 # Call make() to run your work.
 # Your targets will be stored in a hidden .drake/ cache,
 #drake::r_make(plan)
-drake::make(plan)
-vis_drake_graph(plan)
+drake::make(plan, keep_going = TRUE)
 
 # If you do not change any code or data,
 # subsequent make()'s do not build targets.
 
 # Load your targets back into your session with loadd() and readd().
 plan
+loadd(bm_net_group_f3y)
+loadd(bm_net_group_f3y)

### 2020-11-13 report.Rmd
Update report

@@
 ---
+
+```{r, echo = FALSE}
+
+knitr::opts_chunk$set(
+  cache = FALSE,
+  collapse = TRUE,
+  comment = "#>",
+  #fig.dim = c(7, 7),
+  fig.fullwidth = TRUE,
+  fig.show = "hold",
+  echo = FALSE,
+  message = FALSE,
+  warning = FALSE,
+  results = TRUE 
+)
+```
 
@@
 library(kableExtra)
+library(sf)
 source("R/misc.R") # Define your custom code as a bunch of functions.
+source("R/variable_shortcut.R")
 source_dir(get_mypath("R")) # Define your custom code as a bunch of functions.
@@
 ```{r}
-loadd(log_bm_net_group)
+loadd(log_bm_net_group_median)
 ```
@@
 ```{r, fig.height = 12, fig.width = 12}
-log_bm_net_group %>%
+log_bm_net_group_median %>%
   ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
@@
 ```{r, fig.height = 12, fig.width = 12}
-log_bm_net_group %>%
+log_bm_net_group_median %>%
   filter(!is.na(protocol_type)) %>%
@@
 
-log_bm_net_group %>%
+log_bm_net_group_median %>%
   filter(variable == "connectance") %>%
@@
 ```{r}
-loadd(model_log_bm, model_log_bm_summary)
+loadd(model_log_bm, summary_log_bm)
 ```
@@
 
-unique(model_log_bm_summary$variable)
-model_log_bm_table <- model_log_bm_summary %>%
+unique(summary_log_bm$variable)
+model_log_bm_table <- summary_log_bm %>%
   filter(model == "mod_bm_quad2") %>%
@@
 ```{r, fig.height = 12, fig.width = 12}
-pred_log_bm_quad2 <- model_log_bm_summary %>%
+pred_log_bm_quad2 <- summary_log_bm %>%
   filter(model == "mod_bm_quad2") %>%
@@
 ```{r}
-myload(habitat_press, habitat_pressure,
-  envir = environment(),
-  dir = get_mypath("data"))
+loadd(habitat_press, habitat_pressure)
 #habitat_press
@@
 ```{r}
-test <- log_bm_net_group %>%
+test <- log_bm_net_group_median %>%
   filter(variable == "connectance") %>%
@@
 ```{r}
-library(sf)
-myload(region_polygon, envir = environment(), dir = get_mypath("data"))
-myload(station_analysis,
-  envir = environment(),
-  dir = "~/Documents/post-these/mnhn/fishcom/data")
+loadd(region_polygon, station_analysis)
 
@@
   scale_color_viridis()
+```
+
+```{r}
+log_bm_net_group_median %>%
+  filter(variable == "rich_std", bm_slope < 0) %>%
+  left_join(habitat_pressure, by = "station") %>%
+  pivot_longer(cols = c(bm, width_river_mean, temperature_med, alt , RC1, RC2),
+    names_to = "evt_var", values_to = "value") %>%
+ggplot(aes(y = linear_slope, x = value)) +
+geom_point() +
+facet_wrap(~evt_var, scales = "free_x")
+```
+
+```{r}
+loadd(richness_group)
+rich_std_f3y <- richness_group %>% 
+  filter(rich_var == "rich_std", summary_type == "first_3_year", group_type ==
+    "median") %>%
+  select(station, rich)
+
+log_bm_net_group_median %>%
+  filter(variable == "rich_std", bm_slope < 0) %>%
+  left_join(rich_std_f3y, by = "station") %>%
+  ggplot(aes(y = linear_slope, x = rich)) +
+  geom_point()
 ```
@@
 ```{r}
-loadd(bm_net_group, log_bm_net_group, bm_vs_net_trends)
+loadd(bm_net_group_median, log_bm_net_group_median, bm_vs_net_trends)
 bm_vs_net_trends %>%
@@
 
-bm_net_group %>%
+bm_net_group_median %>%
   ggplot(aes(x = bm_slope, y = linear_slope, size = reg_weight, weight = reg_weight, color = log(bm))) +
@@
 
-log_bm_net_group %>%
+log_bm_net_group_median %>%
   ggplot(aes(x = bm_slope, y = linear_slope, size = reg_weight, weight = reg_weight, color = log(bm))) +
@@
 ```{r}
-loadd(bm_net_group)
-loadd(log_bm_net_group)
+loadd(bm_net_group_median)
+loadd(log_bm_net_group_median)
 
-bm_net_group %>%
+bm_net_group_median %>%
   ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm), size = reg_weight, weight = reg_weight)) +
@@
 
-bm_net_group %>%
+bm_net_group_median %>%
   ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
@@
 
-bm_net_group %>%
+bm_net_group_median %>%
   filter(!is.na(protocol_type)) %>%
@@
 ```{r}
-pred_log_bm_quad <- model_log_bm_summary %>%
+pred_log_bm_quad <- summary_log_bm %>%
   filter(model == "mod_bm_quad") %>%
@@
 ```{r}
-loadd(log_bm_net_group, model_log_bm_vif)
+loadd(log_bm_net_group_median, vif_log_bm)
 
-model_log_bm_vif %>%
+vif_log_bm %>%
   ggplot(aes(y= vif, x = term)) +
@@
 ```{r}
-loadd(model_log_bm_by_protocol_vif)
+loadd(vif_log_bm_by_protocol)
 
-protocol_vec <- model_log_bm_by_protocol_vif$protocol_type %>% unique
+protocol_vec <- vif_log_bm_by_protocol$protocol_type %>% unique
 p_vif_protocol <- map(protocol_vec, function (x) {
-  model_log_bm_by_protocol_vif %>%
+  vif_log_bm_by_protocol %>%
     filter(protocol_type == x) %>%
@@
 ```{r}
-loadd(model_log_bm_by_protocol, model_log_bm_by_protocol_summary)
+loadd(model_log_bm_by_protocol, summary_log_bm_by_protocol)
 ```
@@
 ```{r, eval = FALSE}
-complete_log_quad2 <- model_log_bm_by_protocol_summary %>%
+complete_log_quad2 <- summary_log_bm_by_protocol %>%
   filter(model == "mod_bm_quad2", protocol_type == "complete") %>%
@@
 ```{r, eval = FALSE}
-filter(model_log_bm_by_protocol_summary, model == "mod_log_bm_inc")[["resume"]]
-filter(model_log_bm_by_protocol_summary, model == "mod_log_bm_inc")[["anova"]]
+filter(summary_log_bm_by_protocol, model == "mod_log_bm_inc")[["resume"]]
+filter(summary_log_bm_by_protocol, model == "mod_log_bm_inc")[["anova"]]
 
-filter(model_log_bm_by_protocol_summary, model == "mod_bm_quad")[["resume"]]
-filter(model_log_bm_by_protocol_summary, model == "mod_log_bm_inc")[["anova"]]
+filter(summary_log_bm_by_protocol, model == "mod_bm_quad")[["resume"]]
+filter(summary_log_bm_by_protocol, model == "mod_log_bm_inc")[["anova"]]
 ```
@@
 ```{r}
-pred_log_bm_quad2 <- model_log_bm_by_protocol_summary %>%
+pred_log_bm_quad2 <- summary_log_bm_by_protocol %>%
   filter(model == "mod_bm_quad2", protocol_type == "complete") %>%
@@
 ```{r}
-pred_log_bm_quad <- model_log_bm_by_protocol_summary %>%
+pred_log_bm_quad <- summary_log_bm_by_protocol %>%
   filter(model == "mod_bm_quad", protocol_type == "complete") %>%
@@
 ```{r, eval = FALSE}
-pred <- model_log_bm_by_protocol_summary %>%
+pred <- summary_log_bm_by_protocol %>%
   filter(model == "mod_log_bm_inc") %>%
@@
 ```{r}
-cor_bm_net <- bm_net_group %>%
+cor_bm_net <- bm_net_group_median %>%
   select(bm_slope, variable, linear_slope, bm, width_river_mean) %>%

### 2020-11-13 report.Rmd
Improve plan

@@
   filter(term %in% "slope", coeff %in% c("bm_std", "log_bm_std")) %>%
-  select(1:4) %>%
+  select(station:estimate) %>%
   pivot_wider(names_from = "term", values_from = estimate) %>%
@@
   geom_point(aes(color = group)) +
-  facet_wrap(coeff~summary_type, scales = "free") +
+  facet_wrap(summary_type~coeff, scales = "free") +
   labs(x = "Summary of biomass (g)", y = "Slope (g.y^-1)")
@@
 
-```{r}
-loadd(log_bm_net_group_median)
+```{r, cache = FALSE}
+loadd(log_bm_net_group_f3y, model_log_bm_f3y, summary_log_bm_f3y, vif_log_bm_f3y)
+loadd(bm_net_group_median, bm_vs_net_trends)
+loadd(habitat_press, habitat_pressure)
+loadd(region_polygon, station_analysis)
+loadd(richness_group)
 ```
@@
 ```{r, fig.height = 12, fig.width = 12}
-log_bm_net_group_median %>%
+log_bm_net_group_f3y %>%
   ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
@@
 ```{r, fig.height = 12, fig.width = 12}
-log_bm_net_group_median %>%
+log_bm_net_group_f3y %>%
   filter(!is.na(protocol_type)) %>%
@@
 
-log_bm_net_group_median %>%
+log_bm_net_group_f3y %>%
   filter(variable == "connectance") %>%
@@
 
-```{r}
-loadd(model_log_bm, summary_log_bm)
-```
-
 ```{r, eval = TRUE}
@@
 
-unique(summary_log_bm$variable)
-model_log_bm_table <- summary_log_bm %>%
+model_log_bm_f3y_table <- summary_log_bm_f3y %>%
   filter(model == "mod_bm_quad2") %>%
-  filter(!variable %in% c("log_rich_std", "nbnode_std")) %>%
+  filter(variable %in% get_com_str_var(all = FALSE)) %>%
   mutate(
@@
 
-model_log_bm_table[["reg_table"]] %>% 
+model_log_bm_f3y_table[["reg_table"]] %>% 
   bind_rows(.) %>%
-  mutate(variable = rep(model_log_bm_table[["variable"]], each = 6)) %>%
+  mutate(variable = rep(model_log_bm_f3y_table[["variable"]], each = 6)) %>%
   select(variable, everything()) %>%
@@
       "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
-    ) 
-  )
+    )) %>% 
+  kable_styling(latex_options =c("scale_down")) %>%
+  #add_header_above(c(" " = 3, "Indirect effects via" = 5)) %>%
+  #column_spec(1:2, width = "3cm") %>%
+  collapse_rows(columns = 1, valign = "top")
 ```
@@
 ```{r}
-bind_rows(model_log_bm_table[["anova_table"]]) %>% 
-  mutate(variable = rep(model_log_bm_table[["variable"]], each = 6)) %>%
+bind_rows(model_log_bm_f3y_table[["anova_table"]]) %>% 
+  mutate(variable = rep(model_log_bm_f3y_table[["variable"]], each = 6)) %>%
   select(variable, everything()) %>%
@@
 ```{r}
-map_dfr(model_log_bm_table[["model_obj"]], broom::glance) %>%
-  mutate(variable = model_log_bm_table[["variable"]]) %>%
+map_dfr(model_log_bm_f3y_table[["model_obj"]], broom::glance) %>%
+  mutate(variable = model_log_bm_f3y_table[["variable"]]) %>%
   select(variable, everything()) %>%
@@
 ```{r, fig.height = 12, fig.width = 12}
-pred_log_bm_quad2 <- summary_log_bm %>%
+pred_log_bm_quad2 <- summary_log_bm_f3y %>%
   filter(model == "mod_bm_quad2") %>%
@@
 
-pred_log_bm_quad2_plot <- map2(model_log_bm$data, pred_log_bm_quad2$pred_df,
+pred_log_bm_quad2_plot <- map2(model_log_bm_f3y$data, pred_log_bm_quad2$pred_df,
   plot_pred_data)
@@
 pred_log_bm_quad2_plot %<>% map(., ~.x + theme(legend.position = "none"))
-top <- plot_grid(plotlist = pred_log_bm_quad2_plot, labels = model_log_bm$variable)
+top <- plot_grid(plotlist = pred_log_bm_quad2_plot, labels = model_log_bm_f3y$variable)
 plot_grid(top, legend_quad2, rel_widths = c(1, .1))
@@
 ```{r}
-loadd(habitat_press, habitat_pressure)
 #habitat_press
@@
 ```{r}
-test <- log_bm_net_group_median %>%
+test <- log_bm_net_group_f3y %>%
   filter(variable == "connectance") %>%
@@
 ```{r}
-loadd(region_polygon, station_analysis)
 
@@
 ```{r}
-log_bm_net_group_median %>%
+log_bm_net_group_f3y %>%
   filter(variable == "rich_std", bm_slope < 0) %>%
@@
 ```{r}
-loadd(richness_group)
 rich_std_f3y <- richness_group %>% 
@@
 
-log_bm_net_group_median %>%
+log_bm_net_group_f3y %>%
   filter(variable == "rich_std", bm_slope < 0) %>%
@@
 ```
+
 ### Tendancies in rigal increase / decrease
@@
 ```{r}
-loadd(bm_net_group_median, log_bm_net_group_median, bm_vs_net_trends)
 bm_vs_net_trends %>%
@@
 
-log_bm_net_group_median %>%
+log_bm_net_group_f3y %>%
   ggplot(aes(x = bm_slope, y = linear_slope, size = reg_weight, weight = reg_weight, color = log(bm))) +
@@
 ```{r}
-loadd(bm_net_group_median)
-loadd(log_bm_net_group_median)
-
 bm_net_group_median %>%
@@
 ```{r}
-pred_log_bm_quad <- summary_log_bm %>%
+pred_log_bm_quad <- summary_log_bm_f3y %>%
   filter(model == "mod_bm_quad") %>%
@@
 
-test <- map2(model_log_bm$data, pred_log_bm_quad$pred_df, plot_pred_data,
+test <- map2(model_log_bm_f3y$data, pred_log_bm_quad$pred_df, plot_pred_data,
   std_error = TRUE)
-plot_grid(plotlist = test, labels = model_log_bm$variable)
+plot_grid(plotlist = test, labels = model_log_bm_f3y$variable)
 ```
@@
 ```{r}
-loadd(log_bm_net_group_median, vif_log_bm)
 
-vif_log_bm %>%
+vif_log_bm_f3y %>%
   ggplot(aes(y= vif, x = term)) +
@@
 ```{r}
-loadd(model_log_bm_by_protocol, summary_log_bm_by_protocol)
+loadd(model_log_bm_f3y_by_protocol, summary_log_bm_f3y_by_protocol)
 ```
@@
 ```{r, eval = FALSE}
-complete_log_quad2 <- summary_log_bm_by_protocol %>%
+complete_log_quad2 <- summary_log_bm_f3y_by_protocol %>%
   filter(model == "mod_bm_quad2", protocol_type == "complete") %>%
@@
 ```{r, eval = FALSE}
-filter(summary_log_bm_by_protocol, model == "mod_log_bm_inc")[["resume"]]
-filter(summary_log_bm_by_protocol, model == "mod_log_bm_inc")[["anova"]]
+filter(summary_log_bm_f3y_by_protocol, model == "mod_log_bm_inc")[["resume"]]
+filter(summary_log_bm_f3y_by_protocol, model == "mod_log_bm_inc")[["anova"]]
 
-filter(summary_log_bm_by_protocol, model == "mod_bm_quad")[["resume"]]
-filter(summary_log_bm_by_protocol, model == "mod_log_bm_inc")[["anova"]]
+filter(summary_log_bm_f3y_by_protocol, model == "mod_bm_quad")[["resume"]]
+filter(summary_log_bm_f3y_by_protocol, model == "mod_log_bm_inc")[["anova"]]
 ```
@@
 ```{r}
-pred_log_bm_quad2 <- summary_log_bm_by_protocol %>%
+pred_log_bm_quad2 <- summary_log_bm_f3y_by_protocol %>%
   filter(model == "mod_bm_quad2", protocol_type == "complete") %>%
@@
   )
-model_log_bm_by_protocol %<>% filter(protocol_type == "complete")
+model_log_bm_f3y_by_protocol %<>% filter(protocol_type == "complete")
 
-pred_log_bm_quad2_plot <- map2(model_log_bm_by_protocol$data, pred_log_bm_quad2$pred_df,
+pred_log_bm_quad2_plot <- map2(model_log_bm_f3y_by_protocol$data, pred_log_bm_quad2$pred_df,
   plot_pred_data)
-plot_grid(plotlist = pred_log_bm_quad2_plot, labels = model_log_bm$variable)
+plot_grid(plotlist = pred_log_bm_quad2_plot, labels = model_log_bm_f3y$variable)
 ```
@@
 ```{r}
-pred_log_bm_quad <- summary_log_bm_by_protocol %>%
+pred_log_bm_quad <- summary_log_bm_f3y_by_protocol %>%
   filter(model == "mod_bm_quad", protocol_type == "complete") %>%
@@
   )
-model_log_bm_by_protocol %<>% filter(protocol_type == "complete")
+model_log_bm_f3y_by_protocol %<>% filter(protocol_type == "complete")
 
-pred_log_bm_quad_plot <- map2(model_log_bm$data, pred_log_bm_quad$pred_df, plot_pred_data,
+pred_log_bm_quad_plot <- map2(model_log_bm_f3y$data, pred_log_bm_quad$pred_df, plot_pred_data,
   std_error = TRUE)
-plot_grid(plotlist = pred_log_bm_quad_plot, labels = model_log_bm$variable)
+plot_grid(plotlist = pred_log_bm_quad_plot, labels = model_log_bm_f3y$variable)
 ```
@@
 ```{r, eval = FALSE}
-pred <- summary_log_bm_by_protocol %>%
+pred <- summary_log_bm_f3y_by_protocol %>%
   filter(model == "mod_log_bm_inc") %>%

### 2020-11-19 report.Rmd
Function to compare the two models

@@
 #https://stackoverflow.com/questions/44457243/regression-tables-in-r-markdown-rmarkdown-html-pdf
-
-model_log_bm_f3y_table <- summary_log_bm_f3y %>%
-  filter(model == "mod_bm_quad2") %>%
-  filter(variable %in% get_com_str_var(all = FALSE)) %>%
-  mutate(
-    reg_table = map(model_obj, broom::tidy),
-    anova_table = map(anova, broom::tidy)
+model_log_bm_f3y_table <- get_table_from_summary(
+  .data = summary_log_bm_f3y,
+  model =  "mod_bm_quad2",
+  variable = get_com_str_var(all = FALSE)
 )
@@
 model_log_bm_f3y_table[["reg_table"]] %>% 
-  bind_rows(.) %>%
-  mutate(variable = rep(model_log_bm_f3y_table[["variable"]], each = 6)) %>%
-  select(variable, everything()) %>%
   kable(.,
@@
 ```{r}
-bind_rows(model_log_bm_f3y_table[["anova_table"]]) %>% 
-  mutate(variable = rep(model_log_bm_f3y_table[["variable"]], each = 6)) %>%
-  select(variable, everything()) %>%
+model_log_bm_f3y_table[["anova_table"]] %>% 
   kable(., booktabs = TRUE,
@@
     )
-  )
-
+  ) %>%
+  collapse_rows(columns = 1, valign = "top")
 ```
@@
 ```{r}
-map_dfr(model_log_bm_f3y_table[["model_obj"]], broom::glance) %>%
-  mutate(variable = model_log_bm_f3y_table[["variable"]]) %>%
-  select(variable, everything()) %>%
+model_log_bm_f3y_table[["model_obj"]] %>%
   kable(., booktabs = TRUE,
-    caption = 
-      paste0(
-      "Model summary for the model: dN =",
-      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
-    )
+    caption = paste0( "Model summary for the model: dN =",
+      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2.")
   )
@@
 ```
--
+
+### Compare Quad2 and piecewiseregression
+
+```{r}
+effect_quad2_piece <- tibble(
+  effect = c("Dynamic of biomass", "disassembly/assembly", "com size", "Effect of bm dyn dep on com size?", "Effect of bm dyn dep on disassembly/assembly context?", "Effect of bm dyn dep on both dis/assembly and com size ?"),
+  mod_bm_quad2 = c("bm_slope", "I(bm_slope^2)", "bm", "bm_slope:bm", "I(bm_slope^2)", "bm:I(bm_slope^2)"),
+  mod_all_bm = c("bm_slope", "inc_fTRUE", "bm", "bm_slope:bm", "bm_slope:inc_fTRUE", "bm_slope:inc_fTRUE:bm")
+)
+
+combin <- expand.grid(
+  variable = get_com_str_var(),
+  mod_bm_quad2 = unique(effect_quad2_piece$mod_bm_quad2), 
+  stat = c("estimate", "p.value")
+) %>%
+left_join(select(effect_quad2_piece, 2:3)) %>%
+pivot_longer(cols = c(mod_bm_quad2, mod_all_bm), names_to = "model", values_to = "term") %>%
+mutate_all(as.character)
+
+comparison_table <- distinct(combin) %>%
+  mutate(
+    coeff = pmap_dbl(list(variable, stat, model, term),
+      ~get_coef_from_terms(mydata = model_log_bm_f3y,
+	variable = ..1, model = ..3, term = ..4, type = ..2
+	) 
+  )) %>%
+arrange(variable)
+unique(comparison_table$term)
+
+test <- comparison_table %>%
+  left_join(
+    pivot_longer(effect_quad2_piece, cols = c(mod_bm_quad2, mod_all_bm),
+      names_to = "model", values_to = "term")
+  ) %>%
+  select(variable:model, coeff, effect) %>%
+  pivot_wider(names_from = stat, values_from = coeff) %>%
+  pivot_wider(names_from = model, values_from = c(estimate, p.value))
+
+test2 <- comparison_table %>%
+  left_join(
+    pivot_longer(effect_quad2_piece, cols = c(mod_bm_quad2, mod_all_bm),
+      names_to = "model", values_to = "term")) %>%
+  filter(stat == "p.value") %>%
+  select(variable:model, coeff, effect) %>%
+  pivot_wider(names_from = stat, values_from = coeff) %>%
+  pivot_wider(names_from = model, values_from = c(p.value)) %>%
+  kable(., booktabs = TRUE,
+    caption = 
+      paste0(
+      "Comparison of the two Statistical model"
+    )
+  ) %>%
+  collapse_rows(columns = 1, valign = "top")
+```
 
@@
 ```{r, eval = FALSE}
-complete_log_quad2 <- summary_log_bm_f3y_by_protocol %>%
-  filter(model == "mod_bm_quad2", protocol_type == "complete") %>%
-  mutate(
-    reg_table = map(model_obj, broom::tidy),
-    anova_table = map(anova, broom::tidy)
-  )
+complete_log_quad2 <- get_table_from_summary(.data = summary_log_bm_f3y_by_protocol, model = "mod_bm_quad2", protocol = "complete")
 
 complete_log_quad2[["reg_table"]] %>% 
-  bind_rows(.) %>%
-  mutate(variable = rep(complete_log_quad2[["variable"]], each = 6)) %>%
-  select(variable, everything()) %>%
   kable(.,
@@
 complete_log_quad2[["anova_table"]] %>% 
-  bind_rows(.) %>%
-  mutate(variable = rep(complete_log_quad2[["variable"]], each = 6)) %>%
-  select(variable, everything()) %>%
   kable(., booktabs = TRUE,

### 2020-11-24 report.Rmd
Select the model 2 for the follow up

@@
 author: "Alain Danet"
+self_contained: yes
 date: "`r Sys.Date()`"
@@
 
+## The three model
+
+1. $dN = dB + dB \times B + dB^2 + dB^2 \times B$
+
+2. $dN = dB + B + dB \times B + Inc \times B + dB \times Inc \times B$
+
+3. $dN = dB + B + dB \times B + Inc + Inc \times dB + dB \times B \times Inc$
+
+with:
+- $dN$: temporal trend of network structure
+- $dB$: temporal trend of total (log) biomass
+- $B$: total median biomass or total biomass of the first three year
+- $Inc$: Is $dB > 0$?
+
 ```{r, cache = FALSE}
-loadd(log_bm_net_group_f3y, model_log_bm_f3y, summary_log_bm_f3y, vif_log_bm_f3y)
+loadd(log_bm_net_group_f3y, model_log_bm_f3y,
+  summary_log_bm_f3y, vif_log_bm_f3y)
 loadd(bm_net_group_median, bm_vs_net_trends)
@@
 ```{r, fig.height = 12, fig.width = 12}
-log_bm_net_group_f3y %>%
-  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
-  geom_point() +
-  scale_color_viridis() +
-  geom_errorbar(aes(xmin = bm_slope - bm_slope_strd_error,
-      xmax = bm_slope + bm_slope_strd_error), alpha = .3) +
-  geom_errorbar(aes(ymin = linear_slope - linear_slope_strd_error,
-      ymax = linear_slope + linear_slope_strd_error), alpha = .3) +
-  facet_wrap(~variable, scales = "free") +
-  labs_log_bm_net_trends()
+pred_log_bm_quad2 <- summary_log_bm_f3y %>%
+  filter(model == "mod_bm_quad2", variable %in% get_com_str_var()) %>%
+  mutate(
+    pred = map(model_obj, ~ggpredict(.x,
+	terms = c("bm_slope", "bm [quart2]"))),
+    pred_df = map(pred, as_tibble),
+    plot = map(pred, ~plot(.x, add.data = FALSE)),
+    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
+    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
+  )
+pred_log_bm_quad2_plot <- map2(
+  filter(model_log_bm_f3y, variable %in% get_com_str_var())$data,
+  pred_log_bm_quad2$pred_df,
+  plot_pred_data)
+legend_quad2 <- get_legend(pred_log_bm_quad2_plot[[1]])
+pred_log_bm_quad2_plot %<>% map(., ~.x + theme(legend.position = "none"))
+top <- plot_grid(plotlist = pred_log_bm_quad2_plot, labels = model_log_bm_f3y$variable)
+quad2_plot <- plot_grid(top, legend_quad2, rel_widths = c(1, .1))
 ```
 
-```{r, fig.height = 12, fig.width = 12}
-log_bm_net_group_f3y %>%
-  filter(!is.na(protocol_type)) %>%
-  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
-  geom_point() +
-  scale_color_viridis() +
-  geom_errorbar(aes(xmin = bm_slope - bm_slope_strd_error,
-      xmax = bm_slope + bm_slope_strd_error), alpha = .3) +
-  geom_errorbar(aes(ymin = linear_slope - linear_slope_strd_error,
-      ymax = linear_slope + linear_slope_strd_error), alpha = .3) +
-  facet_grid(variable~protocol_type, scales = "free") +
-  labs_log_bm_net_trends()
+```{r}
+pred_log_bm_medium <- summary_log_bm_f3y %>%
+  filter(model == "mod_medium_bm", variable %in% get_com_str_var()) %>%
+  mutate(
+    pred = map(model_obj, ~ggpredict(.x,
+	terms = c("bm_slope [-0.2,-0.00001,0.00001,.2]", "inc_f", "bm [quart2]"))),
+    pred_df = map(pred, as_tibble),
+    plot = map(pred, ~plot(.x, add.data = FALSE)),
+    #myplot = map2(pred, , ~plot_final_model(ggpred = .x))
+  )
+plot_inc <- map2(
+  pred_log_bm_medium$pred,
+  filter(model_log_bm_f3y, variable %in% get_com_str_var())$data,
+  ~plot_final_model(ggpred = .x, rawdata = .y))
 
-log_bm_net_group_f3y %>%
-  filter(variable == "connectance") %>%
-  ggplot(aes(x = bm_slope, y = bm)) +
-  geom_point()
-  labs(x = "Biomass trends (log biomass per year)", y = "Biomass")
+plot_inc %<>% map(., ~.x + theme(legend.position = "none"))
+medium_plot <- plot_grid(plotlist = plot_inc, labels = pred_log_bm_medium$variable)
+```
+
+```{r, fig.height = 12}
+plot_grid(quad2_plot, medium_plot, nrow = 2, labels = c("poly", "piecereg"))
+```
+
+### Compare Quad2 and piecewiseregression
+
+```{r}
+loadd(model_log_bm, summary_model_log_bm,
+  summary_log_bm, vif_model_log_bm)
+```
+
+```{r}
+effect_quad2_piece <- tibble(
+  effect = c("Dynamic of biomass", "disassembly/assembly", "com size", "bm dyn dep on com size?", "bm dyn dep on disassembly/assembly?", "bm dyn dep on both dis/assembly and com size ?"),
+  mod_bm_quad2 = c("bm_slope", "I(bm_slope^2)", "bm", "bm_slope:bm", "I(bm_slope^2)", "bm:I(bm_slope^2)"),
+  mod_medium_bm = c("bm_slope", "bm_slope:inc_fTRUE", "bm", "bm_slope:bm", "bm_slope:inc_fTRUE", "bm_slope:bm:inc_fTRUE")
+)
+effect_quad2_piece %>%
+  kable(., booktabs = TRUE,
+    caption = 
+      paste0(
+      "Hypothesis and matching coefficients."
+    )
+    )
+```
+
+```{r}
+hyp_table_f3y <- make_hyp_table(hyp_table = effect_quad2_piece, mod = model_log_bm_f3y)
+
+hyp_table_f3y %>%
+  kable(., booktabs = TRUE,
+    caption = 
+      paste0(
+      "Comparison of the two Statistical model for first three year"
+    )
+  ) %>%
+  collapse_rows(columns = 1, valign = "top")
+```
+
+```{r}
+hyp_table <- make_hyp_table(hyp_table = effect_quad2_piece, mod = model_log_bm)
+hyp_table %>%
+  kable(., booktabs = TRUE,
+    caption = 
+      paste0(
+      "Comparison of the two Statistical model for the median biomass model"
+    )
+  ) %>%
+  collapse_rows(columns = 1, valign = "top")
 ```
@@
 ```{r}
-model_log_bm_f3y_table[["model_obj"]] %>%
-  kable(., booktabs = TRUE,
-    caption = paste0( "Model summary for the model: dN =",
-      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2.")
+model_log_bm_f3y_table_medium <- get_table_from_summary(
+  .data = summary_log_bm_f3y,
+  model =  "mod_medium_bm",
+  variable = get_com_str_var(all = FALSE)
 )
+
+model_log_bm_f3y_table_medium[["reg_table"]] %>% 
+  kable(.,
+    booktabs = TRUE, 
+    caption = 
+      paste0(
+      "Regression table for the model: dN =",
+      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
+    )) %>% 
+  kable_styling(latex_options =c("scale_down")) %>%
+  #add_header_above(c(" " = 3, "Indirect effects via" = 5)) %>%
+  #column_spec(1:2, width = "3cm") %>%
+  collapse_rows(columns = 1, valign = "top")
 ```
 
-#### Quadratic two
-
-```{r, fig.height = 12, fig.width = 12}
-pred_log_bm_quad2 <- summary_log_bm_f3y %>%
-  filter(model == "mod_bm_quad2") %>%
-  mutate(
-    pred = map(model_obj, ~ggpredict(.x,
-	terms = c("bm_slope", "bm [quart2]"))),
-    pred_df = map(pred, as_tibble),
-    plot = map(pred, ~plot(.x, add.data = FALSE)),
-    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
-    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
-  )
-
-pred_log_bm_quad2_plot <- map2(model_log_bm_f3y$data, pred_log_bm_quad2$pred_df,
-  plot_pred_data)
-legend_quad2 <- get_legend(pred_log_bm_quad2_plot[[1]])
-pred_log_bm_quad2_plot %<>% map(., ~.x + theme(legend.position = "none"))
-top <- plot_grid(plotlist = pred_log_bm_quad2_plot, labels = model_log_bm_f3y$variable)
-plot_grid(top, legend_quad2, rel_widths = c(1, .1))
-```
-
-### Compare Quad2 and piecewiseregression
-
 ```{r}
-effect_quad2_piece <- tibble(
-  effect = c("Dynamic of biomass", "disassembly/assembly", "com size", "Effect of bm dyn dep on com size?", "Effect of bm dyn dep on disassembly/assembly context?", "Effect of bm dyn dep on both dis/assembly and com size ?"),
-  mod_bm_quad2 = c("bm_slope", "I(bm_slope^2)", "bm", "bm_slope:bm", "I(bm_slope^2)", "bm:I(bm_slope^2)"),
-  mod_all_bm = c("bm_slope", "inc_fTRUE", "bm", "bm_slope:bm", "bm_slope:inc_fTRUE", "bm_slope:inc_fTRUE:bm")
-)
-
-combin <- expand.grid(
-  variable = get_com_str_var(),
-  mod_bm_quad2 = unique(effect_quad2_piece$mod_bm_quad2), 
-  stat = c("estimate", "p.value")
-) %>%
-left_join(select(effect_quad2_piece, 2:3)) %>%
-pivot_longer(cols = c(mod_bm_quad2, mod_all_bm), names_to = "model", values_to = "term") %>%
-mutate_all(as.character)
-
-comparison_table <- distinct(combin) %>%
-  mutate(
-    coeff = pmap_dbl(list(variable, stat, model, term),
-      ~get_coef_from_terms(mydata = model_log_bm_f3y,
-	variable = ..1, model = ..3, term = ..4, type = ..2
-	) 
-  )) %>%
-arrange(variable)
-unique(comparison_table$term)
-
-test <- comparison_table %>%
-  left_join(
-    pivot_longer(effect_quad2_piece, cols = c(mod_bm_quad2, mod_all_bm),
-      names_to = "model", values_to = "term")
-  ) %>%
-  select(variable:model, coeff, effect) %>%
-  pivot_wider(names_from = stat, values_from = coeff) %>%
-  pivot_wider(names_from = model, values_from = c(estimate, p.value))
-
-test2 <- comparison_table %>%
-  left_join(
-    pivot_longer(effect_quad2_piece, cols = c(mod_bm_quad2, mod_all_bm),
-      names_to = "model", values_to = "term")) %>%
-  filter(stat == "p.value") %>%
-  select(variable:model, coeff, effect) %>%
-  pivot_wider(names_from = stat, values_from = coeff) %>%
-  pivot_wider(names_from = model, values_from = c(p.value)) %>%
+model_log_bm_f3y_table_medium[["anova_table"]] %>% 
   kable(., booktabs = TRUE,
@@
       paste0(
-      "Comparison of the two Statistical model"
+      "ANOVA table for the model: dN =",
+      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
     )
@@
   labs(title = "Group as mean biomass")
+```
+
+```{r, fig.height = 12, fig.width = 12}
+log_bm_net_group_f3y %>%
+  filter(!is.na(protocol_type)) %>%
+  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
+  geom_point() +
+  scale_color_viridis() +
+  geom_errorbar(aes(xmin = bm_slope - bm_slope_strd_error,
+      xmax = bm_slope + bm_slope_strd_error), alpha = .3) +
+  geom_errorbar(aes(ymin = linear_slope - linear_slope_strd_error,
+      ymax = linear_slope + linear_slope_strd_error), alpha = .3) +
+  facet_grid(variable~protocol_type, scales = "free") +
+  labs_log_bm_net_trends()
+```
+
+```{r}
+knitr::opts_chunk$set(
+  eval = FALSE 
+)
 ```

### 2020-11-24 R/statistical_model.R

@@ -138,21 +138,21 @@ compute_my_lm_vs_net_model <- function (
 	   #linear_slope~ bm_slope + bm_slope:inc_f + bm_slope:bm_group +
 	    #bm_slope:inc_f:bm_group,
 	  #.x, weights = reg_weight)),
-     #mod_medium_bm = map(data, ~lm(
-	   #linear_slope ~ bm_slope + bm_slope:inc_f + bm_slope:bm +
-	    #bm_slope:inc_f:bm,
-	  #.x, weights = reg_weight)),
+     mod_medium_bm = map(data, ~lm(
+	   linear_slope ~ bm_slope + bm + bm_slope:inc_f + bm_slope:bm +
+	    bm_slope:inc_f:bm,
+	  .x, weights = reg_weight)),
       #mod_min_bm = map(data, ~lm(
 	  #linear_slope ~ bm_slope:inc_f + bm_slope:bm +
 	    #bm_slope:inc_f:bm,
 	  #.x, weights = reg_weight)),
       mod_all_bm = map(data, ~lm(linear_slope ~ bm_slope*inc_f*bm, .x, weights = reg_weight)),
-      mod_all_log_bm = map(data, ~lm(linear_slope ~ bm_slope*inc_f*log_bm, .x, weights = reg_weight)),
+      #mod_all_log_bm = map(data, ~lm(linear_slope ~ bm_slope*inc_f*log_bm, .x, weights = reg_weight)),
       #mod_bm = map(data, ~lm(linear_slope ~ bm_slope*bm, .x, weights = reg_weight)),
       mod_bm_quad = map(data, ~lm(linear_slope ~ bm_slope*bm + I(bm_slope^2), .x, weights = reg_weight)),
       mod_bm_quad2 = map(data, ~lm(linear_slope ~ bm_slope*bm + I(bm_slope^2)*bm, .x, weights = reg_weight)),
-      mod_log_bm_quad = map(data, ~lm(linear_slope ~ bm_slope*log_bm + I(bm_slope^2), .x, weights = reg_weight)),
-      mod_log_bm_quad2 = map(data, ~lm(linear_slope ~ bm_slope*log_bm + I(bm_slope^2)*log_bm, .x, weights = reg_weight)),
+      #mod_log_bm_quad = map(data, ~lm(linear_slope ~ bm_slope*log_bm + I(bm_slope^2), .x, weights = reg_weight)),
[…]

### 2020-11-24 make.R

@@ -21,5 +21,3 @@ drake::vis_drake_graph(plan)
 # Load your targets back into your session with loadd() and readd().
 plan
 print(plan, n = 40)
-
-loadd(log_bm_net_group_f3y)

### 2020-11-30 report.Rmd
Predictions with only significant terms

--- 2020-11-13 report.Rmd
@@
 ```{r, echo = FALSE}
-
 knitr::opts_chunk$set(
@@
 ```{r}
-knitr::opts_chunk$set(
-  cache = FALSE,
-  collapse = TRUE,
-  comment = "#>",
-  #fig.dim = c(7, 7),
-  fig.fullwidth = TRUE,
-  fig.show = "hold",
-  echo = FALSE,
-  message = FALSE,
-  warning = FALSE,
-  results = TRUE 
-)
-
 library(drake)
@@
 
-# Results
-
 ## Links betwenn temporal dynamics
-
-```{r}
-loadd(net_dyn_lm)
-loadd(net_dyn_lm_plot)
-```
 
@@
 ```{r}
-loadd(temporal_dynamics_coef)
-loadd(temporal_dynamics_plot)
-loadd(full_data2)
-loadd(biomass_group)
+loadd(p_bm_vs_bm_slope)
+p_bm_vs_bm_slope
 ```
@@
 ```{r}
-temporal_dynamics_coef %>%
-  filter(term %in% "slope", coeff %in% c("bm_std", "log_bm_std")) %>%
-  select(station:estimate) %>%
-  pivot_wider(names_from = "term", values_from = estimate) %>%
-  left_join(biomass_group, by = c("station", "coeff" = "bm_var")) %>%
-  filter(group_type == "median", summary_type %in% c("first_3_year", "median")) %>%
-  ggplot(aes(x = bm, y = slope)) +
-  geom_point(aes(color = group)) +
-  facet_wrap(summary_type~coeff, scales = "free") +
-  labs(x = "Summary of biomass (g)", y = "Slope (g.y^-1)")
+loadd(p_hist_med_bm)
+p_hist_med_bm
 ```
 
-```{r}
-full_data2 %>%
-  group_by(station) %>%
-  summarise(med_bm = median(biomass)) %>%
-  ggplot(aes(x = med_bm)) +
-  geom_histogram() +
-  labs(x = "Median total biomass over time by station (g)")
-```
-
-# Results
+# Methods
 
@@
 
+## The three model
+
+1. $dN = dB + dB \times B + dB^2 + dB^2 \times B$
+
+2. $dN = dB + B + dB \times B + Inc \times B + dB \times Inc \times B$
+
+3. $dN = dB + B + dB \times B + Inc + Inc \times dB + dB \times B \times Inc$
+
+with:
+- $dN$: temporal trend of network structure
+- $dB$: temporal trend of total (log) biomass
+- $B$: total median biomass or total biomass of the first three year
+- $Inc$: Is $dB > 0$?
+
+We kept the second model.
+
+# Results
+
 ```{r, cache = FALSE}
-loadd(log_bm_net_group_f3y, model_log_bm_f3y, summary_log_bm_f3y, vif_log_bm_f3y)
-loadd(bm_net_group_median, bm_vs_net_trends)
-loadd(habitat_press, habitat_pressure)
-loadd(region_polygon, station_analysis)
-loadd(richness_group)
+loadd(log_bm_net_group_f3y, model_log_bm_f3y,
+  summary_log_bm_f3y, vif_log_bm_f3y)
+#loadd(bm_net_group_median, bm_vs_net_trends)
 ```
@@
 ```{r, fig.height = 12, fig.width = 12}
-log_bm_net_group_f3y %>%
-  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
-  geom_point() +
-  scale_color_viridis() +
-  geom_errorbar(aes(xmin = bm_slope - bm_slope_strd_error,
-      xmax = bm_slope + bm_slope_strd_error), alpha = .3) +
-  geom_errorbar(aes(ymin = linear_slope - linear_slope_strd_error,
-      ymax = linear_slope + linear_slope_strd_error), alpha = .3) +
-  facet_wrap(~variable, scales = "free") +
-  labs_log_bm_net_trends()
+loadd(p_pred_quad2_f3y)
+legend_quad2 <- get_legend(p_pred_quad2_f3y[[1]])
+p_pred_quad2_f3y %<>% map(., ~.x + theme(legend.position = "none"))
+top <- plot_grid(
+  plotlist = p_pred_quad2_f3y,
+  labels = names(p_pred_quad2_f3y)
+)
+quad2_plot <- plot_grid(top, legend_quad2, rel_widths = c(1, .1))
 ```
 
-```{r, fig.height = 12, fig.width = 12}
-log_bm_net_group_f3y %>%
-  filter(!is.na(protocol_type)) %>%
-  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
-  geom_point() +
-  scale_color_viridis() +
-  geom_errorbar(aes(xmin = bm_slope - bm_slope_strd_error,
-      xmax = bm_slope + bm_slope_strd_error), alpha = .3) +
-  geom_errorbar(aes(ymin = linear_slope - linear_slope_strd_error,
-      ymax = linear_slope + linear_slope_strd_error), alpha = .3) +
-  facet_grid(variable~protocol_type, scales = "free") +
-  labs_log_bm_net_trends()
+```{r}
+loadd(p_pred_medium_f3y)
+p_pred_medium_f3y %<>% map(., ~.x + theme(legend.position = "none"))
+medium_plot <- plot_grid(plotlist = p_pred_medium_f3y,
+  labels = names(p_pred_medium_f3y))
+```
 
-log_bm_net_group_f3y %>%
-  filter(variable == "connectance") %>%
-  ggplot(aes(x = bm_slope, y = bm)) +
-  geom_point()
-  labs(x = "Biomass trends (log biomass per year)", y = "Biomass")
+```{r, fig.height = 12}
+plot_grid(quad2_plot, medium_plot, nrow = 2, labels = c("poly", "piecereg"))
 ```
+
+Finally, both models does not disagree that much, for the tendancies according
+to the biomass
 
@@
 #https://stackoverflow.com/questions/44457243/regression-tables-in-r-markdown-rmarkdown-html-pdf
-
-model_log_bm_f3y_table <- summary_log_bm_f3y %>%
-  filter(model == "mod_bm_quad2") %>%
+loadd(model_log_bm_f3y_table_medium)
+model_log_bm_f3y_table_medium[["reg_table"]] %>% 
   filter(variable %in% get_com_str_var(all = FALSE)) %>%
-  mutate(
-    reg_table = map(model_obj, broom::tidy),
-    anova_table = map(anova, broom::tidy)
-  )
-
-model_log_bm_f3y_table[["reg_table"]] %>% 
-  bind_rows(.) %>%
-  mutate(variable = rep(model_log_bm_f3y_table[["variable"]], each = 6)) %>%
-  select(variable, everything()) %>%
   kable(.,
@@
       "Regression table for the model: dN =",
-      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
+      "dB + B + dB*B + Inc*B + dB*Inc*B."
     )) %>% 
@@
 ```{r}
-bind_rows(model_log_bm_f3y_table[["anova_table"]]) %>% 
-  mutate(variable = rep(model_log_bm_f3y_table[["variable"]], each = 6)) %>%
-  select(variable, everything()) %>%
+model_log_bm_f3y_table_medium[["anova_table"]] %>% 
+  filter(variable %in% get_com_str_var(all = FALSE)) %>%
   kable(., booktabs = TRUE,
@@
       "ANOVA table for the model: dN =",
-      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
+      "dB + B + dB*B + Inc*B + dB*Inc*B."
     )
-  )
-
+  ) %>%
+  collapse_rows(columns = 1, valign = "top")
 ```
@@
 ```{r}
-map_dfr(model_log_bm_f3y_table[["model_obj"]], broom::glance) %>%
-  mutate(variable = model_log_bm_f3y_table[["variable"]]) %>%
-  select(variable, everything()) %>%
-  kable(., booktabs = TRUE,
-    caption = 
-      paste0(
-      "Model summary for the model: dN =",
-      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
+loadd(pred_plot_signif)
+pred_plot_signif %<>% filter(variable %in% get_com_str_var())
+legend_signif <- get_legend(
+  pred_plot_signif$myplot[[1]] +
+    theme(legend.position = "bottom")
 )
+pred_plot_signif$myplot %<>% map(., ~.x + theme(legend.position = "none"))
+top <- plot_grid(
+  plotlist = pred_plot_signif$myplot,
+  labels = pred_plot_signif$variable
 )
+plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
 ```
-
-#### Quadratic two
-
-```{r, fig.height = 12, fig.width = 12}
-pred_log_bm_quad2 <- summary_log_bm_f3y %>%
-  filter(model == "mod_bm_quad2") %>%
-  mutate(
-    pred = map(model_obj, ~ggpredict(.x,
-	terms = c("bm_slope", "bm [quart2]"))),
-    pred_df = map(pred, as_tibble),
-    plot = map(pred, ~plot(.x, add.data = FALSE)),
-    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
-    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
-  )
-
-pred_log_bm_quad2_plot <- map2(model_log_bm_f3y$data, pred_log_bm_quad2$pred_df,
-  plot_pred_data)
-legend_quad2 <- get_legend(pred_log_bm_quad2_plot[[1]])
-pred_log_bm_quad2_plot %<>% map(., ~.x + theme(legend.position = "none"))
-top <- plot_grid(plotlist = pred_log_bm_quad2_plot, labels = model_log_bm_f3y$variable)
-plot_grid(top, legend_quad2, rel_widths = c(1, .1))
-```
--
 
@@
 ```{r}
-#habitat_press
-```
 
-```{r}
+loadd(habitat_pressure, region_polygon, station_analysis)
+loadd(richness_group)
+loadd(log_bm_net_group_f3y)  
 test <- log_bm_net_group_f3y %>%
@@
 ```{r}
-
 p <- ggplot() +
@@
 ```
+
+```{r}
+loadd(habitat_press)
+hab_press <- habitat_press %>%
+  select(station, long, lat, slope, alt, d_source, strahler, width_river_mean,
+    avg_depth_station_mean, DBO_med, flow_med)
+dyn_press <- log_bm_net_group_f3y %>%
+  filter(variable == "connectance") %>%
+  select(station, bm_slope) %>%
+  left_join(hab_press, by = "station") %>%
+  na.omit
+
+corrplot::corrplot(cor(dyn_press[, -1]))
+```
+
+```{r}
+
+```
+
+## Richness and dynamics
 
@@
 ```
-
-# Methods
-
-## Station grouping
-
-### Rigal station increase / decrease
-
-Les stations ont moins de 40 kilos au départ ont l'air comparable en terme de
-dynamique.
-
-```{r, eval=FALSE}
-loadd(biomass_group)
-
-p_rigal_decrease_increase_slope_st <- 
-  st_decrease_increase_rigal_biomass %>%
-  left_join(biomass_group, by = "station") %>%
-  ggplot(aes(y = linear_slope, x = bm_slope, color = shape_class)) +
-  geom_point() +
-  facet_wrap(~variable)
-p_rigal_decrease_increase_slope_st
-```
-
-### Tendancies in rigal increase / decrease
-
-```{r}
-bm_vs_net_trends %>%
-  ggplot(aes(x = reg_weight)) +
-  geom_histogram() +
-  facet_wrap(~variable)
-
-bm_net_group_median %>%
-  ggplot(aes(x = bm_slope, y = linear_slope, size = reg_weight, weight = reg_weight, color = log(bm))) +
-  geom_point() +
-  scale_color_viridis() +
-  geom_vline(xintercept = 0, color = "red") +
-  geom_smooth() +
-  facet_wrap(~variable, scales = "free_y") +
-  labs(x = "Biomass trend (g.m-1.y-1)", y = "Network trend (U.y-1)")
-
-log_bm_net_group_f3y %>%
-  ggplot(aes(x = bm_slope, y = linear_slope, size = reg_weight, weight = reg_weight, color = log(bm))) +
-  geom_point() +
-  scale_color_viridis() +
-  geom_vline(xintercept = 0, color = "red") +
-  geom_smooth() +
-  facet_wrap(~variable, scales = "free_y") +
-  labs(x = "Log Biomass trend (g.m-1.y-1)", y = "Network trend (U.y-1)")
-```
-
-### With group
-
-#### Median
-
-```{r}
-##Summary of group 
-biomass_group %>%
-  filter(group_type == "median") %>%
-  ggplot(aes(x = bm)) +
-  geom_histogram() +
-  facet_wrap(bm_var~summary_type, scales = "free_x")
-```
-```{r, eval = FALSE}
-group_results <- 
-  rigal_biomass_coeff_dynamics %>%
-  left_join(biomass_group, by = "station") %>% 
-  filter(group_type == "median", bm_var == "bm_std")
-
-p1 <- group_results %>%
-  filter(summary_type == "first_3_year") %>%
-  ggplot(aes(x = linear_slope, y = estimate, color = group,
-      size = reg_weight, weight = reg_weight)) +
-  geom_point() +
-  geom_smooth(method = "lm") +
-  facet_wrap(~coeff, scales = "free_y")
-
-p3 <- group_results  %>%
-  filter(summary_type == "median") %>%
-  ggplot(aes(x = linear_slope, y = estimate, color = group, size = reg_weight, weight = reg_weight)) +
-  geom_point() +
-  geom_smooth(method = "lm") +
-  facet_wrap(~coeff, scales = "free_y")
-
-p1
-p3
-```
-
-#### Little and big rivers
-
-```{r}
-loadd(stream_group)
-#grandes/petites rivières
-stream_group %>%
-  ggplot(aes(x = width_river_mean, fill = group)) +
-  geom_histogram() +
-  facet_grid(~group_type)
-
-stream_group %>%
-  filter(group_type == "median") %>%
-  ggplot(aes(x = width_river_mean, fill = protocol_type)) +
-  geom_histogram()
-
-stream_group %>%
-  filter(group_type == "median") %>%
-  left_join(
-    biomass_group %>%
-    filter(group_type == "median", summary_type == "median") %>%
-    select(-group_type, -summary_type, -group),
-  by = "station"
-  ) %>%
-  filter(!is.na(protocol_type)) %>%
-  ggplot(aes(x = bm, fill = protocol_type)) +
-  geom_histogram() +
-  facet_wrap(~bm_var, scales = "free_x")
-```
-
-# Patterns
-
-```{r}
-bm_net_group_median %>%
-  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm), size = reg_weight, weight = reg_weight)) +
-  geom_point() +
-  scale_color_viridis() +
-  #geom_smooth(method = "lm") +
-  facet_wrap(~variable, scales = "free") +
-  labs(title = "Group as mean biomass")
-
-bm_net_group_median %>%
-  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
-  geom_point() +
-  scale_color_viridis() +
-  geom_errorbar(aes(
-      xmin = bm_slope - bm_slope_strd_error,
-      xmax = bm_slope + bm_slope_strd_error),
-    alpha = .2
-    ) +
-  geom_errorbar(aes(
-      ymin = linear_slope - linear_slope_strd_error,
-      ymax = linear_slope + linear_slope_strd_error),
-    alpha = .2
-    ) +
-  facet_wrap(~variable, scales = "free") +
-  labs(title = "Group as mean biomass")
-
-bm_net_group_median %>%
-  filter(!is.na(protocol_type)) %>%
-  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm), size = reg_weight, weight = reg_weight)) +
-  geom_point() +
-  scale_color_viridis() +
-  #geom_smooth(method = "lm") +
-  facet_grid(variable~protocol_type, scales = "free") +
-  labs(title = "Group as mean biomass")
-```
-
-## Other Statistical model
-
-#### Quadratic one
-
-```{r}
-pred_log_bm_quad <- summary_log_bm_f3y %>%
-  filter(model == "mod_bm_quad") %>%
-  mutate(
-    pred = map(model_obj, ~ggpredict(.x,
-	terms = c("bm_slope", "bm [quart2]"))),
-    pred_df = map(pred, as_tibble),
-    plot = map(pred, ~plot(.x, add.data = FALSE)),
-    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
-    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
-  )
-
-test <- map2(model_log_bm_f3y$data, pred_log_bm_quad$pred_df, plot_pred_data,
-  std_error = TRUE)
-plot_grid(plotlist = test, labels = model_log_bm_f3y$variable)
-```
-
-```{r}
-
-vif_log_bm_f3y %>%
-  ggplot(aes(y= vif, x = term)) +
-  geom_hline(yintercept = 10) +
-  geom_bar(stat = "identity") +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  facet_grid(model_type~variable, scales = "free")
-```
-
-### By protocol
-
-```{r}
-loadd(vif_log_bm_by_protocol)
-
-protocol_vec <- vif_log_bm_by_protocol$protocol_type %>% unique
-p_vif_protocol <- map(protocol_vec, function (x) {
-  vif_log_bm_by_protocol %>%
-    filter(protocol_type == x) %>%
-    ggplot(aes(y= vif, x = term)) +
-    geom_hline(yintercept = 10) +
-    geom_bar(stat = "identity") +
-    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-    labs(title = paste0("Protocol type: ", x)) +
-    facet_grid(model_type~variable, scales = "free_y")
-  })
-p_vif_protocol[[1]]
-p_vif_protocol[[2]]
-```
-
-```{r}
-loadd(model_log_bm_f3y_by_protocol, summary_log_bm_f3y_by_protocol)
-```
-
-```{r, eval = FALSE}
-complete_log_quad2 <- summary_log_bm_f3y_by_protocol %>%
-  filter(model == "mod_bm_quad2", protocol_type == "complete") %>%
-  mutate(
-    reg_table = map(model_obj, broom::tidy),
-    anova_table = map(anova, broom::tidy)
-  )
-
-complete_log_quad2[["reg_table"]] %>% 
-  bind_rows(.) %>%
-  mutate(variable = rep(complete_log_quad2[["variable"]], each = 6)) %>%
-  select(variable, everything()) %>%
-  kable(.,
-    booktabs = TRUE, 
-    caption = 
-      paste0(
-      "Regression table for the model: dN =",
-      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
-    ) 
-  )
-
-complete_log_quad2[["anova_table"]] %>% 
-  bind_rows(.) %>%
-  mutate(variable = rep(complete_log_quad2[["variable"]], each = 6)) %>%
-  select(variable, everything()) %>%
-  kable(., booktabs = TRUE,
-    caption = 
-      paste0(
-      "ANOVA table for the model: dN =",
-      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
-    )
-  )
-```
-
-```{r, eval = FALSE}
-filter(summary_log_bm_f3y_by_protocol, model == "mod_log_bm_inc")[["resume"]]
-filter(summary_log_bm_f3y_by_protocol, model == "mod_log_bm_inc")[["anova"]]
-
-filter(summary_log_bm_f3y_by_protocol, model == "mod_bm_quad")[["resume"]]
-filter(summary_log_bm_f3y_by_protocol, model == "mod_log_bm_inc")[["anova"]]
-```
-
-#### Quadratic two
-
-```{r}
-pred_log_bm_quad2 <- summary_log_bm_f3y_by_protocol %>%
-  filter(model == "mod_bm_quad2", protocol_type == "complete") %>%
-  mutate(
-    pred = map(model_obj, ~ggpredict(.x,
-	terms = c("bm_slope", "bm [quart2]"))),
-    pred_df = map(pred, as_tibble),
-    plot = map(pred, ~plot(.x, add.data = FALSE)),
-    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
-    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
-  )
-model_log_bm_f3y_by_protocol %<>% filter(protocol_type == "complete")
-
-pred_log_bm_quad2_plot <- map2(model_log_bm_f3y_by_protocol$data, pred_log_bm_quad2$pred_df,
-  plot_pred_data)
-plot_grid(plotlist = pred_log_bm_quad2_plot, labels = model_log_bm_f3y$variable)
-```
-
-#### Quadratic one
-
-```{r}
-pred_log_bm_quad <- summary_log_bm_f3y_by_protocol %>%
-  filter(model == "mod_bm_quad", protocol_type == "complete") %>%
-  mutate(
-    pred = map(model_obj, ~ggpredict(.x,
-	terms = c("bm_slope", "bm [quart2]"))),
-    pred_df = map(pred, as_tibble),
-    plot = map(pred, ~plot(.x, add.data = FALSE)),
-    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
-    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
-  )
-model_log_bm_f3y_by_protocol %<>% filter(protocol_type == "complete")
-
-pred_log_bm_quad_plot <- map2(model_log_bm_f3y$data, pred_log_bm_quad$pred_df, plot_pred_data,
-  std_error = TRUE)
-plot_grid(plotlist = pred_log_bm_quad_plot, labels = model_log_bm_f3y$variable)
-```
-
-```{r, eval = FALSE}
-pred <- summary_log_bm_f3y_by_protocol %>%
-  filter(model == "mod_log_bm_inc") %>%
-  mutate(
-    pred = map(model_obj, ~ggpredict(.x,
-	terms = c("bm_slope", "log_bm [quart2]", "inc_f"))),
-    pred_df = map(pred, as_tibble),
-    plot = map(pred, ~plot(.x, add.data = FALSE)),
-    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
-  )
-plot_grid(plotlist = pred$plot, labels = pred$variable)
-```
-
-```{r, eval = FALSE}
-pred <- summary_log_bm_f3y_by_protocol %>%
-  filter(model == "mod_log_bm_inc") %>%
-  mutate(
-    pred = map(model_obj, ~ggpredict(.x,
-	terms = c("bm_slope", "log_bm [quart2]", "inc_f"))),
-    pred_df = map(pred, as_tibble),
-    plot = map(pred, ~plot(.x, add.data = FALSE)),
-    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
-  )
-plot_grid(plotlist = pred$plot, labels = pred$variable)
-```
-
-### Can we predict the model without all simple effects?
-
-```{r, eval = FALSE}
-# Perform a valid model 
-pred <- model_int %>%
-  select(-data, -mod4) %>%
-  pivot_longer(cols = c(mod1:mod5), names_to = "model_type", values_to =
-    "mod_obj") %>%
-  mutate(
-    pred_ref = map2(mod_obj, model_type, function (x, y) {
-       if (y %in% c("mod3", "mod5"))
-	 terms_spec <- c("bm_slope", "inc_f", "bm")
-       else
-	 terms_spec <- c("bm_slope", "inc_f", "bm_group") 
-      ggpredict(x, terms = terms_spec)
-      }
-    ),
-    pred_cte = map2(mod_obj, model_type, function (x, y) {
-       if (y %in% c("mod3", "mod5"))
-	 terms_spec <- c("linear_slope", "inc_f", "bm")
-       else
-	 terms_spec <- c("linear_slope", "inc_f", "bm_group") 
-      ggeffect(x, terms = terms_spec)
-      }
-    )
-  )
-
-pred %<>%
-  mutate(
-  plot_pred_ref = map(pred_ref, plot, add.data = TRUE),
-  plot_pred_cte = map(pred_cte, plot, add.data = TRUE)
-  )
-pred_richness <- pred %>%
-  filter(variable == "richness", model_type == "mod3")
-
-pred$plot_pred_ref[[1]]
-pred$plot_pred_cte[[1]]
-pred$plot_pred[[2]]
-pred$plot_pred[[3]]
-pred$plot_pred_ref[[4]]
-```
-
-```{r, eval = FALSE}
-library(ggeffects)
-mydf <- ggpredict(model_int$mod3[[1]], terms = c("linear_slope", "inc_f",
-    "bm"))
-plot(mydf, add.data = TRUE)
-
-```
-
-```{r, eval = FALSE}
-model_log %<>%
-  mutate(
-    pred5 = map(mod3, ~ggpredict(.x,
-	terms = c("linear_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2, 3, 4, 6]", "inc_f", "bm"))),
-    pred5_df = map(pred5, as_tibble),
-    plot = map(pred5, ~plot(.x, add.data = TRUE)),
-    myplot = map2(pred5, data, ~plot_final_model(ggpred = .x, rawdata = .y))
-  )
-
-#plot_final_model(model_int$pred5[[1]], model_int$data[[1]])
-plot_grid(plotlist = model_int$plot, labels = model_int$variable)
-model_int$plot[[1]]
-summary(model_int$mod3[[1]])
-test <- model_int$data[[1]]
-model_int$pred5_df[[1]]
-test %>%
-  ggplot(aes(x = bm_slope, y = linear_slope, weight = reg_weight, size = reg_weight)) +
-  geom_smooth(method = "lm") +
-  geom_point()
-
-pred_test <-
-  model_int$pred5_df[[1]] %>%
-  as_tibble %>%
-  rename(increasing = group, group = facet) %>%
-  filter(increasing == FALSE & x < 0 | increasing == TRUE & x > 0)
-
-p <- ggplot(pred_test, aes(x = x , y = predicted, color = group)) +
-  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group), alpha =
-    .1) +
-  geom_line() +
-  geom_point(data = rename(test,
-      predicted = linear_slope, x = bm_slope),
-    aes(x = x, y = predicted),
-    inherit.aes = FALSE)
-```
-
-```{r, eval = FALSE}
-model_int$pred5_df[[1]] %>%
-  ggplot()
-
-plot_final_model(model_int$pred5[[1]], rawdata = model_int$data[[1]], facet =
-  TRUE)
-```
-
-# Correlation
-
-```{r}
-cor_bm_net <- bm_net_group_median %>%
-  select(bm_slope, variable, linear_slope, bm, width_river_mean) %>%
-  pivot_wider(names_from = variable, values_from = linear_slope) 
-corrplot::corrplot(cor(na.omit(cor_bm_net)), type = "upper")
-
-library(ade4)
-library(factoextra)
-res.pca <- dudi.pca(na.omit(cor_bm_net),
-                    scannf = FALSE,   # Cacher le scree plot
-                    nf = 3            # Nombre d'axes gardés
-                    )
-screeplot(res.pca, main = "Screeplot - Eigenvalues")
-p1 <- fviz_pca_var(res.pca,
-  col.var = "contrib", 
-  gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
-  repel = TRUE     
-)
-p2 <- fviz_pca_var(res.pca,
-  axes = c(1, 3),
-  col.var = "contrib", 
-  gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
-  repel = TRUE     
-)
-
-p3 <- fviz_pca_var(res.pca,
-  axes = c(2, 3),
-  col.var = "contrib", 
-  gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
-  repel = TRUE     
-)
-plot_grid(p1, p2, p3)
-```
-
-## Richness
-
-```{r}
-knitr::opts_chunk$set(
-  eval = FALSE 
-)
-```
-
-```{r}
-st_big_bm_tendancies <- group_results %>%
-  filter(abs(linear_slope) > 5000) %>%
-  .$station %>%
-  unique
-plot_big_bm_tendancies <- temporal_dynamics_plot %>%
-  filter(variable == "biomass", station %in% st_big_bm_tendancies) %>%
-  .$plot
-plot_grid(
-  plotlist = map(plot_big_bm_tendancies, 
-    ~.x + lims(x = c(0, 10), y = c(0, 155000)))
-)
-```
-
-```{r}
-rigal_shape_var <- rigal_classification %>%
-  unnest(classif) %>%
-  select(station, variable, shape_class) %>%
-  mutate(station = as.character(station))
-
-rigal_shape_var %>%
-  filter(station %in% st_decrease_increase_rigal_biomass$station) %>%
-  ggplot(aes(x = shape_class)) +
-  geom_bar() +
-  facet_wrap(~ variable) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-```
-
-## SAX
-
-```{r, eval = FALSE}
-library(jmotif)
-loadd(full_data2)
-sax_all_variable <- full_data2 %>%
-  select(station, nb_year, biomass:log_bm) %>%
-  pivot_longer(cols = biomass:log_bm, names_to = "variable", values_to = "value") %>%
-  group_by(station, variable) %>%
-  arrange(nb_year) %>%
-  nest() %>%
-  mutate(
-    zts = map(data, function(x) znorm(x$value, threshold = 0.01)),
-    paa = map(zts, ~paa(., 3)),
-    sax = map_chr(paa, ~series_to_string(., 3))
-  ) %>%
-  ungroup()
-
-# CBA:
-sax_all_variable %>%
-  filter(station %in% cba_rigal_sax$station, !variable %in% c("biomass", "nbnode")) %>%
-  ggplot(aes(x = sax)) +
-  geom_bar() +
-  facet_wrap(facets = ~variable)
-
-sax_all_variable %>%
-  filter(
-    station %in% cba_rigal_sax$station,
-    !variable %in% c("biomass", "nbnode")
-    ) %>%
-  ggplot(aes(x = sax)) +
-  geom_bar() +
-  facet_wrap(facets = ~variable)
-```

### 2020-11-30 R/statistical_model.R

@@ -198,7 +198,6 @@ get_mod_pred <- function (summary_mod = NULL) {
     )
 }
 
-
 pval2lgl <- function (x = NULL, thld = 0.05) {
 
   x <- ifelse(x <= thld, TRUE, FALSE)

### 2020-12-01 temporal_dynamics.Rmd
functions to generate plot of the report

---
title: "Temporal dynamics"
author: "Alain Danet"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
    math: katex
---

```{r}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE 
)

library(drake)
library(tidyverse)
library(magrittr)
library(cowplot)
library(viridis)
source("R/misc.R") # Define your custom code as a bunch of functions.
source_dir(get_mypath("R")) # Define your custom code as a bunch of functions.

#theme_set(theme_cowplot())
```

```{r}
loadd(rigal_classification, full_data2, temporal_dynamics_plot)
```

```{r}
myload(biomass_ts_sax, envir = globalenv(),dir = get_mypath("data"))

biomass_classif_rigal <- rigal_classification %>%
  filter(variable %in% c("bm_std", "log_bm_std")) %>%
  unnest(classif) %>%
  mutate(station = as.character(station)) %>%
  select(station, variable,shape_class)

p_biomass_classif_rigal <- biomass_classif_rigal %>%
  ggplot(aes(x = shape_class)) +
  geom_bar() +
  facet_wrap(~variable) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

# Temporal dynamics

```{r}
p_cap <- paste0(
  "Temporal dynamics of biomass and temporal dynamics of
  metrics for 10 randomly selected communities."
)
```

```{r p-tmp-dyn, cache = TRUE, eval = FALSE}

p <- vector(mode = "list", length = 10)
for (i in seq_len(length(p))) {
  to_plot <- temporal_dynamics_plot %>% 
    filter(station == sample(temporal_dynamics_plot$station, 1))
  p[[i]] <- cowplot::plot_grid(plotlist = to_plot$plot, labels = to_plot$station)
}
p
```

## Temporal dynamics decrease/increase constant

### Log biomass

```{r, cache = TRUE, fig.height = 45}
st_decrease_increase_rigal <- biomass_classif_rigal %>%
  filter(variable == "log_bm_std") %>%
  filter(shape_class %in% c("increase_constant", "decrease_constant"))
data_decrease_increase <- full_data2 %>%
  filter(station %in% st_decrease_increase_rigal$station)

log_bm_min_max <- map_dbl(c(min, max),
  ~.x(data_decrease_increase$log_bm_std, na.rm = TRUE))
nb_year_min_max <- map_dbl(c(min, max),
  ~.x(data_decrease_increase$nb_year, na.rm = TRUE))
temporal_dynamics_plot$plot %<>%
  map(., ~ .x + lims(y = log_bm_min_max, x = nb_year_min_max))

temporal_dynamics_plot %>%
  filter(variable == "log_bm_std", station %in% st_decrease_increase_rigal$station) %>%
  plot_grid(plotlist = .$plot, ncol = 3, labels = st_decrease_increase_rigal$station)
```

### Raw Biomass

```{r, cache = TRUE, fig.height = 45}
st_decrease_increase_rigal_biomass <- rigal_classification %>%
  filter(variable == "bm_std") %>%
  unnest(classif) %>%
  filter(shape_class %in% c("increase_constant", "decrease_constant"))

bm_min_max <- map_dbl(
  c(min, max),
  ~.x(data_decrease_increase$bm_std, na.rm = TRUE))
nb_year_min_max <- map_dbl(
  c(min, max),
  ~.x(data_decrease_increase$nb_year, na.rm = TRUE))
temporal_dynamics_plot[temporal_dynamics_plot$variable == "bm_std",]$plot %<>%
  map(., ~ .x + lims(y = bm_min_max, x = nb_year_min_max))

temporal_dynamics_plot %>%
  filter(variable == "bm_std", station %in% st_decrease_increase_rigal_biomass$station) %>%
  plot_grid(plotlist = .$plot, ncol = 3, labels = st_decrease_increase_rigal_biomass$station)
```

### Richness

```{r, cache = TRUE, fig.height = 45}
var_tmp <- "rich_std"
st_decrease_increase_rigal <- rigal_classification %>%
  filter(variable == var_tmp) %>%
  unnest(classif) %>%
  filter(shape_class %in% c("increase_constant", "decrease_constant"))

min_max <- map_dbl(
  c(min, max),
  ~.x(data_decrease_increase[[var_tmp]], na.rm = TRUE))
nb_year_min_max <- map_dbl(
  c(min, max),
  ~.x(data_decrease_increase$nb_year, na.rm = TRUE))
temporal_dynamics_plot[temporal_dynamics_plot$variable == var_tmp,]$plot %<>%
  map(., ~ .x + lims(y = min_max, x = nb_year_min_max))

temporal_dynamics_plot %>%
  filter(variable == var_tmp, station %in% st_decrease_increase_rigal$station) %>%
  plot_grid(plotlist = .$plot, ncol = 3, labels = st_decrease_increase_rigal$station)
```

### Number of nodes

```{r, cache = TRUE, fig.height = 45}
var_tmp <- "nbnode_std"
st_decrease_increase_rigal <- rigal_classification %>%
  filter(variable == var_tmp) %>%
  unnest(classif) %>%
  filter(shape_class %in% c("increase_constant", "decrease_constant"))

min_max <- map_dbl(
  c(min, max),
  ~.x(data_decrease_increase[[var_tmp]], na.rm = TRUE))
nb_year_min_max <- map_dbl(
  c(min, max),
  ~.x(data_decrease_increase$nb_year, na.rm = TRUE))
temporal_dynamics_plot[temporal_dynamics_plot$variable == var_tmp,]$plot %<>%
  map(., ~ .x + lims(y = min_max, x = nb_year_min_max))

temporal_dynamics_plot %>%
  filter(variable == var_tmp, station %in% st_decrease_increase_rigal$station) %>%
  plot_grid(plotlist = .$plot, ncol = 3, labels = st_decrease_increase_rigal$station)
```

### 2020-12-01 R/report_plot.R

@@ -1,0 +1,105 @@
+plot_bm_vs_bm_slope <- function (tps_dyn_coef = NULL, bm_group = NULL) {
+
+  tps_dyn_coef %>%
+    filter(term %in% "slope", coeff %in% c("bm_std", "log_bm_std")) %>%
+    select(station:estimate) %>%
+    pivot_wider(names_from = "term", values_from = estimate) %>%
+    left_join(bm_group, by = c("station", "coeff" = "bm_var")) %>%
+    filter(group_type == "median", summary_type %in% c("first_3_year", "median")) %>%
+    ggplot(aes(x = bm, y = slope)) +
+    geom_point(aes(color = group)) +
+    facet_wrap(summary_type~coeff, scales = "free") +
+    labs(x = "Summary of biomass (g)", y = "Slope (g.y^-1)")
+
+}
+
+plot_hist_med_bm <- function(.data = full_data2) {
+
+  .data %>%
+    group_by(station) %>%
+    summarise(med_bm = median(biomass)) %>%
+    ggplot(aes(x = med_bm)) +
+    geom_histogram() +
+    labs(x = "Median total biomass over time by station (g)")
+}
+
+get_pred_model <- function (
+  summary_model = NULL,
+  model_data = NULL,
+  model_name = NULL,
+  term = NULL,
+  selected_variable = get_com_str_var()
+  ) {
+
+  stopifnot(model_name %in% c("mod_bm_quad2", "mod_medium_bm"))
+
+  if (is.null(term)) {
+    if (model_name == "mod_bm_quad2") {
+      term <- c("bm_slope", "bm [quart2]")
+    }
+    if (model_name == "mod_medium_bm") {
+      term <- c("bm_slope [-0.2,-0.00001,0.00001,.2]", "inc_f", "bm [quart2]")
+    }
+    stopifnot(!is.null(term))
+  }
+
+  pred <- summary_model %>%
+    filter(model == model_name, variable %in% selected_variable) %>%
+    mutate(
+      pred = map(model_obj, ~ggpredict(.x, terms = term)),
+      pred_df = map(pred, as_tibble)
+    )
+
+  model_data %<>% filter(variable %in% selected_variable)
+
+  if (model_name == "mod_medium_bm") {
+    pred_plot <- map2(model_data$data, pred$pred_df,
+      ~plot_final_model(ggpred = .y, rawdata = .x))
+  } else if (model_name == "mod_bm_quad2") {
+    pred_plot <- map2(model_data$data, pred$pred_df,
[…]

### 2020-12-04 report.Rmd
Finalise report

@@
 output:
-  prettydoc::html_pretty:
-    theme: cayman
-    highlight: github
-    math: katex
+  html_document
 ---
@@
 
+#### All protocol
+
+```{r, eval = TRUE}
+#https://stackoverflow.com/questions/44457243/regression-tables-in-r-markdown-rmarkdown-html-pdf
+loadd(model_log_bm_f3y_table_medium)
+model_log_bm_f3y_table_medium[["reg_table"]] %>% 
+  filter(variable %in% get_com_str_var(all = FALSE)) %>%
+  kable(.,
+    booktabs = TRUE, 
+    caption = 
+      paste0(
+      "Regression table for the model: dN =",
+      "dB + B + dB*B + Inc*B + dB*Inc*B."
+    )) %>% 
+  kable_styling(latex_options =c("scale_down", "stripped")) %>%
+  collapse_rows(columns = 1, valign = "top")
+```
+
+```{r}
+model_log_bm_f3y_table_medium[["anova_table"]] %>% 
+  filter(variable %in% get_com_str_var(all = FALSE)) %>%
+  kable(., booktabs = TRUE,
+    caption = 
+      paste0(
+      "ANOVA table for the model: dN =",
+      "dB + B + dB*B + Inc*B + dB*Inc*B."
+    )
+  ) %>%
+  kable_styling(latex_options =c("scale_down", "stripped")) %>%
+  collapse_rows(columns = 1, valign = "top")
+```
+
+### Summary
+
+- Lien entre dynamique du réseau et de biomasse signicatif pour tous sauf la
+  connectance.
+  - Pour la connectance, le lien est dépendant de la biomasse
+- Effect of dis/assembly for connectance, avg trophic level, weighted
+  connectance
+- La dynamique du réseau n'est pas affecté par la biomasse de la
+  communauté (effet biomasse non significatif)
+- Il y a un effet biomasse qui est dépendant de dis/assembly.
+
+- Species richness:
+  - decreases a lot in time when biomass decreases
+  - increases slightly in time when biomass increases
+
+- Avg trophic level:
+  - decreases simultaneously with biomass decreases 
+  - increase simultaneously with biomass increases but increases less for bigger
+    communities
+  - meaning that biomass loss and gain are located in the highest trophic level
+    (except gain of biomass in biggest communities)
+
+### Interpretation
+
+- Richness:
+  - when biomass increases, competitive interactions may prevent the increase in
+    species richness.
+  - when biomass decreases conjointly to species richness, it may reflect...
+    haaaa: difficult because we do not know if the chicken or the egg was first.
+  - Implication for conservation: looks easiest to loose species than gain them.
+
+- Avg trophic level: 
+  - Higest trophic level concentrates most of the biomass, so gain and loss are
+    statistically more linked to them
+
+```{r}
+loadd(pred_plot_signif)
+pred_plot_signif_com <- pred_plot_signif %>%
+  filter(variable %in% get_com_str_var())
+legend_signif <- get_legend(
+  pred_plot_signif_com$myplot[[1]] +
+    theme(legend.position = "bottom")
+)
+pred_plot_signif_com$myplot %<>% map(., ~.x + theme(legend.position = "none"))
+top <- plot_grid(
+  plotlist = pred_plot_signif_com$myplot,
+  labels = pred_plot_signif_com$variable
+)
+plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
+```
+
+## Other variables
+
+```{r}
+model_log_bm_f3y_table_medium[["anova_table"]] %>% 
+  filter(!variable %in% get_com_str_var(all = FALSE)) %>%
+  kable(., booktabs = TRUE,
+    caption = 
+      paste0(
+      "ANOVA table for the model: dN =",
+      "dB + B + dB*B + Inc*B + dB*Inc*B."
+    )
+  ) %>%
+  kable_styling(latex_options =c("scale_down", "stripped")) %>%
+  collapse_rows(columns = 1, valign = "top")
+
+```
+
+```{r pred-other-com}
+plot_signif <- pred_plot_signif %>%
+  filter(!variable %in% get_com_str_var())
+legend_signif <- get_legend(
+  plot_signif$myplot[[1]] +
+    theme(legend.position = "bottom")
+)
+plot_signif$myplot %<>% map(., ~.x + theme(legend.position = "none"))
+top <- plot_grid(
+  plotlist = plot_signif$myplot,
+  labels = plot_signif$variable
+)
+plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
+```
+
+```{r}
+pred_plot_signif %>%
+  select(variable, data) %>%
+  unnest(data) %>%
+  ggplot() %>%
+  geom_errorbar(aes(xmin = bm_slope - bm_slope_strd_error, xmax = bm_slope +
+      bm_slope_strd_error), alpha = .3) +
+  geom_errorbar(aes(ymin = linear_slope - linear_slope_strd_error,
+      ymax = linear_slope + linear_slope_strd_error), alpha = .3)
+  }
+  ggplot()
+plot_final_model
+```
+
+## Link biomass dynamic and environment
+
+```{r}
+loadd(habitat_pressure, region_polygon, station_analysis)
+loadd(richness_group)
+loadd(log_bm_net_group_f3y)  
+test <- log_bm_net_group_f3y %>%
+  filter(variable == "connectance") %>%
+  left_join(habitat_pressure, by = "station")
+test %>%
+  pivot_longer(
+    cols = c(bm, width_river_mean, temperature_med, alt , RC1, RC2),
+    names_to = "evt_var", values_to = "value") %>%
+  ggplot(aes(y = bm_slope, x = value)) +
+  geom_smooth(method = "lm") +
+  geom_point() +
+  facet_wrap(~evt_var, scales = "free_x")
+```
+
+```{r}
+p <- ggplot() +
+  geom_sf(data = st_geometry(region_polygon)) 
+st_bm_slope <- station_analysis %>%
+  rename(station = id) %>%
+  left_join(select(test, station, bm_slope)) %>%
+  filter(!is.na(bm_slope)) %>%
+  mutate(trend = ifelse(bm_slope < 0, "negative", "positive"))
+p_col_bm_slope <- p + 
+  geom_sf(data = st_bm_slope, aes(color = bm_slope)) +
+  scale_color_viridis()
+p_trend_bm_trend <- p +
+  geom_sf(data = st_bm_slope, aes(color = trend))
+plot_grid(p_col_bm_slope, p_trend_bm_trend, nrow = 1)
+```
+
+```{r}
+loadd(habitat_press)
+hab_press <- habitat_press %>%
+  select(station, long, lat, slope, alt, d_source, strahler, width_river_mean,
+    avg_depth_station_mean, DBO_med, flow_med)
+dyn_press <- log_bm_net_group_f3y %>%
+  filter(variable == "connectance") %>%
+  select(station, bm_slope) %>%
+  left_join(hab_press, by = "station") %>%
+  na.omit
+corrplot::corrplot(cor(dyn_press[, -1], method = "spearman"))
+```
+
+## Richness and dynamics
+
+```{r}
+log_bm_net_group_f3y %>%
+  filter(variable == "rich_std", bm_slope < 0) %>%
+  left_join(habitat_pressure, by = "station") %>%
+  pivot_longer(cols = c(bm, width_river_mean, temperature_med, alt , RC1, RC2),
+    names_to = "evt_var", values_to = "value") %>%
+ggplot(aes(y = linear_slope, x = value)) +
+geom_smooth(method = "lm") +
+geom_point() +
+facet_wrap(~evt_var, scales = "free_x")
+```
+
+```{r}
+rich_std_f3y <- richness_group %>% 
+  filter(rich_var == "rich_std", summary_type == "first_3_year", group_type ==
+    "median") %>%
+  select(station, rich)
+
+log_bm_net_group_f3y %>%
+  filter(variable == "rich_std") %>%
+  left_join(rich_std_f3y, by = "station") %>%
+  ggplot(aes(y = linear_slope, x = rich)) +
+  geom_smooth(method = "lm") +
+  labs( x = "Species richness (by m2)",
+    y = "Species richness trend") +
+  geom_point()
+```
+
+##
+
+## The two models
+
 ```{r, fig.height = 12, fig.width = 12}
@@
 Finally, both models does not disagree that much, for the tendancies according
-to the biomass
-
-#### All protocol
-
-```{r, eval = TRUE}
-#https://stackoverflow.com/questions/44457243/regression-tables-in-r-markdown-rmarkdown-html-pdf
-loadd(model_log_bm_f3y_table_medium)
-model_log_bm_f3y_table_medium[["reg_table"]] %>% 
-  filter(variable %in% get_com_str_var(all = FALSE)) %>%
-  kable(.,
-    booktabs = TRUE, 
-    caption = 
-      paste0(
-      "Regression table for the model: dN =",
-      "dB + B + dB*B + Inc*B + dB*Inc*B."
-    )) %>% 
-  kable_styling(latex_options =c("scale_down")) %>%
-  #add_header_above(c(" " = 3, "Indirect effects via" = 5)) %>%
-  #column_spec(1:2, width = "3cm") %>%
-  collapse_rows(columns = 1, valign = "top")
-```
+to the biomass.
 
 ```{r}
-model_log_bm_f3y_table_medium[["anova_table"]] %>% 
-  filter(variable %in% get_com_str_var(all = FALSE)) %>%
-  kable(., booktabs = TRUE,
-    caption = 
-      paste0(
-      "ANOVA table for the model: dN =",
-      "dB + B + dB*B + Inc*B + dB*Inc*B."
-    )
-  ) %>%
-  collapse_rows(columns = 1, valign = "top")
+loadd(log_bm_net_group_f3y, model_log_bm_f3y,
+  summary_log_bm_f3y, vif_log_bm_f3y)
+loadd(vif_log_bm)
 ```
-
-```{r}
-loadd(pred_plot_signif)
-pred_plot_signif %<>% filter(variable %in% get_com_str_var())
-legend_signif <- get_legend(
-  pred_plot_signif$myplot[[1]] +
-    theme(legend.position = "bottom")
-)
-pred_plot_signif$myplot %<>% map(., ~.x + theme(legend.position = "none"))
-top <- plot_grid(
-  plotlist = pred_plot_signif$myplot,
-  labels = pred_plot_signif$variable
-)
-plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
-```
-
-## Link biomass dynamic and environment
-
-```{r}
-
-loadd(habitat_pressure, region_polygon, station_analysis)
-loadd(richness_group)
-loadd(log_bm_net_group_f3y)  
-test <- log_bm_net_group_f3y %>%
-  filter(variable == "connectance") %>%
-  left_join(habitat_pressure, by = "station")
-test %>%
-  pivot_longer(
-    cols = c(bm, width_river_mean, temperature_med, alt , RC1, RC2),
-    names_to = "evt_var", values_to = "value") %>%
-ggplot(aes(y = bm_slope, x = value)) +
-geom_point() +
-facet_wrap(~evt_var, scales = "free_x")
-```
-
-```{r}
-p <- ggplot() +
-  geom_sf(data = st_geometry(region_polygon)) 
-st_bm_slope <- station_analysis %>%
-  rename(station = id) %>%
-  left_join(select(test, station, bm_slope)) %>%
-  filter(!is.na(bm_slope))
-p + 
-  geom_sf(data = st_bm_slope, aes(color = bm_slope)) +
-  scale_color_viridis()
-```
-
-```{r}
-loadd(habitat_press)
-hab_press <- habitat_press %>%
-  select(station, long, lat, slope, alt, d_source, strahler, width_river_mean,
-    avg_depth_station_mean, DBO_med, flow_med)
-dyn_press <- log_bm_net_group_f3y %>%
-  filter(variable == "connectance") %>%
-  select(station, bm_slope) %>%
-  left_join(hab_press, by = "station") %>%
-  na.omit
-
-corrplot::corrplot(cor(dyn_press[, -1]))
-```
-
-```{r}
-
-```
-
-## Richness and dynamics
-
-```{r}
-log_bm_net_group_f3y %>%
-  filter(variable == "rich_std", bm_slope < 0) %>%
-  left_join(habitat_pressure, by = "station") %>%
-  pivot_longer(cols = c(bm, width_river_mean, temperature_med, alt , RC1, RC2),
-    names_to = "evt_var", values_to = "value") %>%
-ggplot(aes(y = linear_slope, x = value)) +
-geom_point() +
-facet_wrap(~evt_var, scales = "free_x")
-```
-
-```{r}
-rich_std_f3y <- richness_group %>% 
-  filter(rich_var == "rich_std", summary_type == "first_3_year", group_type ==
-    "median") %>%
-  select(station, rich)
-
-log_bm_net_group_f3y %>%
-  filter(variable == "rich_std", bm_slope < 0) %>%
-  left_join(rich_std_f3y, by = "station") %>%
-  ggplot(aes(y = linear_slope, x = rich)) +
-  geom_point()
-```

### 2020-12-23 report.Rmd
Compute l, ld, gini, fish-fish network, temporal network, species trends

@@
   - increases slightly in time when biomass increases
+  - No effect of community size! (same for the number of nodes)
 
@@
 
+- Connectance:
+  - do not decrease when biomass decreases in little communities
+  - decreases when biomass decreases in big communities
+  - do not vary when biomass increases
+
+- Weighted connectance:
+  - increases when biomass decreases in little communities
+  - decreases when biomass decreases in big communities
+  - decreases when biomass increases
+
 ### Interpretation
@@
 - Richness:
-  - when biomass increases, competitive interactions may prevent the increase in
-    species richness.
-  - when biomass decreases conjointly to species richness, it may reflect...
-    haaaa: difficult because we do not know if the chicken or the egg was first.
-  - Implication for conservation: looks easiest to loose species than gain them.
+  - When biomass increases, one can that species richness increases as well
+    as when biomass decreases conjointly to species richness.
+  - Increase in species richness necessitates colonization events, i.e.
+    stochastic events while decreases in species richness necessitates
+    disparition of species already in the community. Thus, the colonization
+    process
+  - second explanation: when biomass increases, competitive interactions may prevent the increase in
+    species richness. We expect that processes based on competition would raise
+    the role of community size.
 
@@
     statistically more linked to them
+  - In biggest communities, there was no link between biomass and avg trophic
+    level dyn because those communities already contain high trophic
+    levels (There is a positive correlation between the number of pisc node and
+    biomass of the community). So, there is a saturation at the top of the
+    chain.
+    - The observation that the number of link and link density follow the same
+      pattern confirm this interpretation.
+
+- Connectance:
+  - In little communities, few piscivorous species and so loss of biomass do not
+    change the foodwebs because fish-resource links are quite redondant.
+    - there is a positive correlation between nb of pisc node and biomass.
+    - In bigger communities, the loss of the highest piscivorous nodes/species
+      (see average trophic level), which have a lot of interactions, leads to a
+      decrease of connectance over time.
+  - Increase in biomass was weakly related to an increase in node number or species
+    richness, so it is not surprising that connectance to not vary.
+
+- Weighted connectance:
+  - When biomass decreases in little communities, loss of highest trophic level
+    and so less big predators and weighted connectance become more even
+    - In big communities, the highest number can make the absence of such an effect 
+  - When Biomass increases, the number of predator nodes increases (especially
+    in little communities), and ...
+    the biomass
+
+The key to understand the difference between little and big communities is the
+number of piscivorous nodes.
 
@@
 plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
+```
+
+### Further analysis
+
+```{r}
+loadd(summary_var_f3y)
+
+summary_var_f3y %>%
+  na.omit() %>%
+  select(bm_std, avg_IS, l, ld, m, A, gini, log_bm_std, connectance, log_rich_std, rich_std, w_trph_lvl_avg,
+    weighted_connectance, nbnode_std, nb_pisc_node_std, prop_pisc_node) %>%
+  cor() %>%
+  corrplot::corrplot(corr = .)
+
+summary_var_f3y %>%
+  ggplot(aes(x = bm_std, y = prop_pisc_node)) +
+  geom_point() 
+#summary_var_f3y %>%
+  #ggplot(aes(x = log_bm_std, y = nb_pisc_node_std))+
+  #geom_point() 
+#summary_var_f3y %>%
+  #ggplot(aes(x = , y = nb_pisc_node_std))+
+  #geom_point() 
 ```
@@
 
-```{r pred-other-com}
+```{r pred-other-com, fig.dim = c(12, 10)}
 plot_signif <- pred_plot_signif %>%
@@
 plot_signif$myplot %<>% map(., ~.x + theme(legend.position = "none"))
-top <- plot_grid(
+top_signif_other <- plot_grid(
   plotlist = plot_signif$myplot,
@@
 )
-plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
+plot_grid(top_signif_other, legend_signif, nrow = 2, rel_heights = c(1, .1))
+```
+
+```{r eval = FALSE}
+pred_plot_signif %>%
+  select(variable, data) %>%
+  unnest(data) %>%
+  ggplot(aes(x = bm_slope, y = linear_slope, color = bm)) +
+  geom_errorbar(
+    aes(xmin = bm_slope - bm_slope_strd_error, xmax = bm_slope +
+      bm_slope_strd_error), alpha = .3) +
+  geom_errorbar(
+    aes(ymin = linear_slope - linear_slope_strd_error,
+      ymax = linear_slope + linear_slope_strd_error),
+    alpha = .3)
+```
+
+##
+
+```{r}
+loadd(log_bm_net_group_f3y)
+st_id_plot <- log_bm_net_group_f3y %>%
+  filter(variable %in% get_com_str_var()) %>%
+  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
+  scale_color_viridis() +
+  geom_text(aes(label = station)) +
+  facet_wrap(~variable, scales = "free_y")
+st_id_plot
+st_network_to_plot <- c(513, 1453, 16654, 6020)
+```
+
+- Station ploted: `r st_network_to_plot`
+
+```{r}
+library(tidygraph)
+library(ggraph)
+#source(mypath("R", "plot_methods.R"))
+myload(network_analysis,
+  envir = environment(),
+  dir = get_mypath("data", "classes"))
+myload(op_analysis,
+  metaweb_analysis,
+  envir = environment(),
+  dir = get_mypath("data"))
+meta <- metaweb_analysis; rm(metaweb_analysis)
+st_sp_node <- network_analysis %>%
+  select(opcod, composition) %>%
+  left_join(dplyr::select(op_analysis, opcod, station, date), by = "opcod") %>%
+  unnest(cols = c(composition)) %>%
+  group_by(station) %>%
+  summarise(
+    nbnode = length(unique(sp_class)),
+    nbsp = length(unique(str_extract(sp_class, "[A-Z]+")))
+  ) %>%
+  arrange(nbsp)
+
+net <- network_analysis %>%
+  dplyr::select(opcod, network) %>%
+  unnest(cols = c(network)) %>%
+  left_join(., dplyr::select(op_analysis, opcod, station, date)) %>%
+  mutate(date = lubridate::year(date))
+
+myload(species_color_temporal_plot,
+  envir = environment(),
+  dir = get_mypath("data"))
 ```
@@
 ```{r}
-pred_plot_signif %>%
-  select(variable, data) %>%
-  unnest(data) %>%
-  ggplot() %>%
-  geom_errorbar(aes(xmin = bm_slope - bm_slope_strd_error, xmax = bm_slope +
-      bm_slope_strd_error), alpha = .3) +
-  geom_errorbar(aes(ymin = linear_slope - linear_slope_strd_error,
-      ymax = linear_slope + linear_slope_strd_error), alpha = .3)
-  }
-  ggplot()
-plot_final_model
+#st_id_plot
+temporal_network <- map(st_network_to_plot, function (st) {
+  net_ex <- filter(net, station == st)
+  p <- my_crap_temporal_network(
+    net = net_ex,
+    metaweb = meta$metaweb,
+    network_data = network_analysis,
+    nrow_sp_legend = 2,
+    return_data = TRUE,
+    my_y_lim = c(0, 4.1),
+    bm_var = "bm_std",
+    color_node = species_color_temporal_plot
+  )
+  plot_grid(plotlist = p$plots)
+  })
+temporal_network[[1]]
+temporal_network[[2]]
+temporal_network[[3]]
+temporal_network[[4]]
+```
+
+```{r}
+loadd(rigal_species)
+species_trends <- rigal_species %>%
+  unnest(classif) %>%
+  select(station, species = variable, linear_slope, linear_slope_strd_error, linear_slope_pvalue)
+
+species_trends2 <- species_trends %>%
+  left_join(filter(log_bm_net_group_f3y, variable == "connectance") %>%
+    select(station, bm_slope),
+    by = "station")
+species_trends2 %<>% na.omit
+
+species_trends2 %>%
+  filter(linear_slope_pvalue < 0.05) %>%
+  ggplot(aes(y = linear_slope, x = bm_slope, color = species)) +
+  geom_point()
+
+species_trend_cor <-
+  species_trends2 %>%
+  group_by(species) %>%
+  summarise(
+    spear = cor(linear_slope, bm_slope, method = c("spearman"), use = "pairwise.complete.obs"),
+    n = n()
+  )
+
+species_trend_cor %>%
+  filter(n >= 20) %>%
+  ggplot(aes(y = spear, x = species)) +
+  geom_bar(stat = "identity") +
+  theme(axis.text.x = element_text(angle = 45))
+```
+
+```{r}
+# Obtain avg troph lvl by species
+dead_material <- c("det", "biof")
+tlvl <- NetIndices::TrophInd(meta$metaweb, Dead = dead_material)$TL
+names(tlvl) <- colnames(meta$metaweb) 
+tlvl <- enframe(tlvl, name = "sp_class", value = "tlvl")
+
+species_tlvl <- 
+  tlvl %>%
+  filter(str_detect(sp_class, "[A-Z]{3}.")) %>%
+  mutate(species = str_sub(sp_class, 1, 3)) %>%
+  group_by(species) %>%
+  summarise(tlvl = mean(tlvl, na.rm = TRUE))
+```
+
+```{r}
+species_trend_cor %>%
+  left_join(species_tlvl, by = "species") %>%
+  filter(n > 20) %>%
+  ggplot(aes(x = tlvl, y = spear)) +
+  geom_point() +
+  geom_smooth(method = "lm")
 ```

### 2020-12-23 supplementary.Rmd
Compute l, ld, gini, fish-fish network, temporal network, species trends

---
title: "Supplementary methods and results"
author: "Alain Danet"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
    math: katex
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE 
)
```

```{r}
library(drake)
library(tidyverse)
library(magrittr)
library(cowplot)
library(viridis)
library(kableExtra)
library(sf)
source("R/misc.R") # Define your custom code as a bunch of functions.
source("R/variable_shortcut.R")
source_dir(get_mypath("R")) # Define your custom code as a bunch of functions.

#theme_set(theme_cowplot())
```

```{r}
loadd(temporal_dynamics_coef)
loadd(temporal_dynamics_plot)
loadd(full_data2)
loadd(biomass_group)
```

# Methods

## Station grouping

### Rigal station increase / decrease

Les stations ont moins de 40 kilos au départ ont l'air comparable en terme de
dynamique.

```{r, eval=FALSE}

p_rigal_decrease_increase_slope_st <- 
  st_decrease_increase_rigal_biomass %>%
  left_join(biomass_group, by = "station") %>%
  ggplot(aes(y = linear_slope, x = bm_slope, color = shape_class)) +
  geom_point() +
  facet_wrap(~variable)
p_rigal_decrease_increase_slope_st
```

### Tendancies in rigal increase / decrease

```{r}
bm_vs_net_trends %>%
  ggplot(aes(x = reg_weight)) +
  geom_histogram() +
  facet_wrap(~variable)

bm_net_group_median %>%
  ggplot(aes(x = bm_slope, y = linear_slope, size = reg_weight, weight = reg_weight, color = log(bm))) +
  geom_point() +
  scale_color_viridis() +
  geom_vline(xintercept = 0, color = "red") +
  geom_smooth() +
  facet_wrap(~variable, scales = "free_y") +
  labs(x = "Biomass trend (g.m-1.y-1)", y = "Network trend (U.y-1)")

log_bm_net_group_f3y %>%
  ggplot(aes(x = bm_slope, y = linear_slope, size = reg_weight, weight = reg_weight, color = log(bm))) +
  geom_point() +
  scale_color_viridis() +
  geom_vline(xintercept = 0, color = "red") +
  geom_smooth() +
  facet_wrap(~variable, scales = "free_y") +
  labs(x = "Log Biomass trend (g.m-1.y-1)", y = "Network trend (U.y-1)")
```

### With group

#### Median

```{r}
##Summary of group 
biomass_group %>%
  filter(group_type == "median") %>%
  ggplot(aes(x = bm)) +
  geom_histogram() +
  facet_wrap(bm_var~summary_type, scales = "free_x")
```
```{r, eval = FALSE}
group_results <- 
  rigal_biomass_coeff_dynamics %>%
  left_join(biomass_group, by = "station") %>% 
  filter(group_type == "median", bm_var == "bm_std")

p1 <- group_results %>%
  filter(summary_type == "first_3_year") %>%
  ggplot(aes(x = linear_slope, y = estimate, color = group,
      size = reg_weight, weight = reg_weight)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~coeff, scales = "free_y")

p3 <- group_results  %>%
  filter(summary_type == "median") %>%
  ggplot(aes(x = linear_slope, y = estimate, color = group, size = reg_weight, weight = reg_weight)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~coeff, scales = "free_y")

p1
p3
```

#### Little and big rivers

```{r}
loadd(stream_group)
#grandes/petites rivières
stream_group %>%
  ggplot(aes(x = width_river_mean, fill = group)) +
  geom_histogram() +
  facet_grid(~group_type)

stream_group %>%
  filter(group_type == "median") %>%
  ggplot(aes(x = width_river_mean, fill = protocol_type)) +
  geom_histogram()

stream_group %>%
  filter(group_type == "median") %>%
  left_join(
    biomass_group %>%
    filter(group_type == "median", summary_type == "median") %>%
    select(-group_type, -summary_type, -group),
  by = "station"
  ) %>%
  filter(!is.na(protocol_type)) %>%
  ggplot(aes(x = bm, fill = protocol_type)) +
  geom_histogram() +
  facet_wrap(~bm_var, scales = "free_x")
```

# Patterns

```{r}
bm_net_group_median %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm), size = reg_weight, weight = reg_weight)) +
  geom_point() +
  scale_color_viridis() +
  #geom_smooth(method = "lm") +
  facet_wrap(~variable, scales = "free") +
  labs(title = "Group as mean biomass")

bm_net_group_median %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
  geom_point() +
  scale_color_viridis() +
  geom_errorbar(aes(
      xmin = bm_slope - bm_slope_strd_error,
      xmax = bm_slope + bm_slope_strd_error),
    alpha = .2
    ) +
  geom_errorbar(aes(
      ymin = linear_slope - linear_slope_strd_error,
      ymax = linear_slope + linear_slope_strd_error),
    alpha = .2
    ) +
  facet_wrap(~variable, scales = "free") +
  labs(title = "Group as mean biomass")

bm_net_group_median %>%
  filter(!is.na(protocol_type)) %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm), size = reg_weight, weight = reg_weight)) +
  geom_point() +
  scale_color_viridis() +
  #geom_smooth(method = "lm") +
  facet_grid(variable~protocol_type, scales = "free") +
  labs(title = "Group as mean biomass")
```

```{r, fig.height = 12, fig.width = 12}
log_bm_net_group_f3y %>%
  filter(!is.na(protocol_type)) %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
  geom_point() +
  scale_color_viridis() +
  geom_errorbar(aes(xmin = bm_slope - bm_slope_strd_error,
      xmax = bm_slope + bm_slope_strd_error), alpha = .3) +
  geom_errorbar(aes(ymin = linear_slope - linear_slope_strd_error,
      ymax = linear_slope + linear_slope_strd_error), alpha = .3) +
  facet_grid(variable~protocol_type, scales = "free") +
  labs_log_bm_net_trends()
```

```{r}
knitr::opts_chunk$set(
  eval = FALSE 
)
```

## Other Statistical model

#### Quadratic one

```{r}
pred_log_bm_quad <- summary_log_bm_f3y %>%
  filter(model == "mod_bm_quad") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )

test <- map2(model_log_bm_f3y$data, pred_log_bm_quad$pred_df, plot_pred_data,
  std_error = TRUE)
plot_grid(plotlist = test, labels = model_log_bm_f3y$variable)
```

```{r}

vif_log_bm_f3y %>%
  ggplot(aes(y= vif, x = term)) +
  geom_hline(yintercept = 10) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_grid(model_type~variable, scales = "free")
```

### By protocol

```{r}
loadd(vif_log_bm_by_protocol)

protocol_vec <- vif_log_bm_by_protocol$protocol_type %>% unique
p_vif_protocol <- map(protocol_vec, function (x) {
  vif_log_bm_by_protocol %>%
    filter(protocol_type == x) %>%
    ggplot(aes(y= vif, x = term)) +
    geom_hline(yintercept = 10) +
    geom_bar(stat = "identity") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(title = paste0("Protocol type: ", x)) +
    facet_grid(model_type~variable, scales = "free_y")
  })
p_vif_protocol[[1]]
p_vif_protocol[[2]]
```

```{r}
loadd(model_log_bm_f3y_by_protocol, summary_log_bm_f3y_by_protocol)
```

```{r, eval = FALSE}
complete_log_quad2 <- get_table_from_summary(.data = summary_log_bm_f3y_by_protocol, model = "mod_bm_quad2", protocol = "complete")

complete_log_quad2[["reg_table"]] %>% 
  kable(.,
    booktabs = TRUE, 
    caption = 
      paste0(
      "Regression table for the model: dN =",
      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
    ) 
  )

complete_log_quad2[["anova_table"]] %>% 
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA table for the model: dN =",
      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
    )
  )
```

```{r, eval = FALSE}
filter(summary_log_bm_f3y_by_protocol, model == "mod_log_bm_inc")[["resume"]]
filter(summary_log_bm_f3y_by_protocol, model == "mod_log_bm_inc")[["anova"]]

filter(summary_log_bm_f3y_by_protocol, model == "mod_bm_quad")[["resume"]]
filter(summary_log_bm_f3y_by_protocol, model == "mod_log_bm_inc")[["anova"]]
```

#### Quadratic two

```{r}
pred_log_bm_quad2 <- summary_log_bm_f3y_by_protocol %>%
  filter(model == "mod_bm_quad2", protocol_type == "complete") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )
model_log_bm_f3y_by_protocol %<>% filter(protocol_type == "complete")

pred_log_bm_quad2_plot <- map2(model_log_bm_f3y_by_protocol$data, pred_log_bm_quad2$pred_df,
  plot_pred_data)
plot_grid(plotlist = pred_log_bm_quad2_plot, labels = model_log_bm_f3y$variable)
```

#### Quadratic one

```{r}
pred_log_bm_quad <- summary_log_bm_f3y_by_protocol %>%
  filter(model == "mod_bm_quad", protocol_type == "complete") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )
model_log_bm_f3y_by_protocol %<>% filter(protocol_type == "complete")

pred_log_bm_quad_plot <- map2(model_log_bm_f3y$data, pred_log_bm_quad$pred_df, plot_pred_data,
  std_error = TRUE)
plot_grid(plotlist = pred_log_bm_quad_plot, labels = model_log_bm_f3y$variable)
```

```{r, eval = FALSE}
pred <- summary_log_bm_f3y_by_protocol %>%
  filter(model == "mod_log_bm_inc") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "log_bm [quart2]", "inc_f"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
  )
plot_grid(plotlist = pred$plot, labels = pred$variable)
```

```{r, eval = FALSE}
pred <- summary_log_bm_f3y_by_protocol %>%
  filter(model == "mod_log_bm_inc") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "log_bm [quart2]", "inc_f"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
  )
plot_grid(plotlist = pred$plot, labels = pred$variable)
```

### Can we predict the model without all simple effects?

```{r, eval = FALSE}
# Perform a valid model 
pred <- model_int %>%
  select(-data, -mod4) %>%
  pivot_longer(cols = c(mod1:mod5), names_to = "model_type", values_to =
    "mod_obj") %>%
  mutate(
    pred_ref = map2(mod_obj, model_type, function (x, y) {
       if (y %in% c("mod3", "mod5"))
	 terms_spec <- c("bm_slope", "inc_f", "bm")
       else
	 terms_spec <- c("bm_slope", "inc_f", "bm_group") 
      ggpredict(x, terms = terms_spec)
      }
    ),
    pred_cte = map2(mod_obj, model_type, function (x, y) {
       if (y %in% c("mod3", "mod5"))
	 terms_spec <- c("linear_slope", "inc_f", "bm")
       else
	 terms_spec <- c("linear_slope", "inc_f", "bm_group") 
      ggeffect(x, terms = terms_spec)
      }
    )
  )

pred %<>%
  mutate(
  plot_pred_ref = map(pred_ref, plot, add.data = TRUE),
  plot_pred_cte = map(pred_cte, plot, add.data = TRUE)
  )
pred_richness <- pred %>%
  filter(variable == "richness", model_type == "mod3")

pred$plot_pred_ref[[1]]
pred$plot_pred_cte[[1]]
pred$plot_pred[[2]]
pred$plot_pred[[3]]
pred$plot_pred_ref[[4]]
```

```{r, eval = FALSE}
library(ggeffects)
mydf <- ggpredict(model_int$mod3[[1]], terms = c("linear_slope", "inc_f",
    "bm"))
plot(mydf, add.data = TRUE)

```

```{r, eval = FALSE}
model_log %<>%
  mutate(
    pred5 = map(mod3, ~ggpredict(.x,
	terms = c("linear_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2, 3, 4, 6]", "inc_f", "bm"))),
    pred5_df = map(pred5, as_tibble),
    plot = map(pred5, ~plot(.x, add.data = TRUE)),
    myplot = map2(pred5, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )

#plot_final_model(model_int$pred5[[1]], model_int$data[[1]])
plot_grid(plotlist = model_int$plot, labels = model_int$variable)
model_int$plot[[1]]
summary(model_int$mod3[[1]])
test <- model_int$data[[1]]
model_int$pred5_df[[1]]
test %>%
  ggplot(aes(x = bm_slope, y = linear_slope, weight = reg_weight, size = reg_weight)) +
  geom_smooth(method = "lm") +
  geom_point()

pred_test <-
  model_int$pred5_df[[1]] %>%
  as_tibble %>%
  rename(increasing = group, group = facet) %>%
  filter(increasing == FALSE & x < 0 | increasing == TRUE & x > 0)

p <- ggplot(pred_test, aes(x = x , y = predicted, color = group)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group), alpha =
    .1) +
  geom_line() +
  geom_point(data = rename(test,
      predicted = linear_slope, x = bm_slope),
    aes(x = x, y = predicted),
    inherit.aes = FALSE)
```

```{r, eval = FALSE}
model_int$pred5_df[[1]] %>%
  ggplot()

plot_final_model(model_int$pred5[[1]], rawdata = model_int$data[[1]], facet =
  TRUE)
```

# Correlation

```{r}
cor_bm_net <- bm_net_group_median %>%
  select(bm_slope, variable, linear_slope, bm, width_river_mean) %>%
  pivot_wider(names_from = variable, values_from = linear_slope) 
corrplot::corrplot(cor(na.omit(cor_bm_net)), type = "upper")

library(ade4)
library(factoextra)
res.pca <- dudi.pca(na.omit(cor_bm_net),
                    scannf = FALSE,   # Cacher le scree plot
                    nf = 3            # Nombre d'axes gardés
                    )
screeplot(res.pca, main = "Screeplot - Eigenvalues")
p1 <- fviz_pca_var(res.pca,
  col.var = "contrib", 
  gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
  repel = TRUE     
)
p2 <- fviz_pca_var(res.pca,
  axes = c(1, 3),
  col.var = "contrib", 
  gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
  repel = TRUE     
)

p3 <- fviz_pca_var(res.pca,
  axes = c(2, 3),
  col.var = "contrib", 
  gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
  repel = TRUE     
)
plot_grid(p1, p2, p3)
```

## Richness

```{r}
knitr::opts_chunk$set(
  eval = FALSE 
)
```

```{r}
st_big_bm_tendancies <- group_results %>%
  filter(abs(linear_slope) > 5000) %>%
  .$station %>%
  unique
plot_big_bm_tendancies <- temporal_dynamics_plot %>%
  filter(variable == "biomass", station %in% st_big_bm_tendancies) %>%
  .$plot
plot_grid(
  plotlist = map(plot_big_bm_tendancies, 
    ~.x + lims(x = c(0, 10), y = c(0, 155000)))
)
```

```{r}
rigal_shape_var <- rigal_classification %>%
  unnest(classif) %>%
  select(station, variable, shape_class) %>%
  mutate(station = as.character(station))

rigal_shape_var %>%
  filter(station %in% st_decrease_increase_rigal_biomass$station) %>%
  ggplot(aes(x = shape_class)) +
  geom_bar() +
  facet_wrap(~ variable) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## SAX

```{r, eval = FALSE}
library(jmotif)
loadd(full_data2)
sax_all_variable <- full_data2 %>%
  select(station, nb_year, biomass:log_bm) %>%
  pivot_longer(cols = biomass:log_bm, names_to = "variable", values_to = "value") %>%
  group_by(station, variable) %>%
  arrange(nb_year) %>%
  nest() %>%
  mutate(
    zts = map(data, function(x) znorm(x$value, threshold = 0.01)),
    paa = map(zts, ~paa(., 3)),
    sax = map_chr(paa, ~series_to_string(., 3))
  ) %>%
  ungroup()

# CBA:
sax_all_variable %>%
  filter(station %in% cba_rigal_sax$station, !variable %in% c("biomass", "nbnode")) %>%
  ggplot(aes(x = sax)) +
  geom_bar() +
  facet_wrap(facets = ~variable)

sax_all_variable %>%
  filter(
    station %in% cba_rigal_sax$station,
    !variable %in% c("biomass", "nbnode")
    ) %>%
  ggplot(aes(x = sax)) +
  geom_bar() +
  facet_wrap(facets = ~variable)
```

```{r}
loadd(hyp_table)
hyp_table <- make_hyp_table(hyp_table = effect_quad2_piece, mod = model_log_bm)
hyp_table %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Comparison of the two Statistical model for the median biomass model"
    )
  ) %>%
  collapse_rows(columns = 1, valign = "top")
```

### Compare Quad2 and piecewiseregression

```{r}
loadd(model_log_bm, summary_model_log_bm,
  summary_log_bm, vif_model_log_bm)
```

```{r}
loadd(effect_quad2_piece)
effect_quad2_piece %>%
  kable(., booktabs = TRUE,
    caption = paste0(
      "Hypothesis and matching coefficients."))
```

```{r}
loadd(hyp_table_f3y)
hyp_table_f3y <- make_hyp_table(hyp_table = effect_quad2_piece, mod = model_log_bm_f3y)

hyp_table_f3y %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Comparison of the two Statistical model for first three year"
    )
  ) %>%
  collapse_rows(columns = 1, valign = "top")
```

## Raw bm

```{r, eval = TRUE}
loadd(model_bm, model_bm_vif)

model_bm_vif %>%
  ggplot(aes(y = vif, x = term)) +
  geom_hline(yintercept = 10) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_grid(model_type~variable, scales = "free")
```

```{r, eval = FALSE}
library(yhat)
test <- model_int$mod3[[1]]
CCData <- commonalityCoefficients(model_int$data[[1]],
  "linear_slope",
  list("bm_slope", "inc_f", "bm"), "F")
CCData

test_data <- model_int$data[[1]]
lm_test <- lm(
  formula = linear_slope ~ bm_slope*inc_f*bm,
  weights = reg_weight
)
test <- regr(lm_test)
```

### Effect of protocol type on the model validity

```{r}
loadd(model_bm_by_protocol, model_bm_by_protocol_vif)

protocol_vec <- model_bm_by_protocol_vif$protocol_type %>% unique
p_vif_protocol <- map(protocol_vec, function (x) {
  model_bm_by_protocol_vif %>%
    filter(protocol_type == x) %>%
    ggplot(aes(y= vif, x = term)) +
    geom_hline(yintercept = 10) +
    geom_bar(stat = "identity") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(title = paste0("Protocol type: ", x)) +
    facet_grid(model_type~variable, scales = "free_y")
  })
p_vif_protocol[[1]]
p_vif_protocol[[2]]
```

```{r, eval = FALSE}
filter(model_bm_by_protocol_vif, model_type == "mod_bm_quad")
```

```{r}
loadd(bm_net_group)
bm_net_group %>%
  filter(variable == "connectance") %>%
  ggplot(aes(x = bm_slope, y = bm)) +
  geom_point()
```

### Current best model

$$
Y = \alpha + \beta_1D_b + \beta_2D_bI_b + \beta_3D_bI_bB
$$

```{r, eval = TRUE}
loadd(model_bm_by_protocol_summary)
model_bm_by_protocol_summary %<>%
  filter(protocol_type == "complete")
```

```{r, eval = FALSE}
filter(model_bm_by_protocol_summary, model == "mod_inc_bm")[["resume"]]
filter(model_bm_by_protocol_summary, model == "mod_inc_bm")[["anova"]]

filter(model_bm_by_protocol_summary, model == "mod_bm_inc")[["resume"]]
filter(model_bm_by_protocol_summary, model == "mod_bm_inc")[["anova"]]

filter(model_bm_by_protocol_summary, model == "mod_bm_quad")[["resume"]]
filter(model_bm_by_protocol_summary, model == "mod_bm_quad")[["anova"]]

filter(model_bm_by_protocol_summary, model == "mod_bm_quad2")[["resume"]]
filter(model_bm_by_protocol_summary, model == "mod_bm_quad2")[["anova"]]
```

```{r, eval = TRUE}
pred <- model_bm_by_protocol_summary %>%
  filter(model == "mod_bm_inc") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2, 3, 4, 6]", "bm [quart2]", "inc_f"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )
plot_grid(plotlist = pred$plot, labels = pred$variable)
```

```{r}
pred <- model_bm_by_protocol_summary %>%
  filter(model == "mod_bm_quad2") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope [-8, -6, -4,-3, -2, -1, -.5, -.01, .01, .5, 1, 2, 3, 4, 6]", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )
plot_grid(plotlist = pred$plot_data, labels = pred$variable)
```

#### All protocol

```{r}
loadd(model_bm_summary)
```

```{r, eval = FALSE}
filter(model_bm_summary, model == "mod_inc_bm")[["resume"]]
filter(model_bm_summary, model == "mod_inc_bm")[["anova"]]

filter(model_bm_summary, model == "mod_bm_inc")[["resume"]]
filter(model_bm_summary, model == "mod_bm_inc")[["anova"]]

filter(model_bm_summary, model == "mod_bm_quad")[["resume"]]
filter(model_bm_summary, model == "mod_bm_quad")[["anova"]]

filter(model_bm_summary, model == "mod_bm_quad2")[["resume"]]
filter(model_bm_summary, model == "mod_bm_quad2")[["anova"]]
```

```{r}
pred_bm_quad2 <- model_bm_summary %>%
  filter(model == "mod_bm_quad2") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )
plot_grid(plotlist = pred_bm_quad2$plot, labels = pred_bm_quad2$variable)
pred_bm_quad2_plot <- map2(model_bm$data, pred_bm_quad2$pred_df, plot_pred_data)

plot_grid(plotlist = pred_bm_quad2_plot, labels = pred_bm_quad2$variable)

pred_bm_quad <- model_bm_summary %>%
  filter(model == "mod_bm_quad") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )

pred_bm_quad_plot <- map2(model_bm$data, pred_bm_quad$pred_df, plot_pred_data)
plot_grid(plotlist = pred_bm_quad_plot, labels = pred_bm_quad2$variable)
```

#### Quadratic two

```{r}
#model_bm$data[[1]] %>%
  #ggplot(aes(x = bm_slope, y = linear_slope, fill = log(bm)), shape = 23, size = 4) +
  #scale_fill_viridis() +
  #geom_point() +
  #geom_line(
    #data = pred_bm_quad2$pred_df[[1]] %>%
      #rename(bm_f = group, bm_slope = x, linear_slope = predicted),
    #aes(y = linear_slope, x = bm_slope, color = bm_f),
    #inherit.aes = FALSE)

test <- map2(model_bm$data, pred_bm_quad2$pred_df, function (.data, pred) {

  .data %>%
    ggplot(aes(x = bm_slope, y = linear_slope, fill = log(bm)), shape = 23, size = 4) +
    scale_fill_viridis() +
    geom_point() +
    geom_line(
      data = pred %>%
	rename(bm_f = group, bm_slope = x, linear_slope = predicted),
      aes(y = linear_slope, x = bm_slope, color = bm_f),
      inherit.aes = FALSE)

    })
plot_grid(plotlist = test)
```

#### Quadratic one

```{r}
test <- map2(model_bm$data, pred_bm_quad$pred_df, function (.data, pred) {

  .data %>%
    ggplot(aes(x = bm_slope, y = linear_slope, fill = log(bm)), shape = 23, size = 4) +
    scale_fill_viridis() +
    geom_point() +
    geom_line(
      data = pred %>%
	rename(bm_f = group, bm_slope = x, linear_slope = predicted),
      aes(y = linear_slope, x = bm_slope, color = bm_f),
      inherit.aes = FALSE)

    })
plot_grid(plotlist = test, labels = model_bm$variable)
```

### 2020-12-23 R/plot_methods.R

@@ -1,0 +1,1386 @@
+#' Get species from nodes
+#' @param list 
+#'
+#' @details By convention the node naming scheme is set as the following:
+#'  species_code + _ + class_nb. This function is just a wrapper around
+#'  extract_all().
+#'
+get_species <- function(node_list) {
+
+  species_resource_list <- stringr::str_extract_all(
+    node_list, "[A-Za-z]+", simplify = TRUE)
+
+  species_resource_list
+
+}
+
+#' Colours species 
+#'
+#'  
+#' @inheritParams set_layout_graph a object generated by build_metaweb
+#'
+#' @return a colour scale 
+set_color_species <- function (node_list = NULL, species_list = NULL,  resource_list = NULL,
+  col_resource = NULL) {
+  # Extract species
+  if (is.null(species_list)) {
+    sp_list <- stringr::str_extract_all(
+      node_list, "[A-Z]+", simplify = TRUE) %>%
+    as.vector %>%
+    unique
+    sp_list <- sp_list[sp_list != ""]
+  } else {
+    regex_pattern <- paste0(species_list, collapse = "|")
+    sp_list <- stringr::str_extract_all(
+      node_list, regex_pattern, simplify = TRUE) %>%
+    as.vector %>%
+    unique
+    # Remove empty names
+    sp_list <- sp_list[sp_list != ""]
+  }
+  # get hue color
+  gg_color_hue <- function(n) {
+    hues = seq(0, 360, length = n + 1)
+    hcl(h = hues, l = 65, c = 100)[1:n]
+  }
+  species_color <- gg_color_hue(length(sp_list))
+  names(species_color) <- sp_list
+
+  #Resource:
+  if (is.null(resource_list)) {
+    resource_list <- stringr::str_extract_all(
+      node_list, "[a-z]+", simplify = TRUE) %>%
+    as.vector %>%
+    unique
+    # Remove empty names
+    resource_list <- resource_list[resource_list != ""]
+  }
+  if (is.null(col_resource)) {
+    col_resource <- "#CCCCCC"
+  }
+  resource_color <- rep(col_resource, length(resource_list))
+  names(resource_color) <- resource_list
+  c(species_color, resource_color)
+}
+my_crap_temporal_network <- function (
+  net = NULL,
+  metaweb = parent.frame()$meta$metaweb,
+  network_data = parent.frame()$network_analysis,
[…]

### 2020-12-23 R/synchrony.R

@@ -1,0 +1,187 @@
+################################################################################
+#                        Functions to compute synchrony                        #
+################################################################################
+
+compute_sp_nb_from_com_mat <- function (com_mat = NULL) {
+
+  rowSums(com_mat != 0)
+
+}
+
+compute_avg_cv_sp <- function(biomass, variance) {
+  #Check that the species are in the same order in the vector:
+  stopifnot(names(biomass) == names(variance))
+
+  rel_biomass <- biomass / sum(biomass)
+  rel_sdt <- sqrt(variance) / biomass
+
+  cv_avg <- sum(rel_biomass * rel_sdt)
+  return(cv_avg)
+}
+
+compute_cv_com <- function(synchrony, cv_sp) {
+  sqrt(synchrony) * cv_sp
+}
+
+compute_synchrony <- function(cov_mat) {
+  com_var <- sum(cov_mat)
+  var_intra_sp <- sum(sqrt(diag(cov_mat)))
+  phi <- com_var / (var_intra_sp^2)
+  return(phi)
+}
+
+get_sync_cv_mat <- function(com_analysis = NULL, op_analysis = NULL, presence_threshold = 0.1) {
+
+  # If it is network data, change the "species" colum
+  stopifnot(any(c("species", "sp_class") %in% names(com_analysis)))
+  if ("sp_class" %in% names(com_analysis)) {
+    com_analysis %<>% dplyr::rename(species = sp_class)
+    troph <- TRUE
+  } else {
+    troph <- FALSE 
+  }
+
+  com <- dplyr::ungroup(com_analysis) %>%
+    dplyr::left_join(dplyr::select(op_analysis, opcod, station, year), by = "opcod") %>%
+    dplyr::filter(!is.na(station))
+
+  if (troph) {
+    com %<>% dplyr::select(station, year, species, biomass, troph_level,troph_group)
+  } else {
+    com %<>% dplyr::select(station, year, species, biomass)
+  }
+  
+
+  if (!is.na(presence_threshold)) {
+    # We will compute the variance of each species in each station, which
+    # require that there is some obsversation
+    filter_na <- com %>%
+      dplyr::group_by(station, species) %>%
+      dplyr::summarise(n = sum(!is.na(biomass)) / dplyr::n()) %>%
[…]

### 2021-01-03 report.Rmd
Add NMDS analysis

@@
 
-##
+## Temporal series of networks
 
 ```{r}
-loadd(log_bm_net_group_f3y)
 st_id_plot <- log_bm_net_group_f3y %>%
@@
   ggplot(aes(y = linear_slope, x = bm_slope, color = species)) +
-  geom_point()
+  geom_point() +
+  geom_smooth(method = "lm")
 
@@
   species_trends2 %>%
+  filter(linear_slope_pvalue < 0.05) %>%
   group_by(species) %>%
@@
 species_trend_cor %>%
-  filter(n >= 20) %>%
+  filter(n >= 5) %>%
   ggplot(aes(y = spear, x = species)) +
   geom_bar(stat = "identity") +
+  geom_label(aes(y = 0, label = paste("N=", n)), vjust = 1) +
   theme(axis.text.x = element_text(angle = 45))
@@
   left_join(species_tlvl, by = "species") %>%
-  filter(n > 20) %>%
+  filter(n >= 5) %>%
   ggplot(aes(x = tlvl, y = spear)) +
-  geom_point() +
+  geom_label(aes(label = species)) +
   geom_smooth(method = "lm")
+```
+
+## Composition and biomass trajectory
+
+```{r}
+library(vegan)
+myload(nmds, com_mat,envir = environment(), dir = get_mypath("data"))
+
+bm_slope_df <- log_bm_net_group_f3y %>% 
+  filter(variable == "connectance") %>%
+  select(station, bm_slope, bm) %>%
+  arrange(station)
+
+loadd(com_analysis_data, op_data)
+com_mat <- compute_com_mat(
+  .op = ungroup(op_data) %>% filter(station %in% bm_slope_df$station),
+  com = ungroup(com_analysis_data))
+
+com <- com_mat %>% 
+  arrange(station) 
+#check:
+all(com$station == bm_slope_df$station)
+com <- com[, colSums(com != 0) > 0] %>%
+  select(-station)
+
+nmds <- metaMDS(com, k = 2, trymax = 100)
+
+```
+
+```{r}
+diverging_pal <- c("#67001f", "#b2182b", "#d6604d", "#f4a582", "#fddbc7",
+  "#f7f7f7", "#d1e5f0", "#92c5de", "#4393c3", "#2166ac", "#053061")
+
+par(mfrow = c(1, 2))
+stressplot(nmds)
+title("Stress plot")
+bluefunc <- colorRampPalette(c("lightyellow", "darkred"))
+ordiplot(nmds,type="n")
+orditorp(nmds,display="species",col="gray",air=0.01)
+orditorp(nmds, display="sites",
+  col= diverging_pal[findInterval(bm_slope_df$bm_slope, seq(-0.2,.2, length.out = length(diverging_pal)))],
+   cex = findInterval(bm_slope_df$bm, seq(1, 4, 1))/2,
+  air=0.01, pch = "+", labels = "+")
+title("Color = ; Size of points = biomass")
+
 ```

### 2021-01-03 R/community_analysis.R

@@ -1,0 +1,488 @@
+# Turn community analyze steps into functions 
+
+#' Remove species from community and network
+#' 
+#' @param 
+#' @param com community_analysis
+rm_sp_from_com <- function (com = NULL, sp_to_rm = NULL) {
+
+  com %<>%
+    filter(!species %in% sp_to_rm)
+
+  return(com)
+
+}
+
+#' Summarise network metrics over time
+#'
+#' Compute the median and the CV of network metrics through time 
+#'
+#' @param op data.frame containing opcod and station 
+#' @param network data.frame containing opcod and network metrics 
+#'
+#'
+summarise_network_over_time <- function (
+  op = NULL,
+  class_network = NULL,
+  species_network = NULL,
+  metrics = NULL,
+  type_metrics = "species") {
+
+  op %<>%
+    dplyr::select(opcod, station, year, surface)
+
+  # Metrics are computed with a type of network
+  stopifnot(type_metrics %in% c("species", "classes"))
+  if (type_metrics == "classes") {
+   com <- op %>%
+    dplyr::left_join(class_network, by = "opcod") 
+    
+  } else {
+   com <- op %>%
+    dplyr::left_join(species_network, by = "opcod") 
+  }
+   com %<>%
+    dplyr::group_by(station) %>%
+    dplyr::summarise_at(metrics,
+      list(cv = ~sd(.) / mean(.), med = median, stab = ~mean(.) / sd(.)))
+
+    ##  Trophic group metrics are computed with class network
+    # Get total richness, biomass_med,  by station and trophic group 
+  composition <- class_network %>%
+    dplyr::left_join(op, by = "opcod") %>%
+    dplyr::select(station, composition) %>%
+    tidyr::unnest(composition) %>%
+    dplyr::mutate(species = str_extract_all(sp_class, "[A-Z]{3}"))
+
+  sum_surface <- op %>%
+    dplyr::group_by(station) %>%
+    dplyr::summarise(sum_surface = sum(surface))
+
+  richness_tot <- composition %>%
+    dplyr::group_by(station, troph_group) %>%
+    dplyr::summarise(richness_tot = length(unique(species))) %>%
+    dplyr::left_join(sum_surface, by = "station") %>%
+    dplyr::mutate(rich_tot_std = richness_tot / sum_surface) %>%
[…]

### 2021-01-06 report.Rmd
Add richness analysis

@@
 #loadd(bm_net_group_median, bm_vs_net_trends)
+loadd(bm_net_group_f3y)
+loadd(bm_net_group_f3y)
+loadd(rich_vs_net_trends)
+
+#compute_my_lm_vs_net_model(
+      #.df = filter(my_bm_net_group, !is.na(protocol_type)),
+      #var_to_group = "variable"
+#)
 ```
@@
 
-nmds <- metaMDS(com, k = 2, trymax = 100)
-
 ```
 
-```{r}
+```{r, cache = TRUE}
+nmds <- metaMDS(com, k = 2, trymax = 100)
+```
+
+```{r, fig.width = 8}
 diverging_pal <- c("#67001f", "#b2182b", "#d6604d", "#f4a582", "#fddbc7",
@@
 title("Color = ; Size of points = biomass")
-
 ```

### 2021-01-06 R/get_model_plot.R

@@ -43,7 +43,6 @@ plot_final_model <- function (ggpred = NULL, rawdata = NULL, facet = FALSE, std_
 
   ggpred %<>% as_tibble
 
-
   if ("facet" %in% names(ggpred)) {
   ggpred %<>% rename(increasing = group, group = facet)
   } else{
@@ -56,44 +55,55 @@ plot_final_model <- function (ggpred = NULL, rawdata = NULL, facet = FALSE, std_
     filter(increasing == FALSE & x < 0 | increasing == TRUE & x > 0)
 
   if (is.null(rawdata)) {
-  rawdata <- attr(ggpred, "rawdata")
+    rawdata <- attr(ggpred, "rawdata")
   }
 
+  if ("bm_slope" %in% colnames(rawdata)) {
+    x_var <- "bm_slope"
+    x_var_error <- "bm_slope_strd_error"
+  } else if ("rich_slope" %in% colnames(rawdata)) {
+    x_var <- "rich_slope" 
+    x_var_error <- "rich_slope_strd_error"
+  } else {
+    stop("X var cannot be defined")
+  }
+  
   p <- rawdata %>%
-    ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
+    ggplot(aes_string(x = x_var, y = "linear_slope", color = "log(bm)")) +
     viridis::scale_color_viridis() +
     geom_point() 
 
+  renaming_vector <- c( "x", "predicted")
+  names(renaming_vector) <- c(x_var, "linear_slope")
+
   if ("group" %in% colnames(ggpred)) {
+    renaming_vector <- c(renaming_vector, bm_f = "group")
     p <- p +
       geom_line(
 	data = ggpred %>%
-	  rename(bm_f = group, bm_slope = x, linear_slope = predicted),
-	aes(y = linear_slope, x = bm_slope, linetype = bm_f),
+	  rename(!!!renaming_vector),
+	aes_string(y = "linear_slope", x = x_var, linetype = "bm_f"),
 	inherit.aes = FALSE)
   } else {
     p <- p +
       geom_line(
-	data = ggpred %>%
-	  rename(bm_slope = x, linear_slope = predicted),
-	aes(y = linear_slope, x = bm_slope),
-	inherit.aes = FALSE)
+	data = ggpred %>% rename(!!!renaming_vector),
+	aes_string(y = "linear_slope", x = x_var), inherit.aes = FALSE)
   }
 
-
[…]

### 2021-01-06 R/plan.R

@@ -86,16 +86,20 @@ plan <- drake_plan(
       .names = paste0(c("bm_std", "log_bm_std", "rich_std", "log_rich_std"), "_st_decrease_increase")
     )
   ),
-
   model = target(
     compute_my_lm_vs_net_model(
       .df = filter(my_bm_net_group, !is.na(protocol_type)),
-      var_to_group = grouped_var),
+      var_to_group = grouped_var,
+      x = ifelse("bm_slope" %in% colnames(my_bm_net_group), "bm_slope", "rich_slope")
+      ),
     transform = cross(
-      my_bm_net_group = list(bm_net_group_median, bm_net_group_f3y,
-	log_bm_net_group_median, log_bm_net_group_f3y),
+      my_bm_net_group = list(
+	bm_net_group_median, bm_net_group_f3y,
+	log_bm_net_group_median, log_bm_net_group_f3y,
+	rich_net_group_median, rich_net_group_f3y,
+	log_rich_net_group_median, log_rich_net_group_f3y),
       grouped_var = list(c("variable"), c("variable", "protocol_type")),
-      .names = model_type_var(add_protocol = TRUE)
+      .names = model_type_var(add_protocol = TRUE, add_rich = TRUE) #add rich
     )
     ),
   vif = target(
@@ -103,7 +107,7 @@ plan <- drake_plan(
       all_of(tidyselect::vars_select(names(model), starts_with("mod")))),
     transform = map(model,
       .names = paste0("vif_",
-	model_type_var(cut_prefix = TRUE, add_protocol = TRUE)
+	model_type_var(cut_prefix = TRUE, add_protocol = TRUE, add_rich = TRUE)
       )
     )
     ),
@@ -111,7 +115,7 @@ plan <- drake_plan(
     model_summary(model),
     transform = map(model,
     .names = paste0("summary_",
-	model_type_var(cut_prefix = TRUE, add_protocol = TRUE)
+	model_type_var(cut_prefix = TRUE, add_protocol = TRUE, add_rich = TRUE)
 	)
     )
     ),
@@ -119,11 +123,10 @@ plan <- drake_plan(
     get_mod_pred(model_summary),
     transform = map(model_summary,
     .names = paste0("pred_",
-	model_type_var(cut_prefix = TRUE, add_protocol = TRUE)
+	model_type_var(cut_prefix = TRUE, add_protocol = TRUE, add_rich = TRUE)
 	)
     )
     ),
-
 
   bm_group = target(
[…]

### 2021-01-06 R/variable_shortcut.R

@@ -25,7 +25,10 @@ get_species <- function(node_list) {
 
 }
 
-model_type_var <- function(cut_prefix = FALSE, add_protocol = FALSE) {
+model_type_var <- function(
+  cut_prefix = FALSE,
+  add_protocol = FALSE,
+  add_rich = FALSE) {
 
   x <- c("model_bm", "model_bm_f3y", "model_log_bm", "model_log_bm_f3y")
 
@@ -33,10 +36,15 @@ model_type_var <- function(cut_prefix = FALSE, add_protocol = FALSE) {
     x %<>% str_remove_all("model_")
   }
 
+  if (add_rich) {
+    x <- c(x, str_replace(x, "bm", "rich"))
+  }
+
   if (add_protocol) {
     x <- map(c("", "_by_protocol"), ~paste0(x, .x)) %>%
       unlist
   }
+
   return(x)
 }
 

### 2021-01-06 make.R

@@ -23,3 +23,33 @@ drake::vis_drake_graph(plan)
 # Load your targets back into your session with loadd() and readd().
 plan
 print(plan, n = 40)
+loadd(my_bm_net_group)
+rep(list(c(2,6)),8)
+loadd(log_rich_net_group_f3y, log_bm_net_group_f3y)
+loadd(model_log_rich_f3y)
+
+debugonce(get_model_plot_from_signif_term)
+make(plan)
+
+debugonce(from_term_to_predict_term)
+
+term_model$indiv_term
+term_model$predict_term
+
+filter(model_test, variable == "A")
+filter(term_model, variable == "A")
+
+loadd(pred_plot_signif_log_rich)
+loadd(pred_plot_signif)
+pred_plot_signif$pred[[3]]
+pred_plot_signif$data[[3]]
+pred_plot_signif$predict_term[[3]]
+pred_plot_signif_log_rich$predict_term[[3]]
+plot_final_model(
+  ggpred = pred_plot_signif_log_rich$pred[[3]],
+  rawdata = pred_plot_signif_log_rich$data[[3]],
+  facet = FALSE,
+  std_error = TRUE)
+pred_plot_signif_log_rich$myplot[[1]]
+pred_plot_signif_log_rich$pred[[7]]
+select(pred_plot_signif_log_rich, variable, model_formula, mod)

### 2021-01-07 report.Rmd
Add report and fix plot of model prediction

@@
 
-### Summary
-
-- Lien entre dynamique du réseau et de biomasse signicatif pour tous sauf la
-  connectance.
-  - Pour la connectance, le lien est dépendant de la biomasse
-- Effect of dis/assembly for connectance, avg trophic level, weighted
-  connectance
-- La dynamique du réseau n'est pas affecté par la biomasse de la
-  communauté (effet biomasse non significatif)
-- Il y a un effet biomasse qui est dépendant de dis/assembly.
+### Results
 
@@
 - Weighted connectance:
-  - increases when biomass decreases in little communities
-  - decreases when biomass decreases in big communities
+  - increases (more even flux distribution) when biomass decreases in little communities
+  - decreases (more skewed flux distribution) when biomass decreases in big communities
   - decreases when biomass increases
+
+### Summary of result
+
+- There are a significant link between the dynamics of community biomass and the
+  dynamics of community structure for all the variables: species richness,
+  average trophic level, connectance and weighted connectance.
+
+- We found that the link between network temporal dynamics and biomass temporal
+  dynamics change according if the community loses or gain biomass, for all
+  variables.
+
+- We found that the biomass of the community at the beginning of the temporal
+  series, i.e. community size, had an effect on the link between network
+  dynamics and biomass expect for species richness. We also found that the
+  effect of biomass was stronger in communities losing biomass for connectance and
+  weighted connectance but stronger in communities gaining biomass for average
+  trophic level
+
+### Answer to research questions
+
+- Lost and gain of biomass result in different network structure dynamics,
+  suggesting that the two processes are not symmetric.
+- The effect of community size suggests that the architecture of the community
+  in terms of species richness, number of piscivorous species, plays a role in
+  its dynamics
 
@@
     disparition of species already in the community. Thus, the colonization
-    process
+    process needs element exterior to the community.  
   - second explanation: when biomass increases, competitive interactions may prevent the increase in
@@
   - In little communities, few piscivorous species and so loss of biomass do not
-    change the foodwebs because fish-resource links are quite redondant.
+    change the foodwebs that much because fish-resource links are quite redondant.
     - there is a positive correlation between nb of pisc node and biomass.
@@
     - In big communities, the highest number can make the absence of such an effect 
-  - When Biomass increases, the number of predator nodes increases (especially
-    in little communities), and ...
-    the biomass
+  - When Biomass increases:
+    - but species richness and number of nodes increases and gini coefficient
+      does not move: so it is ninly due to the number of species
+    - Gini decrease (more even link distribution) and number of species
+      decrease also, so weighted_connectance should increase (it is what we see
+      for low biomass communities). No idea for the difference between little
+      and big communites.
 
@@
 library(vegan)
-myload(nmds, com_mat,envir = environment(), dir = get_mypath("data"))
+myload(com_mat, envir = environment(), dir = get_mypath("data"))
 
@@
 
-```{r, fig.width = 8}
+```{r, fig.width = 10, fig.height = 8}
 diverging_pal <- c("#67001f", "#b2182b", "#d6604d", "#f4a582", "#fddbc7",
@@
 title("Color = ; Size of points = biomass")
+```
+
+## Species richness dynamics and network dynamics
+
+```{r}
+loadd(model_log_rich_f3y_table_medium)
+```
+
+```{r}
+model_log_rich_f3y_table_medium[["anova_table"]] %>% 
+  filter(variable %in% get_com_str_var(all = FALSE)) %>%
+  kable(., booktabs = TRUE,
+    caption = 
+      paste0(
+      "ANOVA table for the model: dN =",
+      "dB + B + dB*B + Inc*B + dB*Inc*B."
+    )
+  ) %>%
+  kable_styling(latex_options =c("scale_down", "stripped")) %>%
+  collapse_rows(columns = 1, valign = "top")
+```
+
+```{r}
+loadd(pred_plot_signif_log_rich)
+pred_plot_signif_log_rich_com <- pred_plot_signif_log_rich %>%
+  filter(variable %in% get_com_str_var())
+legend_signif <- get_legend(
+  pred_plot_signif_log_rich_com$myplot[[1]] +
+    theme(legend.position = "bottom")
+)
+pred_plot_signif_log_rich_com$myplot %<>% map(., ~.x + theme(legend.position = "none"))
+top <- plot_grid(
+  plotlist = pred_plot_signif_log_rich_com$myplot,
+  labels = pred_plot_signif_log_rich_com$variable
+)
+plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
 ```

### 2021-01-07 R/plan.R

@@ -218,7 +218,5 @@ plan <- drake_plan(
     variable = NULL
     ),
 
-
-
 )
 

### 2021-01-07 make.R

@@ -23,33 +23,16 @@ drake::vis_drake_graph(plan)
 # Load your targets back into your session with loadd() and readd().
 plan
 print(plan, n = 40)
-loadd(my_bm_net_group)
-rep(list(c(2,6)),8)
-loadd(log_rich_net_group_f3y, log_bm_net_group_f3y)
-loadd(model_log_rich_f3y)
-
-debugonce(get_model_plot_from_signif_term)
-make(plan)
-
-debugonce(from_term_to_predict_term)
-
-term_model$indiv_term
-term_model$predict_term
-
-filter(model_test, variable == "A")
-filter(term_model, variable == "A")
 
 loadd(pred_plot_signif_log_rich)
 loadd(pred_plot_signif)
-pred_plot_signif$pred[[3]]
-pred_plot_signif$data[[3]]
-pred_plot_signif$predict_term[[3]]
-pred_plot_signif_log_rich$predict_term[[3]]
+pred_plot_signif[4, ]$pred
+pred_plot_signif[3, ]$predict_term
+pred_plot_signif[4, ]$predict_term
+pred_plot_signif[4, ]$myplot
+
+debugonce(plot_final_model)
 plot_final_model(
-  ggpred = pred_plot_signif_log_rich$pred[[3]],
-  rawdata = pred_plot_signif_log_rich$data[[3]],
-  facet = FALSE,
-  std_error = TRUE)
-pred_plot_signif_log_rich$myplot[[1]]
-pred_plot_signif_log_rich$pred[[7]]
-select(pred_plot_signif_log_rich, variable, model_formula, mod)
+  rawdata = pred_plot_signif[4, ]$data[[1]],
+  ggpred = pred_plot_signif[4, ]$pred[[1]]
+)

### 2021-01-13 report.Rmd
More generic method to analyze data

@@
 
-## State of the art
+## Abstract
 
-- Report of community biomass (or number of individual) collapses in many
-  ecosystems
-- Modification of community are linked to modification in network structure 
-- Studies have been interested in how network assembles or disassembles
-  themselves.
-- However, the lack of availability of such empirical dataset have prevented the
-answering to this question.
+Determine how community structure will respond to ongoing change remains an ongoing
+challenge. Studies reported strong temporal trends in community biomass, notably
+strong decline in insects and vertebrate populations.
 
-- Questions:
-  1. Is a decrease or a increase in biomass related to a network
-     structure modification?
-     1.1 Is a contant decrease/increase in biomass correspond the same dynamic
-     in network? Or there are non linear dynamics ?
-  2. Are assembly and disassembly of networks symmetric processes?
+However, those studies says nothing about how empirical findings about how
+different aspects of community structure such as species richness react
+to a change in community biomass.
+
+Ecological theory might provide insight on how community structure varies
+according to biomass. Especially BEF predicts a positive link between species richness and
+community biomass especially in grassland.
+
+However, communities used in BEF experiments might not be relevant to get
+insight about what happens in natural settings. Firstly there are statics, i.e.
+not temporal. Secondly, community composition are set to randomly and thus do
+not reflect real perturbations which do not affect communities randomly. 
+(to be fair one could argue that random communities can mimic an average outcome
+over a set of possible perturbations, as perturbation 1 would cause extinction of species
+C, perturbation 2 for species A, etc...).
+
+Overall, we miss empirical findings about the link between biomass and
+community structure.
+
+We investigated the link between the temporal dynamics of community biomass at one side and 
+species richness, connectance and average trophic level at another side using a
+1995-2018 standardized monitoring of fish communities. We questionned the shape
+of the link between both temporal trends.  More specifically, we questionned if
+(2) the link between foodweb structure and biomass dynamics vary between growing
+and shrinking communities, and if the size of the community can modulate this
+response.
+
+We found significant positive relationships the dynamics of community biomass
+and the dynamics of species richness, average trophic level and connectance but
+a negative one for weighted connectance. We also found this relationship was
+different depending on if the community biomass was growing or shrinking through
+time for all variables, suggesting that assembly processes such as colonization
+processes might.
 
@@
   - decreases a lot in time when biomass decreases
-  - increases slightly in time when biomass increases
+  - increases slightly in time when biomass increases (immigration debt)
   - No effect of community size! (same for the number of nodes)
@@
     process needs element exterior to the community.
+    - Immigration debt: (might be relevant if low availability of new species)
   - second explanation: when biomass increases, competitive interactions may prevent the increase in
@@
 
+- Connectance (fish-fish interactions):
+  - Globally positive relationship
+  - when biomass increases: communities gains higher trophic level that might
+    explain this relationship (but species richness increase as well)
+  - When biomass decreases: communities
+
 - Weighted connectance:
@@
 pred_plot_signif_com <- pred_plot_signif %>%
-  filter(variable %in% get_com_str_var())
+  filter(variable %in% c(get_com_str_var(), "ct_ff"))
 legend_signif <- get_legend(
@@
   na.omit() %>%
-  select(bm_std, avg_IS, l, ld, m, A, gini, log_bm_std, connectance, log_rich_std, rich_std, w_trph_lvl_avg,
+  select(bm_std, avg_IS, l, ld, m, A, gini, log_bm_std, connectance, ct_ff, rich_std, w_trph_lvl_avg,
     weighted_connectance, nbnode_std, nb_pisc_node_std, prop_pisc_node) %>%
@@
   corrplot::corrplot(corr = .)
-
-summary_var_f3y %>%
-  ggplot(aes(x = bm_std, y = prop_pisc_node)) +
-  geom_point() 
-#summary_var_f3y %>%
-  #ggplot(aes(x = log_bm_std, y = nb_pisc_node_std))+
-  #geom_point() 
-#summary_var_f3y %>%
-  #ggplot(aes(x = , y = nb_pisc_node_std))+
-  #geom_point() 
 ```

### 2021-01-13 make.R

@@ -24,15 +24,54 @@ drake::vis_drake_graph(plan)
 plan
 print(plan, n = 40)
 
-loadd(pred_plot_signif_log_rich)
-loadd(pred_plot_signif)
-pred_plot_signif[4, ]$pred
-pred_plot_signif[3, ]$predict_term
-pred_plot_signif[4, ]$predict_term
-pred_plot_signif[4, ]$myplot
+loadd(rigal_classification)
+loadd(full_data2)
+test <- get_station_com_summary(
+  .data = full_data2,
+  myvar = c("bm_std", "log_bm_std", "rich_std", "log_rich_std"),
+  var_cat = "com", group = FALSE, summary_type = "median")
+test <- get_station_com_summary(
+  .data = full_data2,
+  myvar = c("bm_std", "log_bm_std", "rich_std", "log_rich_std"),
+  var_cat = "com", group = FALSE, summary_type = "first_3_year")
 
-debugonce(plot_final_model)
-plot_final_model(
-  rawdata = pred_plot_signif[4, ]$data[[1]],
-  ggpred = pred_plot_signif[4, ]$pred[[1]]
-)
+loadd(rich_vs_net_trends, stream_group, biomass_group, bm_vs_net_trends, bm_std_st_decrease_increase, rich_std_st_decrease_increase)
+test2 <- add_stream_bm_caract_to_model(
+  bm_vs_network_df = bm_vs_net_trends,
+  stream_caract = NULL,
+  bm_caract = filter(biomass_group, bm_var == "bm_std",
+    group_type == "median", summary_type == "first_3_year"),
+  bm_group_var = "bm_std", group_type_caract = "median", 
+  bm_summary_type = "first_3_year") %>% 
+filter(station %in% bm_std_st_decrease_increase$station)
+
+add_stream_bm_caract_to_model(bm_vs_network_df = rich_vs_net_trends,
+    stream_caract = stream_group, bm_caract = biomass_group,
+    bm_group_var = "bm_std", group_type_caract = "median", bm_summary_type
+= "first_3_year") %>%
+    filter(station %in% rich_std_st_decrease_increase$station)
+
+
+filter(biomass_group, bm_var == "bm_std", group_type == "median", summary_type ==
+  "first_3_year")
+
+
+
+loadd(summary_var_f3y, rich_vs_net_trends, bm_net_group_f3y)
+left_join(rich_vs_net_trends, summary_var_f3y, by = "station")
+
[…]

### 2021-01-19 report.Rmd
prediction plot and anova table works

@@
 #https://stackoverflow.com/questions/44457243/regression-tables-in-r-markdown-rmarkdown-html-pdf
-loadd(model_log_bm_f3y_table_medium)
-model_log_bm_f3y_table_medium[["reg_table"]] %>% 
-  filter(variable %in% get_com_str_var(all = FALSE)) %>%
-  kable(.,
-    booktabs = TRUE, 
-    caption = 
-      paste0(
-      "Regression table for the model: dN =",
-      "dB + B + dB*B + Inc*B + dB*Inc*B."
-    )) %>% 
-  kable_styling(latex_options =c("scale_down", "stripped")) %>%
-  collapse_rows(columns = 1, valign = "top")
+#loadd(model_log_bm_f3y_table_medium)
+#model_log_bm_f3y_table_medium[["reg_table"]] %>% 
+  #filter(y %in% get_com_str_var(all = FALSE)) %>%
+  #kable(.,
+    #booktabs = TRUE, 
+    #caption = 
+      #paste0(
+      #"Regression table for the model: dN =",
+      #"dB + B + dB*B + Inc*B + dB*Inc*B."
+    #)) %>% 
+  #kable_styling(latex_options =c("scale_down", "stripped")) %>%
+  #collapse_rows(columns = 1, valign = "top")
 ```
@@
 ```{r}
-model_log_bm_f3y_table_medium[["anova_table"]] %>% 
-  filter(variable %in% get_com_str_var(all = FALSE)) %>%
-  kable(., booktabs = TRUE,
-    caption = 
-      paste0(
-      "ANOVA table for the model: dN =",
-      "dB + B + dB*B + Inc*B + dB*Inc*B."
-    )
-  ) %>%
-  kable_styling(latex_options =c("scale_down", "stripped")) %>%
-  collapse_rows(columns = 1, valign = "top")
+#model_log_bm_f3y_table_medium[["anova_table"]] %>% 
+  #filter(variable %in% get_com_str_var(all = FALSE)) %>%
+  #kable(., booktabs = TRUE,
+    #caption = 
+      #paste0(
+      #"ANOVA table for the model: dN =",
+      #"dB + B + dB*B + Inc*B + dB*Inc*B."
+    #)
+  #) %>%
+  #kable_styling(latex_options =c("scale_down", "stripped")) %>%
+  #collapse_rows(columns = 1, valign = "top")
 ```
@@
 ```{r}
-loadd(pred_plot_signif)
-pred_plot_signif_com <- pred_plot_signif %>%
-  filter(variable %in% c(get_com_str_var(), "ct_ff"))
+loadd(predict_plot)
+pred_plot_signif_com <- predict_plot %>%
+  filter(
+    y %in% c(get_com_str_var(), "ct_ff", "log_rich_std"),
+    x == "log_bm_std"
+  )
 legend_signif <- get_legend(
-  pred_plot_signif_com$myplot[[1]] +
+  pred_plot_signif_com$pred_plot[[1]] +
     theme(legend.position = "bottom")
 )
-pred_plot_signif_com$myplot %<>% map(., ~.x + theme(legend.position = "none"))
+pred_plot_signif_com$pred_plot %<>% map(., ~.x + theme(legend.position = "none"))
 top <- plot_grid(
-  plotlist = pred_plot_signif_com$myplot,
-  labels = pred_plot_signif_com$variable
+  plotlist = pred_plot_signif_com$pred_plot,
+  labels = pred_plot_signif_com$y, nrow = 1
 )
-plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
+pred_plot1 <- plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
+```
+
+```{r}
+pred_plot_rich <- predict_plot %>%
+  filter( y %in% c(get_com_str_var(), "ct_ff"), x == "log_rich_std") %>%
+  filter(!y %in% "rich_std")
+legend_signif <- get_legend(
+  pred_plot_rich$pred_plot[[1]] +
+    theme(legend.position = "bottom")
+)
+pred_plot_rich$pred_plot %<>% map(., ~.x + theme(legend.position = "none"))
+top <- plot_grid(
+  plotlist = pred_plot_rich$pred_plot,
+  labels = pred_plot_rich$y
+)
+pred_plot2 <- plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
+```
+
+```{r}
+pred_plot_other <- predict_plot %>%
+  filter( y %in% c("ct_ff", "w_trph_lvl_avg"), x == c("ct_ff", "w_trph_lvl_avg"))
+legend_signif <- get_legend(
+  pred_plot_other$pred_plot[[1]] +
+    theme(legend.position = "bottom")
+)
+pred_plot_other$pred_plot %<>% map(., ~.x + theme(legend.position = "none"))
+top <- plot_grid(
+  plotlist = pred_plot_other$pred_plot,
+  labels = pred_plot_other$y
+)
+pred_plot3 <- plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
+```
+
+```{r, fig.dim = c(12, 8)}
+plot_grid(
+  pred_plot1, plot_grid(pred_plot2, pred_plot3, ncol = 2),
+  nrow = 2
+
+)
+```
+
+```{r}
+loadd(model_log_bm_f3y_table_medium)
+model_log_bm_f3y_table_medium[["anova_table"]] %>%
+  filter( y %in% c(get_com_str_var(), "ct_ff", "log_rich_std")) %>%
+  kable(., booktabs = TRUE,
+    caption = 
+      paste0(
+      "ANOVA table for the model: dN =",
+      "dB + B + dB*B + Inc*B + dB*Inc*B."
+    )
+  ) %>%
+  kable_styling(latex_options =c("scale_down", "stripped")) %>%
+  collapse_rows(columns = 1, valign = "top")
 ```
@@
 
+```{r pred-other-com, fig.dim = c(12, 10)}
+pred_plot_signif <- predict_plot %>%
+  filter(!y %in% c(get_com_str_var(), "ct_ff"), x == "log_bm_std")
+legend_signif2 <- get_legend(
+  pred_plot_signif_com$pred_plot[[1]] + theme(legend.position = "bottom")
+)
+pred_plot_signif$pred_plot %<>% map(., ~.x + theme(legend.position = "none"))
+top2 <- plot_grid(
+  plotlist = pred_plot_signif$pred_plot,
+  labels = pred_plot_signif$y
+)
+plot_grid(top2, legend_signif2, nrow = 2, rel_heights = c(1, .1))
+```
+
 ```{r}
 model_log_bm_f3y_table_medium[["anova_table"]] %>% 
-  filter(!variable %in% get_com_str_var(all = FALSE)) %>%
+  filter(!y %in% get_com_str_var(all = FALSE)) %>%
   kable(., booktabs = TRUE,
@@
   collapse_rows(columns = 1, valign = "top")
-
-```
-
-```{r pred-other-com, fig.dim = c(12, 10)}
-plot_signif <- pred_plot_signif %>%
-  filter(!variable %in% get_com_str_var())
-legend_signif <- get_legend(
-  plot_signif$myplot[[1]] +
-    theme(legend.position = "bottom")
-)
-plot_signif$myplot %<>% map(., ~.x + theme(legend.position = "none"))
-top_signif_other <- plot_grid(
-  plotlist = plot_signif$myplot,
-  labels = plot_signif$variable
-)
-plot_grid(top_signif_other, legend_signif, nrow = 2, rel_heights = c(1, .1))
 ```
@@
 
+```{r setup,  eval = TRUE}
+knitr::opts_chunk$set(eval=FALSE)
+```
+
 ## Temporal series of networks
@@
 
-- Station ploted: `r st_network_to_plot`
+- Station ploted: `r #st_network_to_plot`
 

### 2021-01-19 R/data_frame_manipulation.R

@@ -373,14 +373,7 @@ get_vif <- function (.df = NULL, model_cols = c("mod1", "mod2", "mod3", "mod5"))
     filter(check) %>%
     select(-check)
 
-  if ("protocol_type" %in% names(.df)) {
-    selected_var <- c("variable", "protocol_type", "model_type", "vif")
-  } else {
-    selected_var <- c("variable", "model_type", "vif")
-  }
-
   .df %<>% 
-    select_at(.vars = vars(all_of(selected_var))) %>%
     filter(!any(class(vif) %in% "try-error")) %>%
     unnest(cols = vif)
   return(.df)

### 2021-01-19 R/get_model_plot.R

@@ -266,10 +266,11 @@ get_ggpredict_term_from_anova <- function (aov_tab = NULL, bound = NULL) {
     #tmp$predict_term
     # Get x var to get bounds 
     term <- aov_tab$term
-    x_var <-  term[!str_detect(term, "_slope|Residuals|inc_f")]
+    x_var_slope <-  term[str_ends(term, "_slope")]
+    x_var <- str_remove(x_var_slope, "_slope")
     min_max <- bound[[x_var]]
 
-    ggpred_tmp <- paste0(x_var, "_slope", " [",min_max[1],", -0.000000001, 0.000000001, ", min_max[2], "]")
+    ggpred_tmp <- paste0(x_var_slope, " [",min_max[1],", -0.000000001, 0.000000001, ", min_max[2], "]")
 
     # If no signicant effect, return x slope, may be to change
     if (str_length(pred_term) == 0) {
@@ -283,7 +284,7 @@ get_ggpredict_term_from_anova <- function (aov_tab = NULL, bound = NULL) {
     if (any(!str_detect(pred_term, "inc_f|_slope"))) {
       tmp <- 
       ggpred_tmp <- c(ggpred_tmp,
-	paste0(pred_term[!str_detect(pred_term, "inc_f|_slope")], "[quart2]")
+	paste0(pred_term[!str_detect(pred_term, "inc_f|_slope")], " [quart2]")
       )
     }
 

### 2021-01-19 R/variable_shortcut.R

@@ -50,11 +50,11 @@ model_type_var <- function(
 
 get_com_str_var <- function (all = FALSE) { 
   
-  x <- c("connectance", "w_trph_lvl_avg",
-  "weighted_connectance", "rich_std")
+  x <- c("ct_ff", "w_trph_lvl_avg", #"connectance" ,"weighted_connectance",
+   "rich_std")
 
   if (all) {
-    x <- c(x, "richness", "log_rich_std", "nbnode_std" ,"nb_pisc_rich_std", "nb_pisc_node_std", "prop_pisc_node", "prop_pisc_rich", "l", "ld", "m", "A", "avg_IS", "gini", "ct_ff", "l_ff", "ld_ff")
+    x <- c(x, "connectance", "weighted_connectance", "richness", "log_rich_std", "nbnode_std" ,"nb_pisc_rich_std", "nb_pisc_node_std", "prop_pisc_node", "prop_pisc_rich", "l", "ld", "m", "A", "avg_IS", "gini", "ct_ff", "l_ff", "ld_ff")
   }
   return(x)
 }

### 2021-01-20 report.Rmd
Add eveness to the analysis

@@
 
-```{r, cache = FALSE}
-loadd(log_bm_net_group_f3y, model_log_bm_f3y,
-  summary_log_bm_f3y, vif_log_bm_f3y)
-#loadd(bm_net_group_median, bm_vs_net_trends)
-loadd(bm_net_group_f3y)
-loadd(bm_net_group_f3y)
-loadd(rich_vs_net_trends)
-
-#compute_my_lm_vs_net_model(
-      #.df = filter(my_bm_net_group, !is.na(protocol_type)),
-      #var_to_group = "variable"
-#)
-```
-
-#### All protocol
-
-```{r, eval = TRUE}
-#https://stackoverflow.com/questions/44457243/regression-tables-in-r-markdown-rmarkdown-html-pdf
-#loadd(model_log_bm_f3y_table_medium)
-#model_log_bm_f3y_table_medium[["reg_table"]] %>% 
-  #filter(y %in% get_com_str_var(all = FALSE)) %>%
-  #kable(.,
-    #booktabs = TRUE, 
-    #caption = 
-      #paste0(
-      #"Regression table for the model: dN =",
-      #"dB + B + dB*B + Inc*B + dB*Inc*B."
-    #)) %>% 
-  #kable_styling(latex_options =c("scale_down", "stripped")) %>%
-  #collapse_rows(columns = 1, valign = "top")
-```
-
-```{r}
-#model_log_bm_f3y_table_medium[["anova_table"]] %>% 
-  #filter(variable %in% get_com_str_var(all = FALSE)) %>%
-  #kable(., booktabs = TRUE,
-    #caption = 
-      #paste0(
-      #"ANOVA table for the model: dN =",
-      #"dB + B + dB*B + Inc*B + dB*Inc*B."
-    #)
-  #) %>%
-  #kable_styling(latex_options =c("scale_down", "stripped")) %>%
-  #collapse_rows(columns = 1, valign = "top")
-```
-
 ### Results
@@
   filter(
-    y %in% c(get_com_str_var(), "ct_ff", "log_rich_std"),
+    y %in% c(get_com_str_var(), "log_rich_std"),
     x == "log_bm_std"
@@
 pred_plot_rich <- predict_plot %>%
-  filter( y %in% c(get_com_str_var(), "ct_ff"), x == "log_rich_std") %>%
+  filter( y %in% c(get_com_str_var(), "bm_std", "log_bm_std"), x == "log_rich_std") %>%
   filter(!y %in% "rich_std")

### 2021-01-20 R/get_data.R

@@ -8,8 +8,8 @@ get_community_data <- function (
 
   load(path, envir = environment())
 
-  com <- community_metrics %>% 
-    dplyr::select(opcod, biomass, richness) %>%
+  com <- community_metrics %>%
+    dplyr::select(opcod, biomass, richness, pielou) %>%
     dplyr::filter(!is.na(opcod))
 
   return(com)
@@ -28,9 +28,8 @@ get_community_analysis_data <- function (
     dplyr::ungroup() %>%
     dplyr::left_join(dplyr::select(op, opcod, surface), by = "opcod") %>%
     dplyr::mutate(
-      nind = nind / surface, 
-      length = length / surface, 
-      biomass = biomass / surface
+      nind_std = nind / surface, 
+      bm_std = biomass / surface
     )
   return(com_std)
 }

### 2021-01-20 R/statistical_model.R

@@ -13,7 +13,7 @@ get_lm_station <- function (.data = NULL, var_names = NULL, rhs = NULL) {
   for (i in seq_along(var_names)) {
   
   .data[[var_names[i]]] <-
-    purrr::map(.data$data, compute_linear_model, formulas = paste0(var_names[i], rhs))
+    purrr::map(.data$data, ~try(compute_linear_model(.x, formulas = paste0(var_names[i], rhs))))
   
   }
   # Coefficients

### 2021-01-20 R/variable_shortcut.R

@@ -49,14 +49,14 @@ model_type_var <- function(
 }
 
 get_com_str_var <- function (all = FALSE) { 
-  
-  x <- c("ct_ff", "w_trph_lvl_avg", #"connectance" ,"weighted_connectance",
-   "rich_std")
 
-  if (all) {
-    x <- c(x, "connectance", "weighted_connectance", "richness", "log_rich_std", "nbnode_std" ,"nb_pisc_rich_std", "nb_pisc_node_std", "prop_pisc_node", "prop_pisc_rich", "l", "ld", "m", "A", "avg_IS", "gini", "ct_ff", "l_ff", "ld_ff")
-  }
-  return(x)
+x <- c("ct_ff", "w_trph_lvl_avg", #"connectance" ,"weighted_connectance",
+ "rich_std")
+
+if (all) {
+  x <- c(x, "connectance", "weighted_connectance", "richness", "log_rich_std", "nbnode_std" ,"nb_pisc_rich_std", "nb_pisc_node_std", "prop_pisc_node", "prop_pisc_rich", "l", "ld", "m", "A", "avg_IS", "gini", "ct_ff", "l_ff", "ld_ff", "piel_nind", "piel_bm")
+}
+return(x)
 }
 
 get_model_terms <- function ( ) {

### 2021-01-20 make.R

@@ -16,22 +16,6 @@ drake::make(plan)
 drake::vis_drake_graph(plan)
 
 #make(plan, parallelism = "future", jobs = 3)
-loadd(model_summary)
-loadd(summary_table)
-
-
-summary_table %>% filter(x == "log_bm_std") %>%
- select(-x, -covar, -model, -model_obj) %>%
-
- list(reg_table = map_dfr(.$reg_table, rbind),
-   anova_table = map_dfr(.$anova_table, rbind)
- )
-
-get_table_from_summary(
-    .data = model_summary,
-    model =  "mod_medium_bm",
-    variable = NULL
-  )
 
 # If you do not change any code or data,
 # subsequent make()'s do not build targets.
@@ -40,6 +24,24 @@ get_table_from_summary(
 plan
 print(plan, n = 40)
 
-loadd(model)
-loadd(predict_plot, summary_table, predict_table, slope_x_bound)
+loadd(monotonous_data)
+loadd(monotonous_data)
+loadd(full_data2)
+debugonce(get_lm_station)
+test <- get_lm_station(.data = monotonous_data, 
+    var_name = c(get_biomass_var(), get_com_str_var(all = TRUE)),
+    rhs = " ~ nb_year")
 
+install.packages("betapart")
+library(betapart)
+
+
+  #com_test <- left_join(com, select(.op, opcod, surface), by = "opcod")
+
+  mat <- compute_com_mat(.op = .op, com = com, variable = variable,
+    summarise_by_station = summarise_by_station)
+
+  cbind(mat[, 1:2], compute_pielou_simpson(.data = mat[, 2:ncol(mat)])) %>%
+    as_tibble
+
+}

### 2021-01-22 report.Rmd
Get betapart betadiversity
Plot prediction with lm containing only signif terms

@@
 output:
-  html_document
+  prettydoc::html_pretty:
+    theme: cayman
+    highlight: github
+    math: katex
 ---
@@
 )
-```
-
-```{r}
-loadd(p_bm_vs_bm_slope)
-p_bm_vs_bm_slope
-```
-
-```{r}
-loadd(p_hist_med_bm)
-p_hist_med_bm
 ```
@@
 ```{r}
-loadd(predict_plot)
-pred_plot_signif_com <- predict_plot %>%
+loadd(predict_plot2)
+pred_plot_signif_com <- predict_plot2 %>%
   filter(
-    y %in% c(get_com_str_var(), "log_rich_std"),
+    y %in% c(get_com_str_var(), "log_rich_std", "piel_nind", "piel_bm"),
     x == "log_bm_std"
@@
   plotlist = pred_plot_signif_com$pred_plot,
-  labels = pred_plot_signif_com$y, nrow = 1
+  labels = pred_plot_signif_com$y, nrow = 2
 )
@@
 ```{r}
-pred_plot_rich <- predict_plot %>%
-  filter( y %in% c(get_com_str_var(), "bm_std", "log_bm_std"), x == "log_rich_std") %>%
+pred_plot_rich <- predict_plot2 %>%
+  filter( y %in% c(get_com_str_var(), "bm_std", "log_bm_std", "piel_nind", "piel_bm"), x == "log_rich_std") %>%
   filter(!y %in% "rich_std")
@@
 ```{r}
-pred_plot_other <- predict_plot %>%
-  filter( y %in% c("ct_ff", "w_trph_lvl_avg"), x == c("ct_ff", "w_trph_lvl_avg"))
+pred_plot_other <- predict_plot2 %>%
+  filter( y %in% c("ct_ff", "w_trph_lvl_avg"), x %in% c("ct_ff", "w_trph_lvl_avg"))
 legend_signif <- get_legend(
@@
   plotlist = pred_plot_other$pred_plot,
-  labels = pred_plot_other$y
+  labels = pred_plot_other$y, nrow = 2
 )
@@
 
-```{r, fig.dim = c(12, 8)}
+```{r, fig.dim = c(12, 12)}
 plot_grid(
-  pred_plot1, plot_grid(pred_plot2, pred_plot3, ncol = 2),
+  pred_plot1, plot_grid(pred_plot2, pred_plot3, ncol = 2, rel_widths = c(.75, 1)),
   nrow = 2
+)
+```
 
-)
+```{r, fig.dim = c(10, 5)}
+loadd(betapart_bin, rigal_classification, st_mono_trends_combined_list)
+
+mask <- st_mono_trends_combined_list$variable == "log_bm_std"
+xdata <- rigal_classification %>%
+  filter(variable == "log_bm_std") %>%
+  unnest(classif) %>%
+  filter(station %in% st_mono_trends_combined_list[mask, ]$station[[1]])
+
+beta_xdata <- xdata %>%
+  select(station, linear_slope) %>%
+  left_join(betapart_bin, by = "station")
+
+beta_xdata %>%
+  pivot_longer(cols = c(beta.SIM:beta.SOR), names_to = "type", values_to = "beta") %>%
+  ggplot(aes(x = linear_slope, y = beta)) +
+  geom_point() +
+  facet_grid(cols = vars(type)) +
+  labs(x = "Slope of Log biomass (% biomass by year)", y = "Beta-diversity")
+
+```
+
+```{r}
+# Rich and rich slope
+loadd(summary_var_f3y)
+
+mask <- st_mono_trends_combined_list$variable == "richness"
+xdata <- rigal_classification %>%
+  filter(variable == "richness") %>%
+  unnest(classif) %>%
+  filter(station %in% st_mono_trends_combined_list[mask, ]$station[[1]])
+
+xdata %>%
+  select(station, linear_slope) %>%
+  left_join(summary_var_f3y %>% select(station, richness), by = "station") %>%
+  ggplot(aes(x = linear_slope, y = richness)) +
+  geom_point() +
+  labs(x = "Slope of richness (year)", y = "richness")
+```
+
+```{r}
+#loadd(temporal_dynamics_plot)
 ```
@@
   select(bm_std, avg_IS, l, ld, m, A, gini, log_bm_std, connectance, ct_ff, rich_std, w_trph_lvl_avg,
-    weighted_connectance, nbnode_std, nb_pisc_node_std, prop_pisc_node) %>%
+    weighted_connectance, nbnode_std, nb_pisc_node_std, prop_pisc_node, piel_bm,
+    piel_nind) %>%
   cor() %>%
@@
 ```{r pred-other-com, fig.dim = c(12, 10)}
-pred_plot_signif <- predict_plot %>%
+pred_plot_signif <- predict_plot2 %>%
   filter(!y %in% c(get_com_str_var(), "ct_ff"), x == "log_bm_std")
@@
   collapse_rows(columns = 1, valign = "top")
-```
-
-```{r eval = FALSE}
-pred_plot_signif %>%
-  select(variable, data) %>%
-  unnest(data) %>%
-  ggplot(aes(x = bm_slope, y = linear_slope, color = bm)) +
-  geom_errorbar(
-    aes(xmin = bm_slope - bm_slope_strd_error, xmax = bm_slope +
-      bm_slope_strd_error), alpha = .3) +
-  geom_errorbar(
-    aes(ymin = linear_slope - linear_slope_strd_error,
-      ymax = linear_slope + linear_slope_strd_error),
-    alpha = .3)
 ```
@@
 ```
+
+```{r}
+loadd(p_bm_vs_bm_slope)
+p_bm_vs_bm_slope
+```
+
+```{r}
+loadd(p_hist_med_bm)
+p_hist_med_bm
+```

### 2021-01-22 R/get_model_plot.R

@@ -259,7 +259,8 @@ get_ggpredict_term_from_anova <- function (aov_tab = NULL, bound = NULL) {
       signif_term = paste(term, collapse = "+"),
       indiv_term = list(term)
       ) %>%
-    mutate(single_var_term = map(signif_term, get_lm_single_term),
+    mutate(
+      single_var_term = map(signif_term, get_lm_single_term),
       predict_term = map(single_var_term, from_term_to_predict_term)
     )
     pred_term <- tmp$predict_term[[1]]
@@ -290,6 +291,59 @@ get_ggpredict_term_from_anova <- function (aov_tab = NULL, bound = NULL) {
 
     return(ggpred_tmp)
     
+}
+
+compute_lm_from_signif_anova <- function (aov_tab = NULL , .df = NULL) {
+  tmp <- aov_tab %>%
+    mutate(signf = p.value <= 0.05) %>%
+    filter(signf) %>%
+    summarise(
+      signif_term = paste(term, collapse = "+"), 
+      indiv_term = list(term)
+      ) %>%
+    mutate(single_var_term = map(signif_term, get_lm_single_term))
+
+  #return(tmp)
+  
+
+  term <- aov_tab$term
+  x_var_slope <- term[str_ends(term, "_slope")]
+  x_var_slope_sym <- sym(x_var_slope)
+
+  .df %<>%
+    mutate(
+      increasing := {{x_var_slope_sym}} > 0,
+      inc_f = as.factor(increasing),
+      #"log_{{x_var_sym}}" := log({{x_var_sym}})
+    ) 
+
+  signif_term <- tmp$signif_term[[1]]
+
+  # If no significant term, put slope
+  if (str_length(signif_term) == 0 ) {
+    signif_term <- paste0(x_var_slope)
+  }
+  # If no slope in significant terms, i.e. put it
+  if (!str_detect(signif_term, "_slope")) {
+    signif_term <- paste0(x_var_slope, "+", signif_term)
+  }
+
+  # Get main effet if the interaction is significant 
+  single_terms <- tmp$indiv_term[[1]]
+  if (any(str_detect(single_terms, ":"))) {
+    # left term
+    left_term_inter <- map_chr(
+      single_terms[str_detect(single_terms, ":")],
+	~str_split(.x, ":")[[1]][1]
+      )
+    
+    signif_term <- paste0(left_term_inter, "+", signif_term, collapse = "+") 
+  }
+  #signif_term
+
[…]

### 2021-01-22 make.R

@@ -24,7 +24,12 @@ drake::vis_drake_graph(plan)
 plan
 print(plan, n = 40)
 
+#TODO check rigor of automatic plotting; all the conditions are respected?
 
 library(future)
 plan(multisession, workers = 3)
+
+#######################################
+#  Get the right term from new model  #
+#######################################
 

### 2021-01-27 report.Rmd
New model prediction plot + outline introduction

@@
 
-#theme_set(theme_cowplot())
+mytheme <- theme_cowplot() +
+background_grid()
+
+theme_set(mytheme)
+theme_get()
 ```
@@
 Ecological theory might provide insight on how community structure varies
-according to biomass. Especially BEF predicts a positive link between species richness and
-community biomass especially in grassland.
+according to biomass. Especially BEF predicts a positive link between species
+richness and community biomass especially in grassland.
 
@@
 
-## Links betwenn temporal dynamics
+# Introduction
+
+1. Option1 Global change -> change of biomass 
+   Option2 Ecological communities are dynamics + example
+
+2. Ecological communities often describe by their richness, biomass
+
+3. BEF
 
@@
 
-# Methods
-
-- Methodological choice:
-  - Dynamics of log of the biomass: put big and little station on the same scale
-    (% of biomass gained or lost per year)
-
-## The three model
-
-1. $dN = dB + dB \times B + dB^2 + dB^2 \times B$
-
-2. $dN = dB + B + dB \times B + Inc \times B + dB \times Inc \times B$
-
-3. $dN = dB + B + dB \times B + Inc + Inc \times dB + dB \times B \times Inc$
-
-with:
-- $dN$: temporal trend of network structure
-- $dB$: temporal trend of total (log) biomass
-- $B$: total median biomass or total biomass of the first three year
-- $Inc$: Is $dB > 0$?
-
-We kept the second model.
-
 # Results
 
-### Results
+- Species richness, Avg trophic level, connectance:
+  - increases when biomass increases while decreases when biomass decreases
+  - Avg trophic level: same for species richness  
+  - connectance:  decreases when richness increases while increases when
+    richness decreases (reverse sign compared to biomass)
 
-- Species richness:
-  - decreases a lot in time when biomass decreases
-  - increases slightly in time when biomass increases (immigration debt)
-  - No effect of community size! (same for the number of nodes)
+- Pielou (eveness) :
+  - Indiv: 
+    - do not varies with biomass temporal trends
+    - increases with increasing temporal trends of species richness
+  - Biomass: 
+    - increase when biomass decreases and decreases when biomass increases
+    - decreases when species richness decreases and increase when species
+      richness increases
 
-- Avg trophic level:
-  - decreases simultaneously with biomass decreases 
-  - increase simultaneously with biomass increases but increases less for bigger
-    communities
-  - meaning that biomass loss and gain are located in the highest trophic level
-    (except gain of biomass in biggest communities)
+- Connectance: positive relationship with avg trophic level temporal trends
 
-- Connectance:
-  - do not decrease when biomass decreases in little communities
-  - decreases when biomass decreases in big communities
-  - do not vary when biomass increases
+# Discussion
 
-- Weighted connectance:
-  - increases (more even flux distribution) when biomass decreases in little communities
-  - decreases (more skewed flux distribution) when biomass decreases in big communities
-  - decreases when biomass increases
+## Summary of result
 
-### Summary of result
+- There was a significant positive link between the dynamics of community biomass and the
+  dynamics of community structure for the variables: species richness, average trophic level, connectance except for pielou of
+  individuals and pielou of biomass which had respectively a no and a negative
+  relationship.
+
+- There was a significant positive link between the dynamics of species richness and the
+  dynamics of community structure for the variables: average trophic level, connectance, pielou of
+  individuals and pielou of biomass; except for connectance which had a negative
+  relationship.
 
 - There are a significant link between the dynamics of community biomass and the
-  dynamics of community structure for all the variables: species richness,
-  average trophic level, connectance and weighted connectance.
+  dynamics of community structure for all the variables expect pielou of
+  biomass: species richness, average trophic level, connectance and pielou of
+  individuals
 
 - We found that the link between network temporal dynamics and biomass temporal
-  dynamics change according if the community loses or gain biomass, for all
+  dynamics **does not change** according if the community loses or gain biomass, for all
   variables.
 
-- We found that the biomass of the community at the beginning of the temporal
-  series, i.e. community size, had an effect on the link between network
-  dynamics and biomass expect for species richness. We also found that the
-  effect of biomass was stronger in communities losing biomass for connectance and
-  weighted connectance but stronger in communities gaining biomass for average
-  trophic level
+## Answer to research questions
 
-### Answer to research questions
+- Lost and gain of biomass or species richness resulted in same network structure dynamics,
+  suggesting that the two processes are symmetric.
+- The low effect of community size suggests that the architecture of the
+  community in terms of species richness, number of piscivorous species, plays a
+  role in its dynamics
 
-- Lost and gain of biomass result in different network structure dynamics,
-  suggesting that the two processes are not symmetric.
-- The effect of community size suggests that the architecture of the community
-  in terms of species richness, number of piscivorous species, plays a role in
-  its dynamics
-
-### Interpretation
+## Interpretation
 
 - Richness:
-  - When biomass increases, one can that species richness increases as well
+  - When biomass increases, species richness increases as well
     as when biomass decreases conjointly to species richness.
-  - Increase in species richness necessitates colonization events, i.e.
-    stochastic events while decreases in species richness necessitates
-    disparition of species already in the community. Thus, the colonization
-    process needs element exterior to the community.
-    - Immigration debt: (might be relevant if low availability of new species)
-  - second explanation: when biomass increases, competitive interactions may prevent the increase in
-    species richness. We expect that processes based on competition would raise
-    the role of community size.
 
@@
     statistically more linked to them
-  - In biggest communities, there was no link between biomass and avg trophic
-    level dyn because those communities already contain high trophic
-    levels (There is a positive correlation between the number of pisc node and
-    biomass of the community). So, there is a saturation at the top of the
-    chain.
+  - Low and gain of biomass are linked to big individuals
+
     - The observation that the number of link and link density follow the same
@@
     y %in% c(get_com_str_var(), "log_rich_std", "piel_nind", "piel_bm"),
+    !y %in% c("bm_std", "rich_std"),
     x == "log_bm_std"
@@
 )
-pred_plot_signif_com$pred_plot %<>% map(., ~.x + theme(legend.position = "none"))
-top <- plot_grid(
-  plotlist = pred_plot_signif_com$pred_plot,
-  labels = pred_plot_signif_com$y, nrow = 2
+pred_plot_signif_com %<>% 
+  mutate(
+  pred_plot = pmap(list(pred_plot, y, x),
+    function(p, y, x) {
+      # Replace label
+      label <- str_replace_all(c(x,y), var_replacement(slope = TRUE)) 
+      p +
+	labs(x = label[1], y = label[2]) +
+	theme(legend.position = "none")
+    } )
   )
-pred_plot1 <- plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
+
+list_p <- pred_plot_signif_com$pred_plot
+list_p[[length(list_p) + 1]] <- legend_signif
+
+pred_plot1 <- plot_grid(
+  plotlist = list_p,
+  labels = "AUTO",
+  nrow = 2
+)
+#pred_plot1 <- plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
 ```
@@
 pred_plot_rich <- predict_plot2 %>%
-  filter( y %in% c(get_com_str_var(), "bm_std", "log_bm_std", "piel_nind", "piel_bm"), x == "log_rich_std") %>%
-  filter(!y %in% "rich_std")
+  filter( y %in% c(get_com_str_var(), "log_bm_std", "piel_nind", "piel_bm"), x == "log_rich_std") %>%
+  filter(!y %in% c("rich_std"))
 legend_signif <- get_legend(
@@
 )
-pred_plot_rich$pred_plot %<>% map(., ~.x + theme(legend.position = "none"))
-top <- plot_grid(
-  plotlist = pred_plot_rich$pred_plot,
-  labels = pred_plot_rich$y
+pred_plot_rich %<>% 
+  mutate(
+  pred_plot = pmap(list(pred_plot, y, x),
+    function(p, y, x) {
+      # Replace label
+      label <- str_replace_all(c(x,y), var_replacement(slope = TRUE)) 
+      p +
+	labs(x = label[1], y = label[2]) +
+	theme(legend.position = "none")
+    } )
   )
-pred_plot2 <- plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
+
+list_p <- pred_plot_rich$pred_plot
+list_p[[length(list_p) + 1]] <- legend_signif
+
+pred_plot2 <- plot_grid(
+  plotlist = list_p,
+  nrow = 2,
+  labels = "AUTO" 
+)
+#pred_plot2 <- plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
 ```
@@
 ```{r}
+
 pred_plot_other <- predict_plot2 %>%
@@
 )
-pred_plot_other$pred_plot %<>% map(., ~.x + theme(legend.position = "none"))
-top <- plot_grid(
-  plotlist = pred_plot_other$pred_plot,
-  labels = pred_plot_other$y, nrow = 2
+pred_plot_other %<>% 
+  mutate(
+  pred_plot = pmap(list(pred_plot, y, x),
+    function(p, y, x) {
+      # Replace label
+      label <- str_replace_all(c(x,y), var_replacement(slope = TRUE)) 
+      p +
+	labs(x = label[1], y = label[2]) +
+	theme(legend.position = "none")
+    } )
   )
-pred_plot3 <- plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
+
+list_p <- pred_plot_other$pred_plot
+list_p[[length(list_p) + 1]] <- legend_signif
+
+pred_plot3 <- plot_grid(
+  plotlist = list_p,
+  labels = "AUTO", nrow = 2
+)
+#pred_plot3 <- plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
 ```
 
-```{r, fig.dim = c(12, 12)}
+```{r, fig.dim = c(10, 7)}
+pred_plot1
+pred_plot2
+pred_plot3
+```
+
+```{r, eval = FALSE, fig.dim = c(12, 12)}
 plot_grid(
-  pred_plot1, plot_grid(pred_plot2, pred_plot3, ncol = 2, rel_widths = c(.75, 1)),
+  , plot_grid(, , ncol = 2, rel_widths = c(.75, 1)),
   nrow = 2
@@
 
-```{r, fig.dim = c(10, 5)}
+```{r, eval = FALSE, fig.dim = c(10, 5)}
 loadd(betapart_bin, rigal_classification, st_mono_trends_combined_list)
@@
 ```{r}
-# Rich and rich slope
-loadd(summary_var_f3y)
-
-mask <- st_mono_trends_combined_list$variable == "richness"
-xdata <- rigal_classification %>%
-  filter(variable == "richness") %>%
-  unnest(classif) %>%
-  filter(station %in% st_mono_trends_combined_list[mask, ]$station[[1]])
-
-xdata %>%
-  select(station, linear_slope) %>%
-  left_join(summary_var_f3y %>% select(station, richness), by = "station") %>%
-  ggplot(aes(x = linear_slope, y = richness)) +
-  geom_point() +
-  labs(x = "Slope of richness (year)", y = "richness")
-```
-
-```{r}
 #loadd(temporal_dynamics_plot)
@@
 model_log_bm_f3y_table_medium[["anova_table"]] %>%
-  filter( y %in% c(get_com_str_var(), "ct_ff", "log_rich_std")) %>%
+  filter(
+    y %in% c(get_com_str_var(), "ct_ff", "log_rich_std"),
+    !y %in% "rich_std") %>%
   kable(., booktabs = TRUE,
@@
       "ANOVA table for the model: dN =",
-      "dB + B + dB*B + Inc*B + dB*Inc*B."
+      "dB + B + dB*B + Inc*B + dB*Inc*B. The community structure versus the
+      biomass"
+    )
+  ) %>%
+  kable_styling(latex_options =c("scale_down", "stripped")) %>%
+  collapse_rows(columns = 1, valign = "top")
+```
+
+```{r}
+loadd(model_log_rich_f3y_table_medium)
+model_log_rich_f3y_table_medium[["anova_table"]] %>%
+  filter(
+    y %in% c(get_com_str_var(), "log_bm_std"),
+    !y %in% "rich_std") %>%
+  kable(., booktabs = TRUE,
+    caption = 
+      paste0(
+      "ANOVA table for the model: dN =",
+      "dB + B + dB*B + Inc*B + dB*Inc*B. The community structure versus the
+      species richness"
     )
@@
   collapse_rows(columns = 1, valign = "top")
+```
+
+```{r}
+# Rich and rich slope
+loadd(summary_var_f3y, st_mono_trends_combined_list, rigal_classification)
+
+mask <- st_mono_trends_combined_list$variable == "richness"
+xdata <- rigal_classification %>%
+  filter(variable == "richness") %>%
+  unnest(classif) %>%
+  filter(station %in% st_mono_trends_combined_list[mask, ]$station[[1]])
+
+xdata %>%
+  select(station, linear_slope) %>%
+  left_join(summary_var_f3y %>% select(station, richness), by = "station") %>%
+  ggplot(aes(x = linear_slope, y = richness)) +
+  geom_point() +
+  labs(x = "Slope of richness (year)", y = "richness")
 ```
@@
 ```
+
+# Methods
+
+- Methodological choice:
+  - Dynamics of log of the biomass: put big and little station on the same scale
+    (% of biomass gained or lost per year)
+
+2. $dN = dB + B + dB \times B + Inc \times B + dB \times Inc \times B$
+
+with:
+- $dN$: temporal trend of network structure
+- $dB$: temporal trend of total (log) biomass
+- $B$: total median biomass or total biomass of the first three year
+- $Inc$: Is $dB > 0$?
+
+We kept the second model.

### 2021-01-27 R/get_model_plot.R

@@ -251,9 +251,9 @@ from_term_to_predict_term <- function (term = NULL) {
   term
 }
 
-get_ggpredict_term_from_anova <- function (aov_tab = NULL, bound = NULL) {
+get_ggpredict_term_from_anova <- function (aov_tab = NULL, bound = NULL, pval_threshold = 0.05) {
   tmp <- aov_tab %>%
-    mutate(signf = p.value <= 0.05) %>%
+    mutate(signf = p.value <= pval_threshold) %>%
     filter(signf) %>%
     summarise(
       signif_term = paste(term, collapse = "+"),

### 2021-01-30 paper/manuscript.Rmd
write results and wordstack/outline

---
title: "More than space for time: revealing the tight links constraining the temporal dynamics of network structure"
author: "Alain Danet, Maud Mouchet, Loubna El Madouri, Colin Fontaine"
self_contained: yes
date: "`r Sys.Date()`"
tables: yes
bibliography: references.bib 
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
    math: katex
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE 
)
```

```{r, results = FALSE}
library(drake)
library(tidyverse)
library(magrittr)
library(cowplot)
library(viridis)
library(kableExtra)
library(sf)
mypath <- rprojroot::find_package_root_file 
source(mypath("R/variable_shortcut.R")) # Define your custom code as a bunch of functions.
source(mypath("R/misc.R"))
source_dir(get_mypath("R")) # Define your custom code as a bunch of functions.

mytheme <- theme_cowplot() +
background_grid()

theme_set(mytheme)
```

# Result

Overall, we found no significant effect of the temporal gain or losses of total
biomass and species richness on the relationship between the temporal trends of
community structure and that of biomass and species richness (slope X, Table X).

## Community structure and biomass

We found a significant positive relationship between the temporal trends of total biomass from
one side and species richness, average trophic level, connectance from the other
side (slopes XX, Figure X, Table X), meaning that they increased in time when
the total biomass increased in time and respectively that they decreased in time
when the total biomass decreased in time.

We found that a significant negative relationship between the temporal trends of
total biomass and that of the pielou of biomass (slopes XX, Figure X, Table X),
meaning that the pielou value increased in time when the total biomass decreased in time and
respectively that the pielou value decreased in time when the total biomass
increase in time. However, we found no relationship between the temporal trends of
total biomass and that of the pielou of individual.

## Community structure and species richness

The temporal trends of total biomass, average trophic level, pielou of biomass,
pielou of individual had a positive relationship with that of species
richness (slopes XX, Figure X, Table X).

We also found that the relationship between the temporal trends of pielou of
individual and connectance and that of species richness was dependant of the
overall species richness of the community (Figure X, Table X). The relationship
between temporal trends of pielou of individual and that of species richness
was more positive as the community contained more species (+ XX by species by
square meter). While the relationship between temporal trends of pielou of
individual and that of species richness was more negative as the community
contained more species.

# Discussion

##

[@danet_species_nodate]

# References  {-}

<div id="refs"></div>

# Figures {-}

### 2021-01-30 paper/wordstack.Rmd
write results and wordstack/outline

---
title: "Wordstack and outline of the manuscript"
author: "Alain Danet"
self_contained: yes
date: "`r Sys.Date()`"
tables: yes
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
    math: katex
---

# Wordstack

- Foodwebs
- interactions
- perturbation/perturbation sequences
- network structure
- temporal dynamics
- BEF
- space for time
- extinction sequences

- omnivory
- equilibrium / dynamics

# Outline

### Introduction

1. community structure are dynamics and affect ecosystem functions 
    1. species interactions ?
    2. biomass or richness

2. Community structure dimension are linked 
    1. Biomass and species richness 
	1. experiment: richness and productivity richness and stability
	2. Empirical:
    2. Foodweb/Network structure and biomass/richness 
	1. connectance richness
	2. persistance / connectance

3. Colonisation / Extinction sequences in natural settings
    1. Space for time substitution
    2. Communities are not affected randomly as environment species niche  rel
    3. sequence: is losing something = adding something ?

4. Research questions 
    1. Link between the temporal dynamics of different aspects of community structure ?
	1. Is BEF valid? 
	2. is space for time substitution?
    2. effect of assembly/disassembly

5. blabla Foodweb/fish/super huge top dataset

## Material and methods

1. Data selection
2. Community biomass and richness 
3. Network reconstruction
4. Statistical analysis

## Results

1. No effects of community assembly/disassembly

2. Community structure and biomass
    1. positive links everywhere except piel ind (neutral) and piel biomass
       (negative)
    2. No effect of differences between gain and losses

3. Community structure and species richness
   1. Positive links everywhere except connectance

## Discussion

1. Temporal trends valid theory: BEF and network assembly
    1. Biomass and species richness
    2. Connectance and species richness:
    3. Tlvl and species richness
2. Top trophic levels drives the response to biomass and species richness variation
    1. Top predators represent both few individuals and most of the biomass 
    2. Predators are key to the network structure
3. Biomass and richness gains and losses are symmetric processes in terms of
   community structure
    1. Because big individuals are drivers
    2. We could have imagine other ways, that losses and gain of biomass/species are
       overall due to little individuals. Is it a statistical or an ecological
       effect? because big individuals are less numerous? (can be check with
       nind in covariable?)
4. Are community dynamics fluctuate around equilibrium point

### 2021-01-30 report.Rmd
write results and wordstack/outline

@@
 
-```{r}
+```{r, results = FALSE}
 library(drake)
@@
 theme_set(mytheme)
-theme_get()
-```
-
-# Research questions
-
-## Abstract
-
-Determine how community structure will respond to ongoing change remains an ongoing
-challenge. Studies reported strong temporal trends in community biomass, notably
-strong decline in insects and vertebrate populations.
-
-However, those studies says nothing about how empirical findings about how
-different aspects of community structure such as species richness react
-to a change in community biomass.
-
-Ecological theory might provide insight on how community structure varies
-according to biomass. Especially BEF predicts a positive link between species
-richness and community biomass especially in grassland.
-
-However, communities used in BEF experiments might not be relevant to get
-insight about what happens in natural settings. Firstly there are statics, i.e.
-not temporal. Secondly, community composition are set to randomly and thus do
-not reflect real perturbations which do not affect communities randomly. 
-(to be fair one could argue that random communities can mimic an average outcome
-over a set of possible perturbations, as perturbation 1 would cause extinction of species
-C, perturbation 2 for species A, etc...).
-
-Overall, we miss empirical findings about the link between biomass and
-community structure.
-
-We investigated the link between the temporal dynamics of community biomass at one side and 
-species richness, connectance and average trophic level at another side using a
-1995-2018 standardized monitoring of fish communities. We questionned the shape
-of the link between both temporal trends.  More specifically, we questionned if
-(2) the link between foodweb structure and biomass dynamics vary between growing
-and shrinking communities, and if the size of the community can modulate this
-response.
-
-We found significant positive relationships the dynamics of community biomass
-and the dynamics of species richness, average trophic level and connectance but
-a negative one for weighted connectance. We also found this relationship was
-different depending on if the community biomass was growing or shrinking through
-time for all variables, suggesting that assembly processes such as colonization
-processes might.
-
-# Introduction
-
-1. Option1 Global change -> change of biomass 
-   Option2 Ecological communities are dynamics + example
-
-2. Ecological communities often describe by their richness, biomass
-
-3. BEF
-
-```{r b-bivar-cap}
-bivar_cap <- paste0(
-  "Links between temporal dynamics of biomass and temporal dynamics of
-  metrics for the communities which have a median biomass across time inferior
-  to the median of the station (little) and the other (big)"
-)
 ```
@@
   suggesting that the two processes are symmetric.
-- The low effect of community size suggests that the architecture of the
-  community in terms of species richness, number of piscivorous species, plays a
-  role in its dynamics
-
-## Interpretation
-
-- Richness:
-  - When biomass increases, species richness increases as well
-    as when biomass decreases conjointly to species richness.
-
-- Avg trophic level: 
-  - Higest trophic level concentrates most of the biomass, so gain and loss are
-    statistically more linked to them
-  - Low and gain of biomass are linked to big individuals
-
-    - The observation that the number of link and link density follow the same
-      pattern confirm this interpretation.
-
-- Connectance:
-  - In little communities, few piscivorous species and so loss of biomass do not
-    change the foodwebs that much because fish-resource links are quite redondant.
-    - there is a positive correlation between nb of pisc node and biomass.
-    - In bigger communities, the loss of the highest piscivorous nodes/species
-      (see average trophic level), which have a lot of interactions, leads to a
-      decrease of connectance over time.
-  - Increase in biomass was weakly related to an increase in node number or species
-    richness, so it is not surprising that connectance to not vary.
-
-- Connectance (fish-fish interactions):
-  - Globally positive relationship
-  - when biomass increases: communities gains higher trophic level that might
-    explain this relationship (but species richness increase as well)
-  - When biomass decreases: communities
-
-- Weighted connectance:
-  - When biomass decreases in little communities, loss of highest trophic level
-    and so less big predators and weighted connectance become more even
-    - In big communities, the highest number can make the absence of such an effect 
-  - When Biomass increases:
-    - but species richness and number of nodes increases and gini coefficient
-      does not move: so it is ninly due to the number of species
-    - Gini decrease (more even link distribution) and number of species
-      decrease also, so weighted_connectance should increase (it is what we see
-      for low biomass communities). No idea for the difference between little
-      and big communites.
-
-The key to understand the difference between little and big communities is the
-number of piscivorous nodes.
+- The low effect of community biomass and species richness suggests that the
+  architecture of the community in terms of species richness, number of
+  piscivorous species, does not play a big role in its dynamics
 

### 2021-02-08 paper/manuscript.Rmd
First version of the discussion

@@
 title: "More than space for time: revealing the tight links constraining the temporal dynamics of network structure"
-author: "Alain Danet, Maud Mouchet, Loubna El Madouri, Colin Fontaine"
+author: "Alain Danet, Maud Mouchet, Loubna El Madouri, Colin Fontaine (ordre non fixé)"
 self_contained: yes
@@
 pielou of individual had a positive relationship with that of species
-richness (slopes XX, Figure X, Table X).
+richness (slopes XX, Figure X, Table X). However, the direct relationship
+between the temporal trends of average trophic level and the one of species
+richness was not significant after controling for total biomass temporal trends.
 
@@
 
-##
+- Main results:
+  - different mechanisms for richness and biomass
+  - space for time subtitution works for biomass and tlvl but not for
+    connectance
 
-[@danet_species_nodate]
+## Temporal dynamics confirms space for time substitution BEF
+
+The temporal dynamic of the species richness was positively linked to that of
+biomass. In non-temporal data, this result was already found in streams
+[@woods_testing_2020; @danet_species_nodate] but also in grasslands salt marches
+and forests [@hector_plant_1999; @tilman_biodiversity_2014;
+@wu_relationship_2015; @li_relationship_2018; but see @grace_integrative_2016]. Therefore,
+our results confirm BEF prediction works also in time.
+
+*From the previous manuscript*: the positive relationship of species richness on total
+biomass might be due to resource use complementarity [@carey_determining_2011],
+which is held by niche differentiation [@loreau_biodiversity_1998;
+@loreau_partitioning_2001] or to the higher probability of getting high biomass
+species with higher species richness [@loreau_biodiversity_2001].
+
+We found the temporal dynamic of connectance was negative associated, but
+weakly, with that one of species richness as found in most empirical foodweb
+[@dunne_network_2006]. The relationship is very weak in species rich commuties
+and more negative for species poor commuties. An explanation might be that
+species-rich communities already contains a significant number of piscivores, which have the
+most links whereas species poor communites contains few piscivores.
+
+The temporal dynamic of the average trophic level had no relationship with the
+one of species richness. It is surprising because one can imagine that loss and
+gain of species would reveal assembly/disassembly mechanisms in terms of trophic
+structure. However, we found that when species richness increases, the
+distribution of biomass and individuals among species become more even in the
+community, meaning that dominance decrease. Species richness has often been
+found to be positively or negatively related to individual eveness
+[@soininen_relationship_2012; @maureaud_biodiversity_2019].
+
+## Biomass temporal dynamics is linked to the top trophic level
+
+We further found that the temporal dynamic of the average trophic level was positively
+linked to that of biomass. Increase  of average trophic level can be associated
+to either gain of biomass in the highest trophic level nor losses of biomass in
+the lowest trophic. In our case, such gain or losses of average trophic level is
+certainly associated to the loss or the gain of the biggest individuals. Because
+it seems unlikely that a community gain or loss biomass while respectively
+losing or gaining individuals. Pielou index temporal dynamics further confirm
+this interpretation.
+
+We found that the pielou of biomass decrease through time
+as total biomass decrease and reversely, meaning that biomass distribution
+across species respectively became less and more even when total biomass
+decrease and increase. The structuration in size class of the community might
+explain this pattern.
+
+Finally, we found no relationship between the temporal
+dynamics of pielou based on indivual number and that one of biomass, confirming
+that the temporal trends of total biomass in our study is linked to few big
+individuals. @maureaud_biodiversity_2019 found negative relationship between
+biomass and eveness of indivual in marine ecosystem. One explanation is that
+marine ecosystem studied in [@maureaud_biodiversity_2019] are much larger than
+the stream communities studied in this study.
+
+We further found that the temporal dynamic of connectance was positively
+linked to that one of total biomass, meaning that connectance increases through
+time in a given site when total biomass increases through time and reversely.
+This is in line with the fact that the fishes located at higher trophic level
+also display a larger number of links as the size of the predation window
+increases with the size of the fishes. This is because the predation window of
+freshwater fish species is highly nested.
+
+##  Biomass and richness variation are not the same process
+
+Our results indicate that biomass trends are linked to few big individuals while
+richness trends are linked to overall shift in dominance in communities. This
+results has profound implications for conservation. As more and more studies
+report biomass and richness temporal dynamics [@hallmann_more_2017;
+@ceballos_biological_2017], it is important to note that they might not be
+equivalent in terms of consequences on the structure of the community. Further
+studies should investigate several dimensions of community structure because it
+drives many aspects of ecosystem functioning.
+
+## Biomass and richness gains and losses are symmetric processes in terms of community structure
+
+We found no case in which gain or losses of biomass and richness lead to
+different relationship between the temporal dynamic of community structure and
+the one of biomass and species richness. We could have imagine that
+extinction/colonisation processes or immigration/extinction debt could have lead
+to different relationships.
+
+## Space for time substitution does not always hold
+
+We found that total biomass was linked positively related to species richness
+both in space and in time, indicating that space for time might be use. In the
+same way, we found a positive positive relationship between average trophic
+level and total biomass both in time and in space. However, it was not the case
+for connectance and average trophic level that were respectively weakly or not
+linked to species richness in time whereas our result shows a strong negative
+relation in space. Moreover, connectance displayed a strong positive
+relationship (move to results?) with biomass in time but not in space.
+
+Space for time substitution is a widely
+used tool in ecology [@pickett_space-for-time_1989; @blois_space_2013;
+@damgaard_critique_2019]. However, the drivers of spatial variation might not
+be the ones that drive community variation in time. The successional processes
+driving the assembly or the disassembly of communities might not be reflected in
+spatial gradient.
+
+## Conclusion
+
+We showed that BEF works in time but that richness and biomass temporal trends through
+time relates on different ecological processes inside communities. We further
+found that space for time subtitution does not always work.
 
@@
 # Figures {-}
+
+```{r}
+loadd(p_fig1_2)
+p_fig1_2
+```

### 2021-02-08 paper/wordstack.Rmd
First version of the discussion

@@
     1. Space for time substitution
-    2. Communities are not affected randomly as environment species niche  rel
+    2. Communities are not affected randomly as environment species niche
     3. sequence: is losing something = adding something ?
+    4. assembly / disassembly processes
 
@@
 
-1. Temporal trends valid theory: BEF and network assembly
-    1. Biomass and species richness
-    2. Connectance and species richness:
-    3. Tlvl and species richness
-2. Top trophic levels drives the response to biomass and species richness variation
+1. Temporal trends valid theory: BEF 
+    1. Total Biomass and species richness 
+	- plant: [@tilman_productivity_1996; @grace_integrative_2016;
+	  @hector_plant_1999; @tilman_biodiversity_2014;
+	  @grace_integrative_2016]
+	- stream feeders: [@cardinale_species_2002]
+	- aquatic bacterial consumers [@pennekamp_biodiversity_2018]
+    2. Connectance and species richness: [@dunne_network_2006]
+    3. Tlvl and species richness: []
+    4. Evenness increases with species richness:
+       - It is expected when adding species lead to a transfert of indiv [@jost_relation_2010]
+       - Losses of species richness leads to more dominance of few species
+       - Negative selection effect? See [@maureaud_biodiversity_2019]
+       - Evenness is often positively linked to species richness
+	 [@soininen_relationship_2012]
+
+2. Biomass temporal dynamics is linked to the top trophic level
+   [@maureaud_biodiversity_2019] found neg biomass-eveness (indiv).
     1. Top predators represent both few individuals and most of the biomass 
     2. Predators are key to the network structure
-3. Biomass and richness gains and losses are symmetric processes in terms of
+
+3. Biomass and richness variation are not the same process 
+    1. Linked to few big individuals for biomass 
+    2. Linked to dominance for richness
+
+4. Biomass and richness gains and losses are symmetric processes in terms of
    community structure
     1. Because big individuals are drivers
-    2. We could have imagine other ways, that losses and gain of biomass/species are
-       overall due to little individuals. Is it a statistical or an ecological
-       effect? because big individuals are less numerous? (can be check with
-       nind in covariable?)
-4. Are community dynamics fluctuate around equilibrium point
+    2. We could have imagine other ways, that losses and gain of biomass/species
+       are overall due to little individuals. Is it a statistical or an
+       ecological effect? because big individuals are less numerous? (can be
+       check with nind in covariable?)
+
+5. Space for time substitution does not always hold
+
+6. Are community dynamics fluctuate around equilibrium point

### 2021-05-07 report.Rmd
Late update + add range of temporal data in stations

@@
 - There was a significant positive link between the dynamics of community biomass and the
-  dynamics of community structure for the variables: species richness, average trophic level, connectance except for pielou of
-  individuals and pielou of biomass which had respectively a no and a negative
-  relationship.
+  dynamics of community structure for the variables: species richness, average
+  trophic level, connectance except for pielou of individuals and pielou of
+  biomass which had respectively a no and a negative relationship.
 
-- There was a significant positive link between the dynamics of species richness and the
-  dynamics of community structure for the variables: average trophic level, connectance, pielou of
-  individuals and pielou of biomass; except for connectance which had a negative
-  relationship.
+- There was a significant positive link between the dynamics of species richness
+  and the dynamics of community structure for the variables: average trophic
+  level, connectance, pielou of individuals and pielou of biomass; except for
+  connectance which had a negative relationship.
 
@@
 - We found that the link between network temporal dynamics and biomass temporal
-  dynamics **does not change** according if the community loses or gain biomass, for all
-  variables.
+  dynamics **does not change** according if the community loses or gain biomass,
+  for all variables.
 
@@
 
-- Lost and gain of biomass or species richness resulted in same network structure dynamics,
-  suggesting that the two processes are symmetric.
+- Lost and gain of biomass or species richness resulted in same network
+  structure dynamics, suggesting that the two processes are symmetric.
 - The low effect of community biomass and species richness suggests that the
@@
 ```{r}
+loadd(p_fig1_2)
 loadd(predict_plot2)
-pred_plot_signif_com <- predict_plot2 %>%
-  filter(
-    y %in% c(get_com_str_var(), "log_rich_std", "piel_nind", "piel_bm"),
-    !y %in% c("bm_std", "rich_std"),
-    x == "log_bm_std"
+pl <- get_plot_fig1_2(predict_plot2, get_list = TRUE)
+
+map(pl$bm, function (plo) {
+  plo + theme(legend.position = "none")
+
+  save_plot(
+    file = get_mypath(
+      "figures", 
+      paste0(str_replace_all(plo$labels$y, " ", "_"),
+	"_",
+	str_replace_all(plo$labels$x, " ", "_"),
+	".png"
       )
-legend_signif <- get_legend(
-  pred_plot_signif_com$pred_plot[[1]] +
-    theme(legend.position = "bottom")
-)
-pred_plot_signif_com %<>% 
-  mutate(
-  pred_plot = pmap(list(pred_plot, y, x),
-    function(p, y, x) {
-      # Replace label
-      label <- str_replace_all(c(x,y), var_replacement(slope = TRUE)) 
-      p +
-	labs(x = label[1], y = label[2]) +
-	theme(legend.position = "none")
-    } )
+      ),
+    plot = plo,
+    base_height = 4, base_asp = 1.2#1.618 
   )
 
-list_p <- pred_plot_signif_com$pred_plot
-list_p[[length(list_p) + 1]] <- legend_signif
+} 
+)
+map(pl$rich, function (plo) {
 
-pred_plot1 <- plot_grid(
-  plotlist = list_p,
-  labels = "AUTO",
-  nrow = 2
+  plo + theme(legend.position = "none")
+
+  save_plot(
+    file = get_mypath(
+      "figures", 
+      paste0(str_replace_all(plo$labels$y, " ", "_"),
+	"_",
+	str_replace_all(plo$labels$x, " ", "_"),
+	".png"
       )
-#pred_plot1 <- plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
-```
-
-```{r}
-pred_plot_rich <- predict_plot2 %>%
-  filter( y %in% c(get_com_str_var(), "log_bm_std", "piel_nind", "piel_bm"), x == "log_rich_std") %>%
-  filter(!y %in% c("rich_std"))
-legend_signif <- get_legend(
-  pred_plot_rich$pred_plot[[1]] +
-    theme(legend.position = "bottom")
-)
-pred_plot_rich %<>% 
-  mutate(
-  pred_plot = pmap(list(pred_plot, y, x),
-    function(p, y, x) {
-      # Replace label
-      label <- str_replace_all(c(x,y), var_replacement(slope = TRUE)) 
-      p +
-	labs(x = label[1], y = label[2]) +
-	theme(legend.position = "none")
-    } )
+      ),
+    plot = plo,
+    base_height = 4, base_asp = 1.2#1.618 
   )
 
-list_p <- pred_plot_rich$pred_plot
-list_p[[length(list_p) + 1]] <- legend_signif
-
-pred_plot2 <- plot_grid(
-  plotlist = list_p,
-  nrow = 2,
-  labels = "AUTO" 
-)
-#pred_plot2 <- plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
-```
-
-```{r}
-
-pred_plot_other <- predict_plot2 %>%
-  filter( y %in% c("ct_ff", "w_trph_lvl_avg"), x %in% c("ct_ff", "w_trph_lvl_avg"))
-legend_signif <- get_legend(
-  pred_plot_other$pred_plot[[1]] +
-    theme(legend.position = "bottom")
-)
-pred_plot_other %<>% 
-  mutate(
-  pred_plot = pmap(list(pred_plot, y, x),
-    function(p, y, x) {
-      # Replace label
-      label <- str_replace_all(c(x,y), var_replacement(slope = TRUE)) 
-      p +
-	labs(x = label[1], y = label[2]) +
-	theme(legend.position = "none")
-    } )
+} 
 )
 
-list_p <- pred_plot_other$pred_plot
-list_p[[length(list_p) + 1]] <- legend_signif
+map(pl$nind, function (plo) {
 
-pred_plot3 <- plot_grid(
-  plotlist = list_p,
-  labels = "AUTO", nrow = 2
+  plo + theme(legend.position = "none")
+
+  save_plot(
+    file = get_mypath(
+      "figures", 
+      paste0(str_replace_all(plo$labels$y, " ", "_"),
+	"_",
+	str_replace_all(plo$labels$x, " ", "_"),
+	".png"
       )
-#pred_plot3 <- plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
+      ),
+    plot = plo,
+    base_height = 4, base_asp = 1.2#1.618 
+  )
+
+} 
+)
+
+pred_plot1 <- p_fig1_2[["bm"]]
+pred_plot2 <- p_fig1_2[["rich"]]
+pred_plot3 <- p_fig1_2[["other"]]
+pred_plot4 <- p_fig1_2[["nind"]]
 ```
@@
 pred_plot3
-```
-
-```{r, eval = FALSE, fig.dim = c(12, 12)}
-plot_grid(
-  , plot_grid(, , ncol = 2, rel_widths = c(.75, 1)),
-  nrow = 2
-)
+pred_plot4
 ```
@@
   na.omit() %>%
-  select(bm_std, avg_IS, l, ld, m, A, gini, log_bm_std, connectance, ct_ff, rich_std, w_trph_lvl_avg,
+  select(bm_std, nind_std, log_bm_std, connectance, ct_ff, rich_std, w_trph_lvl_avg,
     weighted_connectance, nbnode_std, nb_pisc_node_std, prop_pisc_node, piel_bm,
@@
 
+#### Réseau ~ Biomasse
+
 ```{r pred-other-com, fig.dim = c(12, 10)}
@@
 legend_signif2 <- get_legend(
-  pred_plot_signif_com$pred_plot[[1]] + theme(legend.position = "bottom")
+  pred_plot_signif$pred_plot[[1]] + theme(legend.position = "bottom")
 )
@@
   collapse_rows(columns = 1, valign = "top")
+```
+
+#### Réseau ~ richnes
+
+```{r pred-other-com-rich, fig.dim = c(12, 10)}
+pred_plot_signif <- predict_plot2 %>%
+  filter(!y %in% c(get_com_str_var(), "ct_ff"), x == "log_rich_std")
+legend_signif2 <- get_legend(
+  pred_plot_signif$pred_plot[[1]] + theme(legend.position = "bottom")
+)
+pred_plot_signif$pred_plot %<>% map(., ~.x + theme(legend.position = "none"))
+top2 <- plot_grid(
+  plotlist = pred_plot_signif$pred_plot,
+  labels = pred_plot_signif$y
+)
+plot_grid(top2, legend_signif2, nrow = 2, rel_heights = c(1, .1))
+```
+
+```{r}
+model_log_rich_f3y_table_medium[["anova_table"]] %>% 
+  filter(!y %in% get_com_str_var(all = FALSE)) %>%
+  kable(., booktabs = TRUE,
+    caption = 
+      paste0(
+      "ANOVA table for the model: dN =",
+      "dB + B + dB*B + Inc*B + dB*Inc*B."
+    )
+  ) %>%
+  kable_styling(latex_options =c("scale_down", "stripped")) %>%
+  collapse_rows(columns = 1, valign = "top")
+```
+```{r}
 ```

### 2021-05-07 R/packages.R

@@ -5,3 +5,4 @@ library(tibble)
 library(tidyverse)
 library(magrittr)
 library(ggeffects)
+library(cowplot)

### 2021-05-07 R/plan.R

@@ -2,7 +2,7 @@
 # Details: https://books.ropensci.org/drake/plans.html
 
 # Variable:
-model_x_var <- c("log_bm_std", "rich_std", "log_rich_std", "ct_ff", "w_trph_lvl_avg")
+model_x_var <- c("log_bm_std", "rich_std", "log_rich_std", "ct_ff", "w_trph_lvl_avg", "nind_std")
 #model_y_var <- c("ct_ff", "w_trph_lvl_avg", "rich_std", "log_rich_std", "w_trph_lvl_avg")
 
 plan <- drake_plan(
@@ -171,6 +171,9 @@ plan <- drake_plan(
     bm_group = biomass_group  
     ),
   p_hist_med_bm = plot_hist_med_bm(.data = full_data2),
+  p_cross_classif_bm_rich = plot_matrix_bm_rich_cross_classif(
+    classif = rigal_classification),
+  p_fig1_2 = get_plot_fig1_2(predict_plot = predict_plot2),
 
   #5. Tables 
   effect_quad2_piece = tibble(
@@ -271,6 +274,14 @@ plan <- drake_plan(
       output_dir = "paper"
     )
   ),
+  manuscript = callr::r(
+    function(...) rmarkdown::render(...),
+    args = list(
+      input = drake::knitr_in("paper/manuscript.Rmd"),
+      output_file = drake::file_out("paper/manuscript.html"),
+      output_dir = "paper"
+    )
+    ),
 
   trace = TRUE
 )

### 2021-05-07 R/report_plot.R

@@ -141,3 +141,81 @@ get_predict_from_signif <- function (mod_summary = NULL) {
     return(model_test)
 
 }
+
+plot_matrix_bm_rich_cross_classif <- function (classif = NULL) {
+
+  ti <- classif %>%
+    filter(variable %in% c("log_bm_std", "log_rich_std")) %>%
+    unnest(classif) %>%
+    select(variable, station, shape_class) %>%
+    pivot_wider(names_from = variable, values_from = shape_class)
+
+  ti2 <- ti %>% 
+    group_by(log_bm_std, log_rich_std) %>%
+    summarise(n = n())
+
+  ggplot(data = ti2, aes(x=log_bm_std, y = log_rich_std, fill=log(n))) + 
+    geom_tile() +
+    viridis::scale_fill_viridis() +
+    geom_text(aes(x=log_bm_std, y = log_rich_std, label = n), color = "black", size = 10)
+
+}
+
+get_plot_fig1_2 <- function(predict_plot = predict_plot2, get_list = FALSE, rm_legend = FALSE) {
+
+  pred_plot_signif_bm <- predict_plot %>%
+    filter(
+      y %in% c(get_com_str_var(), "log_rich_std", "piel_nind", "piel_bm"),
+      !y %in% c("bm_std", "rich_std"),
+      x == "log_bm_std"
+    )
+  pred_plot_signif_rich <- predict_plot %>%
+    filter( y %in% c(get_com_str_var(), "log_bm_std", "piel_nind", "piel_bm"), x == "log_rich_std") %>%
+    filter(!y %in% c("rich_std"))
+  pred_plot_other <- predict_plot %>%
+    filter( y %in% c("ct_ff", "w_trph_lvl_avg"), x %in% c("ct_ff", "w_trph_lvl_avg"))
+  pred_plot_ind <- predict_plot %>%
+    filter( y %in% c(get_com_str_var(), "log_bm_std", "piel_nind", "piel_bm"), x == "nind_std") %>%
+    filter(!y %in% c("nind_std"))
+
+  the_plot <- map(list(pred_plot_signif_bm, pred_plot_signif_rich, pred_plot_other, pred_plot_ind), function (x) {
+    
+  legend_signif <- get_legend(
+    x$pred_plot[[1]] +
+      theme(legend.position = "bottom")
+  )
+  x %<>% 
+    mutate(
+      pred_plot = pmap(list(pred_plot, y, x),
[…]

### 2021-05-07 R/variable_shortcut.R

@@ -54,7 +54,7 @@ get_com_str_var <- function (all = FALSE) {
     "rich_std", "piel_nind", "piel_bm")
 
   if (all) {
-    x <- c(x, "connectance", "weighted_connectance", "richness", "log_rich_std", "nbnode_std" ,"nb_pisc_rich_std", "nb_pisc_node_std", "prop_pisc_node", "prop_pisc_rich", "l", "ld", "m", "A", "avg_IS", "gini", "ct_ff", "l_ff", "ld_ff", "piel_nind", "piel_bm")
+    x <- c(x, "connectance", "weighted_connectance", "richness", "log_rich_std", "nbnode_std" ,"nb_pisc_rich_std", "nb_pisc_node_std", "prop_pisc_node", "prop_pisc_rich", "l", "ld", "m", "A", "avg_IS", "gini", "ct_ff", "l_ff", "ld_ff", "piel_nind", "piel_bm", "nind_std")
   }
 
   x <- unique(x) 

### 2021-05-07 make.R

@@ -19,7 +19,6 @@ make(plan, parallelism = "future", jobs = 3)
 
 # If you do not change any code or data,
 # subsequent make()'s do not build targets.
-
 # Load your targets back into your session with loadd() and readd().
 plan
 print(plan, n = 40)
@@ -29,15 +28,27 @@ print(plan, n = 40)
 library(future)
 plan(multisession, workers = 3)
 
-#######################################
-#  Get the right term from new model  #
-#######################################
+load("data/community_metrics.rda")
+loadd(st_mono_trends_combined_list)
+print(st_mono_trends_combined_list, n = 20)
 
-loadd(predict_table2)
+loadd(data4model)
+test <- data4model %>%
+  filter(x == "log_rich_std", y %in% c("piel_bm", "piel_nind","w_trph_lvl_avg", "log_bm_std")) %>%
+  unnest(data_model) %>%
+  select(station ,y, log_rich_std_slope, linear_slope) %>%
+  pivot_wider(names_from = "y", values_from = "linear_slope")
 
-predict_table2$model_obj[[3]]
+mod <- lm(w_trph_lvl_avg ~ log_rich_std_slope + log_bm_std, data = test)
+summary(mod)
+car::vif(mod)
 
-loadd(predict_plot2)
+# Is it the same for pielou ?
 
-predict_plot2$pred_plot
-  
+mod <- lm(piel_bm ~ log_rich_std_slope + log_bm_std, data = test2)
+summary(mod)
+car::vif(mod)
+
+mod <- lm(piel_nind ~ log_rich_std_slope + log_bm_std, data = test2)
+summary(mod)
+car::vif(mod)

### 2021-05-11 paper/manuscript.Rmd
Add spatial models

@@
 ```
+
+# Methods
+
+## Data selection
+
+## Food-web inference
+
+Because we had few informations about trophic interactions between resources, we
+selected only the fish-fish interactions in subsequent analysis.
+
+## Food-web and community structure
+
+We characterized food-webs by its connectance, describing the degree of
+generalism in a network [@dunne_network_2006, @delmas_analysing_2019]. It is
+computed as the ratio between the actual number of links and the number of
+potential links ($C = \frac{L}{S(S-1)}$, with $L$ being the number of links and
+$S$ the number of trophic species). We also computed the average trophic level,
+weighted by the biomass of the trophic species. The trophic level of a trophic
+species is computed recursively as 1 added to the mean trophic level of the
+preys that it consumes.
+
+We described community structure by its total biomass, species richness and the
+evenness of the number of individual and the amount of biomass across species. The evenness was
+quantified with the Pielou index, computed as the Shannon diversity index
+divided by the number of species ($P = \frac{H'}{N}$, with $H'$ being the
+Shannon diversity index and $N$ the number of species).
+
+```{r}
+loadd(com_analysis_data)
+```
+
+## Classification of temporal trajectories
+
+We characterized the temporal trajectories of network and community structure at
+each site. We used a method based on second order polynomial which allows to
+assess both the direction and the monotony of temporal trends
+[@rigal_method_2020].
+
+- Why do we want to classify temporal trends?
+- How do we select station for each variable?
+
+## Spatial
 

### 2021-05-11 report_rdv.Rmd
Add spatial models

---
title: "Report"
author: "Alain Danet"
self_contained: yes
date: "`r Sys.Date()`"
tables: yes
output:
  html_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE 
)
```

```{r}
library(drake)
library(tidyverse)
library(magrittr)
library(cowplot)
library(viridis)
library(kableExtra)
library(sf)
library(viridis)
source("R/misc.R") # Define your custom code as a bunch of functions.
source("R/variable_shortcut.R")
source_dir(get_mypath("R")) # Define your custom code as a bunch of functions.

theme_set(theme_cowplot())
```

# Research questions

## Abstract

Determine how community structure will respond to ongoing change remains an ongoing
challenge. Studies reported strong temporal trends in community biomass, notably
strong decline in insects and vertebrate populations.

However, those studies says nothing about how empirical findings about how
different aspects of community structure such as species richness react
to a change in community biomass.

Ecological theory might provide insight on how community structure varies
according to biomass. Especially BEF predicts a positive link between species richness and
community biomass especially in grassland.

However, communities used in BEF experiments might not be relevant to get
insight about what happens in natural settings. Firstly there are statics, i.e.
not temporal. Secondly, community composition are set to randomly and thus do
not reflect real perturbations which do not affect communities randomly. 
(to be fair one could argue that random communities can mimic an average outcome
over a set of possible perturbations, as perturbation 1 would cause extinction of species
C, perturbation 2 for species A, etc...).

Overall, we miss empirical findings about the link between biomass and
community structure.

We investigated the link between the temporal dynamics of community biomass at one side and 
species richness, connectance and average trophic level at another side using a
1995-2018 standardized monitoring of fish communities. We questionned the shape
of the link between both temporal trends.  More specifically, we questionned if
(2) the link between foodweb structure and biomass dynamics vary between growing
and shrinking communities, and if the size of the community can modulate this
response.

We found significant positive relationships the dynamics of community biomass
and the dynamics of species richness, average trophic level and connectance but
a negative one for weighted connectance. We also found this relationship was
different depending on if the community biomass was growing or shrinking through
time for all variables, suggesting that assembly processes such as colonization
processes might.

```{r}
loadd(predict_plot)
pred_plot_signif_com <- predict_plot %>%
  filter(
    y %in% c(get_com_str_var(), "log_rich_std", "piel_nind", "piel_bm"),
    x == "log_bm_std"
  )
legend_signif <- get_legend(
  pred_plot_signif_com$pred_plot[[1]] +
    theme(legend.position = "bottom")
)
pred_plot_signif_com$pred_plot %<>% map(., ~.x + theme(legend.position = "none"))
top <- plot_grid(
  plotlist = pred_plot_signif_com$pred_plot,
  labels = pred_plot_signif_com$y, nrow = 2
)
pred_plot1 <- plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
```

```{r}
pred_plot_rich <- predict_plot %>%
  filter( y %in% c(get_com_str_var(), "bm_std", "log_bm_std", "piel_nind", "piel_bm"), x == "log_rich_std") %>%
  filter(!y %in% "rich_std")
legend_signif <- get_legend(
  pred_plot_rich$pred_plot[[1]] +
    theme(legend.position = "bottom")
)
pred_plot_rich$pred_plot %<>% map(., ~.x + theme(legend.position = "none"))
top <- plot_grid(
  plotlist = pred_plot_rich$pred_plot,
  labels = pred_plot_rich$y 
)
pred_plot2 <- plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
```

```{r}
pred_plot_other <- predict_plot %>%
  filter( y %in% c("ct_ff", "w_trph_lvl_avg"), x %in% c("ct_ff", "w_trph_lvl_avg"))
legend_signif <- get_legend(
  pred_plot_other$pred_plot[[1]] +
    theme(legend.position = "bottom")
)
pred_plot_other$pred_plot %<>% map(., ~.x + theme(legend.position = "none"))
top <- plot_grid(
  plotlist = pred_plot_other$pred_plot,
  labels = pred_plot_other$y, nrow = 1
)
pred_plot3 <- plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
```

```{r, fig.dim = c(12, 12)}
plot_grid( pred_plot1, pred_plot2, pred_plot3, rel_heights = c(.4, .4, .20), nrow = 3
)
```

```{r}
loadd(betapart_bin, rigal_classification, st_mono_trends_combined_list,
  summary_var_f3y)
# Rich and rich slope

mask <- st_mono_trends_combined_list$variable == "richness"
xdata <- rigal_classification %>%
  filter(variable == "richness") %>%
  unnest(classif) %>%
  filter(station %in% st_mono_trends_combined_list[mask, ]$station[[1]])

xdata %>%
  select(station, linear_slope) %>%
  left_join(summary_var_f3y %>% select(station, richness), by = "station") %>%
  ggplot(aes(x = linear_slope, y = richness)) +
  geom_point() +
  labs(x = "Slope of richness (year)", y = "richness")
```

```{r, fig.dim = c(10, 5)}
xdata <- rigal_classification %>%
  filter(variable == "log_bm_std") %>%
  unnest(classif) %>%
  filter(station %in% st_mono_trends_combined_list[mask, ]$station[[1]])

beta_xdata <- xdata %>%
  select(station, linear_slope) %>%
  left_join(betapart_bin, by = "station")

beta_xdata %>%
  pivot_longer(cols = c(beta.SIM:beta.SOR), names_to = "type", values_to = "beta") %>%
  ggplot(aes(x = linear_slope, y = beta)) +
  geom_point() +
  facet_grid(cols = vars(type)) +
  labs(x = "Slope of Log biomass (% biomass by year)", y = "Beta-diversity")

```

### Results

#### With biomass

- Species richness:
  - stables in time when biomass decreases
  - increases in time when biomass increases   
  - Difference increase/decrease
  - effect of community size! (same for the number of nodes)

- Avg trophic level:
  - decreases simultaneously with biomass decreases 
  - increase simultaneously with biomass increases but increases less for bigger
    communities
  - meaning that biomass loss and gain are located in the highest trophic level
    (except gain of biomass in biggest communities)

- Connectance:
  - do not decrease when biomass decreases in little communities
  - decreases when biomass decreases in big communities
  - do not vary when biomass increases

- Weighted connectance:
  - increases (more even flux distribution) when biomass decreases in little communities
  - decreases (more skewed flux distribution) when biomass decreases in big communities
  - decreases when biomass increases

### Summary of result

- There are a significant link between the dynamics of community biomass and the
  dynamics of community structure for all the variables: species richness,
  average trophic level, connectance and weighted connectance.

- We found that the link between network temporal dynamics and biomass temporal
  dynamics change according if the community loses or gain biomass, for all
  variables.

- We found that the biomass of the community at the beginning of the temporal
  series, i.e. community size, had an effect on the link between network
  dynamics and biomass expect for species richness. We also found that the
  effect of biomass was stronger in communities losing biomass for connectance and
  weighted connectance but stronger in communities gaining biomass for average
  trophic level

### Answer to research questions

- Lost and gain of biomass result in different network structure dynamics,
  suggesting that the two processes are not symmetric.
- The effect of community size suggests that the architecture of the community
  in terms of species richness, number of piscivorous species, plays a role in
  its dynamics

### Interpretation

- Richness:
  - When biomass increases, one can that species richness increases as well
    as when biomass decreases conjointly to species richness.
  - Increase in species richness necessitates colonization events, i.e.
    stochastic events while decreases in species richness necessitates
    disparition of species already in the community. Thus, the colonization
    process needs element exterior to the community.
    - Immigration debt: (might be relevant if low availability of new species)
  - second explanation: when biomass increases, competitive interactions may prevent the increase in
    species richness. We expect that processes based on competition would raise
    the role of community size.

- Avg trophic level: 
  - Higest trophic level concentrates most of the biomass, so gain and loss are
    statistically more linked to them
  - In biggest communities, there was no link between biomass and avg trophic
    level dyn because those communities already contain high trophic
    levels (There is a positive correlation between the number of pisc node and
    biomass of the community). So, there is a saturation at the top of the
    chain.
    - The observation that the number of link and link density follow the same
      pattern confirm this interpretation.

- Connectance:
  - In little communities, few piscivorous species and so loss of biomass do not
    change the foodwebs that much because fish-resource links are quite redondant.
    - there is a positive correlation between nb of pisc node and biomass.
    - In bigger communities, the loss of the highest piscivorous nodes/species
      (see average trophic level), which have a lot of interactions, leads to a
      decrease of connectance over time.
  - Increase in biomass was weakly related to an increase in node number or species
    richness, so it is not surprising that connectance to not vary.

- Connectance (fish-fish interactions):
  - Globally positive relationship
  - when biomass increases: communities gains higher trophic level that might
    explain this relationship (but species richness increase as well)
  - When biomass decreases: communities

- Weighted connectance:
  - When biomass decreases in little communities, loss of highest trophic level
    and so less big predators and weighted connectance become more even
    - In big communities, the highest number can make the absence of such an effect 
  - When Biomass increases:
    - but species richness and number of nodes increases and gini coefficient
      does not move: so it is ninly due to the number of species
    - Gini decrease (more even link distribution) and number of species
      decrease also, so weighted_connectance should increase (it is what we see
      for low biomass communities). No idea for the difference between little
      and big communites.

The key to understand the difference between little and big communities is the
number of piscivorous nodes.

```{r}
loadd(model_log_bm_f3y_table_medium)
model_log_bm_f3y_table_medium[["anova_table"]] %>% 
  filter(y %in% get_com_str_var(all = FALSE)) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA table for the model: dN =",
      "dB + B + dB*B + Inc*B + dB*Inc*B."
    )
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
# Get the range of variable variation in temporal data and compare it to spatial
# data

loadd(data4model, rigal_classification, full_data2, summary_var_f3y)
rigal_classification$classif[[1]]

range_spatial_variable <- summary_var_f3y %>%
  select(c("station", get_biomass_var(), get_com_str_var(all = FALSE))) %>%
  pivot_longer(!station, names_to = "variable", values_to = "values") %>%
  group_by(variable) %>% 
  summarise(min = min(values, na.rm = TRUE), max = max(values, na.rm = TRUE)) %>%
  mutate(range = max - min)

range_variable_station <- full_data2 %>% 
  select(c("station", get_biomass_var(), get_com_str_var(all = TRUE))) %>%
  pivot_longer(!station, names_to = "variable", values_to = "values") %>%
  group_by(station, variable) %>% 
  summarise(min = min(values, na.rm = TRUE), max = max(values, na.rm = TRUE))

range_variable_station %>%
  filter(variable %in% c(get_biomass_var(), get_com_str_var(all = FALSE))) %>%
  pivot_longer(cols = c(min, max), names_to = "minmax", values_to = "values") %>%
  ggplot(aes(x = values, fill = minmax)) +
  geom_histogram() +
  geom_vline(data = range_spatial_variable %>%
    pivot_longer(cols = c(min, max), names_to = "minmax", values_to = "values"),
  aes(xintercept = values, color = minmax)) + facet_wrap(~variable, scale =
  "free")

# Range distibution 
range_variable_station %>%
  filter(variable %in% c(get_biomass_var(), get_com_str_var(all = FALSE))) %>%
  mutate(range = abs(max - min)) %>%
  ggplot(aes(x = range)) +
  geom_histogram() +
  geom_vline(data = range_spatial_variable, aes(xintercept = range)) +
  facet_wrap(~variable, scale = "free") 
```

```{r}
# Refaire temporal range avec first last year  
range_year_station <- full_data2 %>% 
  select(c("station", year, get_biomass_var(), get_com_str_var(all = TRUE))) %>%
  pivot_longer(!c(station, year), names_to = "variable", values_to = "values") %>%
  group_by(station, variable) %>% 
  summarise(min = values[year == min(year)], max = values[year == max(year)])

p_min_max_station <- range_year_station %>%
  filter(variable %in% c(get_biomass_var(), get_com_str_var(all = FALSE))) %>%
  pivot_longer(cols = c(min, max), names_to = "minmax", values_to = "values") %>%
  ggplot(aes(x = values, fill = minmax)) +
  scale_fill_viridis(discrete=TRUE) +
  scale_color_viridis(discrete=TRUE) +
  geom_histogram() +
  geom_vline(data = range_spatial_variable %>%
    pivot_longer(cols = c(min, max), names_to = "minmax", values_to = "values"),
  aes(xintercept = values, color = minmax)) + 
  facet_wrap(~variable, scale = "free", labeller = as_labeller(var_replacement()))+
  labs(fill='Value', color = "Value")

save_plot(
  filename = get_mypath("figures/min_max_y_station.png"),
  p_min_max_station,
  ncol = 3,
  nrow = 3,
  base_height = 3.71,
  base_asp = 1.618
)

p_range_year_station <- range_year_station %>%
  filter(variable %in% c(get_biomass_var(), get_com_str_var(all = FALSE))) %>%
  mutate(
    range = abs(max - min),
    variable = str_replace_all(variable, var_replacement())
    ) %>%
  ggplot(aes(x = range)) +
  geom_histogram() +
  labs(x = "Range of variables values", y = "Frequency") +
  geom_vline(data = mutate(range_spatial_variable,
      variable = str_replace_all(variable, var_replacement())),
    aes(xintercept = range), color = "red") +
  facet_wrap(~variable, scale = "free_x")

save_plot(
  filename = get_mypath("figures/range_y_station.png"),
  p_range_year_station,
  ncol = 3,
  nrow = 3,
  base_height = 3.71,
  base_asp = 1.618
)

# Refaire temporal range avec predict first last year

```

```{r range-tps-sp}
med_range_year_station <- range_year_station %>%
  filter(variable %in% c(get_biomass_var(), get_com_str_var(all = FALSE))) %>%
  mutate(range = abs(max - min)) %>%
  group_by(variable) %>%
  summarise(med = median(range, na.rm = TRUE))
```

### Spatial model

#### Perform PCA

```{r}
# get all stations used in the analysis
loadd(rigal_classification, data_for_pca, pca, environment_pca)
p_pca <- my_pca_plot(.data = pca$rotated,
  xaxis = "RC1", yaxis = "RC2", ctb_thld = .4, 
  label_size = 4, force_pull = 0.01, force = 10,
  seed = 1
)
p_pca
save_plot(file = get_mypath("figures", 
	"rotated_pca_reversed_axis.pdf"),
    plot = p_pca,
    base_height = 4.5, base_asp = 1.2#1.618 
    )
```

#### Get model

```{r}
loadd(sp_models)
```

#### VIF

```{r}
tmp <- map(colin_sp_models, enframe)

# colinearity table
t_colin_sp_models <- tibble(vif = tmp, mod = names(colin_sp_models)) %>%
  unnest(vif) %>%
  mutate(
    mod = str_replace_all(mod, var_replacement()),
    value = round(value, 1),
    name = str_replace_all(name, var_replacement())
    ) %>%
  rename(`Response variable` = mod) %>%
  spread(name, value)

kable(t_colin_sp_models,
  booktabs = T,
  caption = "Variance Inflation Factor for the linear models used in the structural
  equation models. NA values indicate that the term in column was not included
  in the modeling of the response variable in row."
  ) %>%
  kable_styling()
```

### Plot

```{r}
loadd(sp_relation_plot)
plot_grid(plotlist = sp_relation_plot$gg)

# Write plots:
map(sp_relation_plot$gg,
  ~save_plot(
    file = get_mypath(
      "figures", 
      paste0(
	"spatial_",
	names(.x$labels$y),
	"_",
	names(.x$labels$x),
	".png"
      )
      ),
    plot = .x,
    base_height = 2.5, base_asp = 1.2#1.618 
  ) 
)
```

### 2021-05-11 R/geo_methods.R

@@ -1,0 +1,30 @@
+get_basin_station <- function (sf_obj = FALSE) {
+
+  mypath <- 
+    myload(the_8_hydrologic_basin, station_analysis,
+      envir = environment(), dir = get_mypath("data"))
+
+  station_analysis %<>%
+    sf::st_transform(crs = 2154)
+  the_8_hydrologic_basin %<>%
+    dplyr::mutate(NomDistric = ifelse(CdBassinDC == "B2", "SAMBRE", NomDistric))
+
+  station_basin <- sf::st_intersects(station_analysis, the_8_hydrologic_basin)
+  station_analysis$basin <- purrr::map_chr(station_basin, function(x){
+    if (length(x) == 0) {
+      return(NA)
+    }
+    the_8_hydrologic_basin[["NomDistric"]][x]
+    })
+  station_analysis %<>%
+    #filter(!is.na(basin)) %>%
+    dplyr::mutate(station = id) %>%
+    dplyr::select(station, basin)
+
+  if (!sf_obj) {
+    sf::st_geometry(station_analysis) <- NULL
+  }
+
+  return(station_analysis)
+
+}

### 2021-05-11 R/get_data.R

@@ -208,3 +208,10 @@ update_files <- function () {
    copy.date = TRUE
    )
 }
+
+get_all_station_analysis <- function (classif = NULL) {
+  st_analysis <- map(get_all_var_analysis(), ~get_st_mono_trends(.df = classif, xvar = .x)$station) %>% 
+    unlist %>% unique
+  return(st_analysis)
+
+}

### 2021-05-11 R/plan.R

@@ -117,6 +117,21 @@ plan <- drake_plan(
     classif = rigal_classification,
     st_mono = st_mono_trends_combined_list, type = "min_max"),
 
+  # 2.2 Environment
+  st_analysis = get_all_station_analysis(classif = rigal_classification),
+  data_for_pca = habitat_press %>%
+    filter(station %in% st_analysis) %>%
+    select(all_of(c("station", get_var_for_pca()))),
+  pca = get_pca_environment(.data = data_for_pca),
+  environment_pca = data_for_pca %>%
+    mutate(
+      RC1 = pca$rotated$scores[, 1],
+      log_RC1 = log(RC1 + abs(min(RC1)) + 1),
+      RC2 = pca$rotated$scores[, 2],
+      log_RC2 = log(RC2 + abs(min(RC2)) + 1)
+      ) %>%
+    select(RC1, log_RC1, RC2, log_RC2, everything()),
+
   # 3. Modelling
   comb = list(
     y = c(get_com_str_var(all = TRUE), "bm_std", "log_bm_std"),
@@ -164,6 +179,17 @@ plan <- drake_plan(
   net_dyn_lm_plot = get_net_dyn_lm_plot(net_dyn_lm = net_dyn_lm),
   net_dyn_lm_coeff = get_lm_coeff(.data = net_dyn_lm, col_names = "model"),
 
+  # 3.2 Analysis for the spatial models 
+  basin_station = get_basin_station(),
+  sp_st_data = summary_var_med %>%
+    left_join(environment_pca, by = "station") %>%
+    left_join(basin_station, by = "station") %>%
+    filter(station %in% st_analysis) %>%
+    select(all_of(c("station", "basin", "log_RC1", "log_RC2", get_all_var_analysis()))) %>%
+    na.omit,
+  sp_models = get_mod_list(.data = as.data.frame(sp_st_data)),
+  colin_sp_models = map(sp_models, car::vif),
+  est_sp_models = map(sp_models, broom.mixed::tidy),
 
   #4. The plots
   p_bm_vs_bm_slope = plot_bm_vs_bm_slope(
@@ -174,6 +200,13 @@ plan <- drake_plan(
   p_cross_classif_bm_rich = plot_matrix_bm_rich_cross_classif(
     classif = rigal_classification),
   p_fig1_2 = get_plot_fig1_2(predict_plot = predict_plot2),
[…]

### 2021-05-11 R/plot_methods.R

@@ -1179,7 +1179,12 @@ make_troph_plot <- function (
 ##############
 #  PCA plot  #
 ##############
-my_pca_plot <- function (.data = pca_rotated$rotated, xaxis = NULL, yaxis = NULL, ctb_thld = .4) {
+my_pca_plot <- function (.data = pca_rotated$rotated,
+  xaxis = NULL, yaxis = NULL,
+  ctb_thld = .4, label_size = 2, 
+  force = 10,  force_pull = 1,
+  seed = NA
+  ) {
 
   pca_data <- .data$loadings[1:nrow(.data$loadings),]
   pca_data %<>%
@@ -1217,7 +1222,9 @@ ggplot() +
   ) +
   ggrepel::geom_label_repel(data = pca_label,
     aes_string(x = xaxis, y = yaxis, label = "variable"),
-    size = 2, force = 10, box.padding = .1, label.padding = .1
+    size = label_size,
+    force = force, force_pull = force_pull, seed = seed,
+    box.padding = .1, label.padding = .1
   )
 }
 

### 2021-05-11 R/variable_shortcut.R

@@ -70,6 +70,8 @@ get_model_terms <- function ( ) {
 var_replacement <- function (slope = FALSE) {
 
   x <- c(
+    log_RC1 = "PCA Avg stream size",
+    log_RC2 = "PCA Avg temperature",
     ct_ff = "Connectance",
     w_trph_lvl_avg = "Avg trophic level",
     #connectance ,weighted_connectance,
@@ -88,4 +90,16 @@ var_replacement <- function (slope = FALSE) {
   }
 
   return(x)
+}
+
+get_var_for_pca <- function() {
+  c(
+    "slope", "alt", "d_source", "strahler", "width_river_mean", "avg_depth_station_mean",
+    "width_river_cv", "avg_depth_station_cv", "DBO_med", "flow_med", "temperature_med",
+    "DBO_cv", "flow_cv", "temperature_cv"
+  )
+}
+
+get_all_var_analysis <- function () {
+  c(get_com_str_var(), get_biomass_var(), get_richness_var()) %>% unique
 }

### 2021-05-27 paper/manuscript.Rmd
Add spatial analysis and results

@@
 ```{r}
-loadd(com_analysis_data)
+loadd(com_analysis_data, full_data2)
+```
+```{r}
+nb_st <- unique(full_data2$station) %>% length
 ```
@@
 
-We characterized the temporal trajectories of network and community structure at
-each site. We used a method based on second order polynomial which allows to
-assess both the direction and the monotony of temporal trends
-[@rigal_method_2020].
-
-- Why do we want to classify temporal trends?
-- How do we select station for each variable?
+With the goal to characterize the links among the temporal variations of network
+and community structure and the temporal variations of community biomass and
+species richness, we characterized the temporal trajectories of network and
+community structure at each site. We used a method based on second order
+polynomial which allows to assess both the direction and the monotony of
+temporal trends [@rigal_method_2020]. To avoid complex variations of biomass and
+species richness, we selected the stations that displayed monotonic trends for
+theses variable. Over the `r nb_st` stations, the selection procedure resulted
+in XX stations for biomass and species richness analysis.
 
@@
 
-# Result
+We selected the same stations that was used for the temporal analysis.
 
-Overall, we found no significant effect of the temporal gain or losses of total
-biomass and species richness on the relationship between the temporal trends of
-community structure and that of biomass and species richness (slope X, Table X).
+# Statistical analysis
 
-## Community structure and biomass
+## Temporal trends
 
+With the aim to test (1) the relationship among the temporal dynamics of network
+structure from one side and species richness and community biomass from another
+side, (2) if those relationships were different if the communities were
+assembling or disassembling, (3) if those relationships were different if
+small/big communities, we modelled the dynamics the temporal trends of food-web
+structure ($dN$) in function of the temporal trends of community biomass ($dB$) and species
+richness ($dR$), if the latter was positive of not (Inc) and with respectively the median
+community biomass ($B_i$) and species richness ($R_i$)of the three first years of the temporal
+series .
+
+$dN = dB + B_i + dB \times B + Inc \times B_i + dB \times Inc \times B_i$
+
+$dN = dR + R_i + dR \times R_i + Inc \times R_i + dR \times Inc \times R_i$
+
+With:
+
+  - $dN$: temporal trend of network structure and communities structure
+  - $dB$: temporal trend of community (log) biomass
+  - $dR$: temporal trend of (log) species richness 
+  - $B_i$: median community biomass of the first three year
+  - $R_i$: median species richness of the first three year
+  - $Inc$: Is $dB > 0$?
+
+## Spatial trends
+
+Spatial gradient of food-web structure are partly driven by environmental gradients, so
+we controlled relationships among community structure variables by two PCA axis
+synthesizing respectively (1) stream size and (2) average temperature and
+enrichment. Enrichment was characterized by the average Biological Oxygen
+Demand [BOD, @mallin_factors_2006].
+
+$N =  B + R + E_1 + E_2 $
+
+With:
+
+  - $N$: median network structure and communities structure
+  - $B$: median community biomass
+  - $R$: median species richness
+
+# Results
+
+```{r}
+loadd(rsq_sp_mod, summary_table, sp_models, model_summary)
+rsq <- summary_table %>%
+  filter(y %in% get_com_str_var(all = FALSE), x %in% c("log_bm_std",
+      "log_rich_std")) %>%
+select(y, x, mod_summary_table) %>%
+unnest(mod_summary_table) %>%
+select(y, x, r.squared, adj.r.squared)
+```
+
+```{r}
+rsq_nind_bm <- rsq[rsq$y == "piel_nind" & rsq$x == "log_bm_std",]$adj.r.squared %>%
+  round(., 3)
+rsq_bm_rich <- rsq[rsq$y == "log_bm_std" & rsq$x == "log_rich_std",]$adj.r.squared %>%
+  round(., 3)
+rsq_tlvl_rich_sp <- rsq_sp_mod$log_rich_std[
+  rsq_sp_mod$log_rich_std$Response == "w_trph_lvl_avg", 
+  ]$Conditional %>%
+    round(., 3)
+rsq_piel_bm_rich_sp <- rsq_sp_mod$log_bm_std[
+  rsq_sp_mod$log_rich_std$Response == "piel_bm", 
+  ]$Conditional %>%
+    round(., 3)
+```
+
+Overall, we found high heterogeneity in the explicative power of statistical
+models linking temporal dynamics of food-web structure and the one of community biomass and species richness spanning from $R_{adj}^2= `r rsq_nind_bm`$ for
+the relationships between to $R_{adj}^2= `r rsq_bm_rich`$ between biomass and
+species richness (Table \@ref(tab:rsq)). The spatial relationships among
+food-web structure aspects were more performant, with $R_{cond}^2$ varing from 
+`r rsq_tlvl_rich_sp` to `r rsq_piel_bm_rich_sp` (Table \@ref(tab:rsq-sp)).
+
+Overall, we found no significant effect of the temporal gain or losses of
+communinity biomass biomass and species richness on the relationship between the
+temporal trends of community structure and that of biomass and species richness
+(Table \@ref(tab:aov-bm), \@ref(tab:aov-rich)).
+
+## Relationships between temporal trends
+
+### Food-web structure and biomass
+
+```{r}
+loadd(model_log_bm_f3y_table_medium, model_log_rich_f3y_table_medium)
+reg_bm <- model_log_bm_f3y_table_medium$reg_table
+#reg_bm[reg_bm$y == ]
+```
 We found a significant positive relationship between the temporal trends of total biomass from
 one side and species richness, average trophic level, connectance from the other
-side (slopes XX, Figure X, Table X), meaning that they increased in time when
+side (Fig. \@ref(fig:bm), Table \@ref(tab:aov-bm)), meaning that they increased in time when
 the total biomass increased in time and respectively that they decreased in time
@@
 total biomass and that of the pielou of biomass (slopes XX, Figure X, Table X),
-meaning that the pielou value increased in time when the total biomass decreased in time and
-respectively that the pielou value decreased in time when the total biomass
-increase in time. However, we found no relationship between the temporal trends of
-total biomass and that of the pielou of individual.
+meaning that the eveness of biomass across species increased in time when the
+total biomass decreased in time and respectively that the evenness decreased
+in time when the total biomass increase in time (Fig. \@ref(fig:bm), Table
+\@ref(tab:aov-bm)). However, we found no relationship between the temporal
+trends of total biomass and that of the pielou
+of individual.
 
-## Community structure and species richness
+### Community structure and species richness
 
 The temporal trends of total biomass, average trophic level, pielou of biomass,
-pielou of individual had a positive relationship with that of species
-richness (slopes XX, Figure X, Table X). However, the direct relationship
-between the temporal trends of average trophic level and the one of species
-richness was not significant after controling for total biomass temporal trends.
+pielou of individual had a positive relationship with that of species richness
+(Fig. \@ref(fig:rich), Table \@ref(tab:aov-rich)). However, the direct
+relationship between the temporal trends of average trophic level and the one of
+species richness was not significant after controling for total biomass temporal
+trends.
 
@@
 overall species richness of the community (Figure X, Table X). The relationship
-between temporal trends of pielou of individual and that of species richness
-was more positive as the community contained more species (+ XX by species by
-square meter). While the relationship between temporal trends of pielou of
-individual and that of species richness was more negative as the community
-contained more species.
+between temporal trends of pielou of individual and that of species richness was
+more positive as the community contained more species (+ XX by species by square
+meter). While the relationship between temporal trends of pielou of individual
+and that of species richness was more negative as the community contained more
+species.
 
@@
 ```{r}
-loadd(p_fig1_2)
-p_fig1_2
+loadd(p_fig1_2, sp_relation_plot2, predict_plot2)
+theme_set(theme_cowplot())
+p_bm <- get_plot_fig1_2(predict_plot = predict_plot2, get_list = TRUE,
+  bm_x = "bm_std", rich_x = "rich_std"
+  )$bm
+plot_grid(plotlist = p_bm)
+
+sp_bm <- sp_relation_plot2 %>%
+  filter(x == "bm_std")
+p_sp_bm <- sp_bm$gg 
+names(p_sp_bm) <- sp_bm$y
+
+reorder_p_sp_bm <- p_sp_bm
+reorder_p_sp_bm[[1]] <- p_sp_bm$ct_ff 
+reorder_p_sp_bm[[2]] <- p_sp_bm$w_trph_lvl_avg 
+reorder_p_sp_bm[[3]] <- p_sp_bm$piel_nind 
+reorder_p_sp_bm[[4]] <- p_sp_bm$piel_bm 
+reorder_p_sp_bm[[5]] <- p_sp_bm$log_rich_std 
 ```
+
+```{r}
+fig1_left <- plot_grid(plotlist = p_bm, ncol = 1)
+fig1_right <- plot_grid(plotlist = p_sp_bm, ncol = 1)
+#plot_grid(plotlist = list(p_bm[[1]], p_sp_bm[[1]], ), ncol = 1)
+
+ti <- list()
+for (i in 1:5) {
+  ti[[i]] <- list(p_bm[[i]], reorder_p_sp_bm[[i]]) 
+}
+
+```
+
+```{r bm, fig.height = 12}
+# Make the label on two lines 
+top <- plot_grid(plotlist = c(ti[[1]], ti[[2]], ti[[3]], ti[[4]], ti[[5]]), ncol = 2)
+fig1 <- plot_grid(top, p_bm[[6]], ncol = 1, rel_heights = c(1, .1)) 
+fig1
+```
+
+```{r}
+p_rich <- get_plot_fig1_2(predict_plot = predict_plot2, get_list = TRUE)$rich
+#plot_grid(plotlist = p_rich)
+
+sp_rich <- sp_relation_plot2 %>%
+  filter(x == "log_rich_std")
+p_sp_rich <- sp_rich$gg
+names(p_sp_rich) <- sp_rich$y
+
+reorder_p_sp_rich <- p_sp_rich
+reorder_p_sp_rich[[1]] <- p_sp_rich$ct_ff 
+reorder_p_sp_rich[[2]] <- p_sp_rich$w_trph_lvl_avg 
+reorder_p_sp_rich[[3]] <- p_sp_rich$piel_nind 
+reorder_p_sp_rich[[4]] <- p_sp_rich$piel_bm 
+reorder_p_sp_rich[[5]] <- p_sp_rich$log_bm_std
+
+```
+
+```{r}
+fig2_left <- plot_grid(plotlist = p_rich, ncol = 1)
+fig2_right <- plot_grid(plotlist = p_sp_rich, ncol = 1)
+#plot_grid(plotlist = list(p_bm[[1]], p_sp_bm[[1]], ), ncol = 1)
+
+trich <- list()
+for (i in 1:5) {
+  trich[[i]] <- list(p_rich[[i]], reorder_p_sp_rich[[i]]) 
+}
+```
+
+```{r rich, fig.height = 12}
+# Make the label on two lines 
+top_rich <- plot_grid(plotlist = c(trich[[1]], trich[[2]], trich[[3]], trich[[4]], trich[[5]]), ncol = 2)
+fig2 <- plot_grid(top_rich, p_rich[[6]], ncol = 1, rel_heights = c(1, .1))
+fig2
+```
+
+```{r}
+```
+
+# Tables
+
+## Statistical models
+
+### Temporal
+
+```{r}
+loadd(model_log_bm_f3y_table_medium, model_log_rich_f3y_table_medium)
+```
+
+```{r}
+model_log_bm_f3y_table_medium[["anova_table"]] %>% 
+  filter(y %in% get_com_str_var(all = FALSE)) %>%
+  select(-mod_summary_table) %>%
+  format_anova_table() %>%
+  kable(., booktabs = TRUE,
+    caption = 
+      paste0(
+      "ANOVA results for the links between the temporal trends of 
+      community biomass and the temporal trends of the network structure."
+    ),
+  label = "tab:aov-bm"
+
+  ) %>%
+  kable_styling(latex_options =c("scale_down", "stripped")) %>%
+  collapse_rows(columns = 1, valign = "top")
+```
+
+```{r}
+model_log_rich_f3y_table_medium[["anova_table"]] %>% 
+  filter(y %in% get_com_str_var(all = FALSE)) %>%
+  select(-mod_summary_table) %>%
+  format_anova_table() %>%
+  kable(., booktabs = TRUE,
+    caption = 
+      paste0(
+      "ANOVA results for the links between the temporal trends of species
+      richness and the temporal trends of the network structure."
+    ),
+  label = "tab:aov-rich"
+  ) %>%
+  kable_styling(latex_options =c("scale_down", "stripped")) %>%
+  collapse_rows(columns = 1, valign = "top")
+```
+
+```{r}
+model_log_bm_f3y_table_medium$reg_table %>% 
+  filter(y %in% get_com_str_var(all = FALSE)) %>%
+  format_reg_table() %>%
+  kable(., booktabs = TRUE,
+    caption = 
+      paste0(
+      "Regression coefficients for the linear models explaining the links
+      between the temporal trends of community biomass and the temporal trends
+      of the network structure."),
+  label = "tab:reg-bm"
+  ) %>%
+  kable_styling(latex_options =c("scale_down", "stripped")) %>%
+  collapse_rows(columns = 1, valign = "top")
+```
+
+```{r}
+model_log_rich_f3y_table_medium$reg_table %>% 
+  filter(y %in% get_com_str_var(all = FALSE)) %>%
+  format_reg_table() %>%
+  kable(., booktabs = TRUE,
+    caption = 
+      paste0(
+      "Regression coefficients for the linear models explaining the links
+      between the temporal trends of species richness and the temporal trends of
+      the network structure."
+    ),
+  label = "tab:reg-rich"
+  ) %>%
+  kable_styling(latex_options =c("scale_down", "stripped")) %>%
+  collapse_rows(columns = 1, valign = "top")
+```
+
+```{r}
+rsq %>%
+  rename(
+    Response = y, Explicative = x, 
+    `Squared R` = r.squared, `Adjusted squared R` = adj.r.squared
+  ) %>% 
+  select(Explicative, Response, everything()) %>%
+  kable(., booktabs = TRUE,
+    caption = 
+      paste0(
+      "Squared and adjusted squared R for linear models of spatial relationships."),
+  label = "tab:rsq"
+      ) %>% # 
+  kable_styling(latex_options =c("scale_down", "stripped")) %>%
+  collapse_rows(columns = 1, valign = "top")
+```
+
+### Spatial
+
+```{r}
+loadd(tab_sp_anova)
+```
+
+```{r}
+tab_sp_anova$log_bm_std %>%
+  mutate(
+    y = str_replace_all(y, var_replacement()),
+    term = str_replace_all(term, var_replacement()),
+  ) %>%
+  kable(., booktabs = TRUE,
+    caption = 
+      paste0(
+      "ANOVA results for the links between the spatial variation of community
+      biomass and the one of network structure."),
+  label = "tab:aov-bm-sp"
+  ) %>%
+  kable_styling(latex_options =c("scale_down", "stripped")) %>%
+  collapse_rows(columns = 1, valign = "top")
+```
+
+```{r}
+tab_sp_anova$log_rich_std %>%
+  mutate(
+    y = str_replace_all(y, var_replacement()),
+    term = str_replace_all(term, var_replacement()),
+  ) %>%
+  kable(., booktabs = TRUE,
+    caption = 
+      paste0(
+      "ANOVA results for the links between the spatial variation of species
+      richness and the one of network structure."),
+  label = "tab:aov-rich-sp"
+      ) %>% # 
+  kable_styling(latex_options =c("scale_down", "stripped")) %>%
+  collapse_rows(columns = 1, valign = "top")
+```
+
+```{r}
+
+table_rsq_sp <- map2(rsq_sp_mod, names(rsq_sp_mod),
+  ~mutate(.x, Explicative = .y) %>%
+    select(Explicative, Response, Marginal, Conditional)
+) %>%
+do.call(rbind, .)
+
+table_rsq_sp %>%
+  mutate(
+    Explicative = str_replace_all(Explicative, var_replacement()),
+    Response = str_replace_all(Response, var_replacement())
+  ) %>%
+  kable(., booktabs = TRUE,
+    caption = 
+      paste0(
+      "Marginal and conditional squared R for spatial models."),
+  label = "tab:rsq-sp"
+      ) %>% # 
+  kable_styling(latex_options =c("scale_down", "stripped")) %>%
+  collapse_rows(columns = 1, valign = "top")
+
+```

### 2021-05-27 report_rdv.Rmd
Add spatial analysis and results

@@
 ```{r}
-loadd(sp_relation_plot)
+loadd(sp_relation_plot2)
 plot_grid(plotlist = sp_relation_plot$gg)
@@
 ```
+
+## Connectance and biomass
+
+```{r}
+
+loadd(est_sp_models, colin_sp_models, sp_models)
+loadd(data4model, sp_st_data, summary_var_med)
+data4model[1, ]$data_model[[1]]
+
+est_sp_models$log_bm_std$ct_ff
+colin_sp_models$log_bm_std$ct_ff
+cf_bm_sp_mod <- sp_models$log_bm_std$ct_ff
+```
+
+On ne trouve pas d'effet de la biomasse sur la connectance, à part quand on la
+controle pour la richness. Ce qui se comprend car la richness a un effet très
+fort sur la connectance, qui enlève du coup beaucoup de variabilité.
+
+```{r}
+test_sp_model <- get_mod_list(.data = as.data.frame(sp_st_data))
+est_sp_models = map(test_sp_model, broom.mixed::tidy)
+```
+```{r}
+test_mod <- lm(ct_ff ~ log_RC1 + log_RC2 + log_bm_std, as.data.frame(sp_st_data))
+test_mod_rich <- lm(ct_ff ~ log_RC1 + log_RC2 + log_bm_std + log_rich_std, as.data.frame(sp_st_data))
+```
+
+##
+
+##
+
+```{r}
+loadd(sp_models, anova_table_sp, tab_sp_anova)
+
+```

### 2021-05-27 R/plan.R

@@ -2,7 +2,7 @@
 # Details: https://books.ropensci.org/drake/plans.html
 
 # Variable:
-model_x_var <- c("log_bm_std", "rich_std", "log_rich_std", "ct_ff", "w_trph_lvl_avg", "nind_std")
+model_x_var <- c("bm_std", "rich_std", "ct_ff", "w_trph_lvl_avg", "nind_std")
 #model_y_var <- c("ct_ff", "w_trph_lvl_avg", "rich_std", "log_rich_std", "w_trph_lvl_avg")
 
 plan <- drake_plan(
@@ -118,6 +118,7 @@ plan <- drake_plan(
     st_mono = st_mono_trends_combined_list, type = "min_max"),
 
   # 2.2 Environment
+  st_analysis_by_var = get_station_analysis_by_var(classif = rigal_classification),
   st_analysis = get_all_station_analysis(classif = rigal_classification),
   data_for_pca = habitat_press %>%
     filter(station %in% st_analysis) %>%
@@ -187,9 +188,11 @@ plan <- drake_plan(
     filter(station %in% st_analysis) %>%
     select(all_of(c("station", "basin", "log_RC1", "log_RC2", get_all_var_analysis()))) %>%
     na.omit,
-  sp_models = get_mod_list(.data = as.data.frame(sp_st_data)),
-  colin_sp_models = map(sp_models, car::vif),
-  est_sp_models = map(sp_models, broom.mixed::tidy),
+  st_sp = st4sp_model(my_x_var = model_x_var, .data4model = data4model),
+  sp_models = map(st_sp,
+    ~get_mod_list(.data = as.data.frame(sp_st_data[sp_st_data$station %in% .x, ]))),
+  colin_sp_models = map(sp_models, ~map(.x, car::vif)),
+  est_sp_models = map(sp_models, ~map(.x, broom.mixed::tidy)),
 
   #4. The plots
   p_bm_vs_bm_slope = plot_bm_vs_bm_slope(
@@ -199,13 +202,21 @@ plan <- drake_plan(
   p_hist_med_bm = plot_hist_med_bm(.data = full_data2),
   p_cross_classif_bm_rich = plot_matrix_bm_rich_cross_classif(
     classif = rigal_classification),
-  p_fig1_2 = get_plot_fig1_2(predict_plot = predict_plot2),
+  p_fig1_2 = get_plot_fig1_2(predict_plot = predict_plot2,
+    bm_x = "bm_std", rich_x = "rich_std"
+    ),
[…]

### 2021-05-27 R/plot_methods.R

@@ -1359,6 +1359,41 @@ format_table <- function (x = tmp_stab_indir_table) {
   x
 }
 
+format_anova_table <- function (x = NULL, slope = FALSE) {
+  x <- x[, c("y", names(x)[!names(x) %in% "y"])]
+
+  rm_n <- str_remove_all(var_replacement(slope), pattern = "\n ")
+  names(rm_n) <- names(var_replacement(slope)) 
+  x$y <- str_replace_all(x$y, rm_n)
+
+  term_replacement <- c(
+    log_bm_slope = "Biomass trend",
+    bm_slope = "Biomass trend",
+    bm_std = "Biomass",
+    log_rich_slope = "Richness trend",
+    rich_slope = "Richness trend",
+    rich_std = "Richness",
+    inc_f = "Positive"
+  )
+
+  x$term <- str_replace_all(x$term, term_replacement)
+
+  #colnames(x) %<>% str_remove_all(., pattern = "via_")
+
+  col_replacement <- c(
+    df = "DF",
+    y = "Variable",
+    term = "Term",
+    sumsq = "SS",
+    meansq = "MSS",
+    statistic = "Statistic",
+    p.value = "P"
+  )
+  colnames(x) %<>% str_replace_all(., col_replacement)
+
+  return(x)
+}
+
 plot_sensivity_analysis <- function (.data = NULL, y_lim = c(-1.26, .75), inverse_label_order = FALSE) {
   .data %<>%
     mutate(

### 2021-05-27 paper/manuscript.Rmd
Fix results

@@
 bibliography: references.bib 
+fontsize: 12pt
 output:
-  prettydoc::html_pretty:
-    theme: cayman
-    highlight: github
-    math: katex
+  bookdown::html_document2:
+    fig_caption: true
+    theme: "journal"
 ---
@@
 theme_set(mytheme)
+bookdown::html_document2
+library(bookdown)
+```
+```{r}
+net_var_bm <- c("log_rich_std", "ct_ff", "w_trph_lvl_avg", "piel_bm",
+      "piel_nind")
+net_var_rich <- c("log_bm_std", "ct_ff", "w_trph_lvl_avg", "piel_bm",
+      "piel_nind")
 ```
@@
 ## Data selection
+
+We selected the stations that have been monitored at least 10 times on the
+1995-2018 period.
 
@@
 
-We described community structure by its total biomass, species richness and the
+We described community structure by its community biomass, species richness and the
 evenness of the number of individual and the amount of biomass across species. The evenness was
@@
 rsq <- summary_table %>%
-  filter(y %in% get_com_str_var(all = FALSE), x %in% c("log_bm_std",
-      "log_rich_std")) %>%
+  filter(y %in% unique(c(net_var_bm, net_var_rich))) %>%
 select(y, x, mod_summary_table) %>%
@@
 Overall, we found high heterogeneity in the explicative power of statistical
-models linking temporal dynamics of food-web structure and the one of community biomass and species richness spanning from $R_{adj}^2= `r rsq_nind_bm`$ for
-the relationships between to $R_{adj}^2= `r rsq_bm_rich`$ between biomass and
+models linking temporal dynamics of food-web structure and the one of community
+biomass and species richness spanning from $R_{adj}^2= `r rsq_nind_bm`$ for the
+relationships between to $R_{adj}^2= `r rsq_bm_rich`$ between biomass and
 species richness (Table \@ref(tab:rsq)). The spatial relationships among
@@
 
-### Food-web structure and biomass
+### Community structure and community biomass
 
@@
 ```
-We found a significant positive relationship between the temporal trends of total biomass from
-one side and species richness, average trophic level, connectance from the other
-side (Fig. \@ref(fig:bm), Table \@ref(tab:aov-bm)), meaning that they increased in time when
-the total biomass increased in time and respectively that they decreased in time
-when the total biomass decreased in time.
+We found a significant positive relationship between the temporal trends of
+community biomass from one side and species richness, average trophic level,
+connectance from the other side (Fig. \@ref(fig:bm), Table \@ref(tab:aov-bm)),
+meaning that they temporally increased when the community biomass temporally increased and
+respectively that they temporally decreased when the community biomass decreased in
+time.
 
-We found that a significant negative relationship between the temporal trends of
-total biomass and that of the pielou of biomass (slopes XX, Figure X, Table X),
-meaning that the eveness of biomass across species increased in time when the
-total biomass decreased in time and respectively that the evenness decreased
-in time when the total biomass increase in time (Fig. \@ref(fig:bm), Table
-\@ref(tab:aov-bm)). However, we found no relationship between the temporal
-trends of total biomass and that of the pielou
-of individual.
+We found a significant negative relationship between the temporal trends of
+community biomass and that of the pielou of biomass (Figure \@ref(fig:bm), Table
+\@ref(tab:aov-bm)), meaning that the eveness of biomass across species
+temporally increased when the community biomass temporally decreased and
+respectively that the evenness temporally decreased when the community biomass
+temporally increased (Fig. \@ref(fig:bm), Table \@ref(tab:aov-bm)). However, we
+found no significant relationship between the temporal trends of community biomass and that
+of the pielou of individual.
+
+Overall, we did not find effect of assembly/disassembly on the relationships
+between the temporal trends of community structure and the one of community
+biomass. We also found that the median community biomass had no effect on the
+relationship between the temporal trends of community structure and the one of community
+biomass.
 
@@
 
-The temporal trends of total biomass, average trophic level, pielou of biomass,
+The temporal trends of community biomass, average trophic level, pielou of biomass,
 pielou of individual had a positive relationship with that of species richness
@@
 relationship between the temporal trends of average trophic level and the one of
-species richness was not significant after controling for total biomass temporal
-trends.
+species richness was not significant after controling for community biomass temporal
+trends [**TO CHECK: refaire tous les modèles temporels en mettant à la fois la
+pente des biomasses et de la richness en même temps??**].
 
@@
 individual and connectance and that of species richness was dependant of the
-overall species richness of the community (Figure X, Table X). The relationship
-between temporal trends of pielou of individual and that of species richness was
-more positive as the community contained more species (+ XX by species by square
-meter). While the relationship between temporal trends of pielou of individual
-and that of species richness was more negative as the community contained more
-species.
+overall species richness of the community (Fig. \@ref(fig:rich), Table
+\@ref(tab:aov-rich)), meaning that the relationship between temporal trends of
+pielou of individual and that of species richness was more positive as the
+community contained more species (Fig. \@ref(fig:rich), Table
+\@ref(tab:reg-rich)). While the relationship between temporal trends of pielou
+of individual and that of species richness was more negative as the community
+contained more species (Fig. \@ref(fig:rich), Table \@ref(tab:reg-rich)).
+
+## Spatial relationships
+
+### Community structure and community biomass
+
+We found that species richness, connectance, average trophic level were
+spatially positively related to community biomass while the pielou of biomass was negatively related to
+community biomass (Fig. \@ref(fig:bm), Table \@ref(tab:aov-rich-sp)). However,
+we found no spatial relation between the pielou of individual and community
+biomass.
+
+### Community structure and species richness
+
+We found that community biomass, the pielou of biomass and individual were
+positively related to species richness while average trophic level and
+connectance were negatively related to
+community biomass (Fig. \@ref(fig:rich), Table \@ref(tab:aov-rich-sp)).
 
@@
 
+## Biomass temporal dynamics is linked to the top trophic level
+
+We found that the temporal increase of the average trophic level was positively
+linked to increase of community biomass. Increase of average trophic level can
+be associated to either gain of biomass in the highest trophic level nor losses
+of biomass in the lowest trophic. In our case, such gain or losses of average
+trophic level is probably associated to the variations of the presence of large
+fishes. This interpretation is confirmed by the finding that the evenness of
+biomass, measured by the pielou, decreased through time as community biomass
+decrease and reversely, meaning that biomass distribution across species
+respectively become respectively less and more even when community biomass
+decrease and increase. We also found no relationship between the temporal trends of evenness based
+on indivual number and that community biomass, confirming that the temporal trends
+of community biomass in our study is linked to few big individuals. It further
+indicates that temporal loss of community biomass are linked with the loss of
+the higher trophic level.
+
+We also found in space that evenness of biomass was positively related to
+community while eveness of individual number had no relation. It constrasts with
+previous studies which found a negative relationship between biomass and eveness
+of individual in marine and plant communities [@drobner_relation_1998;
+@maureaud_biodiversityecosystem_2019] or studies that found more even plant
+communities in terms of individual number display higher community biomass
+[@wisley_biodiversity_2000].
+
+We further found that the temporal trends of connectance was positively
+linked to that one of community biomass, meaning that connectance increases through
+time in a given site when community biomass increases through time and reversely.
+This is in line with the fact that the fishes located at higher trophic level
+also display a larger number of links as the size of the predation window
+increases with the size of the fishes. This result is also in accordance with  
+theoretical work showing that higher food-web connectance result in higher
+community biomass [@thebaut_food-web_2003].
+
+##  Biomass and richness variation are not the same process
+
+To the difference with community biomass, the temporal trends evenness of
+biomass and individual were positively related to the temporal trends of species
+richness, meaning that as community biomass temporally increase, the
+distribution of biomass and abondance become more even. Our results indicate
+that biomass trends are linked to few big individuals while richness trends are
+linked to overall shift in dominance in communities.
+
+Surprinsingly, we found the temporal trends of connectance was not related to
+the one of species richness as found spatially in most empirical foodweb
+[@dunne_network_2006]. However, the relationship become slightly negative for
+species poor communities. An explanation might be that species-rich communities
+already contains a significant number of piscivores, which have the most links
+whereas species poor communites contains few piscivores.
+
 ## Temporal dynamics confirms space for time substitution BEF
 
-The temporal dynamic of the species richness was positively linked to that of
-biomass. In non-temporal data, this result was already found in streams
-[@woods_testing_2020; @danet_species_nodate] but also in grasslands salt marches
-and forests [@hector_plant_1999; @tilman_biodiversity_2014;
-@wu_relationship_2015; @li_relationship_2018; but see @grace_integrative_2016]. Therefore,
-our results confirm BEF prediction works also in time.
-
-*From the previous manuscript*: the positive relationship of species richness on total
+Spatially and temporally, the species richness was positively linked to that of
+biomass. Spatially, this result is in accordance with numerous studies was
+already found in streams [@woods_testing_2020; @danet_species_nodate] but also
+in grasslands, salt marches and forests [@hector_plant_1999;
+@tilman_biodiversity_2014; @wu_relationship_2015; @li_relationship_2018; but see
+@grace_integrative_2016]. Therefore, our results confirm that BEF prediction
+works also in time. The positive relationship of species richness on total
 biomass might be due to resource use complementarity [@carey_determining_2011],
@@
 
-We found the temporal dynamic of connectance was negative associated, but
-weakly, with that one of species richness as found in most empirical foodweb
-[@dunne_network_2006]. The relationship is very weak in species rich commuties
-and more negative for species poor commuties. An explanation might be that
-species-rich communities already contains a significant number of piscivores, which have the
-most links whereas species poor communites contains few piscivores.
+HERE
+ @soininen_relationship_2012;
 
-The temporal dynamic of the average trophic level had no relationship with the
+The temporal trend of the average trophic level had no relationship with the
 one of species richness. It is surprising because one can imagine that loss and
@@
 found to be positively or negatively related to individual eveness
-[@soininen_relationship_2012; @maureaud_biodiversity_2019].
-
-## Biomass temporal dynamics is linked to the top trophic level
-
-We further found that the temporal dynamic of the average trophic level was positively
-linked to that of biomass. Increase  of average trophic level can be associated
-to either gain of biomass in the highest trophic level nor losses of biomass in
-the lowest trophic. In our case, such gain or losses of average trophic level is
-certainly associated to the loss or the gain of the biggest individuals. Because
-it seems unlikely that a community gain or loss biomass while respectively
-losing or gaining individuals. Pielou index temporal dynamics further confirm
-this interpretation.
-
-We found that the pielou of biomass decrease through time
-as total biomass decrease and reversely, meaning that biomass distribution
-across species respectively became less and more even when total biomass
-decrease and increase. The structuration in size class of the community might
-explain this pattern.
-
-Finally, we found no relationship between the temporal
-dynamics of pielou based on indivual number and that one of biomass, confirming
-that the temporal trends of total biomass in our study is linked to few big
-individuals. @maureaud_biodiversity_2019 found negative relationship between
-biomass and eveness of indivual in marine ecosystem. One explanation is that
-marine ecosystem studied in [@maureaud_biodiversity_2019] are much larger than
-the stream communities studied in this study.
-
-We further found that the temporal dynamic of connectance was positively
-linked to that one of total biomass, meaning that connectance increases through
-time in a given site when total biomass increases through time and reversely.
-This is in line with the fact that the fishes located at higher trophic level
-also display a larger number of links as the size of the predation window
-increases with the size of the fishes. This is because the predation window of
-freshwater fish species is highly nested.
-
-##  Biomass and richness variation are not the same process
-
-Our results indicate that biomass trends are linked to few big individuals while
-richness trends are linked to overall shift in dominance in communities. This
-results has profound implications for conservation. As more and more studies
-report biomass and richness temporal dynamics [@hallmann_more_2017;
-@ceballos_biological_2017], it is important to note that they might not be
-equivalent in terms of consequences on the structure of the community. Further
-studies should investigate several dimensions of community structure because it
-drives many aspects of ecosystem functioning.
-
-## Biomass and richness gains and losses are symmetric processes in terms of community structure
-
-We found no case in which gain or losses of biomass and richness lead to
-different relationship between the temporal dynamic of community structure and
-the one of biomass and species richness. We could have imagine that
-extinction/colonisation processes or immigration/extinction debt could have lead
-to different relationships.
+[ @maureaud_biodiversityecosystem_2019].
 
@@
 
-We found that total biomass was linked positively related to species richness
+We found that community biomass was linked positively related to species richness
 both in space and in time, indicating that space for time might be use. In the
 same way, we found a positive positive relationship between average trophic
-level and total biomass both in time and in space. However, it was not the case
+level and community biomass both in time and in space. However, it was not the case
 for connectance and average trophic level that were respectively weakly or not
@@
 spatial gradient.
+
+This result has profound implications for conservation. As more and more
+studies report community biomass and richness trends [@hallmann_more_2017;
+@ceballos_biological_2017], it is important to note that they might not be
+equivalent in terms of consequences on the structure of the community. Further
+studies should investigate the temporal trends of several dimensions of
+community structure simultaneously because it drives many aspects of ecosystem functioning.
+
+## Biomass and richness gains and losses are symmetric processes in terms of community structure
+
+We found no case in which gain or losses of biomass and richness lead to
+different relationship between the temporal dynamic of community structure and
+the one of biomass and species richness. We could have imagine that
+extinction/colonisation processes or immigration/extinction debt could have lead
+to different relationships.
 
@@
 ```{r}
+fig_bm_cap <- paste0(
+  "Relationship between community structure and community biomass. Left panel
+  displays the relationships between the temporal trends of community structure
+  and the one of community biomass. Lines correspond to the predictions of the
+  linear models while the points are colored according the median community
+  biomass of the three first years of the given temporal series. The lines surrounding each point represent
+  the standard error associated to the temporal trends. Right panel displays the
+  spatial relationship between median community structure over time and the
+  median community biomass over time."
+
+)
+
+fig_rich_cap <- paste0(
+  "Relationship between community structure and species richness. Left panel
+  displays the relationships between the temporal trends of community structure
+  and the one of species richness. Lines correspond to the predictions of the
+  linear models while the points are colored according the median species
+  richness of the three first years of the given temporal series. The lines
+  surrounding each point represent the standard error associated to the temporal
+  trends. Right panel displays the spatial relationship between median community
+  structure over time and the median species richness over time."
+
+)
+```
+
+```{r}
 loadd(p_fig1_2, sp_relation_plot2, predict_plot2)
@@
 p_bm <- get_plot_fig1_2(predict_plot = predict_plot2, get_list = TRUE,
-  bm_x = "bm_std", rich_x = "rich_std"
+  bm_x = "log_bm_std", rich_x = "log_rich_std",
+  bm_y = c("ct_ff", "w_trph_lvl_avg", "piel_nind", "piel_bm", "log_rich_std") 
   )$bm
-plot_grid(plotlist = p_bm)
+names(p_bm) <- c("ct_ff", "w_trph_lvl_avg", "log_rich_std", "piel_nind",
+  "piel_bm") 
+#plot_grid(plotlist = p_bm)
 
 sp_bm <- sp_relation_plot2 %>%
-  filter(x == "bm_std")
+  filter(x == "log_bm_std")
 p_sp_bm <- sp_bm$gg 
@@
 ```{r}
-fig1_left <- plot_grid(plotlist = p_bm, ncol = 1)
-fig1_right <- plot_grid(plotlist = p_sp_bm, ncol = 1)
-#plot_grid(plotlist = list(p_bm[[1]], p_sp_bm[[1]], ), ncol = 1)
-
 ti <- list()
-for (i in 1:5) {
-  ti[[i]] <- list(p_bm[[i]], reorder_p_sp_bm[[i]]) 
+for (i in c("log_rich_std", "w_trph_lvl_avg",  "piel_bm", "piel_nind", "ct_ff")) {
+  ti[[i]] <- list(p_bm[[i]], p_sp_bm[[i]]) 
 }
-
 ```
 
-```{r bm, fig.height = 12}
+```{r bm, fig.height = 12, fig.cap=fig_bm_cap}
 # Make the label on two lines 
@@
 ```{r}
-p_rich <- get_plot_fig1_2(predict_plot = predict_plot2, get_list = TRUE)$rich
+p_rich <- get_plot_fig1_2(
+  predict_plot = predict_plot2,
+  get_list = TRUE,
+  rich_x = "log_rich_std",
+  rich_y = c("ct_ff", "w_trph_lvl_avg", "piel_nind", "piel_bm", "log_bm_std") 
+  )$rich
+names(p_rich) <- c(
+  "ct_ff", "w_trph_lvl_avg", "piel_nind",
+  "piel_bm", "log_bm_std")
 #plot_grid(plotlist = p_rich)
@@
 names(p_sp_rich) <- sp_rich$y
-
-reorder_p_sp_rich <- p_sp_rich
-reorder_p_sp_rich[[1]] <- p_sp_rich$ct_ff 
-reorder_p_sp_rich[[2]] <- p_sp_rich$w_trph_lvl_avg 
-reorder_p_sp_rich[[3]] <- p_sp_rich$piel_nind 
-reorder_p_sp_rich[[4]] <- p_sp_rich$piel_bm 
-reorder_p_sp_rich[[5]] <- p_sp_rich$log_bm_std
-
 ```
@@
 trich <- list()
-for (i in 1:5) {
-  trich[[i]] <- list(p_rich[[i]], reorder_p_sp_rich[[i]]) 
+for (i in c("log_bm_std", "w_trph_lvl_avg",  "piel_bm", "piel_nind", "ct_ff")) {
+  trich[[i]] <- list(p_rich[[i]], p_sp_rich[[i]]) 
 }
@@
 
-```{r rich, fig.height = 12}
+```{r rich, fig.height = 12, fig.cap=fig_rich_cap}
 # Make the label on two lines 
@@
 
-```{r}
-```
-
-# Tables
+# Tables {-}
 
@@
 model_log_bm_f3y_table_medium[["anova_table"]] %>% 
-  filter(y %in% get_com_str_var(all = FALSE)) %>%
+  filter(y %in% net_var_bm) %>%
   select(-mod_summary_table) %>%
@@
 model_log_rich_f3y_table_medium[["anova_table"]] %>% 
-  filter(y %in% get_com_str_var(all = FALSE)) %>%
+  filter(y %in% net_var_rich) %>%
   select(-mod_summary_table) %>%
@@
 model_log_bm_f3y_table_medium$reg_table %>% 
-  filter(y %in% get_com_str_var(all = FALSE)) %>%
+  filter(y %in% net_var_bm) %>%
   format_reg_table() %>%
@@
 model_log_rich_f3y_table_medium$reg_table %>%
-  filter(y %in% get_com_str_var(all = FALSE)) %>%
+  filter(y %in% net_var_rich) %>%
   format_reg_table() %>%
@@
 tab_sp_anova$log_bm_std %>%
+  filter(y %in% net_var_bm) %>%
   mutate(
@@
 tab_sp_anova$log_rich_std %>%
+  filter(y %in% net_var_rich) %>%
   mutate(
@@
       ) %>% # 
-  kable_styling(latex_options =c("scale_down", "stripped")) %>%
+  kable_styling(latex_options = c("scale_down", "stripped")) %>%
   collapse_rows(columns = 1, valign = "top")
@@
 ```{r}
-
 table_rsq_sp <- map2(rsq_sp_mod, names(rsq_sp_mod),
@@
 do.call(rbind, .)
+rownames(table_rsq_sp) <- NULL
 
 table_rsq_sp %>%
+  filter(Explicative %in% c("log_rich_std", "log_bm_std")) %>%
   mutate(

### 2021-05-27 make.R

@@ -42,6 +42,9 @@ get_st_mono_trends(.df = rigal_classification, xvar = "rich_std")
 get_st_mono_trends(.df = rigal_classification, xvar = "log_rich_std")
 
 comb %>%
+  filter(y == "log_bm_std")
+
+comb %>%
     mutate(
       data_model = map2(x, y, function (myx, myy, classif) {
 	get_y_versus_x_trends(classif = classif, x_var = myx, y_var = myy) %>%

### 2021-05-28 paper/manuscript.Rmd
Write introduction

@@
 ---
-title: "More than space for time: revealing the tight links constraining the temporal dynamics of network structure"
+title: "Biomass and species richness temporal trends drives the assembly and the disassembly of food-web in natural fish assemblages"
 author: "Alain Danet, Maud Mouchet, Loubna El Madouri, Colin Fontaine (ordre non fixé)"
@@
 theme_set(mytheme)
-bookdown::html_document2
-library(bookdown)
 ```
@@
 ```
+
+# Introduction
+
+## community structure are dynamics and affect ecosystem functions
+
+Biodiversity to affect ecosystem properties such as total biomass, productivity
+and stability [@tilman_biodiversity_2014; @loreau_biodiversity_2001]. Numerous
+studies have shown the decline of population and community biomass
+[@ceballos_biological_2017; @hallmann_more_2017; @albano_native_2021], as well
+as ongoing extinction [@barnosky_]. Consequences of such trends on various
+aspects of community structure are not well known whereas numerous ecological studies
+have shown that the different aspects of community structure are tightly linked [REF].
+
+The link between Biodiversity and ecosystem functioning is one of the most
+famous example, experimental studies are in accordance to show a positive
+relationship between species richness and community biomass
+[@tilman_biodiversity_2014; @pennekamp_biodiversity_2018]. But this relation is
+not always found in natural settings [@grace_integrative_2016;
+@li_relationship_2018; @maureaud_biodiversityecosystem_2019]. Also, numerous
+studies have found relation between species richness and evenness, showing that
+communities become more or less even as species richness increase
+[@soininen_relationship_2012; @ma_species_2005;
+@maureaud_biodiversityecosystem_2019], highlighting the diversity of
+assembly processes in ecological communities.
+
+The distribution and the number of ecological interactions, i.e. the structure
+of ecological networks, also covary. In food-web, connectance, which measures the
+degree of generalism in a network, has been theoretically shown to theoretically
+positively scale with community biomass [@thebaut_food-web_2003]. Connectance
+has been also shown to be negatively related to species richness in empirical
+food-webs [@dunne_network_2006]. Trophic level has also been shown to be
+positively linked to total biomass in theoretical models
+[@wang_biodiversity_2018]. All together, these studies show that the
+different dimensions of network structure are closely linked.
+
+The space for time substitution allows to use the studies mentioned above to
+predict how changes in species richness or community biomass will in turn affect
+community and network structure. The hypothesis that space can be use to
+surrogate space is often implicitly made in ecological studies. This method
+began to be widely used in the early 20th century to infer the temporal
+succession of vegetation from space variations [@pickett_space-time_1989].  It
+supposes a homology between variations in space and in time i.e. that spatial
+sequence corresponds to temporal sequences. This methods have raised criticisms
+[@damgaard_critique_2019], with studies showing the coherent in space and time
+[@blois_space_2013] or not [@johnson_testing_2008; @adler_contrasting_2007].
+Spatial turnover of species composition, dispersal limitation, disturbance and
+stochastic processes  has been hypothesised to be responsible for the failure of
+space for time substitution [@adler_contrasting_2007; @blois_space_2013].
+
+In this line, how biomass and species richness temporal trends are linked to
+change in food-web structure is still an open question, as well as if space for
+time substitution works in food-web assembly. The increasing availability of
+ecological temporal series makes possible to assess those questions.
+
+Using a standardized monitoring of fish freshwater communities on the period
+1995-2018, we assessed the relationships among temporal trends of food-web
+structure, trends of community biomass and trends in species richness.  
+Moreover, we tested if the those relationships differs between communities that
+lossed or gained biomass/species richness across time, reflecting potential
+difference between disassembly and assembly processes. We finally assessed if
+spatial relationships display the same patterns than temporal ones, to assess
+the validity of space for time substitution.
 
@@
 ```{r}
-loadd(com_analysis_data, full_data2)
+loadd(com_analysis_data, full_data2, st_mono_trends_combined_list)
 ```
@@
 nb_st <- unique(full_data2$station) %>% length
+nb_st_var <- map_dbl(st_mono_trends_combined_list$station, length) 
+names(nb_st_var) <- st_mono_trends_combined_list$variable
 ```
@@
 theses variable. Over the `r nb_st` stations, the selection procedure resulted
-in XX stations for biomass and species richness analysis.
+in respectively `r nb_st_var["log_bm_std"]` stations  and `r nb_st_var["log_rich_std"]`
+for community biomass and species richness analysis.
 
@@
   - $Inc$: Is $dB > 0$?
+
+In order to control for the uncertainties of the estimated temporal trends, we
+weighted each temporal trends by the inverse of the product between the standard
+error of the estimated trends, i.e. slopes, for the response and the explicative
+variable.
 
@@
 
-- Main results:
-  - different mechanisms for richness and biomass
-  - space for time subtitution works for biomass and tlvl but not for
-    connectance
-
 ## Biomass temporal dynamics is linked to the top trophic level
@@
 biomass and individual were positively related to the temporal trends of species
-richness, meaning that as community biomass temporally increase, the
+richness, meaning that as species richness temporally increase, the
 distribution of biomass and abondance become more even. Our results indicate
@@
 the one of species richness as found spatially in most empirical foodweb
-[@dunne_network_2006]. However, the relationship become slightly negative for
-species poor communities. An explanation might be that species-rich communities
-already contains a significant number of piscivores, which have the most links
-whereas species poor communites contains few piscivores.
+[@dunne_network_2006] and also in the present study. This result suggests that
+the structure of food-webs might be not very sensitive to variation of species
+richness and that species loss and gain concerns species of low trophic level,
+which in turn does not affect connectance. However, the relationship become
+slightly negative for species poor communities. An explanation might be that
+species-rich communities already contains a significant number of piscivores,
+which have the most links whereas species poor communites contains few
+piscivores.
 
@@
 Spatially and temporally, the species richness was positively linked to that of
-biomass. Spatially, this result is in accordance with numerous studies was
+community biomass. Spatially, this result is in accordance with numerous studies was
 already found in streams [@woods_testing_2020; @danet_species_nodate] but also
@@
 
+- Add loss of species richness, loss of biomass and increase dominance?
+
 HERE
@@
 
-The temporal trend of the average trophic level had no relationship with the
-one of species richness. It is surprising because one can imagine that loss and
-gain of species would reveal assembly/disassembly mechanisms in terms of trophic
-structure. However, we found that when species richness increases, the
-distribution of biomass and individuals among species become more even in the
-community, meaning that dominance decrease. Species richness has often been
-found to be positively or negatively related to individual eveness
-[ @maureaud_biodiversityecosystem_2019].
+---
+#The temporal trend of the average trophic level had no relationship with the
+#one of species richness. It is surprising because one can imagine that loss and
+#gain of species would reveal assembly/disassembly mechanisms in terms of trophic
+#structure. However, we found that when species richness increases, the
+#distribution of biomass and individuals among species become more even in the
+#community, meaning that dominance decrease.
+---
 
@@
 both in space and in time, indicating that space for time might be use. In the
-same way, we found a positive positive relationship between average trophic
+same way, we found a positive relationship between average trophic
 level and community biomass both in time and in space. However, it was not the case
@@
 relation in space. Moreover, connectance displayed a strong positive
-relationship (move to results?) with biomass in time but not in space.
-
-Space for time substitution is a widely
-used tool in ecology [@pickett_space-for-time_1989; @blois_space_2013;
-@damgaard_critique_2019]. However, the drivers of spatial variation might not
-be the ones that drive community variation in time. The successional processes
-driving the assembly or the disassembly of communities might not be reflected in
-spatial gradient.
+relationship with biomass in time but not in space. This result is in accordance
+with other studies which found mismatch between spatial and temporal patterns
+[@adler_contrasting_2007; @johnson_testing_2008]. This mismatch is mainly due to the crucial assumptions
+that variations in space will correspond to differences of assembly stages and
+then reflect the assembly/disassembly trajectories in time of communities [@].
 
@@
 studies should investigate the temporal trends of several dimensions of
-community structure simultaneously because it drives many aspects of ecosystem functioning.
+community structure simultaneously because it drives many aspects of ecosystem
+functioning.
 
@@
 
-We showed that BEF works in time but that richness and biomass temporal trends through
-time relates on different ecological processes inside communities. We further
-found that space for time subtitution does not always work.
+We showed that BEF works in time but that richness and biomass temporal trends
+through time relates on different ecological processes. We further found that
+space for time subtitution does not always work.
 
@@
 names(p_sp_bm) <- sp_bm$y 
-
-reorder_p_sp_bm <- p_sp_bm
-reorder_p_sp_bm[[1]] <- p_sp_bm$ct_ff 
-reorder_p_sp_bm[[2]] <- p_sp_bm$w_trph_lvl_avg 
-reorder_p_sp_bm[[3]] <- p_sp_bm$piel_nind 
-reorder_p_sp_bm[[4]] <- p_sp_bm$piel_bm 
-reorder_p_sp_bm[[5]] <- p_sp_bm$log_rich_std 
 ```

### 2021-06-09 paper/appendix.Rmd
New analysis with different subdataset

---
title: Appendix
subtitle:
author: Alain Danet, Maud Mouchet, Loubna El Madouri, Elisa Thébault and Colin Fontaine (ordre non fixé)
date: \today 
output:
  bookdown::pdf_document2:
    fig_caption: true 
    keep_tex: true
    toc: true
fontsize: 12pt
header-includes:
   - \usepackage{natbib}
   - \newcommand{\beginsupplement}{\renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}} 
   - \usepackage{float}
   - \usepackage[table]{xcolor}
   - \usepackage{multirow}
   - \usepackage{booktabs}
   - \usepackage{makecell}
   - \usepackage{setspace}
   - \doublespacing
   - \usepackage{lineno}
   - \linenumbers
geometry: margin=2cm
bibliography: references.bib
number_sections: true
---

```{r}
knitr::opts_chunk$set(
  cache = TRUE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.align = "center",
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE
)
```

```{r, echo = FALSE, message = FALSE, collapse = FALSE}

library(drake)
library(tidyverse)
library(magrittr)
library(ggeffects)
library(cowplot)
library(kableExtra)
library(sf)
library(nlme)

mypath <- rprojroot::find_package_root_file
source(mypath("R/variable_shortcut.R")) # Define your custom code as a bunch of
#functions.

source(mypath("R/misc.R"))
source_dir(get_mypath("R")) # Define your custom code as a bunch of functions.

mytheme <- theme_cowplot() +
background_grid()

theme_set(mytheme)
options(knitr.table.format = "latex")
```
```{r}
var_analysis <- c("ct_ff", "w_trph_lvl_avg", "log_rich_std", "log_bm_std",
  "piel_bm", "piel_nind")

```

\beginsupplement

# Statistical analysis

## Spatial model

```{r}
loadd(est_sp_models, colin_sp_models, sp_models)
```

```{r}
tmp <- map(colin_sp_models, enframe)
t_colin_sp_models <- tibble(vif = tmp, mod = names(colin_sp_models)) %>%
  unnest(vif) %>%
  filter(name %in% c("log_rich_std", "log_bm_std", "ct_ff"), mod == "log_rich_std") %>% #same model for
  #all, so the vif is the same
  rename(Response = name, vif = value) %>%
  select(-mod) %>%
  mutate(vif = map(vif, enframe)) %>%
  unnest(vif) %>%
  mutate(
    value = round(value, 3),
    name = str_replace_all(name, var_replacement()),
    Response = str_replace_all(
      Response,
      c("log_rich_std" = "Richness model", "log_bm_std" = "Biomass model",
	"ct_ff" = "Food-web structure"))
    ) %>%
  spread(name, value)

# colinearity table
kable(t_colin_sp_models,
  row.names = FALSE,
  booktabs = T,
  caption = "Variance Inflation Factor for the linear models in the spatial
  models. NA values indicate that the term in column was not included in the
  modeling of the response variable in row.",
  label = "vif-sp",
  ) %>%
  kable_styling(latex_options = c("scale_down", "stripped"))
```

## Temporal model with richness and biomass

```{r}
loadd(
  resume_bm_rich_mod_mono_trends,
  model_bm_rich_no_covar_no_inc_mono_trends,
  reg_table_bm_rich_mono_trends,
  reg_table_bm_rich_mono_stable_trends,
  reg_table_bm_rich_trends,
  reg_table_bm_rich,
  anova_table_bm_rich_mono_trends,
  anova_table_bm_rich_mono_stable_trends,
  anova_table_bm_rich_trends,
  anova_table_bm_rich,
  anova_bm_rich_mod,
  st_trends_rich_bm,
  st_mono_trends_rich_bm,
  st_mono_trends_stable_rich_bm
)

loadd(pred_bm_rich_mono_trends, pred_bm_rich, pred_bm_rich_trends, pred_bm_rich_mono_stable_trends)
```

We modeled the temporal trends of food-web structure as dependant of the
temporal trends of both species richness and community biomass as:

$dN = dB + dR + \epsilon$

\newpage

### Only mono trends

We kept only the stations that had monotonic trends for biomass and species
richness, with resulting `r length(st_mono_trends_rich_bm)` stations.

```{r}

plot_grid(plotlist = pred_bm_rich_mono_trends$pred_plot)
```

```{r}
reg_table_bm_rich_mono_trends %>%
  kable(., booktabs = TRUE,
  row.names = FALSE,
    caption =
      paste0(
      "Regression coefficients for the linear models explaining the links
      between the temporal trends of the network structure and the one of
      community biomass and species richness."
    ),
  label = "reg-rich-mono"
  ) %>%
  kable_styling(latex_options = c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
anova_table_bm_rich_mono_trends %>%
  kable(., booktabs = TRUE,
  row.names = FALSE,
    caption =
      paste0(
	"ANOVA results for the links between the temporal trends of the network
	structure and the one of community biomass and species richness."
	),
      label = "aov-rich-mono"
      ) %>%
  kable_styling(latex_options = c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

\newpage

### All trends (non monotonic)

We kept all stations that had a significant trend (decrease or increase) for both
species richness and community biomass, with resulting 
`r length(st_mono_trends_rich_bm)` stations.

```{r}
plot_grid(plotlist = pred_bm_rich_trends$pred_plot)
```

```{r}
reg_table_bm_rich_trends %>%
  kable(., booktabs = TRUE,
  row.names = FALSE,
    caption =
      paste0(
	"Regression coefficients for the linear models explaining the links
	between the temporal trends of the network structure and the one of
	community biomass and species richness."
    ),
  label = "reg-rich-trends"
  ) %>%
  kable_styling(latex_options = c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
anova_table_bm_rich_trends %>%
  kable(., booktabs = TRUE,
  row.names = FALSE,
    caption =
      paste0(
	"ANOVA results for the links between the temporal trends of species
	richness and the temporal trends of the network structure."
	),
      label = "aov-rich-trends"
      ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

\newpage

### All monotonic stations (i.e + monotonic stable)

```{r}
plot_grid(plotlist = pred_bm_rich_mono_stable_trends$pred_plot)
```

```{r}
reg_table_bm_rich_mono_stable_trends %>%
  kable(., booktabs = TRUE,
  row.names = FALSE,
    caption =
      paste0(
	"Regression coefficients for the linear models explaining the links
	between the temporal trends of the network structure and the one of
	community biomass and species richness."
    ),
  label = "reg-rich-trends"
  ) %>%
  kable_styling(latex_options = c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
anova_table_bm_rich_mono_stable_trends %>%
  kable(., booktabs = TRUE,
  row.names = FALSE,
    caption =
      paste0(
	"ANOVA results for the links between the temporal trends of species
	richness and the temporal trends of the network structure."
	),
      label = "aov-rich-trends"
      ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

\newpage

### All stations

We kept all the stations.

```{r}
plot_grid(plotlist = pred_bm_rich$pred_plot)
```

```{r}
reg_table_bm_rich %>%
  kable(., booktabs = TRUE,
  row.names = FALSE,
    caption =
      paste0(
	"Regression coefficients for the linear models explaining the links
	between the temporal trends of the network structure and the one of
	community biomass and species richness."
    ),
  label = "reg-rich-all"
  ) %>%
  kable_styling(latex_options = c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
anova_table_bm_rich %>%
  kable(., booktabs = TRUE,
  row.names = FALSE,
  caption =
    paste0(
      "ANOVA results for the links between the temporal trends of species
      richness and the temporal trends of the network structure."
      ),
    label = "aov-rich-all"
    ) %>%
kable_styling(latex_options =c("scale_down", "stripped")) %>%
collapse_rows(columns = 1, valign = "top")
```

### 2021-06-09 paper/manuscript.Rmd
New analysis with different subdataset

@@
 title: "Biomass and species richness temporal trends drives the assembly and the disassembly of food-web in natural fish assemblages"
-author: "Alain Danet, Maud Mouchet, Loubna El Madouri, Colin Fontaine (ordre non fixé)"
-self_contained: yes
-date: "`r Sys.Date()`"
-tables: yes
+author: Alain Danet, Maud Mouchet, Willem Bonnaffé, Elisa Thébault and Colin Fontaine
+date: \today 
+output:
+  bookdown::pdf_document2:
+    fig_caption: true 
+    keep_tex: true
+    toc: true
+fontsize: 12pt
+header-includes:
+   - \usepackage{natbib}
+   - \usepackage{float}
+   - \usepackage[table]{xcolor}
+   - \usepackage{multirow}
+   - \usepackage{booktabs}
+   - \usepackage{makecell}
+   - \usepackage{setspace}
+   - \doublespacing
+   - \usepackage{lineno}
+   - \linenumbers
+geometry: margin=2cm
 bibliography: references.bib
-fontsize: 12pt
-output:
-  bookdown::html_document2:
-    fig_caption: true
-    theme: "journal"
+number_sections: true
 ---
@@
 )
+
 ```
@@
 theme_set(mytheme)
+options(knitr.table.format = "latex")
 ```
@@
 
-Biodiversity to affect ecosystem properties such as total biomass, productivity
-and stability [@tilman_biodiversity_2014; @loreau_biodiversity_2001]. Numerous
-studies have shown the decline of population and community biomass
+Biodiversity affects ecosystem properties such as total biomass, productivity
+and stability [@tilman_biodiversity_2014; @loreau_biodiversity_2001]. However,
+current biodiversity is at risk, numerous
+studies reported dramatic declines of population and community biomass
 [@ceballos_biological_2017; @hallmann_more_2017; @albano_native_2021], as well
-as ongoing extinction [@barnosky_]. Consequences of such trends on various
-aspects of community structure are not well known whereas numerous ecological studies
+as ongoing extinction [@barnosky_has_2011]. Consequences of such trends on various
+aspects of community structure are not well-known whereas numerous ecological studies
 have shown that the different aspects of community structure are tightly linked [REF].
 
-The link between Biodiversity and ecosystem functioning is one of the most
-famous example, experimental studies are in accordance to show a positive
-relationship between species richness and community biomass
+The temporal trends of species richness and community biomass are likely to
+affect community structure. The positive link between Biodiversity and ecosystem
+functioning shown in experimental studies predict that loss and gain of species
+richness should respectively result in loss and gain of community biomass
 [@tilman_biodiversity_2014; @pennekamp_biodiversity_2018]. But this relation is
 not always found in natural settings [@grace_integrative_2016;
-@li_relationship_2018; @maureaud_biodiversityecosystem_2019]. Also, numerous
-studies have found relation between species richness and evenness, showing that
-communities become more or less even as species richness increase
-[@soininen_relationship_2012; @ma_species_2005;
-@maureaud_biodiversityecosystem_2019], highlighting the diversity of
-assembly processes in ecological communities.
+@li_relationship_2018; @maureaud_biodiversityecosystem_2019]. Numerous
+studies find relation between species richness and evenness, but their disagree
+on the sign of the relationships [@soininen_relationship_2012; @ma_species_2005;
+@maureaud_biodiversityecosystem_2019], highlighting the diversity of assembly
+processes in ecological communities.
 
 The distribution and the number of ecological interactions, i.e. the structure
-of ecological networks, also covary. In food-web, connectance, which measures the
-degree of generalism in a network, has been theoretically shown to theoretically
-positively scale with community biomass [@thebaut_food-web_2003]. Connectance
-has been also shown to be negatively related to species richness in empirical
-food-webs [@dunne_network_2006]. Trophic level has also been shown to be
-positively linked to total biomass in theoretical models
-[@wang_biodiversity_2018]. All together, these studies show that the
-different dimensions of network structure are closely linked.
+of ecological networks, also covaries with species richness and community
+biomass. In food-webs, connectance, which measures the degree of generalism in a
+network, has been theoretically shown to theoretically positively scale with
+community biomass [@thebault_food-web_2003]. Connectance has been also shown to
+be negatively related to species richness in empirical food-webs
+[@dunne_network_2006]. Trophic level has also been shown to be positively linked
+to total biomass in theoretical models [@wang_biodiversity_2018]. All together,
+these studies show that the different dimensions of network structure are
+closely linked.
 
@@
 predict how changes in species richness or community biomass will in turn affect
-community and network structure. The hypothesis that space can be use to
+community and network structure. The hypothesis that space can
 surrogate space is often implicitly made in ecological studies. This method
 began to be widely used in the early 20th century to infer the temporal
-succession of vegetation from space variations [@pickett_space-time_1989].  It
+succession of vegetation from space variations [@pickett_space-for-time_1989]. It
 supposes a homology between variations in space and in time i.e. that spatial
-sequence corresponds to temporal sequences. This methods have raised criticisms
-[@damgaard_critique_2019], with studies showing the coherent in space and time
+sequences corresponds to temporal sequences. This method have raised criticisms
+[@damgaard_critique_2019], with studies showing analogous patterns in space and time
 [@blois_space_2013] or not [@johnson_testing_2008; @adler_contrasting_2007].
 Spatial turnover of species composition, dispersal limitation, disturbance and
-stochastic processes  has been hypothesised to be responsible for the failure of
+stochastic processes have been hypothesised to be responsible for the failure of
 space for time substitution [@adler_contrasting_2007; @blois_space_2013].
 
-In this line, how biomass and species richness temporal trends are linked to
+In this line, how community biomass and species richness temporal trends are linked to
 change in food-web structure is still an open question, as well as if space for
-time substitution works in food-web assembly. The increasing availability of
-ecological temporal series makes possible to assess those questions.
+time substitution works to infer consequences of species richness and community
+biomass on food-web structure. The increasing availability of ecological
+temporal series makes possible to assess those questions.
 
@@
 Moreover, we tested if the those relationships differs between communities that
-lossed or gained biomass/species richness across time, reflecting potential
+loosed or gained biomass/species richness across time, reflecting potential
 difference between disassembly and assembly processes. We finally assessed if
-spatial relationships display the same patterns than temporal ones, to assess
+spatial relationships display the same patterns as temporal ones, to assess
 the validity of space for time substitution.
@@
 We characterized food-webs by its connectance, describing the degree of
-generalism in a network [@dunne_network_2006, @delmas_analysing_2019]. It is
+generalism in a network [@dunne_network_2006; @delmas_analysing_2019]. It is
 computed as the ratio between the actual number of links and the number of
@@
 ```{r}
-loadd(com_analysis_data, full_data2, st_mono_trends_combined_list)
+loadd(full_data2, st_mono_trends_combined_list)
 ```
@@
 nb_st <- unique(full_data2$station) %>% length
+rm(full_data2)
 nb_st_var <- map_dbl(st_mono_trends_combined_list$station, length)
@@
 species richness, we selected the stations that displayed monotonic trends for
-theses variable. Over the `r nb_st` stations, the selection procedure resulted
+these variable. Over the `r nb_st` stations, the selection procedure resulted
 in respectively `r nb_st_var["log_bm_std"]` stations  and `r nb_st_var["log_rich_std"]`
@@
 community biomass ($B_i$) and species richness ($R_i$)of the three first years of the temporal
-series .
+series.
 
-$dN = dB + B_i + dB \times B + Inc \times B_i + dB \times Inc \times B_i$
+$dN = dB + B_i + dB \times B + Inc_B \times B_i + dB \times Inc_B \times B_i$
 
-$dN = dR + R_i + dR \times R_i + Inc \times R_i + dR \times Inc \times R_i$
+$dN = dR + R_i + dR \times R_i + Inc_R \times R_i + dR \times Inc_R \times R_i$
 
@@
   - $R_i$: median species richness of the first three year
-  - $Inc$: Is $dB > 0$?
+  - $Inc_B$: Is $dB > 0$?
+  - $Inc_R$: Is $dR > 0$?
 
-In order to control for the uncertainties of the estimated temporal trends, we
-weighted each temporal trends by the inverse of the product between the standard
-error of the estimated trends, i.e. slopes, for the response and the explicative
+In order to control for the uncertainties of the estimated temporal trends, each
+temporal trend was weighted by the inverse of the product of the standard errors of the
+estimated trends, i.e. slopes for the response and the explicative
 variable.
@@
 
-$N =  B + R + E_1 + E_2 $
+$N =  B + R + E_1 + E_2$
 
@@
   - $R$: median species richness 
+  - $E_1$: PCA1 related to stream size
+  - $E_2$: PCA2 related to average temperature and average BOD
 
@@
 communities in terms of individual number display higher community biomass
-[@wisley_biodiversity_2000].
+[@wilsey_biodiversity_2000].
 
@@
 theoretical work showing that higher food-web connectance result in higher
-community biomass [@thebaut_food-web_2003].
+community biomass [@thebault_food-web_2003].
 
@@
 
-To the difference with community biomass, the temporal trends evenness of
+To the difference with community biomass, the temporal trends of evenness of
 biomass and individual were positively related to the temporal trends of species
@@
 @ceballos_biological_2017], it is important to note that they might not be
-equivalent in terms of consequences on the structure of the community. Further
+equivalent in terms of consequences on the structure of the community. Further,
 studies should investigate the temporal trends of several dimensions of
@@
 different relationship between the temporal dynamic of community structure and
-the one of biomass and species richness. We could have imagine that
+the one of biomass and species richness. We could have imagined that
 extinction/colonisation processes or immigration/extinction debt could have lead
@@
   linear models while the points are colored according the median community
-  biomass of the three first years of the given temporal series. The lines surrounding each point represent
-  the standard error associated to the temporal trends. Right panel displays the
+  biomass of the three first years of the given temporal series. The lines
+  surrounding each point represent the standard error associated to the temporal
+  trends. Right panel displays the
   spatial relationship between median community structure over time and the
@@
 ti <- list()
-for (i in c("log_rich_std", "w_trph_lvl_avg",  "piel_bm", "piel_nind", "ct_ff")) {
+for (
+  i in c("log_rich_std", "w_trph_lvl_avg", "piel_bm", "piel_nind", "ct_ff")
+  ) {
   ti[[i]] <- list(p_bm[[i]], p_sp_bm[[i]])
@@
   rich_x = "log_rich_std",
-  rich_y = c("ct_ff", "w_trph_lvl_avg", "piel_nind", "piel_bm", "log_bm_std") 
+  rich_y <- c("ct_ff", "w_trph_lvl_avg", "piel_nind", "piel_bm", "log_bm_std")
   )$rich
@@
 fig2_right <- plot_grid(plotlist = p_sp_rich, ncol = 1)
-#plot_grid(plotlist = list(p_bm[[1]], p_sp_bm[[1]], ), ncol = 1)
+# plot_grid(plotlist = list(p_bm[[1]], p_sp_bm[[1]], ), ncol = 1)
 
@@
 # Make the label on two lines
-top_rich <- plot_grid(plotlist = c(trich[[1]], trich[[2]], trich[[3]], trich[[4]], trich[[5]]), ncol = 2)
+top_rich <- plot_grid(
+  plotlist = c(trich[[1]], trich[[2]], trich[[3]], trich[[4]], trich[[5]]),
+  ncol = 2)
 fig2 <- plot_grid(top_rich, p_rich[[6]], ncol = 1, rel_heights = c(1, .1))
@@
 ```{r}
-loadd(model_log_bm_f3y_table_medium, model_log_rich_f3y_table_medium)
-```
-
-```{r}
 model_log_bm_f3y_table_medium[["anova_table"]] %>%
@@
   format_anova_table() %>%
-  kable(., booktabs = TRUE,
+  kable(.,
+    booktabs = TRUE,
     caption =
@@
     ),
-  label = "tab:aov-bm"
-
+  label = "aov-bm"
   ) %>%
-  kable_styling(latex_options =c("scale_down", "stripped")) %>%
+  kable_styling(latex_options = c("scale_down", "stripped")) %>%
   collapse_rows(columns = 1, valign = "top")
@@
     ),
-  label = "tab:aov-rich"
+  label = "aov-rich"
   ) %>%
@@
       of the network structure."),
-  label = "tab:reg-bm"
+  label = "reg-bm"
   ) %>%
@@
     ),
-  label = "tab:reg-rich"
+  label = "reg-rich"
   ) %>%
@@
       "Squared and adjusted squared R for linear models of spatial relationships."),
-  label = "tab:rsq"
+  label = "rsq"
       ) %>% # 
@@
       biomass and the one of network structure."),
-  label = "tab:aov-bm-sp"
+  label = "aov-bm-sp"
   ) %>%
-  kable_styling(latex_options =c("scale_down", "stripped")) %>%
+  kable_styling(latex_options = c("scale_down", "stripped")) %>%
   collapse_rows(columns = 1, valign = "top")
@@
       richness and the one of network structure."),
-  label = "tab:aov-rich-sp"
+  label = "aov-rich-sp"
       ) %>% #
@@
       "Marginal and conditional squared R for spatial models."),
-  label = "tab:rsq-sp"
+  label = "rsq-sp"
       ) %>% #
-  kable_styling(latex_options =c("scale_down", "stripped")) %>%
+  kable_styling(latex_options = c("scale_down", "stripped")) %>%
   collapse_rows(columns = 1, valign = "top")
-
 ```

### 2021-06-09 R/packages.R

@@ -6,3 +6,4 @@ library(tidyverse)
 library(magrittr)
 library(ggeffects)
 library(cowplot)
+library(lm.beta)

### 2021-06-09 R/statistical_model.R

@@ -243,6 +243,37 @@ test2 <- comparison_table %>%
 return(test2)
 }
 
+get_model_bm_rich_no_covar_no_inc <- function (.data = NULL) {
+
+  list(
+    log_bm_std = lm(
+      log_bm_std ~ log_rich_std,
+      data = {{.data}},
+      weight = 1 / log_rich_std_strd_error * log_bm_std_strd_error),
+    log_rich_std = lm(
+      log_rich_std ~ log_bm_std,
+      data = {{.data}},
+      weight = 1 / log_rich_std_strd_error * log_bm_std_strd_error),
+    ct_ff = lm(
+      ct_ff ~ log_rich_std  + log_bm_std ,
+      data = {{.data}},
+      weight = 1 / log_rich_std_strd_error * log_bm_std_strd_error * ct_ff_strd_error),
+    w_trph_lvl_avg = lm(
+      w_trph_lvl_avg ~  log_rich_std + log_bm_std,
+      data = {{.data}},
+      weight = 1 / log_rich_std_strd_error * log_bm_std_strd_error * w_trph_lvl_avg_strd_error),
+    piel_bm = lm(
+      piel_bm ~ log_rich_std + log_bm_std,
+      data = {{.data}},
+      weight = 1 / log_rich_std_strd_error * log_bm_std_strd_error * piel_bm_strd_error),
+    piel_nind = lm(
+      piel_nind ~ log_rich_std + log_bm_std,
+      data = {{.data}},
+      weight = 1 / log_rich_std_strd_error * log_bm_std_strd_error * piel_nind_strd_error)
+  )
+
+}
+
 #' Compute spatial relationships
 
 get_mod_list <- function(.data = NULL, st_by_var = NULL) {

### 2021-06-10 paper/appendix.Rmd
Spatial models

@@
 species richness and community biomass, with resulting 
-`r length(st_mono_trends_rich_bm)` stations.
+`r length(st_trends_rich_bm)` stations.
 

### 2021-06-10 paper/manuscript.Rmd
Spatial models

@@
 and stability [@tilman_biodiversity_2014; @loreau_biodiversity_2001]. However,
-current biodiversity is at risk, numerous
-studies reported dramatic declines of population and community biomass
-[@ceballos_biological_2017; @hallmann_more_2017; @albano_native_2021], as well
-as ongoing extinction [@barnosky_has_2011]. Consequences of such trends on various
-aspects of community structure are not well-known whereas numerous ecological studies
-have shown that the different aspects of community structure are tightly linked [REF].
+current biodiversity is at risk, numerous studies reported dramatic declines of
+population and community biomass [@ceballos_biological_2017;
+@hallmann_more_2017; @albano_native_2021], as well as decrease in species
+richness 
+[@barnosky_has_2011; @newbold_global_2015]. Consequences of such trends on
+various aspects of community structure are not well-known whereas numerous
+ecological studies have shown that the different aspects of community structure
+are tightly linked [REF].
 
-The temporal trends of species richness and community biomass are likely to
-affect community structure. The positive link between Biodiversity and ecosystem
-functioning shown in experimental studies predict that loss and gain of species
-richness should respectively result in loss and gain of community biomass
-[@tilman_biodiversity_2014; @pennekamp_biodiversity_2018]. But this relation is
-not always found in natural settings [@grace_integrative_2016;
-@li_relationship_2018; @maureaud_biodiversityecosystem_2019]. Numerous
-studies find relation between species richness and evenness, but their disagree
-on the sign of the relationships [@soininen_relationship_2012; @ma_species_2005;
+The temporal trends of species richness and community biomass are indeed
+predicted to affect community structure. The positive link between Biodiversity
+and ecosystem functioning shown in experimental studies predict that loss and
+gain of species richness should respectively result in loss and gain of
+community biomass [@tilman_biodiversity_2014; @pennekamp_biodiversity_2018]. But
+this relation is not always found in natural settings [@grace_integrative_2016;
+@li_relationship_2018; @maureaud_biodiversityecosystem_2019]. Numerous studies
+find relation between species richness and evenness, but their disagree on the
+sign of the relationships [@soininen_relationship_2012; @ma_species_2005;
 @maureaud_biodiversityecosystem_2019], highlighting the diversity of assembly
@@
 biomass. In food-webs, connectance, which measures the degree of generalism in a
-network, has been theoretically shown to theoretically positively scale with
+network, has been theoretically shown to positively scale with
 community biomass [@thebault_food-web_2003]. Connectance has been also shown to
@@
 
-The space for time substitution allows to use the studies mentioned above to
-predict how changes in species richness or community biomass will in turn affect
-community and network structure. The hypothesis that space can
-surrogate space is often implicitly made in ecological studies. This method
-began to be widely used in the early 20th century to infer the temporal
-succession of vegetation from space variations [@pickett_space-for-time_1989]. It
-supposes a homology between variations in space and in time i.e. that spatial
+The links between the different component of community structure often come from
+spatial gradient comparison. The space for time substitution allows to use the
+studies mentioned above to predict how changes in species richness or community
+biomass will in turn affect community and network structure. The hypothesis that
+space can surrogate space is often implicitly made in ecological studies. This
+method began to be widely used in the early 20th century to infer the temporal
+succession of vegetation from space variations [@pickett_space-for-time_1989].
+It supposes a homology between variations in space and in time i.e. that spatial
 sequences corresponds to temporal sequences. This method have raised criticisms
-[@damgaard_critique_2019], with studies showing analogous patterns in space and time
-[@blois_space_2013] or not [@johnson_testing_2008; @adler_contrasting_2007].
-Spatial turnover of species composition, dispersal limitation, disturbance and
-stochastic processes have been hypothesised to be responsible for the failure of
-space for time substitution [@adler_contrasting_2007; @blois_space_2013].
+[@damgaard_critique_2019], with studies showing analogous patterns in space and
+time [@blois_space_2013] or not [@johnson_testing_2008;
+@adler_contrasting_2007]. Spatial turnover of species composition, dispersal
+limitation, disturbance and stochastic processes have been hypothesised to be
+responsible for the failure of space for time substitution
+[@adler_contrasting_2007; @blois_space_2013].
 
-In this line, how community biomass and species richness temporal trends are linked to
-change in food-web structure is still an open question, as well as if space for
-time substitution works to infer consequences of species richness and community
-biomass on food-web structure. The increasing availability of ecological
-temporal series makes possible to assess those questions.
+In this line, how community biomass and species richness temporal trends are
+linked to temporal changes in food-web structure is still an open question, as
+well as if space for time substitution works to infer consequences of species
+richness and community biomass on food-web structure. The increasing
+availability of ecological temporal series makes possible to assess those
+questions.
 

### 2021-06-11 paper/appendix.Rmd
Got sp_models sensibility analysis

@@
   anova_table_bm_rich,
-  anova_bm_rich_mod,
-  st_trends_rich_bm,
-  st_mono_trends_rich_bm,
-  st_mono_trends_stable_rich_bm
+  anova_bm_rich_mod
 )
+loadd(st_trends_rich_bm, st_mono_trends_rich_bm,
+  st_mono_trends_stable_rich_bm)
 
-loadd(pred_bm_rich_mono_trends, pred_bm_rich, pred_bm_rich_trends, pred_bm_rich_mono_stable_trends)
+loadd(pred_bm_rich_mono_trends, pred_bm_rich, pred_bm_rich_trends,
+  pred_bm_rich_mono_stable_trends)
+
 ```

### 2021-06-11 paper/manuscript.Rmd
Got sp_models sensibility analysis

@@
 )
-
 ```
@@
 sp_bm <- sp_relation_plot2 %>%
-  filter(x == "log_bm_std")
+  filter(response == "log_bm_std")
 p_sp_bm <- sp_bm$gg
@@
 sp_rich <- sp_relation_plot2 %>%
-  filter(x == "log_rich_std")
-p_sp_rich <- sp_rich$gg
+  filter(term == "log_rich_std")
+p_sp_rich <- sp_rich$pred_plot
 names(p_sp_rich) <- sp_rich$y

### 2021-06-11 R/plan.R

@@ -261,25 +261,14 @@ model = data4model %>%
     std_error_bar = FALSE
   )
     ),
-  sp_relation_plot2 = rbind(
-    sp_relation_plot$rich_std %>%
-      filter(response == "log_rich_std"),
-    sp_relation_plot$bm_std %>%
-      filter(response == "log_bm_std")
-  ),
-  sp_relation_plot2_mono_trends = rbind(
+  sp_relation_plot2 = sp_relation_plot$rich_std %>%
+      filter(term == "log_rich_std"),
+  sp_relation_plot2_mono_trends =
     sp_relation_plot_mono_trends$rich_std %>%
-      filter(response == "log_rich_std"),
-    sp_relation_plot_mono_trends$bm_std %>%
-      filter(response == "log_bm_std")
-  ),
-  sp_relation_plot2_mono_stable_trends = rbind(
+      filter(term == "log_rich_std"),
+  sp_relation_plot2_mono_stable_trends =
     sp_relation_plot_mono_stable_trends$rich_std %>%
-      filter(response == "log_rich_std"),
-    sp_relation_plot_mono_stable_trends$bm_std %>%
-      filter(response == "log_bm_std")
-  ),
-
+      filter(term == "log_rich_std"),
 
   #5. Tables
   effect_quad2_piece = tibble(
@@ -491,7 +480,10 @@ model = data4model %>%
   ),
   #### Spatial
   target_sp_model_bm_rich = target(
-    get_mod_list(.data = filter(sp_st_data, station %in% y) %>% na.omit),
+    get_mod_list(.data = filter(sp_st_data, station %in% y) %>%
+      na.omit %>%
+      as.data.frame
+      ),
     transform = map(
       y = list(
         st_mono_trends_rich_bm,

### 2021-06-11 make.R

@@ -65,15 +65,14 @@ loadd(model,
 )
 
 loadd(pred_bm_rich_mono_stable_trends)
-loadd(sp_models, slope_x_bound, sp_st_data, st_trends_rich_bm, sp_model_bm_rich_mono_trends)
-map(sp_models, get_sp_model_plot)
+loadd(sp_models, slope_x_bound, sp_st_data, st_trends_rich_bm,
+  sp_model_bm_rich_mono_trends)
+sp_models$log_rich_std
 
 loadd(sp_slope_x_bound, slope_x_bound)
 
-HERE
-debugonce(get_predict_from_new_model)
 test <- get_pred_plot_from_new_model(
-  model =sp_model_bm_rich_mono_trends ,
+  model = sp_model_bm_rich_mono_trends,
   dataset = filter(sp_st_data, station %in% st_trends_rich_bm),
   x_bound = sp_slope_x_bound,
   std_error_bar = FALSE

### 2021-06-14 paper/manuscript.Rmd
Update tables and figures

@@
 title: "Biomass and species richness temporal trends drives the assembly and the disassembly of food-web in natural fish assemblages"
-author: Alain Danet, Maud Mouchet, Willem Bonnaffé, Elisa Thébault and Colin Fontaine
+author: Alain Danet, Maud Mouchet, Loubna El Madouri, Elisa Thébault and Colin Fontaine (ordre non fixé)
 date: \today 
@@
 ```
+
 ```{r}
@@
 
+\newpage
+
 # Figures {-}
@@
 ```{r}
-loadd(p_fig1_2, sp_relation_plot2, predict_plot2)
-theme_set(theme_cowplot())
-p_bm <- get_plot_fig1_2(predict_plot = predict_plot2, get_list = TRUE,
-  bm_x = "log_bm_std", rich_x = "log_rich_std",
-  bm_y = c("ct_ff", "w_trph_lvl_avg", "piel_nind", "piel_bm", "log_rich_std")
-  )$bm
-names(p_bm) <- c("ct_ff", "w_trph_lvl_avg", "log_rich_std", "piel_nind",
-  "piel_bm")
+loadd(sp_fig1_2_bm_rich_mono_stable_trends,
+  pred_bm_rich_mono_stable_trends)
+
+fig1_2 <- get_plot_rich_bm(
+  predict_plot = pred_bm_rich_mono_stable_trends,
+  get_list = TRUE,
+  rm_legend = FALSE,
+  bm_x = "log_bm_std",
+  bm_y = c(get_com_str_var(), "log_rich_std", "piel_nind", "piel_bm"),
+  rich_y = c(get_com_str_var(), "log_bm_std", "piel_nind", "piel_bm"),
+  rich_x = "log_rich_std"
+  )
+p_bm <- fig1_2$bm
+names(p_bm) <- c("log_rich_std", "ct_ff", "w_trph_lvl_avg",
+  "piel_bm", "piel_nind")
 #plot_grid(plotlist = p_bm)
 
-sp_bm <- sp_relation_plot2 %>%
-  filter(response == "log_bm_std")
-p_sp_bm <- sp_bm$gg
-names(p_sp_bm) <- sp_bm$y
+p_sp_bm <- sp_fig1_2_bm_rich_mono_stable_trends$bm
+names(p_sp_bm) <- c("log_rich_std", "ct_ff", "w_trph_lvl_avg",
+  "piel_bm", "piel_nind")
 ```
@@
 # Make the label on two lines
-top <- plot_grid(plotlist = c(ti[[1]], ti[[2]], ti[[3]], ti[[4]], ti[[5]]), ncol = 2)
-fig1 <- plot_grid(top, p_bm[[6]], ncol = 1, rel_heights = c(1, .1))
+fig1 <- plot_grid(plotlist = c(ti[[1]], ti[[2]], ti[[3]], ti[[4]], ti[[5]]), ncol = 2)
 fig1
@@
 ```{r}
-p_rich <- get_plot_fig1_2(
-  predict_plot = predict_plot2,
-  get_list = TRUE,
-  rich_x = "log_rich_std",
-  rich_y <- c("ct_ff", "w_trph_lvl_avg", "piel_nind", "piel_bm", "log_bm_std")
-  )$rich
-names(p_rich) <- c(
-  "ct_ff", "w_trph_lvl_avg", "piel_nind",
-  "piel_bm", "log_bm_std")
-#plot_grid(plotlist = p_rich)
-
-sp_rich <- sp_relation_plot2 %>%
-  filter(term == "log_rich_std")
-p_sp_rich <- sp_rich$pred_plot
-names(p_sp_rich) <- sp_rich$y
+p_rich <- fig1_2$rich
+p_sp_rich <- sp_fig1_2_bm_rich_mono_stable_trends$rich
 ```
@@
 ```{r}
-fig2_left <- plot_grid(plotlist = p_rich, ncol = 1)
-fig2_right <- plot_grid(plotlist = p_sp_rich, ncol = 1)
-# plot_grid(plotlist = list(p_bm[[1]], p_sp_bm[[1]], ), ncol = 1)
-
 trich <- list()
@@
 # Make the label on two lines
-top_rich <- plot_grid(
+fig2 <- plot_grid(
   plotlist = c(trich[[1]], trich[[2]], trich[[3]], trich[[4]], trich[[5]]),
   ncol = 2)
-fig2 <- plot_grid(top_rich, p_rich[[6]], ncol = 1, rel_heights = c(1, .1))
 fig2
 ```
+
+\newpage
 
@@
 ```{r}
-model_log_bm_f3y_table_medium[["anova_table"]] %>%
-  filter(y %in% net_var_bm) %>%
-  select(-mod_summary_table) %>%
-  format_anova_table() %>%
+loadd(pred_bm_rich_mono_stable_trends, anova_table_bm_rich_mono_stable_trends)
+anova_table_bm_rich_mono_stable_trends %>%
+  mutate(
+    response = str_replace_all(response, var_replacement()),
+    term = str_replace_all(term, var_replacement())
+  ) %>%
   kable(.,
     booktabs = TRUE,
+    row.names = FALSE,
     caption =
@@
     ),
-  label = "aov-bm"
+  label = "aov-bm-rich"
   ) %>%
@@
 ```{r}
-model_log_rich_f3y_table_medium[["anova_table"]] %>% 
-  filter(y %in% net_var_rich) %>%
-  select(-mod_summary_table) %>%
-  format_anova_table() %>%
+loadd(reg_table_bm_rich_mono_stable_trends)
+reg_table_bm_rich_mono_stable_trends %>%
+  mutate(
+    response = str_replace_all(response, var_replacement()),
+    term = str_replace_all(term, var_replacement())
+    ) %>%
 kable(., booktabs = TRUE,
-    caption = 
-      paste0(
-      "ANOVA results for the links between the temporal trends of species
-      richness and the temporal trends of the network structure."
-    ),
-  label = "aov-rich"
-  ) %>%
-  kable_styling(latex_options =c("scale_down", "stripped")) %>%
-  collapse_rows(columns = 1, valign = "top")
-```
-
-```{r}
-model_log_bm_f3y_table_medium$reg_table %>% 
-  filter(y %in% net_var_bm) %>%
-  format_reg_table() %>%
-  kable(., booktabs = TRUE,
+  row.names = FALSE,
   caption =
@@
       of the network structure."),
-  label = "reg-bm"
+      label = "reg-bm-rich"
       ) %>%
-  kable_styling(latex_options =c("scale_down", "stripped")) %>%
+  kable_styling(latex_options = c("scale_down", "striped")) %>%
   collapse_rows(columns = 1, valign = "top")
@@
 ```{r}
-model_log_rich_f3y_table_medium$reg_table %>%
-  filter(y %in% net_var_rich) %>%
-  format_reg_table() %>%
+loadd(rsq_table_bm_rich_mono_stable_trends)
+rsq_table_bm_rich_mono_stable_trends %>%
+  mutate(
+    Response = str_replace_all(Response, var_replacement())
+  ) %>%
   kable(., booktabs = TRUE,
@@
       paste0(
-      "Regression coefficients for the linear models explaining the links
-      between the temporal trends of species richness and the temporal trends of
-      the network structure."
-    ),
-  label = "reg-rich"
-  ) %>%
-  kable_styling(latex_options =c("scale_down", "stripped")) %>%
-  collapse_rows(columns = 1, valign = "top")
-```
-
-```{r}
-rsq %>%
-  rename(
-    Response = y, Explicative = x, 
-    `Squared R` = r.squared, `Adjusted squared R` = adj.r.squared
-  ) %>% 
-  select(Explicative, Response, everything()) %>%
-  kable(., booktabs = TRUE,
-    caption = 
-      paste0(
-      "Squared and adjusted squared R for linear models of spatial relationships."),
-  label = "rsq"
+      "Marginal and conditional squared R for temporal models."),
+  label = "rsq-sp"
       ) %>% #
-  kable_styling(latex_options =c("scale_down", "stripped")) %>%
+  kable_styling(latex_options = c("striped")) %>%
   collapse_rows(columns = 1, valign = "top")
@@
 ```{r}
-loadd(tab_sp_anova)
+loadd(
+  sp_anova_table_bm_rich_mono_stable_trends,
+  sp_rsq_table_bm_rich_mono_stable_trends
+)
 ```
@@
 ```{r}
-tab_sp_anova$log_bm_std %>%
-  filter(y %in% net_var_bm) %>%
+sp_anova_table_bm_rich_mono_stable_trends %>%
   mutate(
-    y = str_replace_all(y, var_replacement()),
+    response = str_replace_all(response, var_replacement()),
     term = str_replace_all(term, var_replacement()),
@@
       paste0(
-      "ANOVA results for the links between the spatial variation of community
-      biomass and the one of network structure."),
-  label = "aov-bm-sp"
+      "ANOVA results for the links among the spatial variation of community
+      biomass and species richness and the one of network structure."),
+  label = "aov-sp"
   ) %>%
-  kable_styling(latex_options = c("scale_down", "stripped")) %>%
+  kable_styling(latex_options = c("scale_down", "striped")) %>%
   collapse_rows(columns = 1, valign = "top")
@@
 ```{r}
-tab_sp_anova$log_rich_std %>%
-  filter(y %in% net_var_rich) %>%
+sp_rsq_table_bm_rich_mono_stable_trends %>%
   mutate(
-    y = str_replace_all(y, var_replacement()),
-    term = str_replace_all(term, var_replacement()),
-  ) %>%
-  kable(., booktabs = TRUE,
-    caption =
-      paste0(
-      "ANOVA results for the links between the spatial variation of species
-      richness and the one of network structure."),
-  label = "aov-rich-sp"
-      ) %>% #
-  kable_styling(latex_options = c("scale_down", "stripped")) %>%
-  collapse_rows(columns = 1, valign = "top")
-```
-
-```{r}
-table_rsq_sp <- map2(rsq_sp_mod, names(rsq_sp_mod),
-  ~mutate(.x, Explicative = .y) %>%
-    select(Explicative, Response, Marginal, Conditional)
-) %>%
-do.call(rbind, .)
-rownames(table_rsq_sp) <- NULL
-
-table_rsq_sp %>%
-  filter(Explicative %in% c("log_rich_std", "log_bm_std")) %>%
-  mutate(
-    Explicative = str_replace_all(Explicative, var_replacement()),
     Response = str_replace_all(Response, var_replacement())
@@
       ) %>% #
-  kable_styling(latex_options = c("scale_down", "stripped")) %>%
+  kable_styling(latex_options = c("striped")) %>%
   collapse_rows(columns = 1, valign = "top")

### 2021-06-14 R/packages.R

@@ -7,3 +7,5 @@ library(magrittr)
 library(ggeffects)
 library(cowplot)
 library(lm.beta)
+library(broom)
+library(broom.mixed)

### 2021-06-14 R/plan.R

@@ -1,5 +1,9 @@
 # This is where you write your drake plan.
 # Details: https://books.ropensci.org/drake/plans.html
+mytheme <- theme_cowplot() +
+background_grid()
+
+theme_set(mytheme)
 
 # Variable:
 model_x_var <- c("log_rich_std", "log_bm_std", "bm_std", "rich_std", "ct_ff", "w_trph_lvl_avg", "nind_std")
@@ -545,7 +549,7 @@ model = data4model %>%
   pred_bm_rich_trends = get_pred_plot_from_new_model(
     model = model_bm_rich_trends,
     dataset = filter(slope_com_var_no_covar, station %in% st_trends_rich_bm),
-    x_bound = slope_x_bound
+    x_bound = slope_x_bound, std_error_bar = TRUE
   ),
   pred_bm_rich_mono_trends = get_pred_plot_from_new_model(
     model = model_bm_rich_mono_trends,
@@ -587,15 +591,41 @@ model = data4model %>%
         "sp_pred_bm_rich"
       )
     )
-  ),
+    ),
+  target_sp_fig1_2 = target(
+    get_plot_rich_bm(
+      predict_plot = y,
+      get_list = TRUE,
+      rm_legend = FALSE,
+      bm_x = "log_bm_std",
+      bm_y = c(get_com_str_var(), "log_rich_std", "piel_nind", "piel_bm"),
+      rich_y = c(get_com_str_var(), "log_bm_std", "piel_nind", "piel_bm"),
+      rich_x = "log_rich_std",
+      temporal_label = FALSE
+      ),
+    transform = map(
+      y = list(
+        sp_pred_bm_rich_mono_trends,
+        sp_pred_bm_rich_mono_stable_trends,
+        sp_pred_bm_rich_trends,
+        sp_pred_bm_rich
+        ),
+      .names = c(
+        "sp_fig1_2_bm_rich_mono_trends",
+        "sp_fig1_2_bm_rich_mono_stable_trends",
+        "sp_fig1_2_bm_rich_trends",
+        "sp_fig1_2_bm_rich"
+      )
+    )
+    ),
   ### Table
   reg_table_bm_rich_mono_trends = map2(
     model_bm_rich_mono_trends,
     names(model_bm_rich_mono_trends),
     function(model, name) {
       ml <- broom::tidy(model) %>%
-	mutate(response = name) %>%
-	select(response, everything())
+        mutate(response = name) %>%
[…]

### 2021-06-14 paper/manuscript.Rmd
begin to revise results and methods

@@
 
-We described community structure by its community biomass, species richness and the
-evenness of the number of individual and the amount of biomass across species. The evenness was
-quantified with the Pielou index, computed as the Shannon diversity index
-divided by the number of species ($P = \frac{H'}{N}$, with $H'$ being the
-Shannon diversity index and $N$ the number of species).
+We described community structure by its community biomass, species richness and
+the evenness of the number of individual and the amount of biomass across
+species. The evenness was quantified with the Pielou index, computed as the
+Shannon diversity index divided by the number of species ($P = \frac{H'}{N}$,
+with $H'$ being the Shannon diversity index and $N$ the number of species).
 
 ```{r}
-loadd(full_data2, st_mono_trends_combined_list)
+loadd(slope_com_var_no_covar, st_mono_trends_stable_rich_bm)
 ```
 ```{r}
-nb_st <- unique(full_data2$station) %>% length
-rm(full_data2)
-nb_st_var <- map_dbl(st_mono_trends_combined_list$station, length)
-names(nb_st_var) <- st_mono_trends_combined_list$variable
+nb_st <- unique(slope_com_var_no_covar$station) %>% length
+rm(slope_com_var_no_covar)
+nb_st_rich_bm <- st_mono_trends_stable_rich_bm %>% length
 ```
@@
 
-With the goal to characterize the links among the temporal variations of network
-and community structure and the temporal variations of community biomass and
-species richness, we characterized the temporal trajectories of network and
-community structure at each site. We used a method based on second order
-polynomial which allows to assess both the direction and the monotony of
-temporal trends [@rigal_method_2020]. To avoid complex variations of biomass and
-species richness, we selected the stations that displayed monotonic trends for
-these variable. Over the `r nb_st` stations, the selection procedure resulted
-in respectively `r nb_st_var["log_bm_std"]` stations  and `r nb_st_var["log_rich_std"]`
-for community biomass and species richness analysis.
+To characterize the links among the temporal trends of network and community
+structure and the temporal trends of community biomass and species richness, we
+characterized the temporal trajectories of network and community structure at
+each site. We used a method based on second order polynomial which allows to
+assess both the direction and the monotony of temporal trends
+[@rigal_method_2020]. To avoid complex variations of biomass and species
+richness, we selected the stations that displayed monotonic trends for these
+variables, i.e. the ones for which the second order polynomial term was non
+significant. Over the `r nb_st` stations, the selection procedure resulted in 
+`r nb_st_rich_bm` for community biomass and species richness analysis.
+
+There was a clear relationship between the size of the communities and their
+temporal dynamics. Communities that displayed low community biomass at the
+beginning of their monitoring tend to display increase in biomass through time
+and reversely. There same the same pattern for species richness, with
+communities that displayed high species richness at the
+beginning of their monitoring tend to display decrease in species richness through time
+and reversely.
 
@@
 
-We selected the same stations that was used for the temporal analysis.
+In spatial analysis, we selected the same stations that were used for the
+temporal analysis. We summarised temporal series of each stations by the median
+value over time of each variable.
 
@@
 
-With the aim to test (1) the relationship among the temporal dynamics of network
+With the aim to test the relationship among the temporal dynamics of network
 structure from one side and species richness and community biomass from another
-side, (2) if those relationships were different if the communities were
-assembling or disassembling, (3) if those relationships were different if
-small/big communities, we modelled the dynamics the temporal trends of food-web
+side, we modelled the dynamics the temporal trends of food-web
 structure ($dN$) in function of the temporal trends of community biomass ($dB$) and species
-richness ($dR$), if the latter was positive of not (Inc) and with respectively the median
-community biomass ($B_i$) and species richness ($R_i$)of the three first years of the temporal
-series.
+richness ($dR$).
 
-$dN = dB + B_i + dB \times B + Inc_B \times B_i + dB \times Inc_B \times B_i$
-
-$dN = dR + R_i + dR \times R_i + Inc_R \times R_i + dR \times Inc_R \times R_i$
+$dN = dB + dR$
 
@@
   - $dR$: temporal trend of (log) species richness
-  - $B_i$: median community biomass of the first three year
-  - $R_i$: median species richness of the first three year
-  - $Inc_B$: Is $dB > 0$?
-  - $Inc_R$: Is $dR > 0$?
 
@@
 loadd(rsq_sp_mod, summary_table, sp_models, model_summary)
-rsq <- summary_table %>%
-  filter(y %in% unique(c(net_var_bm, net_var_rich))) %>%
-select(y, x, mod_summary_table) %>%
-unnest(mod_summary_table) %>%
-select(y, x, r.squared, adj.r.squared)
+
+loadd(rsq_table_bm_rich_mono_stable_trends, sp_rsq_table_bm_rich_mono_stable_trends)
 ```
@@
 ```{r}
-rsq_nind_bm <- rsq[rsq$y == "piel_nind" & rsq$x == "log_bm_std",]$adj.r.squared %>%
+rsq_piel_nind <- rsq_table_bm_rich_mono_stable_trends %>%
+  filter(Response == "piel_nind") %>%
+  .$R.squared %>%
   round(., 3)
-rsq_bm_rich <- rsq[rsq$y == "log_bm_std" & rsq$x == "log_rich_std",]$adj.r.squared %>%
+
+rsq_tlvl <- rsq_table_bm_rich_mono_stable_trends %>%
+  filter(Response == "w_trph_lvl_avg") %>%
+  .$R.squared %>%
   round(., 3)
-rsq_tlvl_rich_sp <- rsq_sp_mod$log_rich_std[
-  rsq_sp_mod$log_rich_std$Response == "w_trph_lvl_avg", 
-  ]$Conditional %>%
+
+rsq_tlvl_sp <- sp_rsq_table_bm_rich_mono_stable_trends %>%
+  filter(Response == "w_trph_lvl_avg") %>%
+  .$Conditional %>%
   round(., 3)
-rsq_piel_bm_rich_sp <- rsq_sp_mod$log_bm_std[
-  rsq_sp_mod$log_rich_std$Response == "piel_bm", 
-  ]$Conditional %>%
+
+rsq_piel_bm_sp <- sp_rsq_table_bm_rich_mono_stable_trends %>%
+  filter(Response == "piel_bm") %>%
+  .$Conditional %>%
   round(., 3)
@@
 models linking temporal dynamics of food-web structure and the one of community
-biomass and species richness spanning from $R_{adj}^2= `r rsq_nind_bm`$ for the
-relationships between to $R_{adj}^2= `r rsq_bm_rich`$ between biomass and
-species richness (Table \@ref(tab:rsq)). The spatial relationships among
-food-web structure aspects were more performant, with $R_{cond}^2$ varing from 
-`r rsq_tlvl_rich_sp` to `r rsq_piel_bm_rich_sp` (Table \@ref(tab:rsq-sp)).
+biomass and species richness spanning from $R_{adj}^2= `r rsq_piel_nind`$ for
+pielou of individual number to $R_{adj}^2= `r rsq_tlvl`$ for average trophic
+level (Table \@ref(tab:rsq)). The spatial models
+ were more performant, with $R_{cond}^2$ varing from 
+`r rsq_tlvl_sp` to `r rsq_piel_bm_sp` (Table \@ref(tab:rsq-sp)).
 
-Overall, we found no significant effect of the temporal gain or losses of
-communinity biomass biomass and species richness on the relationship between the
-temporal trends of community structure and that of biomass and species richness
-(Table \@ref(tab:aov-bm), \@ref(tab:aov-rich)).
+---
+#Overall, we found no significant effect of the temporal gain or losses of
+#communinity biomass biomass and species richness on the relationship between the
+#temporal trends of community structure and that of biomass and species richness
+#(Table \@ref(tab:aov)).
+---
 
@@
 community biomass from one side and species richness, average trophic level,
-connectance from the other side (Fig. \@ref(fig:bm), Table \@ref(tab:aov-bm)),
+connectance from the other side (Fig. \@ref(fig:bm), Table \@ref(tab:aov)),
 meaning that they temporally increased when the community biomass temporally increased and
@@
 community biomass and that of the pielou of biomass (Figure \@ref(fig:bm), Table
-\@ref(tab:aov-bm)), meaning that the eveness of biomass across species
+\@ref(tab:aov)), meaning that the eveness of biomass across species
 temporally increased when the community biomass temporally decreased and
 respectively that the evenness temporally decreased when the community biomass
-temporally increased (Fig. \@ref(fig:bm), Table \@ref(tab:aov-bm)). However, we
-found no significant relationship between the temporal trends of community biomass and that
-of the pielou of individual.
+temporally increased (Fig. \@ref(fig:bm), Table \@ref(tab:aov)). We observed the
+same pattern between the temporal trends of
+community biomass and that of the pielou of individual number.
 
-Overall, we did not find effect of assembly/disassembly on the relationships
-between the temporal trends of community structure and the one of community
-biomass. We also found that the median community biomass had no effect on the
-relationship between the temporal trends of community structure and the one of community
-biomass.
+---
+#Overall, we did not find effect of assembly/disassembly on the relationships
+#between the temporal trends of community structure and the one of community
+#biomass. We also found that the median community biomass had no effect on the
+#relationship between the temporal trends of community structure and the one of community
+#biomass.
+---
 
@@
 
+HERE
 The temporal trends of community biomass, average trophic level, pielou of biomass,
 pielou of individual had a positive relationship with that of species richness
-(Fig. \@ref(fig:rich), Table \@ref(tab:aov-rich)). However, the direct
+(Fig. \@ref(fig:rich), Table \@ref(tab:aov)). However, the direct
 relationship between the temporal trends of average trophic level and the one of
@@
 overall species richness of the community (Fig. \@ref(fig:rich), Table
-\@ref(tab:aov-rich)), meaning that the relationship between temporal trends of
+\@ref(tab:aov)), meaning that the relationship between temporal trends of
 pielou of individual and that of species richness was more positive as the
 community contained more species (Fig. \@ref(fig:rich), Table
-\@ref(tab:reg-rich)). While the relationship between temporal trends of pielou
+\@ref(tab:reg)). While the relationship between temporal trends of pielou
 of individual and that of species richness was more negative as the community
-contained more species (Fig. \@ref(fig:rich), Table \@ref(tab:reg-rich)).
+contained more species (Fig. \@ref(fig:rich), Table \@ref(tab:reg)).
 
@@
 spatially positively related to community biomass while the pielou of biomass was negatively related to
-community biomass (Fig. \@ref(fig:bm), Table \@ref(tab:aov-rich-sp)). However,
+community biomass (Fig. \@ref(fig:bm), Table \@ref(tab:aov-sp)). However,
 we found no spatial relation between the pielou of individual and community
@@
 connectance were negatively related to
-community biomass (Fig. \@ref(fig:rich), Table \@ref(tab:aov-rich-sp)).
+community biomass (Fig. \@ref(fig:rich), Table \@ref(tab:aov-sp)).
 
@@
     ),
-  label = "aov-bm-rich"
+  label = "aov"
   ) %>%
@@
       of the network structure."),
-      label = "reg-bm-rich"
+      label = "reg"
       ) %>%
@@
       "Marginal and conditional squared R for temporal models."),
-  label = "rsq-sp"
+  label = "rsq"
       ) %>% #
@@
   ) %>%
-  kable(., booktabs = TRUE,
+  kable(.,
+    booktabs = TRUE,
+    row.names = FALSE,
     caption =

### 2021-06-15 paper/manuscript.Rmd
Compute standardized effect for spatial model

@@
 temporally increased when the community biomass temporally decreased and
-respectively that the evenness temporally decreased when the community biomass
-temporally increased (Fig. \@ref(fig:bm), Table \@ref(tab:aov)). We observed the
-same pattern between the temporal trends of
-community biomass and that of the pielou of individual number.
+respectively that the evenness of biomass temporally decreased when the community biomass
+temporally increased (Fig. \@ref(fig:bm), Table \@ref(tab:aov)). We also found the
+same pattern between the temporal trends of community biomass and that of the
+pielou of individual number.
 
@@
 
-HERE
-The temporal trends of community biomass, average trophic level, pielou of biomass,
-pielou of individual had a positive relationship with that of species richness
-(Fig. \@ref(fig:rich), Table \@ref(tab:aov)). However, the direct
-relationship between the temporal trends of average trophic level and the one of
-species richness was not significant after controling for community biomass temporal
-trends [**TO CHECK: refaire tous les modèles temporels en mettant à la fois la
-pente des biomasses et de la richness en même temps??**].
+The temporal trends of community biomass and pielou of biomass, had a positive
+relationship with that of species richness (Fig. \@ref(fig:rich), Table
+\@ref(tab:aov)) while we did not find significant relationships between the
+temporal trends of average trophic level, connectance, pielou of individual
+number and the one of species richness (Fig. \@ref(fig:rich), Table
+\@ref(tab:aov)).
 
-We also found that the relationship between the temporal trends of pielou of
-individual and connectance and that of species richness was dependant of the
-overall species richness of the community (Fig. \@ref(fig:rich), Table
-\@ref(tab:aov)), meaning that the relationship between temporal trends of
-pielou of individual and that of species richness was more positive as the
-community contained more species (Fig. \@ref(fig:rich), Table
-\@ref(tab:reg)). While the relationship between temporal trends of pielou
-of individual and that of species richness was more negative as the community
-contained more species (Fig. \@ref(fig:rich), Table \@ref(tab:reg)).
+---
+#We also found that the relationship between the temporal trends of pielou of
+#individual and connectance and that of species richness was dependant of the
+#overall species richness of the community (Fig. \@ref(fig:rich), Table
+#\@ref(tab:aov)), meaning that the relationship between temporal trends of
+#pielou of individual and that of species richness was more positive as the
+#community contained more species (Fig. \@ref(fig:rich), Table
+#\@ref(tab:reg)). While the relationship between temporal trends of pielou
+#of individual and that of species richness was more negative as the community
+#contained more species (Fig. \@ref(fig:rich), Table \@ref(tab:reg)).
+---
 
@@
 We found that species richness, connectance, average trophic level were
-spatially positively related to community biomass while the pielou of biomass was negatively related to
-community biomass (Fig. \@ref(fig:bm), Table \@ref(tab:aov-sp)). However,
-we found no spatial relation between the pielou of individual and community
-biomass.
+spatially positively related to community biomass while the pielou of biomass
+was negatively related to community biomass (Fig. \@ref(fig:bm), Table
+\@ref(tab:aov-sp)). However, we found no spatial relation between the pielou of
+individual and community biomass.
 

### 2021-06-15 R/plan.R

@@ -484,7 +484,7 @@ model = data4model %>%
   ),
   #### Spatial
   target_sp_model_bm_rich = target(
-    get_mod_list(.data = filter(sp_st_data, station %in% y) %>%
+    get_mod_list_lme4(.data = filter(sp_st_data, station %in% y) %>%
       na.omit %>%
       as.data.frame
       ),
@@ -503,6 +503,35 @@ model = data4model %>%
       )
     )
   ),
+#### get standardized coefficients 
+  target_std_coef_sp_model_bm_rich = target(
+
+    map2_dfr(y, names(y),
+      function(model, name) {
+        x <- stdCoef.merMod(model)
+        x$term <- row.names(x)
+        row.names(x) <- NULL
+        x$response <- name
+        x %>%
+          select(response, term, std_estimate)
+      }
+    ),
+    transform = map(
+      y = list(
+        sp_model_bm_rich_mono_trends,
+        sp_model_bm_rich_mono_stable_trends,
+        sp_model_bm_rich_trends,
+        sp_model_bm_rich
+        ),
+      .names = c(
+        "sp_std_coef_bm_rich_mono_trends",
+        "sp_std_coef_bm_rich_mono_stable_trends",
+        "sp_std_coef_bm_rich_trends",
+        "sp_std_coef_bm_rich"
+      )
+    )
+  ),
+
   ### Resume
   target_vif_model_bm_rich = target(
     map(y, ~try(car::vif(.x))),
@@ -660,14 +689,17 @@ model = data4model %>%
   do.call(rbind, .),
   target_sp_reg_table_bm_rich = target(
     map2(
-      model_bm_rich,
-      names(model_bm_rich),
+      y,
+      names(y),
       function(model, name) {
         ml <- broom::tidy(model) %>%
           mutate(response = name) %>%
           select(response, everything())
       }) %>%
-    do.call(rbind, .),
+    do.call(rbind, .) %>%
+    left_join(std, by = c("response", "term")) %>%
+    select(-group) %>%
+    select(response, effect, term, estimate, std_estimate, everything()),
   transform = map(
       y = list(
         sp_model_bm_rich_mono_trends,
@@ -675,6 +707,12 @@ model = data4model %>%
         sp_model_bm_rich_trends,
         sp_model_bm_rich
         ),
+      std = list(
+        sp_std_coef_bm_rich_mono_trends,
+        sp_std_coef_bm_rich_mono_stable_trends,
[…]

### 2021-06-15 R/statistical_model.R

@@ -303,7 +303,47 @@ get_mod_list <- function(.data = NULL, st_by_var = NULL) {
       ))
 }
 
-#' Compute PCA 
+get_mod_list_lme4 <- function(.data = NULL) {
+  rlang::eval_tidy(rlang::quo(
+      list(
+        log_bm_std = lme4::lmer(
+          log_bm_std ~ log_RC1 + log_RC2 + log_rich_std + (1 | basin),
+          data = {{.data}}),
+
+        log_rich_std = lme4::lmer(
+          log_rich_std ~ log_RC1 + log_RC2 + log_bm_std + (1 | basin),
+          data = {{.data}}),
+
+        ct_ff = lme4::lmer(
+          ct_ff ~ log_RC1 + log_RC2 + log_rich_std + log_bm_std + (1 | basin),
+          data = {{.data}}),
+
+        w_trph_lvl_avg = lme4::lmer(
+          w_trph_lvl_avg ~ log_RC1 + log_RC2 + log_rich_std + log_bm_std + (1 | basin),
+          data = {{.data}}),
+
+        piel_bm = lme4::lmer(
+          piel_bm ~ log_RC1 + log_RC2 + log_rich_std + log_bm_std + (1 | basin),
+          data = {{.data}}),
+
+        piel_nind = lme4::lmer(
+          piel_nind ~ log_RC1 + log_RC2 + log_rich_std + log_bm_std +
+          (1 | basin),
+          data = {{.data}})
+      )
+      ))
+}
+
+stdCoef.merMod <- function(object) {
+  sdy <- sd(getME(object,"y"))
+  sdx <- apply(getME(object,"X"), 2, sd)
+  sc <- fixef(object)*sdx/sdy
+  se.fixef <- coef(summary(object))[,"Std. Error"]
+  se <- se.fixef*sdx/sdy
+  return(data.frame(std_estimate = sc, stdse = se))
+}
+
+#' Compute PCA
 
 get_pca_environment <- function (.data = data_for_pca) {
   # Perform PCA

### 2021-06-15 make.R

@@ -26,8 +26,9 @@ gc()
 plan
 print(plan, n = 40)
 
-#TODO check rigor of automatic plotting; all the conditions are respected?
 
+loadd(sp_reg_table_bm_rich_mono_stable_trends,
+  sp_std_coef_bm_rich_mono_stable_trends)
 
 library(future)
 plan(multisession, workers = 3)
@@ -37,12 +38,6 @@ attr(body(get_pred_plot_from_new_model), "srcfile")
 loadd(bm_rich_trends, st_sp, sp_st_data, summary_var_med, data_for_pca,
   st_analysis, sp_slope_x_bound, sp_model_bm_rich_mono_trends)
 
-loadd(model_bm_rich_mono_stable_trends)
-class(model_bm_rich_mono_stable_trends[[1]]) <- "lm"
-model_bm_rich_mono_trends
-"model_bm_rich_mono_stable_trends",
-"model_bm_rich_trends",
-"model_bm_rich"
 
 theme_set(theme_cowplot())
 

### 2021-06-16 paper/manuscript.Rmd
Add new figures and add std coef to results

@@
 estimated trends, i.e. slopes for the response and the explicative
-variable.
+variables.
 
@@
   - $E_2$: PCA2 related to average temperature and average BOD
+
+The significativity of the effects were tested with ANOVA.  In order to be able
+to compare the magnitude of the effects of community biomass and species
+richness in both temporal and spatial models, we computed standardized slopes
+($r_{\delta}$) and their associated standard errors.
+
+$r_{\delta} = \beta\frac{s_x}{s_y}$
+
+with $\beta$ being the unstandardised slope, $s_x$ and $s_y$ the standard
+deviation of the explicative and response variable.
+
+All the statistical models displayed low multicollinearity (VIF < 3, Table XX).
+We visually inspected the residuals of the linear models (TODO).
 
@@
 pielou of individual number to $R_{adj}^2= `r rsq_tlvl`$ for average trophic
-level (Table \@ref(tab:rsq)). The spatial models
- were more performant, with $R_{cond}^2$ varing from 
-`r rsq_tlvl_sp` to `r rsq_piel_bm_sp` (Table \@ref(tab:rsq-sp)).
+level (Table \@ref(tab:rsq)). The spatial models were more performant, with
+$R_{cond}^2$ varing from $`r rsq_tlvl_sp`$ to $`r rsq_piel_bm_sp`$ (Table
+\@ref(tab:rsq-sp)).
 
@@
 ```{r}
-loadd(model_log_bm_f3y_table_medium, model_log_rich_f3y_table_medium)
-reg_bm <- model_log_bm_f3y_table_medium$reg_table
-#reg_bm[reg_bm$y == ]
+loadd(std_table_bm_rich_mono_stable_trends)
+std <-
+  std_table_bm_rich_mono_stable_trends %>%
+  mutate(
+    type = recode(type, spatial = "sp", temporal = "tps"),
+    response = recode(response, log_bm_std = "bm", log_rich_std = "rich", ct_ff
+      = "ct", piel_bm = "p_bm", piel_nind = "p_n", w_trph_lvl_avg = "tlvl"),
+    term = recode(term, log_bm_std = "bm", log_rich_std = "rich")
+    ) %>%
+  rename(t = type, rep = response, sest = std_estimate) %>%
+  mutate_at(vars(sest, stdse), ~round(.x, 2))
+tps_bm <- std %>%
+  filter(t == "tps", term == "bm")
+
+tps_bm_sest <- tps_bm$sest
+names(tps_bm_sest) <- tps_bm$rep
 ```
@@
 community biomass from one side and species richness, average trophic level,
-connectance from the other side (Fig. \@ref(fig:bm), Table \@ref(tab:aov)),
-meaning that they temporally increased when the community biomass temporally increased and
-respectively that they temporally decreased when the community biomass decreased in
-time.
+connectance from the other side (Fig. \@ref(fig:bm), Table \@ref(tab:aov),
+respectively  $r_\delta = `r tps_bm_sest["rich"]`$, $`r tps_bm_sest["tlvl"]`$, 
+$`r tps_bm_sest["ct"]`$), meaning that they temporally increased when the community
+biomass temporally increased and respectively that they temporally decreased
+when the community biomass decreased in time.
 
 We found a significant negative relationship between the temporal trends of
-community biomass and that of the pielou of biomass (Figure \@ref(fig:bm), Table
-\@ref(tab:aov)), meaning that the eveness of biomass across species
-temporally increased when the community biomass temporally decreased and
-respectively that the evenness of biomass temporally decreased when the community biomass
-temporally increased (Fig. \@ref(fig:bm), Table \@ref(tab:aov)). We also found the
-same pattern between the temporal trends of community biomass and that of the
-pielou of individual number.
+community biomass and that of the pielou of biomass 
+( $r_\delta = `r tps_bm_sest["p_bm"]`$), meaning that the eveness of biomass
+across species
+temporally increased when the community biomass
+temporally decreased and respectively that the evenness of biomass temporally
+decreased when the community biomass temporally increased (Fig. \@ref(fig:bm),
+Table \@ref(tab:aov)). We also found the same pattern between the temporal
+trends of community biomass and that of the pielou of individual number
+($r_\delta = `r tps_bm_sest["p_n"]`$).
 
@@
 
+```{r}
+tps_r <- std %>%
+  filter(t == "tps", term == "rich")
+
+tps_r_sest <- tps_r$sest
+names(tps_r_sest) <- tps_r$rep
+```
+
 The temporal trends of community biomass and pielou of biomass, had a positive
 relationship with that of species richness (Fig. \@ref(fig:rich), Table
-\@ref(tab:aov)) while we did not find significant relationships between the
-temporal trends of average trophic level, connectance, pielou of individual
-number and the one of species richness (Fig. \@ref(fig:rich), Table
-\@ref(tab:aov)).
+\@ref(tab:aov), $r_\delta = `r tps_r_sest["p_bm"]`$) while we did not find
+significant relationships between the temporal trends of average trophic level,
+connectance, pielou of individual number and the one of species richness (Fig.
+\@ref(fig:rich), Table \@ref(tab:aov)).
 
@@
 
+```{r}
+sp_b <- std %>%
+  filter(t == "sp", term == "bm")
+sp_b_sest <- sp_b$sest
+names(sp_b_sest) <- sp_b$rep
+
+sp_r <- std %>%
+  filter(t == "sp", term == "rich")
+sp_r_sest <- sp_r$sest
+names(sp_r_sest) <- sp_r$rep
+```
+
 ### Community structure and community biomass
@@
 We found that species richness, connectance, average trophic level were
-spatially positively related to community biomass while the pielou of biomass
-was negatively related to community biomass (Fig. \@ref(fig:bm), Table
-\@ref(tab:aov-sp)). However, we found no spatial relation between the pielou of
-individual and community biomass.
+spatially positively related to community biomass (resp. 
+$r_\delta = `r sp_b_sest["rich"]`$, $`r sp_b_sest["ct"]`$, 
+$`r sp_b_sest["tlvl"]`$, Fig.
+\@ref(fig:bm), Table \@ref(tab:aov-sp)) while the pielou of biomass was
+negatively related to community biomass ($r_\delta = `r sp_b_sest["p_bm"]`$).
+However, we found no spatial relation between the pielou of individual and
+community biomass.
 
@@
 
-We found that community biomass, the pielou of biomass and individual were
-positively related to species richness while average trophic level and
-connectance were negatively related to
-community biomass (Fig. \@ref(fig:rich), Table \@ref(tab:aov-sp)).
+Community biomass, the pielou of biomass and individual were
+positively related to species richness (resp. 
+$r_\delta = `r sp_r_sest["bm"]`$, $`r sp_r_sest["p_bm"]`$,
+$`r sp_r_sest["p_n"]`$) while average
+trophic level and connectance were negatively related to
+species richness (resp. $r_\delta = `r sp_r_sest["tlvl"]`$, $`r sp_r_sest["ct"]`$,
+Fig. \@ref(fig:rich), Table \@ref(tab:aov-sp)).
 
@@
 We found that the temporal increase of the average trophic level was positively
-linked to increase of community biomass. Increase of average trophic level can
-be associated to either gain of biomass in the highest trophic level nor losses
-of biomass in the lowest trophic. In our case, such gain or losses of average
-trophic level is probably associated to the variations of the presence of large
-fishes. This interpretation is confirmed by the finding that the evenness of
-biomass, measured by the pielou, decreased through time as community biomass
-decrease and reversely, meaning that biomass distribution across species
-respectively become respectively less and more even when community biomass
-decrease and increase. We also found no relationship between the temporal trends of evenness based
-on indivual number and that community biomass, confirming that the temporal trends
-of community biomass in our study is linked to few big individuals. It further
-indicates that temporal loss of community biomass are linked with the loss of
-the higher trophic level.
+linked to increase of community biomass in line with a previous model suggesting
+that the presence of higher predator can lead to higher community biomass
+[@wang_biodiversity_2018]. Increase of average trophic level can be associated
+to either gain of biomass in the highest trophic level nor losses of biomass in
+the lowest trophic. In our case, such gain or losses of average trophic level is
+probably associated to the variations of the presence of large fishes. The
+finding that the evenness of biomass, measured by the pielou, decreased through
+time as community biomass decrease and reversely, meaning that biomass
+distribution across species respectively become respectively less and more even
+when community biomass decrease and increase. We also found that evenness
+decreased temporally of number of individual when community biomass increased
+temporally, confirming that the temporal trends of community biomass in our
+study is linked to big individuals. It further indicates that temporal loss of
+community biomass are linked with the loss of the higher trophic level.
 
@@
 
-To the difference with community biomass, the temporal trends of evenness of
-biomass and individual were positively related to the temporal trends of species
+To the difference with community biomass, the temporal trends of eveness of
+biomass was positively related to the temporal trends of species
 richness, meaning that as species richness temporally increase, the
-distribution of biomass and abondance become more even. Our results indicate
-that biomass trends are linked to few big individuals while richness trends are
-linked to overall shift in dominance in communities.
+distribution of biomass become more even, while temporal trends of eveness of
+individual had no significant relationship with species richness. Those results
+indicate that biomass trends are linked to few big individuals while richness
+trends are linked to overall shift in dominance in communities.
 
-Surprinsingly, we found the temporal trends of connectance was not related to
-the one of species richness as found spatially in most empirical foodweb
+Surprinsingly, we found that the temporal trends of connectance was not related to
+the one of species richness as found spatially in most empirical food-web
 [@dunne_network_2006] and also in the present study. This result suggests that
@@
 richness and that species loss and gain concerns species of low trophic level,
-which in turn does not affect connectance. However, the relationship become
+which in turn does affect connectance very little. However, the relationship become
 slightly negative for species poor communities. An explanation might be that
@@
 
-- Add loss of species richness, loss of biomass and increase dominance?
-
-HERE
- @soininen_relationship_2012;
-
 ---
@@
 
-We found that community biomass was linked positively related to species richness
-both in space and in time, indicating that space for time might be use. In the
-same way, we found a positive relationship between average trophic
-level and community biomass both in time and in space. However, it was not the case
-for connectance and average trophic level that were respectively weakly or not
+While space for time works for variation of community biomass, it is less clear
+for the variation of species richness. Indeed, it was not the case for
+connectance and average trophic level that were respectively weakly or not
 linked to species richness in time whereas our result shows a strong negative
-relation in space. Moreover, connectance displayed a strong positive
-relationship with biomass in time but not in space. This result is in accordance
-with other studies which found mismatch between spatial and temporal patterns
-[@adler_contrasting_2007; @johnson_testing_2008]. This mismatch is mainly due to the crucial assumptions
+relation in space. This result is in line with other studies which found
+mismatch between spatial and temporal patterns [@adler_contrasting_2007;
+@johnson_testing_2008]. This mismatch is mainly due to the crucial assumptions
 that variations in space will correspond to differences of assembly stages and
 then reflect the assembly/disassembly trajectories in time of communities [@].
+
+In contrast with a meta-analysis [@soininen_relationship_2012], we found that
+the eveness of individual number is positively related to the one of species
+richness in space in stream fish assemblages but found no relationship in time.
 
@@
 
-## Biomass and richness gains and losses are symmetric processes in terms of community structure
-
-We found no case in which gain or losses of biomass and richness lead to
-different relationship between the temporal dynamic of community structure and
-the one of biomass and species richness. We could have imagined that
-extinction/colonisation processes or immigration/extinction debt could have lead
+---
+### Biomass and richness gains and losses are symmetric processes in terms of community structure
+#
+#We found no case in which gain or losses of biomass and richness lead to
+#different relationship between the temporal dynamic of community structure and
+#the one of biomass and species richness. We could have imagined that
+#extinction/colonisation processes or immigration/extinction debt could have lead
 to different relationships.
+---
 
@@
 
-We showed that BEF works in time but that richness and biomass temporal trends
-through time relates on different ecological processes. We further found that
-space for time subtitution does not always work.
+Our study shows that richness and biomass temporal trends in natural fish
+communities relate on different ecological processes, biomass temporal dynamics
+being related to variation of highest trophic level while it is not the case for
+species richness. Our work also suggests that space for time substitution may be
+relevant to predict food-web community structure in case of biomass variation
+but not for species richness variation. We look forward to next investigations
+to see the generality of assembly rules in food-webs. There are crucial to
+better understand the temporal dynamics of food-webs structure and then its
+impact on ecosystem functioning.
 
@@
 fig2
+```
+
+```{r}
+std_cap <- paste0(
+  "Standardized coefficients of the effects of community biomass and species
+  richness on food-web structure for the temporal and spatial models. The lines
+  display the standard errors."
+)
+```
+
+```{r std, fig.cap=std_cap}
+loadd(fig_std_coef)
+fig_std_coef
 ```

### 2021-06-16 R/packages.R

@@ -7,5 +7,6 @@ library(magrittr)
 library(ggeffects)
 library(cowplot)
 library(lm.beta)
+library(lme4)
 library(broom)
 library(broom.mixed)

### 2021-06-16 R/plan.R

@@ -513,7 +513,7 @@ model = data4model %>%
         row.names(x) <- NULL
         x$response <- name
         x %>%
-          select(response, term, std_estimate)
+          select(response, term, std_estimate, stdse)
       }
     ),
     transform = map(
@@ -528,6 +528,34 @@ model = data4model %>%
         "sp_std_coef_bm_rich_mono_stable_trends",
         "sp_std_coef_bm_rich_trends",
         "sp_std_coef_bm_rich"
+      )
+    )
+  ),
+  target_std_coef_model_bm_rich = target(
+
+    map2_dfr(y, names(y),
+      function(model, name) {
+        x <- stdse.lm(model)
+        x$term <- row.names(x)
+        row.names(x) <- NULL
+        x$response <- name
+        x %>%
+          select(response, term, stdse)#, std_estimate
+        # do not put std_estimate since already computed in model
+      }
+    ),
+    transform = map(
+      y = list(
+        model_bm_rich_mono_trends,
+        model_bm_rich_mono_stable_trends,
+        model_bm_rich_trends,
+        model_bm_rich
+        ),
+      .names = c(
+        "std_coef_bm_rich_mono_trends",
+        "std_coef_bm_rich_mono_stable_trends",
+        "std_coef_bm_rich_trends",
+        "std_coef_bm_rich"
       )
     )
   ),
@@ -648,7 +676,7 @@ model = data4model %>%
     )
     ),
   ### Table
-  reg_table_bm_rich_mono_trends = map2(
+  reg_table_bm_rich_mono_trends = map2_dfr(
     model_bm_rich_mono_trends,
     names(model_bm_rich_mono_trends),
     function(model, name) {
@@ -657,8 +685,9 @@ model = data4model %>%
         select(response, everything())
     }
     ) %>%
-  do.call(rbind, .),
-  reg_table_bm_rich_mono_stable_trends = map2(
+  left_join(std_coef_bm_rich_mono_trends, by = c("response", "term")) %>%
+  select(response, term, estimate, std.error, std_estimate, stdse, everything()),
+  reg_table_bm_rich_mono_stable_trends = map2_dfr(
     model_bm_rich_mono_stable_trends,
     names(model_bm_rich_mono_stable_trends),
     function(model, name) {
@@ -667,8 +696,9 @@ model = data4model %>%
         select(response, everything())
     }
     ) %>%
-  do.call(rbind, .),
-  reg_table_bm_rich_trends = map2(
[…]

### 2021-06-16 make.R

@@ -26,25 +26,17 @@ gc()
 plan
 print(plan, n = 40)
 
-loadd(model_bm_rich_mono_stable_trends)
-test <- model_bm_rich_mono_stable_trends[[3]]
-
-stdse.lm(test)
-
+loadd(sp_reg_table_bm_rich_mono_trends, reg_table_bm_rich_mono_trends,std_coef_bm_rich_trends, sp_std_coef_bm_rich_trends)
+loadd(reg_table_bm_rich_trends)
 
 loadd(
+std_coef_bm_rich_mono_stable_trends,
   sp_reg_table_bm_rich_mono_stable_trends,
+reg_table_bm_rich_mono_trends,
   reg_table_bm_rich_mono_stable_trends,
   std_table_bm_rich_mono_stable_trends
   )
 
-std_table_bm_rich_mono_stable_trends %>%
-  filter(term %in% c("log_rich_std", "log_bm_std")) %>%
-  mutate_at(vars(term, response), ~str_replace_all(., var_replacement())) %>%
-  ggplot(aes(y = std_estimate, x = response, fill = type)) +
-  facet_grid(cols = vars(term)) +
-  geom_bar(stat = "identity", position = position_dodge()) +
-  labs(x = "Response", y = "Standardized estimate")
 
 library(future)
 plan(multisession, workers = 3)

### 2021-06-17 paper/appendix.Rmd
Add figures in appendices

@@
   "piel_bm", "piel_nind")
+```
+
+\beginsupplement
+
+# Data exploration
+
+## Maps
+
+```{r}
+loadd(p_st_mono_trends_stable_rich_bm, st_mono_trends_stable_rich_bm)
+
+st_cap <- paste0(
+  "Repartion of the", length(st_mono_trends_stable_rich_bm), " stations used in
+  the data analysis.")
 
@@
 
-\beginsupplement
+```{r st, fig.cap = st_cap}
+p_st_mono_trends_stable_rich_bm
+```
+
+## Range of variation
+
+```{r}
+range_cap <- paste0(
+  "Range of variation of variables in spatial (vertical line) and temporal
+  dataset for the (A) minimum and maximum values and (B) the range (i.e. maximum
+    - minimum)."
+)
+```
+
+```{r range, fig.cap=range_cap, fig.height=10}
+loadd(p_range)
+
+plot_grid(plotlist = p_range, nrow = 2, labels = "AUTO")
+```
+
+## Correlation
+
+```{r}
+cor_cap <- paste0("Correlation plot among variables for spatial and temporal
+  relationships. ", "Median values over temporal series in each station were
+  used for spatial relationships. ", "For temporal relationships, we used the
+  temporal trends in each station. Futhermore, each station was weighted by the
+  average error standard on the temporal trends of the variables.")
+```
+
+```{r cor, fig.cap=cor_cap}
+oldpar <- par()
+loadd(corr_plot_med, corr_plot_tps)
+
+set_names_corr <- function(mat = NULL) {
+  colnames(mat) <- str_replace_all(colnames(mat), var_replacement())
+  rownames(mat) <- str_replace_all(rownames(mat), var_replacement())
+  return(mat)
+}
+
+corr_plot_tps %<>% set_names_corr(.)
+corr_plot_med %<>% set_names_corr(.)
+
+par(mfrow = c(1, 2))
+corrplot::corrplot(corr_plot_med, type = "upper", diag = FALSE, order =
+  "alphabet")
+title("Spatial")
+corrplot::corrplot(corr_plot_tps, type = "upper", diag = FALSE, order =
+  "alphabet")
+title("Temporal trends")
+```
+
+\newpage
 
@@
   pred_bm_rich_mono_stable_trends)
-
 ```

### 2021-06-17 report_rdv.Rmd
Add figures in appendices

@@
 
-loadd(data4model, rigal_classification, full_data2, summary_var_f3y)
-rigal_classification$classif[[1]]
+loadd(data4model, rigal_classification, full_data2, summary_var_med,
+  st_mono_trends_stable_rich_bm)
 
-range_spatial_variable <- summary_var_f3y %>%
-  select(c("station", get_biomass_var(), get_com_str_var(all = FALSE))) %>%
-  pivot_longer(!station, names_to = "variable", values_to = "values") %>%
-  group_by(variable) %>% 
-  summarise(min = min(values, na.rm = TRUE), max = max(values, na.rm = TRUE)) %>%
-  mutate(range = max - min)
+loadd(p_range)
 
-range_variable_station <- full_data2 %>% 
-  select(c("station", get_biomass_var(), get_com_str_var(all = TRUE))) %>%
-  pivot_longer(!station, names_to = "variable", values_to = "values") %>%
-  group_by(station, variable) %>% 
-  summarise(min = min(values, na.rm = TRUE), max = max(values, na.rm = TRUE))
-
-range_variable_station %>%
-  filter(variable %in% c(get_biomass_var(), get_com_str_var(all = FALSE))) %>%
-  pivot_longer(cols = c(min, max), names_to = "minmax", values_to = "values") %>%
-  ggplot(aes(x = values, fill = minmax)) +
-  geom_histogram() +
-  geom_vline(data = range_spatial_variable %>%
-    pivot_longer(cols = c(min, max), names_to = "minmax", values_to = "values"),
-  aes(xintercept = values, color = minmax)) + facet_wrap(~variable, scale =
-  "free")
-
+plot_grid(plotlist = p_range)
 # Range distibution
-range_variable_station %>%
-  filter(variable %in% c(get_biomass_var(), get_com_str_var(all = FALSE))) %>%
-  mutate(range = abs(max - min)) %>%
-  ggplot(aes(x = range)) +
-  geom_histogram() +
-  geom_vline(data = range_spatial_variable, aes(xintercept = range)) +
-  facet_wrap(~variable, scale = "free") 
 ```

### 2021-06-17 R/report_plot.R

@@ -474,3 +474,96 @@ get_pred_plot_from_new_model <- function(
     )
 
 }
+
+get_corr_plot_tps_trends <- function(
+  classif = NULL,
+  st = st_mono_trends_stable_rich_bm,
+  var_to_keep = c(get_com_str_var(),
+    "nbnode_std", "nb_pisc_rich_std",
+    "nb_pisc_node_std", "prop_pisc_node",
+    "prop_pisc_rich", "bm_std", "log_bm_std")) {
+
+  ti <- classif %>%
+    unnest(classif) %>%
+    select(station, variable, linear_slope, linear_slope_strd_error) %>%
+    filter(station %in% st) %>%
+    filter(variable %in% var_to_keep)
+
+    var_slope <- ti %>%
+      select(station, variable, linear_slope) %>%
+      pivot_wider(names_from = variable, values_from = linear_slope) %>%
+      na.omit
+
+    var_slope_error <- ti %>%
+      select(station, variable, linear_slope_strd_error) %>%
+      pivot_wider(names_from = variable, values_from = linear_slope_strd_error) %>%
+      filter(station %in% var_slope$station) %>%
+      select(-station) %>%
+      rowMeans(., na.rm = TRUE)
+
+    weighted_corr <- cov.wt(
+      var_slope[, !colnames(var_slope) %in% "station"],
+      wt = var_slope_error, cor = TRUE)$cor
+
+    #g <- corrplot::corrplot(weighted_corr,  type = "upper")
+    # does not bc it is a base plot 
+    return(weighted_corr)
+}
+
+get_range_variable_plot <- function(
+  full_data = NULL,
+  sp_data = NULL,
+  st = NULL,
+  var_to_keep = c("ct_ff", "w_trph_lvl_avg", "log_rich_std", "log_bm_std",
+    "piel_bm", "piel_nind")
+  ) {
+
+  range_spatial_variable <- sp_data %>%
+    filter(station %in% st) %>%
+    select(c("station", all_of(var_to_keep))) %>%
+    pivot_longer(!station, names_to = "variable", values_to = "values") %>%
+    mutate(variable = str_replace_all(variable, var_replacement())) %>%
+    group_by(variable) %>%
+    summarise(
+      min = min(values, na.rm = TRUE),
+      max = max(values, na.rm = TRUE)) %>%
+    mutate(range = max - min)
+
+  range_variable_station <- full_data %>%
+    filter(station %in% st) %>%
+    select(c("station", all_of(var_to_keep))) %>%
[…]

### 2021-07-01 paper/appendix.Rmd
Add interaction models + surface plot

@@
 ```
+
+## Interaction between community biomass trends and species richness trends
+
+```{r}
+loadd(model_bm_rich_int_mono_stable_trends)
+```
+
+### ANOVA
+
+```{r}
+model_bm_rich_int_mono_stable_trends %>%
+  .[names(.) %in% c("ct_ff", "w_trph_lvl_avg", "piel_bm")] %>%
+  map(., car::Anova) %>%
+  map(., tidy) %>%
+  map2_dfr(., names(.), ~.x %>% mutate(response = .y) %>% select(response,
+      everything())) %>%
+  kable(., booktabs = TRUE,
+  row.names = FALSE,
+  caption =
+    paste0(
+      "ANOVA results with interactions."
+      ),
+    label = "aov-int"
+    ) %>%
+kable_styling(latex_options =c("scale_down", "stripped")) %>%
+collapse_rows(columns = 1, valign = "top")
+#map(model_bm_rich_int_mono_stable_trends, ~try(car::vif(.x)))
+```
+
+```{r}
+model_bm_rich_int_mono_stable_trends %>%
+  .[names(.) %in% c("ct_ff", "w_trph_lvl_avg", "piel_bm")] %>%
+  map(., tidy) %>%
+  map2_dfr(., names(.), ~.x %>% mutate(response = .y) %>% select(response,
+      everything())) %>%
+  kable(., booktabs = TRUE,
+  row.names = FALSE,
+  caption =
+    paste0(
+      "Regression results with interactions."
+      ),
+    label = "aov-int"
+    ) %>%
+kable_styling(latex_options =c("scale_down", "stripped")) %>%
+collapse_rows(columns = 1, valign = "top")
+```
+
+### Plots
+
+```{r}
+pred_int_rich <- map(model_bm_rich_int_mono_stable_trends,
+      ~ggpredict(.x,
+        terms = c("log_rich_std", "log_bm_std [quart2]")) %>%
+        as_tibble() %>%
+        mutate(group = as.numeric(as.character(group))) %>%
+        rename("log_rich_std" = x, "log_bm_std" = group)
+        ) %>%
+enframe(name = "response", value = "pred_int")
+
+ti <- pred_bm_rich_mono_stable_trends %>%
+  filter(term == "log_rich_std", response %in% c("ct_ff", "w_trph_lvl_avg", "piel_bm")) %>%
+  select(response, raw_plot) %>%
+  left_join(pred_int_rich) %>%
+  mutate(pred_plot_color = pmap(
+      list(raw_plot, response, pred_int),
+      function(p, resp, pred) {
+        p +
+          geom_line(data = pred,
+            aes(
+              y = predicted,
+              x = log_rich_std,
+              color = as.factor(log_bm_std)
+            ), size = 1
+          ) +
+        scale_color_discrete()
+      }
+      )
+  )
+rich_leg <- get_legend(ti$pred_plot_color[[1]])
+
+plot_grid(plotlist = map(ti$pred_plot_color, ~.x + theme(legend.position = "none")), rich_leg)
+```
+
+```{r}
+test <- pred_int_rich[3, ]$pred_int[[1]] %>%
+  select(predicted, log_rich_std, log_bm_std) %>%
+  arrange(log_rich_std, log_bm_std)
+
+mat <- reshape2::acast(test, log_rich_std~log_bm_std, value.var = "predicted")
+library(plotly)
+plot_ly(
+  x = ~as.numeric(colnames(mat)),
+  y = ~as.numeric(rownames(mat)),
+  z = ~mat) %>%
+  add_surface()
+```
+
+```{r}
+pred_int_bm <- map(model_bm_rich_int_mono_stable_trends,
+      ~ggpredict(.x,
+        terms = c("log_bm_std", "log_rich_std [quart2]")) %>%
+        as_tibble() %>%
+        mutate(group = as.numeric(as.character(group))) %>%
+        rename("log_bm_std" = x, "log_rich_std" = group)
+        ) %>%
+enframe(name = "response", value = "pred_int")
+
+ti_bm <- pred_bm_rich_mono_stable_trends %>%
+  filter(term == "log_bm_std", response %in% c("ct_ff", "w_trph_lvl_avg", "piel_bm")) %>%
+  select(response, raw_plot) %>%
+  left_join(pred_int_bm) %>%
+  mutate(pred_plot_color = pmap(
+      list(raw_plot, response, pred_int),
+      function(p, resp, pred) {
+        p +
+          geom_line(data = pred,
+            aes(
+              y = predicted,
+              x = log_bm_std,
+              color = as.factor(log_rich_std)
+            ), size = 1
+          ) +
+        scale_color_discrete()
+      }
+      )
+  )
+
+bm_leg <- get_legend(ti_bm$pred_plot_color[[1]])
+plot_grid(plotlist = map(ti_bm$pred_plot_color, ~.x + theme(legend.position = "none")), bm_leg)
+```
+
+```{r, eval=FALSE}
+test <- model_bm_rich_int_mono_stable_trends[["ct_ff"]]
+co <- coef(test)
+pred <- ggpredict(
+  test,
+  terms = c("log_bm_std ", "log_rich_std")
+  ) %>%
+  as_tibble() %>%
+  mutate(group = as.numeric(as.character(group))) %>%
+  rename("log_bm_std" = x, "log_rich_std" = group)
+
+pred$y <- co[1] +
+  co["log_rich_std"] * pred[["log_rich_std"]] +
+  co["log_bm_std"] * pred[["log_bm_std"]] +
+  co["log_rich_std:log_bm_std"] * pred[["log_rich_std"]] * pred[["log_bm_std"]]
+
+# all.equal(pred$y, pred$predicted)
+
+mat <- reshape2::acast(pred, log_rich_std~log_bm_std, value.var = "y")
+library(plotly)
+plot_ly(
+  x = ~as.numeric(colnames(mat)),
+  y = ~as.numeric(rownames(mat)),
+  z = ~mat, ) %>%
+  add_surface() %>%
+  layout(scene = list(
+      xaxis = list(title = "species richness"),
+      yaxis = list(title = "Community biomass"),
+      zaxis = list(title = "Connectance")
+      ))
+```
+
+```{r, eval=FALSE}
+mod4_3d <- model_bm_rich_int_mono_stable_trends[
+  names(model_bm_rich_int_mono_stable_trends) %in%
+    c("ct_ff", "w_trph_lvl_avg")]
+
+pred_list <- map(mod4_3d,
+  function (modl, p) {
+    co <- coef(modl)
+    p$y <- co[1] +
+#      co["log_rich_std"] * p[["log_rich_std"]] +
+      co["log_bm_std"] * p[["log_bm_std"]] +
+      co["log_rich_std:log_bm_std"] * p[["log_rich_std"]] * p[["log_bm_std"]]
+    return(p)
+
+  }, p = pred)
+```
+
+```{r,eval=FALSE}
+mat <- reshape2::acast(
+  pred_list$w_trph_lvl_avg,
+  log_rich_std~log_bm_std,
+  value.var = "y")
+plot_ly(
+  x = ~as.numeric(colnames(mat)),
+  y = ~as.numeric(rownames(mat)),
+  z = ~mat, ) %>%
+  add_surface() %>%
+  layout(scene = list(
+      xaxis = list(title = "Community biomass"),
+      yaxis = list(title = "species richness"),
+      zaxis = list(title = "Avg trophic level")
+      ))
+```
+
+```{r,eval=FALSE}
+test <- model_bm_rich_int_mono_stable_trends[["piel_bm"]]
+car::Anova(test)
+co <- coef(test)
+pred <- ggpredict(
+  test,
+  terms = c("log_bm_std ", "log_rich_std")
+  ) %>%
+  as_tibble() %>%
+  mutate(group = as.numeric(as.character(group))) %>%
+  rename("log_bm_std" = x, "log_rich_std" = group)
+
+pred$y <- co[1] +
+  co["log_rich_std"] * pred[["log_rich_std"]] +
+  co["log_bm_std"] * pred[["log_bm_std"]] +
+  co["log_rich_std:log_bm_std"] * pred[["log_rich_std"]] * pred[["log_bm_std"]]
+
+# all.equal(pred$y, pred$predicted)
+
+mat <- reshape2::acast(pred, log_rich_std~log_bm_std, value.var = "y")
+plot_ly(
+  x = ~as.numeric(colnames(mat)),
+  y = ~as.numeric(rownames(mat)),
+  z = ~mat, ) %>%
+  add_surface() %>%
+  layout(scene = list(
+      xaxis = list(title = "species richness"),
+      yaxis = list(title = "Community biomass"),
+      zaxis = list(title = "Eveness of biomass")
+      ))
+```

### 2021-07-01 paper/manuscript.Rmd
Add figures in appendices
Add interaction models + surface plot

@@
 and reversely. There same the same pattern for species richness, with
-communities that displayed high species richness at the
-beginning of their monitoring tend to display decrease in species richness through time
-and reversely.
+communities that displayed high species richness at the beginning of their
+monitoring tend to display decrease in species richness through time and
+reversely.
 
@@
 structure from one side and species richness and community biomass from another
-side, we modelled the dynamics the temporal trends of food-web
-structure ($dN$) in function of the temporal trends of community biomass ($dB$) and species
+side, we modelled the dynamics the temporal trends of food-web structure ($dN$)
+in function of the temporal trends of community biomass ($dB$) and species
 richness ($dR$).
@@
   bm_x = "log_bm_std",
-  bm_y = c(get_com_str_var(), "log_rich_std", "piel_nind", "piel_bm"),
-  rich_y = c(get_com_str_var(), "log_bm_std", "piel_nind", "piel_bm"),
+  bm_y = c("ct_ff", "w_trph_lvl_avg", "piel_bm"), #, "piel_nind"
+  rich_y = c("ct_ff", "w_trph_lvl_avg", "log_bm_std", "piel_bm"), #, "piel_nind"
   rich_x = "log_rich_std"
@@
 p_bm <- fig1_2$bm
-names(p_bm) <- c("log_rich_std", "ct_ff", "w_trph_lvl_avg",
-  "piel_bm", "piel_nind")
-#plot_grid(plotlist = p_bm)
+names(p_bm) <- c("ct_ff", "w_trph_lvl_avg", "piel_bm")
+plot_grid(plotlist = p_bm)
 
@@
 ```{r}
+fig_bef_cap <- paste0(
+  "Relationship between the temporal trends of community structure
+  and the one of species richness. Lines correspond to the predictions of the
+  linear models. The lines surrounding each point represent the standard error
+  associated to the temporal trends."
+)
+```
+```{r bef, fig.cap=fig_bef_cap}
+fig1_2$rich$log_bm_std
+```
+
+```{r}
+fig_bm_rich_cap <- paste0(
+  "Relationship among the temporal trends of community structure
+  and the one of species richness and community biomass. The lines
+  surrounding each point represent the standard error associated to the temporal
+  trends."
+)
+```
+```{r bmr, fig.height = 12, fig.cap=fig_bm_rich_cap}
+fig2 <- fig1_2
+fig2$rich$log_bm_std <- NULL
+plot_grid(
+  plot_grid(plotlist = fig2$bm, nrow = 1),
+  plot_grid(plotlist = fig2$rich, nrow = 1),
+  nrow = 2
+)
+```
+
+```{r bm, eval=FALSE, fig.height = 12, fig.cap=fig_bm_cap}
 ti <- list()
@@
 }
-```
 
-```{r bm, fig.height = 12, fig.cap=fig_bm_cap}
 # Make the label on two lines
@@
 
-```{r}
+```{r rich, eval=FALSE,fig.height = 12, fig.cap=fig_rich_cap}
 trich <- list()
@@
 }
-```
 
-```{r rich, fig.height = 12, fig.cap=fig_rich_cap}
 # Make the label on two lines

### 2021-07-16 draft.Rmd
first try of a method figure

# For Loubna

```{r}
library(drake)
library(tidyverse)

mypath <- rprojroot::find_package_root_file

source(mypath("R", "misc.R"))
source_dir(mypath("R"))
theme_set(theme_cowplot())
```

```{r}
get_bm_dyn_year <- function (com = NULL, station = NULL) {

  st <- station
  test <- com %>%
    filter(station == st)

  test %<>%
    mutate(sp_tibble = map(sp_vector, ~tibble(species = names(.x), biomass_sp = .x))) %>%
    unnest(sp_tibble) %>%
    mutate(bm_std_sp = biomass_sp / surface) %>%
    dplyr::select(station, year, species, bm_std_sp)

  test %<>% 
    pivot_wider(names_from = species, values_from = "bm_std_sp")%>%
    mutate_at(vars(matches("[A-Z]{3}", ignore.case = FALSE)), ~ifelse(is.na(.), 0, .)) %>%
    pivot_longer(cols = matches("[A-Z]{3}", ignore.case = FALSE), names_to = "species", values_to = "bm_std_sp")

  return(test)
}
get_network_summary <- function (com = NULL, station = NULL, stab = TRUE, com_avg = TRUE) {

  st <- station
  tmp <- com %>%
    filter(station == st) %>%
    mutate_if(is.double, ~round(., 2))

  label_stab <- c(
    "Stability" = tmp$bm_std_stab,
    "Synchrony" = tmp$sync, 
    "CVsp" = tmp$cv_sp,
    "Median total biomass" = tmp$prod_std #"' * (g/m^2) * '"
    )
  label_com <- c(
    "Median species richness" = tmp$richness_med,
    "Median connectance" = tmp$ct,
    "Median avg trophic level" = tmp$t_lvl
  )
  label <- NULL

  if (stab) {
    label <- c(label, label_stab)

  }

  if (com_avg) {

    label <- c(label, label_com)

  }

  return(label)

}

plot_dyn_web  <- function (
  com = NULL, sem_df = NULL, station = NULL,
  stacked = FALSE, .log = FALSE, color_species = NULL, label = NULL,
  label_parsed = FALSE, label_size = 4.5, y_label = NULL, my_ylim = NULL) {

  # get bm dynamic 
  com <- get_bm_dyn_year(com = com, station = station)

  # get total biomass 
    total_bm <- com %>%
	  group_by(year) %>%
	  summarise(bm_std_sp = sum(bm_std_sp)) %>%
	  mutate(species = "Total")

  p <- com %>%
    ggplot(aes(x = year, y = bm_std_sp, color = species))

  if (stacked) {
    p <- p + 
      geom_area(aes(fill = species))
  } else {
    p <- p + 
      geom_line() +
      geom_line(data = total_bm, color = "black")
  }

  if ( !is.null(my_ylim) ) 
  {
    p <- p +
      ylim(my_ylim)
  }

  # Make it professional:
  p <- p +
    labs(y = expression(Biomass~density~(g/m^2)), x = "Year")

  if (!is.null(sem_df)) {

    label <- get_network_summary(com = sem_df, station = station) 
  }

  if (!is.null(label)) {

    if (is.null(y_label)) {
      y_label <- max(total_bm$bm_std_sp) + max(total_bm$bm_std_sp) * 5/100
    }

    p <- p +
    annotate("text", x = median(total_bm$year),
      y = y_label,
      label = label, parse = label_parsed, size = label_size)
  }

  if (.log) {
    p <- p + scale_y_log10()
  }

  if (!is.null(color_species)) {
    p <- p + 
      scale_fill_manual(values = color_species) +
      scale_color_manual(values = color_species)
  }

  return(p)

}

get_label_from_named_vector <- function ( label = NULL, collapse = "\n") {
  paste0(names(label), " = ", label, collapse = collapse)
} 
```

```{r}
get_adj_net_station <- function (net = NULL, station = NULL) {

  st <- station

  net <- net %>%
    filter(station %in% st) %>%
    dplyr::select(station, year, network) %>%
    unnest(cols = c(network))

  ## Compute metrics:
  net %>%
    dplyr::select(year, from, to) %>%
    arrange(year) %>%
    group_by(year) %>%
    nest(network = c(from, to)) %>%
    mutate(
      igraph_obj = map(network, igraph::graph_from_data_frame,
	directed = TRUE),
      adj_mat = map(igraph_obj, igraph::as_adjacency_matrix,
	sparse = FALSE),
      troph = map(adj_mat, ~NetIndices::TrophInd(.x)),
      obs_troph_level_vector = map(troph, function (x) {
	TL <- x$TL
	names(TL) <- rownames(x) 
	return(TL)
	})
    )
}

get_net_biomass <- function (net = NULL, station = NULL) {

  st <- station

  # Get bm
  net <- net %>%
    filter(station %in% st) %>%
    dplyr::select(year, composition) %>%
    unnest(cols = c(composition))  %>%
    dplyr::select(year, sp_class, bm_std)

   # Make list
    net %<>%
      arrange(year) %>%
      group_by(year) %>%
      nest(bm = c(sp_class, bm_std)) %>%
      mutate(bm = map(bm, deframe))
  net
}

set_color_nodes <- function (
  node_list = NULL,
  color_species_resources = NULL
  ) {

  node_list_sp <- stringr::str_replace_all(node_list, "_\\d", "")

  colour <- color_species_resources[node_list_sp]
  names(colour) <- node_list
  return(colour)
}

set_node_resources_abun <- function (
  node_list = NULL,
  node_abun = NULL, resource_abun = NULL) {

  abun <- vector("numeric", length(node_list))  
  names(abun) <- node_list

  if (is.null(resource_abun)) {
    resource_abun <- mean(node_abun)
  }

  abun[names(node_abun)] <- node_abun 
  abun[abun == 0] <- resource_abun 
  return(abun)

}

get_network_temporal_plot <- function (
  net_list = NULL,
  station = NULL,
  selected_years = NULL,
  node_color = NULL,
  scale_node_size = 0.01,
  par_options = par(mar = c(0,0,4,0)),
  add_title = FALSE,
  rel_abun = FALSE,
  log_abun = FALSE
  ) {

  net <- get_adj_net_station(net = net_list, station = station)
  bm <- get_net_biomass(net = net_list, station = station)

  if (!is.null(selected_years)) {
    net %<>% filter(year %in% selected_years) 
    bm %<>% filter(year %in% selected_years) 
  }

  if (is.null(node_color)) {
    node_color <- set_color_species(
      node_list = unique(names(unlist(net$obs_troph_level_vector))),
      species_list = NULL, resource_list = NULL, col_resource = NULL)
  }

  list_p <- list()
  index <- seq_along(net$year)

  for (i in index) {
    if(!is.null(par_options)) {
      par_options
    }
    plot.new()
    PlotWeb(
      TL = net$obs_troph_level_vector[[index[i]]],
      webTL = net$adj_mat[[index[i]]],
      colnode = set_color_nodes(
	node_list = names(net$obs_troph_level_vector[[index[i]]]),
	color_species_resources = node_color),
      abund = set_node_resources_abun(
	node_list = names(net$obs_troph_level_vector[[index[i]]]),
	node_abun = bm$bm[[index[i]]],
	resource_abun = 1
	),
      collink="grey70",
      scale_abun = scale_node_size,
      rel_abun = rel_abun,
      log_abun = log_abun
    )
    if (add_title) {
     title(main = paste0(net$year[[index[i]]]))
    }

    p <- recordPlot()

    list_p[[i]] <- p 
  }

  gg <- map(list_p, ggdraw)
  gg
}
```

```{r}
loadd(rigal_classification, com_data, op_data)
op_data %<>%
  mutate(year = as.integer(year))
myload(community_metrics, dir =
  "~/Documents/post-these/mnhn/fishcom_biomass_dynamics/data", envir =
  environment())

community_metrics %<>%
    left_join(dplyr::select(op_data, station, opcod, year))
ti <- rigal_classification %>%
  filter(variable == "bm_std") %>%
  unnest(classif)
first_st <- ti %>%
  filter(shape_class == "decrease_constant") %>%
  arrange(linear_slope)

tes <- map(first_st$station[1:12], ~plot_dyn_web(
    com = community_metrics,
    sem_df = NULL,
    station = .x,
#    .log = TRUE,
    stacked = TRUE
    ))
plot_grid(plotlist = tes)
```
```{r}

last_st <- ti %>%
  filter(shape_class == "increase_constant") %>%
  arrange(linear_slope)

tes <- map(last_st$station[1:12], ~plot_dyn_web(
    com = community_metrics,
    sem_df = NULL,
    station = .x,
#    .log = TRUE,
    stacked = TRUE
    ))
plot_grid(plotlist = tes)
```

```{r}
st <- first_st$station[4]
st[2] <- last_st$station[13]
names(st) <- c("decreasing", "increasing") 
#11432 my choice
```

```{r}
myload(network_analysis, dir =
  "~/Documents/post-these/mnhn/fishcom_biomass_dynamics/data/classes", envir =
  environment())
network_analysis %<>%
  left_join(dplyr::select(op_data, opcod, station, year)) %>%
  filter(!is.na(opcod))

p <- get_network_temporal_plot(
  net_list = network_analysis,
  station = st[1],
  selected_years = NULL,
  node_color = NULL, scale_node_size = 0.06,
  par_options = par(mar = c(0,0,0,0)),
  log_abun = TRUE
)
g <- plot_grid(plotlist = map(p, ggdraw), nrow = 3)

save_plot(
  "figures/decreasing_biomass_network.png", g,
  nrow = 3,
  ncol = 4,
  base_height = 4,
  base_width = 4)

p2 <- get_network_temporal_plot(
  net_list = network_analysis,
  station = st[2],
  selected_years = NULL,
  node_color = NULL, scale_node_size = 0.06,
  par_options = par(mar = c(0,0,0,0)),
  log_abun = TRUE
)
g2 <- plot_grid(plotlist = map(p2, ggdraw), nrow = 4)

save_plot(
  "figures/increasing_biomass_network.png", g2,
  nrow = 4,
  ncol = 4,
  base_height = 4,
  base_width = 4)
```

```{r}
library(lubridate)

tes <- plot_dyn_web(
    com = mutate(community_metrics, year = ymd(year, truncated = 2L)),
    sem_df = NULL,
    station = st[1],
#    .log = TRUE,
    stacked = TRUE
    )

tps_bm_dec  <- tes +
  theme(legend.position = "none")

save_plot(
  "figures/decreasing_biomass.png", tps_bm_dec,
  nrow = 1,
  ncol = 1,
  base_height = 4,
  base_width = 7)

tes2 <- plot_dyn_web(
    com = mutate(community_metrics, year = ymd(year, truncated = 2L)),
    sem_df = NULL,
    station = st[2],
#    .log = TRUE,
    stacked = TRUE
    )

tps_bm_inc  <- tes2 +
  theme(legend.position = "none")

save_plot(
  "figures/increasing_biomass.png", tps_bm_inc,
  nrow = 1,
  ncol = 1,
  base_height = 4,
  base_width = 7)
```

# Plot temporal dynamics

```{r}
loadd(full_data2, rigal_classification)
```
```{r}
rig_st_dec <- rigal_classification %>%
  filter(variable == "ct_ff") %>%
  unnest(classif) %>%
  filter(station == st[1])
```

```{r}
tps_ct_dec <- full_data2 %>%
  mutate(year = ymd(year, truncated = 2L)) %>%
  filter(station == st[1]) %>%
  ggplot(aes(x = year, y = ct_ff)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ x,
    size = 1, se = FALSE, color = "black") +
  labs(x = "Year", y = "Connectance")

plot_temporal_variable_lm <- function(
  .df = full_data2,
  var = "ct_ff",
  st = 15818) {
  .df %>%
    filter(station %in% st) %>%
    mutate(
      year = ymd(year, truncated = 2L),
      station = str_replace_all(station, setNames(names(st), st))
      ) %>%
    ggplot(aes_string(x = "year", y = var)) +
    geom_point() +
    geom_smooth(aes(group = station), method = "lm", formula = y ~ x,
      size = 1, se = FALSE, color = "black") +
    labs(x = "Year", y = str_replace_all(var, var_replacement()))

}

tps_dec_inc <- map(c("ct_ff", "w_trph_lvl_avg", "log_rich_std", "piel_bm"),
  ~plot_temporal_variable_lm(st = st, var = .x) +
  facet_grid(cols = vars(station))
)

plot_grid(plotlist = tps_dec_inc)
```

```{r}
loadd(map_st)

test_fig_mat_met <- plot_grid(
  map_st,
  plot_grid( plot_grid(tps_bm_dec, tps_bm_inc)), 
  plot_grid(plotlist = tps_dec_inc),
  nrow = 3
)
save_plot(test_fig_mat_met,
  file = get_mypath("figures", "matmet.png") 
)
```

### 2021-08-25 draft.Rmd
Clean appendix

@@
 )
-save_plot(test_fig_mat_met,
+save_plot(
+  test_fig_mat_met,
+  base_height = 7,
+  base_asp = 1.618,
   file = get_mypath("figures", "matmet.png")

### 2021-08-25 paper/appendix.Rmd
Clean appendix

@@
 ```{r, echo = FALSE, message = FALSE, collapse = FALSE}
-
 library(drake)
@@
 source(mypath("R/misc.R"))
-source_dir(get_mypath("R")) # Define your custom code as a bunch of functions.
+source_dir(mypath("R")) # Define your custom code as a bunch of functions.
 
@@
   the data analysis.")
-
 ```
@@
 )
-loadd(st_trends_rich_bm, st_mono_trends_rich_bm,
-  st_mono_trends_stable_rich_bm)
-
-loadd(pred_bm_rich_mono_trends, pred_bm_rich, pred_bm_rich_trends,
-  pred_bm_rich_mono_stable_trends)
+loadd(
+  st_trends_rich_bm,
+  st_mono_trends_rich_bm,
+  st_mono_trends_stable_rich_bm,
+  basin_station
+)
+loadd(
+  pred_bm_rich_mono_trends,
+  pred_bm_rich,
+  pred_bm_rich_trends,
+  pred_bm_rich_mono_stable_trends
+)
 ```
@@
 
-### Only mono trends
+```{r sens, out.width="100%"}
+# Merge reg_table
+merged_reg_table <- pmap_dfr(
+  list(
+    df = list(
+      reg_table_bm_rich_mono_trends,
+      reg_table_bm_rich_mono_stable_trends,
+      reg_table_bm_rich_trends,
+      reg_table_bm_rich
+      ),
+    name = list(
+      "Only monotonuous trends",
+      "Monotonuous + stable trends",
+      "All significant trends",
+      "All trends"
+      ),
+    st = list(
+      st_mono_trends_rich_bm,
+      st_mono_trends_stable_rich_bm,
+      st_trends_rich_bm,
+      seq(1,400)
+    )
+    ), function (df, name, st) {
+    df$selection <- paste0(name, " (N = ", length(st),")")
+    return(select(df, selection, everything()))
+  }
+)
 
-We kept only the stations that had monotonic trends for biomass and species
-richness, with resulting `r length(st_mono_trends_rich_bm)` stations.
-
-```{r}
-
-plot_grid(plotlist = pred_bm_rich_mono_trends$pred_plot)
-```
-
-```{r}
-reg_table_bm_rich_mono_trends %>%
-  kable(., booktabs = TRUE,
-  row.names = FALSE,
-    caption =
-      paste0(
-      "Regression coefficients for the linear models explaining the links
-      between the temporal trends of the network structure and the one of
-      community biomass and species richness."
-    ),
-  label = "reg-rich-mono"
+merged_reg_table %>%
+  filter(! term %in% "(Intercept)", ! response %in% "piel_nind") %>%
+  mutate(
+   response = str_replace_all(response, var_replacement()),
+   term = str_replace_all(term, var_replacement()),
   ) %>%
-  kable_styling(latex_options = c("scale_down", "stripped")) %>%
-  collapse_rows(columns = 1, valign = "top")
-```
-
-```{r}
-anova_table_bm_rich_mono_trends %>%
-  kable(., booktabs = TRUE,
-  row.names = FALSE,
-    caption =
-      paste0(
-	"ANOVA results for the links between the temporal trends of the network
-	structure and the one of community biomass and species richness."
-	),
-      label = "aov-rich-mono"
-      ) %>%
-  kable_styling(latex_options = c("scale_down", "stripped")) %>%
-  collapse_rows(columns = 1, valign = "top")
-```
-
-\newpage
-
-### All trends (non monotonic)
-
-We kept all stations that had a significant trend (decrease or increase) for both
-species richness and community biomass, with resulting 
-`r length(st_trends_rich_bm)` stations.
-
-```{r}
-plot_grid(plotlist = pred_bm_rich_trends$pred_plot)
-```
-
-```{r}
-reg_table_bm_rich_trends %>%
-  kable(., booktabs = TRUE,
-  row.names = FALSE,
-    caption =
-      paste0(
-	"Regression coefficients for the linear models explaining the links
-	between the temporal trends of the network structure and the one of
-	community biomass and species richness."
-    ),
-  label = "reg-rich-trends"
-  ) %>%
-  kable_styling(latex_options = c("scale_down", "stripped")) %>%
-  collapse_rows(columns = 1, valign = "top")
-```
-
-```{r}
-anova_table_bm_rich_trends %>%
-  kable(., booktabs = TRUE,
-  row.names = FALSE,
-    caption =
-      paste0(
-	"ANOVA results for the links between the temporal trends of species
-	richness and the temporal trends of the network structure."
-	),
-      label = "aov-rich-trends"
-      ) %>%
-  kable_styling(latex_options =c("scale_down", "stripped")) %>%
-  collapse_rows(columns = 1, valign = "top")
-```
-
-\newpage
-
-### All monotonic stations (i.e + monotonic stable)
-
-```{r}
-plot_grid(plotlist = pred_bm_rich_mono_stable_trends$pred_plot)
-```
-
-```{r}
-reg_table_bm_rich_mono_stable_trends %>%
-  kable(., booktabs = TRUE,
-  row.names = FALSE,
-    caption =
-      paste0(
-	"Regression coefficients for the linear models explaining the links
-	between the temporal trends of the network structure and the one of
-	community biomass and species richness."
-    ),
-  label = "reg-rich-trends"
-  ) %>%
-  kable_styling(latex_options = c("scale_down", "stripped")) %>%
-  collapse_rows(columns = 1, valign = "top")
-```
-
-```{r}
-anova_table_bm_rich_mono_stable_trends %>%
-  kable(., booktabs = TRUE,
-  row.names = FALSE,
-    caption =
-      paste0(
-	"ANOVA results for the links between the temporal trends of species
-	richness and the temporal trends of the network structure."
-	),
-      label = "aov-rich-trends"
-      ) %>%
-  kable_styling(latex_options =c("scale_down", "stripped")) %>%
-  collapse_rows(columns = 1, valign = "top")
-```
-
-\newpage
-
-### All stations
-
-We kept all the stations.
-
-```{r}
-plot_grid(plotlist = pred_bm_rich$pred_plot)
-```
-
-```{r}
-reg_table_bm_rich %>%
-  kable(., booktabs = TRUE,
-  row.names = FALSE,
-    caption =
-      paste0(
-	"Regression coefficients for the linear models explaining the links
-	between the temporal trends of the network structure and the one of
-	community biomass and species richness."
-    ),
-  label = "reg-rich-all"
-  ) %>%
-  kable_styling(latex_options = c("scale_down", "stripped")) %>%
-  collapse_rows(columns = 1, valign = "top")
-```
-
-```{r}
-anova_table_bm_rich %>%
-  kable(., booktabs = TRUE,
-  row.names = FALSE,
-  caption =
-    paste0(
-      "ANOVA results for the links between the temporal trends of species
-      richness and the temporal trends of the network structure."
-      ),
-    label = "aov-rich-all"
-    ) %>%
-kable_styling(latex_options =c("scale_down", "stripped")) %>%
-collapse_rows(columns = 1, valign = "top")
+  ggplot(aes(x = term, y = std_estimate)) +
+  geom_point(aes(color = selection)) +
+  facet_grid(cols = vars(response)) +
+  labs(
+    x = "Explicative variable",
+    y = "Standardized coefficients"
+  ) +
+  theme(legend.position = "bottom", axis.text.x = element_text(hjust=1, angle = 15))
 ```
@@
 
-```{r}
+```{r eval = FALSE}
 test <- pred_int_rich[3, ]$pred_int[[1]] %>%
@@
 
-```{r, eval=FALSE}
+```{r, echo=FALSE, eval=FALSE}
 test <- model_bm_rich_int_mono_stable_trends[["ct_ff"]]
+car::Anova(test)
 co <- coef(test)
@@
 pred$y <- co[1] +
-  co["log_rich_std"] * pred[["log_rich_std"]] +
+ # co["log_rich_std"] * pred[["log_rich_std"]] + bc not significant
   co["log_bm_std"] * pred[["log_bm_std"]] +
@@
 library(plotly)
-plot_ly(
+p <- plot_ly(
   x = ~as.numeric(colnames(mat)),
@@
 
-```{r, eval=FALSE}
+```{r, result=FALSE}
 mod4_3d <- model_bm_rich_int_mono_stable_trends[
@@
 
-```{r,eval=FALSE}
+```{r,result=FALSE}
 mat <- reshape2::acast(
@@
   value.var = "y")
-plot_ly(
+p <- plot_ly(
   x = ~as.numeric(colnames(mat)),
@@
 
-```{r,eval=FALSE}
+```{r,result=FALSE, eval=FALSE}
 test <- model_bm_rich_int_mono_stable_trends[["piel_bm"]]
@@
 mat <- reshape2::acast(pred, log_rich_std~log_bm_std, value.var = "y")
-plot_ly(
+p <- plot_ly(
   x = ~as.numeric(colnames(mat)),
@@
 ```
+
+```{r}
+p_ct_ff <- ggdraw() +
+    draw_image(get_mypath("figures", "int_rich_bm_cf_ff.png"), scale = 1)
+p_tlvl <- ggdraw() +
+    draw_image(get_mypath("figures", "int_rich_bm_tlvl.png"), scale = 1)
+p_piel_bm <- ggdraw() +
+    draw_image(get_mypath("figures", "int_rich_bm_eveness.png"), scale = 1)
+plot_grid(
+  p_ct_ff,
+  p_tlvl,
+  p_piel_bm
+)
+```
+
+- Results for interactions: 
+  - Connectance: 
+    - Always decreases when richness decreases (inverse of expectation)
+    - Increases when richness increases (inverse of expectation), but always
+      decreases if biomass decreases
+    - Increases when biomass increases
+  - Average trophic level:
+    - Always decreases when biomass decreases 
+    - Always increases when biomass increases 
+    - Whatever the richness dynamics, it is the biomass dynamics which drives
+      all
+  - Pielou of biomass:
+    - Always positive when biomass decreases
+    - Always negative when biomass increases
+
+```{r}
+template_cross <- tibble(
+  bm_std = c("-", "0", "+"),
+  `-` = c(NA, NA, NA),
+  `0` = c(NA, NA, NA),
+  `+` = c(NA, NA, NA),
+  )
+
+ct_ff_cross_table <- tibble(
+  rich_std = c("-", "0", "+", "sign_relationship"),
+  `-` = c("-", "-", "--", "-"),
+  `0` = c("-", "-", "-", "0"),
+  `+` = c("-", "+", "++", "+"),
+  "sign_relationship" = c("0", "+", "+", "")
+  )
+
+kable(ct_ff_cross_table) %>%
+  add_header_above(c(" " = 1, "bm_std" = 3))
+```
+
+```{r}
+tlvl_cross_table <- tibble(
+  rich_std = c("-", "0", "+", "sign_relationship"),
+  `-` = c("-", "0", "+", "+"),
+  `0` = c("-", "0", "+", "+"),
+  `+` = c("-", "0", "+", "+"),
+  "sign_relationship" = c("+", "0", "-", "")
+  )
+
+kable(tlvl_cross_table) %>%
+  add_header_above(c(" " = 1, "bm_std" = 3))
+```

### 2021-08-25 paper/manuscript.Rmd
Clean appendix

@@
     toc: true
+  bookdown::word_document:
 fontsize: 12pt
@@
 
+- TODO:
+  - [ ] RM Pielou of abundances
+  - [ ] Interaction tables 
+  - [ ] Interaction plots
+
 # Introduction
 
-## community structure are dynamics and affect ecosystem functions
+## community structure is dynamic and affect ecosystem functions
 
@@
 @hallmann_more_2017; @albano_native_2021], as well as decrease in species
-richness 
-[@barnosky_has_2011; @newbold_global_2015]. Consequences of such trends on
-various aspects of community structure are not well-known whereas numerous
+richness [@barnosky_has_2011; @newbold_global_2015]. Whereas numerous
 ecological studies have shown that the different aspects of community structure
-are tightly linked [REF].
+are tightly linked [@thebault_food-web_2003; @dunne_network_2006;
+@soininen_relationship_2012], the consequences of temporal variations of community
+biomass and species richness on community structure are not well-known.
 
-The temporal trends of species richness and community biomass are indeed
-predicted to affect community structure. The positive link between Biodiversity
-and ecosystem functioning shown in experimental studies predict that loss and
+## Variations of community biomass and species richness are predicted to affect community structure
+
+Changes of species richness and community biomass are indeed
+predicted to affect community structure. The positive link between biodiversity
+and ecosystem functioning in experimental studies predict that loss and
 gain of species richness should respectively result in loss and gain of
@@
 this relation is not always found in natural settings [@grace_integrative_2016;
-@li_relationship_2018; @maureaud_biodiversityecosystem_2019]. Numerous studies
-find relation between species richness and evenness, but their disagree on the
-sign of the relationships [@soininen_relationship_2012; @ma_species_2005;
-@maureaud_biodiversityecosystem_2019], highlighting the diversity of assembly
-processes in ecological communities.
+@li_relationship_2018; @maureaud_biodiversityecosystem_2019].
+
+Variations of species richness can also result in variation of evenness, i.e.
+equitability of species abundances or biomasses. Several studies shows that
+higher evenness of abundances is linked to higher plant biomass in grasslands
+and primary productivity in marine ecosystems [@soininen_relationship_2012].
+Furthermore, studies reported that higher evenness plays a role of insurance in
+face of perturbations [@wittebolle_initial_2009]. Indeed, most studies reported
+positive relationship between species richness and evenness, but also neutral
+and negative ones [@soininen_relationship_2012; @ma_species_2005;
+@maureaud_biodiversityecosystem_2019].
+
+## Variations of community biomass and species richness are predicted to affect food-web structure
 
@@
 biomass. In food-webs, connectance, which measures the degree of generalism in a
-network, has been theoretically shown to positively scale with
-community biomass [@thebault_food-web_2003]. Connectance has been also shown to
-be negatively related to species richness in empirical food-webs
-[@dunne_network_2006]. Trophic level has also been shown to be positively linked
-to total biomass in theoretical models [@wang_biodiversity_2018]. All together,
-these studies show that the different dimensions of network structure are 
-closely linked.
+network, has been theoretically shown to positively scale with community biomass
+[@thebault_food-web_2003].  Connectance has been also shown to be negatively
+related to species richness in empirical food-webs [@dunne_network_2006].
+Trophic level has also been shown to be positively linked to total biomass in
+theoretical models [@wang_biodiversity_2018].
+
+The different dimensions of network and community structure are closely linked
+but, we have no direct evidence on how they covary according to the
+loss or gain of species richness and community biomass across time.
+
+## Predictions come mainly from space-for-time substitution
 
@@
 1995-2018, we assessed the relationships among temporal trends of food-web
-structure, trends of community biomass and trends in species richness.  
-Moreover, we tested if the those relationships differs between communities that
-loosed or gained biomass/species richness across time, reflecting potential
-difference between disassembly and assembly processes. We finally assessed if
-spatial relationships display the same patterns as temporal ones, to assess
-the validity of space for time substitution.
+structure, trends of community biomass and trends in species richness. We
+then assessed if spatial relationships display the same patterns as temporal
+ones, to assess the validity of space for time substitution.
 
 # Methods
+
+## Data
 
@@
 
+## Biomass
+
+We first inferred the body mass of each fish individual thanks to an allometric
+law, $B_i = 0.01 \times l_i^3.03$, $B_i$ being biomass in gram and $l_i$ the
+body length in millimetre of the individual $i$ [@froese_cube_2006]. Then the
+biomass of each species and community biomass were obtained by summing the body
+mass of individuals. Finally, the biomass was reported to the sampled surface
+(in $m^2$) to account for sampling effort.
+
 ## Food-web inference
 
-Because we had few informations about trophic interactions between resources, we
-selected only the fish-fish interactions in subsequent analysis.
+We inferred food-web structure in two steps [@bonnaffe_comparison_2021;
+@danet_species_nodate]: (1) we first computed the metaweb, describing the
+potential trophic interactions between all species size classes, (2) then we
+extracted each local food-webs by extracting species size classes and their
+interactions according their presence in a given sampling event.
+
+We inferred food-web structure according to ontogenic diet data and body size
+[@gravel_inferring_2013; @poisot_structure_2016; @brose_predator_2019; @bonnaffe_comparison_2021;
+@danet_species_nodate]. The method is extensively described in
+@bonnaffe_comparison_2021 and @danet_species_nodate. The food diet of stream
+fishes, as many organisms, change along their life and therefore according to
+their body size. Each fish species was divided in nine size classes, named
+trophic species, equally distributed in their observed body size range.
+A trophic species is a group of individuals of the same species and size class
+that are expected to share the same preys and predators. We also added seven
+nodes present in the ontogenic food diet database: detritus, biofilm,
+phytoplankton, zooplankton, macrophages, phytobenthos and zoobenthos. 
+The resulting metaweb contained 45 fish species divided into nine size classes
+plus 7 resource nodes, summing up to 412 nodes.  Consideration of size classes,
+i.e. trophic species instead of species, improves inference of trophic
+interactions [@jennings_weak_2001].
+
+We determined the feeding interactions of trophic species according to their
+species identity and their body size. The diet database described two or
+three life stages by fish species, each one being delimited by body size
+[@bonnaffe_comparison_2021; @danet_species_nodate]. The life stage of a fish
+trophic species was determined by the centre of its body size range, hereafter
+midpoint. The ontogenic fish diet database was filled according to fishbase
+(Froese et al. 2021) and literature [@bonnaffe_comparison_2021;
+@danet_species_nodate].
+
+The feeding interactions between fishes were based on the body size ratio
+between predators and preys. As this, we defined the predation window of a
+piscivorous trophic species as 3% to 45% of its midpoint
+[@mittelbach_ontogeny_1998; @claessen_impact_2002; @hart_handbook_2008].  We set
+a trohic interaction  A trophic link was defined between the piscivorous trophic
+species and all the trophic species whose midpoint in body size range was
+included in the predation window.  The fish-resource trophic links were set
+between the trophic species and the resources nodes according to the food items
+of their size class.  Finally, the feed interactions between resources were
+defined according to the literature [@allan_stream_2007; @hart_handbook_2008].
 
@@
 
-$dN = dB + dR$
+$dN = \alpha + \beta_1dB + \beta_2dR + \beta_3dBdR + \epsilon$
 
@@
 
-The significativity of the effects were tested with ANOVA.  In order to be able
-to compare the magnitude of the effects of community biomass and species
-richness in both temporal and spatial models, we computed standardized slopes
-($r_{\delta}$) and their associated standard errors.
+The significativity of the effects were tested with ANOVA. In order to compare
+the magnitude of the effects of community biomass and species richness in both
+temporal and spatial models, we computed standardized slopes ($r_{\delta}$) and
+their associated standard errors.
 
@@
 community biomass from one side and species richness, average trophic level,
-connectance from the other side (Fig. \@ref(fig:bm), Table \@ref(tab:aov),
+connectance from the other side (Fig. \@ref(fig:bef) and \@ref(fig:bmr), Table \@ref(tab:aov),
 respectively  $r_\delta = `r tps_bm_sest["rich"]`$, $`r tps_bm_sest["tlvl"]`$, 
@@
 ( $r_\delta = `r tps_bm_sest["p_bm"]`$), meaning that the eveness of biomass
-across species
-temporally increased when the community biomass
-temporally decreased and respectively that the evenness of biomass temporally
-decreased when the community biomass temporally increased (Fig. \@ref(fig:bm),
-Table \@ref(tab:aov)). We also found the same pattern between the temporal
-trends of community biomass and that of the pielou of individual number
-($r_\delta = `r tps_bm_sest["p_n"]`$).
+across species temporally increased when the community biomass temporally
+decreased and respectively that the evenness of biomass temporally decreased
+when the community biomass temporally increased (Fig. \@ref(fig:bmr),
+Table \@ref(tab:aov)).
+
+---
+#We also found the same pattern between the temporal
+#trends of community biomass and that of the pielou of individual number
+#($r_\delta = `r tps_bm_sest["p_n"]`$). 
+---
 
@@
 The temporal trends of community biomass and pielou of biomass, had a positive
-relationship with that of species richness (Fig. \@ref(fig:rich), Table
+relationship with that of species richness (Fig. \@ref(fig:bmr), Table
 \@ref(tab:aov), $r_\delta = `r tps_r_sest["p_bm"]`$) while we did not find
 significant relationships between the temporal trends of average trophic level,
-connectance, pielou of individual number and the one of species richness (Fig.
-\@ref(fig:rich), Table \@ref(tab:aov)).
+connectance and the one of species richness (Fig.
+\@ref(fig:bmr), Table \@ref(tab:aov)).
 
@@
 $`r sp_b_sest["tlvl"]`$, Fig.
-\@ref(fig:bm), Table \@ref(tab:aov-sp)) while the pielou of biomass was
+\@ref(fig:bmr), Table \@ref(tab:aov-sp)) while the pielou of biomass was
 negatively related to community biomass ($r_\delta = `r sp_b_sest["p_bm"]`$).
-However, we found no spatial relation between the pielou of individual and
-community biomass.
 
@@
 
-Community biomass, the pielou of biomass and individual were
+Community biomass, the eveness of biomass were
 positively related to species richness (resp. 
@@
 species richness (resp. $r_\delta = `r sp_r_sest["tlvl"]`$, $`r sp_r_sest["ct"]`$,
-Fig. \@ref(fig:rich), Table \@ref(tab:aov-sp)).
+Fig. \@ref(fig:bmr), Table \@ref(tab:aov-sp)).
 
@@
 finding that the evenness of biomass, measured by the pielou, decreased through
-time as community biomass decrease and reversely, meaning that biomass
-distribution across species respectively become respectively less and more even
-when community biomass decrease and increase. We also found that evenness
-decreased temporally of number of individual when community biomass increased
-temporally, confirming that the temporal trends of community biomass in our
-study is linked to big individuals. It further indicates that temporal loss of
-community biomass are linked with the loss of the higher trophic level.
+time as community biomass decreased and reversely, meaning that biomass
+distribution across species become less even when community biomass decrease and
+reversely. It further indicates that temporal loss of community biomass are
+linked with the loss of the higher trophic level.
 
 We also found in space that evenness of biomass was positively related to
-community while eveness of individual number had no relation. It constrasts with
-previous studies which found a negative relationship between biomass and eveness
-of individual in marine and plant communities [@drobner_relation_1998;
-@maureaud_biodiversityecosystem_2019] or studies that found more even plant
-communities in terms of individual number display higher community biomass
-[@wilsey_biodiversity_2000].
+community while eveness of abundances had no relation (Fig. SXX). It
+constrasts with previous studies which found a negative relationship between
+biomass and eveness of abundances in marine and plant communities
+[@drobner_relation_1998; @maureaud_biodiversityecosystem_2019] or studies that
+found more even plant communities in terms of abundances number display higher
+community biomass [@wilsey_biodiversity_2000].
 
@@
 richness and that species loss and gain concerns species of low trophic level,
-which in turn does affect connectance very little. However, the relationship become
-slightly negative for species poor communities. An explanation might be that
-species-rich communities already contains a significant number of piscivores,
-which have the most links whereas species poor communites contains few
-piscivores.
+which in turn does affect connectance very little.
 
@@
 This result has profound implications for conservation. As more and more
-studies report community biomass and richness trends [@hallmann_more_2017;
-@ceballos_biological_2017], it is important to note that they might not be
-equivalent in terms of consequences on the structure of the community. Further,
-studies should investigate the temporal trends of several dimensions of
-community structure simultaneously because it drives many aspects of ecosystem
-functioning.
+studies report community biomass and species richness trends [@hallmann_more_2017;
+@ceballos_biological_2017], we documented that they might not be
+equivalent in terms of consequences on the structure of the community. In
+particular, the loss of the highest trophic level associated to the loss of
+community biomass could of have dramatic consequences on ecosystem functioning
+as highest predators are prone to stabilise communities
+[@shanafelt_stability_2018; danet_species_nodate]. In contrasts, the loss of
+species richness was poorly associated to modification of food-web structure,
+suggesting that the species loss and gain.
 
@@
 
-## Conclusion
+## Conclusion and perspectives
 
@@
 communities relate on different ecological processes, biomass temporal dynamics
-being related to variation of highest trophic level while it is not the case for
+being related to variation of highest trophic levels while it is not the case for
 species richness. Our work also suggests that space for time substitution may be
@@
 # Figures {-}
+
+```{r}
+fig_mat_cap <- paste0(
+  "(A) Distribution of the fishing sites. (B-F) Temporal trends of biomass,
+  species richness, connectance, average trophic level and eveness of biomass
+  for two stations."
+)
+```
+```{r, fig.cap=fig_mat_cap, out.width="100%"}
+knitr::include_graphics(get_mypath("figures", "matmet.png"))
+```
 
@@
 names(p_bm) <- c("ct_ff", "w_trph_lvl_avg", "piel_bm")
-plot_grid(plotlist = p_bm)
+#plot_grid(plotlist = p_bm)
 
@@
 ```
-```{r bmr, fig.height = 12, fig.cap=fig_bm_rich_cap}
+```{r bmr, out.width = "100%", fig.cap=fig_bm_rich_cap}
 fig2 <- fig1_2
 fig2$rich$log_bm_std <- NULL
+fig2$rich <- map(fig2$rich,
+  ~ .x +
+    theme(axis.text = element_text(size = 6),
+    axis.title = element_text(size = 8)))
+fig2$bm <- map(fig2$bm,
+  ~ .x + theme(
+    axis.text = element_text(size = 6),
+    axis.title = element_text(size = 8)
+    )
+)
+
 plot_grid(
-  plot_grid(plotlist = fig2$bm, nrow = 1),
-  plot_grid(plotlist = fig2$rich, nrow = 1),
+  plot_grid(plotlist = fig2$bm, nrow = 1, labels = c("A", "B", "C")),
+  plot_grid(plotlist = fig2$rich, nrow = 1, labels = c("D", "E", "F")),
   nrow = 2
@@
 ```{r}
-loadd(pred_bm_rich_mono_stable_trends, anova_table_bm_rich_mono_stable_trends)
+loadd(pred_bm_rich_mono_stable_trends,
+  model_bm_rich_int_mono_stable_trends,
+  model_bm_rich_int_mono_stable_trends,
+  anova_table_bm_rich_mono_stable_trends)
+
 anova_table_bm_rich_mono_stable_trends %>%

### 2021-08-25 R/plan.R

@@ -19,11 +19,12 @@ plan <- drake_plan(
   com_analysis_data = get_community_analysis_data( path =
     file_in(!!get_mypath("data", "community_analysis.rda")), op = op_data),
   op_data = get_op_data(path = file_in(!!get_mypath("data", "op_analysis.rda"))),
-  habitat_press = get_data(obj_name = "habitat_press", dir = get_mypath("data")),
+ habitat_press = get_data(obj_name = "habitat_press", dir = get_mypath("data")),
   habitat_pressure = get_data(obj_name = "habitat_pressure", dir = get_mypath("data")),
   region_polygon = get_data(obj_name = "region_polygon", dir = get_mypath("data")),
   station_analysis = get_data(obj_name = "station_analysis",
     dir = "~/Documents/post-these/mnhn/fishcom/data"),
+  map_st = get_station_map(st = st_mono_trends_stable_rich_bm),
   net_l_ld_IS = get_l_ld_IS(net = net_analysis_data),
   metrics_fishfish_only = get_network_metric_fish_only(net = net_analysis_data),
   net_data2 = left_join(net_data, net_l_ld_IS, by = "opcod") %>%

### 2021-08-25 make.R

@@ -110,3 +110,6 @@ persp(x = as.numeric(colnames(mat)),
   theta = 60,
   phi = 20,
   col = "green", shade = 0.5)
+
+plot_add_pred_data
+plot_raw_data_new_model

### 2021-08-26 paper/appendix.Rmd
Clean appendix

@@
 
-```{r}
+```{r, echo=FALSE}
 knitr::opts_chunk$set(
@@
 
-```{r, echo = FALSE, message = FALSE, collapse = FALSE}
+```{r, echo=FALSE, message=FALSE, results="hide"}
 library(drake)
@@
 \beginsupplement
+\newpage
 
 # Data exploration
-
-## Maps
 
@@
 ```
-
-## Range of variation
 
@@
   temporal trends in each station. Futhermore, each station was weighted by the
-  average error standard on the temporal trends of the variables.")
+  average error standard on the temporal trends of the variables.",
+  " Pisc: piscivorous, Nb: number, node: node of the food-web corresponding to a
+  trophic species, prop: proportion."
+)
 ```
@@
 
-set_names_corr <- function(mat = NULL) {
-  colnames(mat) <- str_replace_all(colnames(mat), var_replacement())
-  rownames(mat) <- str_replace_all(rownames(mat), var_replacement())
+rv <- var_replacement()
+rv_more <- c(
+  nbnode_std = "Nb node",
+  nb_pisc_rich_std = "Nb pisc species",
+  nb_pisc_node_std = "Nb pisc nodes",
+  prop_pisc_node = "Prop pisc node",
+  prop_pisc_rich = "Prop pisc species"
+)
+
+rv <- c(rv_more, rv[!names(rv) == "rich_std"])
+
+set_names_corr <- function(mat = NULL, replacement_vector = var_replacement()) {
+  colnames(mat) <- str_replace_all(colnames(mat), replacement_vector)
+  rownames(mat) <- str_replace_all(rownames(mat), replacement_vector)
   return(mat)
@@
 
-corr_plot_tps %<>% set_names_corr(.)
-corr_plot_med %<>% set_names_corr(.)
+corr_plot_tps %<>% set_names_corr(., replacement_vector = rv)
+corr_plot_med %<>% set_names_corr(., replacement_vector = rv)
 
-par(mfrow = c(1, 2))
-corrplot::corrplot(corr_plot_med, type = "upper", diag = FALSE, order =
-  "alphabet")
-title("Spatial")
+#par(mfrow = c(1, 2))
+corrplot::corrplot(
+  corr_plot_med,
+  type = "upper",
+  diag = FALSE,
+  order = "alphabet",
+  tl.srt = 30,
+  tl.cex = .7
+)
+title("Spatial", adj = 0, line = 3)
 corrplot::corrplot(corr_plot_tps, type = "upper", diag = FALSE, order =
-  "alphabet")
-title("Temporal trends")
+  "alphabet",
+  tl.srt = 30,
+  tl.cex = .7
+)
+title("Temporal trends", adj = 0, line = 3.2)
 ```
@@
 
-## Temporal model with richness and biomass
+## Sensisivity analysis for the temporal model
 
@@
 
-We modeled the temporal trends of food-web structure as dependant of the
-temporal trends of both species richness and community biomass as:
-
-$dN = dB + dR + \epsilon$
-
-\newpage
-
-```{r sens, out.width="100%"}
+```{r}
+cap_sens_temp_model <- paste0("
+  Testing the robustness of the estimated coefficients to the selection of
+  sites. 'All trends' corresponds to all the sites, 'Only monotonuous trends'
+  corresponds to all the trends negative or positive monotonically, 'Monotonuous
+  + stable' includes the previous selection and the stable ones (the selection
+    used in main text), 'All significant trends' correspond to all the trends
+significantly negative or positive.", " We classified a site as
+  having a significant trend when it displays both significant trends in biomass
+and in species richness."
+)
+```
+```{r sens, out.width="100%", fig.cap=cap_sens_temp_model}
 # Merge reg_table
@@
     name = list(
-      "Only monotonuous trends",
-      "Monotonuous + stable trends",
+      "Only monotonuous",
+      "Monotonuous + stable (used in main text)",
       "All significant trends",
-      "All trends"
+      "All sites"
       ),
@@
   ) +
-  theme(legend.position = "bottom", axis.text.x = element_text(hjust=1, angle = 15))
+  theme(
+    legend.position = "bottom",
+    axis.text.x = element_text(hjust = 1, angle = 15, size = 8),
+    text = element_text(size = 8)) +
+  guides(color = guide_legend(nrow = 2, byrow = TRUE))
 ```
+
+We found that selection of data can have either low or high effects on estimated
+effects. When selecting only the sites that display significant decrease or
+increase of community biomass and species richness across time, i.e. 
+a tenth of the site, we found stronger links among the temporal dynamics of
+average trophic level, connectance, biomass and the temporal dynamics of biomass
+and species richness (Fig. \@ref(fig:sens), purple and red points). On the other
+side, we found that the data selection that we used in the main analysis
+displays roughly the same results that the selection that includes all sites
+(Fig. \@ref(fig:sens), blue and green points).
+
+The fact that we observed differences with data selection is that  "Only
+monotonuous" and "All significant trends" do not contain temporal dynamics
+around 0 because they are often non significant. We think that this data
+selection is not satisfactory because we wanted to include the temporal dynamics
+of biomass of species richness that were not significant, i.e. that can be
+considered as stable. The rational is that we wanted to know what was the
+expected temporal trends of food-web structure while the ones of biomass and
+species richness are kept stable. Without those data, the regression becomes
+constrained only by the extreme temporal trends of species richness and
+community biomass.
+
+\newpage
 
@@
 ```
-
-### ANOVA
 
@@
       everything())) %>%
+  mutate(
+    response = str_replace_all(response, var_replacement()),
+    term = str_replace_all(term, var_replacement())
+  ) %>%
+  rename_all(~str_to_title(.)) %>%
   kable(., booktabs = TRUE,
@@
     paste0(
-      "Regression results with interactions."
+      "Regression results of the model with interactions between the temporal
+      dynamics of community biomass and the one of species richness."
       ),
-    label = "aov-int"
+    label = "reg-int"
     ) %>%
@@
 
-### Plots
-
-```{r}
+```{r, results="hide", echo=FALSE}
 pred_int_rich <- map(model_bm_rich_int_mono_stable_trends,
@@
 ti <- pred_bm_rich_mono_stable_trends %>%
-  filter(term == "log_rich_std", response %in% c("ct_ff", "w_trph_lvl_avg", "piel_bm")) %>%
+  filter(
+    term == "log_rich_std",
+    response %in% c("ct_ff", "w_trph_lvl_avg", "piel_bm")
+    ) %>%
   select(response, raw_plot) %>%
@@
       list(raw_plot, response, pred_int),
-      function(p, resp, pred) {
+      function(p, resp, pred, ...) {
         p +
@@
           ) +
-        scale_color_discrete()
+        scale_color_discrete() +
+        labs(x = "Log species richness",
+          y = var_replacement()[resp],
+          color = "Log community biomass"
+          ) +
+        theme(
+          text = element_text(size = 8),
+          axis.text = element_text(size = 8)
+        )
       }
@@
 rich_leg <- get_legend(ti$pred_plot_color[[1]])
+```
 
-plot_grid(plotlist = map(ti$pred_plot_color, ~.x + theme(legend.position = "none")), rich_leg)
+```{r}
+int_rich_cap <- paste0(
+  "Relationships between the temporal dynamics of food-web
+  structure and the one of species richness. The interaction between
+  the temporal dynamic of species richness and community biomass is significant
+  for the three descriptors of food-web structure. The chosen values for the
+  community biomass temporal dynamic correspond respectively to the first,
+  second and third quartiles.
+  ")
+
+```
+
+```{r int-rich, fig.cap=int_rich_cap}
+plot_grid(plotlist = 
+  map(ti$pred_plot_color,
+    ~.x + theme(
+      legend.position = "none",
+    )
+    ),
+rich_leg)
 ```
@@
 
-```{r}
+```{r, results="hide", echo=FALSE}
 pred_int_bm <- map(model_bm_rich_int_mono_stable_trends,
@@
           ) +
-        scale_color_discrete()
+        scale_color_discrete() +
+                labs(x = "Log species richness",
+          y = var_replacement()[resp],
+          color = "Log community biomass"
+          ) +
+        theme(
+          text = element_text(size = 8),
+          axis.text = element_text(size = 8)
+        )
+
       }
@@
   )
+bm_leg <- get_legend(ti_bm$pred_plot_color[[1]])
+```
 
-bm_leg <- get_legend(ti_bm$pred_plot_color[[1]])
+```{r}
+int_bm_cap <- paste0(
+  "Relationships between the temporal dynamics of food-web
+  structure and the one of community biomass. The interaction between
+  the temporal dynamics of species richness and community biomass is significant
+  for the three descriptors of food-web structure. The chosen values for the
+  species richness temporal dynamic correspond respectively to the first,
+  second and third quartiles.
+  "
+)
+```
+
+```{r int-bm, fig.cap=int_bm_cap}
 plot_grid(plotlist = map(ti_bm$pred_plot_color, ~.x + theme(legend.position = "none")), bm_leg)
@@
 
-```{r, echo=FALSE, eval=FALSE}
+```{r, echo=FALSE, results="hide"}
 test <- model_bm_rich_int_mono_stable_trends[["ct_ff"]]
@@
 
-```{r, result=FALSE}
+```{r, results=FALSE}
 mod4_3d <- model_bm_rich_int_mono_stable_trends[
@@
 
-```{r,result=FALSE}
+```{r,results=FALSE}
 mat <- reshape2::acast(
@@
 
-```{r,result=FALSE, eval=FALSE}
+```{r,results=FALSE, eval=FALSE}
 test <- model_bm_rich_int_mono_stable_trends[["piel_bm"]]
@@
 ```{r}
+int_3d_cap <- paste0(
+  "Tri-dimentional plot displaying the relationships among food-web structure
+  from one side and the temporal dynamics of species richness and community
+  biomass from the other side. The surface represents the values predicted by
+  the model."
+)
+```
+
+```{r int-3d, fig.cap=int_3d_cap}
 p_ct_ff <- ggdraw() +
@@
   p_tlvl,
-  p_piel_bm
+  p_piel_bm,
+  labels = "AUTO"
 )
 ```
+
+All together, we found that interactions between the temporal dynamics of
+community biomass and species richness have no major effects on the bivariate
+relationships (Fig. \@ref(fig:int-bm) and \@ref(fig:int-rich)), at least in
+the range of values observed in the dataset (1st to 3rd quartiles).  It is more
+complicated for connectance when exploring the full range of possible values
+(Fig. \@ref(fig:int-3d) A). We found that connectance strongly decrease with
+increasing of community biomass temporal trends when species richness temporal
+trends is strongly negative, while we found the opposite when species richness temporal
+trends is strongly positive. Furthermore we found that the temporal dynamic of
+connectance had a strong positive relationship with the one of species richness
+when community biomass increases through time while we found no relationship
+when the temporal trend of community biomass was strongly negative.
 
@@
     - Always negative when biomass increases 
+    - Whatever the richness dynamics, it is the biomass dynamics which drives
+      all
 

### 2021-10-12 paper/manuscript.Rmd
Update introduction and results

@@
 ---
-title: "Biomass and species richness temporal trends drives the assembly and the disassembly of food-web in natural fish assemblages"
-author: Alain Danet, Maud Mouchet, Loubna El Madouri, Elisa Thébault and Colin Fontaine (ordre non fixé)
+title: "Species richness and biomass temporal trends reveals different assembly processes of food-web in natural fish assemblages " 
+author: Alain Danet, Loubna El Madouri, Maud Mouchet, Elisa Thébault and Colin Fontaine (ordre non fixé)
 date: \today 
@@
     toc: true
-  bookdown::word_document:
+  bookdown::word_document2:
 fontsize: 12pt
@@
 
-- TODO:
-  - [ ] RM Pielou of abundances
-  - [ ] Interaction tables 
-  - [ ] Interaction plots
-
 # Introduction
 
-## community structure is dynamic and affect ecosystem functions
+## Trends of biodiversity needs to be assessed for multiple facets
 
-Biodiversity affects ecosystem properties such as total biomass, productivity
-and stability [@tilman_biodiversity_2014; @loreau_biodiversity_2001]. However,
-current biodiversity is at risk, numerous studies reported dramatic declines of
-population and community biomass [@ceballos_biological_2017;
-@hallmann_more_2017; @albano_native_2021], as well as decrease in species
-richness [@barnosky_has_2011; @newbold_global_2015]. Whereas numerous
-ecological studies have shown that the different aspects of community structure
-are tightly linked [@thebault_food-web_2003; @dunne_network_2006;
-@soininen_relationship_2012], the consequences of temporal variations of community
-biomass and species richness on community structure are not well-known.
-
-## Variations of community biomass and species richness are predicted to affect community structure
-
-Changes of species richness and community biomass are indeed
-predicted to affect community structure. The positive link between biodiversity
-and ecosystem functioning in experimental studies predict that loss and
-gain of species richness should respectively result in loss and gain of
-community biomass [@tilman_biodiversity_2014; @pennekamp_biodiversity_2018]. But
-this relation is not always found in natural settings [@grace_integrative_2016;
-@li_relationship_2018; @maureaud_biodiversityecosystem_2019].
-
-Variations of species richness can also result in variation of evenness, i.e.
-equitability of species abundances or biomasses. Several studies shows that
-higher evenness of abundances is linked to higher plant biomass in grasslands
-and primary productivity in marine ecosystems [@soininen_relationship_2012].
-Furthermore, studies reported that higher evenness plays a role of insurance in
-face of perturbations [@wittebolle_initial_2009]. Indeed, most studies reported
-positive relationship between species richness and evenness, but also neutral
-and negative ones [@soininen_relationship_2012; @ma_species_2005;
-@maureaud_biodiversityecosystem_2019].
-
-## Variations of community biomass and species richness are predicted to affect food-web structure
-
-The distribution and the number of ecological interactions, i.e. the structure
-of ecological networks, also covaries with species richness and community
-biomass. In food-webs, connectance, which measures the degree of generalism in a
-network, has been theoretically shown to positively scale with community biomass
-[@thebault_food-web_2003].  Connectance has been also shown to be negatively
-related to species richness in empirical food-webs [@dunne_network_2006].
-Trophic level has also been shown to be positively linked to total biomass in
-theoretical models [@wang_biodiversity_2018].
-
-The different dimensions of network and community structure are closely linked
-but, we have no direct evidence on how they covary according to the
-loss or gain of species richness and community biomass across time.
+Multiple studies reported dramatic declines of population and community biomass
+[@ceballos_biological_2017; @hallmann_more_2017; @albano_native_2021], as well
+as decrease in species richness [@barnosky_has_2011; @newbold_global_2015] and
+turnover in species composition [@comte_climate_2021]. The documentation of
+biodiversity temporal trends, is crucial to evaluate the effect of
+global changes [but see @cardinale_is_2018]. Unfortunately, studies often
+report trends of one dimension of biodiversity at a time [@hallmann_more_2017,
+etc, but see @]. Because the functioning of ecosystem depends ultimately on
+multiple facets of biodiversity, such as species richness, evenness and
+functional composition [REF @thibaut_understanding_2013], the monitoring of one
+biodiversity trend is not enough to project potential effects on ecosystem
+functioning.
 
@@
 
-The links between the different component of community structure often come from
-spatial gradient comparison. The space for time substitution allows to use the
-studies mentioned above to predict how changes in species richness or community
-biomass will in turn affect community and network structure. The hypothesis that
-space can surrogate space is often implicitly made in ecological studies. This
-method began to be widely used in the early 20th century to infer the temporal
-succession of vegetation from space variations [@pickett_space-for-time_1989].
-It supposes a homology between variations in space and in time i.e. that spatial
-sequences corresponds to temporal sequences. This method have raised criticisms
+Another concern is that the links between the different components of community
+structure often come from spatial comparison [@dunne_network_2006;
+@soininen_relationship_2012; @grace_integrative_2016 @danet_species_nodate]. In
+order to use spatial comparison to predict the fate of communities facing
+changes in species richness or community biomass, studies often implicitly use
+the "space for time substitution" hypothesis. This method began to be widely
+used in the early 20th century to infer the temporal succession of vegetation
+from space variations [@pickett_space-for-time_1989]. It supposes a homology
+between variations in space and in time i.e. that spatial sequences correspond
+to temporal sequences.  This method have raised criticisms
 [@damgaard_critique_2019], with studies showing analogous patterns in space and
@@
 
-In this line, how community biomass and species richness temporal trends are
-linked to temporal changes in food-web structure is still an open question, as
-well as if space for time substitution works to infer consequences of species
-richness and community biomass on food-web structure. The increasing
-availability of ecological temporal series makes possible to assess those
-questions.
+## Temporal variation of food-webs is largely unknown
 
-Using a standardized monitoring of fish freshwater communities on the period
-1995-2018, we assessed the relationships among temporal trends of food-web
-structure, trends of community biomass and trends in species richness. We
-then assessed if spatial relationships display the same patterns as temporal
-ones, to assess the validity of space for time substitution.
+The documentation of biodiversity trends generally neglect species interactions
+although they are fundamentals to ecosystem functioning
+[@thebault_food-web_2003; oconnor_general_2016]. In food-webs, empirical and
+theoretical studies reported generally that trophic level positively scales to
+community biomass [@wang_biodiversity_2018; @danet_species_nodate] (add
+mechanisms ?). Trophic level has also been shown to stabilise the temporal
+variation of community biomass [@shanafelt_stability_2018;
+@danet_species_nodate]. Connectance, which measures the degree of generalism in
+a network, was shown to increase robustness to extinction [@dunne_network_2002].
+However, the temporal variation of food-web structure is largely unknown
+[@kortsch_disentangling_2021]. Food-web temporal variation are often reported
+across small time step [warren_spatial_1969; @pecuchet_species_2020;
+@kaartinen_high_2012].
+
+We know very little how food-web structure vary across time and particularly how
+those variations are linked to the variations of other aspects of community
+structure such as species richness and community biomass. Spatially, connectance
+has been shown to be negatively related to species richness in empirical
+food-webs [reviewed in @dunne_network_2006]. Connectance has been shown to scale
+positively or negatively with community biomass in theoretical models
+[@thebault_food-web_2003; @poisot_trophic_2013] (*Add mechanism?*). In order to
+improve our understanding on the assembly mechanisms in food-webs, it is thus
+crucial to assess how biomass and species richness variation are associated to
+variations in food-web structure.
+
+In this line, how the temporal changes of community biomasse are related to
+temporal changes of species richness can still be question in natural settings,
+especially in food-webs. Our knowledge on how the temporal changes of food-web
+structure are related  to temporal changes in community biomass and species
+richness is almost zero. Our knowledge on the relationships between food-web
+structure comes often from comparison of food-web snapshots along spatial
+gradient, raising the question of the validity of space for time substitution to
+infer consequences of species richness and community biomass on food-web
+structure. The increasing amount of availability ecological temporal series
+makes possible to assess those questions. Using a standardized monitoring of
+fish freshwater communities on the period 1995-2018 and a method of food-web
+inference based on allometric relationships and food diet datas, we assessed the
+relationships among temporal changes of food-web structure, trends of community
+biomass and trends in species richness. We then assessed the validity of space
+for time substitution by comparing if temporal relationships display the same
+patterns than relationships obtained along spatial gradient.
+
+---
+## Variations of community biomass and species richness are predicted to affect community structure
+#Changes of species richness and community biomass are indeed
+#predicted to affect community structure. The positive link between biodiversity
+#and ecosystem functioning in experimental studies predict that loss and
+#gain of species richness should respectively result in loss and gain of
+#community biomass [@tilman_biodiversity_2014; @pennekamp_biodiversity_2018]. But
+#this relation is not always found in natural settings [@grace_integrative_2016;
+#@li_relationship_2018; @maureaud_biodiversityecosystem_2019].
+#
+#Variations of species richness can also result in variation of evenness, i.e.
+#equitability of species abundances or biomasses. Meta-analysis reported that
+#higher evenness of abundances is linked to higher plant biomass in grasslands
+#and primary productivity in marine ecosystems [@soininen_relationship_2012].
+#Furthermore, studies reported that higher evenness plays a role of insurance in
+#face of perturbations [@wittebolle_initial_2009]. Indeed, most studies reported
+#positive relationship between species richness and evenness, but also neutral
+#and negative ones [@soininen_relationship_2012; @ma_species_2005;
+#@maureaud_biodiversityecosystem_2019].
+## Variations of community biomass and species richness are predicted to affect food-web structure
+---
 
@@
 potential trophic interactions between all species size classes, (2) then we
-extracted each local food-webs by extracting species size classes and their
-interactions according their presence in a given sampling event.
+extracted each local time snapshot of food-webs by extracting species size
+classes and their interactions according their presence in a given sampling
+event.
 
 We inferred food-web structure according to ontogenic diet data and body size
-[@gravel_inferring_2013; @poisot_structure_2016; @brose_predator_2019; @bonnaffe_comparison_2021;
-@danet_species_nodate]. The method is extensively described in
-@bonnaffe_comparison_2021 and @danet_species_nodate. The food diet of stream
-fishes, as many organisms, change along their life and therefore according to
-their body size. Each fish species was divided in nine size classes, named
-trophic species, equally distributed in their observed body size range.
-A trophic species is a group of individuals of the same species and size class
-that are expected to share the same preys and predators. We also added seven
-nodes present in the ontogenic food diet database: detritus, biofilm,
-phytoplankton, zooplankton, macrophages, phytobenthos and zoobenthos. 
-The resulting metaweb contained 45 fish species divided into nine size classes
-plus 7 resource nodes, summing up to 412 nodes.  Consideration of size classes,
-i.e. trophic species instead of species, improves inference of trophic
-interactions [@jennings_weak_2001].
+[@gravel_inferring_2013; @poisot_structure_2016; @brose_predator_2019;
+@bonnaffe_comparison_2021; @danet_species_nodate]. The method is extensively
+described in @bonnaffe_comparison_2021 and @danet_species_nodate. The food diet
+of stream fishes, as many organisms, change along their life and therefore
+according to their body size. Each fish species was divided in nine size
+classes, named trophic species, equally distributed in their observed body size
+range.  A trophic species is a group of individuals of the same species and size
+class that are expected to share the same preys and predators. We also added
+seven nodes present in the ontogenic food diet database: detritus, biofilm,
+phytoplankton, zooplankton, macrophages, phytobenthos and zoobenthos.  The
+resulting metaweb contained 45 fish species divided into nine size classes plus
+7 resource nodes, summing up to 412 nodes.  Consideration of size classes, i.e.
+trophic species instead of species, improves inference of trophic interactions
+[@jennings_weak_2001].
 
@@
 piscivorous trophic species as 3% to 45% of its midpoint
-[@mittelbach_ontogeny_1998; @claessen_impact_2002; @hart_handbook_2008].  We set
-a trohic interaction  A trophic link was defined between the piscivorous trophic
-species and all the trophic species whose midpoint in body size range was
-included in the predation window.  The fish-resource trophic links were set
-between the trophic species and the resources nodes according to the food items
-of their size class.  Finally, the feed interactions between resources were
-defined according to the literature [@allan_stream_2007; @hart_handbook_2008].
+[@mittelbach_ontogeny_1998; @claessen_impact_2002; @hart_handbook_2008].  A
+trophic link was defined between the piscivorous trophic species and all the
+trophic species whose midpoint in body size range was included in the predation
+window.  The fish-resource trophic links were set between the trophic species
+and the resources nodes according to the food items of their size class.
+Finally, the feed interactions between resources were defined according to the
+literature [@allan_stream_2007; @hart_handbook_2008].
 
@@
 
-We characterized food-webs by its connectance, describing the degree of
-generalism in a network [@dunne_network_2006; @delmas_analysing_2019]. It is
+We characterized food-webs by their connectance, describing the degree of
+generalism in a network [@dunne_network_2006; @delmas_analysing_2019]. It was 
 computed as the ratio between the actual number of links and the number of
@@
 weighted by the biomass of the trophic species. The trophic level of a trophic
-species is computed recursively as 1 added to the mean trophic level of the
+species was computed recursively as 1 added to the mean trophic level of the
 preys that it consumes.
@@
 assess both the direction and the monotony of temporal trends
-[@rigal_method_2020]. To avoid complex variations of biomass and species
-richness, we selected the stations that displayed monotonic trends for these
-variables, i.e. the ones for which the second order polynomial term was non
-significant. Over the `r nb_st` stations, the selection procedure resulted in 
-`r nb_st_rich_bm` for community biomass and species richness analysis.
+[@rigal_method_2020]. To avoid the inclusion of many types of biomass and species
+richness trends (i.e. accelerating, decelerating, etc...), we selected the
+stations that displayed monotonic trends for these variables, i.e. the ones for
+which the second order polynomial term was non significant. Over the `r nb_st`
+stations, the selection procedure resulted in `r nb_st_rich_bm` for community
+biomass and species richness analysis. However, the results were robust to the
+inclusion of non monotonic trends (Fig. SXX).
 
@@
 temporal dynamics. Communities that displayed low community biomass at the
-beginning of their monitoring tend to display increase in biomass through time
-and reversely. There same the same pattern for species richness, with
+beginning of their monitoring tend to display an biomass increase through time
+and reversely. We observed the same pattern for species richness, with
 communities that displayed high species richness at the beginning of their
-monitoring tend to display decrease in species richness through time and
+monitoring tend to display a decrease in species richness through time and
 reversely.
@@
 
-With the aim to test the relationship among the temporal dynamics of network
+We modelled the dynamics the temporal trends of food-web structure ($dN$)
+in function of the temporal trends of community biomass ($dB$) and species
+richness ($dR$) in order to to test the relationship among the temporal dynamics of network
 structure from one side and species richness and community biomass from another
-side, we modelled the dynamics the temporal trends of food-web structure ($dN$)
-in function of the temporal trends of community biomass ($dB$) and species
-richness ($dR$).
+side.
 
-$dN = \alpha + \beta_1dB + \beta_2dR + \beta_3dBdR + \epsilon$
+$dN = \alpha + \beta_1dB + \beta_2dR + \epsilon$
 
@@
 estimated trends, i.e. slopes for the response and the explicative
-variables.
+variables. We also tested a statistical model taking in account the interaction
+between the temporal trends of species richness and community biomass (i.e.
+adding $\beta_3dBdR$), the
+results are presented in supplementary material (Fig. SXX).
 
@@
 
-$N =  B + R + E_1 + E_2$
+$N = \alpha + \beta_1B + \beta_2R + \beta_3E_1 + \beta_4E_2 + \epsilon$
 
@@
 loadd(rsq_table_bm_rich_mono_stable_trends, sp_rsq_table_bm_rich_mono_stable_trends)
+
+loadd(rigal_classification)
+```
+
+```{r}
+class_trends_bm_rich <- rigal_classification %>%
+  filter(variable %in% c("log_bm_std", "log_rich_std")) %>%
+  unnest(classif) %>%
+  select(variable, station, direction, acceleration, shape_class) 
+res_trends <- class_trends_bm_rich %>%
+  filter(acceleration == "constant") %>%
+  group_by(variable, direction) %>%
+  summarise(n = n()) %>%
+  group_by(variable) %>%
+  mutate(total = sum(n), percent = n / sum(n) * 100 %>% round(., 2))
 ```
@@
 biomass and species richness spanning from $R_{adj}^2= `r rsq_piel_nind`$ for
-pielou of individual number to $R_{adj}^2= `r rsq_tlvl`$ for average trophic
+the evenness of abundances to $R_{adj}^2= `r rsq_tlvl`$ for average trophic
 level (Table \@ref(tab:rsq)). The spatial models were more performant, with
 $R_{cond}^2$ varing from $`r rsq_tlvl_sp`$ to $`r rsq_piel_bm_sp`$ (Table
-\@ref(tab:rsq-sp)).
+\@ref(tab:rsq-sp)). Over the station in the dataset, we found that
+`r res_trends[res_trends$variable == "log_bm_std", ]$total` stations displayed monotonic trends for biomass. Among them, 
+`r res_trends[res_trends$variable == "log_bm_std" & res_trends$direction == "stable", ]$percent`%
+were classified stable,
+`r res_trends[res_trends$variable == "log_bm_std" & res_trends$direction == "decrease", ]$percent`%
+decreasing,
+`r res_trends[res_trends$variable == "log_bm_std" & res_trends$direction == "increase", ]$percent`%
+increasing. Regarding the species richness, we found that
+`r res_trends[res_trends$variable == "log_rich_std", ]$total` stations displayed monotonic trends.
+`r res_trends[res_trends$variable == "log_rich_std" & res_trends$direction == "stable", ]$percent`%
+were classified stable,  
+`r res_trends[res_trends$variable == "log_rich_std" & res_trends$direction == "decrease", ]$percent`%
+as decreasing, and 
+`r res_trends[res_trends$variable == "log_rich_std" & res_trends$direction == "increasing", ]$percent`% increasing.
 
@@
 ## Relationships between temporal trends
-
-### Community structure and community biomass
 
@@
 ```
-We found a significant positive relationship between the temporal trends of
-community biomass from one side and species richness, average trophic level,
-connectance from the other side (Fig. \@ref(fig:bef) and \@ref(fig:bmr), Table \@ref(tab:aov),
-respectively  $r_\delta = `r tps_bm_sest["rich"]`$, $`r tps_bm_sest["tlvl"]`$, 
-$`r tps_bm_sest["ct"]`$), meaning that they temporally increased when the community
-biomass temporally increased and respectively that they temporally decreased
-when the community biomass decreased in time.
-
-We found a significant negative relationship between the temporal trends of
-community biomass and that of the pielou of biomass 
-( $r_\delta = `r tps_bm_sest["p_bm"]`$), meaning that the eveness of biomass
-across species temporally increased when the community biomass temporally
-decreased and respectively that the evenness of biomass temporally decreased
-when the community biomass temporally increased (Fig. \@ref(fig:bmr),
-Table \@ref(tab:aov)).
-
----
-#We also found the same pattern between the temporal
-#trends of community biomass and that of the pielou of individual number
-#($r_\delta = `r tps_bm_sest["p_n"]`$). 
----
-
----
-#Overall, we did not find effect of assembly/disassembly on the relationships
-#between the temporal trends of community structure and the one of community
-#biomass. We also found that the median community biomass had no effect on the
-#relationship between the temporal trends of community structure and the one of community
-#biomass.
----
-
-### Community structure and species richness
 
@@
 ```
-
-The temporal trends of community biomass and pielou of biomass, had a positive
-relationship with that of species richness (Fig. \@ref(fig:bmr), Table
-\@ref(tab:aov), $r_\delta = `r tps_r_sest["p_bm"]`$) while we did not find
-significant relationships between the temporal trends of average trophic level,
-connectance and the one of species richness (Fig.
-\@ref(fig:bmr), Table \@ref(tab:aov)).
-
----
-#We also found that the relationship between the temporal trends of pielou of
-#individual and connectance and that of species richness was dependant of the
-#overall species richness of the community (Fig. \@ref(fig:rich), Table
-#\@ref(tab:aov)), meaning that the relationship between temporal trends of
-#pielou of individual and that of species richness was more positive as the
-#community contained more species (Fig. \@ref(fig:rich), Table
-#\@ref(tab:reg)). While the relationship between temporal trends of pielou
-#of individual and that of species richness was more negative as the community
-#contained more species (Fig. \@ref(fig:rich), Table \@ref(tab:reg)).
----
-
-## Spatial relationships
 
@@
 
-### Community structure and community biomass
+We found a strong positive relationship between the temporal trends of community
+biomass and the one of species richness ($r_\delta = `r tps_r_sest["p_bm"]`$,
+Fig. \@ref(fig:bef), Table \@ref(tab:aov)), meaning that both temporal trends
+had the same direction in average. At stations
+where species richness decreased over time, community biomass also decreased
+over time. On the other hand, at stations where species richness increased over
+time, community biomass also increased over time. In spatial analysis, we also
+found a positive relationship between median community biomass and median
+species richness, but twice less strong than the temporal one
+($r_\delta = `r sp_b_sest["rich"]`$).
 
-We found that species richness, connectance, average trophic level were
-spatially positively related to community biomass (resp. 
-$r_\delta = `r sp_b_sest["rich"]`$, $`r sp_b_sest["ct"]`$, 
-$`r sp_b_sest["tlvl"]`$, Fig.
-\@ref(fig:bmr), Table \@ref(tab:aov-sp)) while the pielou of biomass was
-negatively related to community biomass ($r_\delta = `r sp_b_sest["p_bm"]`$).
+The temporal trends of connectance was positively linked with the one of
+community biomass ($r_\delta = `r tps_bm_sest["ct"]`$), meaning also that both
+temporal trends had the same direction in average. That is, the stations where
+food-web connectance decreased over time had also community biomass that
+decreased over time and reversely. It means that communities that lose biomass
+over time, also loses generalist predators and reversely that communities
+gaining biomass over time also gain generalist predators. Spatially, we found
+also a positive relationship between median connectance and median species
+richness ($r_\delta = `r sp_b_sest["ct"]`$). However, we did not observed
+significant relationships between the temporal trends of connectance and the one
+of species richness (Fig. \@ref(fig:bmr)D) when we found spatially a stong
+negative relationship between median connectance and median species richness
+($r_\delta = `r sp_r_sest["ct"]`$, Fig. \@ref(fig:std)).
 
-### Community structure and species richness
+We found that the temporal trends of average trophic level had a strong positive
+relationship with the one of community biomass 
+($r_\delta = `r tps_bm_sest["tlvl"]`$, Fig. \@ref(fig:bmr)B, Table
+\@ref(tab:aov)), meaning
+that stations where community biomass decreased over time, average trophic level
+decreased over time and vice versa. It means that in communities losing biomass
+over time, the average biomass of the food-web moved toward lower trophic level
+and vice versa. The spatial gradient also showed a positive relationship between
+median average trophic level and median community biomass, but twice less strong
+than the temporal one ($r_\delta = `r sp_b_sest["tlvl"]`$, Fig. \@ref(fig:std),
+Table \@ref(tab:aov-sp)). As for connectance, the temporal trends of average
+trophic level was unrelated to the one of species richness. It means in
+communities either losing or gaining species richness over time, the location of
+average biomass along   trophic level did not significantly change.  However, we
+found a strong negative relationship along the spatial gradient 
+($r_\delta = `r sp_r_sest["tlvl"]`$, Fig. \@ref(fig:std), Table
+\@ref(tab:aov-sp)).
 
-Community biomass, the eveness of biomass were
-positively related to species richness (resp. 
-$r_\delta = `r sp_r_sest["bm"]`$, $`r sp_r_sest["p_bm"]`$,
-$`r sp_r_sest["p_n"]`$) while average
-trophic level and connectance were negatively related to
-species richness (resp. $r_\delta = `r sp_r_sest["tlvl"]`$, $`r sp_r_sest["ct"]`$,
-Fig. \@ref(fig:bmr), Table \@ref(tab:aov-sp)).
+Evenness of species biomass was negatively linked to community
+biomass in time and along the spatial gradient 
+($r_\delta = `r tps_bm_sest["p_bm"]`$ and $`r sp_b_sest["p_bm"]`$ resp.; Fig.
+\@ref(fig:bmr)C, Fig. \@ref(fig:std)). In time, it means that food-webs that
+lost biomass over time also had biomass more evenly distributed by species over
+time and vice versa. A similar reasoning applies to spatial gradient. On the
+other hand, we found a positive relationship between the temporal trends of
+biomass evenness and the one of species richness (Fig. \@ref(fig:bmr)F, Table
+\@ref(tab:aov), $r_\delta = `r tps_r_sest["p_bm"]`$). We found the same
+relationship along the spatial gradient, twice strong however 
+($r_\delta = `r sp_r_sest["p_bm"]`$).
 
 # Discussion
+
+## BEF works in space and time
+
+Spatially and temporally, species richness scaled positively with
+community biomass. Spatially, this result is in accordance with numerous studies was
+already found in streams [@woods_testing_2020; @danet_species_nodate] but also
+in grasslands, salt marches and forests [@hector_plant_1999;
+@tilman_biodiversity_2014; @wu_relationship_2015; @li_relationship_2018; but see
+@grace_integrative_2016]. Therefore, our results confirm that BEF prediction
+works also in time. The positive relationship of species richness on total
+biomass might be due to resource use complementarity [@carey_determining_2011],
+which is held by niche differentiation [@loreau_biodiversity_1998;
+@loreau_partitioning_2001] or to the higher probability of getting high biomass
+species with higher species richness [@loreau_biodiversity_2001].
 
@@
 We found that the temporal increase of the average trophic level was positively
-linked to increase of community biomass in line with a previous model suggesting
-that the presence of higher predator can lead to higher community biomass
-[@wang_biodiversity_2018]. Increase of average trophic level can be associated
-to either gain of biomass in the highest trophic level nor losses of biomass in
-the lowest trophic. In our case, such gain or losses of average trophic level is
-probably associated to the variations of the presence of large fishes. The
-finding that the evenness of biomass, measured by the pielou, decreased through
-time as community biomass decreased and reversely, meaning that biomass
-distribution across species become less even when community biomass decrease and
-reversely. It further indicates that temporal loss of community biomass are
-linked with the loss of the higher trophic level.
+linked to increase of community biomass in line with previous studies suggesting
+that the presence of higher predators can lead to higher community biomass
+[@wang_biodiversity_2018; @danet_species_nodate]. Increase of average trophic
+level can be associated to either gain of biomass in the highest trophic level
+or losses of biomass in the lowest trophic. In our case, such gain or losses of
+average trophic level is probably associated to the variations of the presence
+of large fishes. The finding that the evenness of biomass, measured by the
+pielou, decreased through time as community biomass increased and reversely,
+meaning that biomass distribution across species become more even when community
+biomass decreased and reversely that biomass distribution across species become
+less even when community biomass increased. In the same line, the temporal
+trends of community biomass were positively correlated to the temporal trends of
+the proportion of piscivorous species and trophic species in the community (Fig.
+SXX).
 
 We also found in space that evenness of biomass was positively related to
-community while eveness of abundances had no relation (Fig. SXX). It
+community biomass while evenness of abundances had no relation (Fig. SXX). It
 constrasts with previous studies which found a negative relationship between
-biomass and eveness of abundances in marine and plant communities
+biomass and evenness of abundances in marine and plant communities
 [@drobner_relation_1998; @maureaud_biodiversityecosystem_2019] or studies that
@@
 increases with the size of the fishes. This result is also in accordance with  
-theoretical work showing that higher food-web connectance result in higher
-community biomass [@thebault_food-web_2003].
+theoretical work showing that  higher food-web connectance can result in higher
+community biomass [@thebault_food-web_2003]. But it contrasts with previous
+results [@poisot_trophic_2013; @danet_species_nodate], highlighting that the
+relation between connectance and community biomass may be dependant of assembly
+processes at work.
 
@@
 
-To the difference with community biomass, the temporal trends of eveness of
-biomass was positively related to the temporal trends of species
+In contrasts to the results for the community biomass, the temporal trends of
+evenness of biomass was positively related to the temporal trends of species
 richness, meaning that as species richness temporally increase, the
-distribution of biomass become more even, while temporal trends of eveness of
-individual had no significant relationship with species richness. Those results
-indicate that biomass trends are linked to few big individuals while richness
-trends are linked to overall shift in dominance in communities.
+distribution of biomass become more even, while temporal trends of evenness of
+abondances had no significant relationship with species richness (Fig. SXX).
+Those results seem indicate that biomass trends are linked to few big individuals
+while richness trends are linked to overall shift in dominance in communities.
 
@@
 [@dunne_network_2006] and also in the present study. This result suggests that
-the structure of food-webs might be not very sensitive to variation of species
+the structure of food-webs might not be very sensitive to variation of species
 richness and that species loss and gain concerns species of low trophic level,
-which in turn does affect connectance very little.
-
-## Temporal dynamics confirms space for time substitution BEF
-
-Spatially and temporally, the species richness was positively linked to that of
-community biomass. Spatially, this result is in accordance with numerous studies was
-already found in streams [@woods_testing_2020; @danet_species_nodate] but also
-in grasslands, salt marches and forests [@hector_plant_1999;
-@tilman_biodiversity_2014; @wu_relationship_2015; @li_relationship_2018; but see
-@grace_integrative_2016]. Therefore, our results confirm that BEF prediction
-works also in time. The positive relationship of species richness on total
-biomass might be due to resource use complementarity [@carey_determining_2011],
-which is held by niche differentiation [@loreau_biodiversity_1998;
-@loreau_partitioning_2001] or to the higher probability of getting high biomass
-species with higher species richness [@loreau_biodiversity_2001].
+which in turn affect connectance very little. Remarkably, temporal
+variations of community biomass and the ones of species richness seem to be
+linked to high trophic level in the first while being linked to lower trophic
+level in the second. Those results highlight that variations in community
+biomass and species richness are linked to different assembly processes and/or
+pressures, but it is still an open question.
 
@@
 In contrast with a meta-analysis [@soininen_relationship_2012], we found that
-the eveness of individual number is positively related to the one of species
+the evenness of abundances is positively related to the one of species
 richness in space in stream fish assemblages but found no relationship in time.
@@
 species richness was poorly associated to modification of food-web structure,
-suggesting that the species loss and gain.
+suggesting that the species loss and gain concern lower trophic levels, which
+are also in transmitting energy toward higher level of the trophic chain.
 
@@
   "(A) Distribution of the fishing sites. (B-F) Temporal trends of biomass,
-  species richness, connectance, average trophic level and eveness of biomass
-  for two stations."
+  species richness, connectance, average trophic level and evenness of biomass
+  for two stations. (À retravailler)"
 )
@@
 ```{r, fig.cap=fig_mat_cap, out.width="100%"}
-knitr::include_graphics(get_mypath("figures", "matmet.png"))
+knitr::include_graphics(get_mypath("figures", "mat_met_inkscape.pdf"))
 ```

### 2021-10-12 paper/method_figure.Rmd
Update introduction and results

--- 2021-07-16 draft.Rmd
@@
 source(mypath("R", "misc.R"))
+source(mypath("R", "variable_shortcut.R"))
 source_dir(mypath("R"))
@@
 ```{r}
+myload(metaweb_analysis, dir = get_mypath("data"), envir = environment())
+
+my_species_color <- set_color_species(
+  node_list = colnames(metaweb_analysis$metaweb),
+  resource_list = metaweb_analysis$resource,
+  col_resource = NULL
+)
+```
+
+```{r}
 loadd(rigal_classification, com_data, op_data)
@@
 save_plot(
-  "figures/decreasing_biomass_network.png", g,
+  get_mypath("figures/decreasing_biomass_network.png"),
+  g,
   nrow = 3,
@@
 save_plot(
-  "figures/increasing_biomass_network.png", g2,
+  get_mypath("figures/increasing_biomass_network.png"), g2,
   nrow = 4,
@@
 save_plot(
-  "figures/decreasing_biomass.png", tps_bm_dec,
+  get_mypath("figures/decreasing_biomass.png"), tps_bm_dec,
   nrow = 1,
@@
 save_plot(
-  "figures/increasing_biomass.png", tps_bm_inc,
+  get_mypath("figures/increasing_biomass.png"), tps_bm_inc,
   nrow = 1,
@@
   st = 15818) {
-  .df %>%
+  tex <- .df %>%
     filter(station %in% st) %>%
     mutate(
-      year = ymd(year, truncated = 2L),
-      station = str_replace_all(station, setNames(names(st), st))
-      ) %>%
+      year = ymd(year, truncated = 2L)
+    )
+
+    if(!is.null(names(st))) {
+      tex %<>%
+        mutate(station = str_replace_all(station, setNames(names(st), st)))
+    }
+
+    tex %>%
       ggplot(aes_string(x = "year", y = var)) +
@@
 
+## plot map
+
 ```{r}
 loadd(map_st)
+save_plot(map_st,
+  base_height = 11,
+  base_asp = 1.618,
+  file = get_mypath("figures", "map_st.png")
+)
+```
+
+```{r}
+test_fig_mat_met <- plot_grid(
+  map_st,
+  plot_grid( plot_grid(tps_bm_dec, tps_bm_inc)),
+  plot_grid(plotlist = tps_dec_inc),
+  nrow = 3
+)
+save_plot(
+  test_fig_mat_met,
+  base_height = 12,
+  base_asp = 1.618,
+  file = get_mypath("figures", "matmet.png")
+)
+```
+
+# New figure
+
+```{r}
+# get a station that represents the results 
+st_var_shape <- rigal_classification %>%
+  unnest(classif) %>%
+  filter(variable %in% c(get_com_str_var(), "log_bm_std")) %>%
+  select(station, variable, direction)  %>%
+  pivot_wider(names_from = variable, values_from = direction) 
+dec_representative <- st_var_shape %>%
+  filter(log_bm_std == "decrease", ct_ff == "decrease", w_trph_lvl_avg == "decrease") 
+```
+
+```{r}
+tes <- map(dec_representative$station, ~plot_dyn_web(
+    com = community_metrics,
+    sem_df = NULL,
+    station = .x,
+#    .log = TRUE,
+    stacked = TRUE, 
+    color_species = NULL 
+    ))
+plot_grid(plotlist = tes)
+```
+```{r}
+st_decreasing <- dec_representative$station[3]
+
+p_dec_log_bm <- tes[[3]] +
+  labs(color = "Species", fill = "Species") +
+  theme(legend.position = "bottom")
+
+save_plot(
+  get_mypath("figures/p_dec_log_bm.png"),
+  p_dec_log_bm,
+  nrow = 1,
+  ncol = 1,
+  base_asp = 1.618,
+  base_width = 7)
+```
+```{r}
+tps_dec_inc <- map(c("ct_ff", "w_trph_lvl_avg", "log_rich_std", "piel_bm"),
+  ~plot_temporal_variable_lm(st = st_decreasing, var = .x)
+)
+save_plot(
+  filename = get_mypath("figures/net_str_dec_bm.png"),
+  plot_grid(plotlist = tps_dec_inc),
+  nrow = 2, ncol = 2,
+  base_asp = 1.618,
+  base_width = 5
+)
+```
+```{r temporal foodwebs}
+
+p <- get_network_temporal_plot(
+  net_list = network_analysis,
+  station = st_decreasing,
+  selected_years = c(1996, 2006, 2016),
+  node_color = my_species_color, scale_node_size = 0.027,
+  par_options = par(mar = c(0,0,0,0)),
+  log_abun = TRUE
+)
+g <- plot_grid(plotlist = map(p, ggdraw), ncol = 3)
+
+save_plot(
+  get_mypath("figures/decreasing_biomass_network.pdf"),
+  g,
+  ncol = 3,
+  base_asp = 1.618,
+  base_width = 7)
+```
+
+## plot map
+
+```{r}
+loadd(map_st)
+save_plot(map_st,
+  base_height = 11,
+  base_asp = 1.618,
+  file = get_mypath("figures", "map_st.png")
+)
+```
+
+```{r}
 
@@
 )
-save_plot(test_fig_mat_met,
+save_plot(
+  test_fig_mat_met,
+  base_height = 12,
+  base_asp = 1.618,
   file = get_mypath("figures", "matmet.png")
@@
 ```
+
+```{r}
+test_mat_met <- plot_grid(
+  plot_grid(map_st, p_dec_log_bm, ncol = 2),
+  plot_grid(plot_grid(plotlist = tps_dec_inc), g, ncol = 2),
+  nrow = 2
+)
+save_plot(
+  get_mypath("figures/test_mat_met.png"),
+  test_mat_met,
+  base_asp = .5,
+  base_width = 9
+)
+```

### 2021-10-12 make.R

@@ -11,7 +11,8 @@ source("R/plan.R")      # Create your drake plan.
 # Call make() to run your work.
 # Your targets will be stored in a hidden .drake/ cache,
 #drake::r_make(plan)
-drake::make(plan, keep_going = TRUE)
+#drake::make(plan, targets = "fig_std_coef",  keep_going = TRUE)
+drake::make(plan,  keep_going = TRUE)
 drake::make(plan)
 drake::vis_drake_graph(plan)
 

### 2021-10-15 paper/manuscript.Rmd
Discussion reviewed + add histogram to plots

@@
 ---
-title: "Species richness and biomass temporal trends reveals different assembly processes of food-web in natural fish assemblages " 
+title: "Food-web temporal changes according to changes in species
+richness and community biomass reveal contrasting assembly processes"
 author: Alain Danet, Loubna El Madouri, Maud Mouchet, Elisa Thébault and Colin Fontaine (ordre non fixé)
@@
 
-## Trends of biodiversity needs to be assessed for multiple facets
+## Trends of biodiversity need to be assessed at multiple facets
 
@@
 [@kortsch_disentangling_2021]. Food-web temporal variation are often reported
-across small time step [warren_spatial_1969; @pecuchet_species_2020;
+across small time-steps [@warren_spatial_1989; @pecuchet_novel_2020;
 @kaartinen_high_2012].
@@
 
-In this line, how the temporal changes of community biomasse are related to
+In this line, how the temporal changes of community biomass are related to
 temporal changes of species richness can still be question in natural settings,
@@
 fish freshwater communities on the period 1995-2018 and a method of food-web
-inference based on allometric relationships and food diet datas, we assessed the
+inference based on allometric relationships and food diet data, we assessed the
 relationships among temporal changes of food-web structure, trends of community
@@
 for time substitution by comparing if temporal relationships display the same
-patterns than relationships obtained along spatial gradient.
+patterns as spatial gradient.
 
@@
 temporal dynamics. Communities that displayed low community biomass at the
-beginning of their monitoring tend to display an biomass increase through time
+beginning of their monitoring tend to display biomass increase through time
 and reversely. We observed the same pattern for species richness, with
@@
 in function of the temporal trends of community biomass ($dB$) and species
-richness ($dR$) in order to to test the relationship among the temporal dynamics of network
+richness ($dR$) in order to test the relationship among the temporal dynamics of network
 structure from one side and species richness and community biomass from another
@@
 between the temporal trends of species richness and community biomass (i.e.
-adding $\beta_3dBdR$), the
-results are presented in supplementary material (Fig. SXX).
+adding $\beta_3dBdR$), the results are presented in supplementary material (Fig.
+SXX). To model the relationships between the temporal trends of community
+biomass and the one of species richness, we built equations as $dB = \alpha +
+\beta_1dR + \epsilon$.
 
@@
 
+To model the relationships between community biomass and species richness along
+the spatial gradient, we built the equation as $B = \alpha + \beta_1R +
+\beta_3E_1 + \beta_4E_2 + \epsilon$.
+
 The significativity of the effects were tested with ANOVA. In order to compare
@@
 
-with $\beta$ being the unstandardised slope, $s_x$ and $s_y$ the standard
+With $\beta$ being the unstandardised slope, $s_x$ and $s_y$ the standard
 deviation of the explicative and response variable.
@@
   select(variable, station, direction, acceleration, shape_class)
+
 res_trends <- class_trends_bm_rich %>%
@@
   group_by(variable) %>%
-  mutate(total = sum(n), percent = n / sum(n) * 100 %>% round(., 2))
+  mutate(total = sum(n), percent = round(n / sum(n) * 100))
+
+x_var <- c("log_bm_std", "log_rich_std")
+stable_st_var <- map(x_var,
+  ~class_trends_bm_rich[
+    class_trends_bm_rich$variable == .x &
+    class_trends_bm_rich$direction == "stable",
+      ]$station
+)
+names(stable_st_var) <- x_var
+
+sum(stable_st_var[["log_bm_std"]] %in% stable_st_var[["log_rich_std"]] == TRUE) / length(stable_st_var[["log_bm_std"]])
+
+sum(stable_st_var[["log_rich_std"]] %in% stable_st_var[["log_bm_std"]] == TRUE) / length(stable_st_var[["log_rich_std"]])
 ```
@@
 \@ref(tab:rsq-sp)). Over the station in the dataset, we found that
-`r res_trends[res_trends$variable == "log_bm_std", ]$total` stations displayed monotonic trends for biomass. Among them, 
+`r res_trends[res_trends$variable == "log_bm_std", ]$total[1]` stations displayed monotonic trends for biomass. Among them, 
 `r res_trends[res_trends$variable == "log_bm_std" & res_trends$direction == "stable", ]$percent`%
@@
 increasing. Regarding the species richness, we found that
-`r res_trends[res_trends$variable == "log_rich_std", ]$total` stations displayed monotonic trends.
+`r res_trends[res_trends$variable == "log_rich_std", ]$total[1]` stations displayed monotonic trends.
 `r res_trends[res_trends$variable == "log_rich_std" & res_trends$direction == "stable", ]$percent`%
@@
 also a positive relationship between median connectance and median species
-richness ($r_\delta = `r sp_b_sest["ct"]`$). However, we did not observed
+richness ($r_\delta = `r sp_b_sest["ct"]`$). However, we did not observe
 significant relationships between the temporal trends of connectance and the one
@@
 
-Spatially and temporally, species richness scaled positively with
-community biomass. Spatially, this result is in accordance with numerous studies was
+Spatially and temporally, species richness scaled positively with community
+biomass. Spatially, this result is in accordance with numerous studies was
 already found in streams [@woods_testing_2020; @danet_species_nodate] but also
@@
 @grace_integrative_2016]. Therefore, our results confirm that BEF prediction
-works also in time. The positive relationship of species richness on total
-biomass might be due to resource use complementarity [@carey_determining_2011],
-which is held by niche differentiation [@loreau_biodiversity_1998;
-@loreau_partitioning_2001] or to the higher probability of getting high biomass
-species with higher species richness [@loreau_biodiversity_2001].
+works also in time in food-webs. The positive relationship between species
+richness and total biomass might be due to positive complementarity in resource
+use [@carey_determining_2011], which is held by niche differentiation
+[@loreau_biodiversity_1998; @loreau_partitioning_2001] or to the higher
+probability of getting high biomass species with higher species richness
+[@loreau_biodiversity_2001].
 
-## Biomass temporal dynamics is linked to the top trophic level
+## Biomass and species richness temporal trends relies on different assembly rules
 
-We found that the temporal increase of the average trophic level was positively
-linked to increase of community biomass in line with previous studies suggesting
-that the presence of higher predators can lead to higher community biomass
-[@wang_biodiversity_2018; @danet_species_nodate]. Increase of average trophic
-level can be associated to either gain of biomass in the highest trophic level
-or losses of biomass in the lowest trophic. In our case, such gain or losses of
-average trophic level is probably associated to the variations of the presence
-of large fishes. The finding that the evenness of biomass, measured by the
-pielou, decreased through time as community biomass increased and reversely,
-meaning that biomass distribution across species become more even when community
-biomass decreased and reversely that biomass distribution across species become
-less even when community biomass increased. In the same line, the temporal
-trends of community biomass were positively correlated to the temporal trends of
-the proportion of piscivorous species and trophic species in the community (Fig.
-SXX).
+While we found a strong relationship between the temporal trends of community
+biomass and the one of species richness, our results suggest that temporal trends in
+community biomass and species richness have highly different consequences on the
+structure of food-webs. Indeed, temporal trends of connectance and average
+trophic level was positively associated to the one of community biomass while no
+significant association was found with temporal trends of species richness.
+Moreover, biomass evenness temporal trends was negatively associated to temporal
+trends of community biomass whereas positively associated to temporal trends of
+species richness. All together, it suggests that temporal trends of biomass and
+species richness indicates different food-webs assembly processes.
 
-We also found in space that evenness of biomass was positively related to
-community biomass while evenness of abundances had no relation (Fig. SXX). It
-constrasts with previous studies which found a negative relationship between
-biomass and evenness of abundances in marine and plant communities
-[@drobner_relation_1998; @maureaud_biodiversityecosystem_2019] or studies that
-found more even plant communities in terms of abundances number display higher
-community biomass [@wilsey_biodiversity_2000].
+The temporal trends of connectance was positively linked to that one of
+community biomass, meaning that connectance increases through time in a given
+site when community biomass increases through time and reversely that
+connectance decreased in food-webs where community biomass decreased through
+time. It suggests that community biomass losses are linked to the generalist
+predators while gains in community biomass are associated to the higher presence
+of generalist predators. This interpretation is in line with (2) the results
+that community biomass losses through time were associated to a temporal
+decrease of average trophic level and that community biomass temporal gains were
+associated to temporal increase of average trophic level. Another piece of
+evidence is that evenness of biomass, measured by the pielou, decreased through
+time as community biomass increased, meaning that biomass distribution across
+species become less even when community biomass decreased. Reversely, in
+food-webs that displayed temporal decrease in community biomass, we found that
+evenness of biomass increased, i.e. that biomass distribution across species
+become more even. Because predators-preys interactions relates in part on
+bodysize and thus bodymass in part, we may expect that a given gain in higher
+predators leads to a decrease of biomass evenness and reversely. In the same
+line, the temporal trends of community biomass were positively correlated to the
+temporal trends of the number and proportion of piscivorous trophic species
+present in the community (Fig. SXX).
 
-We further found that the temporal trends of connectance was positively
-linked to that one of community biomass, meaning that connectance increases through
-time in a given site when community biomass increases through time and reversely.
-This is in line with the fact that the fishes located at higher trophic level
-also display a larger number of links as the size of the predation window
-increases with the size of the fishes. This result is also in accordance with  
-theoretical work showing that  higher food-web connectance can result in higher
-community biomass [@thebault_food-web_2003]. But it contrasts with previous
-results [@poisot_trophic_2013; @danet_species_nodate], highlighting that the
-relation between connectance and community biomass may be dependant of assembly
-processes at work.
-
-##  Biomass and richness variation are not the same process
-
-In contrasts to the results for the community biomass, the temporal trends of
-evenness of biomass was positively related to the temporal trends of species
-richness, meaning that as species richness temporally increase, the
-distribution of biomass become more even, while temporal trends of evenness of
-abondances had no significant relationship with species richness (Fig. SXX).
-Those results seem indicate that biomass trends are linked to few big individuals
-while richness trends are linked to overall shift in dominance in communities.
-
-Surprinsingly, we found that the temporal trends of connectance was not related to
-the one of species richness as found spatially in most empirical food-web
-[@dunne_network_2006] and also in the present study. This result suggests that
-the structure of food-webs might not be very sensitive to variation of species
-richness and that species loss and gain concerns species of low trophic level,
-which in turn affect connectance very little. Remarkably, temporal
-variations of community biomass and the ones of species richness seem to be
-linked to high trophic level in the first while being linked to lower trophic
-level in the second. Those results highlight that variations in community
-biomass and species richness are linked to different assembly processes and/or
-pressures, but it is still an open question.
-
----
-#The temporal trend of the average trophic level had no relationship with the
-#one of species richness. It is surprising because one can imagine that loss and
-#gain of species would reveal assembly/disassembly mechanisms in terms of trophic
-#structure. However, we found that when species richness increases, the
-#distribution of biomass and individuals among species become more even in the
-#community, meaning that dominance decrease.
----
+In contrast, we found temporal trends of connectance and average trophic level
+were not related to the temporal trends of species richess. However, we found
+that temporal trends of the number of piscivorous species and piscivorous
+trophic species were strongly positively linked to the temporal trends of
+species richness (Fig. S3). It suggests that the temporal decrease of species
+richness that we observed in our data are concomimant to simultaneous losses of
+piscivorous and non-piscivorous species that leads to the absence of temporal
+trend in connectance and average trophic level and symmetrically for the
+temporal increase of species richness. Furthemore, we found that the temporal
+trends of biomass evenness had a positive relationship with the one of species
+richness, the opposite of what we found for temporal trends of community biomass.
+Together with the fact that species richness temporal trends had a positive
+relationship with the temporal trends of community biomass, it suggests that the
+species richness temporal trends are linked to gain or loss of redundancy in
+food-webs without a clear signature in the vertical structure of the food-webs.
 
@@
 
-While space for time works for variation of community biomass, it is less clear
-for the variation of species richness. Indeed, it was not the case for
-connectance and average trophic level that were respectively weakly or not
-linked to species richness in time whereas our result shows a strong negative
-relation in space. This result is in line with other studies which found
-mismatch between spatial and temporal patterns [@adler_contrasting_2007;
-@johnson_testing_2008]. This mismatch is mainly due to the crucial assumptions
-that variations in space will correspond to differences of assembly stages and
-then reflect the assembly/disassembly trajectories in time of communities [@].
+In time and along spatial gradient, we found that connectance was positively
+linked to community biomass. This result is also in accordance with theoretical
+work showing that higher food-web connectance can result in higher community
+biomass [@thebault_food-web_2003], but other display negative relationship
+[@poisot_trophic_2013], highlighting that the relation between connectance and
+community biomass may be dependant of assembly processes at work.]. In the same
+line, we found that average trophic level had a positive relationship with
+community biomass in space and time. It is in accordance with a theoretical
+model showing that the presence of higher predators can lead to higher community
+biomass [@wang_biodiversity_2018].  We also found in space and time that
+evenness of biomass was negatively related to community biomass. This result is
+in accordance with the observation of top-heavy shape of biomass pyramids in
+food-webs, particularly in freshwater systems [@mccauley_prevalence_2018]. Many
+mechanisms can be responsible have been invoked to explain this pattern but
+omnivory, which is present in most of piscivorous species in our dataset, may
+favor this shape by increasing food transfer efficiency toward higher trophic
+level.
 
-In contrast with a meta-analysis [@soininen_relationship_2012], we found that
-the evenness of abundances is positively related to the one of species
-richness in space in stream fish assemblages but found no relationship in time.
+Surprisingly, we found that the temporal trends of connectance was not related
+to the one of species richness as found spatially in most empirical food-web
+[@dunne_network_2006] and also in the present study. We explained this pattern
+by the fact that the temporal variation of species richness in our dataset seems
+to be linked to variation in the level of redundancy in the role in the
+food-webs rather than overall change of the vertical structure of food-webs. The
+same rational can applied with average trophic level. *This discrependacy might
+be due to the crucial assumptions that variations in space will correspond to
+differences of assembly stages and then reflect the assembly/disassembly
+trajectories in time of communities. Temporal variation of species richness
+might relate on transitory dynamics while spatial gradient reflect aggregated
+dynamics over longer time scale including a far number of processes including
+high species turnover along spatial gradient.* This result is in line with other
+studies which found mismatch between spatial and temporal patterns
+[@adler_contrasting_2007; @johnson_testing_2008].  
+However, we found agreement between space and time analysis for the positive
+relationship between evenness of biomass and species richness. Another reason
+might be that the spatial gradient displays a higher range of variation for
+species richness than the temporal stations (Fig. S2). However, it might not
+explain why we found strong relationships between the temporal trend of species
+richness from one side and the temporal trends of community biomass, biomass
+evenness, the number of piscivore species (Fig. S3). *No more idea, need
+coffee*.
 
-This result has profound implications for conservation. As more and more
-studies report community biomass and species richness trends [@hallmann_more_2017;
-@ceballos_biological_2017], we documented that they might not be
-equivalent in terms of consequences on the structure of the community. In
+However, our result that food-web structure does not change a lot with temporal
+variation of species richness is in line with the insurance hypothesis
+[@yachi_biodiversity_1999]. In this view, the temporal loss and gain of species
+richness represent respectively loss and gain of redundancy in the
+food-web structure. Our results have profound implications for conservation. As
+more and more studies reported community biomass and species richness trends
+[@hallmann_more_2017; @ceballos_biological_2017], we documented that they might
+not be equivalent in terms of consequences on the structure of the community. In
 particular, the loss of the highest trophic level associated to the loss of
-community biomass could of have dramatic consequences on ecosystem functioning
-as highest predators are prone to stabilise communities
-[@shanafelt_stability_2018; danet_species_nodate]. In contrasts, the loss of
-species richness was poorly associated to modification of food-web structure,
-suggesting that the species loss and gain concern lower trophic levels, which
-are also in transmitting energy toward higher level of the trophic chain.
+community biomass could have dramatic consequences on ecosystem functioning
+as the highest predators are prone to stabilise communities
+[@shanafelt_stability_2018; @danet_species_nodate]. In contrasts, the loss of
+species richness might be linked to loss of redundancy in the food-web,
+highlighting that those communities may become more at risk regarding future
+perturbations [@yachi_biodiversity_1999]. Overall, it suggests that monitoring
+several facets of biodiversity is essential to infer how ecological communities
+are reshaped by loss and gain of biomass and species richness.
+
+We further found that most temporal trends of food-webs were classified as
+stable for species richness and community biomass. We found almost the same
+number of stations that displayed temporal decrease or increase for species
+richness, and twice more stations displayed decrease in community biomass than
+increase. While, the spatial coverage of our data is good, it would be rather
+risky to conclude about biodiversity trends in freshwater fish communities in
+France. Mainly because we did not assess pressures that may affect
+the temporal trends such as land-use changes and species invasions
+[@comte_climate_2021; @su_human_2021].
 
@@
 
-Our study shows that richness and biomass temporal trends in natural fish
+Our study suggests that richness and biomass temporal trends in natural fish
 communities relate on different ecological processes, biomass temporal dynamics
-being related to variation of highest trophic levels while it is not the case for
-species richness. Our work also suggests that space for time substitution may be
-relevant to predict food-web community structure in case of biomass variation
-but not for species richness variation. We look forward to next investigations
+being related to variations of at highest trophic levels while species richness
+impacts redundancy of food-web structure. Our result also suggests that space
+for time substitution may be relevant to predict the effects of community
+biomass losses or gains on food-web structure. However, it might not the case
+for species richness temporal variation. We look forward to next investigations
 to see the generality of assembly rules in food-webs. There are crucial to
-better understand the temporal dynamics of food-webs structure and then its
+better understand the temporal dynamics of food-web structure and then its
 impact on ecosystem functioning.
@@
 ```{r bef, fig.cap=fig_bef_cap}
-fig1_2$rich$log_bm_std
+ggMarginal(fig1_2$rich$log_bm_std, type = "histogram")
 ```
@@
 ```{r bmr, out.width = "100%", fig.cap=fig_bm_rich_cap}
+library(ggExtra)
 fig2 <- fig1_2
@@
     theme(axis.text = element_text(size = 6),
-    axis.title = element_text(size = 8)))
+    axis.title = element_text(size = 8))
+  )
 fig2$bm <- map(fig2$bm,
@@
 )
+
+# Add histograms
+fig2$bm <- map(fig2$bm,~ggMarginal(.x, type = "histogram"))
+fig2$rich <- map(fig2$rich,~ggMarginal(.x, type = "histogram"))
 

### 2021-12-13 paper/manuscript.Rmd
Methods reviewed

@@
 ---
-title: "Food-web temporal changes according to changes in species
-richness and community biomass reveal contrasting assembly processes"
+title: "Community biomass and species richness temporal trends reveal contrasting
+    assembly and disassembly processes in natural food-webs"
 author: Alain Danet, Loubna El Madouri, Maud Mouchet, Elisa Thébault and Colin Fontaine (ordre non fixé)
@@
 
+- Tentative titles:
+  - How food-webs assembly and disassembly through time in natural settings?
+    Lessons from freshwater fishes
+  - Relationships among temporal trends of food-web structure, species richness
+    and community biomass reveal contrasting assembly
+    and disassembly processes
+  - Temporal trends in food web structure according to richness and biomass
+    reveal contrasting assembly and disassembly processes
+
 ```{r, results = FALSE}
@@
 as decrease in species richness [@barnosky_has_2011; @newbold_global_2015] and
-turnover in species composition [@comte_climate_2021]. The documentation of
-biodiversity temporal trends, is crucial to evaluate the effect of
-global changes [but see @cardinale_is_2018]. Unfortunately, studies often
-report trends of one dimension of biodiversity at a time [@hallmann_more_2017,
+turnover in species composition [@comte_climate_2021]. Unfortunately, studies often
+focus on the temporal trend of one dimension of biodiversity [@hallmann_more_2017,
 etc, but see @]. Because the functioning of ecosystem depends ultimately on
 multiple facets of biodiversity, such as species richness, evenness and
-functional composition [REF @thibaut_understanding_2013], the monitoring of one
-biodiversity trend is not enough to project potential effects on ecosystem
-functioning.
+functional composition^[1]  [REF @thibaut_understanding_2013], the documentation
+of the trend of one biodiversity facet is likely insufficient to evaluate
+precisely its consequences
+on ecosystem functioning.
 
-## Predictions come mainly from space-for-time substitution
+[^1]: Commentaire de Colin: *je pense qu'il faut lister les facet de biodiv qu'on
+va etudier. sans forcement s'y limiter?* Ici je pense que la composition en role
+trophique rentre dans "functional composition" sans rentrer dans le détail.
 
-Another concern is that the links between the different components of community
-structure often come from spatial comparison [@dunne_network_2006;
-@soininen_relationship_2012; @grace_integrative_2016 @danet_species_nodate]. In
-order to use spatial comparison to predict the fate of communities facing
-changes in species richness or community biomass, studies often implicitly use
-the "space for time substitution" hypothesis. This method began to be widely
+## Current knowledge mainly comes from space-for-time substitution
+
+Current knowledge on the links among different facets of biodiversity mainly
+comes from from spatial comparison [@dunne_network_2006;
+@soininen_relationship_2012; @grace_integrative_2016 @danet_species_nodate]. space-for-time substitution began to be widely
 used in the early 20th century to infer the temporal succession of vegetation
 from space variations [@pickett_space-for-time_1989]. It supposes a homology
-between variations in space and in time i.e. that spatial sequences correspond
+between variations in space and in time, i.e. that spatial sequences correspond
 to temporal sequences.  This method have raised criticisms
@@
 limitation, disturbance and stochastic processes have been hypothesised to be
-responsible for the failure of space for time substitution
+responsible for the non-compliance of space-for-time substitution
 [@adler_contrasting_2007; @blois_space_2013].
@@
 
-The documentation of biodiversity trends generally neglect species interactions
-although they are fundamentals to ecosystem functioning
-[@thebault_food-web_2003; oconnor_general_2016]. In food-webs, empirical and
-theoretical studies reported generally that trophic level positively scales to
-community biomass [@wang_biodiversity_2018; @danet_species_nodate] (add
-mechanisms ?). Trophic level has also been shown to stabilise the temporal
-variation of community biomass [@shanafelt_stability_2018;
+The documentation of biodiversity temporal trends generally neglect species
+interactions although they are fundamentals to ecosystem functioning
+[@thebault_food-web_2003; @oconnor_general_2016]. In food-webs, spatial
+comparisons in empirical and theoretical studies generally reported that trophic
+level positively scales to community biomass [@wang_biodiversity_2018;
+@danet_species_nodate]. Trophic level has also been shown to stabilise the
+temporal variation of community biomass [@shanafelt_stability_2018;
 @danet_species_nodate]. Connectance, which measures the degree of generalism in
@@
 across small time-steps [@warren_spatial_1989; @pecuchet_novel_2020;
-@kaartinen_high_2012].
-
-We know very little how food-web structure vary across time and particularly how
-those variations are linked to the variations of other aspects of community
-structure such as species richness and community biomass. Spatially, connectance
-has been shown to be negatively related to species richness in empirical
-food-webs [reviewed in @dunne_network_2006]. Connectance has been shown to scale
-positively or negatively with community biomass in theoretical models
+@kaartinen_high_2012]. Our knowledge are even more scarce on the variability of
+food-web structure in time and particularly how those temporal variations are linked to
+the temporal variations of other aspects of biodiversity such as species richness
+and community biomass. Spatially, connectance has been shown to be negatively
+related to species richness in empirical food-webs [reviewed in
+@dunne_network_2006]. Connectance has been shown to scale positively or
+negatively with community biomass in theoretical models
 [@thebault_food-web_2003; @poisot_trophic_2013] (*Add mechanism?*). In order to
 improve our understanding on the assembly mechanisms in food-webs, it is thus
-crucial to assess how biomass and species richness variation are associated to
-variations in food-web structure.
+crucial to assess how biomass and species richness temporal trends are associated to
+temporal trends in food-web structure.
 
 In this line, how the temporal changes of community biomass are related to
-temporal changes of species richness can still be question in natural settings,
-especially in food-webs. Our knowledge on how the temporal changes of food-web
-structure are related  to temporal changes in community biomass and species
-richness is almost zero. Our knowledge on the relationships between food-web
-structure comes often from comparison of food-web snapshots along spatial
-gradient, raising the question of the validity of space for time substitution to
-infer consequences of species richness and community biomass on food-web
-structure. The increasing amount of availability ecological temporal series
-makes possible to assess those questions. Using a standardized monitoring of
-fish freshwater communities on the period 1995-2018 and a method of food-web
-inference based on allometric relationships and food diet data, we assessed the
-relationships among temporal changes of food-web structure, trends of community
-biomass and trends in species richness. We then assessed the validity of space
-for time substitution by comparing if temporal relationships display the same
-patterns as spatial gradient.
+temporal changes of species richness is still questionned in natural settings,
+especially in food-webs. Our knowledge on the relationships between food-web
+structure and other facets of biodiversity often comes from the comparison of
+food-web snapshots along spatial gradient, raising the question of the validity
+of space-for-time substitution to infer consequences of species richness and
+community biomass variations on food-web structure.
+
+The increasing availability ecological temporal series and the development of
+methods to reconstruct food-webs [@bonnaffe_comparison_2021;
+@gravel_inferring_2013; @danet_species_nodate] makes possible to assess those
+questions. We used the standardized monitoring of fish freshwater communities on
+the period 1995-2018 over France, documenting the individual size of fishes in
+400 sites during ten years or more. We then reconstruct around 4000 food-webs
+based on allometric relationships and food diet data. We questionned i) how
+temporal trends of food-web structure are  linked to trends of community biomass
+and trends in species richness? ii) Are the relationships observed in time the
+same as those observed in space, i.e. is the space-for-time substitution valid?
 
@@
 
+We used a monitoring of freshwater fishes conducted all over France and
+conducted by the Office Français de la Biodiversité (OFB, previously known as
+ONEMA and AFB). The sampling protocols were standardized since 1995 and a
+complete description of the sampling process can be found in
+@danet_species_nodate (main text and appendixS2). The fishes are sampled using
+electrofishing all across the streams in shallow streams and over the bank by
+boat in deeper streams. All the fishes are counted and the bodysize of fishes are
+recorded for a sample of them, enabling the estimate the distribution of
+individual bodysize by species for each sampling [@bonnaffe_comparison_2021;
+@danet_species_nodate].
+
 ## Data selection
 
-We selected the stations that have been monitored at least 10 times on the
-1995-2018 period.
+We selected the sites that have been monitored at least 10 years on the
+1995-2018 period, with the same sampling protocol over time. We selected
+one sampling a year by site. In each site, we ensured low temporal heterogeneity
+in sampling period by selecting sampling that were performed in the same period,
+leading to a mean standard deviation of sampled month in each site of three
+weeks [@danet_species_nodate]. Those steps leads to the selection of 
+`r nb_st` sites (Figure \@ref{fig:matmet}A).
 
@@
 
-We first inferred the body mass of each fish individual thanks to an allometric
-law, $B_i = 0.01 \times l_i^3.03$, $B_i$ being biomass in gram and $l_i$ the
-body length in millimetre of the individual $i$ [@froese_cube_2006]. Then the
+We first inferred the body mass of each fish individual considering an allometric
+law, $B_i = 0.01 \times l_i^3.03$, $B_i$ being the biomass expressed in gram and $l_i$ the
+body length of the individual $i$ expressed in millimetres  [@froese_cube_2006]. Then the
 biomass of each species and community biomass were obtained by summing the body
@@
 @danet_species_nodate]: (1) we first computed the metaweb, describing the
-potential trophic interactions between all species size classes, (2) then we
-extracted each local time snapshot of food-webs by extracting species size
-classes and their interactions according their presence in a given sampling
+potential trophic interactions among all size classes species, (2) then we
+extracted each yearly snapshot of food-webs by extracting species size
+classes and their interactions according to their presence in a given sampling
 event.
 
-We inferred food-web structure according to ontogenic diet data and body size
+We inferred the metaweb according to ontogenic diet data and body size
 [@gravel_inferring_2013; @poisot_structure_2016; @brose_predator_2019;
@@
 described in @bonnaffe_comparison_2021 and @danet_species_nodate. The food diet
-of stream fishes, as many organisms, change along their life and therefore
+of stream fishes changes along their life cycle or stage, therefore
 according to their body size. Each fish species was divided in nine size
-classes, named trophic species, equally distributed in their observed body size
-range.  A trophic species is a group of individuals of the same species and size
+classes, named "trophic species", equally distributed in their observed body size
+range. Thus, a trophic species is a group of individuals of the same species and size
 class that are expected to share the same preys and predators. We also added
@@
 We determined the feeding interactions of trophic species according to their
-species identity and their body size. The diet database described two or
-three life stages by fish species, each one being delimited by body size
-[@bonnaffe_comparison_2021; @danet_species_nodate]. The life stage of a fish
-trophic species was determined by the centre of its body size range, hereafter
-midpoint. The ontogenic fish diet database was filled according to fishbase
-(Froese et al. 2021) and literature [@bonnaffe_comparison_2021;
-@danet_species_nodate].
+species identity and their body size. The diet database described two or three
+life stages by fish species, each one being delimited by body size
+[@bonnaffe_comparison_2021; @danet_species_nodate]. The ontogenic fish diet
+database was filled according to fishbase (Froese et al. 2021) and literature
+[@bonnaffe_comparison_2021; @danet_species_nodate].
 
-The feeding interactions between fishes were based on the body size ratio
-between predators and preys. As this, we defined the predation window of a
+The feeding interactions among fishes were based on the body size ratio
+between predators and preys. We defined the predation window of a
 piscivorous trophic species as 3% to 45% of its midpoint
@@
 and the resources nodes according to the food items of their size class.
-Finally, the feed interactions between resources were defined according to the
+Finally, the feeding interactions between resources were defined according to the
 literature [@allan_stream_2007; @hart_handbook_2008].
 
-## Food-web and community structure
+## Community and food-web structure
 
-We characterized food-webs by their connectance, describing the degree of
+At each site, yearly food-webs were described by their community biomass,
+species richness and the evenness of biomass across species. The evenness was
+quantified with the Pielou index, computed as the Shannon diversity index
+divided by the number of species ($P = \frac{H'}{N}$, with $H'$ being the
+Shannon diversity index and $N$ the number of species). Yearly food-web
+structure was described by their connectance, describing the degree of
 generalism in a network [@dunne_network_2006; @delmas_analysing_2019]. It was
-computed as the ratio between the actual number of links and the number of
+computed as the ratio between the number of actual links and the number of
 potential links ($C = \frac{L}{S(S-1)}$, with $L$ being the number of links and
@@
 species was computed recursively as 1 added to the mean trophic level of the
-preys that it consumes.
-
-We described community structure by its community biomass, species richness and
-the evenness of the number of individual and the amount of biomass across
-species. The evenness was quantified with the Pielou index, computed as the
-Shannon diversity index divided by the number of species ($P = \frac{H'}{N}$,
-with $H'$ being the Shannon diversity index and $N$ the number of species).
+preys that it consumes [@herendeen_ecological_2008].
 
@@
 
-## Classification of temporal trajectories
+## Temporal trends of food-web
 
@@
 structure and the temporal trends of community biomass and species richness, we
-characterized the temporal trajectories of network and community structure at
-each site. We used a method based on second order polynomial which allows to
-assess both the direction and the monotony of temporal trends
-[@rigal_method_2020]. To avoid the inclusion of many types of biomass and species
-richness trends (i.e. accelerating, decelerating, etc...), we selected the
-stations that displayed monotonic trends for these variables, i.e. the ones for
-which the second order polynomial term was non significant. Over the `r nb_st`
-stations, the selection procedure resulted in `r nb_st_rich_bm` for community
-biomass and species richness analysis. However, the results were robust to the
-inclusion of non monotonic trends (Fig. SXX).
+characterized the temporal trajectories of food-web structure at each site. We
+modeled a linear relationship between food-web structure and
+time with a second order polynome, which allows to assess both the direction and the monotony of temporal
+trends [@rigal_method_2020]. We selected the sites that displayed monotonic
+trends for these variables, i.e. the ones for which the second order polynomial
+term was non significant according to t-tests, to avoid the inclusion of many
+types of biomass and species richness trends (i.e. accelerating, decelerating,
+etc...), . Over the `r nb_st` monitored sites, the selection procedure resulted in `r
+nb_st_rich_bm` sites for community biomass and species richness analysis. However, the
+results were robust to the inclusion of non monotonic trends (Fig. SXX).
 
@@
 temporal dynamics. Communities that displayed low community biomass at the
-beginning of their monitoring tend to display biomass increase through time
-and reversely. We observed the same pattern for species richness, with
-communities that displayed high species richness at the beginning of their
-monitoring tend to display a decrease in species richness through time and
-reversely.
+beginning of their monitoring tend to display a biomass increase through time
+and reversely, we observed the same pattern for species richness. We
+log-transformed (natural logarithm) community biomass and species richness to model their trends,
+which decreased the former effect (Fig. SXX). Temporal
+trends of community biomass and species richness were thus expressed in rate of
+change by year.
 
@@
 
-In spatial analysis, we selected the same stations that were used for the
-temporal analysis. We summarised temporal series of each stations by the median
-value over time of each variable.
+To assess the validity of the space-for-time substitution hypothesis, we
+compared the relationships among food-web structure in time to the ones observed
+along spatial gradient. To do so, we selected the same sites that were used
+for the temporal analysis. We summarised temporal series of each station by the
+median value over time of each facet of food-web structure described above.
 
@@
 
-## Temporal trends
+## Relationships among temporal trends
 
-We modelled the dynamics the temporal trends of food-web structure ($dN$)
-in function of the temporal trends of community biomass ($dB$) and species
-richness ($dR$) in order to test the relationship among the temporal dynamics of network
-structure from one side and species richness and community biomass from another
-side.
+We modelled the relationships among the temporal trends of food-web structure ($dN$)
+depending on the temporal trends of community biomass ($dB$) and species
+richness ($dR$) with a linear model. in order to test the relationship among the temporal of food-web
+structure, that is connectance, average trophic level and evenness of biomass
+from one side and species richness and community biomass from the other side as
+follows:
 
-$dN = \alpha + \beta_1dB + \beta_2dR + \epsilon$
+$dN_j = \alpha + \beta_1dB_j + \beta_2dR_j + \epsilon_j$
 
@@
 
-  - $dN$: temporal trend of network structure and communities structure
-  - $dB$: temporal trend of community (log) biomass
-  - $dR$: temporal trend of (log) species richness
+  - $dN$: temporal trends of food-web structure: connectance, average trophic
+    level and evenness of biomass across species
+  - $dB$: temporal trend of ($\log_e$) community biomass
+  - $dR$: temporal trend of ($\log_e$) species richness
+  - $j$: the site
+  - $\alpha$: intercept 
+  - $\beta$: slope 
+  - $\epsilon$: gaussian error
 
@@
 estimated trends, i.e. slopes for the response and the explicative
-variables. We also tested a statistical model taking in account the interaction
-between the temporal trends of species richness and community biomass (i.e.
-adding $\beta_3dBdR$), the results are presented in supplementary material (Fig.
+variables ($w_j = \dfrac{1}{s_{r_j} s_{e,j}}$, $w_j$ being the weight, $s_{r_j}$ and $s_{e_j}$ being
+respectively the standard errors on the temporal trends of the response and
+explicative variables). We also included a statistical model including the
+interaction between the temporal trends of species richness and community
+biomass (i.e.
+adding $\beta_3dB_jdR_j$), the results are presented in supplementary material (Fig.
 SXX). To model the relationships between the temporal trends of community
-biomass and the one of species richness, we built equations as $dB = \alpha +
-\beta_1dR + \epsilon$.
+biomass and the one of species richness, we built the model as $dB_j = \alpha_j +
+\beta_1dR_j + \epsilon_j$.
 
-## Spatial trends
+## Relationships along spatial gradient
 
-Spatial gradient of food-web structure are partly driven by environmental gradients, so
-we controlled relationships among community structure variables by two PCA axis
+Spatial gradients of food-web structure are partly driven by environmental gradients, so
+we controlled relationships among variables by adding two PCA axis
 synthesizing respectively (1) stream size and (2) average temperature and
 enrichment. Enrichment was characterized by the average Biological Oxygen
-Demand [BOD, @mallin_factors_2006].
+Demand [BOD, @mallin_factors_2006][^2].
 
-$N = \alpha + \beta_1B + \beta_2R + \beta_3E_1 + \beta_4E_2 + \epsilon$
+[^2]: commentaire de colin: il faudrait introduire spatial gradient des l'intro
+et cette partie est plutot sur les relationships among spatial gradient of biodiv facets
+
+$N_j = \alpha + \beta_1B_j + \beta_2R_j + \beta_3E_{1,j} + \beta_4E_{2,j} + \epsilon_j + \epsilon_{\alpha|i}$
 
@@
 
-  - $N$: median network structure and communities structure
-  - $B$: median community biomass
-  - $R$: median species richness 
-  - $E_1$: PCA1 related to stream size
-  - $E_2$: PCA2 related to average temperature and average BOD
+  - $N_j$: median network structure and communities structure
+  - $B_j$: median community biomass
+  - $R_j$: median species richness 
+  - $E_{1,j}$: PCA1 related to stream size
+  - $E_{2,j}$: PCA2 related to average temperature and average BOD
+  - $\epsilon_{\alpha|i}$: random effect of the hydrographic basin
+    $i$ on $\alpha$
 
 To model the relationships between community biomass and species richness along
-the spatial gradient, we built the equation as $B = \alpha + \beta_1R +
-\beta_3E_1 + \beta_4E_2 + \epsilon$.
+the spatial gradient, we built the equation as $B_j = \alpha + \beta_1R_j +
+\beta_3E_{1,j} + \beta_4E_{2,j} + \epsilon_j$.
 
@@
 temporal and spatial models, we computed standardized slopes ($r_{\delta}$) and
-their associated standard errors.
-
-$r_{\delta} = \beta\frac{s_x}{s_y}$
-
+their associated standard errors as $r_{\delta} = \beta\frac{s_x}{s_y}$.
 With $\beta$ being the unstandardised slope, $s_x$ and $s_y$ the standard
-deviation of the explicative and response variable.
+deviation of the explicative and response variables.
 
@@
 
-sum(stable_st_var[["log_bm_std"]] %in% stable_st_var[["log_rich_std"]] == TRUE) / length(stable_st_var[["log_bm_std"]])
+#sum(stable_st_var[["log_bm_std"]] %in% stable_st_var[["log_rich_std"]] == TRUE) / length(stable_st_var[["log_bm_std"]])
 
-sum(stable_st_var[["log_rich_std"]] %in% stable_st_var[["log_bm_std"]] == TRUE) / length(stable_st_var[["log_rich_std"]])
+#sum(stable_st_var[["log_rich_std"]] %in% stable_st_var[["log_bm_std"]] == TRUE) / length(stable_st_var[["log_rich_std"]])
 ```
@@
 ```
+Over the sampling sites in the dataset, we found that
+`r res_trends[res_trends$variable == "log_bm_std", ]$total[1]` stations displayed monotonic trends for biomass. Among them, 
+`r res_trends[res_trends$variable == "log_bm_std" & res_trends$direction == "stable", ]$percent`%
+were classified as stable,
+`r res_trends[res_trends$variable == "log_bm_std" & res_trends$direction == "decrease", ]$percent`%
+as decreasing,
+`r res_trends[res_trends$variable == "log_bm_std" & res_trends$direction == "increase", ]$percent`%
+as increasing. Regarding the species richness, we found that
+`r res_trends[res_trends$variable == "log_rich_std", ]$total[1]` stations displayed monotonic trends.
+`r res_trends[res_trends$variable == "log_rich_std" & res_trends$direction == "stable", ]$percent`%
+were classified as stable,  
+`r res_trends[res_trends$variable == "log_rich_std" & res_trends$direction == "decrease", ]$percent`%
+as decreasing, and 
+`r res_trends[res_trends$variable == "log_rich_std" & res_trends$direction == "increase", ]$percent`% as increasing.
 
 Overall, we found high heterogeneity in the explicative power of statistical
-models linking temporal dynamics of food-web structure and the one of community
+models linking temporal dynamics of food-web structure, evenness of biomass  and the one of community
 biomass and species richness spanning from $R_{adj}^2= `r rsq_piel_nind`$ for
 the evenness of abundances to $R_{adj}^2= `r rsq_tlvl`$ for average trophic
-level (Table \@ref(tab:rsq)). The spatial models were more performant, with
+level (Table \@ref(tab:rsq)). The models over the spatial gradient were more performant, with
 $R_{cond}^2$ varing from $`r rsq_tlvl_sp`$ to $`r rsq_piel_bm_sp`$ (Table
-\@ref(tab:rsq-sp)). Over the station in the dataset, we found that
-`r res_trends[res_trends$variable == "log_bm_std", ]$total[1]` stations displayed monotonic trends for biomass. Among them, 
-`r res_trends[res_trends$variable == "log_bm_std" & res_trends$direction == "stable", ]$percent`%
-were classified stable,
-`r res_trends[res_trends$variable == "log_bm_std" & res_trends$direction == "decrease", ]$percent`%
-decreasing,
-`r res_trends[res_trends$variable == "log_bm_std" & res_trends$direction == "increase", ]$percent`%
-increasing. Regarding the species richness, we found that
-`r res_trends[res_trends$variable == "log_rich_std", ]$total[1]` stations displayed monotonic trends.
-`r res_trends[res_trends$variable == "log_rich_std" & res_trends$direction == "stable", ]$percent`%
-were classified stable,  
-`r res_trends[res_trends$variable == "log_rich_std" & res_trends$direction == "decrease", ]$percent`%
-as decreasing, and 
-`r res_trends[res_trends$variable == "log_rich_std" & res_trends$direction == "increasing", ]$percent`% increasing.
-
+\@ref(tab:rsq-sp)), $R_{cond}^2$ being the $R^2$conditional to the random effect. 
 ---
@@
 ---
-
-## Relationships between temporal trends
 
@@
 We found a strong positive relationship between the temporal trends of community
-biomass and the one of species richness ($r_\delta = `r tps_r_sest["p_bm"]`$,
+biomass and the ones of species richness ($r_\delta = `r tps_r_sest["p_bm"]`$,
 Fig. \@ref(fig:bef), Table \@ref(tab:aov)), meaning that both temporal trends
-had the same direction in average. At stations
+had the same direction in average. At the sites 
 where species richness decreased over time, community biomass also decreased
-over time. On the other hand, at stations where species richness increased over
-time, community biomass also increased over time. In spatial analysis, we also
+over time. On the other hand, at the sites where species richness increased over
+time, community biomass also increased over time. Along the spatial gradient, we also
 found a positive relationship between median community biomass and median
-species richness, but twice less strong than the temporal one
+species richness, but half the strength as the temporal one
 ($r_\delta = `r sp_b_sest["rich"]`$).
 
-The temporal trends of connectance was positively linked with the one of
-community biomass ($r_\delta = `r tps_bm_sest["ct"]`$), meaning also that both
-temporal trends had the same direction in average. That is, the stations where
-food-web connectance decreased over time had also community biomass that
-decreased over time and reversely. It means that communities that lose biomass
-over time, also loses generalist predators and reversely that communities
-gaining biomass over time also gain generalist predators. Spatially, we found
-also a positive relationship between median connectance and median species
+The temporal trends of connectance were positively linked with the ones of
+community biomass ($r_\delta = `r tps_bm_sest["ct"]`$), also meaning that both
+temporal trends had the same direction in average. That is, the sites where
+food-web connectance decreased over time also had community biomass that
+decreased over time and reversely. It suggests that communities that loose biomass
+over time, also loose generalist predators and reversely that communities
+gaining biomass over time also gain generalist predators. Spatially, we also found
+a positive relationship between median connectance and median species
 richness ($r_\delta = `r sp_b_sest["ct"]`$). However, we did not observe
-significant relationships between the temporal trends of connectance and the one
-of species richness (Fig. \@ref(fig:bmr)D) when we found spatially a stong
+significant relationships between the temporal trends of connectance and the
+ones of species richness (Fig. \@ref(fig:bmr)D) while we found a stong
 negative relationship between median connectance and median species richness
+along the spatial gradient
 ($r_\delta = `r sp_r_sest["ct"]`$, Fig. \@ref(fig:std)).
@@
 We found that the temporal trends of average trophic level had a strong positive
-relationship with the one of community biomass 
+relationship with the ones of community biomass 
 ($r_\delta = `r tps_bm_sest["tlvl"]`$, Fig. \@ref(fig:bmr)B, Table
 \@ref(tab:aov)), meaning
-that stations where community biomass decreased over time, average trophic level
-decreased over time and vice versa. It means that in communities losing biomass
-over time, the average biomass of the food-web moved toward lower trophic level
-and vice versa. The spatial gradient also showed a positive relationship between
-median average trophic level and median community biomass, but twice less strong
-than the temporal one ($r_\delta = `r sp_b_sest["tlvl"]`$, Fig. \@ref(fig:std),
-Table \@ref(tab:aov-sp)). As for connectance, the temporal trends of average
-trophic level was unrelated to the one of species richness. It means in
-communities either losing or gaining species richness over time, the location of
-average biomass along   trophic level did not significantly change.  However, we
-found a strong negative relationship along the spatial gradient 
+that sites where community biomass decreased over time, average trophic level
+decreased over time and *vice versa*. It suggests that in communities loosing biomass
+over time, the average biomass of the food-web moved down to lower trophic level
+and *vice versa*. The spatial gradient also showed a positive relationship between
+median average trophic level and median community biomass, but half the strength 
+as the temporal one ($r_\delta = `r sp_b_sest["tlvl"]`$, Fig. \@ref(fig:std),
+Table \@ref(tab:aov-sp)). The temporal trends of average
+trophic level was unrelated to the ones of species richness. It suggests that in
+communities either loosing or gaining species richness over time, the location of
+average biomass along trophic level did not significantly change according to species richnnes.  However, we
+found a strong negative relationship in space 
 ($r_\delta = `r sp_r_sest["tlvl"]`$, Fig. \@ref(fig:std), Table
@@
 
-Evenness of species biomass was negatively linked to community
-biomass in time and along the spatial gradient 
+Evenness of biomass was negatively linked to community
+biomass in time and in space 
 ($r_\delta = `r tps_bm_sest["p_bm"]`$ and $`r sp_b_sest["p_bm"]`$ resp.; Fig.
-\@ref(fig:bmr)C, Fig. \@ref(fig:std)). In time, it means that food-webs that
-lost biomass over time also had biomass more evenly distributed by species over
-time and vice versa. A similar reasoning applies to spatial gradient. On the
+\@ref(fig:bmr)C, Fig. \@ref(fig:std)). Regarding time, it means that food-webs that
+lost biomass over time also had a more even distribution of biomass across species over
+time and *vice versa*. A similar reasoning applies in space. On the
 other hand, we found a positive relationship between the temporal trends of
@@
 \@ref(tab:aov), $r_\delta = `r tps_r_sest["p_bm"]`$). We found the same
-relationship along the spatial gradient, twice strong however 
+relationship in space, twice as strong however 
 ($r_\delta = `r sp_r_sest["p_bm"]`$).
@@
 
-## BEF works in space and time
+## Species richness and community biomass are positively linked in space and time
 
 Spatially and temporally, species richness scaled positively with community
-biomass. Spatially, this result is in accordance with numerous studies was
-already found in streams [@woods_testing_2020; @danet_species_nodate] but also
+biomass. Spatially, this result is in accordance 
+with previous studies in stream communities [@woods_testing_2020; @danet_species_nodate] but also
 in grasslands, salt marches and forests [@hector_plant_1999;
 @tilman_biodiversity_2014; @wu_relationship_2015; @li_relationship_2018; but see
-@grace_integrative_2016]. Therefore, our results confirm that BEF prediction
-works also in time in food-webs. The positive relationship between species
+@grace_integrative_2016]. Therefore, our results confirm that
+Biodiversity-Ecosystem functioning prediction
+works also in the temporal dynamics of food-webs. The positive relationship between species
 richness and total biomass might be due to positive complementarity in resource
@@
 
-## Biomass and species richness temporal trends relies on different assembly rules
+## The temporal of community biomass and species richness relates on different assembly and disassembly rules
 
@@
 biomass and the one of species richness, our results suggest that temporal trends in
-community biomass and species richness have highly different consequences on the
-structure of food-webs. Indeed, temporal trends of connectance and average
-trophic level was positively associated to the one of community biomass while no
+community biomass and species richness are associated with very different temporal trends on the
+connectance, average trophic level and evenness of biomass. Indeed, temporal trends of connectance and average
+trophic level were positively associated to the temporal trends of community biomass while no
 significant association was found with temporal trends of species richness.
-Moreover, biomass evenness temporal trends was negatively associated to temporal
+Moreover, the temporal trends of biomass evenness were negatively associated to the temporal
 trends of community biomass whereas positively associated to temporal trends of
-species richness. All together, it suggests that temporal trends of biomass and
-species richness indicates different food-webs assembly processes.
+species richness. All together, it suggests that temporal trends of community
+biomass and species richness are related to different assembly and disassembly
+processes in food-webs.
 
-The temporal trends of connectance was positively linked to that one of
-community biomass, meaning that connectance increases through time in a given
-site when community biomass increases through time and reversely that
-connectance decreased in food-webs where community biomass decreased through
-time. It suggests that community biomass losses are linked to the generalist
-predators while gains in community biomass are associated to the higher presence
-of generalist predators. This interpretation is in line with (2) the results
-that community biomass losses through time were associated to a temporal
-decrease of average trophic level and that community biomass temporal gains were
-associated to temporal increase of average trophic level. Another piece of
-evidence is that evenness of biomass, measured by the pielou, decreased through
-time as community biomass increased, meaning that biomass distribution across
-species become less even when community biomass decreased. Reversely, in
-food-webs that displayed temporal decrease in community biomass, we found that
-evenness of biomass increased, i.e. that biomass distribution across species
-become more even. Because predators-preys interactions relates in part on
-bodysize and thus bodymass in part, we may expect that a given gain in higher
-predators leads to a decrease of biomass evenness and reversely. In the same
-line, the temporal trends of community biomass were positively correlated to the
-temporal trends of the number and proportion of piscivorous trophic species
-present in the community (Fig. SXX).
+The temporal trends of connectance were positively linked to that of community
+biomass, meaning that when connectance increased through time in a given site
+when community biomass increased through time. Reversely, connectance decreased
+in food-webs when community biomass decreased through time. It suggests that
+community biomass losses and gains are associated to losses and gains in large
+bodied predators. This interpretation is in line with the results that community
+biomass losses through time were associated to a temporal decrease of average
+trophic level and that community biomass temporal gains were associated to
+temporal increase of average trophic level. Another piece of evidence is that
+evenness of biomass, measured by the Pielou index, decreased through time as
+community biomass increased, meaning that biomass distribution across species
+becomes less even when community biomass increased. Reversely, in food-webs that
+displayed temporal decrease in community biomass, we found that evenness of
+biomass increased, i.e. that biomass distribution across species becomes more
+even.  Because predator-prey interactions relate in part on bodysize and thus
+bodymass to a certain extent, we may expect that a given gain in predators of
+higher trophic level leads to a decrease of biomass evenness and reversely. In
+the same line, we found that the temporal trends of community biomass were positively
+correlated to the temporal trends of the number and proportion of piscivorous
+trophic species present in fish communities (Fig. SXX).
 
-In contrast, we found temporal trends of connectance and average trophic level
-were not related to the temporal trends of species richess. However, we found
+In contrast, we found that temporal trends of connectance and average trophic level
+were not related to the temporal trends of species richness. However, we found
 that temporal trends of the number of piscivorous species and piscivorous
@@
 species richness (Fig. S3). It suggests that the temporal decrease of species
-richness that we observed in our data are concomimant to simultaneous losses of
-piscivorous and non-piscivorous species that leads to the absence of temporal
-trend in connectance and average trophic level and symmetrically for the
+richness observed in our data are concomimant to losses of
+piscivorous and non-piscivorous species, leading to the absence of temporal
+trends in connectance and average trophic level and symmetrically for the
 temporal increase of species richness. Furthemore, we found that the temporal
 trends of biomass evenness had a positive relationship with the one of species
-richness, the opposite of what we found for temporal trends of community biomass.
+richness, in contraction of what we found for temporal trends of community biomass.
 Together with the fact that species richness temporal trends had a positive
-relationship with the temporal trends of community biomass, it suggests that the
-species richness temporal trends are linked to gain or loss of redundancy in
-food-webs without a clear signature in the vertical structure of the food-webs.
+relationship with the temporal trends of community biomass, it suggests that
+positive and negative  temporal trends of species richness are linked to gains and
+losses of redundancy in food-webs, without overall effects on connectance
+and average trophic level.
 
-## Space for time substitution does not always hold
+## Space-for-time substitution does not always hold
 
@@
 ```
-```{r, fig.cap=fig_mat_cap, out.width="100%"}
+```{r matmet, fig.cap=fig_mat_cap, out.width="100%"}
 knitr::include_graphics(get_mypath("figures", "mat_met_inkscape.pdf"))
@@
 ```{r bef, fig.cap=fig_bef_cap}
+library(ggExtra)
 ggMarginal(fig1_2$rich$log_bm_std, type = "histogram")
@@
 ```{r bmr, out.width = "100%", fig.cap=fig_bm_rich_cap}
-library(ggExtra)
 fig2 <- fig1_2

### 2022-02-22 paper/manuscript.Rmd
Update figures

@@
 ```{r}
+loadd(rsq_table_bm_rich_mono_stable_trends)
+loadd(reg_table_bm_rich_mono_stable_trends)
+```
+
+```{r}
 net_var_bm <- c("log_rich_std", "ct_ff", "w_trph_lvl_avg", "piel_bm",
@@
       "piel_nind")
+```
+
+```{r}
+loadd(slope_com_var_no_covar, st_mono_trends_stable_rich_bm)
+```
+```{r}
+nb_st <- unique(slope_com_var_no_covar$station) %>% length
+rm(slope_com_var_no_covar)
+nb_st_rich_bm <- st_mono_trends_stable_rich_bm %>% length
 ```
@@
 comes from from spatial comparison [@dunne_network_2006;
-@soininen_relationship_2012; @grace_integrative_2016 @danet_species_nodate]. space-for-time substitution began to be widely
+@soininen_relationship_2012; @grace_integrative_2016; @danet_species_nodate]. space-for-time substitution began to be widely
 used in the early 20th century to infer the temporal succession of vegetation
@@
 interactions although they are fundamentals to ecosystem functioning
-[@thebault_food-web_2003; @oconnor_general_2016]. In food-webs, spatial
+[@thebault_food-web_2003; @oconnor_general_2017]. In food-webs, spatial
 comparisons in empirical and theoretical studies generally reported that trophic
@@
 
-```{r}
-loadd(slope_com_var_no_covar, st_mono_trends_stable_rich_bm)
-```
-```{r}
-nb_st <- unique(slope_com_var_no_covar$station) %>% length
-rm(slope_com_var_no_covar)
-nb_st_rich_bm <- st_mono_trends_stable_rich_bm %>% length
-```
-
 ## Temporal trends of food-web
@@
 types of biomass and species richness trends (i.e. accelerating, decelerating,
-etc...), . Over the `r nb_st` monitored sites, the selection procedure resulted in `r
-nb_st_rich_bm` sites for community biomass and species richness analysis. However, the
+etc...), . Over the `r nb_st` monitored sites, the selection procedure resulted in 
+`r nb_st_rich_bm` sites for community biomass and species richness analysis.
+However, the
 results were robust to the inclusion of non monotonic trends (Fig. SXX).
@@
 
+```{r}
+
+fig_mat_cap <- paste0( "Using  sites of stream fishes in French streams that
+  have been monitored at least 10 years, 1) we infered the food-web at each site
+and each sampling event based on ontogenic food diet information for each
+species and predator-prey body size ratio. 2) We computed the temporal trends
+and the median of community biomass, species richness, connectance, average
+trophic level and evenness of biomass at each site. 3) We then assessed the
+relationships among a) temporal trends of food-web structure. We also assessed
+the spatial relationships among median food-web structure while controlling for
+the environmental gradient with two axis of a rotated PCA. The first axis of the
+PCA is related to the stream gradient from upstream to downstream while the
+second is related to enrichment (BOD) and site altitude (error on the PCA,
+  station is present!!!).")
+
+```
+
+```{r matmet, fig.cap=fig_mat_cap, out.width="80%"}
+knitr::include_graphics(get_mypath("figures", "mat_met_inkscape.pdf"))
+```
+
 # Results
@@
 #sum(stable_st_var[["log_rich_std"]] %in% stable_st_var[["log_bm_std"]] == TRUE) / length(stable_st_var[["log_rich_std"]])
+```
+
+```{r}
+loadd(std_table_bm_rich_mono_stable_trends)
+std <-
+  std_table_bm_rich_mono_stable_trends %>%
+  mutate(
+    type = recode(type, spatial = "sp", temporal = "tps"),
+    response = recode(response, log_bm_std = "bm", log_rich_std = "rich", ct_ff
+      = "ct", piel_bm = "p_bm", piel_nind = "p_n", w_trph_lvl_avg = "tlvl"),
+    term = recode(term, log_bm_std = "bm", log_rich_std = "rich")
+    ) %>%
+  rename(t = type, rep = response, sest = std_estimate) %>%
+  mutate_at(vars(sest, stdse), ~round(.x, 2))
+tps_bm <- std %>%
+  filter(t == "tps", term == "bm")
+
+tps_bm_sest <- tps_bm$sest
+names(tps_bm_sest) <- tps_bm$rep
+```
+
+```{r}
+tps_r <- std %>%
+  filter(t == "tps", term == "rich")
+
+tps_r_sest <- tps_r$sest
+names(tps_r_sest) <- tps_r$rep
+```
+
+```{r}
+sp_b <- std %>%
+  filter(t == "sp", term == "bm")
+sp_b_sest <- sp_b$sest
+names(sp_b_sest) <- sp_b$rep
+
+sp_r <- std %>%
+  filter(t == "sp", term == "rich")
+sp_r_sest <- sp_r$sest
+names(sp_r_sest) <- sp_r$rep
 ```
@@
 \@ref(tab:rsq-sp)), $R_{cond}^2$ being the $R^2$conditional to the random effect.
+
 ---
@@
 ```{r}
-loadd(std_table_bm_rich_mono_stable_trends)
-std <-
-  std_table_bm_rich_mono_stable_trends %>%
-  mutate(
-    type = recode(type, spatial = "sp", temporal = "tps"),
-    response = recode(response, log_bm_std = "bm", log_rich_std = "rich", ct_ff
-      = "ct", piel_bm = "p_bm", piel_nind = "p_n", w_trph_lvl_avg = "tlvl"),
-    term = recode(term, log_bm_std = "bm", log_rich_std = "rich")
+loadd(sp_fig1_2_bm_rich_mono_stable_trends,
+  pred_bm_rich_mono_stable_trends)
+
+fig1_2 <- get_plot_rich_bm(
+  predict_plot = pred_bm_rich_mono_stable_trends,
+  get_list = TRUE,
+  rm_legend = FALSE,
+  bm_x = "log_bm_std",
+  bm_y = c("ct_ff", "w_trph_lvl_avg", "piel_bm"), #, "piel_nind"
+  rich_y = c("ct_ff", "w_trph_lvl_avg", "log_bm_std", "piel_bm"), #, "piel_nind"
+  rich_x = "log_rich_std"
+  )
+p_bm <- fig1_2$bm
+names(p_bm) <- c("ct_ff", "w_trph_lvl_avg", "piel_bm")
+#plot_grid(plotlist = p_bm)
+
+p_sp_bm <- sp_fig1_2_bm_rich_mono_stable_trends$bm
+names(p_sp_bm) <- c("log_rich_std", "ct_ff", "w_trph_lvl_avg",
+  "piel_bm", "piel_nind")
+```
+
+```{r}
+fig_bef_cap <- paste0(
+  "Relationship between the temporal trends of community biomass 
+  and the one of species richness. Red line correspond to the predictions of the
+  linear models. The lines surrounding points display the standard error
+  associated to the temporal trends. The histograms display the distribution of
+  response and predictive variables."
+)
+```
+
+```{r}
+library(ggExtra)
+coeff_bef <- c(
+  rsq = rsq_table_bm_rich_mono_stable_trends %>%
+    filter(Response == "log_bm_std") %$%
+    unlist(.[, c("R.squared")]),
+  reg_table_bm_rich_mono_stable_trends %>%
+    filter(response == "log_bm_std", term == "log_rich_std") %$%
+    unlist(.[, c("estimate", "std.error", "std_estimate", "stdse")])
   ) %>%
-  rename(t = type, rep = response, sest = std_estimate) %>%
-  mutate_at(vars(sest, stdse), ~round(.x, 2))
-tps_bm <- std %>%
-  filter(t == "tps", term == "bm")
-
-tps_bm_sest <- tps_bm$sest
-names(tps_bm_sest) <- tps_bm$rep
-```
-
-```{r}
-tps_r <- std %>%
-  filter(t == "tps", term == "rich")
-
-tps_r_sest <- tps_r$sest
-names(tps_r_sest) <- tps_r$rep
-```
-
-```{r}
-sp_b <- std %>%
-  filter(t == "sp", term == "bm")
-sp_b_sest <- sp_b$sest
-names(sp_b_sest) <- sp_b$rep
-
-sp_r <- std %>%
-  filter(t == "sp", term == "rich")
-sp_r_sest <- sp_r$sest
-names(sp_r_sest) <- sp_r$rep
+round(., 2)
+
+beta_rsq <- function(
+  rsq = NULL,
+  beta = NULL,
+  se = NULL) {
+
+  tmp <- "paste(
+  beta, \" (s.e) \", \" = \",
+  mybeta, \" (\", myse, \"), \",
+
+  italic(R)^2, \" = \", myrsq
+  )"
+
+str_replace_all(tmp,
+  c(
+    "myrsq" =  as.character(rsq),
+    "mybeta" = as.character(beta),
+    "myse" = as.character(se)
+  )
+)
+
+}
+```
+
+```{r bef, fig.cap=fig_bef_cap, out.width="50%"}
+p_bef <- fig1_2$rich$log_bm_std +
+  annotate("text", x = -.05, y = .3, parse = T,
+    label = beta_rsq(rsq = coeff_bef["rsq"],
+      beta = coeff_bef["estimate"], se =
+        coeff_bef["std.error"])
+   ) +
+  labs(
+    y = "Log community biomass (g per year)",
+    x = "Log species richness (per year)"
+  )
+
+ggMarginal(p_bef, type = "histogram")
 ```
@@
 
-# Discussion
-
-## Species richness and community biomass are positively linked in space and time
-
-Spatially and temporally, species richness scaled positively with community
-biomass. Spatially, this result is in accordance 
-with previous studies in stream communities [@woods_testing_2020; @danet_species_nodate] but also
-in grasslands, salt marches and forests [@hector_plant_1999;
-@tilman_biodiversity_2014; @wu_relationship_2015; @li_relationship_2018; but see
-@grace_integrative_2016]. Therefore, our results confirm that
-Biodiversity-Ecosystem functioning prediction
-works also in the temporal dynamics of food-webs. The positive relationship between species
-richness and total biomass might be due to positive complementarity in resource
-use [@carey_determining_2011], which is held by niche differentiation
-[@loreau_biodiversity_1998; @loreau_partitioning_2001] or to the higher
-probability of getting high biomass species with higher species richness
-[@loreau_biodiversity_2001].
-
-## The temporal of community biomass and species richness relates on different assembly and disassembly rules
-
-While we found a strong relationship between the temporal trends of community
-biomass and the one of species richness, our results suggest that temporal trends in
-community biomass and species richness are associated with very different temporal trends on the
-connectance, average trophic level and evenness of biomass. Indeed, temporal trends of connectance and average
-trophic level were positively associated to the temporal trends of community biomass while no
-significant association was found with temporal trends of species richness.
-Moreover, the temporal trends of biomass evenness were negatively associated to the temporal
-trends of community biomass whereas positively associated to temporal trends of
-species richness. All together, it suggests that temporal trends of community
-biomass and species richness are related to different assembly and disassembly
-processes in food-webs.
-
-The temporal trends of connectance were positively linked to that of community
-biomass, meaning that when connectance increased through time in a given site
-when community biomass increased through time. Reversely, connectance decreased
-in food-webs when community biomass decreased through time. It suggests that
-community biomass losses and gains are associated to losses and gains in large
-bodied predators. This interpretation is in line with the results that community
-biomass losses through time were associated to a temporal decrease of average
-trophic level and that community biomass temporal gains were associated to
-temporal increase of average trophic level. Another piece of evidence is that
-evenness of biomass, measured by the Pielou index, decreased through time as
-community biomass increased, meaning that biomass distribution across species
-becomes less even when community biomass increased. Reversely, in food-webs that
-displayed temporal decrease in community biomass, we found that evenness of
-biomass increased, i.e. that biomass distribution across species becomes more
-even.  Because predator-prey interactions relate in part on bodysize and thus
-bodymass to a certain extent, we may expect that a given gain in predators of
-higher trophic level leads to a decrease of biomass evenness and reversely. In
-the same line, we found that the temporal trends of community biomass were positively
-correlated to the temporal trends of the number and proportion of piscivorous
-trophic species present in fish communities (Fig. SXX).
-
-In contrast, we found that temporal trends of connectance and average trophic level
-were not related to the temporal trends of species richness. However, we found
-that temporal trends of the number of piscivorous species and piscivorous
-trophic species were strongly positively linked to the temporal trends of
-species richness (Fig. S3). It suggests that the temporal decrease of species
-richness observed in our data are concomimant to losses of
-piscivorous and non-piscivorous species, leading to the absence of temporal
-trends in connectance and average trophic level and symmetrically for the
-temporal increase of species richness. Furthemore, we found that the temporal
-trends of biomass evenness had a positive relationship with the one of species
-richness, in contraction of what we found for temporal trends of community biomass.
-Together with the fact that species richness temporal trends had a positive
-relationship with the temporal trends of community biomass, it suggests that
-positive and negative  temporal trends of species richness are linked to gains and
-losses of redundancy in food-webs, without overall effects on connectance
-and average trophic level.
-
-## Space-for-time substitution does not always hold
-
-In time and along spatial gradient, we found that connectance was positively
-linked to community biomass. This result is also in accordance with theoretical
-work showing that higher food-web connectance can result in higher community
-biomass [@thebault_food-web_2003], but other display negative relationship
-[@poisot_trophic_2013], highlighting that the relation between connectance and
-community biomass may be dependant of assembly processes at work.]. In the same
-line, we found that average trophic level had a positive relationship with
-community biomass in space and time. It is in accordance with a theoretical
-model showing that the presence of higher predators can lead to higher community
-biomass [@wang_biodiversity_2018].  We also found in space and time that
-evenness of biomass was negatively related to community biomass. This result is
-in accordance with the observation of top-heavy shape of biomass pyramids in
-food-webs, particularly in freshwater systems [@mccauley_prevalence_2018]. Many
-mechanisms can be responsible have been invoked to explain this pattern but
-omnivory, which is present in most of piscivorous species in our dataset, may
-favor this shape by increasing food transfer efficiency toward higher trophic
-level.
-
-Surprisingly, we found that the temporal trends of connectance was not related
-to the one of species richness as found spatially in most empirical food-web
-[@dunne_network_2006] and also in the present study. We explained this pattern
-by the fact that the temporal variation of species richness in our dataset seems
-to be linked to variation in the level of redundancy in the role in the
-food-webs rather than overall change of the vertical structure of food-webs. The
-same rational can applied with average trophic level. *This discrependacy might
-be due to the crucial assumptions that variations in space will correspond to
-differences of assembly stages and then reflect the assembly/disassembly
-trajectories in time of communities. Temporal variation of species richness
-might relate on transitory dynamics while spatial gradient reflect aggregated
-dynamics over longer time scale including a far number of processes including
-high species turnover along spatial gradient.* This result is in line with other
-studies which found mismatch between spatial and temporal patterns
-[@adler_contrasting_2007; @johnson_testing_2008].  
-However, we found agreement between space and time analysis for the positive
-relationship between evenness of biomass and species richness. Another reason
-might be that the spatial gradient displays a higher range of variation for
-species richness than the temporal stations (Fig. S2). However, it might not
-explain why we found strong relationships between the temporal trend of species
-richness from one side and the temporal trends of community biomass, biomass
-evenness, the number of piscivore species (Fig. S3). *No more idea, need
-coffee*.
-
-However, our result that food-web structure does not change a lot with temporal
-variation of species richness is in line with the insurance hypothesis
-[@yachi_biodiversity_1999]. In this view, the temporal loss and gain of species
-richness represent respectively loss and gain of redundancy in the
-food-web structure. Our results have profound implications for conservation. As
-more and more studies reported community biomass and species richness trends
-[@hallmann_more_2017; @ceballos_biological_2017], we documented that they might
-not be equivalent in terms of consequences on the structure of the community. In
-particular, the loss of the highest trophic level associated to the loss of
-community biomass could have dramatic consequences on ecosystem functioning
-as the highest predators are prone to stabilise communities
-[@shanafelt_stability_2018; @danet_species_nodate]. In contrasts, the loss of
-species richness might be linked to loss of redundancy in the food-web,
-highlighting that those communities may become more at risk regarding future
-perturbations [@yachi_biodiversity_1999]. Overall, it suggests that monitoring
-several facets of biodiversity is essential to infer how ecological communities
-are reshaped by loss and gain of biomass and species richness.
-
-We further found that most temporal trends of food-webs were classified as
-stable for species richness and community biomass. We found almost the same
-number of stations that displayed temporal decrease or increase for species
-richness, and twice more stations displayed decrease in community biomass than
-increase. While, the spatial coverage of our data is good, it would be rather
-risky to conclude about biodiversity trends in freshwater fish communities in
-France. Mainly because we did not assess pressures that may affect
-the temporal trends such as land-use changes and species invasions
-[@comte_climate_2021; @su_human_2021].
-
----
-### Biomass and richness gains and losses are symmetric processes in terms of community structure
-#
-#We found no case in which gain or losses of biomass and richness lead to
-#different relationship between the temporal dynamic of community structure and
-#the one of biomass and species richness. We could have imagined that
-#extinction/colonisation processes or immigration/extinction debt could have lead
-to different relationships.
----
-
-## Conclusion and perspectives
-
-Our study suggests that richness and biomass temporal trends in natural fish
-communities relate on different ecological processes, biomass temporal dynamics
-being related to variations of at highest trophic levels while species richness
-impacts redundancy of food-web structure. Our result also suggests that space
-for time substitution may be relevant to predict the effects of community
-biomass losses or gains on food-web structure. However, it might not the case
-for species richness temporal variation. We look forward to next investigations
-to see the generality of assembly rules in food-webs. There are crucial to
-better understand the temporal dynamics of food-web structure and then its
-impact on ecosystem functioning.
-
-# References  {-}
-
-<div id="refs"></div>
-
-\newpage
-
-# Figures {-}
-
-```{r}
-fig_mat_cap <- paste0(
-  "(A) Distribution of the fishing sites. (B-F) Temporal trends of biomass,
-  species richness, connectance, average trophic level and evenness of biomass
-  for two stations. (À retravailler)"
-)
-```
-```{r matmet, fig.cap=fig_mat_cap, out.width="100%"}
-knitr::include_graphics(get_mypath("figures", "mat_met_inkscape.pdf"))
-```
-
 ```{r}
@@
   median community biomass over time."
-
 )
@@
 ```{r}
-loadd(sp_fig1_2_bm_rich_mono_stable_trends,
-  pred_bm_rich_mono_stable_trends)
-
-fig1_2 <- get_plot_rich_bm(
-  predict_plot = pred_bm_rich_mono_stable_trends,
-  get_list = TRUE,
-  rm_legend = FALSE,
-  bm_x = "log_bm_std",
-  bm_y = c("ct_ff", "w_trph_lvl_avg", "piel_bm"), #, "piel_nind"
-  rich_y = c("ct_ff", "w_trph_lvl_avg", "log_bm_std", "piel_bm"), #, "piel_nind"
-  rich_x = "log_rich_std"
-  )
-p_bm <- fig1_2$bm
-names(p_bm) <- c("ct_ff", "w_trph_lvl_avg", "piel_bm")
-#plot_grid(plotlist = p_bm)
-
-p_sp_bm <- sp_fig1_2_bm_rich_mono_stable_trends$bm
-names(p_sp_bm) <- c("log_rich_std", "ct_ff", "w_trph_lvl_avg",
-  "piel_bm", "piel_nind")
-```
-
-```{r}
-fig_bef_cap <- paste0(
-  "Relationship between the temporal trends of community structure
-  and the one of species richness. Lines correspond to the predictions of the
-  linear models. The lines surrounding each point represent the standard error
-  associated to the temporal trends."
-)
-```
-```{r bef, fig.cap=fig_bef_cap}
-library(ggExtra)
-ggMarginal(fig1_2$rich$log_bm_std, type = "histogram")
-```
-
-```{r}
 fig_bm_rich_cap <- paste0(
-  "Relationship among the temporal trends of community structure
-  and the one of species richness and community biomass. The lines
-  surrounding each point represent the standard error associated to the temporal
-  trends."
-)
-```
-```{r bmr, out.width = "100%", fig.cap=fig_bm_rich_cap}
+  "Relationships between the temporal trends of food-web structure
+  and the ones of community biomass (left panel) species richness (right panel).
+  The lines surrounding each point display the standard errors associated to
+  the estimated temporal trends. Red and black lines represent respectively
+  significant relationships. The histograms display the distribution of
+  response and predictive variables.")
+```
+
+```{r}
 fig2 <- fig1_2
@@
 fig2$rich <- map(fig2$rich,
-  ~ .x +
-    theme(axis.text = element_text(size = 6),
-    axis.title = element_text(size = 8))
-  )
-fig2$bm <- map(fig2$bm,
+  ~.x +
+    theme(
+      axis.text = element_text(size = 6),
+      axis.title = element_text(size = 8)
+      )
+  )
+fig2$bm <- map2(fig2$bm, names(fig2$rich),
   ~ .x + theme(
@@
     axis.title = element_text(size = 8)
+    ) +
+  labs(
+    y = paste0(var_replacement()[.y],
+      "\ntrends (per year)"),
+    x = paste0("Log biomass",
+      "\ntrends (per year)"),
+  )
+)
+# Delete redondant legend
+fig2$bm[1:2] <- map(fig2$bm[1:2],
+  ~ .x + theme(
+    axis.text.x = element_blank(),
+    axis.ticks.x = element_blank(),
+    axis.title.x = element_blank()
+  )
+  )
+
+fig2$rich <- map(fig2$rich,
+  ~ .x + theme(
+    axis.text.y = element_blank(),
+    axis.ticks.y = element_blank(),
+    axis.title.y = element_blank()
+  ) +
+  labs(x = paste0("Log species richness",
+      "\ntrends (per year)"))
+  )
+fig2$rich[1:2] <- map(fig2$rich[1:2],
+  ~ .x + theme(
+    axis.text.x = element_blank(),
+    axis.ticks.x = element_blank(),
+    axis.title.x = element_blank()
   )
@@
 # Add histograms
-fig2$bm <- map(fig2$bm,~ggMarginal(.x, type = "histogram"))
-fig2$rich <- map(fig2$rich,~ggMarginal(.x, type = "histogram"))
-
+fig2$bm[[1]] <- ggMarginal(fig2$bm[[1]], type = "histogram", margins = "x")
+fig2$rich[[1]] <- ggMarginal(fig2$rich[[1]], type = "histogram", margins = "both")
+fig2$rich[2:3] <- map(fig2$rich[2:3], ~ggMarginal(.x, type = "histogram", margins = "y"))
+
+```
+
+```{r bmr, out.width="70%", fig.height=7, fig.cap=fig_bm_rich_cap}
 plot_grid(
-  plot_grid(plotlist = fig2$bm, nrow = 1, labels = c("A", "B", "C")),
-  plot_grid(plotlist = fig2$rich, nrow = 1, labels = c("D", "E", "F")),
-  nrow = 2
-)
-```
-
-```{r bm, eval=FALSE, fig.height = 12, fig.cap=fig_bm_cap}
-ti <- list()
-for (
-  i in c("log_rich_std", "w_trph_lvl_avg", "piel_bm", "piel_nind", "ct_ff")
-  ) {
-  ti[[i]] <- list(p_bm[[i]], p_sp_bm[[i]])
-}
-
-# Make the label on two lines
-fig1 <- plot_grid(plotlist = c(ti[[1]], ti[[2]], ti[[3]], ti[[4]], ti[[5]]), ncol = 2)
-fig1
-```
-
-```{r}
-p_rich <- fig1_2$rich
-p_sp_rich <- sp_fig1_2_bm_rich_mono_stable_trends$rich
-```
-
-```{r rich, eval=FALSE,fig.height = 12, fig.cap=fig_rich_cap}
-trich <- list()
-for (i in c("log_bm_std", "w_trph_lvl_avg",  "piel_bm", "piel_nind", "ct_ff")) {
-  trich[[i]] <- list(p_rich[[i]], p_sp_rich[[i]])
-}
-
-# Make the label on two lines
-fig2 <- plot_grid(
-  plotlist = c(trich[[1]], trich[[2]], trich[[3]], trich[[4]], trich[[5]]),
-  ncol = 2)
-fig2
+  plot_grid(plotlist = fig2$bm,
+    ncol = 1, labels = c("A", "B", "C"),
+    hjust = -5.5, vjust = 1.75
+    ),
+  plot_grid(plotlist = fig2$rich,
+    ncol = 1, labels = c("D", "E", "F"),
+    hjust = -2, vjust = 1.75
+    ),
+  ncol = 2,
+  rel_widths = c(1, 1)
+)
 ```
@@
 std_cap <- paste0(
-  "Standardized coefficients of the effects of community biomass and species
-  richness on food-web structure for the temporal and spatial models. The lines
-  display the standard errors."
-)
-```
-
-```{r std, fig.cap=std_cap}
-loadd(fig_std_coef)
-fig_std_coef
-```
+  "Assessment of the space-for-time hypothesis. Effect of community biomass (top
+  panel) and species richness (bottom panel) on food-web structure for the
+temporal and spatial models. Top of
+  bars display the standardized coefficients from the linear models, the lines
+  around display the standard errors.")
+```
+
+```{r std, fig.cap=std_cap, fig.width=6}
+#loadd(fig_std_coef)
+std_table_bm_rich_mono_stable_trends %>%
+  filter(
+    term %in% c("log_rich_std", "log_bm_std"),
+    !response %in% "piel_nind") %>%
+  mutate_at(vars(term, response), ~str_replace_all(., var_replacement(
+        several_lines = TRUE))) %>%
+  mutate(
+    type = str_to_sentence(type),
+    type = factor(type, levels = c("Temporal", "Spatial"))) %>%
+  ggplot(aes(y = std_estimate, x = response, fill = type)) +
+  viridis::scale_fill_viridis(begin = 0.5, end = 1, discrete = TRUE) +
+  facet_grid(rows = vars(term)) +
+  geom_col(position = position_dodge(width = .9)) +
+  geom_linerange(aes(ymin = std_estimate - stdse, ymax = std_estimate + stdse),
+    position = position_dodge(width = .9)) +
+  labs(x = "Response variables", y = "Standardized slopes", fill = "Model") +
+  theme(legend.position = c(0.7, .1),
+    legend.direction = "horizontal",
+    text = element_text(size = 8), axis.text = element_text(size = 8)) +
+  scale_y_continuous(sec.axis = sec_axis(~ ., name = "Predictive variable",
+      breaks = NULL, labels = NULL))
+```
+
+# Discussion
+
+We further found that most temporal trends of food-webs were classified as
+stable for species richness and community biomass. We found almost the same
+number of stations that displayed temporal decrease or increase for species
+richness, and twice more stations displayed decrease in community biomass than
+increase. This result is in accordance with previous meta analysis on species
+richness trends of vertebrate in marine, freshwater and terrestrial systems
+[@dornelas_assemblage_2014; @blowes_geography_2019; @klink_meta-analysis_2020].
+While the spatial coverage of our data is good, it would be rather risky to
+conclude about biodiversity trends in freshwater fish communities because we did
+not assess pressures that may affect the temporal trends such as land-use
+changes and species invasions [@comte_climate_2021; @su_human_2021;
+@cardinale_is_2018].
+
+## Species richness and community biomass are positively linked in space and time
+
+Spatially and temporally, species richness scaled positively with community
+biomass. Spatially, this result is in accordance with previous studies in stream
+communities [@woods_testing_2020; @danet_species_nodate] but also in grasslands,
+salt marches and forests [@hector_plant_1999; @tilman_biodiversity_2014;
+@wu_relationship_2015; @li_relationship_2018; but see @grace_integrative_2016].
+Therefore, our results confirm that Biodiversity-Ecosystem functioning
+prediction works also in the temporal dynamics of food-webs. The positive
+relationship between species richness and total biomass might be due to positive
+complementarity in resource use [@carey_determining_2011], which is held by
+niche differentiation [@loreau_biodiversity_1998; @loreau_partitioning_2001] or
+to the higher probability of getting high biomass species with higher species
+richness [@loreau_biodiversity_2001].
+
+## Food-web structure changes according to the temporal trends of community biomass and species richness
+
+While we found a strong relationship between the temporal trends of community
+biomass and the one of species richness, our results suggest that temporal
+trends in community biomass and species richness are associated with very
+different temporal trends on the connectance, average trophic level and evenness
+of biomass. Indeed, temporal trends of connectance and average trophic level
+were positively associated to the temporal trends of community biomass while no
+significant association was found with temporal trends of species richness.
+Moreover, the temporal trends of biomass evenness were negatively associated to
+the temporal trends of community biomass whereas positively associated to
+temporal trends of species richness. All together, it suggests that temporal
+trends of community biomass and species richness are related to different
+assembly and disassembly processes in food-webs.
+
+The temporal trends of connectance were positively linked to that of community
+biomass, meaning that when connectance increased through time when community
+biomass increased through time in a given site. Reversely, connectance decreased
+in food-webs when community biomass decreased through time. It suggests that
+community biomass losses and gains are associated to losses and gains in large
+bodied piscivores. This interpretation is in
+line with the results that community biomass losses through time were associated
+to a temporal decrease of average trophic level and that community biomass
+temporal gains were associated to temporal increase of average trophic level.
+Another piece of evidence is that evenness of biomass, measured by the Pielou
+index, decreased through time as community biomass increased, meaning that
+biomass distribution across species becomes less even when community biomass
+increased. Reversely, in food-webs that displayed temporal decrease in community
+biomass, we found that evenness of biomass increased, i.e. that biomass
+distribution across species becomes more even. Because predator-prey
+interactions relate in part on bodysize and thus bodymass to a certain extent,
+we may expect that a given gain in predators of higher trophic level leads to a
+decrease of biomass evenness and reversely. In the same line, we found that the
+temporal trends of community biomass were positively accociated to the temporal
+trends of the number and proportion of piscivorous trophic species present in
+fish communities (Fig. SXX).
+
+In contrast, we found that temporal trends of connectance and average trophic
+level were not related to the temporal trends of species richness. However, we
+found that temporal trends of the number of piscivorous species and piscivorous
+trophic species were positively associated to the temporal trends of species
+richness (Fig. S3). It suggests that the temporal decrease of species richness
+observed in our data are concomimant to losses of piscivorous and
+non-piscivorous species, leading to the absence of temporal trends in
+connectance and average trophic level and symmetrically for the temporal
+increase of species richness. Furthemore, we found that the temporal trends of
+biomass evenness had a positive relationship with the one of species richness,
+in contradiction of what we found for temporal trends of community biomass.
+Together with the fact that species richness temporal trends had a positive
+relationship with the temporal trends of community biomass, it suggests that
+positive and negative  temporal trends of species richness are linked to gains
+and losses of redundancy in food-webs, without overall effects on connectance
+and average trophic level. This is in line with the insurance hypothesis
+[@yachi_biodiversity_1999] which predicts the temporal loss and gain of species
+richness represent respectively loss and gain of redundancy in the community,
+here in the food-web structure.
+
+As studies reported community biomass or species richness temporal trends
+[@hallmann_more_2017; @ceballos_biological_2017; @dornelas_assemblage_2014;
+@blowes_geography_2019], we document that temporal trends of species richness
+and community biomass might have different consequences on the structure of the
+community. In particular, the decrease of the average trophic level associated
+to the loss of community biomass could have cascading effect on ecosystem
+functioning as the highest predators are predicted to increase productivity and
+stabilise communities [@wang_biodiversity_2018; @shanafelt_stability_2018;
+@danet_species_nodate]. In contrasts, the loss of species richness might be
+linked to loss of redundancy in the food-web, highlighting that those
+communities may become more at risk regarding future perturbations
+[@yachi_biodiversity_1999]. Overall, it suggests that monitoring several facets
+of community structure is essential to infer how ecological communities are
+reshaped by loss and gain of biomass and species richness.
+
+## Space-for-time substitution does not always hold
+
+In time and space, we found that connectance was positively linked to community
+biomass. This result is also in accordance with theoretical work showing that
+higher food-web connectance can result in higher community biomass
+[@thebault_food-web_2003], or lower [@poisot_trophic_2013], highlighting that
+the relation between connectance and community biomass may be dependant on how
+food-web structure change with community biomass. Likewise, we found that
+average trophic level had a positive relationship with community biomass in
+space and time, in accordance with a theoretical study predicting an increase of
+community biomass subsequent to the presence of higher predators
+[@wang_biodiversity_2018]. We also found that biomass evenness was negatively
+related to community biomass in space and time. This result is in accordance
+with the reported top-heavy shape of biomass pyramids in food-webs,
+particularly in freshwater systems [@mccauley_prevalence_2018]. Many mechanisms
+have been invoked to explain this pattern but omnivory, which
+is present in most of piscivorous species in our dataset, may favor this shape
+by increasing food transfer efficiency toward the higher trophic levels.
+
+Surprisingly, we found that the temporal trends of connectance were not related
+to the one of species richness as found spatially in most empirical food-webs
+[@dunne_network_2006] and also here. We explained this pattern by the fact that
+the temporal variation of species richness in our dataset seems to be linked to
+temporal variation of redundancy level in the structure of food-webs rather than
+overall change of their vertical structure. The same rational can applied with
+average trophic level. This result is in line with other studies which found
+mismatch between spatial and temporal patterns [@adler_contrasting_2007;
+@johnson_testing_2008]. This discrepency in space and time might be due to the
+crucial assumption that variations in space reflect differences in assembly
+stages of ecological communities and then mirrors their temporal
+assembly/disassembly trajectories. Temporal variation of species richness might
+relate on transitory dynamics while spatial gradient reflect aggregated dynamics
+over longer time scale including a far number of processes including high
+species turnover along spatial gradient. However, we fount that the positive
+relationship between evenness of biomass and species richness were consistent in
+space and time. Another reason might be that the spatial gradient displays a
+higher range of variation for species richness than the temporal stations (Fig.
+S2). However, we found strong relationships between the temporal trend of
+species richness from one side and the temporal trends of community biomass,
+biomass evenness, and the number of piscivore species from the other side (Fig. S3).
+
+---
+### Biomass and richness gains and losses are symmetric processes in terms of community structure
+#
+#We found no case in which gain or losses of biomass and richness lead to
+#different relationship between the temporal dynamic of community structure and
+#the one of biomass and species richness. We could have imagined that
+#extinction/colonisation processes or immigration/extinction debt could have lead
+to different relationships.
+---
+
+## Conclusion and perspectives
+
+Our study suggests that richness and biomass temporal trends in natural fish
+communities relate on different ecological processes, biomass temporal dynamics
+being related to variations of food-web structure at the higher trophic levels
+while species richness impacts redundancy of species in food-web structure. Our
+result also suggests that space for time substitution may be relevant to predict
+the effects of community biomass losses or gains on food-web structure. However,
+our findings suggest that space-for-time substitution might not work for species
+richness. Our study calls for further investigations to support the generality of
+assembly rules in food-webs. They are crucial to better understand the
+assembly and disassembly of food-web and then predict its impact on ecosystem
+functioning.
+
+# References  {-}
+
+<div id="refs"></div>
+
+\newpage
 
@@
 ```{r}
-loadd(reg_table_bm_rich_mono_stable_trends)
 reg_table_bm_rich_mono_stable_trends %>%
@@
 ```{r}
-loadd(rsq_table_bm_rich_mono_stable_trends)
-rsq_table_bm_rich_mono_stable_trends %>%
+table_rsq_tps <- rsq_table_bm_rich_mono_stable_trends %>%
   mutate(
     Response = str_replace_all(Response, var_replacement())
-  ) %>%
+  )
+table_rsq_tps %>%
   kable(., booktabs = TRUE,

### 2022-02-22 paper/method_figure.Rmd
Update figures

@@
 save_plot(
-  get_mypath("figures/decreasing_biomass_network.png"),
+  get_mypath("figures/decreasing_biomass_network.pdf"),
   g,
@@
 save_plot(
-  get_mypath("figures/decreasing_biomass.png"), tps_bm_dec,
+  get_mypath("figures/decreasing_biomass.pdf"), tps_bm_dec,
   nrow = 1,
@@
 save_plot(
-  get_mypath("figures/increasing_biomass.png"), tps_bm_inc,
+  get_mypath("figures/increasing_biomass.pdf"), tps_bm_inc,
   nrow = 1,
@@
   var = "ct_ff",
-  st = 15818) {
+  st = 15818,
+  col_trend = "black",
+  add_median = TRUE,
+  col_median = "blue",
+  size_line = 1
+  ) {
   tex <- .df %>%
@@
 
-    tex %>%
+    p <- tex %>%
       ggplot(aes_string(x = "year", y = var)) +
       geom_point() +
-      geom_smooth(aes(group = station), method = "lm", formula = y ~ x,
-        size = 1, se = FALSE, color = "black") +
+      geom_smooth(
+        aes(group = station), method = "lm", formula = y ~ x,
+        size = size_line, se = FALSE, color = col_trend) +
       labs(x = "Year", y = str_replace_all(var, var_replacement()))
 
+    if (add_median) {
+
+      p <- p + 
+        geom_hline(yintercept = median(tex[[var]]), col = col_median, size =
+          size_line)
+    }
+    return(p)
 }
@@
 ```{r}
+color_tes <- map(dec_representative$station,
+  ~set_color_species(
+  node_list = community_metrics %>%
+  filter(station == .x) %$%
+  .$sp_vector %>%
+  reduce(., c) %>%
+  names(.) %>%
+  unique(),
+  resource_list = metaweb_analysis$resource,
+  col_resource = NULL
+  )
+)
+names(color_tes) <- as.character(dec_representative$station)
+
 tes <- map(dec_representative$station, ~plot_dyn_web(
@@
     stacked = TRUE,
-    color_species = NULL 
+    color_species = color_tes[[as.character(.x)]]
     ))
+
+names(tes) <- as.character(dec_representative$station)
 plot_grid(plotlist = tes)
@@
 ```{r}
+
 st_decreasing <- dec_representative$station[3]
 
-p_dec_log_bm <- tes[[3]] +
+p_dec_log_bm <- tes[[as.character(st_decreasing)]] +
   labs(color = "Species", fill = "Species") +
-  theme(legend.position = "bottom")
+  theme(legend.position = c(.2, .8), legend.direction = "horizontal")
 
 save_plot(
-  get_mypath("figures/p_dec_log_bm.png"),
+  get_mypath("figures/p_dec_log_bm.pdf"),
   p_dec_log_bm,
@@
   ncol = 1,
-  base_asp = 1.618,
-  base_width = 7)
+  base_height = 6.6,
+  base_asp = 1.2
+  )
 ```
 ```{r}
-tps_dec_inc <- map(c("ct_ff", "w_trph_lvl_avg", "log_rich_std", "piel_bm"),
-  ~plot_temporal_variable_lm(st = st_decreasing, var = .x)
+v_colors =  viridis(n = 2, begin = 0.5, end = 1)
+names(v_colors) <- c("tps", "sp")
+
+tps_dec_inc <- map(c("log_bm_std", "log_rich_std", "ct_ff", "w_trph_lvl_avg", "piel_bm"), # 
+  ~plot_temporal_variable_lm(st = st_decreasing, var = .x, col_median =
+    v_colors["sp"], col_trend = v_colors["tps"]) +
+    theme(axis.title = element_text(size = 12))
 )
+# Increase point size
+tps_dec_inc  <- map(tps_dec_inc, function(x) {
+  x$layers[[1]]$aes_params$size <- 4
+  return(x)
+})
+
+# Delete x axis
+#tps_dec_inc[-length(tps_dec_inc)]  <- map(tps_dec_inc[-length(tps_dec_inc)], function(x) {
+#  x + theme(
+#    axis.text.x = element_blank(),
+#    axis.ticks.x = element_blank(),
+#    axis.title.x = element_blank()
+#  )
+#})
+
 save_plot(
-  filename = get_mypath("figures/net_str_dec_bm.png"),
-  plot_grid(plotlist = tps_dec_inc),
-  nrow = 2, ncol = 2,
-  base_asp = 1.618,
-  base_width = 5
+  filename = get_mypath("figures/net_str_dec_bm.pdf"),
+  plot_grid(plotlist = tps_dec_inc, nrow = 1, align = "h", axis = "l"),
+  ncol = length(tps_dec_inc), nrow = 1, 
+  base_height = 2.6,
+  base_asp = 1.2 
 )
+theme_get()$text
 ```
+
 ```{r temporal foodwebs}
-
 p <- get_network_temporal_plot(
@@
   station = st_decreasing,
-  selected_years = c(1996, 2006, 2016),
-  node_color = my_species_color, scale_node_size = 0.027,
+  selected_years = c(1995, 2005, 2015),
+  node_color = color_tes[[as.character(st_decreasing)]],
+  scale_node_size = 0.027,
   par_options = par(mar = c(0,0,0,0)),
@@
   g,
-  ncol = 3,
-  base_asp = 1.618,
-  base_width = 7)
+  ncol = 3, nrow = 1,
+  base_width = 7, base_height = 7)
+
 ```
@@
   file = get_mypath("figures", "map_st.png")
+)
+```
+
+```{r}
+loadd(station_analysis, st_mono_trends_stable_rich_bm)
+```
+```{r}
+fr_map <- ne_countries(scale = "medium", returnclass = "sf") %>%
+  filter(geounit == "France") %>%
+  st_transform(crs = 2154)
+st <- station_analysis %>%
+  filter(id %in% st_mono_trends_stable_rich_bm) %>%
+  st_transform(crs = 2154)
+
+p <- ggplot() +
+    geom_sf(data = st_geometry(fr_map), lwd = 0) +
+    geom_sf(data = st_geometry(st)) +
+    coord_sf(
+      xlim = st_bbox(st)[c(1, 3)],
+      ylim = st_bbox(st)[c(2, 4)]
+    ) +
+  theme_bw() +
+  theme(
+    panel.border = element_blank(), panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.ticks = element_blank(), axis.text = element_blank())
+p
+```
+```{r}
+save_plot(
+  p,
+  base_height = 12,
+  base_asp = 1.618,
+  file = get_mypath("figures", "simple_map_matmet.pdf")
 )

### 2022-02-22 R/variable_shortcut.R

@@ -67,8 +67,7 @@ get_model_terms <- function ( ) {
 
 } 
 
-var_replacement <- function (slope = FALSE) {
-
+var_replacement <- function (slope = FALSE, several_lines = FALSE) {
   x <- c(
     log_RC1 = "PCA Avg stream size",
     log_RC2 = "PCA Avg temperature",
@@ -79,9 +78,25 @@ var_replacement <- function (slope = FALSE) {
     log_bm_std = "Log Biomass",
     bm_std = "Biomass",
     rich_std = "Species richness",
-    piel_nind = "Eveness (abundance)",
-    piel_bm = "Eveness (biomass)"
+    piel_nind = "Evenness (abundance)",
+    piel_bm = "Evenness (biomass)"
   )
+
+  if (several_lines) {
+    x <- c(
+      log_RC1 = "PCA\nAvg stream size",
+      log_RC2 = "PCA\n Avg temperature",
+      ct_ff = "Connectance",
+      w_trph_lvl_avg = "Avg\ntrophic level",
+      #connectance ,weighted_connectance,
+      log_rich_std = "Log\nSpecies richness",
+      log_bm_std = "Log Biomass",
+      bm_std = "Biomass",
+      rich_std = "Species\nrichness",
+      piel_nind = "Evenness\n(abundance)",
+      piel_bm = "Evenness\n(biomass)"
+    )
+  }
 
   if (slope) {
     tmp <- names(x)

### 2022-02-23 paper/manuscript.Rmd
Check introduction, matmet and discussion

@@
 ---
-title: "Community biomass and species richness temporal trends reveal contrasting
-    assembly and disassembly processes in natural food-webs"
-author: Alain Danet, Loubna El Madouri, Maud Mouchet, Elisa Thébault and Colin Fontaine (ordre non fixé)
+title: "Community biomass and species richness temporal trends reveal contrasting assembly and disassembly processes in natural food-webs"
+author: Alain Danet, Loubna El Madouri, Maud Mouchet, Elisa Thébault and Colin Fontaine
 date: \today
@@
 [@ceballos_biological_2017; @hallmann_more_2017; @albano_native_2021], as well
-as decrease in species richness [@barnosky_has_2011; @newbold_global_2015] and
-turnover in species composition [@comte_climate_2021]. Unfortunately, studies often
-focus on the temporal trend of one dimension of biodiversity [@hallmann_more_2017,
-etc, but see @]. Because the functioning of ecosystem depends ultimately on
-multiple facets of biodiversity, such as species richness, evenness and
-functional composition^[1]  [REF @thibaut_understanding_2013], the documentation
-of the trend of one biodiversity facet is likely insufficient to evaluate
-precisely its consequences
-on ecosystem functioning.
+as decrease in species richness [@barnosky_has_2011; @newbold_global_2015] but
+also recent studies reported non significant temporal trends in species richness
+[@vellend_global_2013; @dornelas_assemblage_2014; @blowes_geography_2019], total
+abundance [@klink_meta-analysis_2020], high turnover in species composition
+[@dornelas_assemblage_2014; @blowes_geography_2019]. Unfortunately, studies
+often focus on the temporal trend of one dimension of biodiversity
+[@hallmann_more_2017; @klink_meta-analysis_2020, but see 2 in
+@dornelas_assemblage_2014; @blowes_geography_2019]. However biodiversity is a
+multidimensional concept and the functioning of ecosystem depends ultimately on
+several dimensions of biodiversity, such as species richness, evenness and
+functional composition^[1]  [@cardinale_biodiversity_2012; @duffy_why_2009], the
+documentation of the trend of one biodiversity facet is likely insufficient to
+understand changes in community structure and ultimately predict their
+consequences on ecosystem functioning.
 
@@
 
-Current knowledge on the links among different facets of biodiversity mainly
-comes from from spatial comparison [@dunne_network_2006;
-@soininen_relationship_2012; @grace_integrative_2016; @danet_species_nodate]. space-for-time substitution began to be widely
-used in the early 20th century to infer the temporal succession of vegetation
-from space variations [@pickett_space-for-time_1989]. It supposes a homology
-between variations in space and in time, i.e. that spatial sequences correspond
+Current knowledge on the links among the different facets of biodiversity mainly
+comes from spatial comparison [@dunne_network_2006;
+@soininen_relationship_2012; @grace_integrative_2016; @danet_species_nodate],
+which is used to predict how community structure will change in time, under the
+assumption of the space-for-time substitution. It supposes a homology between
+variations in space and in time, i.e. that spatial sequences correspond
 to temporal sequences. This method have raised criticisms
@@
 responsible for the non-compliance of space-for-time substitution
-[@adler_contrasting_2007; @blois_space_2013].
+[@adler_contrasting_2007; @blois_space_2013]. The recent increase in the availability
+of temporal monitoring of ecological communities makes possible to address
+biodiversity trends for multiple facets.
 
@@
 
-The documentation of biodiversity temporal trends generally neglect species
-interactions although they are fundamentals to ecosystem functioning
-[@thebault_food-web_2003; @oconnor_general_2017]. In food-webs, spatial
-comparisons in empirical and theoretical studies generally reported that trophic
-level positively scales to community biomass [@wang_biodiversity_2018;
+More dramatic is that the temporal trends of biodiversity generally neglect
+species interactions. Although species interactions determine for a large part
+community composition, species coexistence and ecosystem functioning
+[@chesson_mechanisms_2000; @thebault_food-web_2003; @oconnor_general_2017].
+Furthermore, species interactions can imply tremendous secondary extinctions
+[@paine_note_1969; @dunne_network_2002]. In food-webs, spatial comparisons in
+empirical and theoretical studies generally reported that trophic level
+positively scales to community biomass [@wang_biodiversity_2018;
 @danet_species_nodate]. Trophic level has also been shown to stabilise the
@@
 across small time-steps [@warren_spatial_1989; @pecuchet_novel_2020;
-@kaartinen_high_2012]. Our knowledge are even more scarce on the variability of
-food-web structure in time and particularly how those temporal variations are linked to
-the temporal variations of other aspects of biodiversity such as species richness
-and community biomass. Spatially, connectance has been shown to be negatively
-related to species richness in empirical food-webs [reviewed in
+@kaartinen_high_2012]. Our knowledge on the variability of food-web structure in
+time are even more scarce and particularly how those temporal variations are
+linked to the temporal variations of other aspects of biodiversity such as
+species richness and community biomass. Spatially, connectance has been shown to
+be negatively related to species richness in empirical food-webs [reviewed in
 @dunne_network_2006]. Connectance has been shown to scale positively or
 negatively with community biomass in theoretical models
-[@thebault_food-web_2003; @poisot_trophic_2013] (*Add mechanism?*). In order to
-improve our understanding on the assembly mechanisms in food-webs, it is thus
-crucial to assess how biomass and species richness temporal trends are associated to
-temporal trends in food-web structure.
-
-In this line, how the temporal changes of community biomass are related to
-temporal changes of species richness is still questionned in natural settings,
-especially in food-webs. Our knowledge on the relationships between food-web
-structure and other facets of biodiversity often comes from the comparison of
-food-web snapshots along spatial gradient, raising the question of the validity
-of space-for-time substitution to infer consequences of species richness and
+[@thebault_food-web_2003; @poisot_trophic_2013]. Average trophic level was
+previously shown to scale negatively with species richness
+[@danet_species_2021].  In order to improve our knowledge on the consequences of
+biodiversity trends such as community biomass and species richness, it is thus
+crucial to assess how biomass and species richness temporal trends are
+associated to temporal trends of food-web structure.
+
+Even how the temporal trends of community biomass are related to temporal
+trends of species richness is still questionned in natural settings, especially
+in food-webs. Our knowledge on the relationships between food-web structure and
+other facets of biodiversity often comes from the comparison of food-web
+snapshots along spatial gradient, raising the question of the validity of
+space-for-time substitution to infer consequences of species richness and
 community biomass variations on food-web structure.
@@
 methods to reconstruct food-webs [@bonnaffe_comparison_2021;
-@gravel_inferring_2013; @danet_species_nodate] makes possible to assess those
-questions. We used the standardized monitoring of fish freshwater communities on
-the period 1995-2018 over France, documenting the individual size of fishes in
+@gravel_inferring_2013; @danet_species_nodate] makes possible to assess the
+relationships among several biodiversity facets, including food-web structure.
+We used the standardized monitoring of fish freshwater communities on the period
+1995-2018 over France, documenting the individual size of fishes in
 400 sites during ten years or more. We then reconstruct around 4000 food-webs
@@
 weeks [@danet_species_nodate]. Those steps leads to the selection of 
-`r nb_st` sites (Figure \@ref{fig:matmet}A).
+`r nb_st` sites (Figure \@ref(fig:matmet)A).
 
@@
 We first inferred the body mass of each fish individual considering an allometric
-law, $B_i = 0.01 \times l_i^3.03$, $B_i$ being the biomass expressed in gram and $l_i$ the
+law, $B_i = 0.01 \times l_i^{3.03}$, $B_i$ being the biomass expressed in gram and $l_i$ the
 body length of the individual $i$ expressed in millimetres  [@froese_cube_2006]. Then the
@@
 We inferred food-web structure in two steps [@bonnaffe_comparison_2021;
-@danet_species_nodate]: (1) we first computed the metaweb, describing the
+@danet_species_2021]: (1) we first computed the metaweb, describing the
 potential trophic interactions among all size classes species, (2) then we
-extracted each yearly snapshot of food-webs by extracting species size
-classes and their interactions according to their presence in a given sampling
-event.
+extracted each yearly snapshot of food-webs by extracting species size classes
+and their interactions according to their presence in a given sampling event.
 
@@
 [@gravel_inferring_2013; @poisot_structure_2016; @brose_predator_2019;
-@bonnaffe_comparison_2021; @danet_species_nodate]. The method is extensively
-described in @bonnaffe_comparison_2021 and @danet_species_nodate. The food diet
-of stream fishes changes along their life cycle or stage, therefore
-according to their body size. Each fish species was divided in nine size
-classes, named "trophic species", equally distributed in their observed body size
-range. Thus, a trophic species is a group of individuals of the same species and size
-class that are expected to share the same preys and predators. We also added
-seven nodes present in the ontogenic food diet database: detritus, biofilm,
-phytoplankton, zooplankton, macrophages, phytobenthos and zoobenthos.  The
-resulting metaweb contained 45 fish species divided into nine size classes plus
-7 resource nodes, summing up to 412 nodes.  Consideration of size classes, i.e.
-trophic species instead of species, improves inference of trophic interactions
-[@jennings_weak_2001].
+@bonnaffe_comparison_2021; @danet_species_2021]. The method is extensively
+described in @bonnaffe_comparison_2021 and @danet_species_2021. The food diet of
+stream fishes changes along their life cycle or stage, therefore according to
+their body size. Each fish species was divided in nine size classes, named
+"trophic species", equally distributed in their observed body size range. Thus,
+a trophic species is a group of individuals of the same species and size class
+that are expected to share the same preys and predators because trophic
+interactions are largely determined by predator-prey size ratio
+[@brose_allometric_2006]. We also added seven nodes present in the ontogenic
+food diet database: detritus, biofilm, phytoplankton, zooplankton, macrophages,
+phytobenthos and zoobenthos.  The resulting metaweb contained 45 fish species
+divided into nine size classes plus 7 resource nodes, summing up to 412 nodes.
+Consideration of size classes, i.e.  trophic species instead of species,
+improves inference of trophic interactions [@jennings_weak_2001].
 
@@
 `r nb_st_rich_bm` sites for community biomass and species richness analysis.
-However, the
-results were robust to the inclusion of non monotonic trends (Fig. SXX).
+However, the results were robust to the inclusion of non monotonic trends (Fig.
+SXX).
 
@@
 compared the relationships among food-web structure in time to the ones observed
-along spatial gradient. To do so, we selected the same sites that were used
+in space. To do so, we selected the same sites that were used
 for the temporal analysis. We summarised temporal series of each station by the
@@
 
-We modelled the relationships among the temporal trends of food-web structure ($dN$)
-depending on the temporal trends of community biomass ($dB$) and species
-richness ($dR$) with a linear model. in order to test the relationship among the temporal of food-web
-structure, that is connectance, average trophic level and evenness of biomass
-from one side and species richness and community biomass from the other side as
-follows:
+We modelled the relationships among the temporal trends of food-web structure
+($dN$), that is connectance, average trophic level and evenness of biomass, and
+the temporal trends of community biomass ($dB$) and species richness ($dR$) with
+Ordinary Least Squares. The simultaneous assessment of the
+effects of species richness and community biomass allows to tease apart their
+respective effect on food-web structure.
 
@@
 In order to control for the uncertainties of the estimated temporal trends, each
-temporal trend was weighted by the inverse of the product of the standard errors of the
-estimated trends, i.e. slopes for the response and the explicative
-variables ($w_j = \dfrac{1}{s_{r_j} s_{e,j}}$, $w_j$ being the weight, $s_{r_j}$ and $s_{e_j}$ being
-respectively the standard errors on the temporal trends of the response and
-explicative variables). We also included a statistical model including the
-interaction between the temporal trends of species richness and community
-biomass (i.e.
-adding $\beta_3dB_jdR_j$), the results are presented in supplementary material (Fig.
-SXX). To model the relationships between the temporal trends of community
-biomass and the one of species richness, we built the model as $dB_j = \alpha_j +
-\beta_1dR_j + \epsilon_j$.
+temporal trend was weighted by the inverse of the product of the standard errors
+of the estimated trends, i.e. estimated slopes for the response and the
+explicative variables ($w_j = \dfrac{1}{s_{r_j} s_{e,j}}$, $w_j$ being the
+weight, $s_{r_j}$ and $s_{e_j}$ being respectively the standard errors on the
+temporal trends of the response and explicative variables). We also included a
+statistical model including the interaction between the temporal trends of
+species richness and community biomass (i.e.  adding $\beta_3dB_jdR_j$), the
+results are presented in supplementary material (Fig.  SXX). To model the
+relationships between the temporal trends of community biomass and the one of
+species richness, we built the model as $dB_j = \alpha_j + \beta_1dR_j +
+\epsilon_j$.
 
@@
 
-Spatial gradients of food-web structure are partly driven by environmental gradients, so
+Spatial variation of food-web structure are partly driven by environmental gradients, so
 we controlled relationships among variables by adding two PCA axis
-synthesizing respectively (1) stream size and (2) average temperature and
-enrichment. Enrichment was characterized by the average Biological Oxygen
-Demand [BOD, @mallin_factors_2006][^2].
+synthesizing respectively (1) stream gradient from upstream to downstream and
+(2) enrichment (Fig. \@ref(fig:matmet)). Enrichment was characterized by the
+average Biological Oxygen Demand [BOD, @mallin_factors_2006][^2]. We further
+added a random effect of the hydrographic basin on the intercept.
 
@@
 
-  - $N_j$: median network structure and communities structure
-  - $B_j$: median community biomass
-  - $R_j$: median species richness 
-  - $E_{1,j}$: PCA1 related to stream size
-  - $E_{2,j}$: PCA2 related to average temperature and average BOD
+  - $N_j$: median food-web structure 
+  - $B_j$: median community biomass ($g.m^-2$) 
+  - $R_j$: median species richness ($m^-2$) 
+  - $E_{1,j}$: First PCA axis 
+  - $E_{2,j}$: Second PCA axis
   - $\epsilon_{\alpha|i}$: random effect of the hydrographic basin
@@
 
-The significativity of the effects were tested with ANOVA. In order to compare
-the magnitude of the effects of community biomass and species richness in both
-temporal and spatial models, we computed standardized slopes ($r_{\delta}$) and
-their associated standard errors as $r_{\delta} = \beta\frac{s_x}{s_y}$.
-With $\beta$ being the unstandardised slope, $s_x$ and $s_y$ the standard
-deviation of the explicative and response variables.
-
-All the statistical models displayed low multicollinearity (VIF < 3, Table XX).
-We visually inspected the residuals of the linear models (TODO).
+In order to compare the magnitude of the effects of community biomass and
+species richness in both temporal and spatial models, we computed standardized
+slopes ($r_{\delta}$) and their associated standard errors as $r_{\delta} =
+\beta\frac{s_x}{s_y}$.  With $\beta$ being the unstandardised slope, $s_x$ and
+$s_y$ the standard deviation of the explicative and response variables.
+
+All the statistical models displayed low multicollinearity (Variance inflation
+factor < 3, Table XX).  We visually inspected the residuals of the linear models
+(TODO).
 
@@
 food-web connectance decreased over time also had community biomass that
-decreased over time and reversely. It suggests that communities that loose biomass
-over time, also loose generalist predators and reversely that communities
+decreased over time and reversely. It suggests that communities that decreased
+in biomass
+over time loose generalist predators over time, as connectance measures the degree of generalism and reversely that communities
 gaining biomass over time also gain generalist predators. Spatially, we also found
@@
 
-We found that the temporal trends of average trophic level had a strong positive
+The temporal trends of average trophic level had a strong positive
 relationship with the ones of community biomass 
@@
 that sites where community biomass decreased over time, average trophic level
-decreased over time and *vice versa*. It suggests that in communities loosing biomass
+decreased over time and *vice versa*. It means that in communities loosing biomass
 over time, the average biomass of the food-web moved down to lower trophic level
-and *vice versa*. The spatial gradient also showed a positive relationship between
-median average trophic level and median community biomass, but half the strength 
-as the temporal one ($r_\delta = `r sp_b_sest["tlvl"]`$, Fig. \@ref(fig:std),
-Table \@ref(tab:aov-sp)). The temporal trends of average
+and *vice versa*. We also found a positive relationship between
+median average trophic level and median community biomass in space, but half the strength 
+as the temporal one ($r_\delta = `r sp_b_sest["tlvl"]`$, Fig. \@ref(fig:std)). The temporal trends of average
 trophic level was unrelated to the ones of species richness. It suggests that in
 communities either loosing or gaining species richness over time, the location of
-average biomass along trophic level did not significantly change according to species richnnes.  However, we
-found a strong negative relationship in space 
+average biomass along trophic level did not significantly change according to
+species richnnes.  However, we found a strong negative relationship in space 
 ($r_\delta = `r sp_r_sest["tlvl"]`$, Fig. \@ref(fig:std), Table
@@
 
-```{r bmr, out.width="70%", fig.height=7, fig.cap=fig_bm_rich_cap}
+```{r bmr, out.width="80%", fig.height=7, fig.cap=fig_bm_rich_cap}
 plot_grid(
@@
 
-We further found that most temporal trends of food-webs were classified as
-stable for species richness and community biomass. We found almost the same
-number of stations that displayed temporal decrease or increase for species
+We found that most temporal trends of food-webs were classified as
+stable for species richness and community biomass. Roughly the same
+number of stations displayed temporal decrease and increase for species
 richness, and twice more stations displayed decrease in community biomass than
@@
 [@dornelas_assemblage_2014; @blowes_geography_2019; @klink_meta-analysis_2020].
-While the spatial coverage of our data is good, it would be rather risky to
-conclude about biodiversity trends in freshwater fish communities because we did
-not assess pressures that may affect the temporal trends such as land-use
-changes and species invasions [@comte_climate_2021; @su_human_2021;
-@cardinale_is_2018].
 
@@
 biomass increased through time in a given site. Reversely, connectance decreased
-in food-webs when community biomass decreased through time. It suggests that
+in food-webs when community biomass decreased through time.  Indeed, food-webs
+have a highly nested structure, in a way that feeding trophic links of species
+at lower trophic level are a subset of the ones of species found at higher
+trophic level [@kondoh_food_2010; @nordstrom_nestedness_2015]. It is because
+feeding interactions are largely driven by body size, consumers being larger
+than their preys [@brose_allometric_2006; @woodward_body_2005]. We also found
+that community biomass losses through time were associated to a temporal
+decrease of average trophic level and that community biomass temporal gains were
+associated to temporal increase of average trophic level. Together with connectance, it suggests that
 community biomass losses and gains are associated to losses and gains in large
-bodied piscivores. This interpretation is in
-line with the results that community biomass losses through time were associated
-to a temporal decrease of average trophic level and that community biomass
-temporal gains were associated to temporal increase of average trophic level.
-Another piece of evidence is that evenness of biomass, measured by the Pielou
-index, decreased through time as community biomass increased, meaning that
-biomass distribution across species becomes less even when community biomass
-increased. Reversely, in food-webs that displayed temporal decrease in community
-biomass, we found that evenness of biomass increased, i.e. that biomass
-distribution across species becomes more even. Because predator-prey
-interactions relate in part on bodysize and thus bodymass to a certain extent,
-we may expect that a given gain in predators of higher trophic level leads to a
-decrease of biomass evenness and reversely. In the same line, we found that the
-temporal trends of community biomass were positively accociated to the temporal
-trends of the number and proportion of piscivorous trophic species present in
-fish communities (Fig. SXX).
+bodied piscivores, i.e. biomass at the higher trophic level. Another piece of evidence
+is that evenness of biomass, measured by the Pielou index, decreased through
+time as community biomass increased, meaning that biomass distribution across
+species becomes less even when community biomass increased. Reversely, in
+food-webs that displayed temporal decrease in community biomass, we found that
+evenness of biomass increased, i.e. that biomass distribution across species
+becomes more even. Because predator-prey interactions relate on bodysize for a
+large part [@brose_allometric_2006; @woodward_body_2005] and thus bodymass to a
+certain extent, we can expect that a given gain in predators of higher trophic
+level leads to a decrease of biomass evenness and reversely. In the same line,
+we found that the temporal trends of community biomass were positively
+associated to the temporal trends of the number and proportion of piscivorous
+trophic species present in fish communities (Fig. SXX). The close association
+between the temporal trends of community biomass from one side, and connectance,
+average trophic level and biomass evenness from the other side, strongly suggest
+that temporal trends in community biomass in natural freshwater fish communities
+are associated to variations in the biomass of the top trophic level.
 
 In contrast, we found that temporal trends of connectance and average trophic
-level were not related to the temporal trends of species richness. However, we
-found that temporal trends of the number of piscivorous species and piscivorous
-trophic species were positively associated to the temporal trends of species
-richness (Fig. S3). It suggests that the temporal decrease of species richness
-observed in our data are concomimant to losses of piscivorous and
-non-piscivorous species, leading to the absence of temporal trends in
-connectance and average trophic level and symmetrically for the temporal
-increase of species richness. Furthemore, we found that the temporal trends of
-biomass evenness had a positive relationship with the one of species richness,
-in contradiction of what we found for temporal trends of community biomass.
-Together with the fact that species richness temporal trends had a positive
-relationship with the temporal trends of community biomass, it suggests that
-positive and negative  temporal trends of species richness are linked to gains
-and losses of redundancy in food-webs, without overall effects on connectance
-and average trophic level. This is in line with the insurance hypothesis
-[@yachi_biodiversity_1999] which predicts the temporal loss and gain of species
-richness represent respectively loss and gain of redundancy in the community,
-here in the food-web structure.
+level were not related to the temporal trends of species richness, in
+contradiction with previous observation in space [@dunne_network_2006;
+@danet_species_nodate]. However, we found that temporal trends of the number of
+piscivorous species and piscivorous trophic species were positively associated
+to the temporal trends of species richness (Fig. S3). It suggests that the
+temporal decrease of species richness observed in our data are concomitant to
+losses of piscivorous and non-piscivorous species, leading to the absence of
+temporal trends in connectance and average trophic level and symmetrically for
+the temporal increase of species richness. Furthermore, we found that the
+temporal trends of biomass evenness had a positive relationship with the one of
+species richness, in contradiction of what we found for temporal trends of
+community biomass. Together with the fact that species richness temporal trends
+had a positive relationship with the temporal trends of community biomass, it
+suggests that positive and negative  temporal trends of species richness are
+linked to gains and losses of redundancy in food-webs, without overall effects
+on connectance and average trophic level. This is in line with the insurance
+hypothesis [@yachi_biodiversity_1999] which predicts the temporal loss and gain
+of species richness represent respectively loss and gain of redundancy in the
+community, in the food-web structure in the present study.
+
+The discrepancy between the effects of the temporal trends of species richness
+and community biomass on food-web structure might be coined in the concepts of
+trophic complementarity and redundancy [@poisot_trophic_2013;
+@nordstrom_nestedness_2015]. The variations of community
+biomass is related to variations in the presence of large bodied predators,
+which affect both trophic complementarity, because they feed on bigger preys,
+and redundancy, because their diet include the diet of lower trophic level.
+Species richness temporal variation seems to affect mainly trophic redundancy
+and not trophic complementarity, as average trophic level and connectance does
+not change despite concomitant variations in the number of piscivorous species
+(**Interesting ?**).
 
@@
 communities may become more at risk regarding future perturbations
-[@yachi_biodiversity_1999]. Overall, it suggests that monitoring several facets
-of community structure is essential to infer how ecological communities are
-reshaped by loss and gain of biomass and species richness.
+[@yachi_biodiversity_1999]. Interestingly, the hypothesis that temporal trends
+in community biomass is related to higher trophic level in our system has a
+strong reasoning with the effect of human fisheries in marine systems which
+affect primarily fish species at top trophic level [@sprules_surfing_2016].
+Overall, our study highlights that monitoring several facets of biodiversity is
+essential to infer how ecological communities are reshaped by loss and gain of
+biomass and species richness.
 
@@
 mismatch between spatial and temporal patterns [@adler_contrasting_2007;
-@johnson_testing_2008]. This discrepency in space and time might be due to the
+@johnson_testing_2008]. This discrepancy in space and time might be due to the
 crucial assumption that variations in space reflect differences in assembly
@@
 species richness from one side and the temporal trends of community biomass,
-biomass evenness, and the number of piscivore species from the other side (Fig. S3).
+biomass evenness, and the number of piscivorous species from the other side (Fig. S3).
 

### 2022-02-23 paper/appendix.Rmd
Fix bound of the prediction lines

@@
 
-st_cap <- paste0(
-  "Repartion of the", length(st_mono_trends_stable_rich_bm), " stations used in
-  the data analysis.")
-```
-
-```{r st, fig.cap = st_cap}
-p_st_mono_trends_stable_rich_bm
 ```
@@
 range_cap <- paste0(
-  "Range of variation of variables in spatial (vertical line) and temporal
+  "Range of variation of variables in spatial (vertical lines) and temporal
   dataset for the (A) minimum and maximum values and (B) the range (i.e. maximum
@@
 
+\newpage
+
 ## Correlation
@@
 ```{r}
-cor_cap <- paste0("Correlation plot among variables for spatial and temporal
-  relationships. ", "Median values over temporal series in each station were
-  used for spatial relationships. ", "For temporal relationships, we used the
+cor_cap <- paste0("Correlation plot among variables.", "Median values over time were
+  used for spatial relationships. ", "For temporal model, we used the
   temporal trends in each station. Futhermore, each station was weighted by the
@@
 ```
+
+\newpage
+
+## Statistical model tables
+
+### Temporal
+
+```{r}
+loadd(
+  pred_bm_rich_mono_stable_trends,
+  model_bm_rich_int_mono_stable_trends,
+  model_bm_rich_int_mono_stable_trends,
+  rsq_table_bm_rich_mono_stable_trends
+)
+```
+
+```{r}
+reg_table_bm_rich_mono_stable_trends %>%
+  mutate(
+    response = str_replace_all(response, var_replacement()),
+    term = str_replace_all(term, var_replacement())
+    ) %>%
+kable(., booktabs = TRUE,
+  row.names = FALSE,
+  caption =
+    paste0(
+      "Regression coefficients for the linear models explaining the links
+      between the temporal trends of community biomass and the temporal trends
+      of the network structure."),
+      label = "reg"
+      ) %>%
+  kable_styling(latex_options = c("scale_down", "striped")) %>%
+  collapse_rows(columns = 1, valign = "top")
+```
+
+```{r}
+table_rsq_tps <- rsq_table_bm_rich_mono_stable_trends %>%
+  mutate(
+    Response = str_replace_all(Response, var_replacement())
+  )
+table_rsq_tps %>%
+  kable(., booktabs = TRUE,
+    caption =
+      paste0(
+      "Marginal and conditional squared R for temporal models."),
+  label = "rsq"
+      ) %>% #
+  kable_styling(latex_options = c("striped")) %>%
+  collapse_rows(columns = 1, valign = "top")
+```
+
+### Spatial
+
+```{r}
+loadd(
+  sp_anova_table_bm_rich_mono_stable_trends,
+  sp_rsq_table_bm_rich_mono_stable_trends
+)
+```
+
+```{r}
+sp_anova_table_bm_rich_mono_stable_trends %>%
+  mutate(
+    response = str_replace_all(response, var_replacement()),
+    term = str_replace_all(term, var_replacement()),
+  ) %>%
+  kable(.,
+    booktabs = TRUE,
+    row.names = FALSE,
+    caption =
+      paste0(
+      "ANOVA results for the links among the spatial variation of community
+      biomass and species richness and the one of network structure."),
+  label = "aov-sp"
+  ) %>%
+  kable_styling(latex_options = c("scale_down", "striped")) %>%
+  collapse_rows(columns = 1, valign = "top")
+```
+
+```{r}
+sp_rsq_table_bm_rich_mono_stable_trends %>%
+  mutate(
+    Response = str_replace_all(Response, var_replacement())
+  ) %>%
+  kable(., booktabs = TRUE,
+    caption =
+      paste0("Marginal and conditional $R^2$ for the spatial models."),
+  label = "rsq-sp"
+      ) %>% #
+  kable_styling(latex_options = c("striped")) %>%
+  collapse_rows(columns = 1, valign = "top")
+```

### 2022-02-23 paper/manuscript.Rmd
Fix bound of the prediction lines

@@
 All the statistical models displayed low multicollinearity (Variance inflation
-factor < 3, Table XX).  We visually inspected the residuals of the linear models
-(TODO).
-
-```{r}
-
-fig_mat_cap <- paste0( "Using  sites of stream fishes in French streams that
+factor < 3, Table SXX).  We visually inspected the residuals of the linear models.
+
+```{r}
+
+fig_mat_cap <- paste0("Using  sites of stream fishes in French streams that
   have been monitored at least 10 years, 1) we infered the food-web at each site
@@
 PCA is related to the stream gradient from upstream to downstream while the
-second is related to enrichment (BOD) and site altitude (error on the PCA,
-  station is present!!!).")
+second is related to enrichment (BOD) and site altitude.")
 
@@
 loadd(rigal_classification)
+```
+
+```{r}
+log_trends_percent <- rigal_classification %>%
+  unnest(classif) %>%
+  filter(variable %in% c("log_bm_std", "log_rich_std")) %>%
+  select(variable, station, linear_slope, linear_slope_strd_error) %>%
+  mutate(
+    slp_percent = round((exp(linear_slope) - 1) * 100),
+    std_err_percent = round((exp(linear_slope_strd_error) - 1) * 100)
+  )
+resume_log_trends <- log_trends_percent %>%
+  group_by(variable) %>%
+  summarise(
+    mean = mean(slp_percent, na.rm = TRUE),
+    sd = sd(slp_percent, na.rm = TRUE))
 ```
@@
 the evenness of abundances to $R_{adj}^2= `r rsq_tlvl`$ for average trophic
-level (Table \@ref(tab:rsq)). The models over the spatial gradient were more performant, with
+level (Table SXX). The models over the spatial gradient were more performant, with
 $R_{cond}^2$ varing from $`r rsq_tlvl_sp`$ to $`r rsq_piel_bm_sp`$ (Table
-\@ref(tab:rsq-sp)), $R_{cond}^2$ being the $R^2$conditional to the random effect.
+SXX), $R_{cond}^2$ being the $R^2$conditional to the random effect.
 
@@
 
+  if (!is.null(rsq)) {
+
     tmp <- "paste(
-  beta, \" (s.e) \", \" = \",
+    beta, \" (s.e.) \", \" = \",
     mybeta, \" (\", myse, \"), \",
-
     italic(R)^2, \" = \", myrsq
     )"
-
 str_replace_all(tmp,
@@
 
+  } else {
+
+    tmp <- "paste(
+    beta, \" (s.e) \", \" = \",
+    mybeta, \" (\", myse, \") \" )"
+str_replace_all(tmp,
+  c(
+    "mybeta" = as.character(beta),
+    "myse" = as.character(se)
+  )
+)
+
   }
+
+}
+
+scale_xy_log_trends <- function(breaks = NULL, axis = "y", sep ="\n") {
+  log_to_percent <- round((exp(breaks) - 1) * 100)
+  labels <- paste0(breaks, sep, log_to_percent, " %")
+
+  if(axis == "y") {
+    fun <- scale_y_continuous
+  } else {
+    fun <- scale_x_continuous
+  }
+
+  fun(breaks = breaks, labels = labels)
+
+}
 ```
@@
 ```{r bef, fig.cap=fig_bef_cap, out.width="50%"}
+lab_log_rich <- expression(atop("Log species richness ("*m^{-2}*")","trend slope (log / % per year)"))
+lab_log_bm <- expression(atop("Log community biomass ("*g.m^{-2}*")", "trend slope (log / % per year)"))
+
 p_bef <- fig1_2$rich$log_bm_std +
-  annotate("text", x = -.05, y = .3, parse = T,
-    label = beta_rsq(rsq = coeff_bef["rsq"],
-      beta = coeff_bef["estimate"], se =
-        coeff_bef["std.error"])
+  annotate("text", x = .1, y = -.5, parse = T,
+    label = beta_rsq(
+      rsq = coeff_bef["rsq"],
+      beta = coeff_bef["estimate"],
+      se = coeff_bef["std.error"]
+    )
    ) +
   labs(
-    y = "Log community biomass (g per year)",
-    x = "Log species richness (per year)"
-  )
+    y = lab_log_bm,
+    x = lab_log_rich
+  ) +
+scale_xy_log_trends(breaks = c(-.10, -.050, 0, .050, .10), axis = "x") +
+scale_xy_log_trends(breaks = c(-.4, -.2, 0, .4, .2), axis = "y", sep = " / ")
 
@@
 biomass and the ones of species richness ($r_\delta = `r tps_r_sest["p_bm"]`$,
-Fig. \@ref(fig:bef), Table \@ref(tab:aov)), meaning that both temporal trends
+Fig. \@ref(fig:bef)), meaning that both temporal trends
 had the same direction in average. At the sites 
@@
 decreased over time and reversely. It suggests that communities that decreased
-in biomass
-over time loose generalist predators over time, as connectance measures the degree of generalism and reversely that communities
+in biomass over time loose generalist predators over time, as connectance
+measures the degree of generalism, and reversely that communities
 gaining biomass over time also gain generalist predators. Spatially, we also found
@@
 relationship with the ones of community biomass 
-($r_\delta = `r tps_bm_sest["tlvl"]`$, Fig. \@ref(fig:bmr)B, Table
-\@ref(tab:aov)), meaning
+($r_\delta = `r tps_bm_sest["tlvl"]`$, Fig. \@ref(fig:bmr)B), meaning
 that sites where community biomass decreased over time, average trophic level
@@
 species richnnes.  However, we found a strong negative relationship in space 
-($r_\delta = `r sp_r_sest["tlvl"]`$, Fig. \@ref(fig:std), Table
-\@ref(tab:aov-sp)).
+($r_\delta = `r sp_r_sest["tlvl"]`$, Fig. \@ref(fig:std)).
 
@@
 other hand, we found a positive relationship between the temporal trends of
-biomass evenness and the one of species richness (Fig. \@ref(fig:bmr)F, Table
-\@ref(tab:aov), $r_\delta = `r tps_r_sest["p_bm"]`$). We found the same
-relationship in space, twice as strong however 
-($r_\delta = `r sp_r_sest["p_bm"]`$).
+biomass evenness and the one of species richness (Fig. \@ref(fig:bmr)F,
+$r_\delta = `r tps_r_sest["p_bm"]`$). We found the same relationship in space,
+twice as strong however ($r_\delta = `r sp_r_sest["p_bm"]`$).
 
@@
   "Relationships between the temporal trends of food-web structure
-  and the ones of community biomass (left panel) species richness (right panel).
+  and the ones of community biomass (left panel, A, C, E) species richness (right panel, B, D, F).
   The lines surrounding each point display the standard errors associated to
   the estimated temporal trends. Red and black lines represent respectively
-  significant relationships. The histograms display the distribution of
-  response and predictive variables.")
+  significant and non-significant slopes, both lines displays prediction from
+  the Ordinary Least Squares model. The histograms display the distribution of response and predictive
+  variables. Labels display the unstandardised slope coefficients and their
+  standard errors (see Fig. \\ref{fig:std} for the standardized coefficients).
+  $R^2$ are displayed only on the right panel, as it is the same model for both
+  panels.")
+
 ```
@@
       "\ntrends (per year)"),
-    x = paste0("Log biomass",
-      "\ntrends (per year)"),
-  )
+    x = lab_log_bm
+  ) +
+  scale_xy_log_trends(breaks = c(-.40, -.20, 0, .20, .40), axis = "x")
 )
@@
   ) +
-  labs(x = paste0("Log species richness",
-      "\ntrends (per year)"))
+  labs(x = lab_log_rich) +
+  scale_xy_log_trends(breaks = c(-.10, -.050, 0, .050, .10), axis = "x")
   )
@@
 
+```
+
+```{r}
+# Add beta and Rsq
+for (i in seq_along(fig2$rich)) {
+
+  resp_var <- names(fig2$rich)[i]
+
+  coeff_rich <- c(
+    rsq = rsq_table_bm_rich_mono_stable_trends %>%
+      filter(Response == resp_var) %$%
+      unlist(.[, c("R.squared")]),
+    reg_table_bm_rich_mono_stable_trends %>%
+      filter(response == resp_var, term == "log_rich_std") %$%
+      unlist(.[, c("estimate", "std.error", "std_estimate", "stdse")])
+    ) %>%
+  round(., 2)
+
+  coeff_bm <- reg_table_bm_rich_mono_stable_trends %>%
+    filter(response == resp_var, term == "log_bm_std") %$%
+    unlist(.[, c("estimate", "std.error", "std_estimate", "stdse")]) %>%
+    round(., 2)
+
+  # Add coeff:
+  fig2$rich[[resp_var]] <- fig2$rich[[resp_var]] +
+  annotate("text", x = -.10, y = Inf, vjust = 1, hjust = 0,
+    size = 2,
+    parse = T,
+    label = beta_rsq(
+      rsq = coeff_rich["rsq"],
+      beta = coeff_rich["estimate"],
+      se = coeff_rich["std.error"]
+    )
+  )
+  fig2$bm[[resp_var]] <- fig2$bm[[resp_var]] +
+  annotate("text", x = -.4, y = Inf, vjust = 1, hjust = 0,
+    size = 2,
+    parse = T,
+    label = beta_rsq(
+      rsq = NULL,
+      beta = coeff_bm["estimate"],
+      se = coeff_bm["std.error"]
+    )
+  )
+}
+```
+
+```{r}
 # Add histograms
@@
 fig2$rich[2:3] <- map(fig2$rich[2:3], ~ggMarginal(.x, type = "histogram", margins = "y"))
-
 ```
@@
   panel) and species richness (bottom panel) on food-web structure for the
-temporal and spatial models. Top of
-  bars display the standardized coefficients from the linear models, the lines
-  around display the standard errors.")
+temporal and spatial models. The bar tops display the standardized slope coefficients
+from the models ($r_\\delta$), the lines around bar tops display the standard errors.")
 ```
@@
     position = position_dodge(width = .9)) +
-  labs(x = "Response variables", y = "Standardized slopes", fill = "Model") +
-  theme(legend.position = c(0.7, .1),
+  labs(
+    x = "Response variables",
+    y = expression(paste("Standardized slope coefficients ", r[delta])),
+    fill = "Model") +
+  theme(legend.position = c(0.6, .05),
     legend.direction = "horizontal",
@@
 \newpage
-
-\newpage
-
-# Tables {-}
-
-## Statistical models
-
-### Temporal
-
-```{r}
-loadd(pred_bm_rich_mono_stable_trends,
-  model_bm_rich_int_mono_stable_trends,
-  model_bm_rich_int_mono_stable_trends,
-  anova_table_bm_rich_mono_stable_trends)
-
-anova_table_bm_rich_mono_stable_trends %>%
-  mutate(
-    response = str_replace_all(response, var_replacement()),
-    term = str_replace_all(term, var_replacement())
-  ) %>%
-  kable(.,
-    booktabs = TRUE,
-    row.names = FALSE,
-    caption =
-      paste0(
-      "ANOVA results for the links between the temporal trends of
-      community biomass and the temporal trends of the network structure."
-    ),
-  label = "aov"
-  ) %>%
-  kable_styling(latex_options = c("scale_down", "stripped")) %>%
-  collapse_rows(columns = 1, valign = "top")
-```
-
-```{r}
-reg_table_bm_rich_mono_stable_trends %>%
-  mutate(
-    response = str_replace_all(response, var_replacement()),
-    term = str_replace_all(term, var_replacement())
-    ) %>%
-kable(., booktabs = TRUE,
-  row.names = FALSE,
-  caption =
-    paste0(
-      "Regression coefficients for the linear models explaining the links
-      between the temporal trends of community biomass and the temporal trends
-      of the network structure."),
-      label = "reg"
-      ) %>%
-  kable_styling(latex_options = c("scale_down", "striped")) %>%
-  collapse_rows(columns = 1, valign = "top")
-```
-
-```{r}
-table_rsq_tps <- rsq_table_bm_rich_mono_stable_trends %>%
-  mutate(
-    Response = str_replace_all(Response, var_replacement())
-  )
-table_rsq_tps %>%
-  kable(., booktabs = TRUE,
-    caption =
-      paste0(
-      "Marginal and conditional squared R for temporal models."),
-  label = "rsq"
-      ) %>% #
-  kable_styling(latex_options = c("striped")) %>%
-  collapse_rows(columns = 1, valign = "top")
-```
-
-### Spatial
-
-```{r}
-loadd(
-  sp_anova_table_bm_rich_mono_stable_trends,
-  sp_rsq_table_bm_rich_mono_stable_trends
-)
-```
-
-```{r}
-sp_anova_table_bm_rich_mono_stable_trends %>%
-  mutate(
-    response = str_replace_all(response, var_replacement()),
-    term = str_replace_all(term, var_replacement()),
-  ) %>%
-  kable(.,
-    booktabs = TRUE,
-    row.names = FALSE,
-    caption =
-      paste0(
-      "ANOVA results for the links among the spatial variation of community
-      biomass and species richness and the one of network structure."),
-  label = "aov-sp"
-  ) %>%
-  kable_styling(latex_options = c("scale_down", "striped")) %>%
-  collapse_rows(columns = 1, valign = "top")
-```
-
-```{r}
-sp_rsq_table_bm_rich_mono_stable_trends %>%
-  mutate(
-    Response = str_replace_all(Response, var_replacement())
-  ) %>%
-  kable(., booktabs = TRUE,
-    caption =
-      paste0(
-      "Marginal and conditional squared R for spatial models."),
-  label = "rsq-sp"
-      ) %>% #
-  kable_styling(latex_options = c("striped")) %>%
-  collapse_rows(columns = 1, valign = "top")
-```

### 2022-02-23 paper/method_figure.Rmd
Fix bound of the prediction lines

@@
 dec_representative <- st_var_shape %>%
-  filter(log_bm_std == "decrease", ct_ff == "decrease", w_trph_lvl_avg == "decrease") 
+  filter(
+    log_bm_std == "decrease",
+    ct_ff == "decrease",
+    w_trph_lvl_avg == "decrease")
 ```
@@
   base_width = 7, base_height = 7)
+```
 
+## Plot PCA
+
+```{r}
+loadd(p_pca)
+save_plot(get_mypath("figures/rotated_pca.pdf"),
+  p_pca,
+  ncol = 1, nrow = 1,
+  base_width = 4, base_height = 4
+)
 ```
@@
 ```{r}
-
 test_fig_mat_met <- plot_grid(

### 2022-02-24 paper/appendix.Rmd
minor updates to manuscript

@@
 knitr::opts_chunk$set(
-  cache = TRUE,
+  cache = FALSE,
   collapse = TRUE,
@@
 loadd(p_range)
-
 plot_grid(plotlist = p_range, nrow = 2, labels = "AUTO")

### 2022-02-24 paper/manuscript.Rmd
minor updates to manuscript

@@
 loadd(slope_com_var_no_covar, st_mono_trends_stable_rich_bm)
+loadd(range_data)
 ```

### 2022-02-24 R/report_plot.R

@@ -572,24 +572,26 @@ get_range_variable <- function(
     filter(station %in% st) %>%
     select(c("station", all_of(var_to_keep))) %>%
     pivot_longer(!station, names_to = "variable", values_to = "values") %>%
-    mutate(variable = str_replace_all(variable, var_replacement())) %>%
+    mutate(variable = var_replacement()[variable]) %>%
     group_by(variable) %>%
     summarise(
       min = min(values, na.rm = TRUE),
       max = max(values, na.rm = TRUE)) %>%
-    mutate(range = max - min)
+    mutate(range = max - min, ratio = max / min)
 
   range_variable_station <- full_data %>%
     filter(station %in% st) %>%
     select(c("station", all_of(var_to_keep))) %>%
     pivot_longer(!station, names_to = "variable", values_to = "values") %>%
-    mutate(variable = str_replace_all(variable, var_replacement())) %>%
+    mutate(variable = var_replacement()[variable]) %>%
     group_by(station, variable) %>%
     summarise(
       min = min(values, na.rm = TRUE),
       max = max(values, na.rm = TRUE),
       .groups = "drop"
-    )
+    ) %>%
+    mutate(range = max - min, ratio = max / min)
+
 
   return(list(
     range_spatial_variable = range_spatial_variable,

### 2022-03-06 supplementary.Rmd
Compute SEM and its CI coefficients

@@
 ```
+
+# SEM
+
+```{r}
+loadd(slope_com_var_no_covar, st_mono_trends_rich_bm)
+library(piecewiseSEM)
+library(semEff)
+```
+
+```{r}
+  sem_tps = list(
+    lm(
+      ct_ff ~ log_bm_std + log_rich_std,
+      data = filter(slope_com_var_no_covar, station %in% st_mono_trends_rich_bm),
+      weight = 1 / log_rich_std_strd_error * log_bm_std_strd_error *
+        ct_ff_strd_error
+      ),
+    lm(
+      w_trph_lvl_avg ~ log_bm_std + log_rich_std,
+      data = filter(slope_com_var_no_covar, station %in% st_mono_trends_rich_bm),
+      weight = 1 / log_rich_std_strd_error * log_bm_std_strd_error *
+        w_trph_lvl_avg_strd_error
+      ),
+    lm(
+      log_bm_std ~ log_rich_std,
+      data = filter(slope_com_var_no_covar, station %in% st_mono_trends_rich_bm),
+      weight = 1 / log_rich_std_strd_error * log_bm_std_strd_error
+    )
+    )
+sem <- list(
+  lm(ct_ff ~ log_bm_std + log_rich_std, data = ti,
+    weight = 1 / log_rich_std_strd_error * log_bm_std_strd_error *
+      ct_ff_strd_error),
+    lm(w_trph_lvl_avg ~ log_bm_std + log_rich_std, data = ti,
+      weight = 1 / log_rich_std_strd_error * log_bm_std_strd_error *
+        w_trph_lvl_avg_strd_error),
+      lm(log_bm_std ~ log_rich_std, data = ti,
+        weight = 1 / log_rich_std_strd_error * log_bm_std_strd_error
+        )
+)
+plot(as.psem(sem))
+```
+
+```{r}
+semeff_tps <- semEff(sem_tps, R = 1000, seed = 13, parallel = "no")
+semeff <- semEff(sem, R = 1000, seed = 13, parallel = "no")
+```
+
+```{r}
+loadd(sp_st_data)
+library(nlme)
+
+data_sp_sem <- na.omit(sp_st_data)
+tuu <- get_mod_list(.data = data_sp_sem)
+
+sp_sem <- list(
+     log_rich_std = lmer(log_rich_std ~ log_RC1 + log_RC2 + (1 | basin), data = data_sp_sem),
+     log_bm_std = lmer(log_bm_std ~ log_rich_std + log_RC1 + log_RC2 + (1 | basin), data = data_sp_sem),
+     ct_ff = lmer(ct_ff ~ log_rich_std + log_bm_std + log_RC1 + log_RC2 + (1 | basin), data = data_sp_sem),
+     w_trph_lvl_avg = lmer(w_trph_lvl_avg ~ log_rich_std + log_bm_std + log_RC1 + log_RC2 +
+       (1 | basin), data = data_sp_sem)
+)
+summary(sp_sem[[4]])
+sp_psem <- as.psem(sp_sem)
+summary_sp_sem <- summary(sp_psem)
+plot(sp_psem, node_attrs = data.frame(shape = "rectangle", color = "black",
+    fillcolor = "grey"))
+
+sp_semeff <- semEff(sp_sem, R = 1000, seed = 13, parallel = "no", type = "parametric")
+```
+
+```{r}
+sp_semeff_df <- from_semEff_to_table(x = sp_semeff)
+semeff_df <- from_semEff_to_table(x = semeff)
+```
+
+```{r}
+get_CI_sem_bootEFF <- function(booteff = NULL) {
+  bootci <- bootCI(booteff)
+
+  map_dfr(bootci, function(x) {
+    # get rid of the table header  
+    tab <- x[-1, ]
+    # keep predictor name
+    predictor <- tab[[1]]
+    numeric_table <- map(tab, as.numeric)
+    # suppr table columns
+    mask_chr_column <- map_lgl(numeric_table, ~all(is.na(.x)))
+    cbind(
+      data.frame(predictor = predictor),
+      tab[, !mask_chr_column]
+    )
+}, .id = "response")
+
+}
+get_CI_sem_bootEFF(test)
+```
+
+```{r}
+```

### 2022-03-06 R/plan.R

@@ -192,6 +192,7 @@ model_vif = get_vif(model,
     anova = map(scaled_mod, ~anova(.x))
   ),
 
+
   #temporal_dynamics_plot = get_temporal_dynamics_plot(temporal_dynamics = temporal_dynamics),
   temporal_dynamics_coef = get_lm_coeff(
     .data = temporal_dynamics,
@@ -522,9 +523,62 @@ model_vif = get_vif(model,
   model_bm_rich_int_mono_stable_trends = get_model_bm_rich_int(
     .data = filter(slope_com_var_no_covar, station %in%
     st_mono_trends_stable_rich_bm)
-  ),
+    ),
+  data_tps_sem = slope_com_var_no_covar %>%
+    filter(station %in% st_mono_trends_stable_rich_bm) %>%
+    select(
+      ct_ff, ct_ff_strd_error,
+      log_bm_std, log_bm_std_strd_error,
+      log_rich_std, log_rich_std_strd_error,
+      w_trph_lvl_avg, w_trph_lvl_avg_strd_error) %>%
+    na.omit(),
+  sem_tps = list(
+    lm(
+      ct_ff ~ log_bm_std + log_rich_std,
+      data = data_tps_sem,
+      weight = 1 / log_rich_std_strd_error * log_bm_std_strd_error *
+        ct_ff_strd_error
+      ),
+    lm(
+      w_trph_lvl_avg ~ log_bm_std + log_rich_std,
+      data = data_tps_sem,
+      weight = 1 / log_rich_std_strd_error * log_bm_std_strd_error *
+        w_trph_lvl_avg_strd_error
+      ),
+    lm(
+      log_bm_std ~ log_rich_std,
+      data = data_tps_sem,
+      weight = 1 / log_rich_std_strd_error * log_bm_std_strd_error
+    )
+    ),
+  semeff = semEff(sem_tps, R = 10000, seed = 13, parallel = "no"),
+
+
 
   #### Spatial
+  data_sp_sem = sp_st_data %>%
+    filter(station %in% st_mono_trends_stable_rich_bm) %>%
+    select(log_rich_std, log_RC1, log_RC2,
+      log_bm_std, ct_ff, w_trph_lvl_avg, basin),
+  sp_sem = list(
+    log_rich_std = lmer(
+      log_rich_std ~ log_RC1 + log_RC2 + (1 | basin),
+      data = data_sp_sem
+      ),
[…]

### 2022-03-06 R/statistical_model.R

@@ -255,7 +255,7 @@ get_model_bm_rich_no_covar_no_inc <- function (.data = NULL) {
       data = {{.data}},
       weight = 1 / log_rich_std_strd_error * log_bm_std_strd_error),
     ct_ff = lm(
-      ct_ff ~ log_rich_std  + log_bm_std ,
+      ct_ff ~ log_rich_std  + log_bm_std,
       data = {{.data}},
       weight = 1 / log_rich_std_strd_error * log_bm_std_strd_error * ct_ff_strd_error),
     w_trph_lvl_avg = lm(

### 2022-03-11 sem.Rmd
Add SEM

---
title: "SEM"
author: AD 
date: \today
output:
  bookdown::html_document2:
    toc: true
    theme: "readable"
    code_folding: hide
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  message = FALSE,
  warning = FALSE,
  results = TRUE
)
```

```{r}
loadd(slope_com_var_no_covar, st_mono_trends_rich_bm)
library(piecewiseSEM)
library(semEff)
library(kableExtra)
library(lme4)
mypath <- rprojroot::find_package_root_file
source(mypath("R/misc.R"))
source(mypath("R/variable_shortcut.R")) # Define your custom code as a bunch of functions.
source_dir(get_mypath("R")) # Define your custom code as a bunch of functions.

mytheme <- theme_cowplot() +
background_grid()

theme_set(mytheme)
```

```{r}
loadd(sp_st_data)
loadd(slope_com_var_no_covar)
loadd(st_mono_trends_stable_rich_bm)
```

```{r}
var_analysis <- c("ct_ff", "log_bm_std", "log_rich_std", "w_trph_lvl_avg")

data_sp_sem <- sp_st_data %>%
  filter(station %in% st_mono_trends_stable_rich_bm) %>%
  select(c("station", all_of(var_analysis), "basin", "log_RC1", "log_RC2")) %>%
  na.omit()
data_tps_sem <- slope_com_var_no_covar %>%
  filter(station %in% st_mono_trends_stable_rich_bm) %>%
  select(station, starts_with(var_analysis)) %>%
  na.omit()
```
# SEM

## Temporal SEM

```{r}
sem <- list(
  lm(ct_ff ~ log_bm_std + log_rich_std, data = data_tps_sem,
    weight = 1 / log_rich_std_strd_error * log_bm_std_strd_error *
      ct_ff_strd_error),
    lm(w_trph_lvl_avg ~ log_bm_std + log_rich_std, data = data_tps_sem,
      weight = 1 / log_rich_std_strd_error * log_bm_std_strd_error *
        w_trph_lvl_avg_strd_error),
      lm(log_bm_std ~ log_rich_std, data = data_tps_sem,
        weight = 1 / log_rich_std_strd_error * log_bm_std_strd_error
        )
)
plot(as.psem(sem),
  node_attrs = data.frame(
    shape = "rectangle", fixedsize = TRUE, width = 1, color = "black",
    fillcolor = "lightgrey")
)
```

## Spatial SEM

```{r}
sp_sem <- list(
     log_rich_std = lmer(log_rich_std ~ log_RC1 + log_RC2 + (1 | basin), data = data_sp_sem),
     log_bm_std = lmer(log_bm_std ~ log_rich_std + log_RC1 + log_RC2 + (1 | basin), data = data_sp_sem),
     ct_ff = lmer(ct_ff ~ log_rich_std + log_bm_std + log_RC1 + log_RC2 + (1 | basin), data = data_sp_sem),
     w_trph_lvl_avg = lmer(w_trph_lvl_avg ~ log_rich_std + log_bm_std + log_RC1 + log_RC2 +
       (1 | basin), data = data_sp_sem)
)
sp_psem <- as.psem(sp_sem)
summary_sp_sem <- summary(sp_psem)
plot(sp_psem,
  node_attrs = data.frame(
    shape = "rectangle", fixedsize = TRUE, width = .8, color = "black",
    fillcolor = "lightgrey", nodesep = 2))
```

- Bootstrap (10000) takes a very long time: 
```{r, eval=FALSE}
sp_semeff <- semEff(sp_sem, R = 10000, seed = 13, parallel = "no", type = "parametric")
save(sp_semeff, file = get_mypath("data", "sp_semeff.rda"))

semeff <- semEff(sem, R = 10000, seed = 13, parallel = "no")
save(semeff, file = get_mypath("data", "semeff.rda"))

semeff_perc <- semEff(sem, R = 100, seed = 13, parallel = "no",
  ci.type = "perc"
)
save(semeff_perc, file = get_mypath("data", "semeff_perc.rda"))

sp_semeff_perc <- semEff(sp_sem, R = 100, seed = 13, parallel = "no",
  ci.type = "perc", ran.eff = "basin"
)
save(sp_semeff_perc, file = get_mypath("data", "sp_semeff_perc.rda"))

sp_semeff_df <- from_semEff_to_table(x = sp_semeff_perc)
semeff_df <- from_semEff_to_table(x = semeff_perc)
```

# Direct, indirect and total effects

```{r}
load(get_mypath("data", "semeff_perc.rda"))
load(get_mypath("data", "sp_semeff_perc.rda"))
```

```{r}
tps_sem_tbl <- from_semEff_to_table(semeff_perc)
tps_sem_tbl[, c("response", "predictor")] <-
  map(c("response", "predictor"),
  ~ var_replacement()[tps_sem_tbl[[.x]]])

sp_sem_tbl <- from_semEff_to_table(sp_semeff_perc)
sp_sem_tbl[, c("response", "predictor")] <-
  map(c("response", "predictor"),
  ~ var_replacement()[sp_sem_tbl[[.x]]])
```

## Temporal SEM

- Temporal sem:
  - Main difference with previous approach: bootstrapping reveals that
    biomass have no more significant direct effect on connectance where as
    anova, regression, and then SEM told us that it was significant

```{r}
tps_sem_tbl$predictor = cell_spec(tps_sem_tbl$predictor,
  color = case_when(
    tps_sem_tbl$lower_ci > 0 & tps_sem_tbl$upper_ci > 0 ~ "red", 
    tps_sem_tbl$lower_ci < 0 & tps_sem_tbl$upper_ci < 0 ~ "blue",
    TRUE ~ "black"
      ))
kbl(tps_sem_tbl, align = "c", format = "html", escape = FALSE) %>%
  kable_paper(full_width = F) %>%
  collapse_rows(columns = 1:2, valign = "top")
```

## Spatial SEM

```{r}
sp_sem_tbl$predictor = cell_spec(
  sp_sem_tbl$predictor,
  color = case_when(
    sp_sem_tbl$lower_ci > 0 & sp_sem_tbl$upper_ci > 0 ~ "red", 
    sp_sem_tbl$lower_ci < 0 & sp_sem_tbl$upper_ci < 0 ~ "blue",
    TRUE ~ "black"
      ))
kbl(sp_sem_tbl, align = "c", format = "html", escape = FALSE) %>%
  kable_paper(full_width = F) %>%
  collapse_rows(columns = 1:2, valign = "top")
```

### 2022-04-04 paper/manuscript.Rmd
Update temporal SEM with weight as sum of sd instead of multiplication

@@
   bm_x = "log_bm_std",
-  bm_y = c("ct_ff", "w_trph_lvl_avg", "piel_bm"), #, "piel_nind"
-  rich_y = c("ct_ff", "w_trph_lvl_avg", "log_bm_std", "piel_bm"), #, "piel_nind"
+  bm_y = c("ct_ff", "w_trph_lvl_avg"), #, "piel_nind"
+  rich_y = c("ct_ff", "w_trph_lvl_avg", "log_bm_std", #, "piel_nind"
   rich_x = "log_rich_std"
@@
 p_bm <- fig1_2$bm
-names(p_bm) <- c("ct_ff", "w_trph_lvl_avg", "piel_bm")
+names(p_bm) <- c("ct_ff", "w_trph_lvl_avg")
 #plot_grid(plotlist = p_bm)
@@
 p_sp_bm <- sp_fig1_2_bm_rich_mono_stable_trends$bm
-names(p_sp_bm) <- c("log_rich_std", "ct_ff", "w_trph_lvl_avg",
-  "piel_bm", "piel_nind")
+names(p_sp_bm) <- c("log_rich_std", "ct_ff", "w_trph_lvl_avg")
 ```

### 2022-04-04 sem.Rmd
Update temporal SEM with weight as sum of sd instead of multiplication

@@
 )
+library(DiagrammeR)
+DiagrammeR::render_graph(graph)
+```
+```{r}
+plot.psem <- function(
+  x,
+  return=FALSE,
+  node_attrs = data.frame(shape = "rectangle", color = "black",
+    fillcolor = "white"),
+  edge_attrs = data.frame(style = "solid", color="black"),
+  ns_dashed = T, alpha=0.05,
+  show = "std", digits = 3, 
+  add_edge_label_spaces = TRUE, ...
+  ){
+
+  #get the coefficients table
+  ctab <- coefs(x)
+  ctab$Response <- as.character(ctab$Response)
+  ctab$Predictor <- as.character(ctab$Predictor)
+
+  #make a nodes DF
+  unique_nodes <- unique(c(ctab$Response, ctab$Predictor))
+  nodes <- create_node_df(n = length(unique_nodes),
+    nodes = unique_nodes,
+    type = "lower",
+    label = unique_nodes)
+  nodes <- cbind(nodes, node_attrs)
+  nodes[] <- lapply(nodes, as.character)
+  nodes$id <- as.numeric(nodes$id)
+
+  #make an edges DF
+  edges <- create_edge_df(
+    from = match(ctab$Predictor, unique_nodes),
+    to = match(ctab$Response, unique_nodes))
+
+  edges <- data.frame(edges, edge_attrs)
+  edges[] <- lapply(edges, as.character)
+  edges$id <- as.numeric(edges$id)
+  edges$from <- as.numeric(edges$from)
+  edges$to <- as.numeric(edges$to)
+  if(ns_dashed) edges$style[which(ctab$P.Value>alpha)] <- "dashed"
+  if(show == "std") edges$label = round(ctab$`Std.Estimate`, digits)
+  if(show == "unstd") edges$label = round(ctab$Estimate, digits)
+  if(add_edge_label_spaces) edges$label = paste0(" ", edges$label, " ")
+
+  #turn into a graph
+  sem_graph <- create_graph(nodes, edges, directed=TRUE)
+
+  if(return) return(sem_graph)
+
+  render_graph(sem_graph, ...)
+
+}
 ```
@@
 ```{r}
+library(drake)
 loadd(slope_com_var_no_covar, st_mono_trends_rich_bm)
@@
   select(station, starts_with(var_analysis)) %>%
-  na.omit()
+  na.omit() %>%
+  mutate(
+    error_mult_ct =
+      (log_rich_std_strd_error * log_bm_std_strd_error *
+        ct_ff_strd_error),
+      error_mult_tlvl =
+        (log_rich_std_strd_error * log_bm_std_strd_error *
+          w_trph_lvl_avg_strd_error),
+        error_mult_bm = 
+          (log_rich_std_strd_error * log_bm_std_strd_error),
+        error_additive_ct = 
+          (log_rich_std_strd_error + log_bm_std_strd_error +
+            ct_ff_strd_error),
+          error_additive_tlvl =
+            (log_rich_std_strd_error + log_bm_std_strd_error +
+              w_trph_lvl_avg_strd_error),
+            error_additive_bm = (log_rich_std_strd_error + log_bm_std_strd_error)
+  )
 ```
@@
     shape = "rectangle", fixedsize = TRUE, width = 1, color = "black",
-    fillcolor = "lightgrey")
+    fillcolor = "lightgrey"),
+  layout = "tree"
 )
+render_graph
 ```
@@
 ```
+
+# Weight
+
+#
+
+```{r}
+weight_df <- data_tps_sem %>%
+  select(c(station, starts_with("error"))) %>%
+  pivot_longer(-station, names_to = "variable", values_to = "value") %>%
+  mutate(variable = str_remove(variable, "error_")) %>%
+  separate(variable, c("type", "variable"), sep = "_") %>%
+  group_by(type, variable) %>%
+  mutate(weight = value / sum(value))
+weight_df %>%
+  summarise(sum_weight = sum(weight))
+weight_df %>%
+  ggplot(aes(x = weight)) +
+  geom_histogram() +
+  facet_grid(rows = vars(variable), cols = vars(type), scale = "free_x")
+```
+
+- La distribution des poids est super asymétrique avec les multiplications de
+  standard deviation, c'est pour ça que ça merde
+- Ci-dessous, j'ai refais les sem avec des poids additifs, les échantillons des
+  bootstraps sont nettement plus stables
+
+```{r}
+semeff_mult_weight <- semEff(sem, R = 150, seed = 123, parallel = "no",
+  ci.type = "perc"
+)
+
+sem_no_weight <- list(
+  lm(ct_ff ~ log_bm_std + log_rich_std, data = data_tps_sem),
+  lm(w_trph_lvl_avg ~ log_bm_std + log_rich_std, data = data_tps_sem),
+  lm(log_bm_std ~ log_rich_std, data = data_tps_sem)
+)
+
+sem_additive_weight <- list(
+  lm(ct_ff ~ log_bm_std + log_rich_std, data = data_tps_sem,
+    weight = 1 / (log_rich_std_strd_error + log_bm_std_strd_error +
+      ct_ff_strd_error)),
+  lm(w_trph_lvl_avg ~ log_bm_std + log_rich_std, data = data_tps_sem,
+    weight = 1 / (log_rich_std_strd_error + log_bm_std_strd_error +
+      w_trph_lvl_avg_strd_error)),
+  lm(log_bm_std ~ log_rich_std, data = data_tps_sem,
+    weight = 1 / (log_rich_std_strd_error + log_bm_std_strd_error)
+  )
+)
+
+semeff_no_weight <- semEff(sem_no_weight, R = 100, seed = 123, parallel = "no",
+  ci.type = "perc"
+)
+semeff_additive_weight <- semEff(sem_additive_weight, R = 100, seed = 123, parallel = "no",
+  ci.type = "perc"
+)
+semeff_avg_weight <- semEff(sem_avg_weight, R = 100, seed = 123, parallel = "no",
+  ci.type = "perc"
+)
+```
+
+```{r}
+semeff_add_weight_tab <- from_semEff_to_table(semeff_avg_weight) %>%
+  mutate(
+    response = var_replacement(several_lines = TRUE)[response],
+    predictor = var_replacement(several_lines = TRUE)[predictor]
+
+  )
+semeff_no_weight_tab <- from_semEff_to_table(semeff_no_weight) %>%
+  mutate(
+    response = var_replacement(several_lines = TRUE)[response],
+    predictor = var_replacement(several_lines = TRUE)[predictor] 
+  )
+
+semeff_mult_weight_tab <- from_semEff_to_table(semeff_mult_weight) %>%
+  mutate(
+    response = var_replacement(several_lines = TRUE)[response],
+    predictor = var_replacement(several_lines = TRUE)[predictor] 
+  )
+```
+
+```{r}
+plot.semeff <- function(
+  x,
+  return=FALSE,
+  node_attrs = data.frame(
+    shape = "rectangle", fixedsize = TRUE, width = 1, color = "black",
+    fillcolor = "lightgrey"),
+  edge_attrs = data.frame(style = "solid", color="black"),
+  ns_dashed = T, alpha=0.05,
+  show = "ci", digits = 2,
+  width_eff = TRUE, scale_fc = 1, 
+  attr_theme = "default",
+  add_edge_label_spaces = TRUE, ...
+  ){
+
+  #get the coefficients table
+  ctab <- x %>%
+    filter(effect_type == "direct")
+
+  #make a nodes DF
+  unique_nodes <- unique(c(ctab$response, ctab$predictor))
+  nodes <- create_node_df(n = length(unique_nodes),
+    nodes = unique_nodes,
+    type = "lower",
+    label = unique_nodes)
+  nodes <- cbind(nodes, node_attrs)
+  nodes[] <- lapply(nodes, as.character)
+  nodes$id <- as.numeric(nodes$id)
+
+  #make an edges DF
+  edges <- create_edge_df(
+    from = match(ctab$predictor, unique_nodes),
+    to = match(ctab$response, unique_nodes))
+
+  edges <- data.frame(edges, edge_attrs)
+  edges[] <- lapply(edges, as.character)
+  edges$id <- as.numeric(edges$id)
+  edges$from <- as.numeric(edges$from)
+  edges$to <- as.numeric(edges$to)
+  if(ns_dashed) edges$style[which(sign(ctab$lower_ci) != sign(ctab$upper_ci))] <- "dashed"
+  if(width_eff) edges$penwidth <- abs(ctab$effect) * scale_fc 
+  if(show == "std") edges$label = round(ctab$effect, digits)
+  if(show == "ci") { edges$label = paste0(
+    round(ctab$effect, digits),
+    " [", round(ctab$lower_ci, digits),"; ",
+    round(ctab$upper_ci, digits), "]"
+  )
+    }
+  if(add_edge_label_spaces) edges$label = paste0(" ", edges$label, " ")
+
+  #turn into a graph
+  sem_graph <- create_graph(nodes, edges, directed=TRUE,
+    attr_theme = attr_theme)
+
+  if(return) return(sem_graph)
+
+  render_graph(sem_graph, ...)
+
+}
+```
+
+```{r}
+p_semeff_add_weight_tab <- plot.semeff(
+  x = semeff_add_weight_tab,
+  show = "ci",
+  node_attrs = data.frame(
+    shape = "rectangle", fixedsize = TRUE, width = 1.1, color = "black",
+    fillcolor = "lightgrey"),
+  edge_attrs = data.frame(style = "solid",  color="black"),
+  scale_fc = 15,
+  return = TRUE, attr_theme = "tb"
+)
+
+export_graph(
+  graph = p_semeff_add_weight_tab,
+  file_name = here::here("figures", "sem_tps_avg_weight.svg"),
+  file_type = "svg"
+)
+
+p_semeff_no_weight_tab <- plot.semeff(
+  x = semeff_no_weight_tab,
+  show = "ci",
+  node_attrs = data.frame(
+    shape = "rectangle", fixedsize = TRUE, width = 1.1, color = "black",
+    fillcolor = "lightgrey"),
+  edge_attrs = data.frame(style = "solid",  color="black"),
+  scale_fc = 15,
+  return = TRUE, attr_theme = "tb"
+)
+render_graph(p_semeff_no_weight_tab)
+
+export_graph(
+  graph = p_semeff_no_weight_tab,
+  file_name = here::here("figures", "sem_tps_no_weight.svg"),
+  file_type = "svg"
+)
+
+p_semeff_mult_weight_tab <- plot.semeff(
+  x = semeff_mult_weight_tab,
+  show = "ci",
+  node_attrs = data.frame(
+    shape = "rectangle", fixedsize = TRUE, width = 1.1, color = "black",
+    fillcolor = "lightgrey"),
+  edge_attrs = data.frame(style = "solid",  color="black"),
+  scale_fc = 15,
+  return = TRUE, attr_theme = "tb"
+)
+
+export_graph(
+  graph = p_semeff_mult_weight_tab,
+  file_name = here::here("figures", "sem_tps_mult_weight.svg"),
+  file_type = "svg"
+)
+
+```
+
+### Multiplicative weight
+
+```{r}
+render_graph(p_semeff_mult_weight_tab)
+```
+
+### Additive weight
+
+```{r}
+render_graph(p_semeff_add_weight_tab)
+```
+
+### No weight
+
+```{r}
+render_graph(p_semeff_no_weight_tab)
+```

### 2022-04-04 supplementary.Rmd
Update temporal SEM with weight as sum of sd instead of multiplication

@@
 library(semEff)
+library(lme4)
 ```
@@
 loadd(sp_st_data)
-library(nlme)
 
@@
 )
-summary(sp_sem[[4]])
 sp_psem <- as.psem(sp_sem)

### 2022-04-05 paper/manuscript.Rmd
Update figures

@@
    - \usepackage{float}
-   - \usepackage[table]{xcolor}
    - \usepackage{multirow}
@@
   warning = FALSE,
-  results = TRUE
+  results = TRUE,
+  fig.path="figures/"
 )
@@
   bm_y = c("ct_ff", "w_trph_lvl_avg"), #, "piel_nind"
-  rich_y = c("ct_ff", "w_trph_lvl_avg", "log_bm_std", #, "piel_nind"
+  rich_y = c("ct_ff", "w_trph_lvl_avg", "log_bm_std"), #, "piel_nind"
   rich_x = "log_rich_std"
@@
 p_bm <- fig1_2$bm
-names(p_bm) <- c("ct_ff", "w_trph_lvl_avg")
-#plot_grid(plotlist = p_bm)
-
-p_sp_bm <- sp_fig1_2_bm_rich_mono_stable_trends$bm
-names(p_sp_bm) <- c("log_rich_std", "ct_ff", "w_trph_lvl_avg")
+
+p_sp_bm <- sp_fig1_2_bm_rich_mono_stable_trends$bm[c("log_rich_std", "ct_ff", "w_trph_lvl_avg")]
 ```
@@
 
-ggMarginal(p_bef, type = "histogram")
 ```
@@
 # Delete redondant legend
-fig2$bm[1:2] <- map(fig2$bm[1:2],
-  ~ .x + theme(
+fig2$bm[[1]] <- fig2$bm[[1]] + theme(
   axis.text.x = element_blank(),
@@
   axis.title.x = element_blank()
-  )
   )
@@
   )
-fig2$rich[1:2] <- map(fig2$rich[1:2],
-  ~ .x + theme(
+fig2$rich[[1]] <- fig2$rich[[1]] + theme(
   axis.text.x = element_blank(),
@@
 # Add histograms
-fig2$bm[[1]] <- ggMarginal(fig2$bm[[1]], type = "histogram", margins = "x")
-fig2$rich[[1]] <- ggMarginal(fig2$rich[[1]], type = "histogram", margins = "both")
-fig2$rich[2:3] <- map(fig2$rich[2:3], ~ggMarginal(.x, type = "histogram", margins = "y"))
-```
-
-```{r bmr, out.width="80%", fig.height=7, fig.cap=fig_bm_rich_cap}
+p_bef2 <- p_bef +
+  theme(
+  axis.text.x = element_blank(),
+  axis.ticks.x = element_blank(),
+  axis.title.x = element_blank()
+  ) 
+p_bef_hist <- ggMarginal(p_bef2, type = "histogram")
+#fig2$bm[[1]] <- ggMarginal(fig2$bm[[1]], type = "histogram", margins = "x")
+fig2$rich[[1]] <- ggMarginal(fig2$rich[[1]], type = "histogram", margins = "y")
+fig2$rich[[2]] <- ggMarginal(fig2$rich[[2]], type = "histogram", margins = "y")
+```
+
+```{r}
+sem_cap <- "Structural equation models on the temporal trends of the food-web
+structure. The path display the standardized slopes and their associated 95%
+  confidence intervals."
+```
+
+```{r sem, fig.cap = sem_cap}
+ti <- magick::image_read(here::here("figures", "sem_tps_avg_weight_ok.svg"),  density = 300)
+ggdraw() +
+  draw_image(ti,
+    x = 0, y = 0, hjust = 0, vjust = 0, width = .9, height = 1)
+```
+
+```{r bmr, out.width="100%", fig.height=7, fig.cap=fig_bm_rich_cap}
+p <- draw_image(here::here("figures", "sem_tps_avg_weight_ok.pdf"),
+  x = 1, y = 1, hjust = 1, vjust = 1, width = 0.13, height = 0.2)
+biplot_model <- plot_grid(
+  plot_grid(, p_bef_hist,
+    labels = c("", "A"), ncol = 2,
+    rel_widths = c(.62, 1)
+    ),
   plot_grid(
   plot_grid(plotlist = fig2$bm,
-    ncol = 1, labels = c("A", "B", "C"),
+    ncol = 1, labels = c("B", "D"),
     hjust = -5.5, vjust = 1.75
@@
   plot_grid(plotlist = fig2$rich,
-    ncol = 1, labels = c("D", "E", "F"),
+    ncol = 1, labels = c("C", "E"),
     hjust = -2, vjust = 1.75
@@
   ncol = 2,
-  rel_widths = c(1, 1)
-)
+  rel_widths = c(.85, 1)
+  ),
+  nrow = 2,
+  rel_heights = c(.6, 1)
+)
+save_plot(
+  filename = here::here("figures", "biplot_model.png"),
+  biplot_model)
+
+biplot_model
 ```
@@
 std_cap <- paste0(
-  "Assessment of the space-for-time hypothesis. Effect of community biomass (top
-  panel) and species richness (bottom panel) on food-web structure for the
-temporal and spatial models. The bar tops display the standardized slope coefficients
-from the models ($r_\\delta$), the lines around bar tops display the standard errors.")
-```
-
-```{r std, fig.cap=std_cap, fig.width=6}
+  "Assessment of the space-for-time hypothesis. Standardized coefficients
+  ($r_\\delta$) derived from the spatial and temporal Structural Equation
+  Models. The left, middle and right panels display respectively the direct,
+  indirect and total effects of community biomass and species richness on the
+  Average trophic level (top panel), the connectance (middle panel) and the
+  community biomass (bottom panel) The lines display the confidence intervals at
+  95%.")
+
+```
+
+```{r std-old, eval = FALSE, fig.cap=std_cap, fig.width=6}
 #loadd(fig_std_coef)
@@
       breaks = NULL, labels = NULL))
+```
+
+```{r std, fig.cap=std_cap, fig.width=6, fig.height = 9}
+load(here::here("data", "semeff.rda"))
+load(here::here("data", "sp_semeff.rda"))
+sp_semeff_tab <- from_semEff_to_table(sp_semeff)
+semeff_tab <- from_semEff_to_table(semeff)
+
+semeff_tot <- rbind(
+  tibble(semeff_tab, model = "temporal"),
+  tibble(sp_semeff_tab, model = "spatial")
+  ) %>%
+filter(
+  !predictor %in% c("log_RC1", "log_RC2"),
+  effect_type != "mediators"
+)
+
+semeff_tot %>%
+  mutate(
+    response = var_replacement()[response],
+    predictor = var_replacement()[predictor]
+    ) %>%
+  ggplot(aes(x = predictor, y = effect, color = model)) +
+  geom_hline(yintercept = 0) +
+  geom_pointrange(aes(ymin = lower_ci, ymax = upper_ci), position = position_dodge(width = 0.4)) +
+  facet_grid(rows = vars(response), cols = vars(effect_type)) +
+  labs(
+    x = "Predictor",
+    y = expression(paste("Standardized slope coefficients ", r[delta])),
+    color = "Model") +
+  theme(axis.text.x = element_text(angle = 20, hjust = 1))
 ```

### 2022-04-05 R/packages.R

@@ -13,3 +13,4 @@ library(broom)
 library(broom.mixed)
 library(piecewiseSEM)
 library(semEff)
+library(DiagrammeR)

### 2022-04-05 R/plan.R

@@ -531,7 +531,24 @@ model_vif = get_vif(model,
       log_bm_std, log_bm_std_strd_error,
       log_rich_std, log_rich_std_strd_error,
       w_trph_lvl_avg, w_trph_lvl_avg_strd_error) %>%
-    na.omit(),
+    na.omit() %>%
+    mutate(
+      error_mult_ct =
+        (log_rich_std_strd_error * log_bm_std_strd_error *
+          ct_ff_strd_error),
+        error_mult_tlvl =
+          (log_rich_std_strd_error * log_bm_std_strd_error *
+            w_trph_lvl_avg_strd_error),
+          error_mult_bm = 
+            (log_rich_std_strd_error * log_bm_std_strd_error),
+          error_additive_ct = 
+            (log_rich_std_strd_error + log_bm_std_strd_error +
+              ct_ff_strd_error),
+            error_additive_tlvl =
+              (log_rich_std_strd_error + log_bm_std_strd_error +
+                w_trph_lvl_avg_strd_error),
+              error_additive_bm = (log_rich_std_strd_error + log_bm_std_strd_error)
+    ),
   sem_tps = list(
     lm(
       ct_ff ~ log_bm_std + log_rich_std,
@@ -551,9 +568,28 @@ model_vif = get_vif(model,
       weight = 1 / (log_rich_std_strd_error + log_bm_std_strd_error)
     )
     ),
-  semeff = semEff(sem_tps, R = 1000, seed = 13, parallel = "no"),
+  semeff = get_tps_semeff(sem = sem_tps, data_tps_sem = data_tps_sem),
+  sem_tps_no_weight = list(
+    lm(ct_ff ~ log_bm_std + log_rich_std,
+      data = data_tps_sem),
+    lm(w_trph_lvl_avg ~ log_bm_std + log_rich_std,
+      data = data_tps_sem),
+    lm(log_bm_std ~ log_rich_std,
+      data = data_tps_sem)
+    ),
+  semeff_no_weight = get_tps_semeff(sem = sem_tps_no_weight),
 
-
+  weight_df = data_tps_sem %>%
+    select(c(station, starts_with("error"))) %>%
+    pivot_longer(-station, names_to = "variable", values_to = "value") %>%
+    mutate(variable = str_remove(variable, "error_")) %>%
+    separate(variable, c("type", "variable"), sep = "_") %>%
+    group_by(type, variable) %>%
+    mutate(weight = value / sum(value)),
[…]

### 2022-04-05 R/sem_helpers.R

@@ -42,3 +42,25 @@ from_semEff_to_table <- function(x = NULL) {
   output[, colnames(output) != "bias"]
 
 }
+
+get_tps_semeff <- function(
+  sem = NULL,
+  data_tps_sem = data_tps_sem
+  ) {
+
+  semeff <- semEff(sem, R = 1000, seed = 13, parallel = "no",
+    ci.type = "perc")
+  return(semeff)
+
+}
+
+get_sp_semeff <- function(
+  sem = NULL,
+  data_sp_sem = data_sp_sem
+  ) {
+
+  semeff <- semEff(sem, R = 1000, seed = 13, parallel = "no",
+    type = "parametric", ci.type = "perc")
+  return(semeff)
+
+}

### 2022-04-05 make.R

@@ -27,17 +27,13 @@ gc()
 plan
 print(plan, n = 40)
 
-library(future)
-plan(multisession, workers = 3)
-
-loadd(data_tps_sem)
 loadd(sem_tps)
-
-semeff <- semEff(sem_tps, R = 10000, seed = 13, parallel = "no")
-save(semeff, file = get_mypath("data", "semeff.rda"))
+semeff <- get_tps_semeff(sem = sem_tps)
+save(semeff, file = here::here("data", "semeff.rda"))
 
 loadd(sp_sem, data_sp_sem)
-sp_semeff <- semEff(sp_sem, R = 10000, seed = 13, parallel = "no", type = "parametric")
-save(sp_semeff, file = get_mypath("data", "sp_semeff.rda"))
+sp_semeff <- get_sp_semeff(sem = sp_sem)
+save(sp_semeff, file = here::here("data", "sp_semeff.rda"))
+
 
 drake::drake_cache("/home/alain/Documents/post-these/mnhn/fishcom_biomass_dynamics/.drake")$unlock()

### 2022-05-02 paper/appendix.Rmd
semeff results + results + discussion

@@
 # Statistical analysis
+
+## Proportion and number of piscivorous species
+
+```{r}
+loadd(rigal_classification, st_mono_trends_stable_rich_bm, full_data2)
+full_data2 %>%
+  select(richness, nb_pisc_rich, nb_non_pisc_rich)
+unique(rigal_classification$variable)
+var_pisc_mod <- c("nb_pisc_rich_std", "prop_pisc_rich", "nb_non_pisc_rich_std",
+    "prop_non_pisc_rich",
+      "log_rich_std", "log_bm_std")
+pisc_data <- map(var_pisc_mod,
+    function(x, var_to_keep, classif_var) {
+
+      x_data <- classif_var[classif_var$variable == x, ] %>%
+	unnest(classif)
+      x_data <- x_data[, colnames(x_data) %in% var_to_keep]
+
+      # Rename according to the variable
+      colnames(x_data)[colnames(x_data) %in% var_to_keep[2:3]] <-
+	paste0(x, c("", "_strd_error"))
+      return(x_data)
+
+    },
+    var_to_keep = c("station", "linear_slope", "linear_slope_strd_error"),
+  classif_var = rigal_classification) %>%
+  Reduce(merge.all, .) %>%
+  filter(station %in% st_mono_trends_stable_rich_bm) %>%
+  na.omit()
+
+# for standardized coefficients 
+pisc_data_scaled <- pisc_data %>%
+  mutate(across(all_of(var_pisc_mod), ~ scale(., center = FALSE)[,1]))
+
+pisc_mod_std <- tibble(
+  response = c("nb_pisc_rich_std", "nb_non_pisc_rich_std", "prop_pisc_rich", "prop_non_pisc_rich"),
+  mod = list(
+    lm(
+      nb_pisc_rich_std ~ log_bm_std + log_rich_std,
+      data = pisc_data_scaled,
+      weight = 1 / (log_rich_std_strd_error + log_bm_std_strd_error +
+        nb_pisc_rich_std_strd_error)
+      ),
+    lm(
+      nb_non_pisc_rich_std ~ log_bm_std + log_rich_std,
+      data = pisc_data_scaled,
+      weight = 1 / (log_rich_std_strd_error + log_bm_std_strd_error +
+        nb_non_pisc_rich_std_strd_error)
+      ),
+    lm(
+      prop_pisc_rich ~ log_bm_std + log_rich_std,
+      data = pisc_data_scaled,
+      weight = 1 / (log_rich_std_strd_error + log_bm_std_strd_error +
+        prop_pisc_rich_strd_error)
+      ),
+    lm(
+      prop_non_pisc_rich ~ log_bm_std + log_rich_std,
+      data = pisc_data_scaled,
+      weight = 1 / (log_rich_std_strd_error + log_bm_std_strd_error +
+        prop_non_pisc_rich_strd_error)
+      )
+  )
+  )
+
+pisc_mod_std <- pisc_mod_std %>%
+  mutate(
+    coefs = map(mod, broom::tidy),
+    perf = map(mod, broom::glance) 
+  )
+
+pisc_mod_std %>%
+  select(response, coefs) %>%
+  unnest(coefs)
+```
 

### 2022-05-02 paper/manuscript.Rmd
semeff results + results + discussion

@@
 output:
+  bookdown::word_document2:
+    fontsize: 12pt
   bookdown::pdf_document2:
@@
     toc: true
-  bookdown::word_document2:
     fontsize: 12pt
@@
     geometry: margin=2cm
+    number_sections: true
 bibliography: references.bib
-number_sections: true
 ---
@@
 loadd(reg_table_bm_rich_mono_stable_trends)
+load(here::here("data", "semeff.rda"))
+load(here::here("data", "sp_semeff.rda"))
 ```
@@
 ---
-## Variations of community biomass and species richness are predicted to affect community structure
-#Changes of species richness and community biomass are indeed
+## Variations of community biomass and species richness are predicted to affect
+community structure #Changes of species richness and community biomass are
+indeed
 #predicted to affect community structure. The positive link between biodiversity
@@
 ## Variations of community biomass and species richness are predicted to affect food-web structure
+
 ---
@@
 
-## Relationships among temporal trends
-
-We modelled the relationships among the temporal trends of food-web structure
-($dN$), that is connectance, average trophic level and evenness of biomass, and
-the temporal trends of community biomass ($dB$) and species richness ($dR$) with
-Ordinary Least Squares. The simultaneous assessment of the
-effects of species richness and community biomass allows to tease apart their
-respective effect on food-web structure.
-
-$dN_j = \alpha + \beta_1dB_j + \beta_2dR_j + \epsilon_j$
-
-With:
-
-  - $dN$: temporal trends of food-web structure: connectance, average trophic
-    level and evenness of biomass across species
-  - $dB$: temporal trend of ($\log_e$) community biomass
-  - $dR$: temporal trend of ($\log_e$) species richness
-  - $j$: the site
-  - $\alpha$: intercept 
-  - $\beta$: slope 
-  - $\epsilon$: gaussian error
-
-In order to control for the uncertainties of the estimated temporal trends, each
-temporal trend was weighted by the inverse of the product of the standard errors
-of the estimated trends, i.e. estimated slopes for the response and the
-explicative variables ($w_j = \dfrac{1}{s_{r_j} s_{e,j}}$, $w_j$ being the
-weight, $s_{r_j}$ and $s_{e_j}$ being respectively the standard errors on the
-temporal trends of the response and explicative variables). We also included a
-statistical model including the interaction between the temporal trends of
-species richness and community biomass (i.e.  adding $\beta_3dB_jdR_j$), the
-results are presented in supplementary material (Fig.  SXX). To model the
-relationships between the temporal trends of community biomass and the one of
-species richness, we built the model as $dB_j = \alpha_j + \beta_1dR_j +
-\epsilon_j$.
-
-## Relationships along spatial gradient
-
-Spatial variation of food-web structure are partly driven by environmental gradients, so
-we controlled relationships among variables by adding two PCA axis
+We modelled the relationships among food-web structure, that is
+connectance and average trophic level, and community biomass ($dB$) and species
+richness ($dR$) with Structural Equation Models. We modelled a it such as species
+richness is related to community biomass and food-web structure. In
+turn community biomass was related to food-web structure. We computed one
+structural equation model to assess the relationships among the temporal trends
+and one for the relationships over the spatial gradient. As spatial variation of
+food-web structure are partly driven by environmental gradients, so we
+controlled relationships among variables by adding two PCA axis
 synthesizing respectively (1) stream gradient from upstream to downstream and
@@
 
-[^2]: commentaire de colin: il faudrait introduire spatial gradient des l'intro
-et cette partie est plutot sur les relationships among spatial gradient of biodiv facets
-
-$N_j = \alpha + \beta_1B_j + \beta_2R_j + \beta_3E_{1,j} + \beta_4E_{2,j} + \epsilon_j + \epsilon_{\alpha|i}$
-
-With:
-
-  - $N_j$: median food-web structure 
-  - $B_j$: median community biomass ($g.m^-2$) 
-  - $R_j$: median species richness ($m^-2$) 
-  - $E_{1,j}$: First PCA axis 
-  - $E_{2,j}$: Second PCA axis
-  - $\epsilon_{\alpha|i}$: random effect of the hydrographic basin
-    $i$ on $\alpha$
-
-To model the relationships between community biomass and species richness along
-the spatial gradient, we built the equation as $B_j = \alpha + \beta_1R_j +
-\beta_3E_{1,j} + \beta_4E_{2,j} + \epsilon_j$.
-
-In order to compare the magnitude of the effects of community biomass and
-species richness in both temporal and spatial models, we computed standardized
-slopes ($r_{\delta}$) and their associated standard errors as $r_{\delta} =
-\beta\frac{s_x}{s_y}$.  With $\beta$ being the unstandardised slope, $s_x$ and
-$s_y$ the standard deviation of the explicative and response variables.
+In order to control for the uncertainties of the estimated temporal trends, each
+temporal trend was weighted by the inverse of the sum of the standard errors
+of the estimated trends, i.e. estimated slopes for the response and the
+explicative variables ($w_j = \dfrac{1}{\sum{e_j}}$, $w_j$ being the
+weight, and $s_{e_j}$ the standard error on the
+temporal trends of the variables).
+
+The coefficients of the Structural Equation Models were computed with
+PiecewiseSEM R package [@lefcheck_piecewisesem_2016]. The coefficients were
+standardizated and the confidence intervals were computed with semEff R package
+[@murphy_semEff_2021]. Confidence intervals were obtained by bootstrapping the
+linear models 1000 times and computing adjusted bootstrap percentile interval
+(BCa), which are adjusted for asymetric distribution of resampling.
 
 All the statistical models displayed low multicollinearity (Variance inflation
-factor < 3, Table SXX).  We visually inspected the residuals of the linear models.
+factor < 3, Table SXX).  We visually inspected the residuals of the linear
+models.
 
@@
 ```{r}
-rsq_piel_nind <- rsq_table_bm_rich_mono_stable_trends %>%
-  filter(Response == "piel_nind") %>%
+rsq_ct <- rsq_table_bm_rich_mono_stable_trends %>%
+  filter(Response == "ct_ff") %>%
   .$R.squared %>%
-  round(., 3)
-
-rsq_tlvl <- rsq_table_bm_rich_mono_stable_trends %>%
-  filter(Response == "w_trph_lvl_avg") %>%
+  round(., 2)
+
+rsq_bm <- rsq_table_bm_rich_mono_stable_trends %>%
+  filter(Response == "log_bm_std") %>%
   .$R.squared %>%
-  round(., 3)
+  round(., 2)
 
@@
   .$Conditional %>%
-  round(., 3)
-
-rsq_piel_bm_sp <- sp_rsq_table_bm_rich_mono_stable_trends %>%
-  filter(Response == "piel_bm") %>%
+  round(., 2)
+
+rsq_ct_sp <- sp_rsq_table_bm_rich_mono_stable_trends %>%
+  filter(Response == "ct_ff") %>%
   .$Conditional %>%
-  round(., 3)
+  round(., 2)
 ```
@@
 
-Overall, we found high heterogeneity in the explicative power of statistical
-models linking temporal dynamics of food-web structure, evenness of biomass  and the one of community
-biomass and species richness spanning from $R_{adj}^2= `r rsq_piel_nind`$ for
-the evenness of abundances to $R_{adj}^2= `r rsq_tlvl`$ for average trophic
-level (Table SXX). The models over the spatial gradient were more performant, with
-$R_{cond}^2$ varing from $`r rsq_tlvl_sp`$ to $`r rsq_piel_bm_sp`$ (Table
-SXX), $R_{cond}^2$ being the $R^2$conditional to the random effect.
+Overall, we found relatively low in the explicative power of statistical
+models linking temporal dynamics of food-web structure and the one of community
+biomass and species richness spanning from $R_{adj}^2= `r rsq_ct`$ for
+connectance to $R_{adj}^2= `r rsq_bm`$ for community biomass (Table SXX).
+The models over the spatial gradient were more performant, with
+$R_{cond}^2$ varing from $`r rsq_tlvl_sp`$ for the average trophic level to
+$`r rsq_ct_sp`$ for connectance (Table SXX), $R_{cond}^2$ being the
+$R^2$conditional to the random effect.
 
@@
 
-```{r bef, fig.cap=fig_bef_cap, out.width="50%"}
-lab_log_rich <- expression(atop("Log species richness ("*m^{-2}*")","trend slope (log / % per year)"))
-lab_log_bm <- expression(atop("Log community biomass ("*g.m^{-2}*")", "trend slope (log / % per year)"))
-
-p_bef <- fig1_2$rich$log_bm_std +
-  annotate("text", x = .1, y = -.5, parse = T,
-    label = beta_rsq(
-      rsq = coeff_bef["rsq"],
-      beta = coeff_bef["estimate"],
-      se = coeff_bef["std.error"]
-    )
-   ) +
-  labs(
-    y = lab_log_bm,
-    x = lab_log_rich
-  ) +
-scale_xy_log_trends(breaks = c(-.10, -.050, 0, .050, .10), axis = "x") +
-scale_xy_log_trends(breaks = c(-.4, -.2, 0, .4, .2), axis = "y", sep = " / ")
-
-```
-
 We found a strong positive relationship between the temporal trends of community
 biomass and the ones of species richness ($r_\delta = `r tps_r_sest["p_bm"]`$,
-Fig. \@ref(fig:bef)), meaning that both temporal trends
+Fig. \@ref(fig:bmr) B), meaning that both temporal trends
 had the same direction in average. At the sites 
@@
 a positive relationship between median connectance and median species
-richness ($r_\delta = `r sp_b_sest["ct"]`$). However, we did not observe
-significant relationships between the temporal trends of connectance and the
-ones of species richness (Fig. \@ref(fig:bmr)D) while we found a stong
-negative relationship between median connectance and median species richness
-along the spatial gradient
+richness ($r_\delta = `r sp_b_sest["ct"]`$). We found a negative 
+relationship between the temporal trends of connectance and the
+ones of species richness ($r_\delta = `r tps_r_sest["ct"]`$, Fig. \@ref(fig:bmr)D)
+while we found negative relationship three times stronger between median connectance and
+median species richness along the spatial gradient 
 ($r_\delta = `r sp_r_sest["ct"]`$, Fig. \@ref(fig:std)).
@@
 and *vice versa*. We also found a positive relationship between
-median average trophic level and median community biomass in space, but half the strength 
-as the temporal one ($r_\delta = `r sp_b_sest["tlvl"]`$, Fig. \@ref(fig:std)). The temporal trends of average
-trophic level was unrelated to the ones of species richness. It suggests that in
-communities either loosing or gaining species richness over time, the location of
-average biomass along trophic level did not significantly change according to
-species richnnes.  However, we found a strong negative relationship in space 
+median average trophic level and median community biomass in space, but half the
+strength as the temporal one ($r_\delta = `r sp_b_sest["tlvl"]`$, Fig.
+\@ref(fig:std)). The temporal trends of average trophic level was unrelated to
+the ones of species richness. It suggests that in communities either loosing or
+gaining species richness over time, the location of average biomass along
+trophic level did not significantly change according to species richnnes.
+However, we found a strong negative relationship in space 
 ($r_\delta = `r sp_r_sest["tlvl"]`$, Fig. \@ref(fig:std)).
 
-Evenness of biomass was negatively linked to community
-biomass in time and in space 
-($r_\delta = `r tps_bm_sest["p_bm"]`$ and $`r sp_b_sest["p_bm"]`$ resp.; Fig.
-\@ref(fig:bmr)C, Fig. \@ref(fig:std)). Regarding time, it means that food-webs that
-lost biomass over time also had a more even distribution of biomass across species over
-time and *vice versa*. A similar reasoning applies in space. On the
-other hand, we found a positive relationship between the temporal trends of
-biomass evenness and the one of species richness (Fig. \@ref(fig:bmr)F,
-$r_\delta = `r tps_r_sest["p_bm"]`$). We found the same relationship in space,
-twice as strong however ($r_\delta = `r sp_r_sest["p_bm"]`$).
+```{r}
+sp_semeff_tab <- from_semEff_to_table(sp_semeff)
+semeff_tab <- from_semEff_to_table(semeff)
+semeff
+semeff_tot <- rbind(
+  tibble(semeff_tab, model = "temporal"),
+  tibble(sp_semeff_tab, model = "spatial")
+  ) %>%
+filter(
+  !predictor %in% c("log_RC1", "log_RC2"),
+  effect_type != "mediators"
+)
+```
+
+```{r}
+semeff_tab_coeff <- semeff_tab %>%
+  mutate(across(where(is.numeric), ~round(., 2))) %>%
+  mutate(eci = paste0(effect, " [", lower_ci, ";", upper_ci, "]"))
+
+sp_semeff_tab_coeff <- sp_semeff_tab %>%
+  mutate(across(where(is.numeric), ~round(., 2))) %>%
+  mutate(eci = paste0(effect, " [", lower_ci, ";", upper_ci, "]")) %>%
+  filter(! predictor %in% c("log_RC1", "log_RC2"))
+
+ctsi <- semeff_tab_coeff %>%
+  filter(response == "ct_ff", effect_type == "indirect")
+ctstr <- semeff_tab_coeff %>%
+  filter(response == "ct_ff", effect_type == "total",
+    predictor == "log_rich_std")
+
+ctspi <- sp_semeff_tab_coeff %>%
+  filter(response == "ct_ff", effect_type == "indirect")
+ctsptr <- sp_semeff_tab_coeff %>%
+  filter(response == "ct_ff", effect_type == "total",
+    predictor == "log_rich_std")
+
+wtsi <- semeff_tab_coeff %>%
+  filter(response == "w_trph_lvl_avg", effect_type == "indirect")
+wtstr <- semeff_tab_coeff %>%
+  filter(response == "w_trph_lvl_avg", effect_type == "total",
+    predictor == "log_rich_std")
+
+wtspi <- sp_semeff_tab_coeff %>%
+  filter(response == "w_trph_lvl_avg", effect_type == "indirect")
+wtsptr <- sp_semeff_tab_coeff %>%
+  filter(response == "w_trph_lvl_avg", effect_type == "total",
+    predictor == "log_rich_std")
+```
+
+The structural model on the temporal trends of food-web structure reveals that
+the species richness has a direct negative effect on connectance but also a
+negative one, twice lower than the former, through community biomass
+($r_\delta$ = `r ctsi[["eci"]]`). It resulted a relatively weak total negative
+effect of species richness on connectance (`r ctstr[["eci"]]`). Spatially,
+we also found a positive indirect effect of richness on connectance through
+community biomass but a weak one (`r ctspi[["eci"]]`), resulting in a strong negative total
+effect of richness on connectance (`r ctsptr[["eci"]]`).
+
+The relationships among temporal trends showed a indirect positive effect of
+species richness on average trophic level (`r wtsi[["eci"]]`), resulting in a total positive
+effect of species richness on average trophic level (`r wtstr[["eci"]]`). Over the spatial
+gradient, we found the same positive indirect effect of richness through
+community biomass (`r wtspi[["eci"]]`). But as the direct effect of richness on connectance
+was strongly negative, it resulted in a total strong negative effect of species
+richness on connectance over the spatial gradient (`r wtsptr[["eci"]]`).
 
@@
 
+```{r bef, fig.cap=fig_bef_cap, out.width="50%"}
+lab_log_rich <- expression(atop("Log species richness ("*m^{-2}*")","trend slope (log / % per year)"))
+lab_log_bm <- expression(atop("Log community biomass ("*g.m^{-2}*")", "trend slope (log / % per year)"))
+
+p_bef <- fig1_2$rich$log_bm_std +
+  labs(
+    y = lab_log_bm,
+    x = lab_log_rich
+  ) +
+scale_xy_log_trends(breaks = c(-.10, -.050, 0, .050, .10), axis = "x") +
+scale_xy_log_trends(breaks = c(-.4, -.2, 0, .4, .2), axis = "y", sep = " / ") +
+    theme(
+      axis.text = element_text(size = 8),
+      axis.title = element_text(size = 10)
+      )
+
+```
+
 ```{r}
@@
     theme(
-      axis.text = element_text(size = 6),
-      axis.title = element_text(size = 8)
+      axis.text = element_text(size = 8),
+      axis.title = element_text(size = 10)
       )
@@
   ~ .x + theme(
-    axis.text = element_text(size = 6),
-    axis.title = element_text(size = 8)
+    axis.text = element_text(size = 8),
+    axis.title = element_text(size = 10)
     ) +
@@
 
-```{r}
+```{r, eval = FALSE}
 # Add beta and Rsq
@@
 ti <- magick::image_read(here::here("figures", "sem_tps_avg_weight_ok.svg"),  density = 300)
-ggdraw() +
+p <- ggdraw() +
   draw_image(ti,
@@
 ```{r bmr, out.width="100%", fig.height=7, fig.cap=fig_bm_rich_cap}
-p <- draw_image(here::here("figures", "sem_tps_avg_weight_ok.pdf"),
-  x = 1, y = 1, hjust = 1, vjust = 1, width = 0.13, height = 0.2)
+#p <- draw_image(here::here("figures", "sem_tps_avg_weight_ok.pdf"),
+#  x = 1, y = 1, hjust = 1, vjust = 1, width = 0.13, height = 0.2)
 biplot_model <- plot_grid(
-  plot_grid(, p_bef_hist,
+  plot_grid(NULL, p_bef_hist,
     labels = c("", "A"), ncol = 2,
-    rel_widths = c(.62, 1)
+    rel_widths = c(.54, 1)
     ),
@@
     ncol = 1, labels = c("B", "D"),
-    hjust = -5.5, vjust = 1.75
+    hjust = -5.5, vjust = 1.75,
+    rel_heights = c(.85, 1)
     ),
@@
     ncol = 1, labels = c("C", "E"),
-    hjust = -2, vjust = 1.75
+    hjust = -2, vjust = 1.75,
+    rel_heights = c(.85, 1)
     ),
   ncol = 2,
-  rel_widths = c(.85, 1)
+  rel_widths = c(.9, 1)
   ),
   nrow = 2,
-  rel_heights = c(.6, 1)
-)
+  rel_heights = c(.55, 1)
+)
+sem_p <- plot_grid(p, biplot_model, ncol = 2, rel_widths = c(.4, .6))
+
 save_plot(
-  filename = here::here("figures", "biplot_model.png"),
-  biplot_model)
-
-biplot_model
+  filename = here::here("paper", "figures", "biplot_tps.png"),
+  biplot_model, nrow = 3, ncol = 2, base_asp = 1)
+save_plot(
+  filename = here::here("paper", "figures", "sem_p.png"),
+  sem_p, nrow = 3, ncol =3)
+sem_p
 ```
@@
 ```{r std, fig.cap=std_cap, fig.width=6, fig.height = 9}
-load(here::here("data", "semeff.rda"))
-load(here::here("data", "sp_semeff.rda"))
-sp_semeff_tab <- from_semEff_to_table(sp_semeff)
-semeff_tab <- from_semEff_to_table(semeff)
-
-semeff_tot <- rbind(
-  tibble(semeff_tab, model = "temporal"),
-  tibble(sp_semeff_tab, model = "spatial")
-  ) %>%
-filter(
-  !predictor %in% c("log_RC1", "log_RC2"),
-  effect_type != "mediators"
-)
-
 semeff_tot %>%
@@
     ) %>%
-  ggplot(aes(x = predictor, y = effect, color = model)) +
+  ggplot(aes(x = predictor, y = effect, fill = effect_type)) +
+  geom_col(
+    position = position_dodge(width = 0.4), width = .4) +
   geom_hline(yintercept = 0) +
-  geom_pointrange(aes(ymin = lower_ci, ymax = upper_ci), position = position_dodge(width = 0.4)) +
-  facet_grid(rows = vars(response), cols = vars(effect_type)) +
+  geom_linerange(
+    aes(ymin = lower_ci, ymax = upper_ci),
+    position = position_dodge(width = 0.4)
+    ) +
+  facet_grid(rows = vars(response), cols = vars(model)) +
   labs(
@@
     y = expression(paste("Standardized slope coefficients ", r[delta])),
-    color = "Model") +
+    fill = "Effect type") +
   theme(axis.text.x = element_text(angle = 20, hjust = 1))
@@
 
-We found that most temporal trends of food-webs were classified as
-stable for species richness and community biomass. Roughly the same
-number of stations displayed temporal decrease and increase for species
-richness, and twice more stations displayed decrease in community biomass than
-increase. This result is in accordance with previous meta analysis on species
-richness trends of vertebrate in marine, freshwater and terrestrial systems
-[@dornelas_assemblage_2014; @blowes_geography_2019; @klink_meta-analysis_2020].
+Most temporal trends of for species richness and community biomasss were
+classified as stable. Roughly the same number of stations displayed temporal
+decrease and increase for species richness, and twice more stations displayed
+decrease in community biomass than increase. This result is in accordance with
+previous meta analysis on species richness trends of vertebrate in marine,
+freshwater and terrestrial systems, which show no change in species richness in
+average [@dornelas_assemblage_2014; @blowes_geography_2019] but an increase in
+total abundance [@klink_meta-analysis_2020].
 
@@
 Therefore, our results confirm that Biodiversity-Ecosystem functioning
-prediction works also in the temporal dynamics of food-webs. The positive
+prediction also hold in the temporal dynamics of food-webs. The positive
 relationship between species richness and total biomass might be due to positive
@@
 trends in community biomass and species richness are associated with very
-different temporal trends on the connectance, average trophic level and evenness
-of biomass. Indeed, temporal trends of connectance and average trophic level
-were positively associated to the temporal trends of community biomass while no
-significant association was found with temporal trends of species richness.
-Moreover, the temporal trends of biomass evenness were negatively associated to
-the temporal trends of community biomass whereas positively associated to
-temporal trends of species richness. All together, it suggests that temporal
-trends of community biomass and species richness are related to different
-assembly and disassembly processes in food-webs.
+different temporal trends on the connectance and average trophic level. Indeed,
+temporal trends of connectance and average trophic level were positively
+associated to the temporal trends of community biomass while we found
+that species richness temporal trends was negatively and no
+significantly related to connectance and average trophic level respectively. All
+together, it suggests that temporal trends of community biomass and species
+richness are related to different assembly and disassembly processes in
+food-webs.
 
@@
 decrease of average trophic level and that community biomass temporal gains were
-associated to temporal increase of average trophic level. Together with connectance, it suggests that
-community biomass losses and gains are associated to losses and gains in large
-bodied piscivores, i.e. biomass at the higher trophic level. Another piece of evidence
-is that evenness of biomass, measured by the Pielou index, decreased through
-time as community biomass increased, meaning that biomass distribution across
-species becomes less even when community biomass increased. Reversely, in
-food-webs that displayed temporal decrease in community biomass, we found that
-evenness of biomass increased, i.e. that biomass distribution across species
-becomes more even. Because predator-prey interactions relate on bodysize for a
-large part [@brose_allometric_2006; @woodward_body_2005] and thus bodymass to a
-certain extent, we can expect that a given gain in predators of higher trophic
-level leads to a decrease of biomass evenness and reversely. In the same line,
-we found that the temporal trends of community biomass were positively
-associated to the temporal trends of the number and proportion of piscivorous
-trophic species present in fish communities (Fig. SXX). The close association
-between the temporal trends of community biomass from one side, and connectance,
-average trophic level and biomass evenness from the other side, strongly suggest
-that temporal trends in community biomass in natural freshwater fish communities
-are associated to variations in the biomass of the top trophic level.
-
-In contrast, we found that temporal trends of connectance and average trophic
-level were not related to the temporal trends of species richness, in
-contradiction with previous observation in space [@dunne_network_2006;
-@danet_species_nodate]. However, we found that temporal trends of the number of
-piscivorous species and piscivorous trophic species were positively associated
-to the temporal trends of species richness (Fig. S3). It suggests that the
-temporal decrease of species richness observed in our data are concomitant to
-losses of piscivorous and non-piscivorous species, leading to the absence of
-temporal trends in connectance and average trophic level and symmetrically for
-the temporal increase of species richness. Furthermore, we found that the
-temporal trends of biomass evenness had a positive relationship with the one of
-species richness, in contradiction of what we found for temporal trends of
-community biomass. Together with the fact that species richness temporal trends
-had a positive relationship with the temporal trends of community biomass, it
-suggests that positive and negative  temporal trends of species richness are
-linked to gains and losses of redundancy in food-webs, without overall effects
-on connectance and average trophic level. This is in line with the insurance
-hypothesis [@yachi_biodiversity_1999] which predicts the temporal loss and gain
-of species richness represent respectively loss and gain of redundancy in the
-community, in the food-web structure in the present study.
-
-The discrepancy between the effects of the temporal trends of species richness
-and community biomass on food-web structure might be coined in the concepts of
-trophic complementarity and redundancy [@poisot_trophic_2013;
-@nordstrom_nestedness_2015]. The variations of community
-biomass is related to variations in the presence of large bodied predators,
-which affect both trophic complementarity, because they feed on bigger preys,
-and redundancy, because their diet include the diet of lower trophic level.
-Species richness temporal variation seems to affect mainly trophic redundancy
-and not trophic complementarity, as average trophic level and connectance does
-not change despite concomitant variations in the number of piscivorous species
-(**Interesting ?**).
+associated to temporal increase of average trophic level. Together with
+connectance, it suggests that community biomass losses and gains are associated
+to losses and gains in large bodied piscivores, i.e. biomass at the higher
+trophic level. In the same line, we found that the temporal trends of community
+biomass were positively associated to the temporal trends of both number and
+proportion of piscivorous fish species present in the communities (Fig.
+SXX). The close association between the temporal trends of community biomass
+from one side, and connectance, average trophic level from the other side,
+strongly suggest that temporal trends in community biomass in natural freshwater
+fish communities are mainly associated to variations in the biomass of the top
+trophic level.
+
+In contrast, we found that temporal trends of connectance was weakly negatively
+related to the temporal trends of species richness, in contrasts with the strong
+negative relationships that we found in the present study and from previous
+results over spatial gradient [@dunne_network_2006; @danet_species_nodate].
+Furthermore, we found that temporal trends of the proportion of piscivorous
+species was negatively associated to the temporal trends of species richness
+(Table SXX), in accordance with previous meta-analysis over spatial gradient
+[@turney_pyramids_2016] and mesocosm experiment [@downing_ecosystem_2002]. It
+resonates with the energetic paradigm of food-webs which proposes that the
+presence of species at higher trophic level is constrained by energy loss along
+the food chain [@lindeman_trophic-dynamic_1942]. It suggests that the temporal
+increase of species richness found in our dataset are associated to a decrease
+of connectance because species richness increases are biased toward
+non-piscivorous species which have less feeding links than piscivorous species.
+We found in the same time that the temporal trends species richness had no
+direct link with the temporal trends of the average trophic level, the latter
+being weighted by the biomass of each node. An explanation can be that when
+species richness increases or decreases through time without community biomass
+trends, the associated decrease and respectively increase in proportion of
+piscivorous species leads to a redistribution of biomass among remaining
+piscivorous species or among the non-piscivorous species.
+
+The temporal trends of species richness had an indirect positive effect on the
+temporal trends of both connectance and average trophic level through the
+positive relationship between the temporal trends of species richness and
+community biomass. The temporal trends of species richness had then an
+total effect on the temporal trends of connectance and average trophic level
+which was twice lower in magnitude than the magnitude of the total effect of the
+temporal trends of community biomass. It suggests that the temporal assembly and
+disassembly of food-webs are more sensible to variations in community biomass
+than in species richness, in other words that food-web structure is more robust
+to species richness change than biomass changes. This result is in line with
+evidences that food-web containing generalist predators can rewire in response
+to changes in the availability of prey species [@bartley_food_2019]. *(J'ai
+regardé dans la biblio envoyé par Elisa et j'ai refais de la biblio moi-même, je
+n'ai rien qui s'approche de ce résultat).* This result also resonates with the
+energy paradigm of food-webs which proposes that food-webs are primarily
+constrained by fluxes of matter and energy [@lindeman_trophic-dynamic_1942], so
+community biomass and not by species richness.
+
+- Remove the following paragraph:
 
@@
 community biomass subsequent to the presence of higher predators
-[@wang_biodiversity_2018]. We also found that biomass evenness was negatively
-related to community biomass in space and time. This result is in accordance
-with the reported top-heavy shape of biomass pyramids in food-webs,
-particularly in freshwater systems [@mccauley_prevalence_2018]. Many mechanisms
-have been invoked to explain this pattern but omnivory, which
-is present in most of piscivorous species in our dataset, may favor this shape
-by increasing food transfer efficiency toward the higher trophic levels.
-
-Surprisingly, we found that the temporal trends of connectance were not related
-to the one of species richness as found spatially in most empirical food-webs
-[@dunne_network_2006] and also here. We explained this pattern by the fact that
-the temporal variation of species richness in our dataset seems to be linked to
-temporal variation of redundancy level in the structure of food-webs rather than
-overall change of their vertical structure. The same rational can applied with
-average trophic level. This result is in line with other studies which found
-mismatch between spatial and temporal patterns [@adler_contrasting_2007;
-@johnson_testing_2008]. This discrepancy in space and time might be due to the
-crucial assumption that variations in space reflect differences in assembly
-stages of ecological communities and then mirrors their temporal
-assembly/disassembly trajectories. Temporal variation of species richness might
-relate on transitory dynamics while spatial gradient reflect aggregated dynamics
-over longer time scale including a far number of processes including high
-species turnover along spatial gradient. However, we fount that the positive
-relationship between evenness of biomass and species richness were consistent in
-space and time. Another reason might be that the spatial gradient displays a
-higher range of variation for species richness than the temporal stations (Fig.
-S2). However, we found strong relationships between the temporal trend of
-species richness from one side and the temporal trends of community biomass,
-biomass evenness, and the number of piscivorous species from the other side (Fig. S3).
+[@wang_biodiversity_2018]. Finally, we found a positive relationship between
+community biomass and species both in space and time, however the relationship
+in time was stronger.
+
+Surprisingly, we found that the temporal trends of connectance were weakly
+related to the one of species richness as found spatially in most empirical
+food-webs [@dunne_network_2006] and also here. We further found a weak negative
+relationship between the temporal trends of average trophic level and the one of
+species richness which we found a twice stronger but positive relationship
+between median average trophic level and median species richness over the
+spatial gradient. An explanation might be that environmental gradient, in
+resources in hydrologic contraints might be responsible for the strong negative
+effect of species richness on both connectance and average trophic level over
+spatial gradient. However, we controlled our spatial analysis by the Biological
+Demand in Oxygen, water temperature and the stream gradient. This result is also
+in line with other studies which found mismatch between spatial and temporal
+patterns [@adler_contrasting_2007; @johnson_testing_2008]. This discrepancy in
+space and time might be due to the crucial assumption that variations in space
+reflect differences in assembly stages of ecological communities and then
+mirrors their temporal assembly/disassembly trajectories. Temporal variation of
+species richness might relate on transitory dynamics while spatial gradient
+reflect aggregated dynamics over longer time scale including a far number of
+processes including high species turnover along spatial gradient. Another reason
+might be that the spatial gradient displays a higher range of variation for
+species richness than the temporal stations (Fig. S2). However, we found
+temporal trends of species richness of -70%/-50% to +80%/+100% by decade.
+
+- Développer un point la-dessus?:
+
+Our study highlights that time series are an important tool to
+understand the assembly and disassembly of food-webs following changes in
+species richness and biomass. Our study also highlights the usefulness of
+structural equation model to highlight direct and indirect pathways.
 
@@
 
-Our study suggests that richness and biomass temporal trends in natural fish
-communities relate on different ecological processes, biomass temporal dynamics
-being related to variations of food-web structure at the higher trophic levels
-while species richness impacts redundancy of species in food-web structure. Our
-result also suggests that space for time substitution may be relevant to predict
-the effects of community biomass losses or gains on food-web structure. However,
-our findings suggest that space-for-time substitution might not work for species
-richness. Our study calls for further investigations to support the generality of
-assembly rules in food-webs. They are crucial to better understand the
-assembly and disassembly of food-web and then predict its impact on ecosystem
-functioning.
+Our study suggests that species richness and community biomass temporal trends
+in natural fish communities relate on different ecological processes, biomass
+temporal dynamics being related to variations of food-web structure at the
+higher trophic levels while variations of species richness is weakly related to
+change in food-web structure. Our result also suggests that space for time
+substitution may be relevant to predict the effects of community biomass losses
+or gains on food-web structure. However, our findings suggest that
+space-for-time substitution might not work for species richness. Our study calls
+for further investigations to support the generality of assembly rules in
+food-webs. They are crucial to better understand the assembly and disassembly of
+food-web and then predict its impact on ecosystem functioning.
 

### 2022-05-02 R/network_methods.R

@@ -78,11 +78,16 @@ get_piscivory_stat_from_network <- function (net) {
 
   tibble(
     nb_pisc_node = length(fish_fish[fish_fish > 0]),
+    nb_non_pisc_node = length(fish_fish) - nb_pisc_node,
     prop_pisc_node = nb_pisc_node / length(fish_fish),
+    prop_non_pisc_node = 1 - prop_pisc_node,
     nb_pisc_rich =  str_extract(names(fish_fish[fish_fish > 0]), "[A-Z]+") %>%
       unique() %>% length(),
+    nb_non_pisc_rich =  str_extract(names(fish_fish), "[A-Z]+") %>%
+      unique() %>% length() - nb_pisc_rich,
     prop_pisc_rich = nb_pisc_rich / str_extract(names(fish_fish), "[A-Z]+") %>%
-      unique() %>% length()
+      unique() %>% length(),
+    prop_non_pisc_rich = 1 - prop_pisc_rich
   )
 
 }

### 2022-07-16 random_network.Rmd
Add food-web extinction analysis

---
title: "Extinction simulation on the metaweb"
author: AD 
date: \today
output:
  bookdown::pdf_document2:
    toc: true
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  echo = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.asp = .5, 
  fig.show = "hold",
  message = FALSE,
  warning = FALSE,
  results = TRUE
)
```
```{r, echo = FALSE, results = FALSE}
library(drake)
library(ggformula)
mypath <- rprojroot::find_package_root_file
source(mypath("R/misc.R"))
source(mypath("R/variable_shortcut.R")) # Define your custom code as a bunch of functions.
source_dir(get_mypath("R")) # Define your custom code as a bunch of functions.

mytheme <- theme_cowplot() +
background_grid()

theme_set(mytheme)
```

```{r}
load(mypath("data", "metaweb_analysis.rda"))
```
```{r}
metaweb <- metaweb_analysis$metaweb
# node seq
node_tlvl <- NetIndices::TrophInd(metaweb)$TL
names(node_tlvl) <- colnames(metaweb_analysis$metaweb)
# 
metric_to_keep <- c("ct", "ct_ff", "avg_tl", "avg_tl_ff", "max_tl", "max_tl_ff")

# species
fish_species_tlvl <- node_tlvl %>%
  enframe(name = "node", value = "tlvl") %>%
  mutate(species = get_species(node)[, 1]) %>%
  filter(str_detect(species, "[A-Z]+")) %>%
  group_by(species) %>%
  summarise(tlvl_med = median(tlvl)) %>%
  arrange(desc(tlvl_med)) %>%
  deframe()
```

```{r, eval = FALSE}
node_seq <- sort(node_tlvl, decreasing = TRUE)
node_fish_seq <- node_seq[fish(names(node_seq))]

node_extinction_inc_dec_tlvl <- tibble(
  node_rm_single = names(node_fish_seq),
  node_tlvl = node_fish_seq,
  node_rm_tot = map(seq_along(node_fish_seq),
      ~node_fish_seq[1:.x]),
  metaweb = map(
  seq_along(node_fish_seq),
  ~metaweb[
    !rownames(metaweb) %in% names(node_fish_seq)[1:.x],
    !colnames(metaweb) %in% names(node_fish_seq)[1:.x]
    ]
)
)
```
```{r, eval=FALSE}
node_extinction_inc_dec_tlvl_metrics <-
  node_extinction_inc_dec_tlvl %>%
    mutate(
      fish_fish_net = map(metaweb, get_fish_fish_matrix),
      metrics = map(metaweb, NetIndices::GenInd),
      ff_metrics = map(fish_fish_net, NetIndices::GenInd),
      ct = map_dbl(metrics, "C"),
      ct_ff = map_dbl(ff_metrics, "C"),
      tl = map(metaweb, ~max(NetIndices::TrophInd(.x)$TL)),
      tl_ff = map(fish_fish_net, ~max(NetIndices::TrophInd(.x)$TL))
    )
```

```{r}
get_fw_metrics <- function(x) {

  ff_metaweb <- get_fish_fish_matrix(x)

  if (ncol(ff_metaweb) == 0) {
    ff_ind <- NA
    ct_ff <- NA
    tl_ff <- NA
    avg_tl_ff <- NA
    max_tl_ff <- NA
  } else {
    ff_ind <- NetIndices::GenInd(ff_metaweb)
    ct_ff <- ff_ind["C"]
    tl_ff <- NetIndices::TrophInd(ff_metaweb)$TL
    avg_tl_ff <- mean(tl_ff)
    max_tl_ff <- max(tl_ff)
  }

  ind <- NetIndices::GenInd(x)
  ct <- ind["C"]
  tl <- NetIndices::TrophInd(x)$TL
  avg_tl <- mean(tl)
  max_tl <- max(tl)

  list(
    ff_metaweb = ff_metaweb,
    ind = ind,
    ff_ind = ff_ind,
    ct = ct,
    ct_ff = ct_ff,
    tl = tl,
    tl_ff = tl_ff,
    avg_tl = avg_tl,
    avg_tl_ff = avg_tl_ff,
    max_tl = max_tl,
    max_tl_ff = max_tl_ff
  )
}

get_fw_metrics2 <- function(x, keep_metaweb = TRUE) {

  ff_metaweb <- get_fish_fish_matrix(x)

  if (ncol(ff_metaweb) == 0) {
    ff_ind <- NA
    ct_ff <- NA
    tl_ff <- NA
    avg_tl_ff <- NA
    max_tl_ff <- NA
  } else {
    ff_ind <- NA
    ct_ff <- sum(ff_metaweb) / (ncol(ff_metaweb) - 1)^2
    tl_ff <- NetIndices::TrophInd(ff_metaweb)$TL
    avg_tl_ff <- mean(tl_ff)
    max_tl_ff <- max(tl_ff)
  }

  if (ncol(x) == 0) {
    ind <- NA
    ct <- NA
    tl <- NA
    avg_tl <- NA
    max_tl <- NA
  } else {
    ind <- NA
    ct <- sum(x) / (ncol(x) - 1)^2
    tl <- NetIndices::TrophInd(x)$TL
    avg_tl <- mean(tl)
    max_tl <- max(tl)
  }

  if (!keep_metaweb) {
    ff_metaweb <- NA
  }

  list(
    ff_metaweb = ff_metaweb,
    ind = ind,
    ff_ind = ff_ind,
    ct = ct,
    ct_ff = ct_ff,
    tl = tl,
    tl_ff = tl_ff,
    avg_tl = avg_tl,
    avg_tl_ff = avg_tl_ff,
    max_tl = max_tl,
    max_tl_ff = max_tl_ff
  )

}

get_sim_net <- function(net = NULL, ext_seq = NULL, keep_metaweb = TRUE) {

  node_extinction <- tibble(
    node_rm_single = names(ext_seq),
    node_tlvl = ext_seq,
    node_rm_tot = map(seq_along(ext_seq),
      ~ext_seq[1:.x]),
    metaweb = furrr::future_map(
      seq_along(ext_seq),
      ~metaweb[
        !rownames(net) %in% names(ext_seq)[1:.x],
        !colnames(net) %in% names(ext_seq)[1:.x]
        ]
    )
  )

  meta_keep <- keep_metaweb
  out <- node_extinction %>%
    mutate(
      metrics = furrr::future_map(
        metaweb, ~try(get_fw_metrics2(.x, keep_metaweb = meta_keep))
      )
    )

  if (!keep_metaweb) {
    out$metaweb <- NULL
  }

  return(out)
}

```

```{r}
node_seq_dec_tlvl <- sort(node_tlvl, decreasing = TRUE)
node_seq_inc_tlvl <- sort(node_tlvl, decreasing = FALSE)
node_fish_seq_dec_tlvl <- node_seq_dec_tlvl[fish(names(node_seq_dec_tlvl))]
node_fish_seq_inc_tlvl <- node_seq_inc_tlvl[fish(names(node_seq_inc_tlvl))]
```

```{r, eval=FALSE}
plan(sequential)
sim_dec_tlvl <- get_sim_net(net = metaweb, ext_seq = node_fish_seq_dec_tlvl,
  keep_metaweb = FALSE)
sim_inc_tlvl <- get_sim_net(net = metaweb, ext_seq = node_fish_seq_inc_tlvl,
  keep_metaweb = FALSE
)
nsim <- 10

sim_random_tlvl <- tibble(
  repl = seq_len(nsim),
  sim = furrr::future_map(repl,
    ~get_sim_net(net = metaweb, ext_seq = sample(node_fish_seq_inc_tlvl),
      keep_metaweb = FALSE)
  )
)

sim_dec_tlvl %<>%
  mutate(met = map(metrics, ~enframe(unlist(.x[metric_to_keep])))) %>%
  unnest(met) %>%
  pivot_wider(names_from = "name", values_from = "value")
save(file = mypath("data", "sim_dec_tlvl.rda"), sim_dec_tlvl)

sim_inc_tlvl %<>%
  mutate(met = map(metrics, ~enframe(unlist(.x[metric_to_keep])))) %>%
  unnest(met) %>%
  pivot_wider(names_from = "name", values_from = "value")
save(file = mypath("data", "sim_inc_tlvl.rda"), sim_inc_tlvl)

sim_random_tlvl %<>%
  mutate(res = map(sim, function(x) {
      x %>%
      mutate(met = map(metrics, ~enframe(unlist(.x[metric_to_keep])))) %>%
      unnest(met) %>%
      pivot_wider(names_from = "name", values_from = "value")
  })) %>%
unnest(res)
save(file = mypath("data", "sim_random_tlvl.rda"), sim_random_tlvl)
```

```{r random-richness, eval = FALSE}
sim_dec_tlvl_species <- vector(mode ="list", length = length(fish_species_tlvl)) 
sim_inc_tlvl_species <- vector(mode = "list", length = length(fish_species_tlvl))
inc_species_tlvl <- sort(fish_species_tlvl, decreasing = FALSE)

for (i in seq_along(fish_species_tlvl)) {
  decreasing_tlvl_metaweb <- metaweb[
    !str_detect(
      rownames(metaweb),
      paste0(names(fish_species_tlvl)[1:i], collapse = "|")
      ),
    !str_detect(
      colnames(metaweb),
      paste0(names(fish_species_tlvl)[1:i], collapse = "|")
      )
    ]
  sim_dec_tlvl_species[[i]] <- get_fw_metrics2(decreasing_tlvl_metaweb,
    keep_metaweb = FALSE)

  increasing_tlvl_metaweb <- metaweb[
    !str_detect(
      rownames(metaweb),
      paste0(names(inc_species_tlvl)[1:i], collapse = "|")
      ),
    !str_detect(
      colnames(metaweb),
      paste0(names(inc_species_tlvl)[1:i], collapse = "|")
      )
    ]
  sim_inc_tlvl_species[[i]] <- get_fw_metrics2(increasing_tlvl_metaweb,
    keep_metaweb = FALSE)
}
dec_species_result <- tibble(
  one_sp_rm = names(fish_species_tlvl),
  species_removed = map(seq_along(fish_species_tlvl),
    ~names(fish_species_tlvl)[1:.x]),
  metrics = sim_dec_tlvl_species
  )

inc_species_result <- tibble(
  one_sp_rm = names(inc_species_tlvl),
  species_removed = map(seq_along(inc_species_tlvl),
    ~names(inc_species_tlvl)[1:.x]),
  metrics = sim_inc_tlvl_species
  )
save(file = mypath("data", "sim_dec_sp_tlvl.rda"), dec_species_result)
save(file = mypath("data", "sim_inc_sp_tlvl.rda"), inc_species_result)
```

```{r, eval = FALSE}
# random simulation
nsim <- 10
set.seed(123)

sim_random_tlvl_species <- vector(mode = "list", length = length(fish_species_tlvl))
sim_random_tlvl_species <- map(sim_random_tlvl_species, ~vector(mode = "list", length = nsim))
sp_to_rm <- vector(mode = "list", length = length(fish_species_tlvl))
sp_to_rm <- map(sp_to_rm, ~vector(mode = "list", length = nsim))

for (i in seq_along(fish_species_tlvl)) {

  for (j in seq_len(nsim)) {
    sp_to_rm[[i]][[j]] <- sample(names(fish_species_tlvl), size = i, replace = FALSE)

    tmp_metaweb <- metaweb[
      !str_detect(
        rownames(metaweb),
        paste0(sp_to_rm[[i]][[j]], collapse = "|")
        ),
      !str_detect(
        colnames(metaweb),
        paste0(sp_to_rm[[i]][[j]], collapse = "|")
      )
      ]
    sim_random_tlvl_species[[i]][[j]] <- get_fw_metrics2(
      tmp_metaweb,
    keep_metaweb = FALSE)
  }
}

random_species_result <- tibble(
  nsp_rm = seq_along(fish_species_tlvl),
  species_removed = sp_to_rm,
  metrics = sim_random_tlvl_species
  )
save(file = mypath("data", "sim_random_sp_tlvl.rda"), random_species_result)
```

# Results

## Node

```{r}
load(mypath("data", "sim_dec_tlvl.rda"))
load(mypath("data", "sim_inc_tlvl.rda"))
load(mypath("data", "sim_random_tlvl.rda"))
```

```{r}
rand_node_tmp <- sim_random_tlvl %>%
  unnest(sim) %>%
  mutate(
    met = map(metrics, ~enframe(unlist(.x[metric_to_keep]))),
    nb_ext = map_int(node_rm_tot, length),
    type = "random",
    extinct = "node"
    ) %>%
  unnest(met) %>%
  rename(metric = name)

sim_node_dec_inc <- rbind(
  sim_dec_tlvl %>%
    pivot_longer(!!metric_to_keep, names_to = "metric", values_to = "value") %>%
    mutate(
    type = "decreasing",
    extinct = "node"
  ),
  sim_inc_tlvl %>%
    pivot_longer(!!metric_to_keep, names_to = "metric", values_to = "value") %>%
    mutate(
      type = "increasing",
      extinct = "node"
    )
)
```

```{r}
p_ext_node <- sim_node_dec_inc %>%
  filter(str_detect(metric, "_ff")) %>%
  mutate(
    nb_ext = map_int(node_rm_tot, length),
    metric = var_replacement()[metric],
    type = str_to_sentence(type)
    ) %>%
  ggplot(aes(x = nb_ext, y = value, color = type)) +
  geom_line() +
  geom_point(data = rand_node_tmp %>%
    filter(str_detect(metric, "_ff")) %>%
    mutate(
      metric = var_replacement()[metric],
      type = str_to_sentence(type)
    )) +
  geom_smooth(data = rand_node_tmp %>%
    filter(str_detect(metric, "_ff")) %>%
    mutate(
      metric = var_replacement()[metric],
      type = str_to_sentence(type)
    ), color = "black") +
  facet_wrap(~metric, scale = "free_y") +
  labs(y = "Network metric values",
    x = "Number of node removed",
    color = "Trophic level scenario") +
  theme(legend.position = "bottom")
```

## Species

```{r}
load(file = mypath("data", "sim_random_sp_tlvl.rda"))
load(file = mypath("data", "sim_dec_sp_tlvl.rda"))
load(file = mypath("data", "sim_inc_sp_tlvl.rda"))
```

```{r}
sim_sp_dec_inc <- rbind(
  inc_species_result %>%
    mutate(
      met = map(metrics, ~enframe(unlist(.x[metric_to_keep]))),
      nb_ext = map_int(species_removed, length),
      type = "increasing",
      extinct = "species"
      ) %>%
  unnest(met) %>%
  rename(metric = name),
dec_species_result %>%
  mutate(
    met = map(metrics, ~enframe(unlist(.x[metric_to_keep]))),
    nb_ext = map_int(species_removed, length),
    type = "decreasing",
    extinct = "species"
    ) %>%
  unnest(met) %>%
  rename(metric = name)
)

rand_sp_met <- random_species_result %>%
  unnest(metrics) %>%
  mutate(
    met = map(metrics, ~enframe(unlist(.x[metric_to_keep]))),
    nb_ext = nsp_rm,
    type = "random",
    extinct = "species"
    ) %>%
  unnest(met) %>%
  rename(metric = name)
```

```{r}
sim_sp_dec_inc %>%
  filter(str_detect(metric, "_ff")) %>%
  mutate(
    metric = var_replacement()[metric],
    type = str_to_sentence(type)
    ) %>%
  ggplot(aes(x = nb_ext, y = value, color = type)) +
  geom_line() +
  geom_point(
    data = rand_sp_met %>%
    filter(str_detect(metric, "_ff")) %>%
    mutate(
      metric = var_replacement()[metric],
      type = str_to_sentence(type)
    )) +
  geom_smooth(data = rand_sp_met %>%
    filter(str_detect(metric, "_ff")) %>%
    mutate(
      metric = var_replacement()[metric],
      type = str_to_sentence(type)
    ), color = "black") +
  facet_wrap(~metric, scale = "free_y") +
  labs(y = "Network metric values", x = "Number of species removed",
    color = "Trophic level scenario") +
  theme(legend.position = "bottom")
p_ext_node
```

### 2022-07-18 paper/appendix.Rmd
Clean Rsq table and figure 3

@@
 ```{r}
-var_analysis <- c("ct_ff", "w_trph_lvl_avg", "log_rich_std", "log_bm_std",
-  "piel_bm", "piel_nind")
+var_analysis <- c("ct_ff", "w_trph_lvl_avg", "log_rich_std", "log_bm_std")
 ```
@@
 ```{r}
-loadd(
-  pred_bm_rich_mono_stable_trends,
-  model_bm_rich_int_mono_stable_trends,
-  model_bm_rich_int_mono_stable_trends,
-  rsq_table_bm_rich_mono_stable_trends
-)
+loadd(sem_tps)
 ```
@@
 ```{r}
-reg_table_bm_rich_mono_stable_trends %>%
-  mutate(
-    response = str_replace_all(response, var_replacement()),
-    term = str_replace_all(term, var_replacement())
-    ) %>%
-kable(., booktabs = TRUE,
-  row.names = FALSE,
-  caption =
-    paste0(
-      "Regression coefficients for the linear models explaining the links
-      between the temporal trends of community biomass and the temporal trends
-      of the network structure."),
-      label = "reg"
-      ) %>%
-  kable_styling(latex_options = c("scale_down", "striped")) %>%
-  collapse_rows(columns = 1, valign = "top")
-```
-
-```{r}
-table_rsq_tps <- rsq_table_bm_rich_mono_stable_trends %>%
+map_dfr(sem_tps, piecewiseSEM::rsquared) %>%
   mutate(
     Response = str_replace_all(Response, var_replacement())
-  )
-table_rsq_tps %>%
+  ) %>%
+  select(Response, R.squared) %>%
   kable(., booktabs = TRUE,
@@
       paste0(
-      "Marginal and conditional squared R for temporal models."),
+      "Marginal R-squared for temporal models."),
   label = "rsq"
       ) %>% #
-  kable_styling(latex_options = c("striped")) %>%
-  collapse_rows(columns = 1, valign = "top")
+  kable_styling(latex_options = c("striped"))
 ```
@@
 ```{r}
-loadd(
-  sp_anova_table_bm_rich_mono_stable_trends,
-  sp_rsq_table_bm_rich_mono_stable_trends
-)
+loadd(sp_sem)
 ```
@@
 ```{r}
-sp_anova_table_bm_rich_mono_stable_trends %>%
-  mutate(
-    response = str_replace_all(response, var_replacement()),
-    term = str_replace_all(term, var_replacement()),
-  ) %>%
-  kable(.,
-    booktabs = TRUE,
-    row.names = FALSE,
-    caption =
-      paste0(
-      "ANOVA results for the links among the spatial variation of community
-      biomass and species richness and the one of network structure."),
-  label = "aov-sp"
-  ) %>%
-  kable_styling(latex_options = c("scale_down", "striped")) %>%
-  collapse_rows(columns = 1, valign = "top")
-```
-
-```{r}
-sp_rsq_table_bm_rich_mono_stable_trends %>%
+map_dfr(sp_sem, piecewiseSEM::rsquared) %>%
   mutate(
     Response = str_replace_all(Response, var_replacement())
+  ) %>%
+  select(Response, Marginal, Conditional) %>%
+  mutate(
+    Response = str_replace_all(Response, var_replacement()),
+    Marginal = round(Marginal, 2),
+    Conditional = round(Conditional, 2)
   ) %>%
@@
       ) %>% #
-  kable_styling(latex_options = c("striped")) %>%
-  collapse_rows(columns = 1, valign = "top")
+  kable_styling(latex_options = c("striped"))
 ```

### 2022-07-18 paper/manuscript.Rmd
Clean Rsq table and figure 3

@@
 semeff_tab <- from_semEff_to_table(semeff)
-semeff
 semeff_tot <- rbind(
@@
 
-```{r std-old, eval = FALSE, fig.cap=std_cap, fig.width=6}
-#loadd(fig_std_coef)
-std_table_bm_rich_mono_stable_trends %>%
-  filter(
-    term %in% c("log_rich_std", "log_bm_std"),
-    !response %in% "piel_nind") %>%
-  mutate_at(vars(term, response), ~str_replace_all(., var_replacement(
-        several_lines = TRUE))) %>%
-  mutate(
-    type = str_to_sentence(type),
-    type = factor(type, levels = c("Temporal", "Spatial"))) %>%
-  ggplot(aes(y = std_estimate, x = response, fill = type)) +
-  viridis::scale_fill_viridis(begin = 0.5, end = 1, discrete = TRUE) +
-  facet_grid(rows = vars(term)) +
-  geom_col(position = position_dodge(width = .9)) +
-  geom_linerange(aes(ymin = std_estimate - stdse, ymax = std_estimate + stdse),
-    position = position_dodge(width = .9)) +
-  labs(
-    x = "Response variables",
-    y = expression(paste("Standardized slope coefficients ", r[delta])),
-    fill = "Model") +
-  theme(legend.position = c(0.6, .05),
-    legend.direction = "horizontal",
-    text = element_text(size = 8), axis.text = element_text(size = 8)) +
-  scale_y_continuous(sec.axis = sec_axis(~ ., name = "Predictive variable",
-      breaks = NULL, labels = NULL))
-```
-
-```{r std, fig.cap=std_cap, fig.width=6, fig.height = 9}
-semeff_tot %>%
+```{r std, fig.cap=std_cap, fig.width=7, fig.asp = .7}
+p_sem_eff <- semeff_tot %>%
   mutate(
     response = var_replacement()[response],
-    predictor = var_replacement()[predictor]
+    predictor = var_replacement()[predictor],
+    effect_type = str_to_sentence(effect_type),
+    model = str_to_sentence(model)
     ) %>%
-  ggplot(aes(x = predictor, y = effect, fill = effect_type)) +
-  geom_col(
+  ggplot(aes(y = predictor, x = effect, colour = effect_type, shape = model)) +
+  geom_point(
     position = position_dodge(width = 0.4), width = .4) +
-  geom_hline(yintercept = 0) +
+  geom_vline(xintercept = 0) +
   geom_linerange(
-    aes(ymin = lower_ci, ymax = upper_ci),
+    aes(xmin = lower_ci, xmax = upper_ci),
     position = position_dodge(width = 0.4)
     ) +
-  facet_grid(rows = vars(response), cols = vars(model)) +
+  facet_grid(rows = vars(response)) +
   labs(
-    x = "Predictor",
-    y = expression(paste("Standardized slope coefficients ", r[delta])),
-    fill = "Effect type") +
-  theme(axis.text.x = element_text(angle = 20, hjust = 1))
+    y = "Predictor",
+    x = expression(paste("Standardized slope coefficients ", r[delta])),
+    color = "Effect type", shape = "Model") +
+  theme(legend.position = "bottom")
+p_sem_eff
 ```

### 2022-07-25 random_network.Rmd
Make lm for random network

@@
 ```{r}
-sim_sp_dec_inc %>%
+p_ext_sp <- sim_sp_dec_inc %>%
   filter(str_detect(metric, "_ff")) %>%
@@
 ```
+
+```{r}
+model_res <- rand_sp_met %>%
+  select(metric, value, nb_ext) %>%
+  filter(str_detect(metric, "_ff")) %>%
+  nest_by(metric) %>%
+  mutate(
+    mod = list(lm(value ~ nb_ext, data)),
+    coefs = list(broom::tidy(mod))
+  ) %>%
+  unnest(coefs) %>%
+  filter(term == "nb_ext")
+```

### 2022-09-20 inla_test.Rmd
Add reanalysis with INLA

---
title: "Extinction simulation on the metaweb"
author: AD 
date: \today
output:
  bookdown::pdf_document2:
    toc: true
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  echo = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.asp = .5, 
  fig.show = "hold",
  message = FALSE,
  warning = FALSE,
  results = TRUE
)
```
```{r, echo = FALSE, results = FALSE}
library(drake)
library(ggformula)
library(INLA)
mypath <- rprojroot::find_package_root_file
source(mypath("R/misc.R"))
source(mypath("R/variable_shortcut.R")) # Define your custom code as a bunch of functions.
source_dir(get_mypath("R")) # Define your custom code as a bunch of functions.

mytheme <- theme_cowplot() +
background_grid()

theme_set(mytheme)
```

```{r}
loadd(full_data2, basin_station)
colnames(full_data2)

data_inla <- full_data2 %>%
  left_join(basin_station, by = "station") %>%
      mutate(
        station = as.character(station),
        basin = as.character(basin),
        basin1 = as.character(basin),
        station1 = as.character(station),
        intercept_basin = as.integer(as.factor(basin)),
        intercept_basin_station = as.integer(as.factor(paste0("basin", basin, ":", "station", station)))
        )
```
```{r}
facet_var <- c(get_biomass_var(), get_com_str_var())
gaussian_inla_no_drivers <- tibble(
  response = facet_var,
  mod = purrr::map(facet_var, ~try(inla(
        formula = get_formula_inla(resp = .x, tau_prior = FALSE),
        control.compute = list(dic = TRUE, waic = TRUE, cpo = TRUE,
              return.marginals=TRUE, return.marginals.predictor=TRUE),
        control.predictor = list(link = 1, compute = T),
        verbose = F,
        data = data_inla
        ))))
save(gaussian_inla_no_drivers, file = mypath("data", "gaussian_inla_no_drivers.rda"))
```

```{r}
gaussian_inla_no_drivers_effects <-
  format_inla_model_list(x = gaussian_inla_no_drivers)
glob_tps_trends_decade_no_drivers <-
  gaussian_inla_no_drivers_effects %>%
  filter(term == "nb_year") %>%
  mutate(
    mean = map2_dbl(response, mean,
      ~compute_trends_meaningful_units(x = .y, resp = .x,
        time = 10)),
    low = map2_dbl(response, low,
      ~compute_trends_meaningful_units(x = .y, resp = .x),
      time = 10),
    high = map2_dbl(response, high,
      ~compute_trends_meaningful_units(x = .y, resp = .x),
      time = 10)
  )
```

```{r}
gaussian_pred_station_tps <- gaussian_inla_no_drivers %>%
  mutate(
    station_tps = map(mod, ~get_re_prediction_inla(.x, effect = "station1"))
  ) %>%
select(-mod) %>%
unnest(station_tps)

gaussian_pred_station_tps10  <- gaussian_pred_station_tps %>%
  mutate(
    mean = map2_dbl(response, mean,
      ~compute_trends_meaningful_units(x = .y, resp = .x,
        time = 10)),
    quant0.025 = map2_dbl(response, quant0.025,
      ~compute_trends_meaningful_units(x = .y, resp = .x),
      time = 10),
    quant0.975 = map2_dbl(response, quant0.975,
      ~compute_trends_meaningful_units(x = .y, resp = .x),
      time = 10)
  )
tps_for_sem <- gaussian_pred_station_tps10 %>%
  select(response, station, mean, sd) %>%
  pivot_wider(everything(), names_from = "response", values_from = c("mean", "sd"))
```

```{r}
library(semEff)
library(piecewiseSEM)
```

```{r}
sem <- list(
  lm(mean_ct_ff ~ mean_log_bm_std + mean_log_rich_std, data = tps_for_sem,
    weight = 1 / (sd_log_rich_std + sd_log_bm_std + sd_ct_ff)),
    lm(mean_w_trph_lvl_avg ~ mean_log_bm_std + mean_log_rich_std, data = tps_for_sem,
      weight = 1 / (sd_log_rich_std + sd_log_bm_std + sd_w_trph_lvl_avg)),
      lm(mean_log_bm_std ~ mean_log_rich_std, data = tps_for_sem,
        weight = 1 / (sd_log_rich_std + sd_log_bm_std)
        )
)
plot(as.psem(sem))
rsquared(sem)
```

```{r}
semeff_perc_inla <- semEff(sem, R = 1000, seed = 13, parallel = "no",
  ci.type = "perc"
)
save(semeff_perc_inla, file = get_mypath("data", "semeff_perc_inla.rda"))
```

```{r}
loadd(environment_pca)
sp_for_sem <- data_inla %>%
  group_by(station) %>%
  summarise(across(facet_var, median))

basin_station <- data_inla %>%
  select(c(station, basin)) %>%
  group_by(station) %>%
  summarise(across(c("basin"), unique))

sp_for_sem <- sp_for_sem %>%
  left_join(environment_pca %>%
    mutate(station = as.character(station)) %>%
    select(c(station, log_RC1, log_RC2)),
    by = "station") %>%
  left_join(basin_station, by = "station")
```

```{r}
sp_sem <- list(
     log_rich_std = lmer(log_rich_std ~ log_RC1 + log_RC2 + (1 | basin), data = sp_for_sem),
     log_bm_std = lmer(log_bm_std ~ log_rich_std + log_RC1 + log_RC2 + (1 | basin), data = sp_for_sem),
     ct_ff = lmer(ct_ff ~ log_rich_std + log_bm_std + log_RC1 + log_RC2 + (1 | basin), data = sp_for_sem),
     w_trph_lvl_avg = lmer(w_trph_lvl_avg ~ log_rich_std + log_bm_std + log_RC1 + log_RC2 +
       (1 | basin), data = sp_for_sem)
)
sp_psem <- as.psem(sp_sem)
summary_sp_sem <- summary(sp_psem)
plot(sp_psem,
  node_attrs = data.frame(
    shape = "rectangle", fixedsize = TRUE, width = .8, color = "black",
    fillcolor = "lightgrey", nodesep = 2))
rsquared(sp_psem)
```

```{r}
sp_semeff_perc <- semEff(sp_sem, R = 1000, seed = 13, parallel = "no",
  ci.type = "perc", ran.eff = "basin"
)
save(sp_semeff_perc, file = get_mypath("data", "sp_semeff_perc.rda"))
```

## Model performance

```{r}
gaussian_inla_rand <- gaussian_inla_no_drivers %>%
  mutate(
        hpd_random = map(
          mod,
          ~get_hpdmarginal_inla(
            inla_mod = .x,
            type = "rand"
          )
        )
        ) %>%
      select(-mod) %>%
      unnest(hpd_random)
```

```{r}
gaussian_inla_var_fitted <- gaussian_inla_no_drivers %>%
      mutate(
        var_pred = furrr::future_map(mod, function(y) {
          map_dbl(y$marginals.fitted.values,
            ~var(inla.rmarginal(100, .x))
          )
        }
          )
      ) %>%
    select(-mod)
```

```{r}
r2_inla <- gaussian_inla_var_fitted %>%
      left_join(get_std_inla_from_rand(inla_rand_tab = gaussian_inla_rand), by = "response") %>%
      mutate(
        r2_mvp_marg = pmap(
          list(var_pred, intercept_basin, intercept_basin_station, epsilon),
          ~r2_mvp(var_pred = ..1, std_intercept = c(..2, ..3), epsilon = ..4, type = "marginal")
          ),
        r2_mvp_cond = pmap(
          list(var_pred, intercept_basin, intercept_basin_station, epsilon),
          ~r2_mvp(var_pred = ..1, std_intercept = c(..2, ..3), epsilon = ..4, type = "conditional")
          ),
        r2_mvp_marg_mean = map_dbl(r2_mvp_marg, mean),
        r2_mvp_marg_med = map_dbl(r2_mvp_marg, median),
        r2_mvp_marg_sd = map_dbl(r2_mvp_marg, sd),
        r2_mvp_cond_mean = map_dbl(r2_mvp_cond, mean),
        r2_mvp_cond_med = map_dbl(r2_mvp_cond, median),
        r2_mvp_cond_sd = map_dbl(r2_mvp_cond, sd),
        lab_r2_marg = paste0("~~~~R^2 == ", round(r2_mvp_marg_med, 2)),
        lab_r2_cond = paste0("~~~~R^2 == ", round(r2_mvp_cond_med, 2)),
        r2_mvp_marg95hpd = map(r2_mvp_marg, ~coda::HPDinterval(coda::as.mcmc(.x))),
        r2_mvp_marg95hpdci = map2_chr(r2_mvp_marg95hpd, r2_mvp_marg_mean,
          ~paste0(
            format(round(.y, 2), nsmall = 2),
            " [",
            format(round(.x[, "lower"], 2), nsmall = 2),
            ",",
            format(round(.x[, "upper"], 2), nsmall = 2),
            "]")
          ),
        r2_mvp_cond95hpd = map(r2_mvp_cond, ~coda::HPDinterval(coda::as.mcmc(.x))),
        r2_mvp_cond95hpdci = map2_chr(r2_mvp_cond95hpd, r2_mvp_cond_mean,
          ~paste0(
            format(round(.y, 2), nsmall = 2),
            " [",
            format(round(.x[, "lower"], 2), nsmall = 2),
            ",",
            format(round(.x[, "upper"], 2), nsmall = 2),
            "]")
          ),
      )
r2_inla %>%
  select(response, r2_mvp_marg95hpdci, r2_mvp_cond95hpdci)
```

```{r}
r2_sem <- rbind(
  rsquared(sp_psem) %>%
  select(Response, Marginal, Conditional) %>%
  mutate(type = "spatial"),
rsquared(sem) %>%
  mutate(Marginal = R.squared, Conditional = NA, type = "temporal") %>%
  select(Response, Marginal, Conditional, type)
)

```

### 2022-09-20 random_network.Rmd
Add reanalysis with INLA

@@
 ---
+
+#
+
+- Nombre de liens in and out
+
+- Simulation avec degree in + out (somme des colonnes et des lignes)
+- Rajouter extinction secondaire
 
@@
   deframe()
+
 ```
@@
   if (ncol(ff_metaweb) == 0) {
+    l_in_ff <- NA
+    l_out_ff <- NA
     ff_ind <- NA
@@
   } else {
+    l_in_ff <- colSums(ff_metaweb)
+    l_out_ff <- rowSums(ff_metaweb)
     ff_ind <- NetIndices::GenInd(ff_metaweb)
@@
     ff_ind = ff_ind,
+    l_in_ff = l_in_ff,
+    l_out_ff = l_out_ff,
     ct = ct,
@@
   } else {
+    l_in_ff <- colSums(ff_metaweb)
+    l_out_ff <- rowSums(ff_metaweb)
     ff_ind <- NA
@@
   if (ncol(x) == 0) {
+    l_in <- NA
+    l_out <- NA
     ind <- NA
@@
   } else {
+    l_in <- colSums(x)
+    l_out <- rowSums(x)
     ind <- NA
@@
     ff_ind = ff_ind,
+    l_in = l_in,
+    l_in_ff = l_in_ff,
+    l_out = l_out,
+    l_out_ff = l_out_ff,
     ct = ct,
@@
       ~ext_seq[1:.x]),
-    metaweb = furrr::future_map(
-      seq_along(ext_seq),
-      ~metaweb[
-        !rownames(net) %in% names(ext_seq)[1:.x],
-        !colnames(net) %in% names(ext_seq)[1:.x]
+    metaweb = furrr::future_map(seq_along(ext_seq),
+      function(x) {
+      tmp <- metaweb[
+        !rownames(net) %in% names(ext_seq)[1:x],
+        !colnames(net) %in% names(ext_seq)[1:x]
         ]
+
+      mask_link <- colSums(tmp) != 0
+      return(tmp[mask_link, mask_link])
+      }
     )
@@
 ```{r, eval=FALSE}
+library(furrr)
 plan(sequential)
@@
 )
+
 nsim <- 10
-
 sim_random_tlvl <- tibble(
@@
     ]
+
+  # Remove without feeding links
+  mask_link <- colSums(decreasing_tlvl_metaweb) != 0
+  decreasing_tlvl_metaweb <- tmp_metaweb[mask_link, mask_link]
   sim_dec_tlvl_species[[i]] <- get_fw_metrics2(decreasing_tlvl_metaweb,
@@
     ]
+
+  # Remove without feeding links
+  mask_link <- colSums(increasing_tlvl_metaweb) != 0
+  increasing_tlvl_metaweb <- tmp_metaweb[mask_link, mask_link]
   sim_inc_tlvl_species[[i]] <- get_fw_metrics2(increasing_tlvl_metaweb,
@@
 }
+
 dec_species_result <- tibble(
@@
       ]
+    # Remove without feeding links
+    mask_link <- colSums(tmp_metaweb) != 0
+    tmp_metaweb <- tmp_metaweb[mask_link, mask_link]
     sim_random_tlvl_species[[i]][[j]] <- get_fw_metrics2(

### 2022-09-20 paper/manuscript.Rmd
Rewrite introduction

@@
 
-# Introduction
-
-## Trends of biodiversity need to be assessed at multiple facets
-
-Multiple studies reported dramatic declines of population and community biomass
-[@ceballos_biological_2017; @hallmann_more_2017; @albano_native_2021], as well
-as decrease in species richness [@barnosky_has_2011; @newbold_global_2015] but
-also recent studies reported non significant temporal trends in species richness
-[@vellend_global_2013; @dornelas_assemblage_2014; @blowes_geography_2019], total
-abundance [@klink_meta-analysis_2020], high turnover in species composition
-[@dornelas_assemblage_2014; @blowes_geography_2019]. Unfortunately, studies
-often focus on the temporal trend of one dimension of biodiversity
-[@hallmann_more_2017; @klink_meta-analysis_2020, but see 2 in
-@dornelas_assemblage_2014; @blowes_geography_2019]. However biodiversity is a
-multidimensional concept and the functioning of ecosystem depends ultimately on
-several dimensions of biodiversity, such as species richness, evenness and
-functional composition^[1]  [@cardinale_biodiversity_2012; @duffy_why_2009], the
-documentation of the trend of one biodiversity facet is likely insufficient to
-understand changes in community structure and ultimately predict their
-consequences on ecosystem functioning.
-
-[^1]: Commentaire de Colin: *je pense qu'il faut lister les facet de biodiv qu'on
-va etudier. sans forcement s'y limiter?* Ici je pense que la composition en role
-trophique rentre dans "functional composition" sans rentrer dans le détail.
-
-## Current knowledge mainly comes from space-for-time substitution
-
-Current knowledge on the links among the different facets of biodiversity mainly
-comes from spatial comparison [@dunne_network_2006;
-@soininen_relationship_2012; @grace_integrative_2016; @danet_species_nodate],
-which is used to predict how community structure will change in time, under the
-assumption of the space-for-time substitution. It supposes a homology between
-variations in space and in time, i.e. that spatial sequences correspond
-to temporal sequences. This method have raised criticisms
-[@damgaard_critique_2019], with studies showing analogous patterns in space and
-time [@blois_space_2013] or not [@johnson_testing_2008;
-@adler_contrasting_2007]. Spatial turnover of species composition, dispersal
-limitation, disturbance and stochastic processes have been hypothesised to be
-responsible for the non-compliance of space-for-time substitution
-[@adler_contrasting_2007; @blois_space_2013]. The recent increase in the availability
-of temporal monitoring of ecological communities makes possible to address
-biodiversity trends for multiple facets.
-
-## Temporal variation of food-webs is largely unknown
-
-More dramatic is that the temporal trends of biodiversity generally neglect
-species interactions. Although species interactions determine for a large part
-community composition, species coexistence and ecosystem functioning
-[@chesson_mechanisms_2000; @thebault_food-web_2003; @oconnor_general_2017].
-Furthermore, species interactions can imply tremendous secondary extinctions
-[@paine_note_1969; @dunne_network_2002]. In food-webs, spatial comparisons in
-empirical and theoretical studies generally reported that trophic level
-positively scales to community biomass [@wang_biodiversity_2018;
-@danet_species_nodate]. Trophic level has also been shown to stabilise the
-temporal variation of community biomass [@shanafelt_stability_2018;
-@danet_species_nodate]. Connectance, which measures the degree of generalism in
-a network, was shown to increase robustness to extinction [@dunne_network_2002].
-However, the temporal variation of food-web structure is largely unknown
-[@kortsch_disentangling_2021]. Food-web temporal variation are often reported
-across small time-steps [@warren_spatial_1989; @pecuchet_novel_2020;
-@kaartinen_high_2012]. Our knowledge on the variability of food-web structure in
-time are even more scarce and particularly how those temporal variations are
-linked to the temporal variations of other aspects of biodiversity such as
-species richness and community biomass. Spatially, connectance has been shown to
-be negatively related to species richness in empirical food-webs [reviewed in
-@dunne_network_2006]. Connectance has been shown to scale positively or
-negatively with community biomass in theoretical models
-[@thebault_food-web_2003; @poisot_trophic_2013]. Average trophic level was
-previously shown to scale negatively with species richness
-[@danet_species_2021].  In order to improve our knowledge on the consequences of
-biodiversity trends such as community biomass and species richness, it is thus
-crucial to assess how biomass and species richness temporal trends are
-associated to temporal trends of food-web structure.
-
-Even how the temporal trends of community biomass are related to temporal
-trends of species richness is still questionned in natural settings, especially
-in food-webs. Our knowledge on the relationships between food-web structure and
-other facets of biodiversity often comes from the comparison of food-web
-snapshots along spatial gradient, raising the question of the validity of
-space-for-time substitution to infer consequences of species richness and
-community biomass variations on food-web structure.
+# Introduction (564 words)
+
+Global diversity is reported to decline at alarming rates [@]. At local scale,
+recent meta-analysis reported a huge variation in species richness temporal
+trends across various taxa and ecosystem types[@vellend_global_2013;
+@dornelas_assemblage_2014; @blowes_geography_2019], with no net variations in
+species richness[@dornelas_assemblage_2014; @blowes_geography_2019].
+Futhermore, recent studies founs that temporal changes in species richness are
+unrelated to changes in species composition[@dornelas_assemblage_2014;
+@blowes_geography_2019], rising the recognition of the multidimensional nature
+of biodiversity changes[@hillebrand_biodiversity_2018; @blowes_local_no_date]
+and the need for further investigations on how biodiversity changes over time.
+
+Species interactions among species, described as ecological networks, drive for
+a large part community composition, species coexistence, and ecosystem
+functioning [@chesson_mechanisms_2000; @thebault_food-web_2003;
+@oconnor_general_2017]. The structure of ecological networks can trigger or
+impede perturbation propagations, i.e secondary extinctions[@paine_note_1969;
+@dunne_network_2002; @srinivasan_response_2007;
+@stouffer_comparmentalization_2011]. Higher connectance, which measures the
+degree of generalism in a network, is predicted to increase robustness to
+secondary extinctions [@dunne_network_2002; @sole_complexity_2001] and studies
+found that higher trophic level was associated to a lower temporal variability
+of community biomass in theoretical models and empirical
+data[@shanafelt_stability_2018; @danet_species_nodate]. Then, accounting for how
+the structure of ecological networks changes over time according to other
+biodiversity facets is crucial.
+
+Th availability of ecological networks timeseries is
+scarce[@kortsch_disentangling_2021], such as predictions about how the strucure
+of ecological networks change according to changes in species richness come from
+spatial comparison. Spatially, connectance has been shown to be negatively
+related to species richness in small (i.e. below 20 species) empirical food-webs
+[reviewed in @dunne_network_2006], which reflects constraints on the number of
+realizable species interactions or an increasing proportion of specialists in
+more rich foodwebs. Connectance has been shown to scale positively or negatively
+with community biomass in theoretical food-webs [@thebault_food-web_2003;
+@poisot_trophic_2013] while the average trophic level was previously shown to
+scale negatively with species richness [@danet_species_2021].
+
+However, predicting how ecological networks will change in time according to
+other biodiversity facets based on spatial comparison of ecological communities
+is valid as long as assumption of the space-for-time substitution is valid as
+well. Space-for-time substitution supposes a homology between variations in
+space and in time, i.e. that spatial sequences correspond to temporal sequences.
+This method have raised criticisms [@damgaard_critique_2019], with studies
+showing analogous patterns in space and time [@blois_space_2013] or not
+[@johnson_testing_2008; @adler_contrasting_2007]. Spatial turnover of species
+composition, dispersal limitation, disturbance and stochastic processes have
+been hypothesised to be responsible for the non-compliance of space-for-time
+substitution [@adler_contrasting_2007; @blois_space_2013].
 
@@
 methods to reconstruct food-webs [@bonnaffe_comparison_2021;
-@gravel_inferring_2013; @danet_species_nodate] makes possible to assess the
-relationships among several biodiversity facets, including food-web structure.
-We used the standardized monitoring of fish freshwater communities on the period
-1995-2018 over France, documenting the individual size of fishes in
-400 sites during ten years or more. We then reconstruct around 4000 food-webs
-based on allometric relationships and food diet data. We questionned i) how
-temporal trends of food-web structure are  linked to trends of community biomass
-and trends in species richness? ii) Are the relationships observed in time the
-same as those observed in space, i.e. is the space-for-time substitution valid?
-
----
-## Variations of community biomass and species richness are predicted to affect
-community structure #Changes of species richness and community biomass are
-indeed
-#predicted to affect community structure. The positive link between biodiversity
-#and ecosystem functioning in experimental studies predict that loss and
-#gain of species richness should respectively result in loss and gain of
-#community biomass [@tilman_biodiversity_2014; @pennekamp_biodiversity_2018]. But
-#this relation is not always found in natural settings [@grace_integrative_2016;
-#@li_relationship_2018; @maureaud_biodiversityecosystem_2019].
-#
-#Variations of species richness can also result in variation of evenness, i.e.
-#equitability of species abundances or biomasses. Meta-analysis reported that
-#higher evenness of abundances is linked to higher plant biomass in grasslands
-#and primary productivity in marine ecosystems [@soininen_relationship_2012].
-#Furthermore, studies reported that higher evenness plays a role of insurance in
-#face of perturbations [@wittebolle_initial_2009]. Indeed, most studies reported
-#positive relationship between species richness and evenness, but also neutral
-#and negative ones [@soininen_relationship_2012; @ma_species_2005;
-#@maureaud_biodiversityecosystem_2019].
-## Variations of community biomass and species richness are predicted to affect food-web structure
-
----
+@gravel_inferring_2013; @danet_species_2021] makes possible to overcome
+those research gaps. We used a standardized monitoring of fish riverine 
+communities on the period 1995-2018 over France, documenting the individual size
+of fishes in 400 sites during ten years or more. We restructed around 4000
+food-webs based on allometric relationships and food diet data, and then
+computed connectance, and average trophic level as well as community biomass and
+species richness.
+
+Our primary objective was to assess how the local structure of foodwebs changes
+over time according to simultaneous changes in community biomass and species
+richness over time. Our second objective was to assess if the relationships
+between changes in food-web structure, community biomass and species richness,
+are the same over space and over time, i.e. is the space-for-time substitution
+valid?  To do so, we first assessed the temporal trends in food-web structure.
+We then built structural equation model to assess the relationships among the
+temporal trends of the different facets of food-web structure.
 

### 2022-09-20 paper/wordstack.Rmd
Late update + add range of temporal data in stations
Fix results
New analysis with different subdataset
Update introduction and results
Rewrite introduction

@@
 ---
+
+# Main messages
+
+- Different assembly processes between biomass and richness
+  - 
+- Space for time works well for biomass but less for species richness
+  - Connectance and average trophic level
 
@@
 
-1. community structure are dynamics and affect ecosystem functions 
-    1. species interactions ?
-    2. biomass or richness
+1. Global trends of biodiversity
+   1. Global declines and threats 
+   2. Reported richness and biomass trends
+   3. Continue to explore trends in community structure and its consequences
+
+2. Ecological communities are ecological networks
+   1. Species interactions matter for ecosystem functioning
+   2.  
+3. Trends in richness and biomass should result in alteration of ecological
+   networks 
+   1. Spatial prediction
+   2. But space-for-time...
+
+4. Limitations before this study
+   1. Low availability of long temporal series 
+   1. No reconstruction method
+   1.
+
+5. Study objectives
+
+3. Colonisation / Extinction sequences in natural settings
+    1. Space for time substitution
+    2. Communities are not affected randomly as environment species niche
+    3. sequence: is losing something = adding something ?
+    4. assembly / disassembly processes
 
@@
 	2. persistance / connectance
-
-3. Colonisation / Extinction sequences in natural settings
-    1. Space for time substitution
-    2. Communities are not affected randomly as environment species niche
-    3. sequence: is losing something = adding something ?
-    4. assembly / disassembly processes
 
@@
 3. Network reconstruction
-4. Statistical analysis
+4. Temporal trends 
+5. Statistical analysis
 

### 2022-10-24 paper/manuscript.Rmd
Switched all figures and analysis to targets

@@
 ```{r}
-loadd(rsq_table_bm_rich_mono_stable_trends)
-loadd(reg_table_bm_rich_mono_stable_trends)
-load(here::here("data", "semeff.rda"))
-load(here::here("data", "sp_semeff.rda"))
+tar_load(full_data2)
+nb_st <- unique(full_data2$station) %>% length
+rm(full_data2)
 ```
 
-```{r}
-net_var_bm <- c("log_rich_std", "ct_ff", "w_trph_lvl_avg", "piel_bm",
-      "piel_nind")
-net_var_rich <- c("log_bm_std", "ct_ff", "w_trph_lvl_avg", "piel_bm",
-      "piel_nind")
-```
+# Abstract (250 words max)
 
-```{r}
-loadd(slope_com_var_no_covar, st_mono_trends_stable_rich_bm)
-loadd(range_data)
-```
-```{r}
-nb_st <- unique(slope_com_var_no_covar$station) %>% length
-rm(slope_com_var_no_covar)
-nb_st_rich_bm <- st_mono_trends_stable_rich_bm %>% length
-```
+# Signifiance (120 words)
 
@@
 
-# Methods
-
-## Data
-
-We used a monitoring of freshwater fishes conducted all over France and
-conducted by the Office Français de la Biodiversité (OFB, previously known as
-ONEMA and AFB). The sampling protocols were standardized since 1995 and a
-complete description of the sampling process can be found in
-@danet_species_nodate (main text and appendixS2). The fishes are sampled using
-electrofishing all across the streams in shallow streams and over the bank by
-boat in deeper streams. All the fishes are counted and the bodysize of fishes are
-recorded for a sample of them, enabling the estimate the distribution of
-individual bodysize by species for each sampling [@bonnaffe_comparison_2021;
-@danet_species_nodate].
-
-## Data selection
-
-We selected the sites that have been monitored at least 10 years on the
-1995-2018 period, with the same sampling protocol over time. We selected
-one sampling a year by site. In each site, we ensured low temporal heterogeneity
-in sampling period by selecting sampling that were performed in the same period,
-leading to a mean standard deviation of sampled month in each site of three
-weeks [@danet_species_nodate]. Those steps leads to the selection of 
-`r nb_st` sites (Figure \@ref(fig:matmet)A).
-
-## Biomass
-
-We first inferred the body mass of each fish individual considering an allometric
-law, $B_i = 0.01 \times l_i^{3.03}$, $B_i$ being the biomass expressed in gram and $l_i$ the
-body length of the individual $i$ expressed in millimetres  [@froese_cube_2006]. Then the
-biomass of each species and community biomass were obtained by summing the body
-mass of individuals. Finally, the biomass was reported to the sampled surface
-(in $m^2$) to account for sampling effort.
-
-## Food-web inference
-
-We inferred food-web structure in two steps [@bonnaffe_comparison_2021;
-@danet_species_2021]: (1) we first computed the metaweb, describing the
-potential trophic interactions among all size classes species, (2) then we
-extracted each yearly snapshot of food-webs by extracting species size classes
-and their interactions according to their presence in a given sampling event.
-
-We inferred the metaweb according to ontogenic diet data and body size
-[@gravel_inferring_2013; @poisot_structure_2016; @brose_predator_2019;
-@bonnaffe_comparison_2021; @danet_species_2021]. The method is extensively
-described in @bonnaffe_comparison_2021 and @danet_species_2021. The food diet of
-stream fishes changes along their life cycle or stage, therefore according to
-their body size. Each fish species was divided in nine size classes, named
-"trophic species", equally distributed in their observed body size range. Thus,
-a trophic species is a group of individuals of the same species and size class
-that are expected to share the same preys and predators because trophic
-interactions are largely determined by predator-prey size ratio
-[@brose_allometric_2006]. We also added seven nodes present in the ontogenic
-food diet database: detritus, biofilm, phytoplankton, zooplankton, macrophages,
-phytobenthos and zoobenthos.  The resulting metaweb contained 45 fish species
-divided into nine size classes plus 7 resource nodes, summing up to 412 nodes.
-Consideration of size classes, i.e.  trophic species instead of species,
-improves inference of trophic interactions [@jennings_weak_2001].
-
-We determined the feeding interactions of trophic species according to their
-species identity and their body size. The diet database described two or three
-life stages by fish species, each one being delimited by body size
-[@bonnaffe_comparison_2021; @danet_species_nodate]. The ontogenic fish diet
-database was filled according to fishbase (Froese et al. 2021) and literature
-[@bonnaffe_comparison_2021; @danet_species_nodate].
-
-The feeding interactions among fishes were based on the body size ratio
-between predators and preys. We defined the predation window of a
-piscivorous trophic species as 3% to 45% of its midpoint
-[@mittelbach_ontogeny_1998; @claessen_impact_2002; @hart_handbook_2008].  A
-trophic link was defined between the piscivorous trophic species and all the
-trophic species whose midpoint in body size range was included in the predation
-window.  The fish-resource trophic links were set between the trophic species
-and the resources nodes according to the food items of their size class.
-Finally, the feeding interactions between resources were defined according to the
-literature [@allan_stream_2007; @hart_handbook_2008].
-
-## Community and food-web structure
-
-At each site, yearly food-webs were described by their community biomass,
-species richness and the evenness of biomass across species. The evenness was
-quantified with the Pielou index, computed as the Shannon diversity index
-divided by the number of species ($P = \frac{H'}{N}$, with $H'$ being the
-Shannon diversity index and $N$ the number of species). Yearly food-web
-structure was described by their connectance, describing the degree of
-generalism in a network [@dunne_network_2006; @delmas_analysing_2019]. It was
-computed as the ratio between the number of actual links and the number of
-potential links ($C = \frac{L}{S(S-1)}$, with $L$ being the number of links and
-$S$ the number of trophic species). We also computed the average trophic level,
-weighted by the biomass of the trophic species. The trophic level of a trophic
-species was computed recursively as 1 added to the mean trophic level of the
-preys that it consumes [@herendeen_ecological_2008].
-
-## Temporal trends of food-web
-
-To characterize the links among the temporal trends of network and community
-structure and the temporal trends of community biomass and species richness, we
-characterized the temporal trajectories of food-web structure at each site. We
-modeled a linear relationship between food-web structure and
-time with a second order polynome, which allows to assess both the direction and the monotony of temporal
-trends [@rigal_method_2020]. We selected the sites that displayed monotonic
-trends for these variables, i.e. the ones for which the second order polynomial
-term was non significant according to t-tests, to avoid the inclusion of many
-types of biomass and species richness trends (i.e. accelerating, decelerating,
-etc...), . Over the `r nb_st` monitored sites, the selection procedure resulted in 
-`r nb_st_rich_bm` sites for community biomass and species richness analysis.
-However, the results were robust to the inclusion of non monotonic trends (Fig.
-SXX).
-
-There was a clear relationship between the size of the communities and their
-temporal dynamics. Communities that displayed low community biomass at the
-beginning of their monitoring tend to display a biomass increase through time
-and reversely, we observed the same pattern for species richness. We
-log-transformed (natural logarithm) community biomass and species richness to model their trends,
-which decreased the former effect (Fig. SXX). Temporal
-trends of community biomass and species richness were thus expressed in rate of
-change by year.
-
-## Spatial
-
-To assess the validity of the space-for-time substitution hypothesis, we
-compared the relationships among food-web structure in time to the ones observed
-in space. To do so, we selected the same sites that were used
-for the temporal analysis. We summarised temporal series of each station by the
-median value over time of each facet of food-web structure described above.
-
-# Statistical analysis
-
-We modelled the relationships among food-web structure, that is
-connectance and average trophic level, and community biomass ($dB$) and species
-richness ($dR$) with Structural Equation Models. We modelled a it such as species
-richness is related to community biomass and food-web structure. In
-turn community biomass was related to food-web structure. We computed one
-structural equation model to assess the relationships among the temporal trends
-and one for the relationships over the spatial gradient. As spatial variation of
-food-web structure are partly driven by environmental gradients, so we
-controlled relationships among variables by adding two PCA axis
-synthesizing respectively (1) stream gradient from upstream to downstream and
-(2) enrichment (Fig. \@ref(fig:matmet)). Enrichment was characterized by the
-average Biological Oxygen Demand [BOD, @mallin_factors_2006][^2]. We further
-added a random effect of the hydrographic basin on the intercept.
-
-In order to control for the uncertainties of the estimated temporal trends, each
-temporal trend was weighted by the inverse of the sum of the standard errors
-of the estimated trends, i.e. estimated slopes for the response and the
-explicative variables ($w_j = \dfrac{1}{\sum{e_j}}$, $w_j$ being the
-weight, and $s_{e_j}$ the standard error on the
-temporal trends of the variables).
-
-The coefficients of the Structural Equation Models were computed with
-PiecewiseSEM R package [@lefcheck_piecewisesem_2016]. The coefficients were
-standardizated and the confidence intervals were computed with semEff R package
-[@murphy_semEff_2021]. Confidence intervals were obtained by bootstrapping the
-linear models 1000 times and computing adjusted bootstrap percentile interval
-(BCa), which are adjusted for asymetric distribution of resampling.
-
-All the statistical models displayed low multicollinearity (Variance inflation
-factor < 3, Table SXX).  We visually inspected the residuals of the linear
-models.
-
-```{r}
-
-fig_mat_cap <- paste0("Using  sites of stream fishes in French streams that
-  have been monitored at least 10 years, 1) we infered the food-web at each site
-and each sampling event based on ontogenic food diet information for each
-species and predator-prey body size ratio. 2) We computed the temporal trends
-and the median of community biomass, species richness, connectance, average
-trophic level and evenness of biomass at each site. 3) We then assessed the
-relationships among a) temporal trends of food-web structure. We also assessed
-the spatial relationships among median food-web structure while controlling for
-the environmental gradient with two axis of a rotated PCA. The first axis of the
-PCA is related to the stream gradient from upstream to downstream while the
-second is related to enrichment (BOD) and site altitude.")
-
-```
-
-```{r matmet, fig.cap=fig_mat_cap, out.width="80%"}
-knitr::include_graphics(get_mypath("figures", "mat_met_inkscape.pdf"))
-```
-
 # Results
@@
 ```{r}
-loadd(rsq_sp_mod, summary_table, sp_models, model_summary)
-
-loadd(rsq_table_bm_rich_mono_stable_trends, sp_rsq_table_bm_rich_mono_stable_trends)
-
-loadd(rigal_classification)
+tar_load(glob_tps_trends_decade_no_drivers)
+gbm <- get_effect_ci(resp = "log_bm_std", ci_lvl = "level:0.80", p = TRUE)
+gr <- get_effect_ci(resp = "log_rich_std", ci_lvl = "level:0.80", p = TRUE)
+gt <- get_effect_ci(resp = "w_trph_lvl_avg", ci_lvl = "level:0.80", p = FALSE)
+gct <- get_effect_ci(resp = "ct_ff", ci_lvl = "level:0.80", p = FALSE)
 ```
@@
 ```{r}
-log_trends_percent <- rigal_classification %>%
-  unnest(classif) %>%
-  filter(variable %in% c("log_bm_std", "log_rich_std")) %>%
-  select(variable, station, linear_slope, linear_slope_strd_error) %>%
-  mutate(
-    slp_percent = round((exp(linear_slope) - 1) * 100),
-    std_err_percent = round((exp(linear_slope_strd_error) - 1) * 100)
+tar_load(r2_inla_tab)
+r2_inla_report <- r2_inla %>%
+  select(response, r2_mvp_marg95hpdci, r2_mvp_cond95hpdci)
+r2ic <- map(
+  setNames(r2_inla_report$response, r2_inla_report$response),
+  ~r2_inla_report[r2_inla_report$response == .x, ]$r2_mvp_cond95hpdci
 )
-resume_log_trends <- log_trends_percent %>%
-  group_by(variable) %>%
-  summarise(
-    mean = mean(slp_percent, na.rm = TRUE),
-    sd = sd(slp_percent, na.rm = TRUE))
+
+tar_load(r2_sem)
+```
+Using a hierarchical model to estimate conjointly the temporal trends of  
+foodweb strucure at each site, we found weak evidence of a global decrease in
+community biomass (CI80%:`r gbm` by decade; median [Credible Interval]) but of a
+global increase in species richness (CI80%: `r gr` by decade) across the `r nb_st` sites. 
+We did not find evidence of a global trends in connectance and average trophic
+level (CI80%: `r gct` and `r gt` respectively). The hierarchical model captured
+well the variance associated to the spatial structure of the data with
+conditional $R^2$ going from  `r r2ic$log_bm_std` (mean [CI95%]) for community
+biomass to `r r2ic$log_rich_std` for species richness (Table SXX).
+
+```{r}
+sem_cap <- "(a) Structural equation models linking the temporal trends of the food-web
+structure. The path widths are proportional to the standardized slope coefficients. The standardized slope coefficients and their associated 95%
+  confidence intervals are displayed along the path. (b to f) Direct bivariate
+relationships derived from the structural equation model. The distribution of the
+site temporal trends are displayed in Fig. SXX."
+```
+
+```{r sem, fig.cap = sem_cap}
+knitr::include_graphics(here::here("figures", "fig2.png"))
 ```
@@
 ```{r}
-class_trends_bm_rich <- rigal_classification %>%
-  filter(variable %in% c("log_bm_std", "log_rich_std")) %>%
-  unnest(classif) %>%
-  select(variable, station, direction, acceleration, shape_class)
+tar_load(semeff_tot)
+semeff_tot <- semeff_tot %>%
+  mutate(across(c(response, predictor), ~str_remove(.x, "mean_")))
 
-res_trends <- class_trends_bm_rich %>%
-  filter(acceleration == "constant") %>%
-  group_by(variable, direction) %>%
-  summarise(n = n()) %>%
-  group_by(variable) %>%
-  mutate(total = sum(n), percent = round(n / sum(n) * 100))
-
-x_var <- c("log_bm_std", "log_rich_std")
-stable_st_var <- map(x_var,
-  ~class_trends_bm_rich[
-    class_trends_bm_rich$variable == .x &
-    class_trends_bm_rich$direction == "stable",
-      ]$station
+rdtps <- map(
+  setNames(
+    c("ct_ff", "w_trph_lvl_avg", "log_bm_std"),
+    c("ct", "tlvl", "bm")
+    ),
+  ~ list(
+    bm = get_semeff_ci(resp = .x, term = "log_bm_std"),
+    r = get_semeff_ci(resp = .x, term = "log_rich_std")
     )
-names(stable_st_var) <- x_var
-
-#sum(stable_st_var[["log_bm_std"]] %in% stable_st_var[["log_rich_std"]] == TRUE) / length(stable_st_var[["log_bm_std"]])
-
-#sum(stable_st_var[["log_rich_std"]] %in% stable_st_var[["log_bm_std"]] == TRUE) / length(stable_st_var[["log_rich_std"]])
-```
-
-```{r}
-loadd(std_table_bm_rich_mono_stable_trends)
-std <-
-  std_table_bm_rich_mono_stable_trends %>%
-  mutate(
-    type = recode(type, spatial = "sp", temporal = "tps"),
-    response = recode(response, log_bm_std = "bm", log_rich_std = "rich", ct_ff
-      = "ct", piel_bm = "p_bm", piel_nind = "p_n", w_trph_lvl_avg = "tlvl"),
-    term = recode(term, log_bm_std = "bm", log_rich_std = "rich")
-    ) %>%
-  rename(t = type, rep = response, sest = std_estimate) %>%
-  mutate_at(vars(sest, stdse), ~round(.x, 2))
-tps_bm <- std %>%
-  filter(t == "tps", term == "bm")
-
-tps_bm_sest <- tps_bm$sest
-names(tps_bm_sest) <- tps_bm$rep
-```
-
-```{r}
-tps_r <- std %>%
-  filter(t == "tps", term == "rich")
-
-tps_r_sest <- tps_r$sest
-names(tps_r_sest) <- tps_r$rep
-```
-
-```{r}
-sp_b <- std %>%
-  filter(t == "sp", term == "bm")
-sp_b_sest <- sp_b$sest
-names(sp_b_sest) <- sp_b$rep
-
-sp_r <- std %>%
-  filter(t == "sp", term == "rich")
-sp_r_sest <- sp_r$sest
-names(sp_r_sest) <- sp_r$rep
-```
-
-```{r}
-rsq_ct <- rsq_table_bm_rich_mono_stable_trends %>%
-  filter(Response == "ct_ff") %>%
-  .$R.squared %>%
-  round(., 2)
-
-rsq_bm <- rsq_table_bm_rich_mono_stable_trends %>%
-  filter(Response == "log_bm_std") %>%
-  .$R.squared %>%
-  round(., 2)
-
-rsq_tlvl_sp <- sp_rsq_table_bm_rich_mono_stable_trends %>%
-  filter(Response == "w_trph_lvl_avg") %>%
-  .$Conditional %>%
-  round(., 2)
-
-rsq_ct_sp <- sp_rsq_table_bm_rich_mono_stable_trends %>%
-  filter(Response == "ct_ff") %>%
-  .$Conditional %>%
-  round(., 2)
-```
-Over the sampling sites in the dataset, we found that
-`r res_trends[res_trends$variable == "log_bm_std", ]$total[1]` stations displayed monotonic trends for biomass. Among them, 
-`r res_trends[res_trends$variable == "log_bm_std" & res_trends$direction == "stable", ]$percent`%
-were classified as stable,
-`r res_trends[res_trends$variable == "log_bm_std" & res_trends$direction == "decrease", ]$percent`%
-as decreasing,
-`r res_trends[res_trends$variable == "log_bm_std" & res_trends$direction == "increase", ]$percent`%
-as increasing. Regarding the species richness, we found that
-`r res_trends[res_trends$variable == "log_rich_std", ]$total[1]` stations displayed monotonic trends.
-`r res_trends[res_trends$variable == "log_rich_std" & res_trends$direction == "stable", ]$percent`%
-were classified as stable,  
-`r res_trends[res_trends$variable == "log_rich_std" & res_trends$direction == "decrease", ]$percent`%
-as decreasing, and 
-`r res_trends[res_trends$variable == "log_rich_std" & res_trends$direction == "increase", ]$percent`% as increasing.
-
-Overall, we found relatively low in the explicative power of statistical
-models linking temporal dynamics of food-web structure and the one of community
-biomass and species richness spanning from $R_{adj}^2= `r rsq_ct`$ for
-connectance to $R_{adj}^2= `r rsq_bm`$ for community biomass (Table SXX).
-The models over the spatial gradient were more performant, with
-$R_{cond}^2$ varing from $`r rsq_tlvl_sp`$ for the average trophic level to
-$`r rsq_ct_sp`$ for connectance (Table SXX), $R_{cond}^2$ being the
-$R^2$conditional to the random effect.
-
----
-#Overall, we found no significant effect of the temporal gain or losses of
-#communinity biomass biomass and species richness on the relationship between the
-#temporal trends of community structure and that of biomass and species richness
-#(Table \@ref(tab:aov)).
----
-
-```{r}
-loadd(sp_fig1_2_bm_rich_mono_stable_trends,
-  pred_bm_rich_mono_stable_trends)
-
-fig1_2 <- get_plot_rich_bm(
-  predict_plot = pred_bm_rich_mono_stable_trends,
-  get_list = TRUE,
-  rm_legend = FALSE,
-  bm_x = "log_bm_std",
-  bm_y = c("ct_ff", "w_trph_lvl_avg"), #, "piel_nind"
-  rich_y = c("ct_ff", "w_trph_lvl_avg", "log_bm_std"), #, "piel_nind"
-  rich_x = "log_rich_std"
 )
-p_bm <- fig1_2$bm
-
-p_sp_bm <- sp_fig1_2_bm_rich_mono_stable_trends$bm[c("log_rich_std", "ct_ff", "w_trph_lvl_avg")]
-```
-
-```{r}
-fig_bef_cap <- paste0(
-  "Relationship between the temporal trends of community biomass 
-  and the one of species richness. Red line correspond to the predictions of the
-  linear models. The lines surrounding points display the standard error
-  associated to the temporal trends. The histograms display the distribution of
-  response and predictive variables."
+rdsp <- map(
+  setNames(
+    c("ct_ff", "w_trph_lvl_avg", "log_bm_std"),
+    c("ct", "tlvl", "bm")
+    ),
+  ~ list(
+    bm = get_semeff_ci(resp = .x, term = "log_bm_std", model = "spatial"),
+    r = get_semeff_ci(resp = .x, term = "log_rich_std", model = "spatial")
+    )
 )
@@
 
-```{r}
-library(ggExtra)
-coeff_bef <- c(
-  rsq = rsq_table_bm_rich_mono_stable_trends %>%
-    filter(Response == "log_bm_std") %$%
-    unlist(.[, c("R.squared")]),
-  reg_table_bm_rich_mono_stable_trends %>%
-    filter(response == "log_bm_std", term == "log_rich_std") %$%
-    unlist(.[, c("estimate", "std.error", "std_estimate", "stdse")])
-  ) %>%
-round(., 2)
-
-beta_rsq <- function(
-  rsq = NULL,
-  beta = NULL,
-  se = NULL) {
-
-  if (!is.null(rsq)) {
-
-    tmp <- "paste(
-    beta, \" (s.e.) \", \" = \",
-    mybeta, \" (\", myse, \"), \",
-    italic(R)^2, \" = \", myrsq
-    )"
-str_replace_all(tmp,
-  c(
-    "myrsq" =  as.character(rsq),
-    "mybeta" = as.character(beta),
-    "myse" = as.character(se)
-  )
-)
-
-  } else {
-
-    tmp <- "paste(
-    beta, \" (s.e) \", \" = \",
-    mybeta, \" (\", myse, \") \" )"
-str_replace_all(tmp,
-  c(
-    "mybeta" = as.character(beta),
-    "myse" = as.character(se)
-  )
-)
-
-  }
-
-}
-
-scale_xy_log_trends <- function(breaks = NULL, axis = "y", sep ="\n") {
-  log_to_percent <- round((exp(breaks) - 1) * 100)
-  labels <- paste0(breaks, sep, log_to_percent, " %")
-
-  if(axis == "y") {
-    fun <- scale_y_continuous
-  } else {
-    fun <- scale_x_continuous
-  }
-
-  fun(breaks = breaks, labels = labels)
-
-}
-```
-
 We found a strong positive relationship between the temporal trends of community
-biomass and the ones of species richness ($r_\delta = `r tps_r_sest["p_bm"]`$,
-Fig. \@ref(fig:bmr) B), meaning that both temporal trends
+biomass and the ones of species richness ($r_\delta = `r rdtps$bm$r`$,
+Fig. \@ref(fig:sem) b), meaning that both temporal trends
 had the same direction in average. At the sites 
@@
 species richness, but half the strength as the temporal one
-($r_\delta = `r sp_b_sest["rich"]`$).
+($r_\delta = `r rdsp$bm$r`$).
 
 The temporal trends of connectance were positively linked with the ones of
-community biomass ($r_\delta = `r tps_bm_sest["ct"]`$), also meaning that both
+community biomass ($r_\delta = `r rdtps$ct$bm`$), also meaning that both
 temporal trends had the same direction in average. That is, the sites where
@@
 a positive relationship between median connectance and median species
-richness ($r_\delta = `r sp_b_sest["ct"]`$). We found a negative 
+richness ($r_\delta = `r rdsp$ct$bm`$). We found a negative 
 relationship between the temporal trends of connectance and the
-ones of species richness ($r_\delta = `r tps_r_sest["ct"]`$, Fig. \@ref(fig:bmr)D)
+ones of species richness ($r_\delta = `r rdtps$ct$r`$, Fig. \@ref(fig:sem)d)
 while we found negative relationship three times stronger between median connectance and
 median species richness along the spatial gradient 
-($r_\delta = `r sp_r_sest["ct"]`$, Fig. \@ref(fig:std)).
+($r_\delta = `r rdsp$ct$r`$, Fig. \@ref(fig:std)).
 
@@
 relationship with the ones of community biomass 
-($r_\delta = `r tps_bm_sest["tlvl"]`$, Fig. \@ref(fig:bmr)B), meaning
+($r_\delta = `r rdtps$tlvl$bm`$, Fig. \@ref(fig:sem)B), meaning
 that sites where community biomass decreased over time, average trophic level
@@
 median average trophic level and median community biomass in space, but half the
-strength as the temporal one ($r_\delta = `r sp_b_sest["tlvl"]`$, Fig.
+strength as the temporal one ($r_\delta = `r rdsp$tlvl$bm`$, Fig.
 \@ref(fig:std)). The temporal trends of average trophic level was unrelated to
@@
 However, we found a strong negative relationship in space 
-($r_\delta = `r sp_r_sest["tlvl"]`$, Fig. \@ref(fig:std)).
+($r_\delta = `r rdsp$tlvl$r`$, Fig. \@ref(fig:std)).
 
 ```{r}
-sp_semeff_tab <- from_semEff_to_table(sp_semeff)
-semeff_tab <- from_semEff_to_table(semeff)
-semeff_tot <- rbind(
-  tibble(semeff_tab, model = "temporal"),
-  tibble(sp_semeff_tab, model = "spatial")
-  ) %>%
-filter(
-  !predictor %in% c("log_RC1", "log_RC2"),
-  effect_type != "mediators"
+ridtps <- map(
+  setNames(
+    c("ct_ff", "w_trph_lvl_avg", "log_bm_std"),
+    c("ct", "tlvl", "bm")
+    ),
+  ~ list(
+    r = get_semeff_ci(resp = .x, term = "log_rich_std", type = "indirect")
     )
-```
-
-```{r}
-semeff_tab_coeff <- semeff_tab %>%
-  mutate(across(where(is.numeric), ~round(., 2))) %>%
-  mutate(eci = paste0(effect, " [", lower_ci, ";", upper_ci, "]"))
-
-sp_semeff_tab_coeff <- sp_semeff_tab %>%
-  mutate(across(where(is.numeric), ~round(., 2))) %>%
-  mutate(eci = paste0(effect, " [", lower_ci, ";", upper_ci, "]")) %>%
-  filter(! predictor %in% c("log_RC1", "log_RC2"))
-
-ctsi <- semeff_tab_coeff %>%
-  filter(response == "ct_ff", effect_type == "indirect")
-ctstr <- semeff_tab_coeff %>%
-  filter(response == "ct_ff", effect_type == "total",
-    predictor == "log_rich_std")
-
-ctspi <- sp_semeff_tab_coeff %>%
-  filter(response == "ct_ff", effect_type == "indirect")
-ctsptr <- sp_semeff_tab_coeff %>%
-  filter(response == "ct_ff", effect_type == "total",
-    predictor == "log_rich_std")
-
-wtsi <- semeff_tab_coeff %>%
-  filter(response == "w_trph_lvl_avg", effect_type == "indirect")
-wtstr <- semeff_tab_coeff %>%
-  filter(response == "w_trph_lvl_avg", effect_type == "total",
-    predictor == "log_rich_std")
-
-wtspi <- sp_semeff_tab_coeff %>%
-  filter(response == "w_trph_lvl_avg", effect_type == "indirect")
-wtsptr <- sp_semeff_tab_coeff %>%
-  filter(response == "w_trph_lvl_avg", effect_type == "total",
-    predictor == "log_rich_std")
+)
+ridsp <- map(
+  setNames(
+    c("ct_ff", "w_trph_lvl_avg", "log_bm_std"),
+    c("ct", "tlvl", "bm")
+    ),
+  ~ list(
+    r = get_semeff_ci(resp = .x, term = "log_rich_std",
+      model = "spatial", type = "indirect")
+    )
+)
+rttps <- map(
+  setNames(
+    c("ct_ff", "w_trph_lvl_avg", "log_bm_std"),
+    c("ct", "tlvl", "bm")
+    ),
+  ~ list(
+    bm = get_semeff_ci(resp = .x, term = "log_bm_std", type = "total"),
+    r = get_semeff_ci(resp = .x, term = "log_rich_std", type = "total")
+    )
+)
+rtsp <- map(
+  setNames(
+    c("ct_ff", "w_trph_lvl_avg", "log_bm_std"),
+    c("ct", "tlvl", "bm")
+    ),
+  ~ list(
+    bm = get_semeff_ci(resp = .x, term = "log_bm_std",
+      model = "spatial", type = "total"),
+    r = get_semeff_ci(resp = .x, term = "log_rich_std",
+      model = "spatial", type = "total")
+    )
+)
 ```
@@
 the species richness has a direct negative effect on connectance but also a
-negative one, twice lower than the former, through community biomass
-($r_\delta$ = `r ctsi[["eci"]]`). It resulted a relatively weak total negative
-effect of species richness on connectance (`r ctstr[["eci"]]`). Spatially,
+positive one through community biomass
+($r_\delta$ = `r ridtps$ct$r`). It resulted a relatively weak total negative
+effect of species richness on connectance (`r rttps$ct$r`). Spatially,
 we also found a positive indirect effect of richness on connectance through
-community biomass but a weak one (`r ctspi[["eci"]]`), resulting in a strong negative total
-effect of richness on connectance (`r ctsptr[["eci"]]`).
+community biomass but a weak one (`r ridsp$ct$r`), resulting in a strong negative total
+effect of richness on connectance (`r rtsp$ct$r`).
 
 The relationships among temporal trends showed a indirect positive effect of
-species richness on average trophic level (`r wtsi[["eci"]]`), resulting in a total positive
-effect of species richness on average trophic level (`r wtstr[["eci"]]`). Over the spatial
+species richness on average trophic level (`r ridtps$tlvl$r`), resulting in a total positive
+effect of species richness on average trophic level (`r rttps$tlvl$r`). Over the spatial
 gradient, we found the same positive indirect effect of richness through
-community biomass (`r wtspi[["eci"]]`). But as the direct effect of richness on connectance
-was strongly negative, it resulted in a total strong negative effect of species
-richness on connectance over the spatial gradient (`r wtsptr[["eci"]]`).
-
-```{r}
-fig_bm_cap <- paste0(
-  "Relationship between community structure and community biomass. Left panel
-  displays the relationships between the temporal trends of community structure
-  and the one of community biomass. Lines correspond to the predictions of the
-  linear models while the points are colored according the median community
-  biomass of the three first years of the given temporal series. The lines
-  surrounding each point represent the standard error associated to the temporal
-  trends. Right panel displays the
-  spatial relationship between median community structure over time and the
-  median community biomass over time."
-)
-
-fig_rich_cap <- paste0(
-  "Relationship between community structure and species richness. Left panel
-  displays the relationships between the temporal trends of community structure
-  and the one of species richness. Lines correspond to the predictions of the
-  linear models while the points are colored according the median species
-  richness of the three first years of the given temporal series. The lines
-  surrounding each point represent the standard error associated to the temporal
-  trends. Right panel displays the spatial relationship between median community
-  structure over time and the median species richness over time."
-
-)
-```
-
-```{r}
-fig_bm_rich_cap <- paste0(
-  "Relationships between the temporal trends of food-web structure
-  and the ones of community biomass (left panel, A, C, E) species richness (right panel, B, D, F).
-  The lines surrounding each point display the standard errors associated to
-  the estimated temporal trends. Red and black lines represent respectively
-  significant and non-significant slopes, both lines displays prediction from
-  the Ordinary Least Squares model. The histograms display the distribution of response and predictive
-  variables. Labels display the unstandardised slope coefficients and their
-  standard errors (see Fig. \\ref{fig:std} for the standardized coefficients).
-  $R^2$ are displayed only on the right panel, as it is the same model for both
-  panels.")
-
-```
-
-```{r bef, fig.cap=fig_bef_cap, out.width="50%"}
-lab_log_rich <- expression(atop("Log species richness ("*m^{-2}*")","trend slope (log / % per year)"))
-lab_log_bm <- expression(atop("Log community biomass ("*g.m^{-2}*")", "trend slope (log / % per year)"))
-
-p_bef <- fig1_2$rich$log_bm_std +
-  labs(
-    y = lab_log_bm,
-    x = lab_log_rich
-  ) +
-scale_xy_log_trends(breaks = c(-.10, -.050, 0, .050, .10), axis = "x") +
-scale_xy_log_trends(breaks = c(-.4, -.2, 0, .4, .2), axis = "y", sep = " / ") +
-    theme(
-      axis.text = element_text(size = 8),
-      axis.title = element_text(size = 10)
-      )
-
-```
-
-```{r}
-fig2 <- fig1_2
-fig2$rich$log_bm_std <- NULL
-fig2$rich <- map(fig2$rich,
-  ~.x +
-    theme(
-      axis.text = element_text(size = 8),
-      axis.title = element_text(size = 10)
-      )
-  )
-fig2$bm <- map2(fig2$bm, names(fig2$rich),
-  ~ .x + theme(
-    axis.text = element_text(size = 8),
-    axis.title = element_text(size = 10)
-    ) +
-  labs(
-    y = paste0(var_replacement()[.y],
-      "\ntrends (per year)"),
-    x = lab_log_bm
-  ) +
-  scale_xy_log_trends(breaks = c(-.40, -.20, 0, .20, .40), axis = "x")
-)
-# Delete redondant legend
-fig2$bm[[1]] <- fig2$bm[[1]] + theme(
-  axis.text.x = element_blank(),
-  axis.ticks.x = element_blank(),
-  axis.title.x = element_blank()
-  )
-
-fig2$rich <- map(fig2$rich,
-  ~ .x + theme(
-    axis.text.y = element_blank(),
-    axis.ticks.y = element_blank(),
-    axis.title.y = element_blank()
-  ) +
-  labs(x = lab_log_rich) +
-  scale_xy_log_trends(breaks = c(-.10, -.050, 0, .050, .10), axis = "x")
-  )
-fig2$rich[[1]] <- fig2$rich[[1]] + theme(
-  axis.text.x = element_blank(),
-  axis.ticks.x = element_blank(),
-  axis.title.x = element_blank()
-  )
-
-```
-
-```{r, eval = FALSE}
-# Add beta and Rsq
-for (i in seq_along(fig2$rich)) {
-
-  resp_var <- names(fig2$rich)[i]
-
-  coeff_rich <- c(
-    rsq = rsq_table_bm_rich_mono_stable_trends %>%
-      filter(Response == resp_var) %$%
-      unlist(.[, c("R.squared")]),
-    reg_table_bm_rich_mono_stable_trends %>%
-      filter(response == resp_var, term == "log_rich_std") %$%
-      unlist(.[, c("estimate", "std.error", "std_estimate", "stdse")])
-    ) %>%
-  round(., 2)
-
-  coeff_bm <- reg_table_bm_rich_mono_stable_trends %>%
-    filter(response == resp_var, term == "log_bm_std") %$%
-    unlist(.[, c("estimate", "std.error", "std_estimate", "stdse")]) %>%
-    round(., 2)
-
-  # Add coeff:
-  fig2$rich[[resp_var]] <- fig2$rich[[resp_var]] +
-  annotate("text", x = -.10, y = Inf, vjust = 1, hjust = 0,
-    size = 2,
-    parse = T,
-    label = beta_rsq(
-      rsq = coeff_rich["rsq"],
-      beta = coeff_rich["estimate"],
-      se = coeff_rich["std.error"]
-    )
-  )
-  fig2$bm[[resp_var]] <- fig2$bm[[resp_var]] +
-  annotate("text", x = -.4, y = Inf, vjust = 1, hjust = 0,
-    size = 2,
-    parse = T,
-    label = beta_rsq(
-      rsq = NULL,
-      beta = coeff_bm["estimate"],
-      se = coeff_bm["std.error"]
-    )
-  )
-}
-```
-
-```{r}
-# Add histograms
-p_bef2 <- p_bef +
-  theme(
-  axis.text.x = element_blank(),
-  axis.ticks.x = element_blank(),
-  axis.title.x = element_blank()
-  ) 
-p_bef_hist <- ggMarginal(p_bef2, type = "histogram")
-#fig2$bm[[1]] <- ggMarginal(fig2$bm[[1]], type = "histogram", margins = "x")
-fig2$rich[[1]] <- ggMarginal(fig2$rich[[1]], type = "histogram", margins = "y")
-fig2$rich[[2]] <- ggMarginal(fig2$rich[[2]], type = "histogram", margins = "y")
-```
-
-```{r}
-sem_cap <- "Structural equation models on the temporal trends of the food-web
-structure. The path display the standardized slopes and their associated 95%
-  confidence intervals."
-```
-
-```{r sem, fig.cap = sem_cap}
-ti <- magick::image_read(here::here("figures", "sem_tps_avg_weight_ok.svg"),  density = 300)
-p <- ggdraw() +
-  draw_image(ti,
-    x = 0, y = 0, hjust = 0, vjust = 0, width = .9, height = 1)
-```
-
-```{r bmr, out.width="100%", fig.height=7, fig.cap=fig_bm_rich_cap}
-#p <- draw_image(here::here("figures", "sem_tps_avg_weight_ok.pdf"),
-#  x = 1, y = 1, hjust = 1, vjust = 1, width = 0.13, height = 0.2)
-biplot_model <- plot_grid(
-  plot_grid(NULL, p_bef_hist,
-    labels = c("", "A"), ncol = 2,
-    rel_widths = c(.54, 1)
-    ),
-  plot_grid(
-  plot_grid(plotlist = fig2$bm,
-    ncol = 1, labels = c("B", "D"),
-    hjust = -5.5, vjust = 1.75,
-    rel_heights = c(.85, 1)
-    ),
-  plot_grid(plotlist = fig2$rich,
-    ncol = 1, labels = c("C", "E"),
-    hjust = -2, vjust = 1.75,
-    rel_heights = c(.85, 1)
-    ),
-  ncol = 2,
-  rel_widths = c(.9, 1)
-  ),
-  nrow = 2,
-  rel_heights = c(.55, 1)
-)
-sem_p <- plot_grid(p, biplot_model, ncol = 2, rel_widths = c(.4, .6))
-
-save_plot(
-  filename = here::here("paper", "figures", "biplot_tps.png"),
-  biplot_model, nrow = 3, ncol = 2, base_asp = 1)
-save_plot(
-  filename = here::here("paper", "figures", "sem_p.png"),
-  sem_p, nrow = 3, ncol =3)
-sem_p
-```
+community biomass (`r ridsp$tlvl$r`). WHATTTT? But as the direct effect of
+richness on average trophic level was strongly negative, it resulted in a total
+strong negative effect of species richness on average trophic level over the
+spatial gradient (`r rtsp$tlvl$r`).
 
@@
   95%.")
-
 ```
@@
 ```{r std, fig.cap=std_cap, fig.width=7, fig.asp = .7}
-p_sem_eff <- semeff_tot %>%
-  mutate(
-    response = var_replacement()[response],
-    predictor = var_replacement()[predictor],
-    effect_type = str_to_sentence(effect_type),
-    model = str_to_sentence(model)
-    ) %>%
-  ggplot(aes(y = predictor, x = effect, colour = effect_type, shape = model)) +
-  geom_point(
-    position = position_dodge(width = 0.4), width = .4) +
-  geom_vline(xintercept = 0) +
-  geom_linerange(
-    aes(xmin = lower_ci, xmax = upper_ci),
-    position = position_dodge(width = 0.4)
-    ) +
-  facet_grid(rows = vars(response)) +
-  labs(
-    y = "Predictor",
-    x = expression(paste("Standardized slope coefficients ", r[delta])),
-    color = "Effect type", shape = "Model") +
-  theme(legend.position = "bottom")
-p_sem_eff
+knitr::include_graphics(here::here("figures", "p_sem_tps_sp.pdf"))
 ```
@@
 
+# Material & Methods
+
+We used a monitoring of freshwater fishes conducted all over France and
+conducted by the Office Français de la Biodiversité (OFB, previously known as
+ONEMA and AFB). The sampling protocols were standardized since 1995 and a
+complete description of the sampling process can be found in
+@danet_species_nodate (main text and appendixS2). The fishes are sampled using
+electrofishing all across the streams in shallow streams and over the bank by
+boat in deeper streams. All the fishes are counted and the bodysize of fishes are
+recorded for a sample of them, enabling the estimate the distribution of
+individual bodysize by species for each sampling [@bonnaffe_comparison_2021;
+@danet_species_nodate].
+
+We selected the sites that have been monitored at least 10 years on the
+1995-2018 period, with the same sampling protocol over time. We selected
+one sampling a year by site. In each site, we ensured low temporal heterogeneity
+in sampling period by selecting sampling that were performed in the same period,
+leading to a mean standard deviation of sampled month in each site of three
+weeks [@danet_species_nodate]. Those steps leads to the selection of 
+`r nb_st` sites (Figure \@ref(fig:matmet)A).
+
+## Biomass
+
+We first inferred the body mass of each fish individual considering an allometric
+law, $B_i = 0.01 \times l_i^{3.03}$, $B_i$ being the biomass expressed in gram and $l_i$ the
+body length of the individual $i$ expressed in millimetres [@froese_cube_2006]. Then the
+biomass of each species and community biomass were obtained by summing the body
+mass of individuals. Finally, the biomass was reported to the sampled surface
+(in $m^2$) to account for sampling effort.
+
+## Food-web inference
+
+We inferred food-web structure in two steps [@bonnaffe_comparison_2021;
+@danet_species_2021]: (1) we first computed the metaweb, describing the
+potential trophic interactions among all size classes species, (2) then we
+extracted each yearly snapshot of food-webs by extracting species size classes
+and their interactions according to their presence in a given sampling event.
+
+We inferred the metaweb according to ontogenic diet data and body size
+[@gravel_inferring_2013; @poisot_structure_2016; @brose_predator_2019;
+@bonnaffe_comparison_2021; @danet_species_2021]. The method is extensively
+described in @bonnaffe_comparison_2021 and @danet_species_2021. The food diet of
+stream fishes changes along their life cycle or stage, therefore according to
+their body size. Each fish species was divided in nine size classes, named
+"trophic species", equally distributed in their observed body size range. Thus,
+a trophic species is a group of individuals of the same species and size class
+that are expected to share the same preys and predators because trophic
+interactions are largely determined by predator-prey size ratio
+[@brose_allometric_2006]. We also added seven nodes present in the ontogenic
+food diet database: detritus, biofilm, phytoplankton, zooplankton, macrophages,
+phytobenthos and zoobenthos.  The resulting metaweb contained 45 fish species
+divided into nine size classes plus 7 resource nodes, summing up to 412 nodes.
+Consideration of size classes, i.e.  trophic species instead of species,
+improves inference of trophic interactions [@jennings_weak_2001].
+
+We determined the feeding interactions of trophic species according to their
+species identity and their body size. The diet database described two or three
+life stages by fish species, each one being delimited by body size
+[@bonnaffe_comparison_2021; @danet_species_nodate]. The ontogenic fish diet
+database was filled according to fishbase (Froese et al. 2021) and literature
+[@bonnaffe_comparison_2021; @danet_species_nodate].
+
+The feeding interactions among fishes were based on the body size ratio
+between predators and preys. We defined the predation window of a
+piscivorous trophic species as 3% to 45% of its midpoint
+[@mittelbach_ontogeny_1998; @claessen_impact_2002; @hart_handbook_2008].  A
+trophic link was defined between the piscivorous trophic species and all the
+trophic species whose midpoint in body size range was included in the predation
+window.  The fish-resource trophic links were set between the trophic species
+and the resources nodes according to the food items of their size class.
+Finally, the feeding interactions between resources were defined according to the
+literature [@allan_stream_2007; @hart_handbook_2008].
+
+## Community and food-web structure
+
+At each site, yearly food-webs were described by their community biomass,
+species richness and the evenness of biomass across species. The evenness was
+quantified with the Pielou index, computed as the Shannon diversity index
+divided by the number of species ($P = \frac{H'}{N}$, with $H'$ being the
+Shannon diversity index and $N$ the number of species). Yearly food-web
+structure was described by their connectance, describing the degree of
+generalism in a network [@dunne_network_2006; @delmas_analysing_2019]. It was
+computed as the ratio between the number of actual links and the number of
+potential links ($C = \frac{L}{S(S-1)}$, with $L$ being the number of links and
+$S$ the number of trophic species). We also computed the average trophic level,
+weighted by the biomass of the trophic species. The trophic level of a trophic
+species was computed recursively as 1 added to the mean trophic level of the
+preys that it consumes [@herendeen_ecological_2008].
+
+## Temporal trends of food-web
+
+We modeled the temporal trends of food-web structure at each site ($Y_i$) using 
+linear hierarchical model. Time was considered as the number of year since the
+first sampling ($t = 0$) at each site. We accounted for the spatial structure of
+the data by adding random intercepts ($a$) and slopes ($b$) for the
+basin ($a_n$, $b_n$) and site ($a_{i|n}$, $b_{i|n}$) identity, site effects
+being nested in the basin one.
+
+$$
+\begin{aligned}
+    Y_{i|n, t} &= \alpha + \betaTime_t + \epsilon_{i|n, t}
+  (\#eq:gen)
+\end{aligned}
+$$
+
+- $\alpha = \alpha_0 + a_n + a_{i|n}$
+- $\beta = \mu + b_n + b_{i|n}$
+- $a_n, a_{i|n}, b_n, b_{i|n}, \epsilon_{i|n, t} \sim \mathcal{N}(0,\,\sigma^{2})$
+- $n$: basin, $i$: site $i$, $t$: time $t$
+
+The model parameters were estimated using INLA (Integrated Nested Laplacian
+Approximation) bayesian inference with default uninformative priors
+[@rue_bayesian_2017]. The prior distributions for the fixed intercept and slope were
+modelled as a flat normal distribution with a mean of zero ($\mathcal{N}(0,\, 1000)$).
+Prior distributions for the gaussian error $\epsilon_{i|n, t}$ and the random
+effects were modelled as a log gamma distribution with
+shape and inverse scale parameters ($\mathcal{G}(s, \, \tau) = \mathcal{G}(1, \,
+5.10^-5)$), then their respective standard deviation were obtained by
+backtransforming the inverse scale parameter ($\sigma = 1 / \sqrt{\tau}$).
+Community biomass and species richness were logged transformed.
+
+The performance of the model was assessed visually by plotting the fitted versus
+the observed values (Fig. SXX). We also visually inspected the Posterior
+Integral Transform (PIT) and Conditional Predictive Ordinate (CPO) to assess
+the quality of the model fit. We also computed the marginal ($R^2_m$)and
+conditional ($R^2_c$) R-squared of the models following previous formulations
+[@nakagawa_general_2013; @lahuis_explained_2014]. In order to account for the
+variability associated with the priors [@gelman_r-squared_2019], we computed the variance of the
+posterior distribution  of each predicted
+values ($Var_{fit} = \sigma^2(\hat{Y_i})$). We computed $R^2$ values for each predicted
+values, then obtaining a $R^2$ distribution [@gelman_r-squared_2019]. We reported mean marginal and
+conditional $R^2$ associated the 95% credible interval computed using the
+Highest Posterior Density method.
+
+$$
+R^2_m = \dfrac{Var_{fit}}{Var_{fit} + Var_{res}} = \dfrac{\sigma^2(\hat{Y_i})}{\sigma^2(\hat{Y_i}) + \sigma^2(Y_i - \hat{Y_i})}
+$$
+
+$$
+R^2_c = \dfrac{Var_{fit} + (a_n)^2 + (a_{i|n})^2}{Var_{fit}  + (a_n)^2 + (a_{i|n})^2 + Var_{res}}
+$$
+
+$y_i$ and $\hat{y_i}$ being respectively the observations and the
+predicted values, $Var_{fit}$ and $Var_{res}$ being respectively the variance of
+predictive means and the variance of the residuals. $a_n$ and $a_{i|n}$ are
+respectively the standard deviation on the random intercept associated to the
+basin and the site.
+
+The temporal trends at each site have been extracted from the hierarchical model
+using mean BLUP values (Best Linear Unbiaised Predictor), then multiplied
+by 10 to get temporal trends by decade. For logged transformed biomass and
+species richness, we derived percentage change by decade by transforming the
+slopes ($\beta\prime = (e^{\beta } - 1) \times 100 \times 10$).
+
+## Spatial
+
+To assess the validity of the space-for-time substitution hypothesis, we
+compared the relationships among food-web structure in time to the ones observed
+in space. To do so, we selected the same sites that were used
+for the temporal analysis. We summarised temporal series of each station by the
+median value over time of each facet of food-web structure described above.
+
+# Statistical analysis
+
+We modelled the relationships among food-web structure, that is
+connectance and average trophic level, and community biomass ($dB$) and species
+richness ($dR$) with Structural Equation Models. We modelled a it such as species
+richness is related to community biomass and food-web structure. In
+turn community biomass was related to food-web structure. We computed one
+structural equation model to assess the relationships among the temporal trends
+and one for the relationships over the spatial gradient. As spatial variation of
+food-web structure are partly driven by environmental gradients, so we
+controlled relationships among variables by adding two PCA axis
+synthesizing respectively (1) stream gradient from upstream to downstream and
+(2) enrichment (Fig. \@ref(fig:matmet)). Enrichment was characterized by the
+average Biological Oxygen Demand [BOD, @mallin_factors_2006][^2]. We further
+added a random effect of the hydrographic basin on the intercept.
+
+In order to control for the uncertainties of the estimated temporal trends, each
+temporal trend was weighted by the inverse of the sum of the standard deviation 
+of the estimated trends, i.e. estimated slopes for the response and the
+explicative variables ($w_j = \dfrac{1}{\sum{e_j}}$, $w_j$ being the
+weight, and $s_{e_j}$ the standard deviation on the temporal trends of the
+variables).
+
+The coefficients of the Structural Equation Models were computed with
+PiecewiseSEM R package [@lefcheck_piecewisesem_2016]. The coefficients were
+standardizated and the confidence intervals were computed with semEff R package
+[@murphy_semEff_2021]. Confidence intervals were obtained by bootstrapping the
+linear models 1000 times and computing adjusted bootstrap percentile interval
+(BCa), which are adjusted for asymetric distribution of resampling. The marginal
+and conditional $R^2$ associated to the linear model of the SEMs were computed
+the Nagelkerke method [@lefcheck_piecewisesem_2016].
+
+All the statistical models displayed low multicollinearity (Variance inflation
+factor < 3, Table SXX).  We visually inspected the residuals of the linear
+models.
+
+```{r}
+fig_mat_cap <- paste0("Using sites of stream fishes in French streams that
+  have been monitored at least 10 years, 1) we infered the food-web at each site
+and each sampling event based on ontogenic food diet information for each
+species and predator-prey body size ratio. 2) We computed the temporal trends
+and the median of community biomass, species richness, connectance, average
+trophic level and evenness of biomass at each site. 3) We then assessed the
+relationships among food-web structure descriptors, (a) in time and (b) across space.")
+```
+
+```{r matmet, fig.cap=fig_mat_cap, out.width="80%"}
+knitr::include_graphics(get_mypath("figures", "mat_met.pdf"))
+```
+
 # References  {-}

### 2022-10-24 random_network.Rmd
Switched all figures and analysis to targets

--- 2022-07-25 random_network.Rmd
@@
 ```{r}
-get_fw_metrics <- function(x) {
-
-  ff_metaweb <- get_fish_fish_matrix(x)
-
-  if (ncol(ff_metaweb) == 0) {
-    ff_ind <- NA
-    ct_ff <- NA
-    tl_ff <- NA
-    avg_tl_ff <- NA
-    max_tl_ff <- NA
-  } else {
-    ff_ind <- NetIndices::GenInd(ff_metaweb)
-    ct_ff <- ff_ind["C"]
-    tl_ff <- NetIndices::TrophInd(ff_metaweb)$TL
-    avg_tl_ff <- mean(tl_ff)
-    max_tl_ff <- max(tl_ff)
-  }
-
-  ind <- NetIndices::GenInd(x)
-  ct <- ind["C"]
-  tl <- NetIndices::TrophInd(x)$TL
-  avg_tl <- mean(tl)
-  max_tl <- max(tl)
-
-  list(
-    ff_metaweb = ff_metaweb,
-    ind = ind,
-    ff_ind = ff_ind,
-    ct = ct,
-    ct_ff = ct_ff,
-    tl = tl,
-    tl_ff = tl_ff,
-    avg_tl = avg_tl,
-    avg_tl_ff = avg_tl_ff,
-    max_tl = max_tl,
-    max_tl_ff = max_tl_ff
-  )
-}
-
-get_fw_metrics2 <- function(x, keep_metaweb = TRUE) {
-
-  ff_metaweb <- get_fish_fish_matrix(x)
-
-  if (ncol(ff_metaweb) == 0) {
-    ff_ind <- NA
-    ct_ff <- NA
-    tl_ff <- NA
-    avg_tl_ff <- NA
-    max_tl_ff <- NA
-  } else {
-    ff_ind <- NA
-    ct_ff <- sum(ff_metaweb) / (ncol(ff_metaweb) - 1)^2
-    tl_ff <- NetIndices::TrophInd(ff_metaweb)$TL
-    avg_tl_ff <- mean(tl_ff)
-    max_tl_ff <- max(tl_ff)
-  }
-
-  if (ncol(x) == 0) {
-    ind <- NA
-    ct <- NA
-    tl <- NA
-    avg_tl <- NA
-    max_tl <- NA
-  } else {
-    ind <- NA
-    ct <- sum(x) / (ncol(x) - 1)^2
-    tl <- NetIndices::TrophInd(x)$TL
-    avg_tl <- mean(tl)
-    max_tl <- max(tl)
-  }
-
-  if (!keep_metaweb) {
-    ff_metaweb <- NA
-  }
-
-  list(
-    ff_metaweb = ff_metaweb,
-    ind = ind,
-    ff_ind = ff_ind,
-    ct = ct,
-    ct_ff = ct_ff,
-    tl = tl,
-    tl_ff = tl_ff,
-    avg_tl = avg_tl,
-    avg_tl_ff = avg_tl_ff,
-    max_tl = max_tl,
-    max_tl_ff = max_tl_ff
-  )
-
-}
-
-get_sim_net <- function(net = NULL, ext_seq = NULL, keep_metaweb = TRUE) {
-
-  node_extinction <- tibble(
-    node_rm_single = names(ext_seq),
-    node_tlvl = ext_seq,
-    node_rm_tot = map(seq_along(ext_seq),
-      ~ext_seq[1:.x]),
-    metaweb = furrr::future_map(
-      seq_along(ext_seq),
-      ~metaweb[
-        !rownames(net) %in% names(ext_seq)[1:.x],
-        !colnames(net) %in% names(ext_seq)[1:.x]
-        ]
-    )
-  )
-
-  meta_keep <- keep_metaweb
-  out <- node_extinction %>%
-    mutate(
-      metrics = furrr::future_map(
-        metaweb, ~try(get_fw_metrics2(.x, keep_metaweb = meta_keep))
-      )
-    )
-
-  if (!keep_metaweb) {
-    out$metaweb <- NULL
-  }
-
-  return(out)
-}
-
 ```
@@
 ```{r random-richness, eval = FALSE}
-sim_dec_tlvl_species <- vector(mode ="list", length = length(fish_species_tlvl)) 
-sim_inc_tlvl_species <- vector(mode = "list", length = length(fish_species_tlvl))
-inc_species_tlvl <- sort(fish_species_tlvl, decreasing = FALSE)
-
-for (i in seq_along(fish_species_tlvl)) {
-  decreasing_tlvl_metaweb <- metaweb[
-    !str_detect(
-      rownames(metaweb),
-      paste0(names(fish_species_tlvl)[1:i], collapse = "|")
-      ),
-    !str_detect(
-      colnames(metaweb),
-      paste0(names(fish_species_tlvl)[1:i], collapse = "|")
-      )
-    ]
-  sim_dec_tlvl_species[[i]] <- get_fw_metrics2(decreasing_tlvl_metaweb,
-    keep_metaweb = FALSE)
-
-  increasing_tlvl_metaweb <- metaweb[
-    !str_detect(
-      rownames(metaweb),
-      paste0(names(inc_species_tlvl)[1:i], collapse = "|")
-      ),
-    !str_detect(
-      colnames(metaweb),
-      paste0(names(inc_species_tlvl)[1:i], collapse = "|")
-      )
-    ]
-  sim_inc_tlvl_species[[i]] <- get_fw_metrics2(increasing_tlvl_metaweb,
-    keep_metaweb = FALSE)
-}
-dec_species_result <- tibble(
-  one_sp_rm = names(fish_species_tlvl),
-  species_removed = map(seq_along(fish_species_tlvl),
-    ~names(fish_species_tlvl)[1:.x]),
-  metrics = sim_dec_tlvl_species
-  )
-
-inc_species_result <- tibble(
-  one_sp_rm = names(inc_species_tlvl),
-  species_removed = map(seq_along(inc_species_tlvl),
-    ~names(inc_species_tlvl)[1:.x]),
-  metrics = sim_inc_tlvl_species
-  )
 save(file = mypath("data", "sim_dec_sp_tlvl.rda"), dec_species_result)
@@
 # random simulation
-nsim <- 10
-set.seed(123)
-
-sim_random_tlvl_species <- vector(mode = "list", length = length(fish_species_tlvl))
-sim_random_tlvl_species <- map(sim_random_tlvl_species, ~vector(mode = "list", length = nsim))
-sp_to_rm <- vector(mode = "list", length = length(fish_species_tlvl))
-sp_to_rm <- map(sp_to_rm, ~vector(mode = "list", length = nsim))
-
-for (i in seq_along(fish_species_tlvl)) {
-
-  for (j in seq_len(nsim)) {
-    sp_to_rm[[i]][[j]] <- sample(names(fish_species_tlvl), size = i, replace = FALSE)
-
-    tmp_metaweb <- metaweb[
-      !str_detect(
-        rownames(metaweb),
-        paste0(sp_to_rm[[i]][[j]], collapse = "|")
-        ),
-      !str_detect(
-        colnames(metaweb),
-        paste0(sp_to_rm[[i]][[j]], collapse = "|")
-      )
-      ]
-    sim_random_tlvl_species[[i]][[j]] <- get_fw_metrics2(
-      tmp_metaweb,
-    keep_metaweb = FALSE)
-  }
-}
-
-random_species_result <- tibble(
-  nsp_rm = seq_along(fish_species_tlvl),
-  species_removed = sp_to_rm,
-  metrics = sim_random_tlvl_species
-  )
 save(file = mypath("data", "sim_random_sp_tlvl.rda"), random_species_result)

### 2022-10-24 R/extinction_sim_utils.R

@@ -1,0 +1,144 @@
+get_fw_metrics <- function(x) {
+
+  ff_metaweb <- get_fish_fish_matrix(x)
+
+  if (ncol(ff_metaweb) == 0) {
+    l_in_ff <- NA
+    l_out_ff <- NA
+    ff_ind <- NA
+    ct_ff <- NA
+    tl_ff <- NA
+    avg_tl_ff <- NA
+    max_tl_ff <- NA
+  } else {
+    l_in_ff <- colSums(ff_metaweb)
+    l_out_ff <- rowSums(ff_metaweb)
+    ff_ind <- NetIndices::GenInd(ff_metaweb)
+    ct_ff <- ff_ind["C"]
+    tl_ff <- NetIndices::TrophInd(ff_metaweb)$TL
+    avg_tl_ff <- mean(tl_ff)
+    max_tl_ff <- max(tl_ff)
+  }
+
+  ind <- NetIndices::GenInd(x)
+  ct <- ind["C"]
+  tl <- NetIndices::TrophInd(x)$TL
+  avg_tl <- mean(tl)
+  max_tl <- max(tl)
+
+  list(
+    ff_metaweb = ff_metaweb,
+    ind = ind,
+    ff_ind = ff_ind,
+    l_in_ff = l_in_ff,
+    l_out_ff = l_out_ff,
+    ct = ct,
+    ct_ff = ct_ff,
+    tl = tl,
+    tl_ff = tl_ff,
+    avg_tl = avg_tl,
+    avg_tl_ff = avg_tl_ff,
+    max_tl = max_tl,
+    max_tl_ff = max_tl_ff
+  )
+}
+
+get_fw_metrics2 <- function(x, keep_metaweb = TRUE) {
+
+  ff_metaweb <- get_fish_fish_matrix(x)
+
+  if (ncol(ff_metaweb) == 0) {
+    l_in_ff <- NA
+    l_out_ff <- NA
+    ff_ind <- NA
+    ct_ff <- NA
+    tl_ff <- NA
+    avg_tl_ff <- NA
+    max_tl_ff <- NA
+  } else {
+    l_in_ff <- colSums(ff_metaweb)
+    l_out_ff <- rowSums(ff_metaweb)
+    ff_ind <- NA
+    ct_ff <- sum(ff_metaweb) / (ncol(ff_metaweb) - 1)^2
[…]

### 2022-10-24 R/get_data.R

@@ -34,6 +34,7 @@ get_community_analysis_data <- function (
   return(com_std)
 }
 
+
 #' Get network metrics
 #'
 #' @param dir path to the data

### 2022-10-24 R/plot_model.R

@@ -1,0 +1,34 @@
+plot_obs_fitted_inla <- function(
+  mod_inla = NULL,
+  dataset = NULL,
+  resp = NULL,
+  pred_nrows = NULL,
+  return_df = FALSE
+  ) {
+
+  fitted_values <- mod_inla$summary.fitted.values[["mean"]]
+
+  if (!is.null(pred_nrows)) {
+    row_selection <- length(fitted_values) - pred_nrows
+    fitted_values <-
+      fitted_values[1:row_selection]
+  }
+
+  obs_fit <- tibble(
+    response = resp,
+    station = dataset[["station"]],
+    year = dataset[["year"]],
+    fit = fitted_values,
+    obs = dataset[[resp]]
+  )
+
+  if (return_df) {
+    return(obs_fit)
+  }
+
+  obs_fit %>%
+    ggplot(aes(x = fit, y = obs)) +
+    geom_point(alpha = .5, size = 2) +
+    geom_abline(intercept = 0, slope = 1, color = "red") +
+    labs(x = "Fitted values", y = "Observed values")
+}

### 2022-10-24 make.R

@@ -7,9 +7,3 @@ library(targets)
 library(tarchetypes)
 
 tar_make()
-
-library(tidyverse)
-library(magrittr)
-tar_meta(fields = warnings) %>%
-  filter(!is.na(warnings))
-tar_make(names = sp_semeff_perc)

### 2022-10-31 paper/manuscript.Rmd
Update results

@@
 ```{r, results = FALSE}
-library(drake)
+library(targets)
 library(tidyverse)
@@
 @blowes_geography_2019], rising the recognition of the multidimensional nature
-of biodiversity changes[@hillebrand_biodiversity_2018; @blowes_local_no_date]
+of biodiversity changes[@hillebrand_biodiversity_2018; @blowes_local_nodate]
 and the need for further investigations on how biodiversity changes over time.
@@
 a large part community composition, species coexistence, and ecosystem
-functioning [@chesson_mechanisms_2000; @thebault_food-web_2003;
+functioning[@chesson_mechanisms_2000; @thebault_food-web_2003;
 @oconnor_general_2017]. The structure of ecological networks can trigger or
@@
 @dunne_network_2002; @srinivasan_response_2007;
-@stouffer_comparmentalization_2011]. Higher connectance, which measures the
+@stouffer_compartmentalization_2011]. Higher connectance, which measures the
 degree of generalism in a network, is predicted to increase robustness to
-secondary extinctions [@dunne_network_2002; @sole_complexity_2001] and studies
+secondary extinctions[@dunne_network_2002; @sole_complexity_2001] and studies
 found that higher trophic level was associated to a lower temporal variability
 of community biomass in theoretical models and empirical
-data[@shanafelt_stability_2018; @danet_species_nodate]. Then, accounting for how
+data[@shanafelt_stability_2018; @danet_species_2021]. Then, accounting for how
 the structure of ecological networks changes over time according to other
@@
 more rich foodwebs. Connectance has been shown to scale positively or negatively
-with community biomass in theoretical food-webs [@thebault_food-web_2003;
+with community biomass in theoretical food-webs[@thebault_food-web_2003;
 @poisot_trophic_2013] while the average trophic level was previously shown to
-scale negatively with species richness [@danet_species_2021].
+scale negatively with species richness[@danet_species_2021].
 
@@
 space and in time, i.e. that spatial sequences correspond to temporal sequences.
-This method have raised criticisms [@damgaard_critique_2019], with studies
-showing analogous patterns in space and time [@blois_space_2013] or not
+This method have raised criticisms[@damgaard_critique_2019], with studies
+showing analogous patterns in space and time[@blois_space_2013] or not
 [@johnson_testing_2008; @adler_contrasting_2007]. Spatial turnover of species
@@
 been hypothesised to be responsible for the non-compliance of space-for-time
-substitution [@adler_contrasting_2007; @blois_space_2013].
+substitution[@adler_contrasting_2007; @blois_space_2013].
 
 The increasing availability ecological temporal series and the development of
-methods to reconstruct food-webs [@bonnaffe_comparison_2021;
+methods to reconstruct food-webs[@bonnaffe_comparison_2021;
 @gravel_inferring_2013; @danet_species_2021] makes possible to overcome
@@
 ```{r}
-tar_load(r2_inla_tab)
+tar_load(c(r2_inla_tab, r2_inla, r2_sem))
 r2_inla_report <- r2_inla %>%
@@
 )
+```
 
-tar_load(r2_sem)
-```
 Using a hierarchical model to estimate conjointly the temporal trends of  
@@
 
-We found a strong positive relationship between the temporal trends of community
-biomass and the ones of species richness ($r_\delta = `r rdtps$bm$r`$,
-Fig. \@ref(fig:sem) b), meaning that both temporal trends
-had the same direction in average. At the sites 
-where species richness decreased over time, community biomass also decreased
-over time. On the other hand, at the sites where species richness increased over
-time, community biomass also increased over time. Along the spatial gradient, we also
-found a positive relationship between median community biomass and median
-species richness, but half the strength as the temporal one
-($r_\delta = `r rdsp$bm$r`$).
-
-The temporal trends of connectance were positively linked with the ones of
-community biomass ($r_\delta = `r rdtps$ct$bm`$), also meaning that both
-temporal trends had the same direction in average. That is, the sites where
-food-web connectance decreased over time also had community biomass that
-decreased over time and reversely. It suggests that communities that decreased
-in biomass over time loose generalist predators over time, as connectance
-measures the degree of generalism, and reversely that communities
-gaining biomass over time also gain generalist predators. Spatially, we also found
-a positive relationship between median connectance and median species
-richness ($r_\delta = `r rdsp$ct$bm`$). We found a negative 
-relationship between the temporal trends of connectance and the
-ones of species richness ($r_\delta = `r rdtps$ct$r`$, Fig. \@ref(fig:sem)d)
-while we found negative relationship three times stronger between median connectance and
-median species richness along the spatial gradient 
-($r_\delta = `r rdsp$ct$r`$, Fig. \@ref(fig:std)).
-
-The temporal trends of average trophic level had a strong positive
-relationship with the ones of community biomass 
-($r_\delta = `r rdtps$tlvl$bm`$, Fig. \@ref(fig:sem)B), meaning
-that sites where community biomass decreased over time, average trophic level
-decreased over time and *vice versa*. It means that in communities loosing biomass
-over time, the average biomass of the food-web moved down to lower trophic level
-and *vice versa*. We also found a positive relationship between
-median average trophic level and median community biomass in space, but half the
-strength as the temporal one ($r_\delta = `r rdsp$tlvl$bm`$, Fig.
-\@ref(fig:std)). The temporal trends of average trophic level was unrelated to
-the ones of species richness. It suggests that in communities either loosing or
-gaining species richness over time, the location of average biomass along
-trophic level did not significantly change according to species richnnes.
-However, we found a strong negative relationship in space 
-($r_\delta = `r rdsp$tlvl$r`$, Fig. \@ref(fig:std)).
-
 ```{r}
@@
 
-The structural model on the temporal trends of food-web structure reveals that
-the species richness has a direct negative effect on connectance but also a
-positive one through community biomass
-($r_\delta$ = `r ridtps$ct$r`). It resulted a relatively weak total negative
-effect of species richness on connectance (`r rttps$ct$r`). Spatially,
-we also found a positive indirect effect of richness on connectance through
-community biomass but a weak one (`r ridsp$ct$r`), resulting in a strong negative total
-effect of richness on connectance (`r rtsp$ct$r`).
+Using structural equation models to disentangle the direct and indirect
+relationships among foodweb structure descriptors, we found a strong positive
+relationship between the temporal trends of community biomass and of
+species richness ($r_\delta = `r rdtps$bm$r`$, Fig. \@ref(fig:sem) a and b,
+$r_\delta$: standardized slope coefficients, [95% CI]), meaning that both
+temporal trends had the same direction in average. At the sites where species
+richness decreased over time, community biomass also decreased over time. On the
+other hand, at the sites where species richness increased over time, community
+biomass also increased over time.
 
-The relationships among temporal trends showed a indirect positive effect of
-species richness on average trophic level (`r ridtps$tlvl$r`), resulting in a total positive
-effect of species richness on average trophic level (`r rttps$tlvl$r`). Over the spatial
-gradient, we found the same positive indirect effect of richness through
-community biomass (`r ridsp$tlvl$r`). WHATTTT? But as the direct effect of
-richness on average trophic level was strongly negative, it resulted in a total
-strong negative effect of species richness on average trophic level over the
-spatial gradient (`r rtsp$tlvl$r`).
+The temporal trends of connectance were positively linked with the ones of
+community biomass ($r_\delta = `r rdtps$ct$bm`$), also meaning that both
+temporal trends had the same direction in average. That is, the sites where
+food-web connectance decreased over time also had community biomass that
+decreased over time and reversely. It suggests that communities that decreased
+in biomass over time lose highly connected trophic species over time, and
+reversely that communities gaining biomass over time also gain highly connected
+trophic species over time. We found a negative relationship between the temporal
+trends of connectance and the ones of species richness
+($r_\delta = `r rdtps$ct$r`$, Fig. \@ref(fig:sem)d). We further found the
+species richness had an indirect positive effect on connectance, through
+community biomass ($r_\delta = `r ridtps$ct$r`$). It resulted in a relatively
+weak total negative effect of species richness on connectance
+($r_\delta = `r rttps$ct$r`$).
+
+The temporal trends of average trophic level had a strong positive relationship
+with the ones of community biomass ($r_\delta = `r rdtps$tlvl$bm`$, Fig.
+\@ref(fig:sem)e), meaning that sites where
+community biomass decreased over time, average trophic level decreased over time
+and reversely. It means that in communities losing biomass over time, the
+average biomass of the food-web moved down to lower trophic level and vice
+versa. However, we found that the temporal trends of average trophic level had
+no direct relationship the ones of species richness ($r_\delta = `r rdtps$tlvl$r`$,
+Fig. \@ref(fig:sem)f). It suggests that in communities either
+losing or gaining species richness over time, the location of average biomass
+along trophic level does not significantly change according to species richness.
+However, the temporal trends of species richness had an indirect positive
+relationship with the temporal trends of average trophic level through community
+biomass ($r_\delta = `r ridtps$tlvl$r`$), resulting in a total positive
+relationship ($r_\delta = `r rttps$tlvl$r`$).
 
@@
 
+As for the temporal analysis, we found a positive relationship between
+median community biomass and median species richness along the spatial gradient,
+but half the strength as the temporal one ($r_\delta = `r rdsp$bm$r`$, Fig.
+\@ref(fig:std)). We further found a positive relationship between median
+connectance and median community biomass ($r_\delta = `r rdsp$ct$bm`$), as in
+temporal trends analysis. However, we found a negative relationship between
+median connectance and median species richness, but
+three times stronger than in the temporal analysis ($r_\delta = `r rdsp$ct$r`$,
+Fig. \@ref(fig:std)). We also found a positive indirect effect of median
+richness on median connectance through median community biomass but a weak one
+($r_\delta = `r ridsp$ct$r`$), resulting in a strong negative total effect of
+median richness on median connectance ($r_\delta = `r rtsp$ct$r`$).
+
+We found a positive relationship between median average trophic level and median
+community biomass, but half the strength as in the temporal analysis ($r_\delta
+= `r rdsp$tlvl$bm`$, Fig. \@ref(fig:std)). However, we found a strong negative
+relationship between median average trophic level and median richness ($r_\delta
+= `r rdsp$tlvl$r`$), in contrast with findings in temporal analysis. We also
+found a positive indirect relationship between average trophic level and  median
+richness through median community biomass (`r ridsp$tlvl$r`), resulting in a
+strong total negative effect of median richness on median average trophic level
+(`r rtsp$tlvl$r`).
+
 # Discussion
@@
 average [@dornelas_assemblage_2014; @blowes_geography_2019] but an increase in
-total abundance [@klink_meta-analysis_2020].
+total abundance [@van_klink_meta-analysis_2020].
 
@@
 evidences that food-web containing generalist predators can rewire in response
-to changes in the availability of prey species [@bartley_food_2019]. *(J'ai
-regardé dans la biblio envoyé par Elisa et j'ai refais de la biblio moi-même, je
-n'ai rien qui s'approche de ce résultat).* This result also resonates with the
-energy paradigm of food-webs which proposes that food-webs are primarily
-constrained by fluxes of matter and energy [@lindeman_trophic-dynamic_1942], so
-community biomass and not by species richness.
+to changes in the availability of prey species [@bartley_food_2019]. This result
+also resonates with the energy paradigm of food-webs which proposes that
+food-webs are primarily constrained by fluxes of matter and energy
+[@lindeman_trophic-dynamic_1942], so community biomass and not by species
+richness.
 
-- Remove the following paragraph:
-
-As studies reported community biomass or species richness temporal trends
-[@hallmann_more_2017; @ceballos_biological_2017; @dornelas_assemblage_2014;
-@blowes_geography_2019], we document that temporal trends of species richness
-and community biomass might have different consequences on the structure of the
-community. In particular, the decrease of the average trophic level associated
-to the loss of community biomass could have cascading effect on ecosystem
-functioning as the highest predators are predicted to increase productivity and
-stabilise communities [@wang_biodiversity_2018; @shanafelt_stability_2018;
-@danet_species_nodate]. In contrasts, the loss of species richness might be
-linked to loss of redundancy in the food-web, highlighting that those
-communities may become more at risk regarding future perturbations
-[@yachi_biodiversity_1999]. Interestingly, the hypothesis that temporal trends
-in community biomass is related to higher trophic level in our system has a
-strong reasoning with the effect of human fisheries in marine systems which
-affect primarily fish species at top trophic level [@sprules_surfing_2016].
-Overall, our study highlights that monitoring several facets of biodiversity is
-essential to infer how ecological communities are reshaped by loss and gain of
-biomass and species richness.
+---
+# - Remove the following paragraph:  
+# As studies reported community biomass or species richness temporal trends
+# [@hallmann_more_2017; @ceballos_biological_2017; @dornelas_assemblage_2014;
+# @blowes_geography_2019], we document that temporal trends of species richness
+# and community biomass might have different consequences on the structure of the
+# community. In particular, the decrease of the average trophic level associated
+# to the loss of community biomass could have cascading effect on ecosystem
+# functioning as the highest predators are predicted to increase productivity and
+# stabilise communities [@wang_biodiversity_2018; @shanafelt_stability_2018;
+# @danet_species_nodate]. In contrasts, the loss of species richness might be
+# linked to loss of redundancy in the food-web, highlighting that those
+# communities may become more at risk regarding future perturbations
+# [@yachi_biodiversity_1999]. Interestingly, the hypothesis that temporal trends
+# in community biomass is related to higher trophic level in our system has a
+# strong reasoning with the effect of human fisheries in marine systems which
+# affect primarily fish species at top trophic level [@sprules_surfing_2016].
+# Overall, our study highlights that monitoring several facets of biodiversity is
+# essential to infer how ecological communities are reshaped by loss and gain of
+# biomass and species richness.
+---
 
@@
 reflect aggregated dynamics over longer time scale including a far number of
-processes including high species turnover along spatial gradient. Another reason
-might be that the spatial gradient displays a higher range of variation for
-species richness than the temporal stations (Fig. S2). However, we found
-temporal trends of species richness of -70%/-50% to +80%/+100% by decade.
-
-- Développer un point la-dessus?:
-
-Our study highlights that time series are an important tool to
-understand the assembly and disassembly of food-webs following changes in
-species richness and biomass. Our study also highlights the usefulness of
-structural equation model to highlight direct and indirect pathways.
-
----
-### Biomass and richness gains and losses are symmetric processes in terms of community structure
-#
-#We found no case in which gain or losses of biomass and richness lead to
-#different relationship between the temporal dynamic of community structure and
-#the one of biomass and species richness. We could have imagined that
-#extinction/colonisation processes or immigration/extinction debt could have lead
-to different relationships.
----
+processes including high species turnover along spatial gradient.
 

### 2022-11-05 paper/appendix.Rmd
Add abstract and significance statements

--- 2022-02-24 paper/appendix.Rmd
@@
 subtitle:
-author: Alain Danet, Maud Mouchet, Loubna El Madouri, Elisa Thébault and Colin Fontaine (ordre non fixé)
+author: Alain Danet, Loubna El Madouri, Maud Mouchet, Elisa Thébault and Colin Fontaine
 date: \today 
@@
 
-# Data exploration
-
 ```{r}
-loadd(p_st_mono_trends_stable_rich_bm, st_mono_trends_stable_rich_bm)
-
+tar_load(r2_inla_tab)
+kable(r2_inla_tab,
+  row.names = FALSE,
+  booktabs = T,
+  caption = "Marginal and Conditional R-squared for the INLA models estimating
+  the temporal trends of the food-web structure", label = "inlarsq",
+  ) %>%
+  kable_styling(latex_options = c("scale_down", "stripped"))
 ```
@@
 ```{r}
-range_cap <- paste0(
-  "Range of variation of variables in spatial (vertical lines) and temporal
-  dataset for the (A) minimum and maximum values and (B) the range (i.e. maximum
-    - minimum)."
+tps10_cap <- paste0("Distribution of temporal trends per decade of the food-web
+  structure by site estimated from the Bayesian models using Best Linear
+  Unbiaised Predictor (BLUP). Species richness and biomass temporal trends are
+  reported in percentage change per decade.")
+
+```
+```{r tps10, fig.cap=tps10_cap}
+knitr::include_graphics(here::here("figures", "p_hist_site_tps10.pdf"))
+```
+
+```{r}
+rand_sim_cap <- paste0(
+  "Simulations of (a) species and (b) nodes extinctions in the metaweb according
+  to three scenarios: random extinction sequence, decreasing trophic level,
+  increasing trophic level."
+
 )
 ```
-
-```{r range, fig.cap=range_cap, fig.height=10}
-loadd(p_range)
-plot_grid(plotlist = p_range, nrow = 2, labels = "AUTO")
+```{r ext, fig.cap=rand_sim_cap}
+knitr::include_graphics(here::here("figures", "tot_ext_sim.pdf"))
 ```
 
-\newpage
-
-## Correlation
-
 ```{r}
-cor_cap <- paste0("Correlation plot among variables.", "Median values over time were
-  used for spatial relationships. ", "For temporal model, we used the
-  temporal trends in each station. Futhermore, each station was weighted by the
-  average error standard on the temporal trends of the variables.",
-  " Pisc: piscivorous, Nb: number, node: node of the food-web corresponding to a
-  trophic species, prop: proportion."
+cor_cap <- paste0("Correlation among food-web metrics for a) temporal trends by site, b) median values by site (cf Main Methods)", " Pisc: piscivorous, rich.: species richness, node: node
+  of the food-web corresponding to a trophic species, prop.: proportion."
 )
@@
 ```{r cor, fig.cap=cor_cap}
-oldpar <- par()
-loadd(corr_plot_med, corr_plot_tps)
-
-rv <- var_replacement()
-rv_more <- c(
-  nbnode_std = "Nb node",
-  nb_pisc_rich_std = "Nb pisc species",
-  nb_pisc_node_std = "Nb pisc nodes",
-  prop_pisc_node = "Prop pisc node",
-  prop_pisc_rich = "Prop pisc species"
-)
-
-rv <- c(rv_more, rv[!names(rv) == "rich_std"])
-
-set_names_corr <- function(mat = NULL, replacement_vector = var_replacement()) {
-  colnames(mat) <- str_replace_all(colnames(mat), replacement_vector)
-  rownames(mat) <- str_replace_all(rownames(mat), replacement_vector)
-  return(mat)
-}
-
-corr_plot_tps %<>% set_names_corr(., replacement_vector = rv)
-corr_plot_med %<>% set_names_corr(., replacement_vector = rv)
-
-#par(mfrow = c(1, 2))
-corrplot::corrplot(
-  corr_plot_med,
-  type = "upper",
-  diag = FALSE,
-  order = "alphabet",
-  tl.srt = 30,
-  tl.cex = .7
-)
-title("Spatial", adj = 0, line = 3)
-corrplot::corrplot(corr_plot_tps, type = "upper", diag = FALSE, order =
-  "alphabet",
-  tl.srt = 30,
-  tl.cex = .7
-)
-title("Temporal trends", adj = 0, line = 3.2)
-```
-
-\newpage
-
-# Statistical analysis
-
-## Spatial model
-
-```{r}
-loadd(est_sp_models, colin_sp_models, sp_models)
+knitr::include_graphics(here::here("fig", "p_corr.png"))
 ```
@@
 ```{r}
-tmp <- map(colin_sp_models, enframe)
-t_colin_sp_models <- tibble(vif = tmp, mod = names(colin_sp_models)) %>%
-  unnest(vif) %>%
-  filter(name %in% c("log_rich_std", "log_bm_std", "ct_ff"), mod == "log_rich_std") %>% #same model for
-  #all, so the vif is the same
-  rename(Response = name, vif = value) %>%
-  select(-mod) %>%
-  mutate(vif = map(vif, enframe)) %>%
-  unnest(vif) %>%
-  mutate(
-    value = round(value, 3),
-    name = str_replace_all(name, var_replacement()),
-    Response = str_replace_all(
-      Response,
-      c("log_rich_std" = "Richness model", "log_bm_std" = "Biomass model",
-	"ct_ff" = "Food-web structure"))
-    ) %>%
-  spread(name, value)
+obs_fit_cap <- "Fitted versus observed values from the INLA models estimating
+the temporal trends of the food-web structure. The black line depicts the first
+bissector. Pearson's correlation coefficients are displayed."
+```
 
-# colinearity table
-kable(t_colin_sp_models,
+```{r, fig.cap=obs_fit_cap}
+knitr::include_graphics(here::here("figures", "p_obs_fit.pdf"))
+```
+
+```{r}
+tar_load(tabvif)
+kable(tabvif,
   row.names = FALSE,
   booktabs = T,
-  caption = "Variance Inflation Factor for the linear models in the spatial
-  models. NA values indicate that the term in column was not included in the
-  modeling of the response variable in row.",
-  label = "vif-sp",
+  caption = "Variance Inflation Factor for the more complex linear models
+  included in the Structural Equation Models.",
+  label = "vif",
   ) %>%
@@
 
-## Sensisivity analysis for the temporal model
-
 ```{r}
-loadd(
-  resume_bm_rich_mod_mono_trends,
-  model_bm_rich_no_covar_no_inc_mono_trends,
-  reg_table_bm_rich_mono_trends,
-  reg_table_bm_rich_mono_stable_trends,
-  reg_table_bm_rich_trends,
-  reg_table_bm_rich,
-  anova_table_bm_rich_mono_trends,
-  anova_table_bm_rich_mono_stable_trends,
-  anova_table_bm_rich_trends,
-  anova_table_bm_rich,
-  anova_bm_rich_mod
-)
-loadd(
-  st_trends_rich_bm,
-  st_mono_trends_rich_bm,
-  st_mono_trends_stable_rich_bm,
-  basin_station
-)
-loadd(
-  pred_bm_rich_mono_trends,
-  pred_bm_rich,
-  pred_bm_rich_trends,
-  pred_bm_rich_mono_stable_trends
-)
-```
-
-```{r}
-cap_sens_temp_model <- paste0("
-  Testing the robustness of the estimated coefficients to the selection of
-  sites. 'All trends' corresponds to all the sites, 'Only monotonuous trends'
-  corresponds to all the trends negative or positive monotonically, 'Monotonuous
-  + stable' includes the previous selection and the stable ones (the selection
-    used in main text), 'All significant trends' correspond to all the trends
-significantly negative or positive.", " We classified a site as
-  having a significant trend when it displays both significant trends in biomass
-and in species richness."
-)
-```
-```{r sens, out.width="100%", fig.cap=cap_sens_temp_model}
-# Merge reg_table
-merged_reg_table <- pmap_dfr(
-  list(
-    df = list(
-      reg_table_bm_rich_mono_trends,
-      reg_table_bm_rich_mono_stable_trends,
-      reg_table_bm_rich_trends,
-      reg_table_bm_rich
-      ),
-    name = list(
-      "Only monotonuous",
-      "Monotonuous + stable (used in main text)",
-      "All significant trends",
-      "All sites"
-      ),
-    st = list(
-      st_mono_trends_rich_bm,
-      st_mono_trends_stable_rich_bm,
-      st_trends_rich_bm,
-      seq(1,400)
-    )
-    ), function (df, name, st) {
-    df$selection <- paste0(name, " (N = ", length(st),")")
-    return(select(df, selection, everything()))
-  }
-)
-
-merged_reg_table %>%
-  filter(! term %in% "(Intercept)", ! response %in% "piel_nind") %>%
-  mutate(
-   response = str_replace_all(response, var_replacement()),
-   term = str_replace_all(term, var_replacement()),
+tar_load(r2_sem_tab)
+kable(r2_sem_tab,
+  row.names = FALSE,
+  booktabs = T,
+  caption = "Marginal and conditional R squared for the Structural Equation
+  Models.",
+  label = "r2sem",
   ) %>%
-  ggplot(aes(x = term, y = std_estimate)) +
-  geom_point(aes(color = selection)) +
-  facet_grid(cols = vars(response)) +
-  labs(
-    x = "Explicative variable",
-    y = "Standardized coefficients"
-  ) +
-  theme(
-    legend.position = "bottom",
-    axis.text.x = element_text(hjust = 1, angle = 15, size = 8),
-    text = element_text(size = 8)) +
-  guides(color = guide_legend(nrow = 2, byrow = TRUE))
-```
-
-We found that selection of data can have either low or high effects on estimated
-effects. When selecting only the sites that display significant decrease or
-increase of community biomass and species richness across time, i.e. 
-a tenth of the site, we found stronger links among the temporal dynamics of
-average trophic level, connectance, biomass and the temporal dynamics of biomass
-and species richness (Fig. \@ref(fig:sens), purple and red points). On the other
-side, we found that the data selection that we used in the main analysis
-displays roughly the same results that the selection that includes all sites
-(Fig. \@ref(fig:sens), blue and green points).
-
-The fact that we observed differences with data selection is that  "Only
-monotonuous" and "All significant trends" do not contain temporal dynamics
-around 0 because they are often non significant. We think that this data
-selection is not satisfactory because we wanted to include the temporal dynamics
-of biomass of species richness that were not significant, i.e. that can be
-considered as stable. The rational is that we wanted to know what was the
-expected temporal trends of food-web structure while the ones of biomass and
-species richness are kept stable. Without those data, the regression becomes
-constrained only by the extreme temporal trends of species richness and
-community biomass.
-
-\newpage
-
-## Interaction between community biomass trends and species richness trends
-
-```{r}
-loadd(model_bm_rich_int_mono_stable_trends)
-```
-
-```{r}
-model_bm_rich_int_mono_stable_trends %>%
-  .[names(.) %in% c("ct_ff", "w_trph_lvl_avg", "piel_bm")] %>%
-  map(., car::Anova) %>%
-  map(., tidy) %>%
-  map2_dfr(., names(.), ~.x %>% mutate(response = .y) %>% select(response,
-      everything())) %>%
-  mutate(
-    response = str_replace_all(response, var_replacement()),
-    term = str_replace_all(term, var_replacement())
-  ) %>%
-  rename_all(~str_to_title(.)) %>%
-  kable(., booktabs = TRUE,
-  row.names = FALSE,
-  caption =
-    paste0(
-      "ANOVA results with interactions."
-      ),
-    label = "aov-int"
-    ) %>%
-kable_styling(latex_options =c("scale_down", "stripped")) %>%
-collapse_rows(columns = 1, valign = "top")
-#map(model_bm_rich_int_mono_stable_trends, ~try(car::vif(.x)))
-```
-
-```{r}
-model_bm_rich_int_mono_stable_trends %>%
-  .[names(.) %in% c("ct_ff", "w_trph_lvl_avg", "piel_bm")] %>%
-  map(., tidy) %>%
-  map2_dfr(., names(.), ~.x %>% mutate(response = .y) %>% select(response,
-      everything())) %>%
-  mutate(
-    response = str_replace_all(response, var_replacement()),
-    term = str_replace_all(term, var_replacement())
-  ) %>%
-  rename_all(~str_to_title(.)) %>%
-  kable(., booktabs = TRUE,
-  row.names = FALSE,
-  caption =
-    paste0(
-      "Regression results of the model with interactions between the temporal
-      dynamics of community biomass and the one of species richness."
-      ),
-    label = "reg-int"
-    ) %>%
-kable_styling(latex_options =c("scale_down", "stripped")) %>%
+  kable_styling(latex_options = c("scale_down", "stripped")) %>%
   collapse_rows(columns = 1, valign = "top")
 ```
-
-```{r, results="hide", echo=FALSE}
-pred_int_rich <- map(model_bm_rich_int_mono_stable_trends,
-      ~ggpredict(.x,
-        terms = c("log_rich_std", "log_bm_std [quart2]")) %>%
-        as_tibble() %>%
-        mutate(group = as.numeric(as.character(group))) %>%
-        rename("log_rich_std" = x, "log_bm_std" = group)
-        ) %>%
-enframe(name = "response", value = "pred_int")
-
-ti <- pred_bm_rich_mono_stable_trends %>%
-  filter(
-    term == "log_rich_std",
-    response %in% c("ct_ff", "w_trph_lvl_avg", "piel_bm")
-    ) %>%
-  select(response, raw_plot) %>%
-  left_join(pred_int_rich) %>%
-  mutate(pred_plot_color = pmap(
-      list(raw_plot, response, pred_int),
-      function(p, resp, pred, ...) {
-        p +
-          geom_line(data = pred,
-            aes(
-              y = predicted,
-              x = log_rich_std,
-              color = as.factor(log_bm_std)
-            ), size = 1
-          ) +
-        scale_color_discrete() +
-        labs(x = "Log species richness",
-          y = var_replacement()[resp],
-          color = "Log community biomass"
-          ) +
-        theme(
-          text = element_text(size = 8),
-          axis.text = element_text(size = 8)
-        )
-      }
-        )
-  )
-rich_leg <- get_legend(ti$pred_plot_color[[1]])
-```
-
-```{r}
-int_rich_cap <- paste0(
-  "Relationships between the temporal dynamics of food-web
-  structure and the one of species richness. The interaction between
-  the temporal dynamic of species richness and community biomass is significant
-  for the three descriptors of food-web structure. The chosen values for the
-  community biomass temporal dynamic correspond respectively to the first,
-  second and third quartiles.
-  ")
-
-```
-
-```{r int-rich, fig.cap=int_rich_cap}
-plot_grid(plotlist = 
-  map(ti$pred_plot_color,
-    ~.x + theme(
-      legend.position = "none",
-    )
-    ),
-rich_leg)
-```
-
-```{r eval = FALSE}
-test <- pred_int_rich[3, ]$pred_int[[1]] %>%
-  select(predicted, log_rich_std, log_bm_std) %>%
-  arrange(log_rich_std, log_bm_std)
-
-mat <- reshape2::acast(test, log_rich_std~log_bm_std, value.var = "predicted")
-library(plotly)
-plot_ly(
-  x = ~as.numeric(colnames(mat)),
-  y = ~as.numeric(rownames(mat)),
-  z = ~mat) %>%
-  add_surface()
-```
-
-```{r, results="hide", echo=FALSE}
-pred_int_bm <- map(model_bm_rich_int_mono_stable_trends,
-      ~ggpredict(.x,
-        terms = c("log_bm_std", "log_rich_std [quart2]")) %>%
-        as_tibble() %>%
-        mutate(group = as.numeric(as.character(group))) %>%
-        rename("log_bm_std" = x, "log_rich_std" = group)
-        ) %>%
-enframe(name = "response", value = "pred_int")
-
-ti_bm <- pred_bm_rich_mono_stable_trends %>%
-  filter(term == "log_bm_std", response %in% c("ct_ff", "w_trph_lvl_avg", "piel_bm")) %>%
-  select(response, raw_plot) %>%
-  left_join(pred_int_bm) %>%
-  mutate(pred_plot_color = pmap(
-      list(raw_plot, response, pred_int),
-      function(p, resp, pred) {
-        p +
-          geom_line(data = pred,
-            aes(
-              y = predicted,
-              x = log_bm_std,
-              color = as.factor(log_rich_std)
-            ), size = 1
-          ) +
-        scale_color_discrete() +
-                labs(x = "Log species richness",
-          y = var_replacement()[resp],
-          color = "Log community biomass"
-          ) +
-        theme(
-          text = element_text(size = 8),
-          axis.text = element_text(size = 8)
-        )
-
-      }
-      )
-  )
-bm_leg <- get_legend(ti_bm$pred_plot_color[[1]])
-```
-
-```{r}
-int_bm_cap <- paste0(
-  "Relationships between the temporal dynamics of food-web
-  structure and the one of community biomass. The interaction between
-  the temporal dynamics of species richness and community biomass is significant
-  for the three descriptors of food-web structure. The chosen values for the
-  species richness temporal dynamic correspond respectively to the first,
-  second and third quartiles.
-  "
-)
-```
-
-```{r int-bm, fig.cap=int_bm_cap}
-plot_grid(plotlist = map(ti_bm$pred_plot_color, ~.x + theme(legend.position = "none")), bm_leg)
-```
-
-```{r, echo=FALSE, results="hide"}
-test <- model_bm_rich_int_mono_stable_trends[["ct_ff"]]
-car::Anova(test)
-co <- coef(test)
-pred <- ggpredict(
-  test,
-  terms = c("log_bm_std ", "log_rich_std")
-  ) %>%
-  as_tibble() %>%
-  mutate(group = as.numeric(as.character(group))) %>%
-  rename("log_bm_std" = x, "log_rich_std" = group)
-
-pred$y <- co[1] +
- # co["log_rich_std"] * pred[["log_rich_std"]] + bc not significant
-  co["log_bm_std"] * pred[["log_bm_std"]] +
-  co["log_rich_std:log_bm_std"] * pred[["log_rich_std"]] * pred[["log_bm_std"]]
-
-# all.equal(pred$y, pred$predicted)
-
-mat <- reshape2::acast(pred, log_rich_std~log_bm_std, value.var = "y")
-library(plotly)
-p <- plot_ly(
-  x = ~as.numeric(colnames(mat)),
-  y = ~as.numeric(rownames(mat)),
-  z = ~mat, ) %>%
-  add_surface() %>%
-  layout(scene = list(
-      xaxis = list(title = "species richness"),
-      yaxis = list(title = "Community biomass"),
-      zaxis = list(title = "Connectance")
-      ))
-```
-
-```{r, results=FALSE}
-mod4_3d <- model_bm_rich_int_mono_stable_trends[
-  names(model_bm_rich_int_mono_stable_trends) %in%
-    c("ct_ff", "w_trph_lvl_avg")]
-
-pred_list <- map(mod4_3d,
-  function (modl, p) {
-    co <- coef(modl)
-    p$y <- co[1] +
-#      co["log_rich_std"] * p[["log_rich_std"]] +
-      co["log_bm_std"] * p[["log_bm_std"]] +
-      co["log_rich_std:log_bm_std"] * p[["log_rich_std"]] * p[["log_bm_std"]]
-    return(p)
-
-  }, p = pred)
-```
-
-```{r,results=FALSE}
-mat <- reshape2::acast(
-  pred_list$w_trph_lvl_avg,
-  log_rich_std~log_bm_std,
-  value.var = "y")
-p <- plot_ly(
-  x = ~as.numeric(colnames(mat)),
-  y = ~as.numeric(rownames(mat)),
-  z = ~mat, ) %>%
-  add_surface() %>%
-  layout(scene = list(
-      xaxis = list(title = "Community biomass"),
-      yaxis = list(title = "species richness"),
-      zaxis = list(title = "Avg trophic level")
-      ))
-```
-
-```{r,results=FALSE, eval=FALSE}
-test <- model_bm_rich_int_mono_stable_trends[["piel_bm"]]
-car::Anova(test)
-co <- coef(test)
-pred <- ggpredict(
-  test,
-  terms = c("log_bm_std ", "log_rich_std")
-  ) %>%
-  as_tibble() %>%
-  mutate(group = as.numeric(as.character(group))) %>%
-  rename("log_bm_std" = x, "log_rich_std" = group)
-
-pred$y <- co[1] +
-  co["log_rich_std"] * pred[["log_rich_std"]] +
-  co["log_bm_std"] * pred[["log_bm_std"]] +
-  co["log_rich_std:log_bm_std"] * pred[["log_rich_std"]] * pred[["log_bm_std"]]
-
-# all.equal(pred$y, pred$predicted)
-
-mat <- reshape2::acast(pred, log_rich_std~log_bm_std, value.var = "y")
-p <- plot_ly(
-  x = ~as.numeric(colnames(mat)),
-  y = ~as.numeric(rownames(mat)),
-  z = ~mat, ) %>%
-  add_surface() %>%
-  layout(scene = list(
-      xaxis = list(title = "species richness"),
-      yaxis = list(title = "Community biomass"),
-      zaxis = list(title = "Eveness of biomass")
-      ))
-```
-
-```{r}
-int_3d_cap <- paste0(
-  "Tri-dimentional plot displaying the relationships among food-web structure
-  from one side and the temporal dynamics of species richness and community
-  biomass from the other side. The surface represents the values predicted by
-  the model."
-)
-```
-
-```{r int-3d, fig.cap=int_3d_cap}
-p_ct_ff <- ggdraw() +
-    draw_image(get_mypath("figures", "int_rich_bm_cf_ff.png"), scale = 1)
-p_tlvl <- ggdraw() +
-    draw_image(get_mypath("figures", "int_rich_bm_tlvl.png"), scale = 1)
-p_piel_bm <- ggdraw() +
-    draw_image(get_mypath("figures", "int_rich_bm_eveness.png"), scale = 1)
-plot_grid(
-  p_ct_ff,
-  p_tlvl,
-  p_piel_bm,
-  labels = "AUTO"
-)
-```
-
-All together, we found that interactions between the temporal dynamics of
-community biomass and species richness have no major effects on the bivariate
-relationships (Fig. \@ref(fig:int-bm) and \@ref(fig:int-rich)), at least in
-the range of values observed in the dataset (1st to 3rd quartiles).  It is more
-complicated for connectance when exploring the full range of possible values
-(Fig. \@ref(fig:int-3d) A). We found that connectance strongly decrease with
-increasing of community biomass temporal trends when species richness temporal
-trends is strongly negative, while we found the opposite when species richness temporal
-trends is strongly positive. Furthermore we found that the temporal dynamic of
-connectance had a strong positive relationship with the one of species richness
-when community biomass increases through time while we found no relationship
-when the temporal trend of community biomass was strongly negative.
-
-- Results for interactions: 
-  - Connectance: 
-    - Always decreases when richness decreases (inverse of expectation)
-    - Increases when richness increases (inverse of expectation), but always
-      decreases if biomass decreases
-    - Increases when biomass increases
-  - Average trophic level:
-    - Always decreases when biomass decreases 
-    - Always increases when biomass increases 
-    - Whatever the richness dynamics, it is the biomass dynamics which drives
-      all
-  - Pielou of biomass:
-    - Always positive when biomass decreases
-    - Always negative when biomass increases 
-    - Whatever the richness dynamics, it is the biomass dynamics which drives
-      all
-
-```{r}
-template_cross <- tibble(
-  bm_std = c("-", "0", "+"),
-  `-` = c(NA, NA, NA),
-  `0` = c(NA, NA, NA),
-  `+` = c(NA, NA, NA),
-  )
-
-ct_ff_cross_table <- tibble(
-  rich_std = c("-", "0", "+", "sign_relationship"),
-  `-` = c("-", "-", "--", "-"),
-  `0` = c("-", "-", "-", "0"),
-  `+` = c("-", "+", "++", "+"),
-  "sign_relationship" = c("0", "+", "+", "")
-  )
-
-kable(ct_ff_cross_table) %>%
-  add_header_above(c(" " = 1, "bm_std" = 3))
-```
-
-```{r}
-tlvl_cross_table <- tibble(
-  rich_std = c("-", "0", "+", "sign_relationship"),
-  `-` = c("-", "0", "+", "+"),
-  `0` = c("-", "0", "+", "+"),
-  `+` = c("-", "0", "+", "+"),
-  "sign_relationship" = c("+", "0", "-", "")
-  )
-
-kable(tlvl_cross_table) %>%
-  add_header_above(c(" " = 1, "bm_std" = 3))
-```
-
-\newpage
-
-## Statistical model tables
-
-### Temporal
-
-```{r}
-loadd(
-  pred_bm_rich_mono_stable_trends,
-  model_bm_rich_int_mono_stable_trends,
-  model_bm_rich_int_mono_stable_trends,
-  rsq_table_bm_rich_mono_stable_trends
-)
-```
-
-```{r}
-reg_table_bm_rich_mono_stable_trends %>%
-  mutate(
-    response = str_replace_all(response, var_replacement()),
-    term = str_replace_all(term, var_replacement())
-    ) %>%
-kable(., booktabs = TRUE,
-  row.names = FALSE,
-  caption =
-    paste0(
-      "Regression coefficients for the linear models explaining the links
-      between the temporal trends of community biomass and the temporal trends
-      of the network structure."),
-      label = "reg"
-      ) %>%
-  kable_styling(latex_options = c("scale_down", "striped")) %>%
-  collapse_rows(columns = 1, valign = "top")
-```
-
-```{r}
-table_rsq_tps <- rsq_table_bm_rich_mono_stable_trends %>%
-  mutate(
-    Response = str_replace_all(Response, var_replacement())
-  )
-table_rsq_tps %>%
-  kable(., booktabs = TRUE,
-    caption =
-      paste0(
-      "Marginal and conditional squared R for temporal models."),
-  label = "rsq"
-      ) %>% #
-  kable_styling(latex_options = c("striped")) %>%
-  collapse_rows(columns = 1, valign = "top")
-```
-
-### Spatial
-
-```{r}
-loadd(
-  sp_anova_table_bm_rich_mono_stable_trends,
-  sp_rsq_table_bm_rich_mono_stable_trends
-)
-```
-
-```{r}
-sp_anova_table_bm_rich_mono_stable_trends %>%
-  mutate(
-    response = str_replace_all(response, var_replacement()),
-    term = str_replace_all(term, var_replacement()),
-  ) %>%
-  kable(.,
-    booktabs = TRUE,
-    row.names = FALSE,
-    caption =
-      paste0(
-      "ANOVA results for the links among the spatial variation of community
-      biomass and species richness and the one of network structure."),
-  label = "aov-sp"
-  ) %>%
-  kable_styling(latex_options = c("scale_down", "striped")) %>%
-  collapse_rows(columns = 1, valign = "top")
-```
-
-```{r}
-sp_rsq_table_bm_rich_mono_stable_trends %>%
-  mutate(
-    Response = str_replace_all(Response, var_replacement())
-  ) %>%
-  kable(., booktabs = TRUE,
-    caption =
-      paste0("Marginal and conditional $R^2$ for the spatial models."),
-  label = "rsq-sp"
-      ) %>% #
-  kable_styling(latex_options = c("striped")) %>%
-  collapse_rows(columns = 1, valign = "top")
-```

### 2022-11-05 paper/manuscript.Rmd
Add abstract and significance statements

@@
 output:
-  bookdown::word_document2:
-    fontsize: 12pt
+#  bookdown::word_document2:
+#    fontsize: 12pt
   bookdown::pdf_document2:
@@
 mypath <- rprojroot::find_package_root_file
-source(mypath("R/variable_shortcut.R")) # Define your custom code as a bunch of functions.
+source(mypath("R/variable_shortcut.R"))
 source(mypath("R/misc.R"))
@@
 nb_st <- unique(full_data2$station) %>% length
+nb_op <- nrow(full_data2) %>% round(., -3)
+
 rm(full_data2)
@@
 
-# Abstract (250 words max)
+# Abstract (267 / 250 words max)
 
-# Signifiance (120 words)
+Understanding how biodiversity changes is a central question in ecology, but
+still challenging because of the multidimensionality of biodiversity changes.
+Although the structure of ecological networks is a crucial determinant of
+community dynamics, this dimension of biodiversity changes have been greatly
+overlooked. One main reason is the scarce availability of the temporal series of
+ecological networks. Our knowledge of the relationships among structural
+properties of ecological networks comes mainly from spatial comparison, assuming
+a space-for-time equivalence. However, little is know about the validity of the
+space-for-time hypothesis, i.e. if spatial comparison of ecological networks
+accurately translates temporal sequences of assemblages. Here we questioned the
+relationships between the temporal trends of food-web structure and the ones
+of community biomass and species richness, and we assessed how those
+relationships differed from the ones estimated in space. We inferred the
+structure of using food diet and individual body size data from fish monitoring
+in France. We estimated the temporal trends of food-web structure in 400 sites
+using a hierarchical Bayesian model and then assess the relationships among them
+using structural equation models. We found that temporal trends of connectance
+and average trophic level are positively related to ones of community biomass
+but surprisingly poorly related to the temporal trends of species richness. We
+further found support for space-for-time hypothesis for community biomass, but
+not for species richness. We suggest that our results resonates with the
+energetic paradigm of food-webs. Our study sheds a new light on the dynamics of
+food-web assemblage in natural settings and how the structure of ecological
+networks changes according to the changes of other biodiversity facets.
 
-# Introduction (564 words)
+# Significance (109 / 120 words max)
 
-Global diversity is reported to decline at alarming rates [@]. At local scale,
-recent meta-analysis reported a huge variation in species richness temporal
-trends across various taxa and ecosystem types[@vellend_global_2013;
-@dornelas_assemblage_2014; @blowes_geography_2019], with no net variations in
-species richness[@dornelas_assemblage_2014; @blowes_geography_2019].
-Futhermore, recent studies founs that temporal changes in species richness are
-unrelated to changes in species composition[@dornelas_assemblage_2014;
-@blowes_geography_2019], rising the recognition of the multidimensional nature
-of biodiversity changes[@hillebrand_biodiversity_2018; @blowes_local_nodate]
-and the need for further investigations on how biodiversity changes over time.
+While the multidimensional nature of biodiversity changes has been clearly
+emphasized, little is know how the structure of food-web changes according to
+changes in species richness and community biomass. By inferring food-web
+structure based on food-diet data and body size ratios, we analyzed how food-web
+structure in time according to simultaneously changes in species richness and
+community biomass. We identify that community biomass is the primary driver of
+temporal changes in foodweb structure, but that species richness has surprisingly
+low effect. We further show that space-for-time leads to contrasting results for
+species richness. Our results shed a new light on how foodweb assemble
+and disassemble in natural settings.
 
-Species interactions among species, described as ecological networks, drive for
-a large part community composition, species coexistence, and ecosystem
+# Introduction (487 words)
+
+There is rising recognition that biodiversity changes are
+multidimensional[@mcgill_fifteen_2015; @blowes_geography_2019;
+@hillebrand_biodiversity_2018; @blowes_local_nodate]. Studies found important
+changes in species composition despite no changes in species richness in average
+[@dornelas_assemblage_2014; @blowes_geography_2019], and highlighting the need
+for further investigations on how biodiversity changes over time.
+
+Yet species interactions are largely absent from biodiversity changes. Although
+species interactions, described as ecological networks, drive for a large part
+community composition, species coexistence, and ecosystem
 functioning[@chesson_mechanisms_2000; @thebault_food-web_2003;
@@
 
-Th availability of ecological networks timeseries is
-scarce[@kortsch_disentangling_2021], such as predictions about how the strucure
+Th availability of ecological network timeseries is
+scarce[@kortsch_disentangling_2021], such as predictions about how the structure
 of ecological networks change according to changes in species richness come from
-spatial comparison. Spatially, connectance has been shown to be negatively
-related to species richness in small (i.e. below 20 species) empirical food-webs
-[reviewed in @dunne_network_2006], which reflects constraints on the number of
-realizable species interactions or an increasing proportion of specialists in
-more rich foodwebs. Connectance has been shown to scale positively or negatively
-with community biomass in theoretical food-webs[@thebault_food-web_2003;
-@poisot_trophic_2013] while the average trophic level was previously shown to
-scale negatively with species richness[@danet_species_2021].
+spatial comparison of networks. Such studies showed that connectance is
+negatively related to species richness in small (i.e. below 20 species)
+empirical food-webs [reviewed in @dunne_network_2006], which reflects
+constraints on the number of realizable species interactions or an increasing
+proportion of specialists in more rich foodwebs. Connectance has been shown to
+scale positively or negatively with community biomass in theoretical
+food-webs[@thebault_food-web_2003; @poisot_trophic_2013] while the average
+trophic level was previously shown to scale negatively with species
+richness[@danet_species_2021].
 
@@
 methods to reconstruct food-webs[@bonnaffe_comparison_2021;
-@gravel_inferring_2013; @danet_species_2021] makes possible to overcome
-those research gaps. We used a standardized monitoring of fish riverine 
-communities on the period 1995-2018 over France, documenting the individual size
-of fishes in 400 sites during ten years or more. We restructed around 4000
+@gravel_inferring_2013; @danet_species_2021] makes possible to overcome those
+research gaps. We used a standardized monitoring of fish riverine communities on
+the period 1995-2018 over France, documenting the individual size of fishes in
+`r nb_st` sites during ten years or more. We reconstructed around `r nb_op`
 food-webs based on allometric relationships and food diet data, and then
 computed connectance, and average trophic level as well as community biomass and
-species richness.
-
-Our primary objective was to assess how the local structure of foodwebs changes
-over time according to simultaneous changes in community biomass and species
-richness over time. Our second objective was to assess if the relationships
-between changes in food-web structure, community biomass and species richness,
-are the same over space and over time, i.e. is the space-for-time substitution
-valid?  To do so, we first assessed the temporal trends in food-web structure.
-We then built structural equation model to assess the relationships among the
-temporal trends of the different facets of food-web structure.
+species richness. We assessed how the local structure of food-webs changes over
+time according to simultaneous changes in community biomass and species richness
+over time and then if the relationships between changes in food-web structure,
+community biomass and species richness, are the same over space and over time,
+i.e. is the space-for-time substitution valid?
 
@@
 Using a hierarchical model to estimate conjointly the temporal trends of  
-foodweb strucure at each site, we found weak evidence of a global decrease in
+foodweb structure at all sites, we found weak evidence of a global decrease in
 community biomass (CI80%:`r gbm` by decade; median [Credible Interval]) but of a
@@
 conditional $R^2$ going from  `r r2ic$log_bm_std` (mean [CI95%]) for community
-biomass to `r r2ic$log_rich_std` for species richness (Table SXX).
+biomass to `r r2ic$log_rich_std` for species richness (Table S1).
 
@@
 sem_cap <- "(a) Structural equation models linking the temporal trends of the food-web
-structure. The path widths are proportional to the standardized slope coefficients. The standardized slope coefficients and their associated 95%
-  confidence intervals are displayed along the path. (b to f) Direct bivariate
-relationships derived from the structural equation model. The distribution of the
-site temporal trends are displayed in Fig. SXX."
+structure. The path widths are proportional to the standardized slope
+coefficients. The standardized slope coefficients and their associated 95%
+confidence intervals are displayed along the path. The marginal R-squared of the
+linear models are displayed. (b to f) Direct bivariate relationships derived
+from the structural equation model. The distribution of the site temporal trends
+are displayed in Fig. S1."
 ```
@@
 weak total negative effect of species richness on connectance
-($r_\delta = `r rttps$ct$r`$).
+($r_\delta = `r rttps$ct$r`$), that we also found in random extinction
+simulation (Fig. S2).
 
@@
 with the ones of community biomass ($r_\delta = `r rdtps$tlvl$bm`$, Fig.
-\@ref(fig:sem)e), meaning that sites where
-community biomass decreased over time, average trophic level decreased over time
-and reversely. It means that in communities losing biomass over time, the
-average biomass of the food-web moved down to lower trophic level and vice
-versa. However, we found that the temporal trends of average trophic level had
-no direct relationship the ones of species richness ($r_\delta = `r rdtps$tlvl$r`$,
-Fig. \@ref(fig:sem)f). It suggests that in communities either
-losing or gaining species richness over time, the location of average biomass
-along trophic level does not significantly change according to species richness.
-However, the temporal trends of species richness had an indirect positive
-relationship with the temporal trends of average trophic level through community
-biomass ($r_\delta = `r ridtps$tlvl$r`$), resulting in a total positive
-relationship ($r_\delta = `r rttps$tlvl$r`$).
+\@ref(fig:sem)e), meaning that sites where community biomass decreased over
+time, average trophic level decreased over time and reversely. It means that in
+communities losing biomass over time, the average biomass of the food-web moved
+down to lower trophic level and vice versa. However, we found that the temporal
+trends of average trophic level had no direct relationship the ones of species
+richness ($r_\delta = `r rdtps$tlvl$r`$, Fig. \@ref(fig:sem)f). It suggests that
+in communities either losing or gaining species richness over time, the location
+of average biomass along trophic level does not significantly change according
+to species richness. However, the temporal trends of species richness had an
+indirect positive relationship with the temporal trends of average trophic level
+through community biomass ($r_\delta = `r ridtps$tlvl$r`$), resulting in a total
+positive relationship ($r_\delta = `r rttps$tlvl$r`$).
 
@@
 
-Most temporal trends of for species richness and community biomasss were
-classified as stable. Roughly the same number of stations displayed temporal
-decrease and increase for species richness, and twice more stations displayed
-decrease in community biomass than increase. This result is in accordance with
-previous meta analysis on species richness trends of vertebrate in marine,
-freshwater and terrestrial systems, which show no change in species richness in
-average [@dornelas_assemblage_2014; @blowes_geography_2019] but an increase in
-total abundance [@van_klink_meta-analysis_2020].
-
-## Species richness and community biomass are positively linked in space and time
-
-Spatially and temporally, species richness scaled positively with community
-biomass. Spatially, this result is in accordance with previous studies in stream
-communities [@woods_testing_2020; @danet_species_nodate] but also in grasslands,
-salt marches and forests [@hector_plant_1999; @tilman_biodiversity_2014;
-@wu_relationship_2015; @li_relationship_2018; but see @grace_integrative_2016].
-Therefore, our results confirm that Biodiversity-Ecosystem functioning
-prediction also hold in the temporal dynamics of food-webs. The positive
-relationship between species richness and total biomass might be due to positive
-complementarity in resource use [@carey_determining_2011], which is held by
-niche differentiation [@loreau_biodiversity_1998; @loreau_partitioning_2001] or
-to the higher probability of getting high biomass species with higher species
+We found that species richness scaled positively with community biomass, both in
+spatial and temporal analysis. This result is in accordance with previous
+analysis across space in stream communities [@woods_testing_2020;
+@danet_species_2021] but also in grasslands, salt marches and forests
+[@hector_plant_1999; @tilman_biodiversity_2014; @wu_relationship_2015;
+@li_relationship_2018; but see @grace_integrative_2016]. Therefore, our results
+suggest that Biodiversity-Ecosystem functioning prediction also hold in the
+temporal dynamics of food-webs. The positive relationship between species
+richness and total biomass might be due to positive complementarity in resource
+use [@carey_determining_2011], which is held by niche differentiation
+[@loreau_biodiversity_1998; @loreau_partitioning_2001] or to the higher
+probability of getting high biomass species with higher species
 richness [@loreau_biodiversity_2001].
 
-## Food-web structure changes according to the temporal trends of community biomass and species richness
+We found that both connectance and average trophic level had a positive
+relationship with community biomass over time, meaning that connectance and
+average trophic level increase over time when community biomass increases over
+time as well, and likewise that connectance and average trophic level decrease
+over time when community biomass decreases over time. We also found that the
+temporal trends of connectance and average trophic level were strongly
+correlated (Fig. S2). All together, it suggests that the disturbances that
+lead to decline or increase of community biomass over time are concomitant to
+the decline and increase respectively of trophic species at high trophic level.
+Likewise, we found that the temporal trends of community biomass were positively
+associated to the temporal trends of both number and proportion of piscivorous
+fish species present in the communities (Fig. S2). This result is in
+accordance with the energetic paradigm of food-webs which proposes that
+food-webs are primarily constrained by fluxes of matter and energy
+[@lindeman_trophic-dynamic_1942], which suggest that productivity constraints
+food chain length by energy limitation [@jenkins_productivity_1992;
+@takimoto_ecosystem_2008]. Higher trophic levels have been shown to be more
+sensible to ecosystem size [@takimoto_ecosystem_2008; @post_ecosystem_2000], to
+resource availability and disturbance in small systems [@post_long_2002] and
+particularly to disturbance in hydrologic regimes in streams [@sabo_role_2010;
+@mchugh_dual_2010; @jake_vander_zanden_global_2007]. In the same line, the
+metabolic theory of ecology also predicts that top predators are highly
+constrained by energy limitation [@arim_relationship_2007]. However this
+interpretation does hold if the temporal trends of community biomass are related
+to the quantity of resource available. Another explanation can be that top
+trophic level species are often the ones that are targeted, harvested and those
+that are artificially introduced for recreational fisheries
+[@reid_emerging_2019]. Further investigations on the drivers of community
+biomass decline and increase over time would be needed to further conclude.
 
-While we found a strong relationship between the temporal trends of community
-biomass and the one of species richness, our results suggest that temporal
-trends in community biomass and species richness are associated with very
-different temporal trends on the connectance and average trophic level. Indeed,
-temporal trends of connectance and average trophic level were positively
-associated to the temporal trends of community biomass while we found
-that species richness temporal trends was negatively and no
-significantly related to connectance and average trophic level respectively. All
-together, it suggests that temporal trends of community biomass and species
-richness are related to different assembly and disassembly processes in
-food-webs.
+In contrast, we found that the temporal trends of connectance was negatively
+related to the temporal trends of species richness, in accordance with the
+strong negative relationships that we found in the present study and from
+previous results over spatial gradient [@dunne_network_2006;
+@danet_species_2021]. Furthermore, we found that temporal trends of the
+proportion of piscivorous species was negatively associated with the temporal
+trends of species richness (Fig. S2), meaning that communities that increase in
+richness over time have an increase in the proportion of non-piscivore over time
+and vice versa. This result is in accordance with a meta-analysis showing the
+number of species by trophic level decrease toward higher trophic level
+[@turney_pyramids_2016]. It suggests that the temporal increase of species
+richness found in our dataset is associated with a decrease of connectance
+because species richness increases are biased toward non-piscivorous species
+which have no piscivory links. We also found that the changes of average trophic
+level over time were not related to the changes of species richness over time.
+All together, an explanation can be that species richness changes over time,
+without changes in community biomass, are more linked to non piscivorous species
+having lower trophic level and relatively low biomass, which results in negative
+relationships with temporal trends in connectance and no relationship with
+average trophic level.
 
-The temporal trends of connectance were positively linked to that of community
-biomass, meaning that when connectance increased through time when community
-biomass increased through time in a given site. Reversely, connectance decreased
-in food-webs when community biomass decreased through time. Indeed, food-webs
-have a highly nested structure, in a way that feeding trophic links of species
-at lower trophic level are a subset of the ones of species found at higher
-trophic level [@kondoh_food_2010; @nordstrom_nestedness_2015]. It is because
-feeding interactions are largely driven by body size, consumers being larger
-than their preys [@brose_allometric_2006; @woodward_body_2005]. We also found
-that community biomass losses through time were associated to a temporal
-decrease of average trophic level and that community biomass temporal gains were
-associated to temporal increase of average trophic level. Together with
-connectance, it suggests that community biomass losses and gains are associated
-to losses and gains in large bodied piscivores, i.e. biomass at the higher
-trophic level. In the same line, we found that the temporal trends of community
-biomass were positively associated to the temporal trends of both number and
-proportion of piscivorous fish species present in the communities (Fig.
-SXX). The close association between the temporal trends of community biomass
-from one side, and connectance, average trophic level from the other side,
-strongly suggest that temporal trends in community biomass in natural freshwater
-fish communities are mainly associated to variations in the biomass of the top
-trophic level.
+However, as we found a strong positive relationship between the temporal trends
+of species richness and community biomass, it results that species richness
+temporal trends had an indirect positive effect on the temporal trends of both
+connectance and average trophic level via community biomass. Then, our study
+suggests that species richness and community biomass have antagonistic effects
+on connectance, respectively negative and positive. The temporal trends of
+species richness had then a total effect on the temporal trends of connectance
+and average trophic level which was twice lower than the one of the temporal
+trends of community biomass. It suggests that the temporal assembly and
+disassembly of food-webs are more sensitive to variations in community biomass
+than in species richness, in other words that food-web structure is more robust
+to changes in species richness than in biomass over time. Our study then
+suggests that the changes of food-web structure over time related to changes in
+species richness could be actually mediated by changes in community biomass.
 
-In contrast, we found that temporal trends of connectance was weakly negatively
-related to the temporal trends of species richness, in contrasts with the strong
-negative relationships that we found in the present study and from previous
-results over spatial gradient [@dunne_network_2006; @danet_species_nodate].
-Furthermore, we found that temporal trends of the proportion of piscivorous
-species was negatively associated to the temporal trends of species richness
-(Table SXX), in accordance with previous meta-analysis over spatial gradient
-[@turney_pyramids_2016] and mesocosm experiment [@downing_ecosystem_2002]. It
-resonates with the energetic paradigm of food-webs which proposes that the
-presence of species at higher trophic level is constrained by energy loss along
-the food chain [@lindeman_trophic-dynamic_1942]. It suggests that the temporal
-increase of species richness found in our dataset are associated to a decrease
-of connectance because species richness increases are biased toward
-non-piscivorous species which have less feeding links than piscivorous species.
-We found in the same time that the temporal trends species richness had no
-direct link with the temporal trends of the average trophic level, the latter
-being weighted by the biomass of each node. An explanation can be that when
-species richness increases or decreases through time without community biomass
-trends, the associated decrease and respectively increase in proportion of
-piscivorous species leads to a redistribution of biomass among remaining
-piscivorous species or among the non-piscivorous species.
+As studies reported community biomass or species richness temporal trends
+[@hallmann_more_2017; @ceballos_biological_2017; @dornelas_assemblage_2014;
+@blowes_geography_2019], we document that temporal trends of species richness
+and community biomass might have different consequences on the structure of the
+community. In particular, the decrease of the average trophic level associated
+to the loss of community biomass could have cascading effect on ecosystem
+functioning as the highest predators are predicted to increase productivity and
+stabilize communities [@wang_biodiversity_2018; @shanafelt_stability_2018;
+@danet_species_2021]. In contrast, the loss of species richness might be linked
+to loss of redundancy in the food-web, highlighting that those communities may
+become more at risk regarding future perturbations [@yachi_biodiversity_1999].
+Interestingly, the hypothesis that temporal trends in community biomass is
+related to higher trophic level in our system has a strong reasoning with the
+effect of human fisheries in marine systems which affect primarily fish species
+at top trophic levels [@sprules_surfing_2016].
 
-The temporal trends of species richness had an indirect positive effect on the
-temporal trends of both connectance and average trophic level through the
-positive relationship between the temporal trends of species richness and
-community biomass. The temporal trends of species richness had then an
-total effect on the temporal trends of connectance and average trophic level
-which was twice lower in magnitude than the magnitude of the total effect of the
-temporal trends of community biomass. It suggests that the temporal assembly and
-disassembly of food-webs are more sensible to variations in community biomass
-than in species richness, in other words that food-web structure is more robust
-to species richness change than biomass changes. This result is in line with
-evidences that food-web containing generalist predators can rewire in response
-to changes in the availability of prey species [@bartley_food_2019]. This result
-also resonates with the energy paradigm of food-webs which proposes that
-food-webs are primarily constrained by fluxes of matter and energy
-[@lindeman_trophic-dynamic_1942], so community biomass and not by species
-richness.
-
----
-# - Remove the following paragraph:  
-# As studies reported community biomass or species richness temporal trends
-# [@hallmann_more_2017; @ceballos_biological_2017; @dornelas_assemblage_2014;
-# @blowes_geography_2019], we document that temporal trends of species richness
-# and community biomass might have different consequences on the structure of the
-# community. In particular, the decrease of the average trophic level associated
-# to the loss of community biomass could have cascading effect on ecosystem
-# functioning as the highest predators are predicted to increase productivity and
-# stabilise communities [@wang_biodiversity_2018; @shanafelt_stability_2018;
-# @danet_species_nodate]. In contrasts, the loss of species richness might be
-# linked to loss of redundancy in the food-web, highlighting that those
-# communities may become more at risk regarding future perturbations
-# [@yachi_biodiversity_1999]. Interestingly, the hypothesis that temporal trends
-# in community biomass is related to higher trophic level in our system has a
-# strong reasoning with the effect of human fisheries in marine systems which
-# affect primarily fish species at top trophic level [@sprules_surfing_2016].
-# Overall, our study highlights that monitoring several facets of biodiversity is
-# essential to infer how ecological communities are reshaped by loss and gain of
-# biomass and species richness.
----
-
-## Space-for-time substitution does not always hold
-
-In time and space, we found that connectance was positively linked to community
-biomass. This result is also in accordance with theoretical work showing that
-higher food-web connectance can result in higher community biomass
-[@thebault_food-web_2003], or lower [@poisot_trophic_2013], highlighting that
-the relation between connectance and community biomass may be dependant on how
-food-web structure change with community biomass. Likewise, we found that
-average trophic level had a positive relationship with community biomass in
-space and time, in accordance with a theoretical study predicting an increase of
-community biomass subsequent to the presence of higher predators
+Regarding the space-for-time substitution, we found that connectance was
+positively linked to community biomass both over space and time. This result
+resonates with theoretical work showing that higher food-web connectance can
+result in higher community biomass [@thebault_food-web_2003], or lower
+[@poisot_trophic_2013] over space, highlighting that the relation between
+connectance and community biomass may be dependant on how food-web structure
+change with community biomass over space and time. Likewise, we found that the
+average trophic level had a positive relationship with community biomass over
+space and time, in accordance with a theoretical study over space predicting an
+increase of community biomass subsequent to the presence of higher predators
 [@wang_biodiversity_2018]. Finally, we found a positive relationship between
-community biomass and species both in space and time, however the relationship
-in time was stronger.
-
-Surprisingly, we found that the temporal trends of connectance were weakly
-related to the one of species richness as found spatially in most empirical
-food-webs [@dunne_network_2006] and also here. We further found a weak negative
-relationship between the temporal trends of average trophic level and the one of
-species richness which we found a twice stronger but positive relationship
-between median average trophic level and median species richness over the
-spatial gradient. An explanation might be that environmental gradient, in
-resources in hydrologic contraints might be responsible for the strong negative
-effect of species richness on both connectance and average trophic level over
-spatial gradient. However, we controlled our spatial analysis by the Biological
-Demand in Oxygen, water temperature and the stream gradient. This result is also
-in line with other studies which found mismatch between spatial and temporal
-patterns [@adler_contrasting_2007; @johnson_testing_2008]. This discrepancy in
-space and time might be due to the crucial assumption that variations in space
-reflect differences in assembly stages of ecological communities and then
-mirrors their temporal assembly/disassembly trajectories. Temporal variation of
-species richness might relate on transitory dynamics while spatial gradient
-reflect aggregated dynamics over longer time scale including a far number of
-processes including high species turnover along spatial gradient.
+community biomass and species richness both in space and time, however the
+temporal relationship was stronger. We also found a negative relationship
+between connectance and species richness space and time, in accordance with
+previous findings over space in empirical food-webs [@dunne_network_2006]. We further
+found no relationship between average trophic level and species richness over
+time while we found a twice stronger but positive relationship between median
+average trophic level and median species richness over the spatial gradient. An
+explanation might be that environmental gradient and the pattern of fish
+migration since the last glaciation, for the strong negative effect of species
+richness on both connectance and average trophic level over spatial gradient.
+However, we controlled our spatial analysis by the Biological Demand in Oxygen,
+water temperature and the stream gradient. This result is also in line with
+other studies which found a mismatch between spatial and temporal patterns
+[@adler_contrasting_2007; @johnson_testing_2008]. This discrepancy in space
+and time might be due to the strong assumption that variations in space reflect
+differences in assembly stages of ecological communities and then mirror their
+temporal assembly/disassembly trajectories. Temporal variation of species
+richness might relate to transitory dynamics while spatial gradients reflect
+aggregated dynamics over a longer time scale including a far number of processes
+including high species turnover along spatial gradients.
 
@@
 substitution may be relevant to predict the effects of community biomass losses
-or gains on food-web structure. However, our findings suggest that
-space-for-time substitution might not work for species richness. Our study calls
-for further investigations to support the generality of assembly rules in
-food-webs. They are crucial to better understand the assembly and disassembly of
-food-web and then predict its impact on ecosystem functioning.
+or gains on food-web structure but also that space-for-time substitution might
+not work for species richness. Our study calls for further investigations to
+support the generality of assembly rules in food-webs. They are crucial to
+better understand the assembly and disassembly of food-webs and then predict its
+impact on ecosystem functioning.
 
@@
 complete description of the sampling process can be found in
-@danet_species_nodate (main text and appendixS2). The fishes are sampled using
+@danet_species_2021 (main text and appendix S2). The fishes are sampled using
 electrofishing all across the streams in shallow streams and over the bank by
@@
 individual bodysize by species for each sampling [@bonnaffe_comparison_2021;
-@danet_species_nodate].
+@danet_species_2021].
 
@@
 leading to a mean standard deviation of sampled month in each site of three
-weeks [@danet_species_nodate]. Those steps leads to the selection of 
+weeks [@danet_species_2021]. Those steps leads to the selection of 
 `r nb_st` sites (Figure \@ref(fig:matmet)A).
@@
 life stages by fish species, each one being delimited by body size
-[@bonnaffe_comparison_2021; @danet_species_nodate]. The ontogenic fish diet
+[@bonnaffe_comparison_2021; @danet_species_2021]. The ontogenic fish diet
 database was filled according to fishbase (Froese et al. 2021) and literature
-[@bonnaffe_comparison_2021; @danet_species_nodate].
+[@bonnaffe_comparison_2021; @danet_species_2021].
 
@@
 \begin{aligned}
-    Y_{i|n, t} &= \alpha + \betaTime_t + \epsilon_{i|n, t}
+    Y_{i|n, t} &= \alpha + \beta Time_t + \epsilon_{i|n, t}
   (\#eq:gen)
@@
 the observed values (Fig. SXX). We also visually inspected the Posterior
-Integral Transform (PIT) and Conditional Predictive Ordinate (CPO) to assess
-the quality of the model fit. We also computed the marginal ($R^2_m$)and
-conditional ($R^2_c$) R-squared of the models following previous formulations
+Integral Transform (PIT) and Conditional Predictive Ordinate (CPO) to assess the
+quality of the model fit. We also computed the marginal ($R^2_m$)and conditional
+($R^2_c$) R-squared of the models following previous formulations
 [@nakagawa_general_2013; @lahuis_explained_2014]. In order to account for the
-variability associated with the priors [@gelman_r-squared_2019], we computed the variance of the
-posterior distribution  of each predicted
-values ($Var_{fit} = \sigma^2(\hat{Y_i})$). We computed $R^2$ values for each predicted
-values, then obtaining a $R^2$ distribution [@gelman_r-squared_2019]. We reported mean marginal and
-conditional $R^2$ associated the 95% credible interval computed using the
-Highest Posterior Density method.
+variability associated with the priors [@gelman_r-squared_2019], we computed the
+variance of the posterior distribution  of each predicted values ($Var_{fit} =
+\sigma^2(\hat{Y_i})$). We computed $R^2$ values for each predicted values, then
+obtaining a $R^2$ distribution [@gelman_r-squared_2019]. We reported mean
+marginal and conditional $R^2$ associated the 95% credible interval computed
+using the Highest Posterior Density method.
 
@@
 The temporal trends at each site have been extracted from the hierarchical model
-using mean BLUP values (Best Linear Unbiaised Predictor), then multiplied
+using mean BLUP values (Best Linear Unbiaised Prediction), then multiplied
 by 10 to get temporal trends by decade. For logged transformed biomass and
@@
 [@murphy_semEff_2021]. Confidence intervals were obtained by bootstrapping the
-linear models 1000 times and computing adjusted bootstrap percentile interval
+linear models 100 times and computing adjusted bootstrap percentile interval
 (BCa), which are adjusted for asymetric distribution of resampling. The marginal
 and conditional $R^2$ associated to the linear model of the SEMs were computed
-the Nagelkerke method [@lefcheck_piecewisesem_2016].
+with the Nagelkerke method [@lefcheck_piecewisesem_2016].
 
@@
 
+# Extinction simulation in the metaweb
+
+We simulated extinction sequences in the metaweb according to three scenarios to get expectations on how the food-web structure should change according to the addition and deletion of species and nodes.
+The scenario of extinction sequences were related to the trophic level of the species/nodes.
+In the decreasing and increasing scenario, we removed species/nodes in decreasing, resp.
+increasing order, of their trophic level, i.e.
+respectively the higest and lowest trophic level first.
+In the random extinction sequence, we built 50 random extinction sequences.
+For each simulation, we removed fish species/nodes that lost all their preys.
+We computed the connectance, the average and the maximum trophic level.
+
 # References  {-}

### 2022-11-06 paper/appendix.Rmd
Add tables to appendix

@@
     keep_tex: true
-    toc: true
-fontsize: 12pt
+    toc: false 
+fontsize: 10pt
 header-includes:
@@
    - \linenumbers
+   - \renewcommand{\arraystretch}{1}
 geometry: margin=2cm
 bibliography: references.bib
-number_sections: true
+number_sections: false 
 ---
@@
 )
+options(
+  #kableExtra.latex.load_packages = FALSE,
+  knitr.table.format = "latex"
+)
 ```
@@
 ```{r, echo=FALSE, message=FALSE, results="hide"}
-library(drake)
+library(targets)
 library(tidyverse)
@@
 theme_set(mytheme)
-options(knitr.table.format = "latex")
 ```
@@
 ```{r}
-tar_load(r2_inla_tab)
-kable(r2_inla_tab,
+tar_load(tab_inla_r2_rand)
+kable(tab_inla_r2_rand,
   row.names = FALSE,
@@
   caption = "Marginal and Conditional R-squared for the INLA models estimating
-  the temporal trends of the food-web structure", label = "inlarsq",
-  ) %>%
-  kable_styling(latex_options = c("scale_down", "stripped"))
+  the temporal trends of the food-web structure. The table also displays the
+  standard deviation associated to the random effects and the general error of
+  the models. Confidence interval at 95\\% are displayed between square brackets.",
+  label = "inlarsq") %>%
+  collapse_rows(columns = c(1, 2, 3), valign = "top") %>%
+  kable_styling(latex_options = c("scale_down"))
 ```
@@
   structure by site estimated from the Bayesian models using Best Linear
-  Unbiaised Predictor (BLUP). Species richness and biomass temporal trends are
-  reported in percentage change per decade.")
+  Unbiaised Prediction (BLUP). Species richness and biomass temporal trends are
+  reported in percentage change per decade. Dashed red line and solid black line
+  respectively indicate 0 and median change.")
 
@@
 ```
+
 ```{r ext, fig.cap=rand_sim_cap}
@@
 ```{r}
-cor_cap <- paste0("Correlation among food-web metrics for a) temporal trends by site, b) median values by site (cf Main Methods)", " Pisc: piscivorous, rich.: species richness, node: node
-  of the food-web corresponding to a trophic species, prop.: proportion."
+cor_cap <- paste0("Correlation among food-web metrics for a) temporal trends by
+  site, b) median values by site (cf Main Methods)", " Pisc: piscivorous, rich.:
+species richness, node: node of the food-web corresponding to a trophic species,
+prop.: proportion."
 )
@@
 ```{r cor, fig.cap=cor_cap}
-knitr::include_graphics(here::here("fig", "p_corr.png"))
+knitr::include_graphics(here::here("figures", "p_corr.pdf"))
 ```
@@
   label = "vif",
-  ) %>%
-  kable_styling(latex_options = c("scale_down", "stripped"))
+  )
 ```
@@
   ) %>%
-  kable_styling(latex_options = c("scale_down", "stripped")) %>%
-  collapse_rows(columns = 1, valign = "top")
+  kableExtra::collapse_rows(columns = 1, valign = "top")
 ```
+
+```{r}
+tar_load(c(pca_table, op_table, com_metric_tab))
+tab_quanti <- purrr::map_dfr(
+  list(com_metric_tab, op_table, pca_table),
+  function(x) {colnames(x)[1] <- "Variable"; x}
+)
+purrr::map_int(list(com_metric_tab, op_table, pca_table), nrow)
+
+tab_quanti %>%
+  kbl(
+    caption = "Summary distribution of community metrics, fish monitoring and of
+    environmental variables used in the PCA for the spatial SEM.",
+    booktabs = T
+    ) %>%
+  kable_styling() %>%
+  pack_rows("Community metrics", 1, 8) %>%
+  pack_rows("Summary of fish monitoring", 9, 12) %>%
+  pack_rows("Summary of Envionmental variables", 13, 26)
+```

### 2022-11-06 _targets.R

@@ -459,9 +459,32 @@ list(
     mutate(response = var_replacement()[response]) %>%
     select(
       Response = response,
-      `Marg. Rsq (95% CI)` = r2_mvp_marg95hpdci,
-      `Cond. Rsq (95% CI)` = r2_mvp_cond95hpdci
+      `Marg. Rsq` = r2_mvp_marg95hpdci,
+      `Cond. Rsq` = r2_mvp_cond95hpdci
     )
+    ),
+  tar_target(tab_inla_r2_rand,
+    gaussian_inla_rand %>%
+      filter(
+        ci_level == "level:0.95",
+        response %in% c("log_bm_std", "ct_ff", "w_trph_lvl_avg", "log_rich_std")
+        ) %>%
+    select(-ci_level) %>%
+    mutate(across(c(mean, low, high), ~round(., 3))) %>%
+    mutate(
+      response = var_replacement()[response],
+      term = str_remove(term, "Precision for the |Precision for |"),
+      term = replacement_random_term()[term],
+      ci = paste0(mean, " [", high,",", low,"]")
+      ) %>%
+    arrange(response, desc(term)) %>%
+    select(
+      `Response` = response,
+      `Term` = term,
+      `S.D.` = ci
+      ) %>%
+    left_join(r2_inla_tab, by = "Response") %>%
+    select(1, 4, 5, 2, 3)
     ),
   tar_target(p_corr, {
     cor_tps <- tps_for_sem %>%
@@ -496,7 +519,6 @@ list(
       ncol = 3,
       rel_widths = c(1, 1, .1),
       labels = c("a", "b", ""))
-
   }),
 
   ## Random network extinction
@@ -877,8 +899,101 @@ list(
       format = "file"
     ),
   tar_target(figcorr,
-    save_plot(here("figures", "p_corr.png"), p_corr, ncol = 2),
+    save_plot(here("figures", "p_corr.pdf"), p_corr, ncol = 2),
     format = "file"
+  ),
+
+  # Tables:
+  tar_target(pca_table,
+    data_for_pca %>%
+      pivot_longer(-station, names_to = "metric", values_to = "values") %>%
+      group_by(metric) %>%
+      summarise(summ = list(enframe(summary_distribution(values, na.rm = TRUE)))) %>%
+      unnest(summ) %>%
+      pivot_wider(names_from = "name", values_from = "value") %>%
+      mutate(
+        median = format(round(median, 2), nsmall = 2),
+        `Median (Q1, Q3)` = paste0(median, " (",
[…]

### 2022-11-06 packages.R

@@ -1,5 +1,7 @@
 # Load all your packages before calling make().
 
+library(tarchetypes)
+library(here)
 library(drake)
 library(tibble)
 library(tidyverse)

### 2022-11-06 paper/appendix.Rmd
Use tar_load for figure path

@@
 ```{r tps10, fig.cap=tps10_cap}
-knitr::include_graphics(here::here("figures", "p_hist_site_tps10.pdf"))
+tar_load(figStps10)
+knitr::include_graphics(figStps10)
 ```
@@
   "Simulations of (a) species and (b) nodes extinctions in the metaweb according
-  to three scenarios: random extinction sequence, decreasing trophic level,
-  increasing trophic level."
-
+  to three scenarios: random extinction sequence, extinction sequence by decreasing order of trophic level,
+ extinction sequence by increasing order of trophic level. The black line
+ represents the prediction of a GAM model for the random extinction sequences (N = 50)."
 )
@@
 ```{r ext, fig.cap=rand_sim_cap}
-knitr::include_graphics(here::here("figures", "tot_ext_sim.pdf"))
+tar_load(figSext)
+knitr::include_graphics(figSext)
 ```
@@
 ```{r cor, fig.cap=cor_cap}
-knitr::include_graphics(here::here("figures", "p_corr.pdf"))
+tar_load(figcorr)
+knitr::include_graphics(figcorr)
 ```
@@
 ```{r, fig.cap=obs_fit_cap}
-knitr::include_graphics(here::here("figures", "p_obs_fit.pdf"))
+tar_load(figSobsfit)
+knitr::include_graphics(figSobsfit)
 ```
@@
 )
-purrr::map_int(list(com_metric_tab, op_table, pca_table), nrow)
+#purrr::map_int(list(com_metric_tab, op_table, pca_table), nrow)
 

### 2022-11-07 paper/appendix.Rmd
Cosmetic to pdf

@@
   #kableExtra.latex.load_packages = FALSE,
-  knitr.table.format = "latex"
+  knitr.table.format = "latex",
+  knitr.graphics.rel_path = FALSE
 )

### 2022-11-07 paper/manuscript.Rmd
Cosmetic to pdf

@@
     keep_tex: true
-    toc: true
+    toc: false 
     fontsize: 12pt
@@
 )
+options(
+  knitr.table.format = "latex",
+  knitr.graphics.rel_path = FALSE
+)
 ```
-
-- Tentative titles:
-  - How food-webs assembly and disassembly through time in natural settings?
-    Lessons from freshwater fishes
-  - Relationships among temporal trends of food-web structure, species richness
-    and community biomass reveal contrasting assembly
-    and disassembly processes
-  - Temporal trends in food web structure according to richness and biomass
-    reveal contrasting assembly and disassembly processes
 
@@
 There is rising recognition that biodiversity changes are
-multidimensional[@mcgill_fifteen_2015; @blowes_geography_2019;
+multidimensional [@mcgill_fifteen_2015; @blowes_geography_2019;
 @hillebrand_biodiversity_2018; @blowes_local_nodate]. Studies found important
@@
 community composition, species coexistence, and ecosystem
-functioning[@chesson_mechanisms_2000; @thebault_food-web_2003;
+functioning [@chesson_mechanisms_2000; @thebault_food-web_2003;
 @oconnor_general_2017]. The structure of ecological networks can trigger or
-impede perturbation propagations, i.e secondary extinctions[@paine_note_1969;
+impede perturbation propagations, i.e secondary extinctions [@paine_note_1969;
 @dunne_network_2002; @srinivasan_response_2007;
@@
 degree of generalism in a network, is predicted to increase robustness to
-secondary extinctions[@dunne_network_2002; @sole_complexity_2001] and studies
+secondary extinctions [@dunne_network_2002; @sole_complexity_2001] and studies
 found that higher trophic level was associated to a lower temporal variability
 of community biomass in theoretical models and empirical
-data[@shanafelt_stability_2018; @danet_species_2021]. Then, accounting for how
+data [@shanafelt_stability_2018; @danet_species_2021]. Then, accounting for how
 the structure of ecological networks changes over time according to other
@@
 Th availability of ecological network timeseries is
-scarce[@kortsch_disentangling_2021], such as predictions about how the structure
+scarce [@kortsch_disentangling_2021], such as predictions about how the structure
 of ecological networks change according to changes in species richness come from
@@
 scale positively or negatively with community biomass in theoretical
-food-webs[@thebault_food-web_2003; @poisot_trophic_2013] while the average
+food-webs [@thebault_food-web_2003; @poisot_trophic_2013] while the average
 trophic level was previously shown to scale negatively with species
-richness[@danet_species_2021].
+richness [@danet_species_2021].
 
@@
 space and in time, i.e. that spatial sequences correspond to temporal sequences.
-This method have raised criticisms[@damgaard_critique_2019], with studies
-showing analogous patterns in space and time[@blois_space_2013] or not
+This method have raised criticisms [@damgaard_critique_2019], with studies
+showing analogous patterns in space and time [@blois_space_2013] or not
 [@johnson_testing_2008; @adler_contrasting_2007]. Spatial turnover of species
@@
 been hypothesised to be responsible for the non-compliance of space-for-time
-substitution[@adler_contrasting_2007; @blois_space_2013].
+substitution [@adler_contrasting_2007; @blois_space_2013].
 
 The increasing availability ecological temporal series and the development of
-methods to reconstruct food-webs[@bonnaffe_comparison_2021;
+methods to reconstruct food-webs [@bonnaffe_comparison_2021;
 @gravel_inferring_2013; @danet_species_2021] makes possible to overcome those
@@
 
-```{r}
+```{r, results=FALSE}
 tar_load(glob_tps_trends_decade_no_drivers)
+glob_tps_trends_decade_no_drivers
 gbm <- get_effect_ci(resp = "log_bm_std", ci_lvl = "level:0.80", p = TRUE)
@@
 ```{r sem, fig.cap = sem_cap}
-knitr::include_graphics(here::here("figures", "fig2.png"))
+knitr::include_graphics(here::here("figures", "fig2.pdf"))
 ```
@@
 relationship between the temporal trends of community biomass and of
-species richness ($r_\delta = `r rdtps$bm$r`$, Fig. \@ref(fig:sem) a and b,
+species richness ($r_\delta =$ `r rdtps$bm$r`, Fig. \@ref(fig:sem) a and b,
 $r_\delta$: standardized slope coefficients, [95% CI]), meaning that both
@@
 The temporal trends of connectance were positively linked with the ones of
-community biomass ($r_\delta = `r rdtps$ct$bm`$), also meaning that both
+community biomass ($r_\delta =$ `r rdtps$ct$bm`), also meaning that both
 temporal trends had the same direction in average. That is, the sites where
@@
 trends of connectance and the ones of species richness
-($r_\delta = `r rdtps$ct$r`$, Fig. \@ref(fig:sem)d). We further found the
+($r_\delta =$ `r rdtps$ct$r`, Fig. \@ref(fig:sem)d). We further found the
 species richness had an indirect positive effect on connectance, through
-community biomass ($r_\delta = `r ridtps$ct$r`$). It resulted in a relatively
+community biomass ($r_\delta =$ `r ridtps$ct$r`). It resulted in a relatively
 weak total negative effect of species richness on connectance
-($r_\delta = `r rttps$ct$r`$), that we also found in random extinction
+($r_\delta =$ `r rttps$ct$r`), that we also found in random extinction
 simulation (Fig. S2).
@@
 The temporal trends of average trophic level had a strong positive relationship
-with the ones of community biomass ($r_\delta = `r rdtps$tlvl$bm`$, Fig.
+with the ones of community biomass ($r_\delta =$ `r rdtps$tlvl$bm`, Fig.
 \@ref(fig:sem)e), meaning that sites where community biomass decreased over
@@
 trends of average trophic level had no direct relationship the ones of species
-richness ($r_\delta = `r rdtps$tlvl$r`$, Fig. \@ref(fig:sem)f). It suggests that
+richness ($r_\delta =$ `r rdtps$tlvl$r`, Fig. \@ref(fig:sem)f). It suggests that
 in communities either losing or gaining species richness over time, the location
@@
 indirect positive relationship with the temporal trends of average trophic level
-through community biomass ($r_\delta = `r ridtps$tlvl$r`$), resulting in a total
-positive relationship ($r_\delta = `r rttps$tlvl$r`$).
+through community biomass ($r_\delta =$ `r ridtps$tlvl$r`), resulting in a total
+positive relationship ($r_\delta =$ `r rttps$tlvl$r`).
 
@@
 median community biomass and median species richness along the spatial gradient,
-but half the strength as the temporal one ($r_\delta = `r rdsp$bm$r`$, Fig.
+but half the strength as the temporal one ($r_\delta =$ `r rdsp$bm$r`, Fig.
 \@ref(fig:std)). We further found a positive relationship between median
-connectance and median community biomass ($r_\delta = `r rdsp$ct$bm`$), as in
+connectance and median community biomass ($r_\delta =$ `r rdsp$ct$bm`), as in
 temporal trends analysis. However, we found a negative relationship between
 median connectance and median species richness, but
-three times stronger than in the temporal analysis ($r_\delta = `r rdsp$ct$r`$,
+three times stronger than in the temporal analysis ($r_\delta =$ `r rdsp$ct$r`,
 Fig. \@ref(fig:std)). We also found a positive indirect effect of median
 richness on median connectance through median community biomass but a weak one
-($r_\delta = `r ridsp$ct$r`$), resulting in a strong negative total effect of
-median richness on median connectance ($r_\delta = `r rtsp$ct$r`$).
+($r_\delta =$ `r ridsp$ct$r`), resulting in a strong negative total effect of
+median richness on median connectance ($r_\delta =$ `r rtsp$ct$r`).
 
@@
 community biomass, but half the strength as in the temporal analysis ($r_\delta
-= `r rdsp$tlvl$bm`$, Fig. \@ref(fig:std)). However, we found a strong negative
+=$ `r rdsp$tlvl$bm`, Fig. \@ref(fig:std)). However, we found a strong negative
 relationship between median average trophic level and median richness ($r_\delta
-= `r rdsp$tlvl$r`$), in contrast with findings in temporal analysis. We also
+=$ `r rdsp$tlvl$r`), in contrast with findings in temporal analysis. We also
 found a positive indirect relationship between average trophic level and  median
@@
 
-# Statistical analysis
+## Statistical analysis
 
@@
 (2) enrichment (Fig. \@ref(fig:matmet)). Enrichment was characterized by the
-average Biological Oxygen Demand [BOD, @mallin_factors_2006][^2]. We further
+average Biological Oxygen Demand [BOD, @mallin_factors_2006]. We further
 added a random effect of the hydrographic basin on the intercept.
@@
 All the statistical models displayed low multicollinearity (Variance inflation
-factor < 3, Table SXX).  We visually inspected the residuals of the linear
+factors < 3, Table SXX).  We visually inspected the residuals of the linear
 models.
@@
 
-```{r matmet, fig.cap=fig_mat_cap, out.width="80%"}
-knitr::include_graphics(get_mypath("figures", "mat_met.pdf"))
-```
-
-# Extinction simulation in the metaweb
+## Extinction simulation in the metaweb
 
@@
 
+```{r matmet, fig.cap=fig_mat_cap, out.width="80%"}
+knitr::include_graphics(get_mypath("figures", "mat_met.pdf"))
+```
+
 # References  {-}

### 2022-11-08 paper/manuscript.Rmd
Finalise manuscript preparation

@@
 title: "Community biomass and species richness temporal trends reveal contrasting assembly and disassembly processes in natural food-webs"
-author: Alain Danet, Loubna El Madouri, Maud Mouchet, Elisa Thébault and Colin Fontaine
-date: \today
+author: Alain Danet (a), Loubna El Madouri (a, c), Maud Mouchet (a), Elisa Thébault (d) and Colin Fontaine (a)
+date: Research report 
 output:
-#  bookdown::word_document2:
+  #bookdown::word_document2:
   #  fontsize: 12pt
@@
 bibliography: references.bib
+csl: pnas.csl
 ---
@@
 
-# Abstract (267 / 250 words max)
+- Corresponding author: Alain Danet (a.h.danet@sheffield.ac.uk)
 
-Understanding how biodiversity changes is a central question in ecology, but
-still challenging because of the multidimensionality of biodiversity changes.
+- Author affiliations:
+
+(a) Centre d’Ecologie et des Sciences de la Conservation, UMR 7204 MNHN7
+CNRS-Sorbonne Université, Muséum national d’Histoire naturelle de Paris, 43 rue
+8 Buffon, 75005 Paris, France
+
+(b) Department of Biosciences, Alfred Denny Building, University of Sheffield,
+Western Bank, Sheffield S10 2TN, United Kingdom
+
+(c) ?
+
+(d) Sorbonne Université, CNRS, IRD, INRAE, Université Paris Est Créteil, 15
+Institute of Ecology and Environmental Sciences of Paris (iEES-Paris), Paris,
+France
+
+- Classification: Biological Sciences (major) - Ecology (minor)
+
+- Keywords: food-web, biodiversity changes, assembly rules, space-for-time
+
+# Abstract (242 / 250 words max)
+
+Understanding how biodiversity changes is a central question in ecology, but a
+challenging one because of the multidimensionality of biodiversity changes.
 Although the structure of ecological networks is a crucial determinant of
@@
 properties of ecological networks comes mainly from spatial comparison, assuming
-a space-for-time equivalence. However, little is know about the validity of the
-space-for-time hypothesis, i.e. if spatial comparison of ecological networks
-accurately translates temporal sequences of assemblages. Here we questioned the
-relationships between the temporal trends of food-web structure and the ones
-of community biomass and species richness, and we assessed how those
-relationships differed from the ones estimated in space. We inferred the
-structure of using food diet and individual body size data from fish monitoring
-in France. We estimated the temporal trends of food-web structure in 400 sites
-using a hierarchical Bayesian model and then assess the relationships among them
-using structural equation models. We found that temporal trends of connectance
-and average trophic level are positively related to ones of community biomass
-but surprisingly poorly related to the temporal trends of species richness. We
-further found support for space-for-time hypothesis for community biomass, but
-not for species richness. We suggest that our results resonates with the
-energetic paradigm of food-webs. Our study sheds a new light on the dynamics of
-food-web assemblage in natural settings and how the structure of ecological
-networks changes according to the changes of other biodiversity facets.
+a space-for-time equivalence, which have rarely tested. We questioned the
+relationships between the temporal changes of food-web structure and the ones of
+community biomass and species richness, and assessed if they differed from the
+ones estimated in space. We inferred the structure of using food diet and body
+size data from fish monitoring in France. We estimated the temporal trends of
+food-web structure in 400 sites using a hierarchical Bayesian model and then
+assessed the relationships among them using structural equation models. We found
+that temporal trends of connectance and average trophic level are positively
+related to ones of community biomass but surprisingly poorly related to the
+temporal trends of species richness, which resonates with the energetic paradigm
+of food-webs. We further found general support for the space-for-time hypothesis
+for community biomass, but not for species richness. Our study
+sheds a new light on the dynamics of food-web assemblage in natural settings and
+how the structure of ecological networks changes according to the changes of
+other biodiversity facets.
 
-# Significance (109 / 120 words max)
+# Significance (115 / 120 words max)
 
 While the multidimensional nature of biodiversity changes has been clearly
-emphasized, little is know how the structure of food-web changes according to
+emphasized, little is known on how the structure of food-web changes according to
 changes in species richness and community biomass. By inferring food-web
 structure based on food-diet data and body size ratios, we analyzed how food-web
-structure in time according to simultaneously changes in species richness and
+structure in time according to concomitant changes in species richness and
 community biomass. We identify that community biomass is the primary driver of
-temporal changes in foodweb structure, but that species richness has surprisingly
+temporal changes in food-web structure, but that species richness has surprisingly
 low effect. We further show that space-for-time leads to contrasting results for
-species richness. Our results shed a new light on how foodweb assemble
-and disassemble in natural settings.
+species richness. Our results shed a new light on the assembly and disassembly
+of food-web according to changes in biomass and in species richness.
 
@@
 
-There is rising recognition that biodiversity changes are
-multidimensional [@mcgill_fifteen_2015; @blowes_geography_2019;
-@hillebrand_biodiversity_2018; @blowes_local_nodate]. Studies found important
-changes in species composition despite no changes in species richness in average
-[@dornelas_assemblage_2014; @blowes_geography_2019], and highlighting the need
-for further investigations on how biodiversity changes over time.
-
-Yet species interactions are largely absent from biodiversity changes. Although
-species interactions, described as ecological networks, drive for a large part
-community composition, species coexistence, and ecosystem
-functioning [@chesson_mechanisms_2000; @thebault_food-web_2003;
+Understanding how biodiversity changes is a central question in ecology,
+although challenging because biodiversity changes are multidimensional
+[@mcgill_fifteen_2015; @blowes_geography_2019; @hillebrand_biodiversity_2018],
+such as important changes in species composition can happen despite no changes
+in species richness in average [@dornelas_assemblage_2014;
+@blowes_geography_2019]. Yet species interactions are largely absent from
+biodiversity changes. Although species interactions, described as ecological
+networks, drive for a large part community composition, species coexistence, and
+ecosystem functioning [@chesson_mechanisms_2000; @thebault_food-web_2003;
 @oconnor_general_2017]. The structure of ecological networks can trigger or
-impede perturbation propagations, i.e secondary extinctions [@paine_note_1969;
+impede perturbation propagations, i.e. secondary extinctions [@paine_note_1969;
 @dunne_network_2002; @srinivasan_response_2007;
@@
 secondary extinctions [@dunne_network_2002; @sole_complexity_2001] and studies
-found that higher trophic level was associated to a lower temporal variability
-of community biomass in theoretical models and empirical
-data [@shanafelt_stability_2018; @danet_species_2021]. Then, accounting for how
-the structure of ecological networks changes over time according to other
-biodiversity facets is crucial.
+found that the presence of higher trophic levels is associated to a higher temporal stability of
+community biomass in theoretical models and empirical data
+[@shanafelt_stability_2018; @danet_species_2021]. Then, accounting for how the
+structure of ecological networks changes over time according to other
+biodiversity facets is crucial to understand biodiversity changes.
 
-Th availability of ecological network timeseries is
-scarce [@kortsch_disentangling_2021], such as predictions about how the structure
-of ecological networks change according to changes in species richness come from
+The availability of ecological network timeseries is scarce
+[@kortsch_disentangling_2021], such as predictions about how the structure of
+ecological networks change according to changes in species richness come from
 spatial comparison of networks. Such studies showed that connectance is
-negatively related to species richness in small (i.e. below 20 species)
-empirical food-webs [reviewed in @dunne_network_2006], which reflects
-constraints on the number of realizable species interactions or an increasing
-proportion of specialists in more rich foodwebs. Connectance has been shown to
-scale positively or negatively with community biomass in theoretical
-food-webs [@thebault_food-web_2003; @poisot_trophic_2013] while the average
-trophic level was previously shown to scale negatively with species
-richness [@danet_species_2021].
+negatively related to species richness in food-webs [reviewed in
+@dunne_network_2006; @danet_species_2021], which reflects constraints on the
+number of realizable species interactions or an increasing proportion of
+specialists in more rich food-webs. Connectance has been shown to scale
+positively or negatively with community biomass in theoretical food-webs
+[@thebault_food-web_2003; @poisot_trophic_2013] while the average trophic level
+was previously shown to scale negatively with species richness in empirical
+food-webs [@danet_species_2021].
 
 However, predicting how ecological networks will change in time according to
-other biodiversity facets based on spatial comparison of ecological communities
-is valid as long as assumption of the space-for-time substitution is valid as
+other biodiversity facets based on spatial comparison of food-webs 
+is valid if the assumption of space-for-time substitution is as
 well. Space-for-time substitution supposes a homology between variations in
 space and in time, i.e. that spatial sequences correspond to temporal sequences.
-This method have raised criticisms [@damgaard_critique_2019], with studies
+This method raised criticisms [@damgaard_critique_2019], with studies
 showing analogous patterns in space and time [@blois_space_2013] or not
@@
 composition, dispersal limitation, disturbance and stochastic processes have
-been hypothesised to be responsible for the non-compliance of space-for-time
+been hypothesized to be responsible for the non-compliance of space-for-time
 substitution [@adler_contrasting_2007; @blois_space_2013].
@@
 
-Using a hierarchical model to estimate conjointly the temporal trends of  
-foodweb structure at all sites, we found weak evidence of a global decrease in
-community biomass (CI80%:`r gbm` by decade; median [Credible Interval]) but of a
+Using a Bayesian hierarchical model to estimate conjointly the temporal trends of
+food-web structure at all sites, we found weak evidence of a global decrease in
+community biomass (CI80%:`r gbm` by decade; median [Credible Interval], Fig. S1) but of a
 global increase in species richness (CI80%: `r gr` by decade) across the `r nb_st` sites. 
@@
 Using structural equation models to disentangle the direct and indirect
-relationships among foodweb structure descriptors, we found a strong positive
+relationships among food-web structure descriptors, we found a strong positive
 relationship between the temporal trends of community biomass and of
 species richness ($r_\delta =$ `r rdtps$bm$r`, Fig. \@ref(fig:sem) a and b,
-$r_\delta$: standardized slope coefficients, [95% CI]), meaning that both
+$r_\delta$: standardized slope coefficient, [95% CI]), meaning that both
 temporal trends had the same direction in average. At the sites where species
@@
 
-We found that both connectance and average trophic level had a positive
-relationship with community biomass over time, meaning that connectance and
-average trophic level increase over time when community biomass increases over
-time as well, and likewise that connectance and average trophic level decrease
-over time when community biomass decreases over time. We also found that the
-temporal trends of connectance and average trophic level were strongly
-correlated (Fig. S2). All together, it suggests that the disturbances that
-lead to decline or increase of community biomass over time are concomitant to
-the decline and increase respectively of trophic species at high trophic level.
-Likewise, we found that the temporal trends of community biomass were positively
-associated to the temporal trends of both number and proportion of piscivorous
-fish species present in the communities (Fig. S2). This result is in
-accordance with the energetic paradigm of food-webs which proposes that
-food-webs are primarily constrained by fluxes of matter and energy
-[@lindeman_trophic-dynamic_1942], which suggest that productivity constraints
-food chain length by energy limitation [@jenkins_productivity_1992;
-@takimoto_ecosystem_2008]. Higher trophic levels have been shown to be more
-sensible to ecosystem size [@takimoto_ecosystem_2008; @post_ecosystem_2000], to
-resource availability and disturbance in small systems [@post_long_2002] and
-particularly to disturbance in hydrologic regimes in streams [@sabo_role_2010;
-@mchugh_dual_2010; @jake_vander_zanden_global_2007]. In the same line, the
-metabolic theory of ecology also predicts that top predators are highly
-constrained by energy limitation [@arim_relationship_2007]. However this
-interpretation does hold if the temporal trends of community biomass are related
-to the quantity of resource available. Another explanation can be that top
-trophic level species are often the ones that are targeted, harvested and those
-that are artificially introduced for recreational fisheries
-[@reid_emerging_2019]. Further investigations on the drivers of community
-biomass decline and increase over time would be needed to further conclude.
+Our results suggest that the disturbances that lead to decline or increase of
+community biomass over time are concomitant to the decline and increase
+respectively of trophic species at high trophic level. We found that both
+connectance and average trophic level had a positive relationship with community
+biomass over time, meaning that connectance and average trophic level increase
+over time when community biomass increases over time as well, and likewise that
+connectance and average trophic level decrease over time when community biomass
+decreases over time. We also found that the temporal trends of connectance and
+average trophic level were strongly correlated (Fig. S3). Likewise, we found
+that the temporal trends of community biomass were positively associated to the
+temporal trends of both number and proportion of piscivorous species
+present (Fig. S3). This result is in accordance with the
+energetic paradigm of food-webs which proposes that food-webs are primarily
+constrained by fluxes of matter and energy [@lindeman_trophic-dynamic_1942],
+which suggest that productivity constraints food chain length by energy
+limitation [@jenkins_productivity_1992; @takimoto_ecosystem_2008]. Higher
+trophic levels have been shown to be more sensible to ecosystem size
+[@takimoto_ecosystem_2008; @post_ecosystem_2000], to resource availability and
+disturbance in small systems [@post_long_2002] and particularly to disturbance
+in hydrologic regimes in streams [@sabo_role_2010; @mchugh_dual_2010;
+@jake_vander_zanden_global_2007]. In the same line, the metabolic theory of
+ecology also predicts that top predators are highly constrained by energy
+limitation [@arim_relationship_2007]. However, this interpretation holds if
+the temporal trends of community biomass are related to the quantity of resource
+available. Another explanation can be that top trophic level species are often
+the ones that are targeted, harvested and those that are artificially introduced
+for recreational fisheries [@reid_emerging_2019]. Further investigations on the
+drivers of community biomass decline and increase over time would be needed to
+further conclude.
 
@@
 proportion of piscivorous species was negatively associated with the temporal
-trends of species richness (Fig. S2), meaning that communities that increase in
-richness over time have an increase in the proportion of non-piscivore over time
+trends of species richness (Fig. S3), meaning that communities that increase in
+richness over time have an increase in the proportion of non-piscivorous species over time
 and vice versa. This result is in accordance with a meta-analysis showing the
@@
 
-However, as we found a strong positive relationship between the temporal trends
-of species richness and community biomass, it results that species richness
-temporal trends had an indirect positive effect on the temporal trends of both
-connectance and average trophic level via community biomass. Then, our study
-suggests that species richness and community biomass have antagonistic effects
-on connectance, respectively negative and positive. The temporal trends of
+Our findings further suggest that species richness and community biomass have
+antagonistic effects on connectance, respectively negative and positive. As we
+found a strong positive relationship between the temporal trends of species
+richness and community biomass, it results that species richness temporal trends
+had an indirect positive effect on the temporal trends of both connectance and
+average trophic level via community biomass. Then,  The temporal trends of
 species richness had then a total effect on the temporal trends of connectance
@@
 Interestingly, the hypothesis that temporal trends in community biomass is
-related to higher trophic level in our system has a strong reasoning with the
-effect of human fisheries in marine systems which affect primarily fish species
-at top trophic levels [@sprules_surfing_2016].
+related to species of higher trophic level in our system has a strong reasoning
+with the effect of human fisheries in marine systems which affect primarily fish
+species at top trophic levels [@sprules_surfing_2016].
 
-Regarding the space-for-time substitution, we found that connectance was
-positively linked to community biomass both over space and time. This result
-resonates with theoretical work showing that higher food-web connectance can
-result in higher community biomass [@thebault_food-web_2003], or lower
-[@poisot_trophic_2013] over space, highlighting that the relation between
-connectance and community biomass may be dependant on how food-web structure
-change with community biomass over space and time. Likewise, we found that the
-average trophic level had a positive relationship with community biomass over
-space and time, in accordance with a theoretical study over space predicting an
-increase of community biomass subsequent to the presence of higher predators
-[@wang_biodiversity_2018]. Finally, we found a positive relationship between
-community biomass and species richness both in space and time, however the
-temporal relationship was stronger. We also found a negative relationship
-between connectance and species richness space and time, in accordance with
-previous findings over space in empirical food-webs [@dunne_network_2006]. We further
-found no relationship between average trophic level and species richness over
-time while we found a twice stronger but positive relationship between median
-average trophic level and median species richness over the spatial gradient. An
-explanation might be that environmental gradient and the pattern of fish
-migration since the last glaciation, for the strong negative effect of species
-richness on both connectance and average trophic level over spatial gradient.
-However, we controlled our spatial analysis by the Biological Demand in Oxygen,
-water temperature and the stream gradient. This result is also in line with
-other studies which found a mismatch between spatial and temporal patterns
-[@adler_contrasting_2007; @johnson_testing_2008]. This discrepancy in space
-and time might be due to the strong assumption that variations in space reflect
-differences in assembly stages of ecological communities and then mirror their
-temporal assembly/disassembly trajectories. Temporal variation of species
-richness might relate to transitory dynamics while spatial gradients reflect
-aggregated dynamics over a longer time scale including a far number of processes
-including high species turnover along spatial gradients.
+We found evidence that space-for-time substitution is valid for community
+biomass but not for species richness. More specifically, we found a positive
+relationship between community biomass and species richness both in space and
+time. We also found that connectance was positively linked to community biomass
+both over space and time, it resonates with theoretical studies showing that
+higher food-web connectance can result in higher community biomass
+[@thebault_food-web_2003], or lower [@poisot_trophic_2013] over space,
+highlighting that the relation between connectance and community biomass may be
+dependent on how food-web structure change with community biomass over space and
+time. Likewise, we found that the average trophic level had a positive
+relationship with community biomass over space and time, in accordance with a
+theoretical study predicting an increase of community biomass
+linked to the presence of higher predators [@wang_biodiversity_2018].
+However, while we found a total negative effect between connectance and species
+richness in space, in accordance with previous findings over space in
+empirical food-webs [@dunne_network_2006; @danet_species_2021], we found a null
+total effect in time. The result is even more contrasting for average trophic
+level, where we found a total positive effect of species richness in time but a
+negative one in space. This result is also in line with other studies which
+found a mismatch between spatial and temporal patterns [@adler_contrasting_2007;
+@johnson_testing_2008]. This discrepancy in space and time might be due to the
+strong assumption that variations in space reflect differences in assembly
+stages of ecological communities and then mirror their temporal
+assembly/disassembly trajectories. Temporal variation of species richness might
+relate to transitory dynamics while spatial gradients reflect aggregated
+dynamics over a longer time scale including a far number of processes including
+high species turnover along spatial gradients. Our results then suggest that food-web
+structure comparison along space gradient might be a reasonable surrogate for
+time sequence, it is probably not the case for species richness spatial
+comparison.
 
@@
 Our study suggests that species richness and community biomass temporal trends
-in natural fish communities relate on different ecological processes, biomass
-temporal dynamics being related to variations of food-web structure at the
-higher trophic levels while variations of species richness is weakly related to
-change in food-web structure. Our result also suggests that space for time
-substitution may be relevant to predict the effects of community biomass losses
-or gains on food-web structure but also that space-for-time substitution might
-not work for species richness. Our study calls for further investigations to
-support the generality of assembly rules in food-webs. They are crucial to
-better understand the assembly and disassembly of food-webs and then predict its
-impact on ecosystem functioning.
+in natural fish communities relate on different ecological processes. Biomass
+changes in time are related to variations of food-web structure at the
+higher trophic levels while changes in species richness are weakly related to
+changes in food-web structure, in accordance with the energetic
+paradigm of food-webs. Our results further highlight that the effects of species
+richness changes on food-web structure are strongly mediated by antagonistic
+effects of community biomass. We also find evidences which suggest that
+space-for-time substitution may be relevant to predict the effects of community
+biomass losses or gains on food-web structure but also that space-for-time
+substitution might not work for species richness. Our study calls for further
+investigations to support the generality of assembly rules in food-webs,
+according to changes in community biomass and species richness. They are crucial
+to better understand how biodiversity changes will affect community dynamics
+and ecosystem functioning.
 
@@
 weeks [@danet_species_2021]. Those steps leads to the selection of 
-`r nb_st` sites (Figure \@ref(fig:matmet)A).
+`r nb_st` sites (Fig. \@ref(fig:matmet), Table S2).
 
@@
 law, $B_i = 0.01 \times l_i^{3.03}$, $B_i$ being the biomass expressed in gram and $l_i$ the
-body length of the individual $i$ expressed in millimetres [@froese_cube_2006]. Then the
+body length of the individual $i$ expressed in millimeters [@froese_cube_2006]. Then the
 biomass of each species and community biomass were obtained by summing the body
@@
 species identity and their body size. The diet database described two or three
-life stages by fish species, each one being delimited by body size
-[@bonnaffe_comparison_2021; @danet_species_2021]. The ontogenic fish diet
-database was filled according to fishbase (Froese et al. 2021) and literature
-[@bonnaffe_comparison_2021; @danet_species_2021].
+life stages by fish species, each one being delimited by body size. The
+ontogenic fish diet database was filled according to fishbase
+[@froese_fishbase_2021] and literature [@bonnaffe_comparison_2021;
+@danet_species_2021].
 
@@
 
-At each site, yearly food-webs were described by their community biomass,
-species richness and the evenness of biomass across species. The evenness was
-quantified with the Pielou index, computed as the Shannon diversity index
-divided by the number of species ($P = \frac{H'}{N}$, with $H'$ being the
-Shannon diversity index and $N$ the number of species). Yearly food-web
-structure was described by their connectance, describing the degree of
-generalism in a network [@dunne_network_2006; @delmas_analysing_2019]. It was
-computed as the ratio between the number of actual links and the number of
-potential links ($C = \frac{L}{S(S-1)}$, with $L$ being the number of links and
-$S$ the number of trophic species). We also computed the average trophic level,
-weighted by the biomass of the trophic species. The trophic level of a trophic
-species was computed recursively as 1 added to the mean trophic level of the
-preys that it consumes [@herendeen_ecological_2008].
+At each site, yearly food-webs were described by their community biomass and
+species richness. Yearly food-web structure was described by their connectance,
+describing the degree of generalism in a network [@dunne_network_2006;
+@delmas_analysing_2019]. It was computed as the ratio between the number of
+actual links and the number of potential links ($C = \frac{L}{S(S-1)}$, with $L$
+being the number of links and $S$ the number of trophic species). We also
+computed the average trophic level, weighted by the biomass of the trophic
+species. The trophic level of a trophic species was computed recursively as 1
+added to the mean trophic level of the preys that it consumes
+[@herendeen_ecological_2008].
 
@@
 The model parameters were estimated using INLA (Integrated Nested Laplacian
-Approximation) bayesian inference with default uninformative priors
+Approximation) Bayesian inference with default uninformative priors
 [@rue_bayesian_2017]. The prior distributions for the fixed intercept and slope were
-modelled as a flat normal distribution with a mean of zero ($\mathcal{N}(0,\, 1000)$).
-Prior distributions for the gaussian error $\epsilon_{i|n, t}$ and the random
+modeled as a flat normal distribution with a mean of zero ($\mathcal{N}(0,\, 1000)$).
+Prior distributions for the Gaussian error $\epsilon_{i|n, t}$ and the random
 effects were modelled as a log gamma distribution with
@@
 The performance of the model was assessed visually by plotting the fitted versus
-the observed values (Fig. SXX). We also visually inspected the Posterior
+the observed values (Fig. S4). We also visually inspected the Posterior
 Integral Transform (PIT) and Conditional Predictive Ordinate (CPO) to assess the
@@
 
-The temporal trends at each site have been extracted from the hierarchical model
+We extracted the temporal trends at each site from the hierarchical model
 using mean BLUP values (Best Linear Unbiaised Prediction), then multiplied
@@
 
-To assess the validity of the space-for-time substitution hypothesis, we
-compared the relationships among food-web structure in time to the ones observed
-in space. To do so, we selected the same sites that were used
-for the temporal analysis. We summarised temporal series of each station by the
-median value over time of each facet of food-web structure described above.
+We assessed the validity of the space-for-time substitution hypothesis by
+comparing the relationships estimated among food-web structure in time to the
+ones inferred in space. We used the same sites as in the temporal analysis,
+but we summarised temporal series of each station by the median value over time
+of each facet of food-web structure described above (Fig. \@ref(fig:matmet)).
 
@@
 
-We modelled the relationships among food-web structure, that is
+We modeled the relationships among food-web structure, that is
 connectance and average trophic level, and community biomass ($dB$) and species
-richness ($dR$) with Structural Equation Models. We modelled a it such as species
-richness is related to community biomass and food-web structure. In
+richness ($dR$) with Structural Equation Models. We modeled species
+richness as related to community biomass and food-web structure. In
 turn community biomass was related to food-web structure. We computed one
@@
 synthesizing respectively (1) stream gradient from upstream to downstream and
-(2) enrichment (Fig. \@ref(fig:matmet)). Enrichment was characterized by the
-average Biological Oxygen Demand [BOD, @mallin_factors_2006]. We further
+(2) enrichment [details in @danet_species_2021]. Enrichment was characterized by
+the average Biological Oxygen Demand [BOD, @mallin_factors_2006]. We further
 added a random effect of the hydrographic basin on the intercept.
 
-In order to control for the uncertainties of the estimated temporal trends, each
-temporal trend was weighted by the inverse of the sum of the standard deviation 
-of the estimated trends, i.e. estimated slopes for the response and the
-explicative variables ($w_j = \dfrac{1}{\sum{e_j}}$, $w_j$ being the
-weight, and $s_{e_j}$ the standard deviation on the temporal trends of the
-variables).
+In order to control for the uncertainties of the estimated temporal trends, we
+weighted each temporal trend by the inverse of the sum of the standard deviation
+of the estimated trends, i.e. the estimated slopes for the response and the
+explicative variables ($w_j = 1 / \sum{e_j}$, $w_j$ being the weight, and
+$s_{e_j}$ the standard deviation on the temporal trends of the variables).
 
@@
 PiecewiseSEM R package [@lefcheck_piecewisesem_2016]. The coefficients were
-standardizated and the confidence intervals were computed with semEff R package
-[@murphy_semEff_2021]. Confidence intervals were obtained by bootstrapping the
+standardized and the confidence intervals were computed with semEff R package
+[@murphy_semeff_2021]. Confidence intervals were obtained by bootstrapping the
 linear models 100 times and computing adjusted bootstrap percentile interval
-(BCa), which are adjusted for asymetric distribution of resampling. The marginal
-and conditional $R^2$ associated to the linear model of the SEMs were computed
-with the Nagelkerke method [@lefcheck_piecewisesem_2016].
+(BCa), which are adjusted for the asymmetric distribution of resampling. The marginal
+and conditional $R^2$ associated to the linear models of the SEMs were computed
+with the Nagelkerke method [@lefcheck_piecewisesem_2016, Fig. S5].
 
 All the statistical models displayed low multicollinearity (Variance inflation
-factors < 3, Table SXX).  We visually inspected the residuals of the linear
+factors < 3, Table S4). We visually inspected the residuals of the linear
 models.
@@
 
-We simulated extinction sequences in the metaweb according to three scenarios to get expectations on how the food-web structure should change according to the addition and deletion of species and nodes.
-The scenario of extinction sequences were related to the trophic level of the species/nodes.
-In the decreasing and increasing scenario, we removed species/nodes in decreasing, resp.
-increasing order, of their trophic level, i.e.
-respectively the higest and lowest trophic level first.
-In the random extinction sequence, we built 50 random extinction sequences.
-For each simulation, we removed fish species/nodes that lost all their preys.
-We computed the connectance, the average and the maximum trophic level.
+We simulated extinction sequences in the metaweb according to three scenarios to
+get expectations on how the food-web structure should change according to the
+addition and deletion of species and nodes. The scenario of extinction sequences
+were related to the trophic level of the species/nodes. In the decreasing and
+increasing scenario, we removed species/nodes in decreasing, resp. increasing
+order, of their trophic level, i.e. respectively beginning by the highest and
+lowest trophic level. In the random extinction sequence, we built 50 random
+extinction sequences. For each simulation, we removed fish species/nodes that
+lost all their preys. We then computed the connectance, the average and the
+maximum trophic level after each extinction.
 

### 2024-08-02 paper/manuscript.Rmd
Rewrite discussion

@@
 
-# Abstract (242 / 250 words max)
+# Abstract (240 / 250 words max)
 
-Understanding how biodiversity changes is a central question in ecology, but a
-challenging one because of the multidimensionality of biodiversity changes.
-Although the structure of ecological networks is a crucial determinant of
-community dynamics, this dimension of biodiversity changes have been greatly
-overlooked. One main reason is the scarce availability of the temporal series of
-ecological networks. Our knowledge of the relationships among structural
-properties of ecological networks comes mainly from spatial comparison, assuming
-a space-for-time equivalence, which have rarely tested. We questioned the
-relationships between the temporal changes of food-web structure and the ones of
-community biomass and species richness, and assessed if they differed from the
-ones estimated in space. We inferred the structure of using food diet and body
-size data from fish monitoring in France. We estimated the temporal trends of
-food-web structure in 400 sites using a hierarchical Bayesian model and then
-assessed the relationships among them using structural equation models. We found
-that temporal trends of connectance and average trophic level are positively
-related to ones of community biomass but surprisingly poorly related to the
-temporal trends of species richness, which resonates with the energetic paradigm
-of food-webs. We further found general support for the space-for-time hypothesis
-for community biomass, but not for species richness. Our study
-sheds a new light on the dynamics of food-web assemblage in natural settings and
-how the structure of ecological networks changes according to the changes of
-other biodiversity facets.
+Understanding food-web assembly processes is central to biological conservation
+and maintenance of ecosystem functions. In particular, temporal changes in
+community biomass and species richness are expected to significantly impact
+food-web structure but empirical assessments are lacking so far. Here, we
+investigate how temporal trends in species richness and community biomass affect
+temporal trends in food-web structure. To do so, we used more than 6000 sampled
+riverine fish community in 400 sites from french monitoring data. We inferred
+food-web structure for each sampling event, using diet data and body size. Using
+structural equation models, we estimated the effects of temporal changes in
+community biomass and species richness on temporal changes in food-web
+structure. We found that a positive effect of temporal trends in community
+biomass on the temporal trends of connectance and average trophic level, a
+result also found using spatial variations and a bioenergetic model. Temporal
+trends in species richness had a positive effect on average trophic level, but
+no effects on connectance. In space and in simulations, species richness had in
+contrast a negative effect on average trophic level and connectance. In sum, our
+study highlight that local temporal changes in biomass and species richness have
+contrasting effects on food-web structure. It further reveals that temporal
+changes and spatial variations in biomass lead to coherent food-web assembly
+patterns, in contrast to species richness. Our study sheds a new light on
+food-web assembly in natural settings.
 
@@
 
+*Introduce hypothesis and the food-web metrics (connectance and average trophic
+level)*
+
 # Results
@@
 tar_load(glob_tps_trends_decade_no_drivers)
-glob_tps_trends_decade_no_drivers
 gbm <- get_effect_ci(resp = "log_bm_std", ci_lvl = "level:0.80", p = TRUE)
@@
 r2_inla_report <- r2_inla %>%
-  select(response, r2_mvp_marg95hpdci, r2_mvp_cond95hpdci)
+  select(response, r2_mvp_marg95hpdci, r2_mvp_cond95hpdci, r2_mvp_cond_mean)
+r2cond <- map(
+  setNames(r2_inla_report$response, r2_inla_report$response),
+  ~round(r2_inla_report[r2_inla_report$response == .x, ]$r2_mvp_cond_mean, 2)
+)
 r2ic <- map(
@@
 
-Using a Bayesian hierarchical model to estimate conjointly the temporal trends of
-food-web structure at all sites, we found weak evidence of a global decrease in
-community biomass (CI80%:`r gbm` by decade; median [Credible Interval], Fig. S1) but of a
-global increase in species richness (CI80%: `r gr` by decade) across the `r nb_st` sites. 
-We did not find evidence of a global trends in connectance and average trophic
-level (CI80%: `r gct` and `r gt` respectively). The hierarchical model captured
-well the variance associated to the spatial structure of the data with
-conditional $R^2$ going from  `r r2ic$log_bm_std` (mean [CI95%]) for community
-biomass to `r r2ic$log_rich_std` for species richness (Table S1).
+```{r}
+dfv <- function(
+  x = summary_pred_station_tps10,
+  r = "ct_ff",
+  v = "min",
+  d = 4
+) {
+  out <- x[x$response == r, ][[v]]
+  format(round(out, d), nsmall = d)
+}
+grbmn <- dfv(r = "log_bm_std", v = "min", d = 0)
+grbmx <- dfv(r = "log_bm_std", v = "max", d = 0)
+grrhn <- dfv(r = "log_rich_std", v = "min", d = 0)
+grrhx <- dfv(r = "log_rich_std", v = "max", d = 0)
+grctn <- dfv(r = "ct_ff", v = "min", d = 2)
+grctx <- dfv(r = "ct_ff", v = "max", d = 2)
+grtln <- dfv(r = "w_trph_lvl_avg", v = "min", d = 2)
+grtlx <- dfv(r = "w_trph_lvl_avg", v = "max", d = 2)
+```
+
+Using a Bayesian hierarchical model to jointly estimate the temporal trends of
+food-web structure at all sites, we found weak evidence of an overall decrease
+in community biomass (CI80%:`r gbm` by decade; median [Credible Interval], Fig.
+S1) but a weak evidence of an overall temporal increase in species richness
+(CI80%: `r gr` by decade) across the `r nb_st` sites. We did not find evidence
+of average temporal trends in connectance and average trophic level (CI80%:
+`r gct` and `r gt` respectively). However, we found a great heterogeneity in the
+temporal trends estimated at the site level (community biomass: from `r grbmn`%
+to `r grbmx`% per decade, species richness: `r grrhn` to +`r grrhx`%, average
+trophic level: `r grtln` to +`r grtlx`, connectance: `r grctn` to +`r grctx`,
+Fig. S1) which was well captured by the hierarchical model with conditional R2
+going from `r r2cond$log_bm_std` for community biomass to `r r2cond$log_rich_std`
+for species richness (Table S1).
 
@@
 ```{r}
-tar_load(semeff_tot)
+tar_load(c(semeff_tot, semeff_tot_ok))
 semeff_tot <- semeff_tot %>%
   mutate(across(c(response, predictor), ~str_remove(.x, "mean_")))
+unique(semeff_tot_ok$predictor)
 
@@
     r = get_semeff_ci(resp = .x, term = "log_rich_std", model = "spatial")
+    )
+)
+rdm <- map(
+  setNames(
+    c("Connectance", "Avg trophic level", "Biomass"),
+    c("ct", "tlvl", "bm")
+    ),
+  ~ list(
+    bm = get_semeff_ci(x = semeff_tot_ok, type = "Direct", resp = .x, term = "Biomass", model = "Theoretical model"),
+    r = get_semeff_ci(x = semeff_tot_ok, type = "Direct", resp = .x, term = "Species richness", model = "Theoretical model")
     )
@@
 )
+ridm <- map(
+  setNames(
+    c("Connectance", "Avg trophic level", "Biomass"),
+    c("ct", "tlvl", "bm")
+    ),
+  ~ list(
+    bm = get_semeff_ci(x = semeff_tot_ok, type = "Indirect", resp = .x, term = "Biomass", model = "Theoretical model"),
+    r = get_semeff_ci(x = semeff_tot_ok, type = "Indirect", resp = .x, term = "Species richness", model = "Theoretical model")
+    )
+)
 rttps <- map(
@@
 )
+rtm <- map(
+  setNames(
+    c("Connectance", "Avg trophic level", "Biomass"),
+    c("ct", "tlvl", "bm")
+    ),
+  ~ list(
+    bm = get_semeff_ci(x = semeff_tot_ok, type = "Total", resp = .x, term = "Biomass", model = "Theoretical model"),
+    r = get_semeff_ci(x = semeff_tot_ok, type = "Total", resp = .x, term = "Species richness", model = "Theoretical model")
+    )
+)
 ```
 
-Using structural equation models to disentangle the direct and indirect
-relationships among food-web structure descriptors, we found a strong positive
-relationship between the temporal trends of community biomass and of
-species richness ($r_\delta =$ `r rdtps$bm$r`, Fig. \@ref(fig:sem) a and b,
-$r_\delta$: standardized slope coefficient, [95% CI]), meaning that both
-temporal trends had the same direction in average. At the sites where species
-richness decreased over time, community biomass also decreased over time. On the
-other hand, at the sites where species richness increased over time, community
-biomass also increased over time.
+Using structural equation models to disentangle the direct and indirect effects
+of temporal trends in fish species richness and community biomass on temporal
+trends in food-web structure, we found a strong positive effect of the temporal
+trends in species richness on community biomass ($r_\delta =$ `r rdtps$bm$r`,
+Fig. \@ref(fig:sem) a and b, $r_\delta$: standardized slope coefficient, [95%
+CI]), meaning that both temporal trends had the same direction in average. In
+other word, food-webs that have experienced a decrease in species richness over
+time have decreased in community biomass, and conversely, those that increased
+in species richness have increased in community biomass.
+Temporal trends in community biomass had in turn a positive effect on connectance and
+average trophic level (resp. $r_\delta =$ `r rdtps$ct$bm` and `r rdtps$tlvl$bm`,
+Fig. \@ref(fig:sem)a, c, e), meaning that food-web whose community biomass
+decreased over time have decreased in connectance and average trophic level, and
+conversely, those that have experienced an increase in biomass have increased in
+connectance and average trophic level. We further found that the temporal
+trends of community biomass were positively associated to the temporal trends of
+both number and proportion of piscivorous species present (Fig. S3a), meaning
+biomass trends are linked to the presence of high trophic level trophic
+species.
 
-The temporal trends of connectance were positively linked with the ones of
-community biomass ($r_\delta =$ `r rdtps$ct$bm`), also meaning that both
-temporal trends had the same direction in average. That is, the sites where
-food-web connectance decreased over time also had community biomass that
-decreased over time and reversely. It suggests that communities that decreased
-in biomass over time lose highly connected trophic species over time, and
-reversely that communities gaining biomass over time also gain highly connected
-trophic species over time. We found a negative relationship between the temporal
-trends of connectance and the ones of species richness
-($r_\delta =$ `r rdtps$ct$r`, Fig. \@ref(fig:sem)d). We further found the
-species richness had an indirect positive effect on connectance, through
-community biomass ($r_\delta =$ `r ridtps$ct$r`). It resulted in a relatively
-weak total negative effect of species richness on connectance
-($r_\delta =$ `r rttps$ct$r`), that we also found in random extinction
-simulation (Fig. S2).
+We further tested if we find the same patterns using spatial variations in
+food-web structure rather than temporal changes over time, i.e. if the
+space-for-time hypothesis hold. To do so, we used the same dataset and same
+structural equation model but with the median food-web structure per site
+instead of the temporal trends. We additionally performed theoretical
+simulations with a bioenergetic food-web model to further get theoretical
+expectations about how food-web structure changes according to community biomass and
+species richness variations (see Methods). As in temporal data, species richness
+had a positive effect on community biomass both in empirical data and in
+theoretical simulations (resp. $r_\delta =$ `r rdsp$bm$r` and `r rdm$bm$r`, Fig.
+\@ref(fig:std)). In both empirical data and theoretical simulations, community
+biomass had a positive effect on connectance (resp. $r_\delta =$ `r rdsp$ct$bm`
+and `r rdm$ct$bm`, Fig. \@ref(fig:std)) and average trophic level (resp.
+$r_\delta =$ `r rdsp$tlvl$bm` and `r rdm$tlvl$bm`), as in temporal analysis.
 
-The temporal trends of average trophic level had a strong positive relationship
-with the ones of community biomass ($r_\delta =$ `r rdtps$tlvl$bm`, Fig.
-\@ref(fig:sem)e), meaning that sites where community biomass decreased over
-time, average trophic level decreased over time and reversely. It means that in
-communities losing biomass over time, the average biomass of the food-web moved
-down to lower trophic level and vice versa. However, we found that the temporal
-trends of average trophic level had no direct relationship the ones of species
-richness ($r_\delta =$ `r rdtps$tlvl$r`, Fig. \@ref(fig:sem)f). It suggests that
-in communities either losing or gaining species richness over time, the location
-of average biomass along trophic level does not significantly change according
-to species richness. However, the temporal trends of species richness had an
-indirect positive relationship with the temporal trends of average trophic level
-through community biomass ($r_\delta =$ `r ridtps$tlvl$r`), resulting in a total
-positive relationship ($r_\delta =$ `r rttps$tlvl$r`).
+The effects of species richness were more complex, because species richness had
+indirect effects on food-web structure through community biomass. Temporal
+trends in species richness had a direct negative effect on connectance
+($r_\delta =$ `r rdtps$ct$r`, Fig. \@ref(fig:sem)d), but had also a positive
+indirect effect through community biomass ($r_\delta =$ `r ridtps$ct$r`), so
+that species richness temporal trends had no effect in total on temporal in
+connectance ($r_\delta =$ `r rttps$ct$r`, Fig. \@ref(fig:sem)d).
+In contrast, temporal trends in species had no direct effects on the temporal
+trends in average trophic level ($r_\delta =$ `r rdtps$tlvl$r`, Fig.
+\@ref(fig:sem)f), however it had a positive indirect effect through community
+biomass ($r_\delta =$ `r ridtps$tlvl$r`). It means food-webs that have
+experienced a decrease in species richness over time have decreased in average
+trophic level, and conversely, those that increased in species richness have
+increased in average trophic level, through community biomass. Furthermore, we
+found that temporal trends of the proportion of piscivorous species was
+negatively associated with the temporal trends of species richness (Fig. S3),
+meaning that communities that increase in richness over time have an increase in
+the proportion of non-piscivorous species over time and vice versa.
+
+The effects of spatial variations in species richness on food-web structure
+contrasts with the ones found with temporal trends. We found a direct negative
+effect of species richness on connectance both using data and model simulations
+(resp. $r_\delta =$ `r rdsp$ct$r` and `r rdm$ct$r`, Fig. \@ref(fig:std)) and on
+average trophic level (resp. $r_\delta =$ `r rdsp$tlvl$r` and `r rdm$tlvl$r`).
+Despite indirect positive effect of species richness through community biomass,
+species richness had strong total negative effects on connectance in empirical
+data and simulations (resp. $r_\delta =$ `r rtsp$ct$r` and `r rtm$ct$r` ) and
+average trophic level (resp. $r_\delta =$ `r rtsp$tlvl$r` and `r rtm$tlvl$r`).
+
+We performed extinction simulations scenario on the metaweb, the food-web
+including all the species and nodes found in the empirical data, to better
+understand how species richness change affect food-web structure. When species
+are removed in a sequential order beginning by the highest trophic levels,
+connectance and average trophic level decreased as we removed species (red
+lines, Fig. S2a). At the opposite, removing first low trophic level species first
+increase connectance and average trophic level (green lines, Fig. S2a). In turn,
+random species extinction sequence had little effect on food-web structure
+(black lines, Fig. S2a).
 
@@
 
-As for the temporal analysis, we found a positive relationship between
-median community biomass and median species richness along the spatial gradient,
-but half the strength as the temporal one ($r_\delta =$ `r rdsp$bm$r`, Fig.
-\@ref(fig:std)). We further found a positive relationship between median
-connectance and median community biomass ($r_\delta =$ `r rdsp$ct$bm`), as in
-temporal trends analysis. However, we found a negative relationship between
-median connectance and median species richness, but
-three times stronger than in the temporal analysis ($r_\delta =$ `r rdsp$ct$r`,
-Fig. \@ref(fig:std)). We also found a positive indirect effect of median
-richness on median connectance through median community biomass but a weak one
-($r_\delta =$ `r ridsp$ct$r`), resulting in a strong negative total effect of
-median richness on median connectance ($r_\delta =$ `r rtsp$ct$r`).
-
-We found a positive relationship between median average trophic level and median
-community biomass, but half the strength as in the temporal analysis ($r_\delta
-=$ `r rdsp$tlvl$bm`, Fig. \@ref(fig:std)). However, we found a strong negative
-relationship between median average trophic level and median richness ($r_\delta
-=$ `r rdsp$tlvl$r`), in contrast with findings in temporal analysis. We also
-found a positive indirect relationship between average trophic level and  median
-richness through median community biomass (`r ridsp$tlvl$r`), resulting in a
-strong total negative effect of median richness on median average trophic level
-(`r rtsp$tlvl$r`).
-
 # Discussion
 
+We found remarkable heterogeneity in community biomass and species richness
+changes over the last decades in riverine fish communities, linked to changes in
+food-web structure. Community biomass changes spanned from `r grbmn`% to `r
+grbmx`% per decade, species richness from `r grrhn`% to +`r grrhx`% per decade,
+in line previous reports of the heterogeneity of local biodiversity changes in
+terrestrial, marine and freshwater realms[@dornelas_assemblage_2014;
+@blowes_geography_2019; @danet_past_2024]. In turn, connectance temporal changes
+spanned from `r grctn` to +`r grctx` per decade and average trophic level, from
+`r grtln` to +`r grtlx` per decade. We questioned the effects of community
+biomass and species richness changes over time on temporal changes in food-web
+structure, that we also tested across space and with simulations using a
+bioenergetic food-web model. We found positive effects of species richness
+changes on changes in community biomass that were consistent across temporal and
+spatial analysis and with the theoretical model. The effects of community
+biomass changes on food-web structure were also consistent across analysis,
+suggesting that loss of community biomass are linked to the loss of the trophic
+species of high trophic level. However, changes in species richness had
+contrasting effects on food-web structure depending on the type of analysis,
+temporal or spatial and theoretical simulations. It suggests that food-web
+structure changes induced by changes in species richness differs from the one
+induced by the changes in community biomass, and that they imply different
+processes across time and space. In what follows, we discuss how changes
+in community biomass and species richness changes over time and space are
+related to food-web assembly and disassembly processes.
+
 We found that species richness scaled positively with community biomass, both in
-spatial and temporal analysis. This result is in accordance with previous
+temporal, spatial and theoretical simulations, in accordance with previous
 analysis across space in stream communities [@woods_testing_2020;
@@
 [@hector_plant_1999; @tilman_biodiversity_2014; @wu_relationship_2015;
-@li_relationship_2018; but see @grace_integrative_2016]. Therefore, our results
-suggest that Biodiversity-Ecosystem functioning prediction also hold in the
-temporal dynamics of food-webs. The positive relationship between species
-richness and total biomass might be due to positive complementarity in resource
-use [@carey_determining_2011], which is held by niche differentiation
-[@loreau_biodiversity_1998; @loreau_partitioning_2001] or to the higher
-probability of getting high biomass species with higher species
-richness [@loreau_biodiversity_2001].
+@li_relationship_2018; but see @grace_integrative_2016]. This results is in
+agreement with previous findings showing that food-web diversity can increase
+biomass by stimulating primary production and resource uptake
+[@wang_biodiversity_2018]. Our results suggest that food-web losing species
+richness over time also experience a loss of biomass, while those gaining
+species experience a increase in community biomass. This results is coherent the
+Biodiversity-Ecosystem Functioning theory [@loreau_biodiversity_2001;
+@wang_biodiversity_2018], and suggest that the loss of species richness and
+biomass might impair ecosystem functioning.
 
-Our results suggest that the disturbances that lead to decline or increase of
-community biomass over time are concomitant to the decline and increase
-respectively of trophic species at high trophic level. We found that both
-connectance and average trophic level had a positive relationship with community
-biomass over time, meaning that connectance and average trophic level increase
-over time when community biomass increases over time as well, and likewise that
-connectance and average trophic level decrease over time when community biomass
-decreases over time. We also found that the temporal trends of connectance and
-average trophic level were strongly correlated (Fig. S3). Likewise, we found
-that the temporal trends of community biomass were positively associated to the
-temporal trends of both number and proportion of piscivorous species
-present (Fig. S3). This result is in accordance with the
-energetic paradigm of food-webs which proposes that food-webs are primarily
-constrained by fluxes of matter and energy [@lindeman_trophic-dynamic_1942],
-which suggest that productivity constraints food chain length by energy
-limitation [@jenkins_productivity_1992; @takimoto_ecosystem_2008]. Higher
-trophic levels have been shown to be more sensible to ecosystem size
-[@takimoto_ecosystem_2008; @post_ecosystem_2000], to resource availability and
-disturbance in small systems [@post_long_2002] and particularly to disturbance
-in hydrologic regimes in streams [@sabo_role_2010; @mchugh_dual_2010;
-@jake_vander_zanden_global_2007]. In the same line, the metabolic theory of
-ecology also predicts that top predators are highly constrained by energy
-limitation [@arim_relationship_2007]. However, this interpretation holds if
-the temporal trends of community biomass are related to the quantity of resource
-available. Another explanation can be that top trophic level species are often
-the ones that are targeted, harvested and those that are artificially introduced
-for recreational fisheries [@reid_emerging_2019]. Further investigations on the
-drivers of community biomass decline and increase over time would be needed to
-further conclude.
+Our results suggest that food-web that have undergone a biomass decline
+experienced a loss of top trophic levels species and connectance, those gaining
+biomass experienced a gain in top trophic levels and connectance. Importantly,
+the same results were found using spatial comparison and theoretical models.
+This results can be linked with the energetic and trophic biogeography theories
+[@lindeman_trophic-dynamic_1942; @gravel_trophic_2011], which posits that the
+presence of top predators is limited by the amount of energy and
+resource available [@lindeman_trophic-dynamic_1942, @takimoto_ecosystem_2008;
+@post_ecosystem_2000; @post_long_2002]. Thereby, a decrease in community biomass
+can limit the amount of resource available to sustain top predators, while
+increase in community biomass may result in more resource available for top
+predators [@takimoto_ecosystem_2008; @post_ecosystem_2000].
 
-In contrast, we found that the temporal trends of connectance was negatively
-related to the temporal trends of species richness, in accordance with the
-strong negative relationships that we found in the present study and from
-previous results over spatial gradient [@dunne_network_2006;
-@danet_species_2021]. Furthermore, we found that temporal trends of the
-proportion of piscivorous species was negatively associated with the temporal
-trends of species richness (Fig. S3), meaning that communities that increase in
-richness over time have an increase in the proportion of non-piscivorous species over time
-and vice versa. This result is in accordance with a meta-analysis showing the
-number of species by trophic level decrease toward higher trophic level
-[@turney_pyramids_2016]. It suggests that the temporal increase of species
-richness found in our dataset is associated with a decrease of connectance
-because species richness increases are biased toward non-piscivorous species
-which have no piscivory links. We also found that the changes of average trophic
-level over time were not related to the changes of species richness over time.
-All together, an explanation can be that species richness changes over time,
-without changes in community biomass, are more linked to non piscivorous species
-having lower trophic level and relatively low biomass, which results in negative
-relationships with temporal trends in connectance and no relationship with
-average trophic level.
+Species richness temporal changes were positively associated to changes in average
+trophic level, such as food-webs that have suffered a decline in species richness
+have experienced a concomitant decline in average trophic level, those have seen
+an increase in species richness have experienced an increase in average trophic
+level. However, the effect of species richness temporal trends on average
+trophic level were twice lower than the one of community biomass, and had no
+effects on connectance temporal changes. Altogether, it suggests that species
+richness increase and decrease were less clearly linked to specific changes in
+food-web structure. Species richness temporal trends could be more linked to
+changes in the redundancy of trophic roles in the food-webs, such as it has
+little effects of food-web structure but increases its community biomass. This
+interpretation align with the insurance hypothesis [@yachi_biodiversity_1999;
+@loreau_biodiversity_2021], such as species richness and associated redundancy
+in species roles can increase ecosystem stability by buffering the impacts of
+perturbations [@sanders_trophic_2018].
 
-Our findings further suggest that species richness and community biomass have
-antagonistic effects on connectance, respectively negative and positive. As we
-found a strong positive relationship between the temporal trends of species
-richness and community biomass, it results that species richness temporal trends
-had an indirect positive effect on the temporal trends of both connectance and
-average trophic level via community biomass. Then,  The temporal trends of
-species richness had then a total effect on the temporal trends of connectance
-and average trophic level which was twice lower than the one of the temporal
-trends of community biomass. It suggests that the temporal assembly and
+When considering spatial analysis and model simulations, species richness
+effects on food-web structure were highly distinct from the temporal analysis.
+Spatial analysis and theoretical models suggest that increase in species
+richness results in lower connectance and average trophic level, a well known
+patterns in empirical food-web [@dunne_network_2006; @danet_species_2021]. This
+result is also in line with other studies which found a mismatch between spatial
+and temporal trends [@adler_contrasting_2007; @johnson_testing_2008]. This
+discrepancy in space and time is due to the strong assumption that variations in
+space reflect differences in assembly stages of ecological communities and then
+mirror their temporal assembly/disassembly trajectories. Temporal changes in
+species richness might relate to short-term dynamics while spatial gradients
+reflect aggregated dynamics over a longer time scale including a far number of
+processes including high species turnover along spatial gradients. Our results
+then suggest community biomass changes in space might be a good surrogate to
+infer assembly and disassembly of food-web in time, but that it is probably not
+the case for species richness.
+
+*Final message*
+
+It suggests that the temporal assembly and
 disassembly of food-webs are more sensitive to variations in community biomass
@@
 
-As studies reported community biomass or species richness temporal trends
-[@hallmann_more_2017; @ceballos_biological_2017; @dornelas_assemblage_2014;
-@blowes_geography_2019], we document that temporal trends of species richness
-and community biomass might have different consequences on the structure of the
-community. In particular, the decrease of the average trophic level associated
-to the loss of community biomass could have cascading effect on ecosystem
-functioning as the highest predators are predicted to increase productivity and
-stabilize communities [@wang_biodiversity_2018; @shanafelt_stability_2018;
-@danet_species_2021]. In contrast, the loss of species richness might be linked
-to loss of redundancy in the food-web, highlighting that those communities may
-become more at risk regarding future perturbations [@yachi_biodiversity_1999].
-Interestingly, the hypothesis that temporal trends in community biomass is
-related to species of higher trophic level in our system has a strong reasoning
-with the effect of human fisheries in marine systems which affect primarily fish
-species at top trophic levels [@sprules_surfing_2016].
-
-We found evidence that space-for-time substitution is valid for community
-biomass but not for species richness. More specifically, we found a positive
-relationship between community biomass and species richness both in space and
-time. We also found that connectance was positively linked to community biomass
-both over space and time, it resonates with theoretical studies showing that
-higher food-web connectance can result in higher community biomass
-[@thebault_food-web_2003], or lower [@poisot_trophic_2013] over space,
-highlighting that the relation between connectance and community biomass may be
-dependent on how food-web structure change with community biomass over space and
-time. Likewise, we found that the average trophic level had a positive
-relationship with community biomass over space and time, in accordance with a
-theoretical study predicting an increase of community biomass
-linked to the presence of higher predators [@wang_biodiversity_2018].
-However, while we found a total negative effect between connectance and species
-richness in space, in accordance with previous findings over space in
-empirical food-webs [@dunne_network_2006; @danet_species_2021], we found a null
-total effect in time. The result is even more contrasting for average trophic
-level, where we found a total positive effect of species richness in time but a
-negative one in space. This result is also in line with other studies which
-found a mismatch between spatial and temporal patterns [@adler_contrasting_2007;
-@johnson_testing_2008]. This discrepancy in space and time might be due to the
-strong assumption that variations in space reflect differences in assembly
-stages of ecological communities and then mirror their temporal
-assembly/disassembly trajectories. Temporal variation of species richness might
-relate to transitory dynamics while spatial gradients reflect aggregated
-dynamics over a longer time scale including a far number of processes including
-high species turnover along spatial gradients. Our results then suggest that food-web
-structure comparison along space gradient might be a reasonable surrogate for
-time sequence, it is probably not the case for species richness spatial
-comparison.
-
 ## Conclusion and perspectives
 
-Our study suggests that species richness and community biomass temporal trends
-in natural fish communities relate on different ecological processes. Biomass
-changes in time are related to variations of food-web structure at the
-higher trophic levels while changes in species richness are weakly related to
-changes in food-web structure, in accordance with the energetic
-paradigm of food-webs. Our results further highlight that the effects of species
-richness changes on food-web structure are strongly mediated by antagonistic
-effects of community biomass. We also find evidences which suggest that
-space-for-time substitution may be relevant to predict the effects of community
-biomass losses or gains on food-web structure but also that space-for-time
-substitution might not work for species richness. Our study calls for further
-investigations to support the generality of assembly rules in food-webs,
-according to changes in community biomass and species richness. They are crucial
-to better understand how biodiversity changes will affect community dynamics
-and ecosystem functioning.
+We investigated how food-web assemble and disassemble according to changes in
+community biomass and species richness. Our study shows that temporal changes in
+community biomass induced changes in food-web structure, such as decline in
+biomass translates in food-webs with fewer trophic links and top predators while
+increases in biomass results in food-webs with more trophic links and top
+predators. Species richness temporal trends translate in low changes in food-web
+structure, suggesting that species richness changes relates more to trophic role
+redundancy than in changes in food-web structure. Using replicating the analysis
+over spatial gradient and with a theoretical model, our study shows that
+community biomass changes over space and theoretical model results in the same
+changes in food-web structure than in temporal analysis, which is not the case
+for species richness. It suggests that using space-for-time substitution to
+infer assembly and disassembly processes in food-web structure works well for
+community biomass and not species richness.
+
+In the context of biodiversity crisis, our study reveals that declines of
+community biomass results in food-web downgrading. As species of top trophic
+levels plays a great role in ecosystem functioning [@estes_trophic_2011;
+@wang_biodiversity_2018; @thebault_food-web_2003], it raises concerns about the
+functioning of such degraded ecosystems. Loss of species richness in turn did
+not affect significantly food-web structure, suggesting that it implies loss of
+redundancy in trophic roles. As redundancy has a key role in buffering ecosystem
+variability against perturbations [@sanders_trophic_2018;
+@yachi_biodiversity_1999], it raises concerns about the stability of such
+food-webs. We used here empirical freshwater food-web inferred from in-situ fish
+bodysize and diet [@danet_species_2021; @bonnaffe_comparison_2021], which do not
+account for the variability in invertebrates and primary producers presences,
+and do not a number of processes such as changes in interaction strengths.
+However, the theoretical model embedding complete food-webs showed remarkably
+similar results to the empirical data.
+
+Our study opens stimulating perspectives to further understand of biodiversity
+changes alters community structure and ecosystem functioning. It is particularly
+needed for ecological networks, whose structure has tremendous effects on
+ecosystem functioning and stability. It implies to further investigate which
+processes drive the differences in the effects of species richness
+changes on food-web structure in space and time.
 

### 2024-08-02 R/variable_shortcut.R

@@ -11,7 +11,7 @@ get_richness_var <- function (all = FALSE) {
 
   x <- c("log_rich_std")
   if (all) {
-    x <- c(x, "rich_std", "richness", "log_rich") 
+    x <- c(x, "rich_std", "richness", "log_rich")
   }
   return(x)
 }
@@ -71,14 +71,16 @@ get_com_str_var <- function (all = FALSE) {
 get_model_terms <- function ( ) {
   c("bm_slope", "inc_f", "bm", "log_bm")
 
-} 
+}
 
 var_replacement <- function (slope = FALSE, several_lines = FALSE) {
   x <- c(
     log_RC1 = "PCA Avg stream size",
     log_RC2 = "PCA Avg temperature",
     ct_ff = "Connectance",
+    ct = "Connectance",
     avg_tl_ff = "Avg trophic level",
+    tlvl = "Avg trophic level",
     max_tl_ff = "Max trophic level",
     w_trph_lvl_avg = "Avg trophic level",
     #connectance ,weighted_connectance,
@@ -86,11 +88,14 @@ var_replacement <- function (slope = FALSE, several_lines = FALSE) {
     log_bm_std = "Biomass",
     bm_std = "Biomass (g.m^-2)",
     rich_std = "Species richness (m^-2)",
+    log_final_richness = "Species richness",
     piel_nind = "Evenness (abundance)",
     piel_bm = "Evenness (biomass)",
     prop_pisc_node = "Piscivorous node prop.",
     prop_pisc_rich = "Piscivorous rich prop.",
     biomass = "Biomass (g)",
+    bm = "Biomass",
+    log_total_bm = "Biomass",
     biomass_kg = "Biomass (kg)",
     richness = "Species richness",
     nbnode = "Nb of nodes",

### 2024-08-06 paper/appendix.Rmd
Finalise manuscript preparation
Add redundancy + update fig & tables

--- 2022-11-06 paper/appendix.Rmd
@@
   fig.fullwidth = TRUE,
-  fig.show = "hold",
+  fig.pos = "H",
   echo = FALSE,
@@
 ```
-```{r}
-var_analysis <- c("ct_ff", "w_trph_lvl_avg", "log_rich_std", "log_bm_std")
-```
 
 \beginsupplement
-\newpage
 
-```{r}
-tar_load(tab_inla_r2_rand)
-kable(tab_inla_r2_rand,
-  row.names = FALSE,
-  booktabs = T,
-  caption = "Marginal and Conditional R-squared for the INLA models estimating
-  the temporal trends of the food-web structure. The table also displays the
-  standard deviation associated to the random effects and the general error of
-  the models. Confidence interval at 95\\% are displayed between square brackets.",
-  label = "inlarsq") %>%
-  collapse_rows(columns = c(1, 2, 3), valign = "top") %>%
-  kable_styling(latex_options = c("scale_down"))
-```
+# Supplementary figures
 
@@
 ```{r}
-tar_load(tabvif)
-kable(tabvif,
+sem_sp_mod_cap <- "Direct effects of biomass and species richness on food-web
+structure, derived from the structural equation models for the (a) spatial and
+(b) bioenergetic model. Points display the data, black lines display the
+predicted relationships."
+
+```
+
+```{r, fig.cap=sem_sp_mod_cap, out.width = "100%"}
+tar_load(p_sem_sp_sim_file)
+knitr::include_graphics(p_sem_sp_sim_file)
+```
+
+\pagebreak
+
+# Supplementary tables
+
+```{r}
+tar_load(r2_inla_tab)
+kable(r2_inla_tab,
   row.names = FALSE,
   booktabs = T,
-  caption = "Variance Inflation Factor for the more complex linear models
-  included in the Structural Equation Models.",
-  label = "vif",
+  caption = "Marginal and Conditional R-squared for the INLA models estimating
+  the temporal trends of the food-web structure. Mean [95\\% Credible Interval].",
+  label = "inlarsq") %>%
+  kable_styling()
+```
+
+```{r}
+tar_load(c(op_table, com_metric_tab))
+tab_quanti <- purrr::map_dfr(
+  list(com_metric_tab, op_table),
+  function(x) {colnames(x)[1] <- "Variable"; x}
 )
+tab_quanti %>%
+  kbl(
+    caption = "Summary distribution of community metrics and fish monitoring variables.",
+    booktabs = T
+    ) %>%
+  kable_styling() %>%
+  pack_rows("Community metrics", 1, 8) %>%
+  pack_rows("Summary of fish monitoring", 9, 13)
+```
+
+```{r}
+tar_load(tab_inla_rand)
+tab_inla_rand %>%
+  mutate(Response = factor(Response, levels = unique(var_replacement()))) %>%
+  arrange(Response) %>%
+  kable(
+    row.names = FALSE,
+    booktabs = T,
+    caption = "Standard deviation associated to the random effects and the residual error of
+    the models. Mean [95\\% Credible Interval].",
+    label = "inlarand") %>%
+  collapse_rows(columns = c(1), valign = "top") %>%
+  kable_styling()
+```
+
+```{r}
+tar_load(semeff_tot_tab)
+ti <- semeff_tot_tab %>%
+  pivot_wider(names_from = "Effect type", values_from = "Effect") %>%
+  mutate(Response = factor(Response, levels = unique(var_replacement()))) %>%
+  arrange(Model, Response)
+kable(ti %>%
+    select(-Model),
+  row.names = FALSE,
+  booktabs = T,
+  caption = "Direct and total Standardized effects derived from the structural
+  equation models. [95\\% Confidence Interval]. The confidence intervals were
+  obtained with bootstrap (see Methods).") %>%
+  collapse_rows(columns = c(1), valign = "top") %>%
+  pack_rows(index = table(ti$Model))
 ```
@@
 tar_load(r2_sem_tab)
-kable(r2_sem_tab,
+kable(r2_sem_tab %>%
+  mutate(
+    Type = factor(Type, levels = effect_type_var()),
+    Response = factor(Response, levels = unique(var_replacement()))
+    ) %>%
+  arrange(Type, Response),
   row.names = FALSE,
@@
 ```{r}
-tar_load(c(pca_table, op_table, com_metric_tab))
-tab_quanti <- purrr::map_dfr(
-  list(com_metric_tab, op_table, pca_table),
-  function(x) {colnames(x)[1] <- "Variable"; x}
+tar_load(tabvif)
+kable(tabvif,
+  row.names = FALSE,
+  booktabs = T,
+  caption = "Variance Inflation Factor for the more complex linear models
+  included in the Structural Equation Models.",
+  label = "vif",
   )
-#purrr::map_int(list(com_metric_tab, op_table, pca_table), nrow)
-
-tab_quanti %>%
-  kbl(
-    caption = "Summary distribution of community metrics, fish monitoring and of
-    environmental variables used in the PCA for the spatial SEM.",
-    booktabs = T
-    ) %>%
-  kable_styling() %>%
-  pack_rows("Community metrics", 1, 8) %>%
-  pack_rows("Summary of fish monitoring", 9, 12) %>%
-  pack_rows("Summary of Envionmental variables", 13, 26)
 ```

### 2024-08-06 paper/manuscript.Rmd
Add redundancy + update fig & tables

@@
 gt <- get_effect_ci(resp = "w_trph_lvl_avg", ci_lvl = "level:0.80", p = FALSE)
-gct <- get_effect_ci(resp = "ct_ff", ci_lvl = "level:0.80", p = FALSE)
+gct <- get_effect_ci(resp = "connectance", ci_lvl = "level:0.80", p = FALSE)
+gl <- get_effect_ci(resp = "prop_redundant_links", ci_lvl = "level:0.80", p = FALSE)
 ```
@@
 ```{r}
+tar_load(summary_pred_station_tps10)
 dfv <- function(
   x = summary_pred_station_tps10,
-  r = "ct_ff",
+  r = "connectance",
   v = "min",
@@
 grrhx <- dfv(r = "log_rich_std", v = "max", d = 0)
-grctn <- dfv(r = "ct_ff", v = "min", d = 2)
-grctx <- dfv(r = "ct_ff", v = "max", d = 2)
+grctn <- dfv(r = "connectance", v = "min", d = 2)
+grctx <- dfv(r = "connectance", v = "max", d = 2)
 grtln <- dfv(r = "w_trph_lvl_avg", v = "min", d = 2)
 grtlx <- dfv(r = "w_trph_lvl_avg", v = "max", d = 2)
+grln <- dfv(r = "prop_redundant_links", v = "min", d = 2)
+grlx <- dfv(r = "prop_redundant_links", v = "max", d = 2)
 ```
@@
 in community biomass (CI80%:`r gbm` by decade; median [Credible Interval], Fig.
-S1) but a weak evidence of an overall temporal increase in species richness
+S1) but no evidence of an overall temporal increase in species richness
 (CI80%: `r gr` by decade) across the `r nb_st` sites. We did not find evidence
 of average temporal trends in connectance and average trophic level (CI80%:
-`r gct` and `r gt` respectively). However, we found a great heterogeneity in the
-temporal trends estimated at the site level (community biomass: from `r grbmn`%
-to `r grbmx`% per decade, species richness: `r grrhn` to +`r grrhx`%, average
-trophic level: `r grtln` to +`r grtlx`, connectance: `r grctn` to +`r grctx`,
-Fig. S1) which was well captured by the hierarchical model with conditional R2
-going from `r r2cond$log_bm_std` for community biomass to `r r2cond$log_rich_std`
-for species richness (Table S1).
+`r gct` and `r gt` respectively), but an increase in redundancy (measured by the
+proportion of redundant links, CI80%: `r gl`). However, we found a great
+heterogeneity in the temporal trends estimated at the site level (community
+biomass: from `r grbmn`% to `r grbmx`% per decade, species richness: `r grrhn`
+to +`r grrhx`%, average trophic level: `r grtln` to +`r grtlx`, connectance: `r
+grctn` to +`r grctx`, redundancy: `r grln` to +`r grlx`, Fig. S1) which was well
+captured by the hierarchical model with conditional R2 going from `r r2cond$log_bm_std` for community biomass to `r r2cond$log_rich_std` for species
+richness (Table S1).
 
@@
 coefficients. The standardized slope coefficients and their associated 95%
-confidence intervals are displayed along the path. The marginal R-squared of the
-linear models are displayed. (b to f) Direct bivariate relationships derived
-from the structural equation model. The distribution of the site temporal trends
-are displayed in Fig. S1."
+confidence intervals obtained by bootstrapping are displayed along the path. The
+marginal R-squared of the linear models are displayed. (b to f) Direct bivariate
+relationships derived from the structural equation model. The distribution of
+the site temporal trends are displayed in Fig. S1. All the effects are reported
+in Table S4."
 ```
@@
   mutate(across(c(response, predictor), ~str_remove(.x, "mean_")))
-unique(semeff_tot_ok$predictor)
 
@@
   setNames(
-    c("ct_ff", "w_trph_lvl_avg", "log_bm_std"),
-    c("ct", "tlvl", "bm")
+    c("connectance", "w_trph_lvl_avg", "log_bm_std", "prop_redundant_links"),
+    c("ct", "tlvl", "bm", "red")
     ),
@@
   setNames(
-    c("Connectance", "Avg trophic level", "Biomass"),
-    c("ct", "tlvl", "bm")
+    c("Connectance", "Avg trophic level", "Biomass", "Redundancy"),
+    c("ct", "tlvl", "bm", "red")
     ),
@@
 in species richness have increased in community biomass.
-Temporal trends in community biomass had in turn a positive effect on connectance and
-average trophic level (resp. $r_\delta =$ `r rdtps$ct$bm` and `r rdtps$tlvl$bm`,
-Fig. \@ref(fig:sem)a, c, e), meaning that food-web whose community biomass
-decreased over time have decreased in connectance and average trophic level, and
+Temporal trends in community biomass had in turn a positive effect on connectance,
+average trophic level, and redundancy (resp. $r_\delta =$ `r rdtps$ct$bm`,
+`r rdtps$tlvl$bm`, `r rdtps$red$bm`, Fig. \@ref(fig:sem)b, c, d), meaning that
+food-web whose community biomass decreased over time have decreased in
+connectance, average trophic level and redundancy, and
 conversely, those that have experienced an increase in biomass have increased in
-connectance and average trophic level. We further found that the temporal
+connectance, average trophic level and redundancy. We further found that the temporal
 trends of community biomass were positively associated to the temporal trends of
@@
 theoretical simulations (resp. $r_\delta =$ `r rdsp$bm$r` and `r rdm$bm$r`, Fig.
-\@ref(fig:std)). In both empirical data and theoretical simulations, community
+\@ref(fig:std) and S5). In both empirical data and theoretical simulations, community
 biomass had a positive effect on connectance (resp. $r_\delta =$ `r rdsp$ct$bm`
-and `r rdm$ct$bm`, Fig. \@ref(fig:std)) and average trophic level (resp.
-$r_\delta =$ `r rdsp$tlvl$bm` and `r rdm$tlvl$bm`), as in temporal analysis.
+and `r rdm$ct$bm`, Fig. \@ref(fig:std)), average trophic level (resp.
+$r_\delta =$ `r rdsp$tlvl$bm` and `r rdm$tlvl$bm`), and redundancy (resp.
+$r_\delta =$ `r rdsp$red$bm` and `r rdm$red$bm`), as in temporal analysis.
 
@@
 trends in species richness had a direct negative effect on connectance
-($r_\delta =$ `r rdtps$ct$r`, Fig. \@ref(fig:sem)d), but had also a positive
+($r_\delta =$ `r rdtps$ct$r`, Fig. \@ref(fig:sem)f), a positive
 indirect effect through community biomass ($r_\delta =$ `r ridtps$ct$r`), so
-that species richness temporal trends had no effect in total on temporal in
-connectance ($r_\delta =$ `r rttps$ct$r`, Fig. \@ref(fig:sem)d).
+that species richness temporal trends had a negative effect in total on temporal in
+connectance ($r_\delta =$ `r rttps$ct$r`, Fig. \@ref(fig:std)).
 In contrast, temporal trends in species had no direct effects on the temporal
 trends in average trophic level ($r_\delta =$ `r rdtps$tlvl$r`, Fig.
-\@ref(fig:sem)f), however it had a positive indirect effect through community
-biomass ($r_\delta =$ `r ridtps$tlvl$r`). It means food-webs that have
-experienced a decrease in species richness over time have decreased in average
-trophic level, and conversely, those that increased in species richness have
-increased in average trophic level, through community biomass. Furthermore, we
-found that temporal trends of the proportion of piscivorous species was
-negatively associated with the temporal trends of species richness (Fig. S3),
-meaning that communities that increase in richness over time have an increase in
-the proportion of non-piscivorous species over time and vice versa.
+\@ref(fig:sem)g), a positive indirect effect through community
+biomass ($r_\delta =$ `r ridtps$tlvl$r`), which adds up to a positive total
+effect of species richness temporal trends on average trophic level ($r_\delta
+=$ `r rttps$tlvl$r`, Fig. \@ref(fig:std)). Species richness temporal trends had
+direct and indirect positive effect on the temporal trends in redundancy (resp.
+$r_\delta =$ `r rdtps$red$r`, `r ridtps$red$r`), which adds up to a strong
+positive effect $r_\delta =$ `r rttps$red$r`. Furthermore, we found that
+temporal trends of the proportion of piscivorous species was negatively
+associated with the temporal trends of species richness (Fig. S3), meaning that
+communities that increase in richness over time have an increase in the
+proportion of non-piscivorous species over time and vice versa. It means
+food-webs that have experienced a decrease in species richness over time have
+decreased in average trophic level and redundancy but increase in connectance,
+and conversely, those that increased in species richness have increased in
+average trophic level, redundancy, but decreased in connectance.
 
 The effects of spatial variations in species richness on food-web structure
-contrasts with the ones found with temporal trends. We found a direct negative
+mostly agreed with the ones found with temporal trends. We found a direct negative
 effect of species richness on connectance both using data and model simulations
-(resp. $r_\delta =$ `r rdsp$ct$r` and `r rdm$ct$r`, Fig. \@ref(fig:std)) and on
-average trophic level (resp. $r_\delta =$ `r rdsp$tlvl$r` and `r rdm$tlvl$r`).
-Despite indirect positive effect of species richness through community biomass,
-species richness had strong total negative effects on connectance in empirical
-data and simulations (resp. $r_\delta =$ `r rtsp$ct$r` and `r rtm$ct$r` ) and
-average trophic level (resp. $r_\delta =$ `r rtsp$tlvl$r` and `r rtm$tlvl$r`).
+(resp. $r_\delta =$ `r rdsp$ct$r` and `r rdm$ct$r`, Fig. \@ref(fig:std)), on
+average trophic level (resp. $r_\delta =$ `r rdsp$tlvl$r` and `r rdm$tlvl$r`),
+but a direct positive effect on redundancy (resp. $r_\delta =$ `r rdsp$red$r`
+and `r rdm$red$r`). Species richess had indirect positive effect of species
+richness through community biomass, which added up to strong total negative
+effects on connectance in empirical data and simulations (resp. $r_\delta =$
+`r rtsp$ct$r` and `r rtm$ct$r` ) and positive on redundancy (resp. $r_\delta =$
+`r rtsp$red$r` and `r rtm$red$r`). We found that species richness had a total
+positive effect on average trophic level in bioenergetic model, in agreement
+with temporal trends (resp. $r_\delta =$ `r rtm$tlvl$r`), but a total negative
+effect in spatial variations (resp. $r_\delta =$ `r rtsp$tlvl$r`).
 
@@
 std_cap <- paste0(
-  "Assessment of the space-for-time hypothesis. Standardized coefficients
-  ($r_\\delta$) derived from the spatial and temporal Structural Equation
-  Models. The left, middle and right panels display respectively the direct,
-  indirect and total effects of community biomass and species richness on the
-  Average trophic level (top panel), the connectance (middle panel) and the
-  community biomass (bottom panel) The lines display the confidence intervals at
-  95%.")
+  "Direct and total effects of community biomass and species richness.
+  Standardized coefficients ($r_\\delta$) derived from the temporal, spatial,
+  and bioenergetic model Structural Equation Models. Points and lines display
+  the estimated effects and their confidence intervals at 95\\%. Values are
+  displayed in Table SXX, R-squared in Table SXX, and the visualisation of the
+  bivariate relationships for the spatial and bioenergetic model SEMs are
+  displayed in Figure SXX.")
+
 ```
@@
 temporal or spatial and theoretical simulations. It suggests that food-web
-structure changes induced by changes in species richness differs from the one
+structural changes induced by changes in species richness differs from the one
 induced by the changes in community biomass, and that they imply different
-processes across time and space. In what follows, we discuss how changes
-in community biomass and species richness changes over time and space are
-related to food-web assembly and disassembly processes.
+processes across time and space. However, all analysis converged to indicate
+that community biomass and species richness declines trigger a decrease in
+food-web redundancy. In what follows, we discuss how changes in community
+biomass and species richness changes over time and space are related to food-web
+assembly and disassembly processes.
 
@@
 When considering spatial analysis and model simulations, species richness
-effects on food-web structure were highly distinct from the temporal analysis.
-Spatial analysis and theoretical models suggest that increase in species
-richness results in lower connectance and average trophic level, a well known
-patterns in empirical food-web [@dunne_network_2006; @danet_species_2021]. This
-result is also in line with other studies which found a mismatch between spatial
-and temporal trends [@adler_contrasting_2007; @johnson_testing_2008]. This
-discrepancy in space and time is due to the strong assumption that variations in
-space reflect differences in assembly stages of ecological communities and then
-mirror their temporal assembly/disassembly trajectories. Temporal changes in
-species richness might relate to short-term dynamics while spatial gradients
-reflect aggregated dynamics over a longer time scale including a far number of
-processes including high species turnover along spatial gradients. Our results
-then suggest community biomass changes in space might be a good surrogate to
-infer assembly and disassembly of food-web in time, but that it is probably not
-the case for species richness.
-
-*Final message*
-
-It suggests that the temporal assembly and
-disassembly of food-webs are more sensitive to variations in community biomass
-than in species richness, in other words that food-web structure is more robust
-to changes in species richness than in biomass over time. Our study then
-suggests that the changes of food-web structure over time related to changes in
-species richness could be actually mediated by changes in community biomass.
+effects on food-web structure mostly consistent from the temporal analysis. All
+analysis converged to indicate that increases in species richness result in
+decreases in connectance, a well documented pattern in empirical food-webs
+[@dunne_network_2006; @danet_species_2021]. However, spatial analysis found that
+species richness decrease average trophic level, while temporal analysis and
+theoretical models found that species richness increases result in higher
+average trophic level. This result is also in line with other studies which
+found a mismatch between spatial and temporal trends [@adler_contrasting_2007;
+@johnson_testing_2008]. This discrepancy in space and time is due to the strong
+assumption that variations in space reflect differences in assembly stages of
+ecological communities and then mirror their temporal assembly/disassembly
+trajectories. Temporal changes in species richness might relate to short-term
+dynamics while spatial gradients reflect aggregated dynamics over a longer time
+scale including a far number of processes including high species turnover along
+spatial gradients. Our results then suggest community biomass changes in space
+might be a good surrogate to infer assembly and disassembly of food-web in time,
+but that it is probably not always the case for species richness.
 
 ## Conclusion and perspectives
+
+- Revise: biomass pyramids, connectance different from top predators
+- Add redundancy
 
@@
 community biomass induced changes in food-web structure, such as decline in
-biomass translates in food-webs with fewer trophic links and top predators while
+biomass translates in food-webs with *lower connectance* and fewer top predators
+while increases in biomass results in food-webs with higher connectance and more
+top predators. In turn, decline in species richness translates in food-webs with
+fewer trophic links and top predators while
 increases in biomass results in food-webs with more trophic links and top
-predators. Species richness temporal trends translate in low changes in food-web
-structure, suggesting that species richness changes relates more to trophic role
+predatorstranslate in low changes in
+food-web structure, suggesting that species richness changes relates more to
+trophic role
 redundancy than in changes in food-web structure. Using replicating the analysis
@@
 infer assembly and disassembly processes in food-web structure works well for
-community biomass and not species richness.
+community biomass but not so well for species richness.
 
@@
 similar results to the empirical data.
-
-Our study opens stimulating perspectives to further understand of biodiversity
-changes alters community structure and ecosystem functioning. It is particularly
-needed for ecological networks, whose structure has tremendous effects on
-ecosystem functioning and stability. It implies to further investigate which
-processes drive the differences in the effects of species richness
-changes on food-web structure in space and time.
 

### 2024-08-06 draft.jl

@@ -17,150 +17,3 @@ ti = sim(fw1.A, t = 5000, Z = 100,
          saveat = 10,
          tspan = [3500, 5000]);
 get_output_sim(ti.model, ti.solution)
-
-living_species_indexes = findall(ti.solution[:, end] .> 0)
-mi = disconnected_species(
-                     ti.model.A[living_species_indexes, living_species_indexes],
-                     ti.model.metabolic_classes[living_species_indexes],
-                     ti.model.species_names[living_species_indexes]
-                    )
-length(mi.species_to_keep)
-
-
-base_model = default_model(
-              fw1, BodyMass(Z = 100), BioenergeticResponse(h = 1.5),
-              without = ProducerGrowth
-             );
-K = K_global * (1 + (alpha_ij * (base_model.n_producers - 1))) / base_model.n_producers
-# Rebuild model
-m = base_model + LogisticGrowth(; r = 1, K = K, producers_competition = p);
-B0 = rand(m.richness);
-sol = simulate(m, B0, 2000, extinction_threshold = 10^-6);
-get_output_sim(m, sol)
-
-living_species_indexes = findall(sol[:, end] .> 0)
-ti = disconnected_species(
-                     m.A[living_species_indexes, living_species_indexes],
-                     m.metabolic_classes[living_species_indexes],
-                     m.species_names[living_species_indexes]
-                    )
-to_keep_idxs = [i ∈  ti.species_to_keep for i in m.species_names]
-base_model = default_model(
-                           Foodweb(m.A[to_keep_idxs, to_keep_idxs]),
-                           MetabolicClass(m.metabolic_classes[to_keep_idxs]),
-              without = ProducerGrowth
-             );
-consumer_to_remove = retrieve_disconnected_consumers(
-                                m.A[living_species_indexes, living_species_indexes],
-                                m.metabolic_classes[living_species_indexes],
-                                m.species_names[living_species_indexes]
-                               )
[…]

### 2024-08-06 scripts/simulations_richness_carrying_capacity.jl

@@ -10,7 +10,7 @@ if !isdir(dest_dir)
 end
 
 #df_fw = DataFrame(Arrow.Table(joinpath(proj_dir, "scripts/fw_comb_ct_S.arrow")))
-#df_fw = DataFrame(Arrow.Table(joinpath("scripts/fw_comb_ct_S.arrow")))
+df_fw = DataFrame(Arrow.Table(joinpath("scripts/fw_comb_ct_S.arrow")))
 #
 # Add carrying capacity
 K = collect(1:10)

### 2024-08-06 src/sim.jl

@@ -75,19 +75,20 @@ function get_output_sim(model, solution; last = 1)
 
     if ismissing(model)
         output = (;
-         total_bm = missing,
-         final_richness = missing,
-         maximum_trophic_level = missing,
-         average_trophic_level = missing,
-         weighted_average_trophic_level = missing,
-         connectance_final = missing,
-         persistence_final = missing,
-         top_consumer_bm = missing,
-         producer_bm = missing,
-         intermediate_consumer_bm = missing,
-         top_consumer_richness = missing,
-         producer_richness = missing,
-         intermediate_consumer_richness = missing
+                  A = missing,
+                  total_bm = missing,
+                  final_richness = missing,
+                  maximum_trophic_level = missing,
+                  average_trophic_level = missing,
+                  weighted_average_trophic_level = missing,
+                  connectance_final = missing,
+                  persistence_final = missing,
+                  top_consumer_bm = missing,
+                  producer_bm = missing,
+                  intermediate_consumer_bm = missing,
+                  top_consumer_richness = missing,
+                  producer_richness = missing,
+                  intermediate_consumer_richness = missing
         )
         return output
     end
@@ -97,9 +98,10 @@ function get_output_sim(model, solution; last = 1)
     final_richness = mean(richness(solution)[(end - last + 1):end])
     bm_species = vec(mean(solution[living_species_indexes, (end - last + 1):end], dims = 2))
     rel_bm_species = bm_species ./ sum(bm_species)
+    A = model.A[living_species_indexes, living_species_indexes]
 
     #@infiltrate
-    m = default_model(Foodweb(model.A[living_species_indexes, living_species_indexes]),
+    m = default_model(Foodweb(A),
                        MetabolicClass(model.metabolic_classes[living_species_indexes])
                   )
     tops_consumer_mask =  m.consumers_mask .& m.tops_mask
@@ -118,6 +120,7 @@ function get_output_sim(model, solution; last = 1)
     intermediate_consumer_richness = final_richness - top_consumer_richness - producer_richness
 
     (;
+     A,
      total_bm,
      final_richness,
      maximum_trophic_level,

### 2024-08-07 paper/manuscript.Rmd
Revise discussion + add theoretical model methods

@@
 rm(full_data2)
+tar_load(glob_tps_trends_decade_no_drivers)
 ```
@@
 ```{r, results=FALSE}
-tar_load(glob_tps_trends_decade_no_drivers)
 gbm <- get_effect_ci(resp = "log_bm_std", ci_lvl = "level:0.80", p = TRUE)
@@
 biomass: from `r grbmn`% to `r grbmx`% per decade, species richness: `r grrhn`
-to +`r grrhx`%, average trophic level: `r grtln` to +`r grtlx`, connectance: `r
-grctn` to +`r grctx`, redundancy: `r grln` to +`r grlx`, Fig. S1) which was well
-captured by the hierarchical model with conditional R2 going from `r r2cond$log_bm_std` for community biomass to `r r2cond$log_rich_std` for species
-richness (Table S1).
+to +`r grrhx`%, average trophic level: `r grtln` to +`r grtlx`, connectance:
+`r grctn` to +`r grctx`, redundancy: `r grln` to +`r grlx`, Fig. S1) which was
+well captured by the hierarchical model with conditional R2 going from
+`r r2cond$log_bm_std` for community biomass to `r r2cond$log_rich_std` for
+species richness (Table S1).
 
@@
 \@ref(fig:std) and S5). In both empirical data and theoretical simulations, community
-biomass had a positive effect on connectance (resp. $r_\delta =$ `r rdsp$ct$bm`
-and `r rdm$ct$bm`, Fig. \@ref(fig:std)), average trophic level (resp.
+biomass had a positive effect average trophic level (resp.
 $r_\delta =$ `r rdsp$tlvl$bm` and `r rdm$tlvl$bm`), and redundancy (resp.
 $r_\delta =$ `r rdsp$red$bm` and `r rdm$red$bm`), as in temporal analysis.
+We found weak evidence of a positive effect of spatial variation in community
+biomass on connectance in empirical data ($r_\delta =$ `r rdsp$ct$bm`) but
+strong evidence in theoretical simulation ($r_\delta =$ `r rdm$ct$bm`, Fig. \@ref(fig:std)).
 
@@
 direct and indirect positive effect on the temporal trends in redundancy (resp.
-$r_\delta =$ `r rdtps$red$r`, `r ridtps$red$r`), which adds up to a strong
-positive effect $r_\delta =$ `r rttps$red$r`. Furthermore, we found that
+$r_\delta =$ `r rdtps$red$r`, `r ridtps$red$r`), which added up to a strong
+positive effect ($r_\delta =$ `r rttps$red$r`). Furthermore, we found that
 temporal trends of the proportion of piscivorous species was negatively
@@
 proportion of non-piscivorous species over time and vice versa. It means
-food-webs that have experienced a decrease in species richness over time have
-decreased in average trophic level and redundancy but increase in connectance,
-and conversely, those that increased in species richness have increased in
-average trophic level, redundancy, but decreased in connectance.
+food-webs that have experienced declines in species richness over the last
+decades have decreased in average trophic level and redundancy but increase in
+connectance, and conversely, those that experienced increases in species
+richness have increased in average trophic level, redundancy, but decreased in
+connectance.
 
 The effects of spatial variations in species richness on food-web structure
-mostly agreed with the ones found with temporal trends. We found a direct negative
-effect of species richness on connectance both using data and model simulations
+mostly agreed with the ones found with temporal trends, expect for average
+trophic level. We found a direct negative effect of species richness on
+connectance both using data and model simulations
 (resp. $r_\delta =$ `r rdsp$ct$r` and `r rdm$ct$r`, Fig. \@ref(fig:std)), on
@@
 but a direct positive effect on redundancy (resp. $r_\delta =$ `r rdsp$red$r`
-and `r rdm$red$r`). Species richess had indirect positive effect of species
+and `r rdm$red$r`). Species richness had indirect positive effect of species
 richness through community biomass, which added up to strong total negative
@@
 changes over the last decades in riverine fish communities, linked to changes in
-food-web structure. Community biomass changes spanned from `r grbmn`% to `r
+food-web structure. Community biomass changes spanned from -`r grbmn`% to `r
 grbmx`% per decade, species richness from `r grrhn`% to +`r grrhx`% per decade,
@@
 @blowes_geography_2019; @danet_past_2024]. In turn, connectance temporal changes
-spanned from `r grctn` to +`r grctx` per decade and average trophic level, from
-`r grtln` to +`r grtlx` per decade. We questioned the effects of community
+spanned from `r grctn` to +`r grctx` per decade, average trophic level, from
+`r grtln` to +`r grtlx` per decade and the proportion of redundant trophic links
+from `r grln` to +`r grlx` per decades. We questioned the effects of community
 biomass and species richness changes over time on temporal changes in food-web
@@
 [@lindeman_trophic-dynamic_1942; @gravel_trophic_2011], which posits that the
-presence of top predators is limited by the amount of energy and
-resource available [@lindeman_trophic-dynamic_1942, @takimoto_ecosystem_2008;
+presence of top predators is limited by the amount of energy and resource
+available [@lindeman_trophic-dynamic_1942, @takimoto_ecosystem_2008;
 @post_ecosystem_2000; @post_long_2002]. Thereby, a decrease in community biomass
@@
 
-Species richness temporal changes were positively associated to changes in average
-trophic level, such as food-webs that have suffered a decline in species richness
-have experienced a concomitant decline in average trophic level, those have seen
-an increase in species richness have experienced an increase in average trophic
-level. However, the effect of species richness temporal trends on average
-trophic level were twice lower than the one of community biomass, and had no
-effects on connectance temporal changes. Altogether, it suggests that species
-richness increase and decrease were less clearly linked to specific changes in
-food-web structure. Species richness temporal trends could be more linked to
-changes in the redundancy of trophic roles in the food-webs, such as it has
-little effects of food-web structure but increases its community biomass. This
-interpretation align with the insurance hypothesis [@yachi_biodiversity_1999;
+Species richness temporal changes were positively associated to changes in
+average trophic level through community biomass and in connectance mainly
+through direct effects, such as food-webs that have suffered a decline in
+species richness over last decades have experienced a concomitant decline in
+average trophic level and increase in connectance, those have seen an increase
+in species richness have experienced an increase in average trophic level and
+decline in connectance. However, the effect of species richness temporal trends
+on average trophic level were twice lower than the one of community biomass.
+Altogether, it suggests that species richness increase and decrease were less
+clearly linked to specific changes in top trophic levels than community biomass.
+Species richness temporal trends could be more linked to changes in the
+redundancy of trophic roles in the food-webs, such as it has little effects of
+food-web structure but increases its community biomass. This interpretation
+align with the insurance hypothesis [@yachi_biodiversity_1999;
 @loreau_biodiversity_2021], such as species richness and associated redundancy
@@
 
-## Conclusion and perspectives
+Our study demonstrates that redundancy of trophic pathways in food-webs are
+positively associated to both community biomass and species richness changes, so
+as declines in community biomass and species richness triggers a loss in the
+proportion of redundant links in food-webs, while increases in community biomass
+and species richness over time results in the increase in the proportion of
+redundant links in food-webs. Redundant links are the trophic links that can be
+removed with triggering secondary extinctions [@allesina_who_2004;
+@bodini_using_2009], such an higher proportion of redundant interactions
+increase robustness of food-webs to perturbations [@allesina_functional_2009].
+It suggests that declines in community biomass and species richness result in a
+decline of food-web robustness to further perturbations.
 
-- Revise: biomass pyramids, connectance different from top predators
-- Add redundancy
-
-We investigated how food-web assemble and disassemble according to changes in
-community biomass and species richness. Our study shows that temporal changes in
-community biomass induced changes in food-web structure, such as decline in
-biomass translates in food-webs with *lower connectance* and fewer top predators
-while increases in biomass results in food-webs with higher connectance and more
-top predators. In turn, decline in species richness translates in food-webs with
-fewer trophic links and top predators while
-increases in biomass results in food-webs with more trophic links and top
-predatorstranslate in low changes in
-food-web structure, suggesting that species richness changes relates more to
-trophic role
-redundancy than in changes in food-web structure. Using replicating the analysis
-over spatial gradient and with a theoretical model, our study shows that
-community biomass changes over space and theoretical model results in the same
-changes in food-web structure than in temporal analysis, which is not the case
-for species richness. It suggests that using space-for-time substitution to
-infer assembly and disassembly processes in food-web structure works well for
-community biomass but not so well for species richness.
-
-In the context of biodiversity crisis, our study reveals that declines of
-community biomass results in food-web downgrading. As species of top trophic
-levels plays a great role in ecosystem functioning [@estes_trophic_2011;
-@wang_biodiversity_2018; @thebault_food-web_2003], it raises concerns about the
-functioning of such degraded ecosystems. Loss of species richness in turn did
-not affect significantly food-web structure, suggesting that it implies loss of
-redundancy in trophic roles. As redundancy has a key role in buffering ecosystem
-variability against perturbations [@sanders_trophic_2018;
-@yachi_biodiversity_1999], it raises concerns about the stability of such
-food-webs. We used here empirical freshwater food-web inferred from in-situ fish
-bodysize and diet [@danet_species_2021; @bonnaffe_comparison_2021], which do not
-account for the variability in invertebrates and primary producers presences,
-and do not a number of processes such as changes in interaction strengths.
-However, the theoretical model embedding complete food-webs showed remarkably
-similar results to the empirical data.
+Our study brings evidences that temporal changes in community biomass and
+species richness are related to changes in food-web structure in empirical
+settings. We completed the temporal analysis with a spatial analysis and
+theoretical simulations. Altogether, it suggests that community biomass changes
+are associated with changes in the presence of top predators, in agreement with
+the hypothesis that food-web maximum trophic level are limited by the amount of
+energy available in lower trophic level. In contrast, species richness changes
+seems to be linked to changes in upper and lower part of the food-webs.
+Importantly, temporal and spatial analysis using empirical fish food-webs are
+largely in agreement with theoretical simulations, which highlight the potential
+generality of the food-web assembly rules that we report. The study finally
+highlights that increases in community biomass and species brings robustness to
+food-webs by increasing the proportion of redundant trophic links. Conversely, it
+suggests that community declines in species richness and community biomass are
+likely to decrease significantly the community robustness to further
+perturbations. Thereby, the numerous reported declines in biodiversity might
+hide increase in the fragility of ecosystems.
 
@@
 added to the mean trophic level of the preys that it consumes
-[@herendeen_ecological_2008].
+[@herendeen_ecological_2008]. We computed the number of redundant and functional
+links using the dominator tree approach [@allesina_functional_2009]. A species
+$i$ is a dominator of species $j$ if $i$ mediates the connection $j$ to basal
+resources such as the extinction of $i$ remove the connection of $j$ to basal
+resources. It is then to identify the set of trophic links that are essential to
+connect species to basal resources, i.e. functional links, and the
+redundant links. This method requires a single basal root in the food-webs. To
+do so, we added a basal dummy resource node to the empirical food-webs connected
+to biofilm and phytoplankton resource node. For food-webs generated from
+theoretical simulations (see below), we added a resource node connected to all
+primary producers. We computed the set of dominator trees using the
+`dominator_tree()` function in `igraph` R package. We computed the number of
+functional links as the number of links in the resulting dominator tree of the
+food-web. We checked that the procedure reproduced the examples presented in
+@allesina_functional_2009. We then derived the proportion of redundant links in
+food-webs of empirical and theoretical simulations.
 
@@
 We modeled the relationships among food-web structure, that is
-connectance and average trophic level, and community biomass ($dB$) and species
-richness ($dR$) with Structural Equation Models. We modeled species
+connectance, average trophic level, the proportion of redundant trophic links, and
+community biomass ($dB$) and species richness ($dR$) with Structural Equation
+Models. We modeled species
 richness as related to community biomass and food-web structure. In
@@
 structural equation model to assess the relationships among the temporal trends
-and one for the relationships over the spatial gradient. As spatial variation of
-food-web structure are partly driven by environmental gradients, so we
-controlled relationships among variables by adding two PCA axis
-synthesizing respectively (1) stream gradient from upstream to downstream and
-(2) enrichment [details in @danet_species_2021]. Enrichment was characterized by
-the average Biological Oxygen Demand [BOD, @mallin_factors_2006]. We further
-added a random effect of the hydrographic basin on the intercept.
+and one for the relationships over the spatial gradient, we added a random effect
+of the hydrographic basin on the intercept for the latter one.
 
@@
 [@murphy_semeff_2021]. Confidence intervals were obtained by bootstrapping the
-linear models 100 times and computing adjusted bootstrap percentile interval
+linear models 1000 times and computing adjusted bootstrap percentile interval
 (BCa), which are adjusted for the asymmetric distribution of resampling. The marginal
@@
 
+## Theoretical simulations
+
+```{r}
+tar_load(sim_param)
+nsim <- nrow(sim_param)
+nfw <- length(unique(sim_param$fw_id))
+s_range <- c(min = min(sim_param$S), max = max(sim_param$S))
+c_range <- c(min = min(sim_param$C), max = max(sim_param$C))
+k_range <- c(min = min(sim_param$K), max = max(sim_param$K))
+```
+
+We used a bioenergetic food-web model to simulate the effects of community
+biomass and species richness changes on food-web structure. This food-web model
+lifts one of the limitation of our data, that is it includes the biomass of all
+the food-webs from primary producers to top predators. This model allows to
+simulate complex communities because its parametrization depends mainly on
+species bodymasses. We first generated `r nfw` food-webs varying in species
+richness (range: `r s_range["min"]`-`r s_range["max"]`)
+and connectance (range: `r c_range["min"]`-`r c_range["max"]`) using the niche
+model algorithm, which reproduces food-web topology tipically found in empirical
+food-webs [@williams_simple_2000]. We set species bodymasses ($M_i$) using a predator-prey
+mass ratio of 100 ($Z$) [@brose_allometric_2006; @brose_predator_2019], such as $M_i =
+Z^{(TL_i - 1)}$, $TL_i$ being the trophic level of the species $i$. The
+metabolic rates of the species ($x_i$) were then derived from allometric
+relationships between metabolism and bodymass empirically estimated
+[@brose_allometric_2006], such as $x_i = aM_i^b$, with $a = xx$ and $b = -0.25$.
+
+The dynamics of species biomasses are described by an ODE systems of two
+equations, for primary producers (eq. \@ref(eq:prod)) and consumers (eq. \@ref(eq:cons)) respectively:
+
+\begin{equation}
+    (\#eq:prod)
+	\frac{dB_i}{dt} =
+    r_i B_i G_i
+    - \sum_{j \in \{\mathrm{cons}\}_i} \frac{x_j y_j B_j F_{ji}}{e_{ij}}
+\end{equation}
+
+\begin{equation}
+    (\#eq:growth)
+    G_i = (1 - \dfrac{\sum_{j \in \{\mathrm{prod}\}} \alpha_{ij} B_j}{K_i})
+\end{equation}
+
+The primary producer biomass increase with a growth rate ($r_i$) of 1 and a
+logistic growth (eq. \@ref(eq:growth)), growth being limited by intraspecific
+($\alpha_{ii}$, set to 1), interspecific ($\alpha_{ij}$, set to 0.5) competition,
+and carrying capacity ($K_i$, varying in the simulations). Primary producers
+loses biomass by being eaten by consumers at a rate that depend on consumer
+metabolic rates ($x_j$), attack rates ($y_j$, set to 8 @delmas_analysing_2019),
+a functional response (F_{ji}), and assimilation efficiency ($e_{ij}$, set to
+0.45 for herbivores and 0.85 for carnivores, @delmas_analysing_2019).
+
+\begin{equation}
+    (\#eq:cons)
+        \frac{dB_i}{dt} =
+        \sum_{j \in \{\mathrm{res}\}_i} x_i y_i B_k F_{ij}
+        - \sum_{j \in \{\mathrm{cons}\}_i} \frac{x_j y_j B_j F_{ji}}{e_{ij}}
+        - x_i B_i
+\end{equation}
+
+Consumers gain biomass by eating other species and lose biomass by being
+consumed and by metabolic loses ($x_i$, eq. \@ref(eq:cons)). The functional
+response (eq. \@ref(eq:holling)) of consumer feeding depends on the preference
+for its preys ($\omega_{ij}$, set even across consumer preys) and
+half-saturation rate ($B_0$, set to 0.5). The hill coefficient ($h$, set to 1.5)
+determines the shape of the functional response (Holling's type II or III).
+
+\begin{equation}
+    (\#eq:holling)
+    F_{ij} = \frac{\omega_{ij} B_j^h}
+    {B_0^h + \sum_{k \in \{\mathrm{res}\}_i} \omega_{ik} B_k^h}
+\end{equation}
+
+We simulated the food-webs dynamics across a gradient of global carrying capacity (K,
+range: `r k_range["min"]`-`r k_range["max"]`). The carrying capacity were
+standardized according to the number of producers and interspecific competition
+($K_i = \frac{1 + \alpha_{ij} (S - 1)}{S}K$) to prevent changes in productivity
+due to system size [@ives_stability_2000; @loreau_synchrony_2008]. We ran
+simulations for 5000 timesteps. At the end of simulations, we removed dead
+species and measured community biomass, species richness and food-web structure.
+If the final community contained disconnected producers (i.e. without consumers)
+or disconnected consumers (i.e. consumers without preys), we discarded them and
+run the simulations again with the same parametrisation. The simulations were
+done using the Julia package `EcologicalNetworksDynamics.jl`
+[@lajaiiti_ecological_2024].
+
 ```{r matmet, fig.cap=fig_mat_cap, out.width="80%"}

### 2024-08-07 paper/manuscript.Rmd
Update manuscript fig + add guidelines for introduction review

@@
 author: Alain Danet (a), Loubna El Madouri (a, c), Maud Mouchet (a), Elisa Thébault (d) and Colin Fontaine (a)
-date: Research report
+date: "Research report"
 output:
-  #bookdown::word_document2:
-  #  fontsize: 12pt
   bookdown::pdf_document2:
-    fig_caption: true
+    latex_engine: xelatex
     keep_tex: true
+    spacing: double
+    number_sections: false
+  officedown::rdocx_document:
+    number_sections: false
+    base_format: "bookdown::word_document2"
+always_allow_html: true
+bibliography: references.bib
+link-citations: true
+#csl: ecology-letters.csl
 toc: false
-    fontsize: 12pt
+linestretch: 2.0
 header-includes:
-   - \usepackage{natbib}
-   - \usepackage{float}
-   - \usepackage{multirow}
-   - \usepackage{booktabs}
-   - \usepackage{makecell}
-   - \usepackage{setspace}
-   - \doublespacing
-   - \usepackage{lineno}
+  - \usepackage[left]{lineno}
   - \linenumbers
-geometry: margin=2cm
-number_sections: true
-bibliography: references.bib
+  - \usepackage{hyperref}
+  - \hypersetup{backref=true}
+  - \usepackage{setspace}\doublespacing
 csl: pnas.csl
@@
 
-(c) ?
+(c) Laboratoire d’Écologie Fonctionnelle et Environnement, UMR 5245
+CNRS-UT3-INPT, Avenue de l’Agrobiopôle, Toulouse, France
 
@@
 
+- Biodiversity changes = changes in food-web structure that are important for
+  ecosystem functioning and stability.
+- Unique combination of empirical data and theoretical simulations.
+- Inform how community biomass and species richness declines result in an
+  increase of the fragility of food-webs.
+
 While the multidimensional nature of biodiversity changes has been clearly
@@
 # Introduction (487 words)
+
+- Ideas:
+  1. Biodiversity at risk; widespread heterogeneity in changes; ignores
+     community struture
+  2. Community structure is important for ecosystem functioning and robustness
+     to perturbations
+  3. Questions: assembly and disassembly processes of food-webs associated with
+     biodiversity changes?; possible due to inference of food-web structure;
+     Energetic constraints, redundancy and robustness; Validity of space for
+     time hypothesis
+  4. Presentation of the study data, theoretical models and extinction
+     simulation: presentation of the hypothesis associated to the SEM
+
+Why redundancy? Because not all links in the same way to the robustness of
+food-webs
 
@@
 secondary extinctions [@dunne_network_2002; @sole_complexity_2001] and studies
-found that the presence of higher trophic levels is associated to a higher temporal stability of
-community biomass in theoretical models and empirical data
+found that the presence of higher trophic levels is associated to a higher
+temporal stability of community biomass in theoretical models and empirical data
 [@shanafelt_stability_2018; @danet_species_2021]. Then, accounting for how the
@@
 level)*
+
+```{r}
+fig_mat_cap <- paste0("Using sites of stream fishes in French streams that
+  have been monitored at least 10 years, 1) we infered the food-web at each site
+and each sampling event based on ontogenic food diet information for each
+species and predator-prey body size ratio. 2) We computed the temporal trends
+and the median of community biomass, species richness, connectance, average
+trophic level and evenness of biomass at each site. 3) We then assessed the
+relationships among food-web structure descriptors, (a) in time and (b) across space.")
+```
+
+```{r matmet, fig.cap=fig_mat_cap, out.width="100%"}
+knitr::include_graphics(get_mypath("figures", "mat_met.png"))
+```
 
@@
 
-```{r sem, fig.cap = sem_cap}
-knitr::include_graphics(here::here("figures", "fig2.pdf"))
+```{r sem, fig.cap = sem_cap, out.width = "100%"}
+tar_load(p_sem_tps_file)
+knitr::include_graphics(p_sem_tps_file)
 ```
@@
 std_cap <- paste0(
-  "Direct and total effects of community biomass and species richness.
-  Standardized coefficients ($r_\\delta$) derived from the temporal, spatial,
-  and bioenergetic model Structural Equation Models. Points and lines display
-  the estimated effects and their confidence intervals at 95\\%. Values are
-  displayed in Table SXX, R-squared in Table SXX, and the visualisation of the
-  bivariate relationships for the spatial and bioenergetic model SEMs are
-  displayed in Figure SXX.")
+  "Direct and total effects of community biomass and species richness on
+  food-web structure. Standardized coefficients ($r_\\delta$) derived from the
+  temporal, spatial, and bioenergetic model Structural Equation Models. Points
+  and lines display the estimated effects and their confidence intervals at
+  95\\%. Values are displayed in Table SXX, R-squared in Table SXX, and the
+  visualisation of the bivariate relationships for the spatial and bioenergetic
+  model SEMs are displayed in Figure SXX.")
 
@@
 
-```{r std, fig.cap=std_cap, fig.width=7, fig.asp = .7}
-knitr::include_graphics(here::here("figures", "p_sem_tps_sp.pdf"))
+```{r std, fig.cap=std_cap, out.width = "100%"}
+tar_load(p_semeff_tot_ok_file)
+knitr::include_graphics(p_semeff_tot_ok_file)
 ```
@@
 increase in community biomass may result in more resource available for top
-predators [@takimoto_ecosystem_2008; @post_ecosystem_2000].
+predators [@takimoto_ecosystem_2008; @post_ecosystem_2000]. (Add something about
+the role of apex predators?)
 
@@
 
-```{r}
-fig_mat_cap <- paste0("Using sites of stream fishes in French streams that
-  have been monitored at least 10 years, 1) we infered the food-web at each site
-and each sampling event based on ontogenic food diet information for each
-species and predator-prey body size ratio. 2) We computed the temporal trends
-and the median of community biomass, species richness, connectance, average
-trophic level and evenness of biomass at each site. 3) We then assessed the
-relationships among food-web structure descriptors, (a) in time and (b) across space.")
-```
-
 ## Extinction simulation in the metaweb
@@
 ($K_i = \frac{1 + \alpha_{ij} (S - 1)}{S}K$) to prevent changes in productivity
-due to system size [@ives_stability_2000; @loreau_synchrony_2008]. We ran
+due to system size [@ives_stability_2000; @loreau_species_2008]. We ran
 simulations for 5000 timesteps. At the end of simulations, we removed dead
@@
 done using the Julia package `EcologicalNetworksDynamics.jl`
-[@lajaiiti_ecological_2024].
-
-```{r matmet, fig.cap=fig_mat_cap, out.width="80%"}
-knitr::include_graphics(get_mypath("figures", "mat_met.pdf"))
-```
+[@lajaaiti_ecologicalnetworksdynamicsjl_2024].
 

### 2024-08-08 paper/appendix.Rmd
Rewrite intro + reorder appendix

@@
   fig.fullwidth = TRUE,
+  fig.show = "hold",
   fig.pos = "H",
@@
 
-# Supplementary figures
+# Supplementary figures {-}
 
@@
 ```
+
 ```{r tps10, fig.cap=tps10_cap}
@@
 knitr::include_graphics(figStps10)
+```
+
+```{r}
+cor_cap <- paste0("Correlation among food-web metrics for a) temporal trends by
+  site, b) median values by site (cf Main Methods)", " Pisc: piscivorous, rich.:
+species richness, node: node of the food-web corresponding to a trophic species,
+prop.: proportion."
+)
+```
+
+```{r cor, fig.cap=cor_cap}
+tar_load(figcorr)
+knitr::include_graphics(figcorr)
+```
+
+```{r}
+sem_sp_mod_cap <- "Direct effects of biomass and species richness on food-web
+structure, derived from the structural equation models for the (a) spatial and
+(b) bioenergetic model. Points display the data, black lines display the
+predicted relationships."
+
+```
+
+```{r, fig.cap=sem_sp_mod_cap, out.width = "100%"}
+tar_load(p_sem_sp_sim_file)
+knitr::include_graphics(p_sem_sp_sim_file)
 ```
@@
 ```{r}
-cor_cap <- paste0("Correlation among food-web metrics for a) temporal trends by
-  site, b) median values by site (cf Main Methods)", " Pisc: piscivorous, rich.:
-species richness, node: node of the food-web corresponding to a trophic species,
-prop.: proportion."
-)
-```
-
-```{r cor, fig.cap=cor_cap}
-tar_load(figcorr)
-knitr::include_graphics(figcorr)
-```
-
-```{r}
 obs_fit_cap <- "Fitted versus observed values from the INLA models estimating
@@
 
-```{r}
-sem_sp_mod_cap <- "Direct effects of biomass and species richness on food-web
-structure, derived from the structural equation models for the (a) spatial and
-(b) bioenergetic model. Points display the data, black lines display the
-predicted relationships."
+\pagebreak
+\newpage
 
-```
-
-```{r, fig.cap=sem_sp_mod_cap, out.width = "100%"}
-tar_load(p_sem_sp_sim_file)
-knitr::include_graphics(p_sem_sp_sim_file)
-```
+# Supplementary tables {-}
 
 \pagebreak
-
-# Supplementary tables
-
-```{r}
-tar_load(r2_inla_tab)
-kable(r2_inla_tab,
-  row.names = FALSE,
-  booktabs = T,
-  caption = "Marginal and Conditional R-squared for the INLA models estimating
-  the temporal trends of the food-web structure. Mean [95\\% Credible Interval].",
-  label = "inlarsq") %>%
-  kable_styling()
-```
 
@@
 ```{r}
-tar_load(tab_inla_rand)
-tab_inla_rand %>%
-  mutate(Response = factor(Response, levels = unique(var_replacement()))) %>%
-  arrange(Response) %>%
-  kable(
+tar_load(r2_inla_tab)
+kable(r2_inla_tab,
   row.names = FALSE,
   booktabs = T,
-    caption = "Standard deviation associated to the random effects and the residual error of
-    the models. Mean [95\\% Credible Interval].",
-    label = "inlarand") %>%
-  collapse_rows(columns = c(1), valign = "top") %>%
+  caption = "Marginal and Conditional R-squared for the INLA models estimating
+  the temporal trends of the food-web structure. Mean [95\\% Credible Interval].",
+  label = "inlarsq") %>%
   kable_styling()
@@
 ```{r}
+tar_load(tab_inla_rand)
+tab_inla_rand %>%
+  mutate(Response = factor(Response, levels = unique(var_replacement()))) %>%
+  arrange(Response) %>%
+  kable(
+    row.names = FALSE,
+    booktabs = T,
+    caption = "Standard deviation associated to the random effects and the residual error of
+    the models. Mean [95\\% Credible Interval].",
+    label = "inlarand") %>%
+  collapse_rows(columns = c(1), valign = "top") %>%
+  kable_styling()
+```
+
+```{r}
 tar_load(tabvif)

### 2024-08-08 paper/manuscript.Rmd
Rewrite intro + reorder appendix

@@
   results = TRUE,
-  fig.path="figures/"
+  fig.path = "figures/"
 )
@@
 
-# Abstract (240 / 250 words max)
+# Abstract (250 / 250 words max)
 
-Understanding food-web assembly processes is central to biological conservation
-and maintenance of ecosystem functions. In particular, temporal changes in
-community biomass and species richness are expected to significantly impact
-food-web structure but empirical assessments are lacking so far. Here, we
-investigate how temporal trends in species richness and community biomass affect
-temporal trends in food-web structure. To do so, we used more than 6000 sampled
-riverine fish community in 400 sites from french monitoring data. We inferred
-food-web structure for each sampling event, using diet data and body size. Using
-structural equation models, we estimated the effects of temporal changes in
-community biomass and species richness on temporal changes in food-web
-structure. We found that a positive effect of temporal trends in community
-biomass on the temporal trends of connectance and average trophic level, a
-result also found using spatial variations and a bioenergetic model. Temporal
-trends in species richness had a positive effect on average trophic level, but
-no effects on connectance. In space and in simulations, species richness had in
-contrast a negative effect on average trophic level and connectance. In sum, our
-study highlight that local temporal changes in biomass and species richness have
-contrasting effects on food-web structure. It further reveals that temporal
-changes and spatial variations in biomass lead to coherent food-web assembly
-patterns, in contrast to species richness. Our study sheds a new light on
-food-web assembly in natural settings.
+While there are widespread evidence of biodiversity decline, little is known how
+food-web disassemble in response. Such knowledge is crucial as food-web
+structure determine ecosystem functioning and stability to perturbations.
+However, assessing how changes in biodiversity affect changes in food-web
+structure require the availability of food-web timeseries and to account for the
+differential effects of different biodiversity facets on food-web structure.
+Here, we used a standardized monitoring of riverine fish communities over the
+last decades (1995-2018) in France, from which we inferred the food-web
+structure for each sampling events using diet data and allometric scaling rules.
+We estimated the temporal trends in community biomass, species richness, and
+food-web structure using hierarchical Bayesian models. We assessed the effects
+of community biomass and species richness temporal changes on temporal changes
+in food-web structure: connectance, average trophic level and redundancy. We
+further assess the generality and robustness of our findings by replicating the
+analysis over space and using theoretical simulations with a bioenergetic model.
+Our result suggest that food-webs that experienced a decline in community
+biomass experienced conjointly a loss of species at upper trophic levels and
+conversely. While species richness temporal trends had less clear effects on
+food-web structure, mainly due through its indirect effects on community biomass
+temporal trends. Both community biomass and species richness declines were
+associated with a decrease in redundancy, raising concerns about robustness of
+such communities to further perturbations. Our study highlight how biodiversity
+changes affect food-web structure, raising concerns about consequences on
+ecosystem functioning and robustness.
 
-# Significance (115 / 120 words max)
+# Significance (109 / 120 words max)
 
-- Biodiversity changes = changes in food-web structure that are important for
-  ecosystem functioning and stability.
-- Unique combination of empirical data and theoretical simulations.
-- Inform how community biomass and species richness declines result in an
-  increase of the fragility of food-webs.
-
-While the multidimensional nature of biodiversity changes has been clearly
-emphasized, little is known on how the structure of food-web changes according to
-changes in species richness and community biomass. By inferring food-web
-structure based on food-diet data and body size ratios, we analyzed how food-web
-structure in time according to concomitant changes in species richness and
-community biomass. We identify that community biomass is the primary driver of
-temporal changes in food-web structure, but that species richness has surprisingly
-low effect. We further show that space-for-time leads to contrasting results for
-species richness. Our results shed a new light on the assembly and disassembly
-of food-web according to changes in biomass and in species richness.
+Biodiversity temporal changes can lead to simultaneous changes in food-web
+structure, which is turn can have consequences on ecosystem functioning and
+stability. We provide empirical evidence that temporal changes in community
+biomass and species richness are linked to changes contrasted assembly and
+disassembly processes in food-webs in natural settings. We then show that loss
+in both community biomass and species richness are related to a loss of
+redundancy in the food-webs, which raise concerns about the robustness of such
+communities to perturbations. We further added spatial and theoretical evidence
+suggesting that our results are quite robust and open to assess how biodiversity
+changes might affect ecosystem functioning and robustness.
 
@@
 
-- Ideas:
-  1. Biodiversity at risk; widespread heterogeneity in changes; ignores
-     community struture
-  2. Community structure is important for ecosystem functioning and robustness
-     to perturbations
-  3. Questions: assembly and disassembly processes of food-webs associated with
-     biodiversity changes?; possible due to inference of food-web structure;
-     Energetic constraints, redundancy and robustness; Validity of space for
-     time hypothesis
-  4. Presentation of the study data, theoretical models and extinction
-     simulation: presentation of the hypothesis associated to the SEM
+Biodiversity is experiencing massive declines due to continuously increasing
+human pressures, which is expected to have striking consequences on ecosystem
+functioning and fragility. It is increasing recognised that biodiversity
+changes are widely heterogeneous spatially [@mcgill_fifteen_2015;
+@blowes_geography_2019], such as species richness declines and increases can be
+related to spatial variations in human pressures [@cardinale_is_2018;
+@danet_past_2024]. It is increasing recognised that biodiversity changes alter
+community structure [@dornelas_assemblage_2014; @hillebrand_biodiversity_2018;
+@danet_past_2024], but so far, one key component of biodiversity, species
+interactions, has been mostly ignored by studies assessing temporal changes in
+biodiversity, despite the importance of biotic interactions for species
+coexistence, ecosystem functioning and stability [@chesson_mechanisms_2000;
+@thebault_food-web_2003; @oconnor_general_2017; @danet_species_2021]. A better
+understanding of biodiversity changes will then need to account how biodiversity
+changes alter the structure of ecological networks.
 
-Why redundancy? Because not all links in the same way to the robustness of
-food-webs
+Yet, both species richness and food-web structure have a significant impact on
+coexistence [@chesson_interaction_2008], ecosystem functioning
+[@thebault_food-web_2003; @wang_biodiversity_2018], stability
+[@danet_species_2021; @eschenbrenner_diversity_2023], and ecosystem robustness
+to perturbations [@dunne_network_2002; @allesina_functional_2009;
+@bodini_using_2009; @allesina_functional_2009]. Many predator species play a
+keystone role by protecting preys from competitive exclusion
+[@heithaus_predicting_2008; @johnson_rarity_2007; @estes_trophic_2011], thereby
+maintaining species richness. Food-web with higher trophic levels also increase
+ecosystem productivity [@thebault_food-web_2003; @wang_biodiversity_2018] and
+community temporal stability [@danet_species_2021;
+@eschenbrenner_diversity_2023]. Finally, the number and distribution of trophic
+links in food-webs determine the robustness of communities to perturbations
+[@dunne_network_2002; @allesina_functional_2009; @bodini_using_2009;
+@allesina_functional_2009]. Accounting for how food-web assemble and disassemble
+according to biodiversity changes is then crucial to evaluate the consequences
+of biodiversity changes on ecosystem functioning and stability.
 
-Understanding how biodiversity changes is a central question in ecology,
-although challenging because biodiversity changes are multidimensional
-[@mcgill_fifteen_2015; @blowes_geography_2019; @hillebrand_biodiversity_2018],
-such as important changes in species composition can happen despite no changes
-in species richness in average [@dornelas_assemblage_2014;
-@blowes_geography_2019]. Yet species interactions are largely absent from
-biodiversity changes. Although species interactions, described as ecological
-networks, drive for a large part community composition, species coexistence, and
-ecosystem functioning [@chesson_mechanisms_2000; @thebault_food-web_2003;
-@oconnor_general_2017]. The structure of ecological networks can trigger or
-impede perturbation propagations, i.e. secondary extinctions [@paine_note_1969;
-@dunne_network_2002; @srinivasan_response_2007;
-@stouffer_compartmentalization_2011]. Higher connectance, which measures the
-degree of generalism in a network, is predicted to increase robustness to
-secondary extinctions [@dunne_network_2002; @sole_complexity_2001] and studies
-found that the presence of higher trophic levels is associated to a higher
-temporal stability of community biomass in theoretical models and empirical data
-[@shanafelt_stability_2018; @danet_species_2021]. Then, accounting for how the
-structure of ecological networks changes over time according to other
-biodiversity facets is crucial to understand biodiversity changes.
+However, assessing the effects of biodiversity changes on food-web structure
+requires the availability of multiple temporal timeseries of biodiversity and
+food-webs structure, to disentangle the direct and indirect effects of
+biodiversity changes on food-web structure, and to account for theories about
+the multiple constraints on food-web assembly. We propose to monitor three
+structural properties of food-webs and two common monitored biodiversity facets
+(i.e. community biomass and species) that are grounded in food-web assembly,
+ecosystem functioning, and stability research areas: connectance (i.e. degree of
+generalism), weighted average trophic level (i.e. vertical location of biomass),
+and redundancy (i.e. the proportion of redundant links). Their are pieces of
+evidence to connect those food-web structural metrics to changes in ecosystem
+functioning and robustness that we review before to present the temporal
+timeseries that allows to assess them.
 
-The availability of ecological network timeseries is scarce
-[@kortsch_disentangling_2021], such as predictions about how the structure of
-ecological networks change according to changes in species richness come from
-spatial comparison of networks. Such studies showed that connectance is
-negatively related to species richness in food-webs [reviewed in
-@dunne_network_2006; @danet_species_2021], which reflects constraints on the
-number of realizable species interactions or an increasing proportion of
-specialists in more rich food-webs. Connectance has been shown to scale
-positively or negatively with community biomass in theoretical food-webs
-[@thebault_food-web_2003; @poisot_trophic_2013] while the average trophic level
-was previously shown to scale negatively with species richness in empirical
-food-webs [@danet_species_2021].
+Food-web assembly theory provides predictions on how food-web structure should
+change according to changes in community biomass and species richness. The
+energetic paradigm and the trophic theory of biogeography
+[@lindeman_trophic-dynamic_1942; @gravel_trophic_2011] stand that the presence
+of top predators is conditional on the presence of preys in number enough that
+it can provide enough energy from the bottom to the top to sustain high trophic
+level species. In turn, it can that the presence of generalist predators, which is
+positively associated to average trophic level and connectance, will be linked
+more to community biomass changes than to species richness. In turn, connectance
+and average trophic level are commonly reported to decrease with as species
+richness increases [@dunne_network_2006; @danet_species_2021] because predators
+are limited in the number of species they can consume and conversely preys are
+limited in the number of predator they can sustain. Food-web structure has also
+been linked to the robustness to species extinctions [@dunne_network_2002;
+@allesina_who_2004; @bodini_using_2009]. Historically having being linked to
+connectance, i.e. the number of links, more recent studies have proposed to
+separate links that are functional or redundant [@allesina_who_2004;
+@allesina_functional_2009; @bodini_using_2009]. The idea is that the loss of
+functional links will trigger secondary extinctions because it suppresses
+obligatory pathways from resources to consumers while the loss of redundant
+links do not remove such obligatory pathways [@allesina_who_2004]. It means that
+redundant trophic links enhance ecosystem robustness as they can be safely
+removed without triggering secondary extinctions. Thereby we expected that
+higher species richness results in higher redundancy in food-webs, meaning that
+they create more independent pathways connecting basal producers to higher
+trophic level. Finally, biodiversity and ecosystem functioning theory suggest
+that in context of significant niche complementarity, community biomass should
+be positively related to species richness [@wang_biodiversity_2018;
+@schneider_animal_2016], such as it is necessary to account for the indirect
+effects of species richness on food-web structure through community biomass.
 
-However, predicting how ecological networks will change in time according to
-other biodiversity facets based on spatial comparison of food-webs
-is valid if the assumption of space-for-time substitution is as
-well. Space-for-time substitution supposes a homology between variations in
-space and in time, i.e. that spatial sequences correspond to temporal sequences.
-This method raised criticisms [@damgaard_critique_2019], with studies
-showing analogous patterns in space and time [@blois_space_2013] or not
-[@johnson_testing_2008; @adler_contrasting_2007]. Spatial turnover of species
-composition, dispersal limitation, disturbance and stochastic processes have
-been hypothesized to be responsible for the non-compliance of space-for-time
-substitution [@adler_contrasting_2007; @blois_space_2013].
-
-The increasing availability ecological temporal series and the development of
-methods to reconstruct food-webs [@bonnaffe_comparison_2021;
-@gravel_inferring_2013; @danet_species_2021] makes possible to overcome those
-research gaps. We used a standardized monitoring of fish riverine communities on
-the period 1995-2018 over France, documenting the individual size of fishes in
-`r nb_st` sites during ten years or more. We reconstructed around `r nb_op`
-food-webs based on allometric relationships and food diet data, and then
-computed connectance, and average trophic level as well as community biomass and
-species richness. We assessed how the local structure of food-webs changes over
-time according to simultaneous changes in community biomass and species richness
-over time and then if the relationships between changes in food-web structure,
-community biomass and species richness, are the same over space and over time,
-i.e. is the space-for-time substitution valid?
-
-*Introduce hypothesis and the food-web metrics (connectance and average trophic
-level)*
+Here, we report on a study that combine empirical assessment of food-web
+structure and biodiversity temporal changes in natural settings, extinction
+simulations in empirical food-webs, and theoretical simulations using
+bioenergetic model. The availability of food-web timeseries used to be scarce
+[@kortsch_disentangling_2021], but the increasing availability of biodiversity
+timeseries and the development of methods to reconstruct food-webs
+[@bonnaffe_comparison_2021; @gravel_inferring_2013; @danet_species_2021] makes
+possible to overcome this limitation. We used a standardized monitoring of fish
+riverine communities on the period 1995-2018 over France, documenting the
+individual size of fishes in `r nb_st` sites during ten years or more (Table S1). We
+reconstructed around `r nb_op` food-webs based on allometric relationships and
+food diet data, and then computed connectance, and average trophic level
+weighted by trophic species biomass as well as community biomass and species
+richness (Fig. \@ref(fig:matmet)). This dataset and method has already been used
+in previous studies [@danet_species_2021; @bonnaffe_comparison_2021;
+@bonnaffe_interaction_2024]. Using hierarchical Bayesian models, we estimated
+temporal trends in food-web structure, community biomass and richness at each
+site [@danet_past_2024]. We then used structural equation models (SEM) to
+assess the effects of community biomass and species richness temporal changes on
+changes in food-web structure, while accounting for the effects of species
+richness on community biomass. We then assessed if those effects are holding in
+space, i.e. if the space-for-time substitution hypothesis hold
+[@blois_space_2013; @damgaard_critique_2019; @adler_contrasting_2007]. We did so
+by considering median values of food-web structure and community structure over
+the timeseries at each site (Fig. \@ref(fig:matmet)). Finally, we ran
+simulations using the bioenergetic model to assess if our results hold beyond
+our empirical fish food-webs.
 
@@
 `r r2cond$log_bm_std` for community biomass to `r r2cond$log_rich_std` for
-species richness (Table S1).
+species richness (Table S2).
 
@@
 the site temporal trends are displayed in Fig. S1. All the effects are reported
-in Table S4."
+in Table S3."
 ```
@@
 Fig. \@ref(fig:sem) a and b, $r_\delta$: standardized slope coefficient, [95%
-CI]), meaning that both temporal trends had the same direction in average. In
+CI], Table S3), meaning that both temporal trends had the same direction in average. In
 other word, food-webs that have experienced a decrease in species richness over
@@
 trends of community biomass were positively associated to the temporal trends of
-both number and proportion of piscivorous species present (Fig. S3a), meaning
+both number and proportion of piscivorous species present (Fig. S2a), meaning
 biomass trends are linked to the presence of high trophic level trophic
@@
 theoretical simulations (resp. $r_\delta =$ `r rdsp$bm$r` and `r rdm$bm$r`, Fig.
-\@ref(fig:std) and S5). In both empirical data and theoretical simulations, community
+\@ref(fig:std) and S3). In both empirical data and theoretical simulations, community
 biomass had a positive effect average trophic level (resp.
@@
 biomass on connectance in empirical data ($r_\delta =$ `r rdsp$ct$bm`) but
-strong evidence in theoretical simulation ($r_\delta =$ `r rdm$ct$bm`, Fig. \@ref(fig:std)).
+strong evidence in theoretical simulation ($r_\delta =$ `r rdm$ct$bm`, Fig.
+\@ref(fig:std)).
 
@@
 temporal trends of the proportion of piscivorous species was negatively
-associated with the temporal trends of species richness (Fig. S3), meaning that
+associated with the temporal trends of species richness (Fig. S2), meaning that
 communities that increase in richness over time have an increase in the
@@
 connectance and average trophic level decreased as we removed species (red
-lines, Fig. S2a). At the opposite, removing first low trophic level species first
-increase connectance and average trophic level (green lines, Fig. S2a). In turn,
+lines, Fig. S4a). At the opposite, removing first low trophic level species first
+increase connectance and average trophic level (green lines, Fig. S4a). In turn,
 random species extinction sequence had little effect on food-web structure
-(black lines, Fig. S2a).
+(black lines, Fig. S4a).
 
@@
   and lines display the estimated effects and their confidence intervals at
-  95\\%. Values are displayed in Table SXX, R-squared in Table SXX, and the
+  95\\%. Values are displayed in Table S3, R-squared in Table S4, and the
   visualisation of the bivariate relationships for the spatial and bioenergetic
-  model SEMs are displayed in Figure SXX.")
+  model SEMs are displayed in Figure S3.")
 
@@
 changes over the last decades in riverine fish communities, linked to changes in
-food-web structure. Community biomass changes spanned from -`r grbmn`% to `r
-grbmx`% per decade, species richness from `r grrhn`% to +`r grrhx`% per decade,
-in line previous reports of the heterogeneity of local biodiversity changes in
-terrestrial, marine and freshwater realms[@dornelas_assemblage_2014;
+food-web structure. Community biomass changes spanned from `r grbmn`% to
++`r grbmx`% per decade, species richness from `r grrhn`% to +`r grrhx`% per
+decade, in line previous reports of the heterogeneity of local biodiversity
+changes in terrestrial, marine and freshwater realms[@dornelas_assemblage_2014;
 @blowes_geography_2019; @danet_past_2024]. In turn, connectance temporal changes
@@
 complete description of the sampling process can be found in
-@danet_species_2021 (main text and appendix S2). The fishes are sampled using
+@danet_species_2021. The fishes are sampled using
 electrofishing all across the streams in shallow streams and over the bank by
@@
 weeks [@danet_species_2021]. Those steps leads to the selection of
-`r nb_st` sites (Fig. \@ref(fig:matmet), Table S2).
+`r nb_st` sites (Fig. \@ref(fig:matmet), Table S1).
 
@@
 The performance of the model was assessed visually by plotting the fitted versus
-the observed values (Fig. S4). We also visually inspected the Posterior
+the observed values (Fig. S5). We also visually inspected the Posterior
 Integral Transform (PIT) and Conditional Predictive Ordinate (CPO) to assess the
@@
 
+Overall, we found that standard deviation attributed to site effects in both
+baseline and temporal trends in community structure were much higher than the
+ones found for hydrographic basin (Table S5).
+
 ## Spatial
@@
 
-We modeled the relationships among food-web structure, that is
+We modelled the relationships among food-web structure, that is
 connectance, average trophic level, the proportion of redundant trophic links, and
 community biomass ($dB$) and species richness ($dR$) with Structural Equation
-Models. We modeled species
+Models. We modelled species
 richness as related to community biomass and food-web structure. In
@@
 and conditional $R^2$ associated to the linear models of the SEMs were computed
-with the Nagelkerke method [@lefcheck_piecewisesem_2016, Fig. S5].
+with the Nagelkerke method [@lefcheck_piecewisesem_2016, Table S4].
 
 All the statistical models displayed low multicollinearity (Variance inflation
-factors < 3, Table S4). We visually inspected the residuals of the linear
+factors < 3, Table S6). We visually inspected the residuals of the linear
 models.

### 2024-08-09 paper/manuscript.Rmd
typo fixing

@@
 ---
-title: "Community biomass and species richness temporal trends reveal contrasting assembly and disassembly processes in natural food-webs"
-author: Alain Danet (a), Loubna El Madouri (a, c), Maud Mouchet (a), Elisa Thébault (d) and Colin Fontaine (a)
+title: "Temporal dynamics of food-web structure in response to biodiversity changes in riverine ecosystems"
+author: "Alain Danet (a,b), Loubna El Madouri (a,c), Maud Mouchet (a), Elisa Thébault (d) and Colin Fontaine (a)"
 date: "Research report"
 output:
+  officedown::rdocx_document:
+    number_sections: false
+    base_format: "bookdown::word_document2"
   bookdown::pdf_document2:
@@
     number_sections: false
-  officedown::rdocx_document:
+always_allow_html: true
 number_sections: false
-    base_format: "bookdown::word_document2"
-always_allow_html: true
 bibliography: references.bib
@@
 analysis over space and using theoretical simulations with a bioenergetic model.
-Our result suggest that food-webs that experienced a decline in community
+Our results suggest that food-webs that experienced a decline in community
 biomass experienced conjointly a loss of species at upper trophic levels and
@@
 associated with a decrease in redundancy, raising concerns about robustness of
-such communities to further perturbations. Our study highlight how biodiversity
+such communities to further perturbations. Our study highlights how biodiversity
 changes affect food-web structure, raising concerns about consequences on
@@
 related to spatial variations in human pressures [@cardinale_is_2018;
-@danet_past_2024]. It is increasing recognised that biodiversity changes alter
-community structure [@dornelas_assemblage_2014; @hillebrand_biodiversity_2018;
-@danet_past_2024], but so far, one key component of biodiversity, species
-interactions, has been mostly ignored by studies assessing temporal changes in
-biodiversity, despite the importance of biotic interactions for species
-coexistence, ecosystem functioning and stability [@chesson_mechanisms_2000;
-@thebault_food-web_2003; @oconnor_general_2017; @danet_species_2021]. A better
-understanding of biodiversity changes will then need to account how biodiversity
-changes alter the structure of ecological networks.
+@danet_past_2024]. Biodiversity changes result in altered community structure
+[@dornelas_assemblage_2014; @hillebrand_biodiversity_2018; @danet_past_2024],
+but so far, one key component of biodiversity, species interactions, has been
+mostly ignored by studies assessing temporal changes in biodiversity, despite
+the importance of biotic interactions for species coexistence, ecosystem
+functioning and stability [@chesson_mechanisms_2000; @thebault_food-web_2003;
+@oconnor_general_2017; @danet_species_2021]. A better understanding of
+biodiversity changes will then need to account how biodiversity changes alter
+the structure of ecological networks.
 
@@
 generalism), weighted average trophic level (i.e. vertical location of biomass),
-and redundancy (i.e. the proportion of redundant links). Their are pieces of
+and redundancy (i.e. the proportion of redundant links). There are pieces of
 evidence to connect those food-web structural metrics to changes in ecosystem
@@
 fig_mat_cap <- paste0("Using sites of stream fishes in French streams that
-  have been monitored at least 10 years, 1) we infered the food-web at each site
+  have been monitored at least 10 years, 1) we inferred the food-web at each site
 and each sampling event based on ontogenic food diet information for each
@@
 [@hector_plant_1999; @tilman_biodiversity_2014; @wu_relationship_2015;
-@li_relationship_2018; but see @grace_integrative_2016]. This results is in
+@li_relationship_2018; but see @grace_integrative_2016]. This result is in
 agreement with previous findings showing that food-web diversity can increase
@@
 richness over time also experience a loss of biomass, while those gaining
-species experience a increase in community biomass. This results is coherent the
+species experience a increase in community biomass. This result is coherent the
 Biodiversity-Ecosystem Functioning theory [@loreau_biodiversity_2001;
@@
 trajectories. Temporal changes in species richness might relate to short-term
-dynamics while spatial gradients reflect aggregated dynamics over a longer time
-scale including a far number of processes including high species turnover along
-spatial gradients. Our results then suggest community biomass changes in space
-might be a good surrogate to infer assembly and disassembly of food-web in time,
-but that it is probably not always the case for species richness.
+dynamics while spatial gradients reflect aggregated dynamics over a longer
+timescale including a far number of processes including high species turnover
+along spatial gradients. Our results then suggest community biomass changes in
+space might be a good surrogate to infer assembly and disassembly of food-web in
+time, but that it is probably not always the case for species richness.
 
@@
 removed with triggering secondary extinctions [@allesina_who_2004;
-@bodini_using_2009], such an higher proportion of redundant interactions
+@bodini_using_2009], such a higher proportion of redundant interactions
 increase robustness of food-webs to perturbations [@allesina_functional_2009].
@@
 leading to a mean standard deviation of sampled month in each site of three
-weeks [@danet_species_2021]. Those steps leads to the selection of
+weeks [@danet_species_2021]. Those steps lead to the selection of
 `r nb_st` sites (Fig. \@ref(fig:matmet), Table S1).
@@
 Prior distributions for the Gaussian error $\epsilon_{i|n, t}$ and the random
-effects were modelled as a log gamma distribution with
+effects were modeled as a log gamma distribution with
 shape and inverse scale parameters ($\mathcal{G}(s, \, \tau) = \mathcal{G}(1, \,
@@
 ones inferred in space. We used the same sites as in the temporal analysis,
-but we summarised temporal series of each station by the median value over time
+but we summarized temporal series of each station by the median value over time
 of each facet of food-web structure described above (Fig. \@ref(fig:matmet)).
@@
 
-We modelled the relationships among food-web structure, that is
-connectance, average trophic level, the proportion of redundant trophic links, and
-community biomass ($dB$) and species richness ($dR$) with Structural Equation
-Models. We modelled species
-richness as related to community biomass and food-web structure. In
-turn community biomass was related to food-web structure. We computed one
+We modeled the relationships among food-web structure, that is connectance,
+average trophic level, the proportion of redundant trophic links, and community
+biomass ($dB$) and species richness ($dR$) with Structural Equation Models. We
+modeled species richness as related to community biomass and food-web structure.
+In turn community biomass was related to food-web structure. We computed one
 structural equation model to assess the relationships among the temporal trends
-and one for the relationships over the spatial gradient, we added a random effect
-of the hydrographic basin on the intercept for the latter one.
+and one for the relationships over the spatial gradient, we added a random
+effect of the hydrographic basin on the intercept for the latter one.
 
@@
 lifts one of the limitation of our data, that is it includes the biomass of all
-the food-webs from primary producers to top predators. This model allows to
-simulate complex communities because its parametrization depends mainly on
+the food-webs from primary producers to top predators. This model allows
+simulating complex communities because its parameterization depends mainly on
 species bodymasses. We first generated `r nfw` food-webs varying in species
@@
 and connectance (range: `r c_range["min"]`-`r c_range["max"]`) using the niche
-model algorithm, which reproduces food-web topology tipically found in empirical
+model algorithm, which reproduces food-web topology typically found in empirical
 food-webs [@williams_simple_2000]. We set species bodymasses ($M_i$) using a predator-prey
@@
 relationships between metabolism and bodymass empirically estimated
-[@brose_allometric_2006], such as $x_i = aM_i^b$, with $a = xx$ and $b = -0.25$.
+[@brose_allometric_2006], such as $x_i = -0.314M_i^{-0.25}$.
 
 The dynamics of species biomasses are described by an ODE systems of two
-equations, for primary producers (eq. \@ref(eq:prod)) and consumers (eq. \@ref(eq:cons)) respectively:
+equations, for primary producers (eq. \@ref(eq:prod)) and consumers (eq.
+\@ref(eq:cons)) respectively:
 
@@
 
-We simulated the food-webs dynamics across a gradient of global carrying capacity (K,
+We simulated the dynamics of the `r nfw` food-webs across a gradient of global carrying capacity (K,
 range: `r k_range["min"]`-`r k_range["max"]`). The carrying capacity were
@@
 done using the Julia package `EcologicalNetworksDynamics.jl`
-[@lajaaiti_ecologicalnetworksdynamicsjl_2024].
+[@lajaaiti_ecologicalnetworksdynamicsjl_2024]. Then we computed the community
+and food-web metrics at the last timesteps and analyzed the data with the same
+SEM than described above.
 

### 2024-11-14 paper/appendix.Rmd
Update extinction plots + cleaning targets

@@
 cor_cap <- paste0("Correlation among food-web metrics for a) temporal trends by
-  site, b) median values by site (cf Main Methods)", " Pisc: piscivorous, rich.:
+  site, b) median values by site (cf Main Methods), c) bioenergetic model.", " Pisc: piscivorous, rich.:
 species richness, node: node of the food-web corresponding to a trophic species,
@@
 rand_sim_cap <- paste0(
-  "Simulations of (a) species and (b) nodes extinctions in the metaweb according
-  to three scenarios: random extinction sequence, extinction sequence by decreasing order of trophic level,
- extinction sequence by increasing order of trophic level. The black line
- represents the prediction of a GAM model for the random extinction sequences (N = 50)."
+  "Simulations of (b) nodes extinctions in the metaweb according to three
+  scenarios: random extinction sequence (grey dots), extinction sequence by
+  decreasing order of trophic level, extinction sequence by increasing order of
+  trophic level. The black line represents the average prediction of a GAM
+  linear model for the 50 random extinction sequences."
 )
@@
 tar_load(figSext)
-knitr::include_graphics(figSext)
+knitr::include_graphics(figSext[[1]])
 ```
@@
 ```{r}
-obs_fit_cap <- "Fitted versus observed values from the INLA models estimating
+obs_fit_cap <- "Fitted versus observed values from the linear models estimating
 the temporal trends of the food-web structure. The black line depicts the first

### 2024-11-14 _targets.R

@@ -771,133 +771,40 @@ tar_target(semeff_tot_tab,
       node_fish_inc_tlvl = node_inc_tlvl[fish(names(node_inc_tlvl))]
     )
     }),
-  tar_target(sim_dec_tlvl,
-    get_sim_net(net = metaweb_analysis$metaweb, ext_seq = node_seq$node_fish_dec_tlvl,
-      keep_metaweb = FALSE)
-    ),
-  tar_target(sim_inc_tlvl,
-    get_sim_net(net = metaweb_analysis$metaweb, ext_seq = node_seq$node_fish_inc_tlvl,
-      keep_metaweb = FALSE)
-    ),
-  tar_target(sim_random_tlvl, {
-    nsim <- 50
-    set.seed(123)
-    tibble(
-      repl = seq_len(nsim),
-      sim = furrr::future_map(repl,
-        ~get_sim_net(net = metaweb_analysis$metaweb, ext_seq = sample(node_seq$node_fish_inc_tlvl),
-          keep_metaweb = FALSE)
-      )
-    )
-    }),
-  tar_target(node_sim_metrics,
-    list(
-      dec = sim_dec_tlvl %>%
-        mutate(met = map(metrics, ~enframe(unlist(.x[net_ext_met_to_keep()])))) %>%
-        select(-metrics) %>%
-        unnest(met) %>%
-        pivot_wider(names_from = "name", values_from = "value"),
-      inc = sim_inc_tlvl %>%
-        mutate(met = map(metrics, ~enframe(unlist(.x[net_ext_met_to_keep()])))) %>%
-        select(-metrics) %>%
-        unnest(met) %>%
-        pivot_wider(names_from = "name", values_from = "value"),
-      random = sim_random_tlvl %>%
-        mutate(res = map(sim, function(x) {
-            x %>%
-              mutate(met = map(metrics, ~enframe(unlist(.x[net_ext_met_to_keep()])))) %>%
-              unnest(met) %>%
-              pivot_wider(names_from = "name", values_from = "value")
-          })) %>%
-      select(-sim) %>%
-      unnest(res)
-    )
-    ),
-  tar_target(rand_node_tmp,
-    sim_random_tlvl %>%
-      unnest(sim) %>%
-      mutate(
-        met = map(metrics, ~enframe(unlist(.x[net_ext_met_to_keep()]))),
-        nb_ext = map_int(node_rm_tot, length),
-        type = "random",
[…]

### 2024-11-14 paper/appendixB.Rmd
Add examples of Bodini et al. (2009) + Allesina et al. (2009)

---
title: Appendix B - Dominator tree and redundancy
subtitle:
author: Alain Danet, Loubna El Madouri, Maud Mouchet, Elisa Thébault and Colin Fontaine
date: \today
output:
  bookdown::pdf_document2:
    fig_caption: true
    keep_tex: true
    toc: false
fontsize: 10pt
header-includes:
   - \newcommand{\beginsupplement}{\renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
   - \usepackage{float}
   - \usepackage{multirow}
   - \usepackage{booktabs}
   - \usepackage{makecell}
   - \usepackage{setspace}
   - \doublespacing
   - \usepackage{lineno}
   - \linenumbers
   - \renewcommand{\arraystretch}{1}
geometry: margin=2cm
bibliography: references.bib
number_sections: false
---

```{r, echo=FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.align = "center",
  fig.fullwidth = TRUE,
  fig.show = "hold",
  fig.pos = "H",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE
)
options(
  #kableExtra.latex.load_packages = FALSE,
  knitr.table.format = "latex",
  knitr.graphics.rel_path = FALSE
)
```

```{r, echo=FALSE, message=FALSE, results="hide"}
library(targets)
library(tidyverse)
library(magrittr)
library(cowplot)
library(kableExtra)
library(igraph)

mypath <- rprojroot::find_package_root_file
source(mypath("R/variable_shortcut.R")) # Define your custom code as a bunch of
#functions.
source(mypath("R/misc.R"))
source_dir(mypath("R")) # Define your custom code as a bunch of functions.

mytheme <- theme_cowplot() +
  background_grid()

theme_set(mytheme)
old_par <- par()
```

\beginsupplement

As each trophic link does not contribute equally to the robustness of an
ecological network. In particular in a food-web, ....[Explain why the metric is
really cool]

[Implementation] An developed approach is based on the use of denomitor trees
[@bodini_using_2009; @allesina_who_2004; @allesina_functional_2009].
[...] The number of functional and redundant links are straightforward to
compute We computed the number of redundant and functional links using the
dominator tree approach [@allesina_functional_2009]. A species
$i$ is a dominator of species $j$ if $i$ mediates the connection $j$ to basal
resources such as the extinction of $i$ remove the connection of $j$ to basal
resources. It is then to identify the set of trophic links that are essential to
connect species to basal resources, i.e. functional links, and the
redundant links. This method requires a single basal root in the food-webs.

Pioneer papers explained the algorithm [@bodini_using_2009] and examples.
Replicating the algorithm could seem somewhat intimitating at the time, but the
computing the dominator tree of a food-web became straightforward. In R, it is
available in `igraph::dominator_tree()`. Below is presented the function and an
example of how to use it to compute functional and redundant links.

```{r, echo = TRUE}
compute_redundancy
```

```{r}
# Get the food-web example from Bodini et al. (2009), Appendix 1 
get_bodini_graph_appendix
out <- compute_redundancy(get_bodini_graph_appendix(), root = "R")
as.data.frame(out)
```

We used this function to reproduce the
two examples (Fig. \@ref(fig:bod1), \@ref(fig:)) showcased in the Fig.1 and Appendix
1 of @bodini_using_2009 , and the example (Fig. \@ref(fig:)) presented in the Fig.1 of
@allesina_functional_2009.

(ref:bod1-cap) bodin cap

```{r bod1, fig.cap="(ref:bod1-cap)"}
par(mfrow = c(1, 2))

bodinifig1 <- get_bodini_graph_fig1()

# Complete graph
lg <- layout_as_tree(bodinifig1, root = "root")
lg[, 2] <- -lg[, 2]
plot(bodinifig1, layout = lg, main = "Redundant & Functional\nlinks")

# Only functional links
bodinifig1_dtree <- dominator_tree(bodinifig1, root = "root")
layout <- layout_as_tree(bodinifig1_dtree$domtree, root = "root")
layout[, 2] <- -layout[, 2]
plot(bodinifig1_dtree$domtree, layout = layout, main = "Functional\nlinks only")
```

```{r bod2}
par(mfrow = c(1, 2))

g <- get_bodini_graph_appendix()

# Complete graph
lg <- layout_as_tree(g, root = "R")
lg[, 2] <- -lg[, 2]
plot(g, layout = lg, main = "Redundant + Functional\nlinks")

# Only functional links
dtree <- dominator_tree(g, root = "R")
layout <- layout_as_tree(dtree$domtree, root = "R")
layout[, 2] <- -layout[, 2]
plot(dtree$domtree, layout = layout, main = "Functional\nlinks only")
```

```{r all1}
par(mfrow = c(1, 2))

allesinafig1 <- get_allesina_graph(diag = FALSE)
lg <- layout_as_tree(allesinafig1, root = "0")
lg[, 2] <- -lg[, 2]
plot(allesinafig1, layout = lg, main = "Redundant + Functional\nlinks")

# Only functional links
allesinafig1_dtree <- dominator_tree(allesinafig1, root = "0")
layout <- layout_as_tree(allesinafig1_dtree$domtree, root = "0")
layout[, 2] <- -layout[, 2]
plot(allesinafig1_dtree$domtree, layout = layout,
  main = "Functional\nlinks only")
```

```{r}
examples <- list(
  bodiniappendix = g,
  bodinifig1 = bodinifig1,
  allesinafig1 = allesinafig1
)
redundancy_examples <- map2_dfr(
  examples,
  list(bodiniappendix = "R", bodinifig1 = "root", allesinafig1 = "0"),
  ~compute_redundancy(.x, root = .y), .id = "reference")
```

```{r}
paper_replacement <- c(
  bodinifig1 = "Bodini et al. (2009) Fig. 1",
  bodiniappendix = "Bodini et al. (2009) Supp material 1",
  allesinafig1 = "Allesina et al. (2009) Fig. 1"
)

redundancy_var_replacement <- function() {
  c(
    reference = "References",
    functional_links = "Nb functional links",
    redundant_links = "Nb redundant links",
    total_links = "Nb links",
    prop_functional_links = "Prop. functional links",
    prop_redundant_links = "Prop. redundant links"
  )
}

redundancy_examples %>%
  select(reference, total_links,
    functional_links, redundant_links,
    prop_functional_links, prop_redundant_links
  ) %>%
  mutate(reference = paper_replacement[reference]) %>%
  rename_with(~redundancy_var_replacement()[.x]) %>%
  kable(
    digits = 2,
    row.names = FALSE,
    booktabs = T,
    caption = "Computation of the number (Nb) of functional, redundant links, and
    their proportion (Prop.) from previous published examples.",
    label = "inlarand") %>%
  collapse_rows(columns = c(1), valign = "top") %>%
  kable_styling(latex_options = "scale_down")
```

# References {-}

### 2024-11-14 R/network_methods.R

@@ -138,7 +138,8 @@ compute_gini <- function (mat) {
 #' Computes redundant and functional links.
 #'
 #' @examples
-#' The example from Allesina et al. (2009) https://doi.org/10.1098/rstb.2008.0214
+#' The example from Bodini et al. (2009): https://doi.org/10.1098/rstb.2008.0278
+#' https://royalsocietypublishing.org/action/downloadSupplement?doi=10.1098%2Frstb.2008.0278&file=rstb20080278supp01.doc
 #' tu_names <- c("R", "Sediment_1", "POC", "Benthos", "Zooplankton")
 #' tu <- matrix(
 #'   c(
@@ -158,7 +159,7 @@ compute_gini <- function (mat) {
 #' plot(dtree$domtree, layout=layout, vertex.label=V(dtree$domtree)$name)
 get_redundancy <- function(x = NULL) {
   # Get a root "R" to compute dominant tree
-  root_names <- c("R","det", "biof", "phytopl")
+  root_names <- c("R", "det", "biof", "phytopl")
   root_mat <- matrix(
     c(
       0, 1, 1, 1,
@@ -168,7 +169,11 @@ get_redundancy <- function(x = NULL) {
       ), nrow = 4, byrow = TRUE,
     dimnames = list(root_names, root_names)
   )
-  root_graph <- igraph::graph_from_adjacency_matrix(root_mat, mode = "directed", diag = FALSE)
+  root_graph <- igraph::graph_from_adjacency_matrix(
+    root_mat,
+    mode = "directed",
+    diag = FALSE
+  )
 
   # Check for starving fish nodes
   no_int <- colnames(x)[colSums(x) == 0]
@@ -183,23 +188,89 @@ get_redundancy <- function(x = NULL) {
       prop_functional_links = NA
     )
   } else {
-
     mygraph <- igraph::graph_from_adjacency_matrix(x, mode = "directed", diag = FALSE)
     rooted_graph <- mygraph + root_graph
-    dtree <- igraph::dominator_tree(rooted_graph, root="R", mode = "out")
-    functional_links <- length(igraph::E(dtree$domtree))
-    total_links <- length(igraph::E(rooted_graph))
-    redundant_links  <- total_links - functional_links
+    out <- compute_redundancy(rooted_graph = rooted_graph)
+  }
+  out
+}
 
[…]

### 2024-11-14 draft.R

@@ -12,134 +12,10 @@ library(lme4)
 library(INLA)
 lapply(list.files(here::here("R"), full.names = TRUE), source)
 
-map2(p_list_sem_tps, names(p_list_sem_tps),
-  function(p, name) {
-    tmp <- p +
-      theme_half_open()
-    p_name <- str_replace(name, "p_", "tps_")
-
-    ggsave(
-      filename = here::here("figures", paste0(p_name, ".pdf")),
-      plot = tmp,
-      scale = 2.0,
-      width = 88,
-      height = 88 * .8,
-      units = "mm"
-    )
-  }
-)
+library(sf)
+tar_load(c(basin_dce, station_analysis))
 
 tar_load(full_data2)
 
-v_colors <- viridisLite::viridis(n = 2, begin = 0.5, end = 1)
-names(v_colors) <- c("tps", "sp")
+library(igraph)
 
-tps_dec_inc <- map(c("log_bm_std", "log_rich_std", "prop_redundant_links", "connectance", "w_trph_lvl_avg"), #
-  function(x) {
-    tmp <- plot_temporal_variable_lm(
-      st = "9561",
-      var = x,
-      add_median = FALSE,
-      col_median = v_colors["sp"],
-      col_trend = v_colors["tps"]
-      ) +
-    theme_half_open() +
-    theme(axis.title = element_text(size = 12))
-  tmp$layers[[1]]$aes_params$size <- 4
-  tmp
-  }
-)
-
-ex_tps_net <- plot_grid(plotlist = tps_dec_inc)
-ggsave_multiple(
-  paste0("example_tps_net", c(".png", ".pdf")),
-  plot = ex_tps_net,
-  path = here::here("figures"),
-  scale = 1.8,
-  width = 120,
-  height = 120 * .6,
-  units = "mm")
-
-tar_load(semeff_tot)
-
-# Talk EEB sheffield
-tps_dec_inc <- map(c("log_bm_std", "log_rich_std", "prop_redundant_links"), #
-  function(x) {
-    tmp <- plot_temporal_variable_lm(
-      st = "9561",
-      var = x,
-      add_median = FALSE,
-      col_median = v_colors["sp"],
-      col_trend = v_colors["tps"]
-      ) +
-    theme_half_open() +
-    theme(axis.title = element_text(size = 12))
-  tmp$layers[[1]]$aes_params$size <- 4
-  tmp
-  }
-)
[…]

### 2024-11-18 paper/appendixB.Rmd
Make appendix B to explain redundancy metrics

@@
 subtitle:
-author: Alain Danet, Loubna El Madouri, Maud Mouchet, Elisa Thébault and Colin Fontaine
+author:
 date: \today
@@
 
-As each trophic link does not contribute equally to the robustness of an
-ecological network. In particular in a food-web, ....[Explain why the metric is
-really cool]
+Because species are interdependant, species loss can have cascading effects and
+triger secondary extinctions [@dunne_network_2002]. So assessing the robustness
+of ecological networks to species losses has been a big question in Ecology.
+Previous research showed that food-web structure, such as connectance, increased
+robustness [@dunne_network_2002]. The idea is that more connected food-web will
+be more stable because they contain a large number of pathways convey biomass
+through the food-web. However, connectance as some limitations as a robustness
+metric has some limitations, because each trophic link does not contribute
+equally to the robustness of an ecological network. Trophic links can be as
+functional or redundant, depending on their role in transmitting biomass through
+the food-web. Functional links are the set of links that is required to connect
+every species to the basal resource of the food-web, all of the other being
+redundant. Only functional links affect directly robustness, as their removal
+will trigger secondary extinctions. The removal of redundant links in turn do
+not trigger secondary extinctions, but makes the food-webs more fragile to
+further extinctions [@allesina_functional_2009].
 
-[Implementation] An developed approach is based on the use of denomitor trees
-[@bodini_using_2009; @allesina_who_2004; @allesina_functional_2009].
-[...] The number of functional and redundant links are straightforward to
-compute We computed the number of redundant and functional links using the
-dominator tree approach [@allesina_functional_2009]. A species
-$i$ is a dominator of species $j$ if $i$ mediates the connection $j$ to basal
-resources such as the extinction of $i$ remove the connection of $j$ to basal
-resources. It is then to identify the set of trophic links that are essential to
-connect species to basal resources, i.e. functional links, and the
-redundant links. This method requires a single basal root in the food-webs.
-
-Pioneer papers explained the algorithm [@bodini_using_2009] and examples.
-Replicating the algorithm could seem somewhat intimitating at the time, but the
-computing the dominator tree of a food-web became straightforward. In R, it is
-available in `igraph::dominator_tree()`. Below is presented the function and an
-example of how to use it to compute functional and redundant links.
+The identification of functional and redundant links is based on the use of
+denomitor trees [@bodini_using_2009; @allesina_who_2004;
+@allesina_functional_2009]. Dominator trees allows to identify the set of
+trophic links that are essential to connect species to basal resources, i.e.
+functional links, and the redundant links. Pioneer papers explained the
+algorithm to compute the set of dominator trees and I refer to them for further
+information [@bodini_using_2009; @allesina_who_2004; @allesina_functional_2009]
+and examples. Here, we aim to show that while implementing this algorithm could
+seem somewhat intimitating at the time, this algorithm is now widely
+implemented. In R, it is available in `igraph::dominator_tree()`. Below we show
+how functional and redundant links can be computed easily from R by replicating
+three examples presented in previous studies.
 
@@
 
-```{r}
+Here is an example with the food-web displayed in appendix of
+@bodini_using_2009:
+
+```{r, echo = TRUE}
 # Get the food-web example from Bodini et al. (2009), Appendix 1 
-get_bodini_graph_appendix
-out <- compute_redundancy(get_bodini_graph_appendix(), root = "R")
+g <- get_bodini_graph_appendix()
+# compute reduncancy
+out <- compute_redundancy(g, root = "R")
 as.data.frame(out)
@@
 
-We used this function to reproduce the
-two examples (Fig. \@ref(fig:bod1), \@ref(fig:)) showcased in the Fig.1 and Appendix
-1 of @bodini_using_2009 , and the example (Fig. \@ref(fig:)) presented in the Fig.1 of
-@allesina_functional_2009.
+```{r}
+vertex_color <- "white"
+vertex_size  <- 40
+```
 
-(ref:bod1-cap) bodin cap
+We used this function to reproduce the three examples (Fig. \@ref(fig:examples)),
+which were displayed in the Fig.1 and Appendix 1 of @bodini_using_2009, and
+in the Fig.1 of @allesina_functional_2009. The table \@ref(tab:redun) displays
+the number and the proportion of functional and redundant links.
 
-```{r bod1, fig.cap="(ref:bod1-cap)"}
-par(mfrow = c(1, 2))
-
+```{r bod1}
 bodinifig1 <- get_bodini_graph_fig1()
@@
 # Complete graph
+p_bodinifig1_all <- ~{
   lg <- layout_as_tree(bodinifig1, root = "root")
   lg[, 2] <- -lg[, 2]
-plot(bodinifig1, layout = lg, main = "Redundant & Functional\nlinks")
+  plot(bodinifig1, layout = lg, vertex.color = vertex_color, vertex.size = vertex_size)
+}
 
@@
 bodinifig1_dtree <- dominator_tree(bodinifig1, root = "root")
+p_bodinifig1_functional <- ~{
   layout <- layout_as_tree(bodinifig1_dtree$domtree, root = "root")
   layout[, 2] <- -layout[, 2]
-plot(bodinifig1_dtree$domtree, layout = layout, main = "Functional\nlinks only")
+  plot(bodinifig1_dtree$domtree, layout = layout, vertex.color = vertex_color, vertex.size = vertex_size)
+}
 ```
 
-```{r bod2}
-par(mfrow = c(1, 2))
-
+```{r bod2, echo = FALSE, results = "hide"}
 g <- get_bodini_graph_appendix()
@@
 # Complete graph
+p_bodiniappen_all <- ~{
   lg <- layout_as_tree(g, root = "R")
   lg[, 2] <- -lg[, 2]
-plot(g, layout = lg, main = "Redundant + Functional\nlinks")
+  plot(g, layout = lg, vertex.color = vertex_color, vertex.size = vertex_size)
+}
 
@@
 dtree <- dominator_tree(g, root = "R")
-layout <- layout_as_tree(dtree$domtree, root = "R")
-layout[, 2] <- -layout[, 2]
-plot(dtree$domtree, layout = layout, main = "Functional\nlinks only")
+p_bodiniappen_functional <- ~{
+  lg <- layout_as_tree(dtree$domtree, root = "R")
+  lg[, 2] <- -lg[, 2]
+  plot(
+    dtree$domtree,
+    layout = lg,
+    vertex.color = vertex_color,
+    vertex.size = vertex_size
+  )
+}
+
+p_bodini <- plot_grid(
+  ggdraw(p_bodinifig1_all), ggdraw(p_bodinifig1_functional),
+  ggdraw(p_bodiniappen_all), ggdraw(p_bodiniappen_functional),
+  labels = "auto"
+)
+ggsave_multiple(
+  paste0("p_bodini", c(".png", ".pdf")),
+  plot = p_bodini,
+  path = here::here("figures"),
+  scale = 2.6,
+  units = c("mm"),
+  width = 80,
+  height = 80 * 1.5)
 ```
 
-```{r all1}
-par(mfrow = c(1, 2))
+```{r all1, echo = FALSE, results = "hide"}
+allesinafig1 <- get_allesina_graph(diag = FALSE)
 
-allesinafig1 <- get_allesina_graph(diag = FALSE)
+p_allesinafig1_all <- ~{
   lg <- layout_as_tree(allesinafig1, root = "0")
   lg[, 2] <- -lg[, 2]
-plot(allesinafig1, layout = lg, main = "Redundant + Functional\nlinks")
+  plot(allesinafig1, layout = lg, vertex.color = vertex_color, vertex.size = vertex_size)
+}
 
@@
 allesinafig1_dtree <- dominator_tree(allesinafig1, root = "0")
+p_allesinafig1_functional <- ~{
   layout <- layout_as_tree(allesinafig1_dtree$domtree, root = "0")
   layout[, 2] <- -layout[, 2]
-plot(allesinafig1_dtree$domtree, layout = layout,
-  main = "Functional\nlinks only")
+  plot(
+    allesinafig1_dtree$domtree,
+    layout = layout,
+    vertex.color = vertex_color,
+    vertex.size = vertex_size
+  )
+}
+
+p_examples <- plot_grid(
+  ggdraw(p_bodinifig1_all), ggdraw(p_bodinifig1_functional),
+  ggdraw(p_bodiniappen_all), ggdraw(p_bodiniappen_functional),
+  ggdraw(p_allesinafig1_all), ggdraw(p_allesinafig1_functional),
+  nrow = 3,
+  labels = "auto"
+)
+ggsave_multiple(
+  paste0("p_examples", c(".png", ".pdf")),
+  plot = p_examples,
+  path = here::here("figures"),
+  scale = 4.0,
+  units = c("mm"),
+  width = 80,
+  height = 80 * 1.2)
+```
+
+(ref:example-cap) Reproduced examples of categorising functional links in
+food-webs using `igraph::dominator_tree()` R function. Left columns (a, c, e)
+displays the complete food-web while right column displays food-web with the
+functional links only (b, d, f). (a,b): reproduction of Fig. 1 of
+@bodini_using_2009, (c, d): reproduction of appendix figures of @bodini_using_2009,
+(e, f): reproduction of fig. 1 of @allesina_functional_2009. Note that (e, f) is
+a bit different from the original, as noted by the authors, they could have
+removed further redundant links (i.e. $2 \to 5$, or $3 \to 5$).
+
+```{r examples, fig.cap = "(ref:example-cap)", out.height = "80%"}
+knitr::include_graphics(here::here("figures", "p_examples.png"))
 ```
@@
     row.names = FALSE,
+    label = "redun",
     booktabs = T,
     caption = "Computation of the number (Nb) of functional, redundant links, and
-    their proportion (Prop.) from previous published examples.",
-    label = "inlarand") %>%
+    their proportion (Prop.) from previous published food-webs.",
+    ) %>%
   collapse_rows(columns = c(1), valign = "top") %>%

### 2025-02-03 paper/appendix.Rmd
Manuscript update before Maud & Colin comments

@@
 ---
-title: Appendix
-subtitle:
-author: Alain Danet, Loubna El Madouri, Maud Mouchet, Elisa Thébault and Colin Fontaine
-date: \today
+title: "Biodiversity changes are linked to changes in food-web structure and redundancy in riverine ecosystems"
+subtitle: "Alain Danet (a,b), Loubna El Madouri (a,c), Andrew P. Beckerman (b),
+Maud Mouchet (a), Colin Fontaine (a) and Elisa Thébault (d)"
+date: Supplementary figures and tables
 output:

### 2025-02-03 paper/appendixB.Rmd
Manuscript update before Maud & Colin comments

@@
 ---
-title: Appendix B - Dominator tree and redundancy
-subtitle:
-author:
-date: \today
+title: "Biodiversity changes are linked to changes in food-web structure and redundancy in riverine ecosystems"
+subtitle: "Alain Danet (a,b), Loubna El Madouri (a,c), Andrew P. Beckerman (b),
+Maud Mouchet (a), Colin Fontaine (a) and Elisa Thébault (d)"
+date: Appendix B - Computation of redundancy of trophic pathways in food webs
 output:
@@
 
-Because species are interdependant, species loss can have cascading effects and
-triger secondary extinctions [@dunne_network_2002]. So assessing the robustness
-of ecological networks to species losses has been a big question in Ecology.
-Previous research showed that food-web structure, such as connectance, increased
+Because species biomass are involved in trophic interactions, species losses can
+have cascading effects and trigger secondary extinctions [@dunne_network_2002].
+In the context of biodiversity crisis, assessing the robustness of ecological
+networks to species losses has been then a big question in Ecology. Previous
+research showed that food-web structure, such as connectance, increased
 robustness [@dunne_network_2002]. The idea is that more connected food-web will
@@
 through the food-web. However, connectance as some limitations as a robustness
-metric has some limitations, because each trophic link does not contribute
-equally to the robustness of an ecological network. Trophic links can be as
+metric, because each trophic link does not contribute equally to the robustness
+of an ecological network [@allesina_who_2004]. Trophic links can be categorised as
 functional or redundant, depending on their role in transmitting biomass through
@@
 will trigger secondary extinctions. The removal of redundant links in turn do
-not trigger secondary extinctions, but makes the food-webs more fragile to
-further extinctions [@allesina_functional_2009].
+not directly trigger secondary extinctions, but makes the food-webs more fragile
+to further extinctions [@allesina_functional_2009].
 
 The identification of functional and redundant links is based on the use of
-denomitor trees [@bodini_using_2009; @allesina_who_2004;
+denominator trees [@bodini_using_2009; @allesina_who_2004;
 @allesina_functional_2009]. Dominator trees allows to identify the set of
-trophic links that are essential to connect species to basal resources, i.e.
-functional links, and the redundant links. Pioneer papers explained the
-algorithm to compute the set of dominator trees and I refer to them for further
-information [@bodini_using_2009; @allesina_who_2004; @allesina_functional_2009]
-and examples. Here, we aim to show that while implementing this algorithm could
-seem somewhat intimitating at the time, this algorithm is now widely
-implemented. In R, it is available in `igraph::dominator_tree()`. Below we show
-how functional and redundant links can be computed easily from R by replicating
-three examples presented in previous studies.
+trophic links that are essential to connect all the consumers to the basal resource, i.e.
+the functional links, and the redundant links, i.e. the redundant trophic pathways
+from basal resource to consumers. Pioneer papers explained the algorithm to
+compute the set of dominator trees and we refer to them for further
+information and examples [@bodini_using_2009; @allesina_who_2004;
+@allesina_functional_2009]. Here, we aim to show that while implementing this
+analysis could be difficult at the time, this algorithm is now widely
+available. In R, it is available in `igraph::dominator_tree()`. Below we show
+how the number of functional and redundant links can be  easily computed from R
+by replicating three examples presented in previous studies.
 
@@
 We used this function to reproduce the three examples (Fig. \@ref(fig:examples)),
-which were displayed in the Fig.1 and Appendix 1 of @bodini_using_2009, and
-in the Fig.1 of @allesina_functional_2009. The table \@ref(tab:redun) displays
-the number and the proportion of functional and redundant links.
+which were displayed in the Fig. 1 and Appendix 1 of @bodini_using_2009, and
+in the Fig. 1 of @allesina_functional_2009. The table \@ref(tab:redun) displays
+the number and the proportion of functional and redundant links from those
+examples.
 
@@
 (ref:example-cap) Reproduced examples of categorising functional links in
-food-webs using `igraph::dominator_tree()` R function. Left columns (a, c, e)
+food webs using `igraph::dominator_tree()` R function. Left columns (a, c, e)
 displays the complete food-web while right column displays food-web with the

### 2025-02-03 paper/manuscript.Rmd
Manuscript update before Maud & Colin comments

@@
 ---
-title: "Temporal dynamics of food-web structure in response to biodiversity changes in riverine ecosystems"
-author: "Alain Danet (a,b), Loubna El Madouri (a,c), Maud Mouchet (a), Elisa Thébault (d) and Colin Fontaine (a)"
+title: "Biodiversity changes are linked to changes in food-web structure and redundancy in riverine ecosystems"
+subtitle: "Alain Danet (a,b), Loubna El Madouri (a,c), Andrew P. Beckerman (b),
+Maud Mouchet (a), Colin Fontaine (a) and Elisa Thébault (d)"
 date: "Research report"
@@
     base_format: "bookdown::word_document2"
-  bookdown::pdf_document2:
-    latex_engine: xelatex
-    keep_tex: true
-    spacing: double
-    number_sections: false
 always_allow_html: true
@@
 
-(b) Department of Biosciences, Alfred Denny Building, University of Sheffield,
+(b) School of Biosciences, Alfred Denny Building, University of Sheffield,
 Western Bank, Sheffield S10 2TN, United Kingdom
@@
 
-- Keywords: food-web, biodiversity changes, assembly rules, space-for-time
-
-# Abstract (250 / 250 words max)
-
-While there are widespread evidence of biodiversity decline, little is known how
-food-web disassemble in response. Such knowledge is crucial as food-web
-structure determine ecosystem functioning and stability to perturbations.
-However, assessing how changes in biodiversity affect changes in food-web
-structure require the availability of food-web timeseries and to account for the
-differential effects of different biodiversity facets on food-web structure.
-Here, we used a standardized monitoring of riverine fish communities over the
-last decades (1995-2018) in France, from which we inferred the food-web
-structure for each sampling events using diet data and allometric scaling rules.
-We estimated the temporal trends in community biomass, species richness, and
-food-web structure using hierarchical Bayesian models. We assessed the effects
-of community biomass and species richness temporal changes on temporal changes
-in food-web structure: connectance, average trophic level and redundancy. We
-further assess the generality and robustness of our findings by replicating the
-analysis over space and using theoretical simulations with a bioenergetic model.
-Our results suggest that food-webs that experienced a decline in community
-biomass experienced conjointly a loss of species at upper trophic levels and
-conversely. While species richness temporal trends had less clear effects on
-food-web structure, mainly due through its indirect effects on community biomass
-temporal trends. Both community biomass and species richness declines were
-associated with a decrease in redundancy, raising concerns about robustness of
-such communities to further perturbations. Our study highlights how biodiversity
-changes affect food-web structure, raising concerns about consequences on
-ecosystem functioning and robustness.
-
-# Significance (109 / 120 words max)
-
-Biodiversity temporal changes can lead to simultaneous changes in food-web
-structure, which is turn can have consequences on ecosystem functioning and
-stability. We provide empirical evidence that temporal changes in community
-biomass and species richness are linked to changes contrasted assembly and
-disassembly processes in food-webs in natural settings. We then show that loss
-in both community biomass and species richness are related to a loss of
-redundancy in the food-webs, which raise concerns about the robustness of such
-communities to perturbations. We further added spatial and theoretical evidence
-suggesting that our results are quite robust and open to assess how biodiversity
-changes might affect ecosystem functioning and robustness.
+- Keywords: food web structure, biodiversity changes, redundancy, biodiversity &
+  ecosystem functioning
+
+# Abstract (152 / 250 words max)
+
+Changes in biodiversity can fundamentally alter ecological communities, yet how
+these changes affect food web structure remains poorly understood. Here, we
+analyze temporal trends in over 400 riverine fish communities across France
+spanning 1995-2018, examining relationships between species richness, community
+biomass, and three key metrics of food web structure: connectance, weighted
+average trophic level, and trophic pathway redundancy. Using structural equation
+modeling, theoretical simulations, and robustness analyses, we demonstrate that declining
+community biomass leads to loss of top trophic levels and decreased food web
+connectance, while species richness negatively correlates with connectance but
+positively affects trophic redundancy. Notably, both biomass and species
+richness positively influence the proportion of redundant trophic links,
+suggesting that biodiversity loss reduces community robustness to future
+perturbations. Our findings, consistent across temporal, spatial, and
+theoretical approaches, reveal how biodiversity change restructures food webs
+and highlights the utility of food web metrics as indicators of ecosystem
+function and fragility.
+
+# Significance (124 / 120 words max)
+
+Understanding how biodiversity loss affects ecological communities is crucial
+for predicting and mitigating human impacts on ecosystems. This study
+provides comprehensive evidence linking biodiversity changes to food web
+structure using an extensive dataset of riverine fish communities. We
+demonstrate that changes in community biomass and species richness
+systematically alter food web architecture, affecting trophic levels,
+connectance, and the redundancy of feeding relationships. Our findings unite
+multiple ecological theories, showing how energetic constraints and
+biodiversity-ecosystem functioning mechanisms jointly shape food web assembly
+and disassembly. Importantly, we show that declining biodiversity reduces the
+redundancy of trophic pathways, potentially making communities more vulnerable
+to future perturbations. These results suggest that food web structure metrics
+could serve as valuable indicators for monitoring ecosystem health and
+evaluating conservation strategies.
 
@@
 
-Biodiversity is experiencing massive declines due to continuously increasing
-human pressures, which is expected to have striking consequences on ecosystem
-functioning and fragility. It is increasing recognised that biodiversity
-changes are widely heterogeneous spatially [@mcgill_fifteen_2015;
-@blowes_geography_2019], such as species richness declines and increases can be
-related to spatial variations in human pressures [@cardinale_is_2018;
-@danet_past_2024]. Biodiversity changes result in altered community structure
-[@dornelas_assemblage_2014; @hillebrand_biodiversity_2018; @danet_past_2024],
-but so far, one key component of biodiversity, species interactions, has been
-mostly ignored by studies assessing temporal changes in biodiversity, despite
-the importance of biotic interactions for species coexistence, ecosystem
-functioning and stability [@chesson_mechanisms_2000; @thebault_food-web_2003;
-@oconnor_general_2017; @danet_species_2021]. A better understanding of
-biodiversity changes will then need to account how biodiversity changes alter
-the structure of ecological networks.
-
-Yet, both species richness and food-web structure have a significant impact on
-coexistence [@chesson_interaction_2008], ecosystem functioning
-[@thebault_food-web_2003; @wang_biodiversity_2018], stability
-[@danet_species_2021; @eschenbrenner_diversity_2023], and ecosystem robustness
-to perturbations [@dunne_network_2002; @allesina_functional_2009;
-@bodini_using_2009; @allesina_functional_2009]. Many predator species play a
-keystone role by protecting preys from competitive exclusion
-[@heithaus_predicting_2008; @johnson_rarity_2007; @estes_trophic_2011], thereby
-maintaining species richness. Food-web with higher trophic levels also increase
-ecosystem productivity [@thebault_food-web_2003; @wang_biodiversity_2018] and
-community temporal stability [@danet_species_2021;
-@eschenbrenner_diversity_2023]. Finally, the number and distribution of trophic
-links in food-webs determine the robustness of communities to perturbations
+Ecological communities are experiencing massive changes due to human pressures,
+which are expected to have striking consequences on ecosystem functioning and
+fragility. It is increasingly recognized that such changes across space are
+associated with spatial variations in human pressures [@mcgill_fifteen_2015;
+@blowes_geography_2019], such as freshwater
+and terrestrial biodiversity declines linked to land degradation
+[@newbold_global_2015; @cardinale_is_2018; @danet_past_2024], and declining
+biomass of marine fishes linked to increased fishing pressures on predatory
+fishes [@christensen_century_2014]. These documented changes in diversity and
+biomass result in altered community structure and composition
+[@dornelas_assemblage_2014; @hillebrand_biodiversity_2018; @danet_past_2024].
+
+The structure of ecological networks, which describe the number, distribution
+and strength of interactions among species, is important because it, along with
+species richness per se, underpins species coexistence, ecosystem functioning
+and the stability of ecological dynamics and ecosystem function
+[@chesson_interaction_2008; @thebault_food-web_2003; @oconnor_general_2017;
+@danet_species_2021; @eschenbrenner_diversity_2023; @danet_response_2024].
+Theory and empirical data have shown that species richness and food-web
+structure impact on coexistence [@chesson_interaction_2008], ecosystem
+functioning [@thebault_food-web_2003; @wang_biodiversity_2018], stability
+[@danet_species_2021; @danet_response_2024; @eschenbrenner_diversity_2023], and
+ecosystem robustness to perturbations [@dunne_network_2002;
+@allesina_functional_2009; @bodini_using_2009; @allesina_functional_2009].
+Keystone predator species regulating dominant competitors can limit competitive
+exclusion [@heithaus_predicting_2008; @johnson_rarity_2007;
+@estes_trophic_2011], and thereby maintain species richness. Food-webs with
+higher trophic levels are linked to elevated  ecosystem productivity
+[@thebault_food-web_2003; @wang_biodiversity_2018] and community temporal
+stability [@danet_species_2021; @eschenbrenner_diversity_2023;
+@danet_response_2024]. Finally, the number and distribution of trophic links in
+food-webs determine the robustness of communities to perturbations
 [@dunne_network_2002; @allesina_functional_2009; @bodini_using_2009;
-@allesina_functional_2009]. Accounting for how food-web assemble and disassemble
-according to biodiversity changes is then crucial to evaluate the consequences
-of biodiversity changes on ecosystem functioning and stability.
-
-However, assessing the effects of biodiversity changes on food-web structure
-requires the availability of multiple temporal timeseries of biodiversity and
-food-webs structure, to disentangle the direct and indirect effects of
-biodiversity changes on food-web structure, and to account for theories about
-the multiple constraints on food-web assembly. We propose to monitor three
-structural properties of food-webs and two common monitored biodiversity facets
-(i.e. community biomass and species) that are grounded in food-web assembly,
-ecosystem functioning, and stability research areas: connectance (i.e. degree of
-generalism), weighted average trophic level (i.e. vertical location of biomass),
-and redundancy (i.e. the proportion of redundant links). There are pieces of
-evidence to connect those food-web structural metrics to changes in ecosystem
-functioning and robustness that we review before to present the temporal
-timeseries that allows to assess them.
-
-Food-web assembly theory provides predictions on how food-web structure should
-change according to changes in community biomass and species richness. The
-energetic paradigm and the trophic theory of biogeography
-[@lindeman_trophic-dynamic_1942; @gravel_trophic_2011] stand that the presence
-of top predators is conditional on the presence of preys in number enough that
-it can provide enough energy from the bottom to the top to sustain high trophic
-level species. In turn, it can that the presence of generalist predators, which is
-positively associated to average trophic level and connectance, will be linked
-more to community biomass changes than to species richness. In turn, connectance
-and average trophic level are commonly reported to decrease with as species
-richness increases [@dunne_network_2006; @danet_species_2021] because predators
-are limited in the number of species they can consume and conversely preys are
-limited in the number of predator they can sustain. Food-web structure has also
-been linked to the robustness to species extinctions [@dunne_network_2002;
-@allesina_who_2004; @bodini_using_2009]. Historically having being linked to
-connectance, i.e. the number of links, more recent studies have proposed to
-separate links that are functional or redundant [@allesina_who_2004;
-@allesina_functional_2009; @bodini_using_2009]. The idea is that the loss of
-functional links will trigger secondary extinctions because it suppresses
-obligatory pathways from resources to consumers while the loss of redundant
-links do not remove such obligatory pathways [@allesina_who_2004]. It means that
-redundant trophic links enhance ecosystem robustness as they can be safely
-removed without triggering secondary extinctions. Thereby we expected that
-higher species richness results in higher redundancy in food-webs, meaning that
-they create more independent pathways connecting basal producers to higher
-trophic level. Finally, biodiversity and ecosystem functioning theory suggest
-that in context of significant niche complementarity, community biomass should
-be positively related to species richness [@wang_biodiversity_2018;
-@schneider_animal_2016], such as it is necessary to account for the indirect
-effects of species richness on food-web structure through community biomass.
-
-Here, we report on a study that combine empirical assessment of food-web
-structure and biodiversity temporal changes in natural settings, extinction
-simulations in empirical food-webs, and theoretical simulations using
-bioenergetic model. The availability of food-web timeseries used to be scarce
-[@kortsch_disentangling_2021], but the increasing availability of biodiversity
-timeseries and the development of methods to reconstruct food-webs
-[@bonnaffe_comparison_2021; @gravel_inferring_2013; @danet_species_2021] makes
-possible to overcome this limitation. We used a standardized monitoring of fish
-riverine communities on the period 1995-2018 over France, documenting the
-individual size of fishes in `r nb_st` sites during ten years or more (Table S1). We
-reconstructed around `r nb_op` food-webs based on allometric relationships and
-food diet data, and then computed connectance, and average trophic level
-weighted by trophic species biomass as well as community biomass and species
-richness (Fig. \@ref(fig:matmet)). This dataset and method has already been used
-in previous studies [@danet_species_2021; @bonnaffe_comparison_2021;
-@bonnaffe_interaction_2024]. Using hierarchical Bayesian models, we estimated
-temporal trends in food-web structure, community biomass and richness at each
-site [@danet_past_2024]. We then used structural equation models (SEM) to
-assess the effects of community biomass and species richness temporal changes on
-changes in food-web structure, while accounting for the effects of species
-richness on community biomass. We then assessed if those effects are holding in
-space, i.e. if the space-for-time substitution hypothesis hold
-[@blois_space_2013; @damgaard_critique_2019; @adler_contrasting_2007]. We did so
-by considering median values of food-web structure and community structure over
-the timeseries at each site (Fig. \@ref(fig:matmet)). Finally, we ran
-simulations using the bioenergetic model to assess if our results hold beyond
-our empirical fish food-webs.
+@allesina_functional_2009]. A better knowledge of the consequences of
+biodiversity change on the structure of ecological networks is thus necessary to
+quantify and mitigate anthropogenic driven changes to biodiversity.
+
+There are three key components to the mapping between biodiversity changes and
+food-web structure. First, the energetic paradigm underpinning the trophic
+theory of biogeography [@lindeman_trophic-dynamic_1942; @gravel_trophic_2011]
+posits that the presence of top consumers requires resources in enough numbers
+at lower trophic levels derived from bottom up productivity. From this, it can
+be further hypothesized that the presence of generalist top consumers will be
+strongly conditioned by the amount of community biomass.
+
+Second, connectance (the proportion of realized trophic links), is commonly
+reported to decrease as species richness increases [@oconnor_general_2017;
+@dunne_network_2006], because consumers are limited in the number of resources
+they can consume. Connectance has also been linked to the robustness to species
+extinctions [@dunne_network_2002; @allesina_who_2004; @bodini_using_2009]. More
+in detail, it is the prevalence of redundant (versus functional) links in food
+webs [@allesina_who_2004; @bodini_using_2009; @allesina_functional_2009], i.e.
+the redundancy of trophic pathways, that predicts ecosystem robustness as they
+can be safely removed without triggering secondary extinctions. We thus predict
+that higher species richness covaries with higher redundancy of trophic pathways
+in food-webs [@allesina_functional_2009]. Together, these relationships mean
+that biodiversity changes are likely to be associated with changes in trophic
+links distribution and then possibly to changes in robustness to perturbations,
+such as increases in species richness should increase the number of redundant
+trophic pathways to top predators and then increase community robustness.
+
+Finally, biodiversity and ecosystem functioning theory suggest specifically that
+community biomass should be positively related to species richness
+[@loreau_biodiversity_2001]. This arises specifically because of niche
+complementarity where species exploit different resources. In the particular
+case of food webs, theoretical studies show that the presence of higher trophic
+level species decreases niche overlap among producers which then increase
+productivity and community biomass [@schneider_animal_2016;
+@wang_biodiversity_2018; @wang_intraguild_2019; @nie_will_2023].
+
+Here, we report on an analysis of riverine fish community times series to
+document the ecological consequences of biodiversity changes on food web
+structure. We specifically aim to reveal the relationship between community
+biomass and species richness and three key metrics of food web structure:
+connectance, weighted average trophic level, and the proportion of redundant
+trophic links (hereafter “redundancy”). To do this, we implemented a sequence of
+analyses that allows us to enumerate these relationships as covariation among
+temporal trends. First, we estimated `r nb_op` food web structure for `r nb_st`
+fish communities with 10+ years of community dynamics spanning 1995-2018 over
+France (Fig. \@ref(fig:matmet)a-c, Table S1).  Second, using these food webs, we
+estimated the temporal trends in each of species richness, biomass, connectance,
+trophic structure and redundancy. Having estimated each temporal trend, we next
+constructed an SEM to make specific inference about the relative effects of
+community biomass and species richness  temporal trends on the temporal trends
+three metrics of food web structure, and the effect of species richness on
+community biomass (Fig. \@ref(fig:matmet)d). We also implemented a robustness analysis on the
+meta-food web (i.e. the food web grouping all trophic species found in the
+dataset and their inferred interactions) to identify species extinction
+scenarios that might explain the variation in food web structure that we see in
+the timeseries. Finally, we performed three further analysis to evaluate the
+robustness and the generality of our results. We replicated our temporal
+analysis with a space-for-time approach (Fig. \@ref(fig:matmet)c & e) using median metrics in
+each site instead of the temporal trends; we created a simulation of complex
+communities using a bioenergetic food web model to assess the generality of our
+results in complex communities that allow relaxation of some of the constraints
+defined by our fish biodiversity data; and we performed a three-scenario,
+topological secondary extinction analysis on the full empirical metaweb to
+evaluate the role of top predators on food-web structure.
 
 ```{r}
-fig_mat_cap <- paste0("Using sites of stream fishes in French streams that
-  have been monitored at least 10 years, 1) we inferred the food-web at each site
-and each sampling event based on ontogenic food diet information for each
-species and predator-prey body size ratio. 2) We computed the temporal trends
+fig_mat_cap <- paste0("Using ", nb_st," sites of stream fishes in (a) French streams that
+  have been monitored at least 10 years, (b) we reconstructed the food-web at each
+  site and each sampling event by building a metaweb based on ontogenic food diet information for each
+  species and predator-prey body size ratio. (c) We computed the temporal trends
   and the median of community biomass, species richness, connectance, average
-trophic level and evenness of biomass at each site. 3) We then assessed the
-relationships among food-web structure descriptors, (a) in time and (b) across space.")
+  trophic level, and redundancy at each site. We then assessed the relationships
+  among food web structure descriptors, (d) in time and (e) across
+  space. We additionally performed extinction simulations from the metaweb and
+  insilico experiments using a bioenergetic food web model to gain more insights
+  and assess the generality of our results (see Methods).")
 ```
@@
 
-Using a Bayesian hierarchical model to jointly estimate the temporal trends of
-food-web structure at all sites, we found weak evidence of an overall decrease
-in community biomass (CI80%:`r gbm` by decade; median [Credible Interval], Fig.
-S1) but no evidence of an overall temporal increase in species richness
-(CI80%: `r gr` by decade) across the `r nb_st` sites. We did not find evidence
-of average temporal trends in connectance and average trophic level (CI80%:
-`r gct` and `r gt` respectively), but an increase in redundancy (measured by the
-proportion of redundant links, CI80%: `r gl`). However, we found a great
-heterogeneity in the temporal trends estimated at the site level (community
-biomass: from `r grbmn`% to `r grbmx`% per decade, species richness: `r grrhn`
-to +`r grrhx`%, average trophic level: `r grtln` to +`r grtlx`, connectance:
-`r grctn` to +`r grctx`, redundancy: `r grln` to +`r grlx`, Fig. S1) which was
-well captured by the hierarchical model with conditional R2 going from
-`r r2cond$log_bm_std` for community biomass to `r r2cond$log_rich_std` for
-species richness (Table S2).
+## Estimating temporal trends
+
+Our food web reconstruction delivered `r nb_op` estimates of species richness,
+biomass, connectance, weighted average trophic level, and the proportion of
+redundant trophic links (hereafter "redundancy", see Appendix B) from our 403
+fish communities with 10+ years of population dynamics spanning 1995-2018 over
+France (Fig. 1a-c). We implemented Bayesian hierarchical models to jointly
+estimate the temporal trends in these metrics. We found a great heterogeneity in
+the temporal trends at the site level (community biomass: from `r grbmn`% to
+`r grbmx`% per decade, species richness: `r grrhn` to +`r grrhx`%, average
+trophic level: `r grtln` to +`r grtlx`, connectance: `r grctn` to +`r grctx`,
+redundancy: `r grln` to +`r grlx`, Fig. S1) which was effectively captured by
+the hierarchical model (with conditional R2 between `r r2cond$log_bm_std` for
+community biomass to `r r2cond$log_rich_std` for species richness, Table S2).
 
 ```{r}
-sem_cap <- "(a) Structural equation models linking the temporal trends of the food-web
-structure. The path widths are proportional to the standardized slope
+sem_cap <- "(a) Structural equation models linking the temporal trends of the
+food-web structure. The path widths are proportional to the standardized slope
 coefficients. The standardized slope coefficients and their associated 95%
-confidence intervals obtained by bootstrapping are displayed along the path. The
-marginal R-squared of the linear models are displayed. (b to f) Direct bivariate
-relationships derived from the structural equation model. The distribution of
-the site temporal trends are displayed in Fig. S1. All the effects are reported
-in Table S3."
+  confidence intervals obtained by bootstrapping are displayed along the path.
+R2 displays the marginal R-squared of the linear models. (b to h) Direct
+bivariate relationships derived from the structural equation model. Points
+display the temporal trends at each site estimated with a hierarchical Bayesian
+model, lines display the linear relationship estimated with the SEM. The
+distribution of the site temporal trends are displayed in Fig. S1. All the
+effects are reported in Table S3. Average trophic level is weighted by the
+biomass of the trophic species. Redundancy is the proportion of redundant
+links."
 ```
@@
 
-Using structural equation models to disentangle the direct and indirect effects
-of temporal trends in fish species richness and community biomass on temporal
-trends in food-web structure, we found a strong positive effect of the temporal
-trends in species richness on community biomass ($r_\delta =$ `r rdtps$bm$r`,
+## Association between biodiversity and food-web temporal trends
+
+These temporal trend estimations at the site level were the input to our SEM,
+allowing us to evaluate the direct and indirect effect of species richness and
+community biomass changes on food web structure changes and between species
+richness and community biomass. We detected a strong positive association
+between community biomass and in species richness ($r_\delta =$ `r rdtps$bm$r`,
 Fig. \@ref(fig:sem) a and b, $r_\delta$: standardized slope coefficient, [95%
-CI], Table S3), meaning that both temporal trends had the same direction in average. In
-other word, food-webs that have experienced a decrease in species richness over
-time have decreased in community biomass, and conversely, those that increased
-in species richness have increased in community biomass.
-Temporal trends in community biomass had in turn a positive effect on connectance,
+CI], Table S3). This indicates that communities with decreasing species richness
+over time experienced a concomitant decrease in community biomass and
+vice-versa.
+
+Our SEM also predicts a positive effect of community biomass on connectance,
 average trophic level, and redundancy (resp. $r_\delta =$ `r rdtps$ct$bm`,
-`r rdtps$tlvl$bm`, `r rdtps$red$bm`, Fig. \@ref(fig:sem)b, c, d), meaning that
-food-web whose community biomass decreased over time have decreased in
-connectance, average trophic level and redundancy, and
-conversely, those that have experienced an increase in biomass have increased in
-connectance, average trophic level and redundancy. We further found that the temporal
-trends of community biomass were positively associated to the temporal trends of
-both number and proportion of piscivorous species present (Fig. S2a), meaning
-biomass trends are linked to the presence of high trophic level trophic
-species.
-
-We further tested if we find the same patterns using spatial variations in
-food-web structure rather than temporal changes over time, i.e. if the
-space-for-time hypothesis hold. To do so, we used the same dataset and same
-structural equation model but with the median food-web structure per site
-instead of the temporal trends. We additionally performed theoretical
-simulations with a bioenergetic food-web model to further get theoretical
-expectations about how food-web structure changes according to community biomass and
-species richness variations (see Methods). As in temporal data, species richness
-had a positive effect on community biomass both in empirical data and in
-theoretical simulations (resp. $r_\delta =$ `r rdsp$bm$r` and `r rdm$bm$r`, Fig.
-\@ref(fig:std) and S3). In both empirical data and theoretical simulations, community
-biomass had a positive effect average trophic level (resp.
-$r_\delta =$ `r rdsp$tlvl$bm` and `r rdm$tlvl$bm`), and redundancy (resp.
-$r_\delta =$ `r rdsp$red$bm` and `r rdm$red$bm`), as in temporal analysis.
-We found weak evidence of a positive effect of spatial variation in community
-biomass on connectance in empirical data ($r_\delta =$ `r rdsp$ct$bm`) but
-strong evidence in theoretical simulation ($r_\delta =$ `r rdm$ct$bm`, Fig.
-\@ref(fig:std)).
-
-The effects of species richness were more complex, because species richness had
-indirect effects on food-web structure through community biomass. Temporal
-trends in species richness had a direct negative effect on connectance
-($r_\delta =$ `r rdtps$ct$r`, Fig. \@ref(fig:sem)f), a positive
-indirect effect through community biomass ($r_\delta =$ `r ridtps$ct$r`), so
-that species richness temporal trends had a negative effect in total on temporal in
-connectance ($r_\delta =$ `r rttps$ct$r`, Fig. \@ref(fig:std)).
-In contrast, temporal trends in species had no direct effects on the temporal
-trends in average trophic level ($r_\delta =$ `r rdtps$tlvl$r`, Fig.
-\@ref(fig:sem)g), a positive indirect effect through community
-biomass ($r_\delta =$ `r ridtps$tlvl$r`), which adds up to a positive total
-effect of species richness temporal trends on average trophic level ($r_\delta
-=$ `r rttps$tlvl$r`, Fig. \@ref(fig:std)). Species richness temporal trends had
-direct and indirect positive effect on the temporal trends in redundancy (resp.
-$r_\delta =$ `r rdtps$red$r`, `r ridtps$red$r`), which added up to a strong
-positive effect ($r_\delta =$ `r rttps$red$r`). Furthermore, we found that
-temporal trends of the proportion of piscivorous species was negatively
-associated with the temporal trends of species richness (Fig. S2), meaning that
-communities that increase in richness over time have an increase in the
-proportion of non-piscivorous species over time and vice versa. It means
-food-webs that have experienced declines in species richness over the last
-decades have decreased in average trophic level and redundancy but increase in
-connectance, and conversely, those that experienced increases in species
+`r rdtps$tlvl$bm`, `r rdtps$red$bm`, Fig. \@ref(fig:sem)b, c, d). Thus, when communities
+experienced a decrease in biomass, they also experimented a concomitant decrease
+in connectance, average trophic level and redundancy, and vice versa. We further
+found that the temporal trends in community biomass were positively associated
+with both the number and the proportion of piscivorous species (Fig. S2a),
+suggesting that the presence of high trophic level trophic species has a
+disproportionate role community biomass.
+
+The effects of species richness were more complex, because species richness in
+this model has indirect effects on food-web structure through community biomass.
+Species richness had a direct negative effect on connectance ($r_\delta =$
+`r rdtps$ct$r`, Fig. \@ref(fig:sem)f), a positive indirect effect through
+community biomass ($r_\delta =$ `r ridtps$ct$r`), so that species richness had a
+negative effect in total on connectance ($r_\delta =$ `r rttps$ct$r`, Fig.
+\@ref(fig:std)a). In contrast, species richness had no direct effects on in
+average trophic level ($r_\delta =$ `r rdtps$tlvl$r`, Fig. \@ref(fig:sem)g), a
+positive indirect effect through community biomass ($r_\delta =$
+`r ridtps$tlvl$r`), which adds up to a positive total effect of species richness
+temporal trends on average trophic level ($r_\delta =$ `r rttps$tlvl$r`, Fig.
+\@ref(fig:std)a). Species richness temporal trends had direct and indirect
+positive effect on the temporal trends in redundancy (resp. $r_\delta =$
+`r rdtps$red$r`, `r ridtps$red$r`), which added up to a strong positive effect
+($r_\delta =$ `r rttps$red$r`).
+
+Furthermore, we found that temporal trends of the proportion of piscivorous
+species was negatively associated with the temporal trends of species richness
+(Fig. S2), meaning that communities that increase in richness over time have an
+increase in the proportion of non-piscivorous species over time and vice versa.
+It means food-webs that have experienced declines in species richness over the
+last decades have decreased in average trophic level and redundancy but increase
+in connectance, and conversely, those that experienced increases in species
 richness have increased in average trophic level, redundancy, but decreased in
@@
 
+## Theoretical simulations and space-for-time analysis (mostly) agree with the temporal analysis
+
+We further assessed the consistency of the reported associations among temporal
+trends by implementing two additional analyses. We first tested if the
+associations among the temporal trends within sites was holding across sites,
+i.e. using spatial variations in food-web structure rather than temporal changes
+over time (space-for-time hypothesis). Second, we performed theoretical
+simulations with a bioenergetic food-web model to cross-reference our site and
+species specific empirical data on riverine fish with a more generalized
+representation of food web dynamics known to represent accurate relationships
+among our focal variables [@brose_allometric_2006; @eschenbrenner_diversity_2023;
+@danet_response_2024]. With those additional empirical and theoretical data, we
+assessed additional SEM models with the same structure as in Section 4.2.
+
+As in the temporal analysis, species richness had a positive effect on community
+biomass both in empirical data and in theoretical simulations (resp. $r_\delta
+=$ `r rdsp$bm$r` and `r rdm$bm$r`, Fig. \@ref(fig:std)a and S3). In both
+empirical data and theoretical simulations, community biomass had a positive
+effect on average trophic level (resp. $r_\delta =$ `r rdsp$tlvl$bm` and
+`r rdm$tlvl$bm`), and redundancy (resp. $r_\delta =$ `r rdsp$red$bm` and
+`r rdm$red$bm`), as in temporal analysis. We found weak evidence of a positive
+effect of spatial variation in community biomass on connectance in empirical
+data ($r_\delta =$ `r rdsp$ct$bm`) but strong evidence in theoretical
+simulations ($r_\delta =$ `r rdm$ct$bm`, Fig. \@ref(fig:std)a).
+
 The effects of spatial variations in species richness on food-web structure
-mostly agreed with the ones found with temporal trends, expect for average
+mostly aligned with those from the temporal trend analysis, except for average
 trophic level. We found a direct negative effect of species richness on
-connectance both using data and model simulations
-(resp. $r_\delta =$ `r rdsp$ct$r` and `r rdm$ct$r`, Fig. \@ref(fig:std)), on
-average trophic level (resp. $r_\delta =$ `r rdsp$tlvl$r` and `r rdm$tlvl$r`),
-but a direct positive effect on redundancy (resp. $r_\delta =$ `r rdsp$red$r`
-and `r rdm$red$r`). Species richness had indirect positive effect of species
-richness through community biomass, which added up to strong total negative
-effects on connectance in empirical data and simulations (resp. $r_\delta =$
-`r rtsp$ct$r` and `r rtm$ct$r` ) and positive on redundancy (resp. $r_\delta =$
-`r rtsp$red$r` and `r rtm$red$r`). We found that species richness had a total
-positive effect on average trophic level in bioenergetic model, in agreement
-with temporal trends (resp. $r_\delta =$ `r rtm$tlvl$r`), but a total negative
-effect in spatial variations (resp. $r_\delta =$ `r rtsp$tlvl$r`).
-
-We performed extinction simulations scenario on the metaweb, the food-web
-including all the species and nodes found in the empirical data, to better
-understand how species richness change affect food-web structure. When species
-are removed in a sequential order beginning by the highest trophic levels,
-connectance and average trophic level decreased as we removed species (red
-lines, Fig. S4a). At the opposite, removing first low trophic level species first
-increase connectance and average trophic level (green lines, Fig. S4a). In turn,
-random species extinction sequence had little effect on food-web structure
-(black lines, Fig. S4a).
+connectance both using data and model simulations (resp. $r_\delta =$
+`r rdsp$ct$r` and `r rdm$ct$r`, Fig. \@ref(fig:std)a), on average trophic level
+(resp. $r_\delta =$ `r rdsp$tlvl$r` and `r rdm$tlvl$r`), but a direct positive
+effect on redundancy (resp. $r_\delta =$ `r rdsp$red$r` and `r rdm$red$r`).
+Species richness had an indirect positive effect of species richness through
+community biomass, which added up to strong total negative effects on
+connectance in empirical data and simulations (resp. $r_\delta =$
+`r rtsp$ct$r` and `r rtm$ct$r`) and positive on redundancy (resp. $r_\delta =$
+`r rtsp$red$r` and `r rtm$red$r`). We found that
+species richness had a total positive effect on average trophic level in
+bioenergetic model, in agreement with temporal trends (resp. $r_\delta =$ `r rtm$tlvl$r`),
+but a total negative effect in spatial variations (resp. $r_\delta =$ `r rtsp$tlvl$r`).
+
+## Robustness of food web structure to species extinctions
+
+We implemented three secondary extinction simulation scenarios on the empirical
+metaweb defined as a food-web containing all the trophic species found across
+all sites in the empirical data. This was to access a second line of inference
+about whether top species were drivers of biomass and structure patterns (see
+section 4.2). When species are removed in a sequential order beginning by the
+highest trophic levels, connectance, average trophic level, and redundancy
+decreased (purple lines, Fig. \@ref(fig:std)b). On the other hand, removing low trophic level
+species first increases connectance and average trophic level, but do not affect
+redundancy (yellow lines, Fig. \@ref(fig:std)b). In turn, random species extinction sequence
+had little effect on food-web structure (black line, Fig. \@ref(fig:std)b). These results, in
+tandem with our empirical analyses above, suggest that top consumers play a
+disproportionate role in driving the changes in food web structure that we
+report.
 
 ```{r}
-std_cap <- paste0(
-  "Direct and total effects of community biomass and species richness on
-  food-web structure. Standardized coefficients ($r_\\delta$) derived from the
-  temporal, spatial, and bioenergetic model Structural Equation Models. Points
-  and lines display the estimated effects and their confidence intervals at
-  95\\%. Values are displayed in Table S3, R-squared in Table S4, and the
-  visualisation of the bivariate relationships for the spatial and bioenergetic
-  model SEMs are displayed in Figure S3.")
-
+std_cap <- paste0( "a, Direct and total effects of community biomass and species
+  richness trends on food-web structure trends. Standardized coefficients (r)
+  derived from the temporal, spatial, and bioenergetic model Structural Equation
+  Models. Points and lines display the estimated effects and their confidence
+  intervals at 95\\%. Values are displayed in Table S3, R-squared in Table S4, and
+  the visualization of the bivariate relationships for the spatial and
+  bioenergetic model SEMs are displayed in Figure S3. Average trophic level is
+  weighted by the biomass of the trophic species. Redundancy is the proportion
+  of redundant links. b, Effect of species extinctions on the structure of the
+  empirical metaweb according to three scenarios. In the Decreasing and
+  Increasing scenarios, species were ordered by their trophic level and removed
+  from the metaweb starting respectively from the highest and lowest trophic
+  level. Species were removed in a random sequence (50 sequences, grey dots) for
+  the random scenario, the black line displaying the average predicted by a GAM
+  linear model. For the extinction sequence, the average trophic level was not
+  weighted by the biomass of species as this information is not available at the
+  metaweb scale. Similar results were obtained with trophic species (i.e. node)
+  extinction (Fig. S4).")
 ```
@@
 ```{r std, fig.cap=std_cap, out.width = "100%"}
-tar_load(p_semeff_tot_ok_file)
-knitr::include_graphics(p_semeff_tot_ok_file)
+tar_load(p_sem_tot_ext_sp_file)
+knitr::include_graphics(p_sem_tot_ext_sp_file[[1]])
 ```
@@
 
-We found remarkable heterogeneity in community biomass and species richness
-changes over the last decades in riverine fish communities, linked to changes in
-food-web structure. Community biomass changes spanned from `r grbmn`% to
-+`r grbmx`% per decade, species richness from `r grrhn`% to +`r grrhx`% per
-decade, in line previous reports of the heterogeneity of local biodiversity
-changes in terrestrial, marine and freshwater realms[@dornelas_assemblage_2014;
-@blowes_geography_2019; @danet_past_2024]. In turn, connectance temporal changes
-spanned from `r grctn` to +`r grctx` per decade, average trophic level, from
-`r grtln` to +`r grtlx` per decade and the proportion of redundant trophic links
-from `r grln` to +`r grlx` per decades. We questioned the effects of community
-biomass and species richness changes over time on temporal changes in food-web
-structure, that we also tested across space and with simulations using a
-bioenergetic food-web model. We found positive effects of species richness
-changes on changes in community biomass that were consistent across temporal and
-spatial analysis and with the theoretical model. The effects of community
-biomass changes on food-web structure were also consistent across analysis,
-suggesting that loss of community biomass are linked to the loss of the trophic
-species of high trophic level. However, changes in species richness had
-contrasting effects on food-web structure depending on the type of analysis,
-temporal or spatial and theoretical simulations. It suggests that food-web
-structural changes induced by changes in species richness differs from the one
-induced by the changes in community biomass, and that they imply different
-processes across time and space. However, all analysis converged to indicate
-that community biomass and species richness declines trigger a decrease in
-food-web redundancy. In what follows, we discuss how changes in community
-biomass and species richness changes over time and space are related to food-web
-assembly and disassembly processes.
-
-We found that species richness scaled positively with community biomass, both in
-temporal, spatial and theoretical simulations, in accordance with previous
-analysis across space in stream communities [@woods_testing_2020;
-@danet_species_2021] but also in grasslands, salt marches and forests
-[@hector_plant_1999; @tilman_biodiversity_2014; @wu_relationship_2015;
-@li_relationship_2018; but see @grace_integrative_2016]. This result is in
-agreement with previous findings showing that food-web diversity can increase
+We found remarkable variability in the estimated temporal trends in biomass,
+species richness and three metrics of food web structure in riverine fish
+communities across more than 400 locations throughout France. Those contrasted
+situations were instrumental to evaluation the association between biodiversity
+temporal changes and food-web structure temporal changes.
+
+Via a combination of SEM modelling, simulations and more specific assessment of
+robustness to identify guild/tropho-species drivers, we found, across temporal,
+space-for-time and simulations that (1) average trophic level is consistently
+positively related to changes in total biomass; (2) connectance is consistently
+negatively related to changes in species richness; and (3) redundancy covaries
+positively with community biomass and species richness. We also found (4) a
+weak relationship between species richness and average trophic level that varied
+by temporal versus space-for-time approaches. Additionally (5) we found evidence
+for a significant role of top predator species in driving these patterns. Here
+we discuss these patterns and their implications in more depth.
+
+We found that species richness scaled positively with community biomass.  Our
+result was consistent across our temporal, spatial and theoretical simulations
+and is in-line with previous analysis across space in stream communities
+[@woods_testing_2020; @danet_species_2021] and in grasslands, salt marshes and
+forests [@hector_plant_1999; @tilman_biodiversity_2014; @wu_relationship_2015;
+@li_relationship_2018; but see @grace_integrative_2016].   These empirical data
+collectively align with theory showing that food-web diversity can increase
 biomass by stimulating primary production and resource uptake
-[@wang_biodiversity_2018]. Our results suggest that food-web losing species
-richness over time also experience a loss of biomass, while those gaining
-species experience a increase in community biomass. This result is coherent the
-Biodiversity-Ecosystem Functioning theory [@loreau_biodiversity_2001;
-@wang_biodiversity_2018], and suggest that the loss of species richness and
-biomass might impair ecosystem functioning.
-
-Our results suggest that food-web that have undergone a biomass decline
-experienced a loss of top trophic levels species and connectance, those gaining
-biomass experienced a gain in top trophic levels and connectance. Importantly,
-the same results were found using spatial comparison and theoretical models.
-This results can be linked with the energetic and trophic biogeography theories
-[@lindeman_trophic-dynamic_1942; @gravel_trophic_2011], which posits that the
-presence of top predators is limited by the amount of energy and resource
-available [@lindeman_trophic-dynamic_1942, @takimoto_ecosystem_2008;
-@post_ecosystem_2000; @post_long_2002]. Thereby, a decrease in community biomass
-can limit the amount of resource available to sustain top predators, while
-increase in community biomass may result in more resource available for top
-predators [@takimoto_ecosystem_2008; @post_ecosystem_2000]. (Add something about
-the role of apex predators?)
-
-Species richness temporal changes were positively associated to changes in
-average trophic level through community biomass and in connectance mainly
-through direct effects, such as food-webs that have suffered a decline in
-species richness over last decades have experienced a concomitant decline in
-average trophic level and increase in connectance, those have seen an increase
-in species richness have experienced an increase in average trophic level and
-decline in connectance. However, the effect of species richness temporal trends
-on average trophic level were twice lower than the one of community biomass.
-Altogether, it suggests that species richness increase and decrease were less
-clearly linked to specific changes in top trophic levels than community biomass.
-Species richness temporal trends could be more linked to changes in the
-redundancy of trophic roles in the food-webs, such as it has little effects of
-food-web structure but increases its community biomass. This interpretation
-align with the insurance hypothesis [@yachi_biodiversity_1999;
-@loreau_biodiversity_2021], such as species richness and associated redundancy
-in species roles can increase ecosystem stability by buffering the impacts of
-perturbations [@sanders_trophic_2018].
-
-When considering spatial analysis and model simulations, species richness
-effects on food-web structure mostly consistent from the temporal analysis. All
-analysis converged to indicate that increases in species richness result in
-decreases in connectance, a well documented pattern in empirical food-webs
-[@dunne_network_2006; @danet_species_2021]. However, spatial analysis found that
-species richness decrease average trophic level, while temporal analysis and
-theoretical models found that species richness increases result in higher
-average trophic level. This result is also in line with other studies which
-found a mismatch between spatial and temporal trends [@adler_contrasting_2007;
-@johnson_testing_2008]. This discrepancy in space and time is due to the strong
-assumption that variations in space reflect differences in assembly stages of
-ecological communities and then mirror their temporal assembly/disassembly
-trajectories. Temporal changes in species richness might relate to short-term
-dynamics while spatial gradients reflect aggregated dynamics over a longer
-timescale including a far number of processes including high species turnover
-along spatial gradients. Our results then suggest community biomass changes in
-space might be a good surrogate to infer assembly and disassembly of food-web in
-time, but that it is probably not always the case for species richness.
-
-Our study demonstrates that redundancy of trophic pathways in food-webs are
+[@schneider_animal_2016; @wang_biodiversity_2018; @wang_intraguild_2019;
+@nie_will_2023] and Biodiversity-Ecosystem Functioning theory where the loss of
+species richness and biomass predicts impaired ecosystem functioning
+[@loreau_biodiversity_2001]. These data and theory firmly indicate that loss of
+biodiversity per se (e.g. species richness) can lead to overall loss of biomass
+in many ecosystems and mitigating actions that increase biodiversity can lead to
+an increase in community biomass.
+
+Our results also show that food-webs that have undergone a biomass decline
+experienced significant structural changes marked by a loss of top trophic
+levels species and a decreased connectance. These results can be linked with the
+energetic and trophic biogeography theories [@lindeman_trophic-dynamic_1942;
+@gravel_trophic_2011], which posit that the presence of high trophic level
+species is limited by the productivity and the amount of energy available
+[@lindeman_trophic-dynamic_1942, @takimoto_ecosystem_2008; @post_ecosystem_2000;
+@post_long_2002]. Thus, our results suggest a decrease in community biomass can
+limit the amount of resource available to sustain high trophic level species,
+while increase in community biomass may translate in more resources available
+for high trophic level species [@takimoto_ecosystem_2008; @post_ecosystem_2000].
+
+Biodiversity-Ecosystem Functioning theory offers an alternative causal
+explanation, indeed the presence of higher trophic level species can decrease
+niche overlap among producers and then increase productivity and community
+biomass [@schneider_animal_2016; @wang_biodiversity_2018; @wang_intraguild_2019;
+@nie_will_2023]. The positive association of connectance with community biomass
+was weaker than for average trophic level, which might be related to the
+contrasting effects of connectance, negative or positive, on productivity
+previously reported in theoretical models [@nie_will_2023;
+@wang_intraguild_2019; @thebault_food-web_2003; @poisot_trophic_2013;
+@schneider_animal_2016]. While increasing connectance between herbivores and
+plants has been reported to either increase or decrease productivity
+[@thebault_food-web_2003; @poisot_trophic_2013; @nie_will_2023], increasing
+connectance within carnivores having generally a positive effect on productivity
+because higher connectance can decrease top-down control and allow biomass to
+accumulate across trophic level [@wang_intraguild_2019; @schneider_animal_2016].
+
+Species richness was negatively associated with connectance, confirming previous
+results [@dunne_network_2006], and was suggested to be the results of
+limitations of predator generality [@dunne_network_2006]. The effects of species
+richness changes on the average trophic level were more contrasted and twice
+lower in strength than the effects of community biomass. The direct effect of
+species richness on average trophic level being null, or negative considering
+temporal or spatial and theoretical models. When accounting for the indirect
+effect of species richness on community biomass, temporal and theoretical
+analysis indicates changes in species richness are positively associated with
+changes in average trophic level. Those contrasted effects of species richness
+on average trophic level can be related to the results of our extinction
+simulations where the removal of top trophic level species had much less impact
+on average trophic level than on connectance and redundancy. This discrepancy in
+space and time is likely due to the strong assumption that variations in space
+reflect differences in assembly stages of ecological communities and then mirror
+their temporal assembly/disassembly trajectories. Spatial gradients reflect
+aggregated dynamics over a longer timescale including a far number of
+processes including high species turnover and differences in ecosystem
+productivity along spatial gradients that are not captured by species richness
+[@post_ecosystem_2000; @post_long_2002].
+
+Altogether, our results then suggest community biomass changes in space might be
+a good surrogate to infer assembly and disassembly of food-webs in time, but
+that it is probably not always the case for species richness. Furthermore, it
+suggests that species richness increase and decrease were less clearly linked to
+specific changes in top trophic levels than community biomass. Species richness
+temporal trends could be more linked to changes in the redundancy of trophic
+roles in the food-webs, such as it has little effect on food-web structure
+itself but increases its community biomass. This interpretation aligns with the
+insurance hypothesis [@yachi_biodiversity_1999; @loreau_biodiversity_2021], such
+as species richness and associated redundancy in species roles can increase
+ecosystem stability by buffering the impacts of perturbations
+[@sanders_trophic_2018].
+
+Our study also demonstrates that redundancy of trophic pathways in food-webs are
 positively associated to both community biomass and species richness changes, so
@@
 removed with triggering secondary extinctions [@allesina_who_2004;
-@bodini_using_2009], such a higher proportion of redundant interactions
-increase robustness of food-webs to perturbations [@allesina_functional_2009].
-It suggests that declines in community biomass and species richness result in a
-decline of food-web robustness to further perturbations.
-
-Our study brings evidences that temporal changes in community biomass and
-species richness are related to changes in food-web structure in empirical
-settings. We completed the temporal analysis with a spatial analysis and
-theoretical simulations. Altogether, it suggests that community biomass changes
-are associated with changes in the presence of top predators, in agreement with
-the hypothesis that food-web maximum trophic level are limited by the amount of
-energy available in lower trophic level. In contrast, species richness changes
-seems to be linked to changes in upper and lower part of the food-webs.
+@bodini_using_2009], such a higher proportion of redundant interactions increase
+robustness of food-webs to perturbations [@allesina_functional_2009]. It
+suggests that declines in community biomass and species richness result in a
+decline of food-web robustness to further perturbations. The positive link
+between redundancy and biomass is consistent to previous theoretical results
+showing that higher redundancy in trophic pathways could be associated with a
+decrease in complementarity within trophic species which in turn can reduce
+top-down effects and stimulate biomass productions [@wang_biodiversity_2018;
+@wang_intraguild_2019], and also give opportunity for compensatory dynamics
+which in turn increase robustness following extinctions
+[@staniczenko_structural_2010].
+
+We aimed to expose the relationships among three metrics of food web structure,
+community biomass and species richness. Our results, derived from a larger and
+extensive temporal and spatially resolved dataset, align with multiple bodies of
+theory and deliver consistent results across multiple methodologies. In an era
+of rapid anthropogenic driven change impacting directly the biodiversity of
+communities, these relationships are vital to our capacity to predict and
+mitigate effects. For example, our results suggest that community biomass
+changes are associated with changes in the presence and biomass of top
+predators, in agreement with two bodies of theory. Energetic theory which
+assumes that food-web maximum trophic level are mainly limited by the amount of
+energy available in lower trophic levels and Biodiversity-Ecosystem Functioning
+theory which assumes that the presence of higher trophic levels is the cause of
+higher productivity and total biomass. In contrast, species richness changes
+seem to be linked to changes in the upper and lower part of the food-webs.
 Importantly, temporal and spatial analysis using empirical fish food-webs are
@@
 generality of the food-web assembly rules that we report. The study finally
-highlights that increases in community biomass and species brings robustness to
-food-webs by increasing the proportion of redundant trophic links. Conversely, it
-suggests that community declines in species richness and community biomass are
-likely to decrease significantly the community robustness to further
-perturbations. Thereby, the numerous reported declines in biodiversity might
-hide increase in the fragility of ecosystems.
+highlights that increases in community biomass and species richness brings
+robustness to food-webs by increasing the proportion of redundant trophic links.
+Altogether, our results suggest that assessments of food-web structure,
+community biomass and richness, which may be more feasible than direct
+estimation of function, may deliver much needed indicators of functional decline
+and metrics thus for the efficacy of mitigation strategies.
 
@@
 We used a monitoring of freshwater fishes conducted all over France and
-conducted by the Office Français de la Biodiversité (OFB, previously known as
-ONEMA and AFB). The sampling protocols were standardized since 1995 and a
-complete description of the sampling process can be found in
-@danet_species_2021. The fishes are sampled using
-electrofishing all across the streams in shallow streams and over the bank by
-boat in deeper streams. All the fishes are counted and the bodysize of fishes are
-recorded for a sample of them, enabling the estimate the distribution of
+conducted by the Office Français de la Biodiversité (OFB). The sampling
+protocols were standardized since 1995 and a complete description of the
+sampling process can be found in @danet_species_2021. The fishes are sampled
+using electrofishing all across the streams in shallow streams and over the bank
+by boat in deeper streams. All the fishes are counted and the bodysize of fishes
+are recorded for a sample of them, enabling the estimate the distribution of
 individual bodysize by species for each sampling [@bonnaffe_comparison_2021;
@@
 We inferred the metaweb according to ontogenic diet data and body size
-[@gravel_inferring_2013; @poisot_structure_2016; @brose_predator_2019;
+[@gravel_inferring_2013; @@poisot_trophic_2013; @brose_predator_2019;
 @bonnaffe_comparison_2021; @danet_species_2021]. The method is extensively

### 2025-02-03 _targets.R

@@ -1337,6 +1337,16 @@ tar_target(semeff_tot_tab,
       width = 80, height = 80 * .75),
     format = "file"
     ),
+  tar_target(p_sem_tot_ext_sp_file,
+    ggsave_multiple(
+      paste0("p_sem_tot_ext_sp", c(".png", ".pdf")),
+      plot = tar_read(p_sem_tot_ext_sp),
+      path = here::here("figures"),
+      scale = 2.4,
+      units = c("mm"),
+      width = 120,
+      height = 120 * .65)
+    ),
   # Tables:
   tar_target(pca_table,
     data_for_pca %>%

### 2025-02-03 draft.R

@@ -22,6 +22,8 @@ g <- get_root_graph4fish()
 
 
 
+
+
 ```{r}
 tar_load(op_data)
 st <- op_data %>%

### 2025-02-07 paper/manuscript.Rmd
Improve hierarchy and clarity of the objectives and findings:
- Improve hierarchy
- Mirror discussion and intro
- Mv details of spatial analysis to appendix

@@
 ---
-title: "Biodiversity changes are linked to changes in food-web structure and redundancy in riverine ecosystems"
+title: "Biodiversity temporal trends are reshaping food web structure and redundancy in riverine ecosystems"
 subtitle: "Alain Danet (a,b), Loubna El Madouri (a,c), Andrew P. Beckerman (b),
@@
 #csl: ecology-letters.csl
+#https://pkgs.rstudio.com/rticles/articles/examples.html
 toc: false
@@
 
-(a) Centre d’Ecologie et des Sciences de la Conservation, UMR 7204 MNHN7
-CNRS-Sorbonne Université, Muséum national d’Histoire naturelle de Paris, 43 rue
-8 Buffon, 75005 Paris, France
+(a) Centre d’Ecologie et des Sciences de la Conservation, UMR 7204
+MNHN-CNRS-Sorbonne Université, Muséum national d’Histoire naturelle de Paris, 43
+rue Buffon, 75005 Paris, France
 
@@
 
-# Abstract (152 / 250 words max)
-
-Changes in biodiversity can fundamentally alter ecological communities, yet how
-these changes affect food web structure remains poorly understood. Here, we
-analyze temporal trends in over 400 riverine fish communities across France
-spanning 1995-2018, examining relationships between species richness, community
-biomass, and three key metrics of food web structure: connectance, weighted
-average trophic level, and trophic pathway redundancy. Using structural equation
-modeling, theoretical simulations, and robustness analyses, we demonstrate that declining
-community biomass leads to loss of top trophic levels and decreased food web
-connectance, while species richness negatively correlates with connectance but
-positively affects trophic redundancy. Notably, both biomass and species
-richness positively influence the proportion of redundant trophic links,
-suggesting that biodiversity loss reduces community robustness to future
-perturbations. Our findings, consistent across temporal, spatial, and
-theoretical approaches, reveal how biodiversity change restructures food webs
-and highlights the utility of food web metrics as indicators of ecosystem
-function and fragility.
-
-# Significance (124 / 120 words max)
+# Abstract (229 / 250 words max)
+
+Biodiversity changes are expected to profoundly impact ecosystem functioning and
+stability, yet empirical evidence remains limited. Bridging this gap requires
+aligning biodiversity trends with food web theory and Biodiversity-Ecosystem
+Functioning research, which provide strong predictions about the ecological
+consequences of biodiversity loss. Most insights rely on spatial comparisons of
+ecological communities, assuming they reflect temporal trends—a space-for-time
+substitution. Here, we analyze biodiversity and food web time series from over
+400 riverine fish communities across France (1995–2018) to evaluate how
+biodiversity trends reshape food web structure. We examine relationships among
+species richness, community biomass, and three key food web metrics:
+connectance, weighted average trophic level, and trophic pathway redundancy. We
+also test the space-for-time hypothesis using spatial gradients and a
+theoretical food web model. Structural equation models and robustness analyses
+reveal that declines in species richness strongly correlate with reduced
+community biomass, with top trophic-level species playing a disproportionate
+role in food web changes. Declining biomass leads to the loss of top trophic
+levels and decreased connectance, while species richness negatively correlates
+with connectance. Both biomass and species richness declines reduce trophic
+pathway redundancy, suggesting biodiversity loss undermines community robustness
+to future perturbations. Our findings align with food web theory and
+Biodiversity-Ecosystem Functioning research, support the validity of
+space-for-time approaches for basic food web metrics, and highlight the utility
+of food web metrics as indicators of ecosystem function and fragility.
+
+# Significance (118 / 120 words max)
 
 Understanding how biodiversity loss affects ecological communities is crucial
-for predicting and mitigating human impacts on ecosystems. This study
-provides comprehensive evidence linking biodiversity changes to food web
-structure using an extensive dataset of riverine fish communities. We
-demonstrate that changes in community biomass and species richness
-systematically alter food web architecture, affecting trophic levels,
-connectance, and the redundancy of feeding relationships. Our findings unite
-multiple ecological theories, showing how energetic constraints and
-biodiversity-ecosystem functioning mechanisms jointly shape food web assembly
-and disassembly. Importantly, we show that declining biodiversity reduces the
-redundancy of trophic pathways, potentially making communities more vulnerable
-to future perturbations. These results suggest that food web structure metrics
-could serve as valuable indicators for monitoring ecosystem health and
-evaluating conservation strategies.
+for predicting and mitigating human impacts on ecosystems. This study provides
+comprehensive evidence on how biodiversity changes are reshaping food web structure using
+an extensive dataset of riverine fish communities. We demonstrate that changes
+in species richness and community biomass consistently alter trophic levels,
+connectance, and the redundancy of feeding relationships. Our findings show how
+energetic constraints and biodiversity-ecosystem functioning mechanisms jointly
+shape food web assembly and disassembly. Importantly, we show that declining
+biodiversity reduces the redundancy of trophic pathways, potentially making
+communities more vulnerable to future perturbations. These results suggest that
+food web structure metrics could serve as valuable indicators for monitoring
+ecosystem health and evaluating conservation strategies.
 
@@
 
-Ecological communities are experiencing massive changes due to human pressures,
-which are expected to have striking consequences on ecosystem functioning and
-fragility. It is increasingly recognized that such changes across space are
-associated with spatial variations in human pressures [@mcgill_fifteen_2015;
-@blowes_geography_2019], such as freshwater
+Human pressures are driving profound biodiversity changes, including freshwater
 and terrestrial biodiversity declines linked to land degradation
-[@newbold_global_2015; @cardinale_is_2018; @danet_past_2024], and declining
-biomass of marine fishes linked to increased fishing pressures on predatory
-fishes [@christensen_century_2014]. These documented changes in diversity and
-biomass result in altered community structure and composition
-[@dornelas_assemblage_2014; @hillebrand_biodiversity_2018; @danet_past_2024].
-
-The structure of ecological networks, which describe the number, distribution
-and strength of interactions among species, is important because it, along with
-species richness per se, underpins species coexistence, ecosystem functioning
-and the stability of ecological dynamics and ecosystem function
+[@newbold_global_2015; @cardinale_is_2018; @danet_past_2024] and reductions in
+marine fish biomass due to intensified fishing pressures on predatory species
+[@christensen_century_2014]. A central goal of Biodiversity-Ecosystem
+Functioning and food web research has been to understand the ecological
+consequences of these widespread biodiversity losses for ecosystem functioning
+and stability [@loreau_biodiversity_2001; @loreau_ecological_2022;
+@thebault_food-web_2003; @schneider_animal_2016; @dunne_network_2002;
+@sole_complexity_2001; @allesina_functional_2009; @montoya_press_2009; @sanders_trophic_2018]. However,
+research on biodiversity changes remains largely disconnected from studies
+examining their ecological impacts, primarily due to a lack of simultaneous
+temporal data on biodiversity and food web dynamics [@danet_species_2021]. As a
+result, much of our understanding of the ecological consequences of biodiversity
+changes over time relies on experimental and theoretical approaches. These
+approaches often depend on the critical assumption that spatial comparisons of
+ecological communities can serve as a proxy for temporal trends—a space-for-time
+substitution—when direct temporal data are scarce. To advance our understanding
+of the ecological consequences of biodiversity changes, it is essential to
+investigate how these changes are reshaping food web structure in natural
+settings.
+
+Here, we bridge the gap between biodiversity changes and food web dynamics by
+leveraging a unique dataset of riverine fish communities sampled repeatedly over
+a 23-year period (1995–2018) across 403 locations in France. By reconstructing
+yearly food web structures [@danet_species_2021; @bonnaffe_comparison_2021], we
+investigate how temporal biodiversity trends reshape food web metrics such as
+connectance, weighted average trophic level, and the proportion of redundant
+trophic links (hereafter “redundancy”). Linking these findings to established
+theories of Biodiversity-Ecosystem Functioning and food web dynamics, we address
+three key objectives: (i) documenting how temporal biodiversity trends reshape
+food web structure, (ii) connecting these changes to ecosystem functioning and
+food web theories, and (iii) assessing the validity of the space-for-time
+substitution assumption in the context of biodiversity and food web structure
+changes.
+
+The structure of ecological networks, which describes the number, distribution,
+and strength of interactions among species, is critical for understanding
+species coexistence, ecosystem functioning, and stability to perturbations
 [@chesson_interaction_2008; @thebault_food-web_2003; @oconnor_general_2017;
-@danet_species_2021; @eschenbrenner_diversity_2023; @danet_response_2024].
-Theory and empirical data have shown that species richness and food-web
-structure impact on coexistence [@chesson_interaction_2008], ecosystem
-functioning [@thebault_food-web_2003; @wang_biodiversity_2018], stability
-[@danet_species_2021; @danet_response_2024; @eschenbrenner_diversity_2023], and
-ecosystem robustness to perturbations [@dunne_network_2002;
-@allesina_functional_2009; @bodini_using_2009; @allesina_functional_2009].
-Keystone predator species regulating dominant competitors can limit competitive
-exclusion [@heithaus_predicting_2008; @johnson_rarity_2007;
-@estes_trophic_2011], and thereby maintain species richness. Food-webs with
-higher trophic levels are linked to elevated  ecosystem productivity
-[@thebault_food-web_2003; @wang_biodiversity_2018] and community temporal
-stability [@danet_species_2021; @eschenbrenner_diversity_2023;
-@danet_response_2024]. Finally, the number and distribution of trophic links in
-food-webs determine the robustness of communities to perturbations
-[@dunne_network_2002; @allesina_functional_2009; @bodini_using_2009;
-@allesina_functional_2009]. A better knowledge of the consequences of
-biodiversity change on the structure of ecological networks is thus necessary to
-quantify and mitigate anthropogenic driven changes to biodiversity.
-
-There are three key components to the mapping between biodiversity changes and
-food-web structure. First, the energetic paradigm underpinning the trophic
-theory of biogeography [@lindeman_trophic-dynamic_1942; @gravel_trophic_2011]
-posits that the presence of top consumers requires resources in enough numbers
-at lower trophic levels derived from bottom up productivity. From this, it can
-be further hypothesized that the presence of generalist top consumers will be
-strongly conditioned by the amount of community biomass.
-
-Second, connectance (the proportion of realized trophic links), is commonly
-reported to decrease as species richness increases [@oconnor_general_2017;
-@dunne_network_2006], because consumers are limited in the number of resources
-they can consume. Connectance has also been linked to the robustness to species
-extinctions [@dunne_network_2002; @allesina_who_2004; @bodini_using_2009]. More
-in detail, it is the prevalence of redundant (versus functional) links in food
-webs [@allesina_who_2004; @bodini_using_2009; @allesina_functional_2009], i.e.
-the redundancy of trophic pathways, that predicts ecosystem robustness as they
-can be safely removed without triggering secondary extinctions. We thus predict
-that higher species richness covaries with higher redundancy of trophic pathways
-in food-webs [@allesina_functional_2009]. Together, these relationships mean
-that biodiversity changes are likely to be associated with changes in trophic
-links distribution and then possibly to changes in robustness to perturbations,
-such as increases in species richness should increase the number of redundant
-trophic pathways to top predators and then increase community robustness.
-
-Finally, biodiversity and ecosystem functioning theory suggest specifically that
-community biomass should be positively related to species richness
-[@loreau_biodiversity_2001]. This arises specifically because of niche
-complementarity where species exploit different resources. In the particular
-case of food webs, theoretical studies show that the presence of higher trophic
-level species decreases niche overlap among producers which then increase
-productivity and community biomass [@schneider_animal_2016;
-@wang_biodiversity_2018; @wang_intraguild_2019; @nie_will_2023].
-
-Here, we report on an analysis of riverine fish community times series to
-document the ecological consequences of biodiversity changes on food web
-structure. We specifically aim to reveal the relationship between community
-biomass and species richness and three key metrics of food web structure:
-connectance, weighted average trophic level, and the proportion of redundant
-trophic links (hereafter “redundancy”). To do this, we implemented a sequence of
-analyses that allows us to enumerate these relationships as covariation among
-temporal trends. First, we estimated `r nb_op` food web structure for `r nb_st`
-fish communities with 10+ years of community dynamics spanning 1995-2018 over
-France (Fig. \@ref(fig:matmet)a-c, Table S1).  Second, using these food webs, we
-estimated the temporal trends in each of species richness, biomass, connectance,
-trophic structure and redundancy. Having estimated each temporal trend, we next
-constructed an SEM to make specific inference about the relative effects of
-community biomass and species richness  temporal trends on the temporal trends
-three metrics of food web structure, and the effect of species richness on
-community biomass (Fig. \@ref(fig:matmet)d). We also implemented a robustness analysis on the
-meta-food web (i.e. the food web grouping all trophic species found in the
-dataset and their inferred interactions) to identify species extinction
-scenarios that might explain the variation in food web structure that we see in
-the timeseries. Finally, we performed three further analysis to evaluate the
-robustness and the generality of our results. We replicated our temporal
-analysis with a space-for-time approach (Fig. \@ref(fig:matmet)c & e) using median metrics in
-each site instead of the temporal trends; we created a simulation of complex
-communities using a bioenergetic food web model to assess the generality of our
-results in complex communities that allow relaxation of some of the constraints
-defined by our fish biodiversity data; and we performed a three-scenario,
-topological secondary extinction analysis on the full empirical metaweb to
-evaluate the role of top predators on food-web structure.
+@danet_species_2021; @eschenbrenner_diversity_2023; @danet_response_2024]. Both
+theory and empirical evidence demonstrate that species richness and food web
+structure influence coexistence [@chesson_interaction_2008], ecosystem
+productivity [@thebault_food web_2003; @wang_biodiversity_2018], temporal
+stability [@danet_species_2021; @danet_response_2024;
+@eschenbrenner_diversity_2023], and robustness to disturbances
+[@sole_complexity_2001; @dunne_network_2002; @allesina_functional_2009;
+@bodini_using_2009; @montoya_press_2009; @sanders_trophic_2018]. For instance,
+keystone predators can regulate dominant competitors, preventing competitive
+exclusion and maintaining species richness [@heithaus_predicting_2008;
+@johnson_rarity_2007; @estes_trophic_2011]. Similarly, food webs with higher
+trophic levels are associated with greater ecosystem productivity
+[@wang_biodiversity_2018; @schneider_animal_2016; @wang_biodiversity_2018;
+@wang_intraguild_2019; @nie_will_2023] and community stability
+[@danet_species_2021; @eschenbrenner_diversity_2023; @danet_response_2024],
+while the number and distribution of trophic links determine resilience to
+perturbations [@dunne_network_2002; @allesina_who_2004; @bodini_using_2009;
+@allesina_functional_2009; @sanders_trophic_2018]. Understanding how
+biodiversity changes reshape ecological networks is therefore essential for
+quantifying and mitigating anthropogenic impacts on ecosystems.
+
+Three key components link biodiversity changes to food web structure. First, the
+energetic paradigm of food web dynamics posits that the presence of top
+consumers depends on sufficient resource availability at lower trophic levels,
+driven by bottom-up productivity [@lindeman_trophic-dynamic_1942;
+@gravel_trophic_2011]. Thus, the biomass of generalist top consumers is likely
+constrained by overall community biomass. Second, connectance—the proportion of
+realized trophic links—typically decreases with increasing species richness, as
+consumers are limited in the number of resources they can exploit
+[@oconnor_general_2017; @dunne_network_2006]. However, higher species richness
+is expected to increase the redundancy of trophic pathways, enhancing ecosystem
+robustness to species extinctions [@dunne_network_2002; @allesina_who_2004;
+@bodini_using_2009; @allesina_functional_2009]. This redundancy underpins the
+insurance effect of biodiversity, where greater diversity buffers ecosystems
+against perturbations and environmental changes [@yachi_biodiversity_1999;
+@loreau_ecological_2022]. Finally, biodiversity-ecosystem functioning theory
+suggests that species richness promotes community biomass through niche
+complementarity [@loreau_biodiversity_2001]. In food webs, the presence of
+higher trophic levels reduces niche overlap among producers, further boosting
+productivity and biomass [@schneider_animal_2016; @wang_biodiversity_2018;
+@wang_intraguild_2019; @nie_will_2023]. Together, these mechanisms highlight how
+biodiversity changes can alter trophic link distribution, robustness, and
+ecosystem functioning.
+
+To achieve these objectives, we analyzed temporal trends in species richness,
+biomass, and food web structure across `r nb_op` community samplings (Fig.
+\@ref(fig:matmet)a-c, Table S1). Using structural equation modeling (SEM), we
+inferred the relative effects of biomass and species richness trends on food web
+metrics, as well as the effect of species richness on biomass (Fig.
+\@ref(fig:matmet)d). We also conducted a robustness analysis on the meta-food
+web (comprising all trophic species and their interactions) to identify species
+extinction scenarios that could explain observed variations in food web
+structure. To test the space-for-time hypothesis, we compared temporal findings
+with spatial gradients using two approaches: (i) replicating our temporal
+analysis using median biodiversity and food web metrics across sites (Fig.
+\@ref(fig:matmet)c & e), and (ii) simulating food web dynamics across gradients
+of species richness and primary productivity using a bioenergetic model
+[@brose_allometric_2006; @lajaaiti_ecologicalnetworksdynamicsjl_2025]. These
+simulations allowed us to evaluate whether theoretical predictions align with
+our empirical data, which are limited to fish biodiversity.
 
 ```{r}
-fig_mat_cap <- paste0("Using ", nb_st," sites of stream fishes in (a) French streams that
-  have been monitored at least 10 years, (b) we reconstructed the food-web at each
-  site and each sampling event by building a metaweb based on ontogenic food diet information for each
-  species and predator-prey body size ratio. (c) We computed the temporal trends
-  and the median of community biomass, species richness, connectance, average
-  trophic level, and redundancy at each site. We then assessed the relationships
-  among food web structure descriptors, (d) in time and (e) across
-  space. We additionally performed extinction simulations from the metaweb and
-  insilico experiments using a bioenergetic food web model to gain more insights
-  and assess the generality of our results (see Methods).")
+fig_mat_cap <- paste0("Methodological Approach: (a) We analyzed ", nb_st, "
+  stream fish communities in France, each monitored for at least 10 years. (b)
+  For each site and sampling event, we reconstructed food webs using a metaweb
+  based on ontogenetic diet information and predator-prey body size ratios. (c)
+  We computed temporal trends and median values for community biomass, species
+  richness, connectance, average trophic level, and redundancy at each site. (d)
+  We then assessed relationships among these food web descriptors over time and
+  (e) across spatial gradients.")
 ```
@@
 
-Our food web reconstruction delivered `r nb_op` estimates of species richness,
-biomass, connectance, weighted average trophic level, and the proportion of
-redundant trophic links (hereafter "redundancy", see Appendix B) from our 403
-fish communities with 10+ years of population dynamics spanning 1995-2018 over
-France (Fig. 1a-c). We implemented Bayesian hierarchical models to jointly
-estimate the temporal trends in these metrics. We found a great heterogeneity in
-the temporal trends at the site level (community biomass: from `r grbmn`% to
-`r grbmx`% per decade, species richness: `r grrhn` to +`r grrhx`%, average
-trophic level: `r grtln` to +`r grtlx`, connectance: `r grctn` to +`r grctx`,
-redundancy: `r grln` to +`r grlx`, Fig. S1) which was effectively captured by
-the hierarchical model (with conditional R2 between `r r2cond$log_bm_std` for
-community biomass to `r r2cond$log_rich_std` for species richness, Table S2).
+Our food web reconstruction delivered `r nb_op` annual estimates of species
+richness, biomass, connectance, weighted average trophic level, and the
+proportion of redundant trophic links (hereafter “redundancy”, see Appendix B)
+from our `r nb_st` fish communities with 10+ years of population dynamics
+spanning 1995-2018 over France (Fig. \@ref(fig:matmet)a-c). We implemented Bayesian hierarchical
+models to jointly estimate the temporal trends in these metrics. We found a
+great heterogeneity in the temporal trends at the site level (community biomass:
+from `r grbmn`% to +`r grbmx`% per decade, species richness: `r grrhn` to +`r
+grrhx`%, average trophic level: `r grtln` to +`r grtlx`, connectance: `r grctn`
+to +`r grctx`, redundancy: `r grln` to +`r grlx`, Fig. S1) which was effectively
+captured by the hierarchical model ( conditional R2 ranging from `r
+r2cond$log_bm_std` for community biomass to `r r2cond$log_rich_std` for species
+richness, Table S2).
 
 ```{r}
-sem_cap <- "(a) Structural equation models linking the temporal trends of the
-food-web structure. The path widths are proportional to the standardized slope
-coefficients. The standardized slope coefficients and their associated 95%
-  confidence intervals obtained by bootstrapping are displayed along the path.
-R2 displays the marginal R-squared of the linear models. (b to h) Direct
-bivariate relationships derived from the structural equation model. Points
-display the temporal trends at each site estimated with a hierarchical Bayesian
-model, lines display the linear relationship estimated with the SEM. The
-distribution of the site temporal trends are displayed in Fig. S1. All the
-effects are reported in Table S3. Average trophic level is weighted by the
-biomass of the trophic species. Redundancy is the proportion of redundant
-links."
+sem_cap <- "(a) Structural equation models linking the temporal trends of
+biodiversity and food web structure. Dashed and solid arrows display
+respectively negative and positive the standardized slope coefficients, their
+widths being proportional to the absolute values of the coefficients.. The
+standardized slope coefficients and their associated 95% confidence intervals
+obtained by bootstrapping are displayed along the path. R2 displays the marginal
+R-squared of the linear models. (b to h) Direct bivariate relationships derived
+from the structural equation model. Points display the temporal trends at each
+site estimated with a hierarchical Bayesian model, lines display the linear
+relationship estimated with the SEM. The distribution of the site temporal
+trends are displayed in Fig. S1. All the effects are reported in Table S3.
+Average trophic level is weighted by the biomass of the trophic species.
+Redundancy is the proportion of redundant links."
+
 ```
@@
 
-## Association between biodiversity and food-web temporal trends
+## Association between biodiversity and food web temporal trends
 
 These temporal trend estimations at the site level were the input to our SEM,
-allowing us to evaluate the direct and indirect effect of species richness and
-community biomass changes on food web structure changes and between species
-richness and community biomass. We detected a strong positive association
-between community biomass and in species richness ($r_\delta =$ `r rdtps$bm$r`,
+allowing us to evaluate the direct effect of the temporal trends of species
+richness and community biomass on the temporal trends of food web structure, the
+direct effect of  species richness temporal trends on the temporal trends of
+community biomass, and the indirect effect of species richness temporal trends
+on the temporal trends in food web structure through community biomass. We
+detected a strong positive effect of species richness temporal trends on the
+temporal trends in community biomass ($r_\delta =$ `r rdtps$bm$r`,
 Fig. \@ref(fig:sem) a and b, $r_\delta$: standardized slope coefficient, [95%
-CI], Table S3). This indicates that communities with decreasing species richness
-over time experienced a concomitant decrease in community biomass and
-vice-versa.
-
-Our SEM also predicts a positive effect of community biomass on connectance,
-average trophic level, and redundancy (resp. $r_\delta =$ `r rdtps$ct$bm`,
-`r rdtps$tlvl$bm`, `r rdtps$red$bm`, Fig. \@ref(fig:sem)b, c, d). Thus, when communities
-experienced a decrease in biomass, they also experimented a concomitant decrease
-in connectance, average trophic level and redundancy, and vice versa. We further
-found that the temporal trends in community biomass were positively associated
-with both the number and the proportion of piscivorous species (Fig. S2a),
-suggesting that the presence of high trophic level trophic species has a
-disproportionate role community biomass.
+CI], Table S3). This indicates that communities with decreasing, or increasing,
+species richness over time experienced a concomitant decrease, or increase, in
+community biomass.
+
+We also find a positive effect of the temporal trend in community biomass on the
+temporal trends of connectance, average trophic level, and redundancy (resp.
+$r_\delta =$ `r rdtps$ct$bm`, `r rdtps$tlvl$bm`, `r rdtps$red$bm`, Fig.
+\@ref(fig:sem)b-d). Thus, when communities experienced a decrease, or increase,
+in community biomass, they also experienced a concomitant decrease, or increase,
+in connectance, average trophic level and redundancy. To assess whether top
+trophic level species were driving those relationships, we additionally looked
+at the temporal trends in the number and the proportion of piscivorous species.
+The temporal trends in community biomass were positively associated with both
+the temporal trends in the number and proportion of piscivorous species (Fig.
+S2a). Then, communities with increasing biomass have an increase in average
+trophic level, in the number and proportion of piscivorous fishes (or
+reciprocally for decreasing biomass), suggesting that temporal trends in
+community biomass are driven by high trophic level fishes.
+
+The total effect of the temporal trends in species richness on the temporal
+trend in connectance was negative ($r_\delta =$ `r rttps$ct$r`, Fig.
+\@ref(fig:std)a), resulting from a negative direct effect ($r_\delta =$
+`r rdtps$ct$r`, Fig. \@ref(fig:sem)f) and a positive indirect effect via changes
+in the temporal trends in community biomass ($r_\delta =$ `r ridtps$ct$r`).
+Thus, when communities experienced an increase, or decrease, in species
+richness, they also experienced a concomitant increase, or decrease, in
+connectance. In contrast, species richness temporal trends had no direct effects
+on trends in average trophic level ($r_\delta =$ `r rdtps$tlvl$r`, Fig.
+\@ref(fig:sem)g), but a positive indirect effect via changes in the trends of
+community biomass ($r_\delta =$ `r ridtps$tlvl$r`), which
+adds up to a total positive effect of species richness temporal trends on
+average trophic level ($r_\delta =$ `r rttps$tlvl$r`, Fig. \@ref(fig:std)a).
+Temporal trends in species richness had a strong total positive effect on the
+trends in redundancy (resp. $r_\delta =$ `r rdtps$red$r`, `r ridtps$red$r`), via
+direct and indirect positive effects ($r_\delta =$ `r rttps$red$r`). All
+together, it means that communities that have experienced species richness
+declines over the last decades have decreased in average trophic level and
+redundancy but increased in connectance. Conversely, those that experienced
+species richness increases have increased in average trophic level, redundancy,
+but decreased in connectance.
 
 The effects of species richness were more complex, because species richness in
-this model has indirect effects on food-web structure through community biomass.
+this model has indirect effects on food web structure through community biomass.
 Species richness had a direct negative effect on connectance ($r_\delta =$
@@
 
-Furthermore, we found that temporal trends of the proportion of piscivorous
-species was negatively associated with the temporal trends of species richness
-(Fig. S2), meaning that communities that increase in richness over time have an
-increase in the proportion of non-piscivorous species over time and vice versa.
-It means food-webs that have experienced declines in species richness over the
-last decades have decreased in average trophic level and redundancy but increase
-in connectance, and conversely, those that experienced increases in species
-richness have increased in average trophic level, redundancy, but decreased in
-connectance.
-
-## Theoretical simulations and space-for-time analysis (mostly) agree with the temporal analysis
-
-We further assessed the consistency of the reported associations among temporal
-trends by implementing two additional analyses. We first tested if the
-associations among the temporal trends within sites was holding across sites,
-i.e. using spatial variations in food-web structure rather than temporal changes
-over time (space-for-time hypothesis). Second, we performed theoretical
-simulations with a bioenergetic food-web model to cross-reference our site and
-species specific empirical data on riverine fish with a more generalized
-representation of food web dynamics known to represent accurate relationships
-among our focal variables [@brose_allometric_2006; @eschenbrenner_diversity_2023;
-@danet_response_2024]. With those additional empirical and theoretical data, we
-assessed additional SEM models with the same structure as in Section 4.2.
-
-As in the temporal analysis, species richness had a positive effect on community
-biomass both in empirical data and in theoretical simulations (resp. $r_\delta
-=$ `r rdsp$bm$r` and `r rdm$bm$r`, Fig. \@ref(fig:std)a and S3). In both
-empirical data and theoretical simulations, community biomass had a positive
-effect on average trophic level (resp. $r_\delta =$ `r rdsp$tlvl$bm` and
-`r rdm$tlvl$bm`), and redundancy (resp. $r_\delta =$ `r rdsp$red$bm` and
-`r rdm$red$bm`), as in temporal analysis. We found weak evidence of a positive
-effect of spatial variation in community biomass on connectance in empirical
-data ($r_\delta =$ `r rdsp$ct$bm`) but strong evidence in theoretical
-simulations ($r_\delta =$ `r rdm$ct$bm`, Fig. \@ref(fig:std)a).
-
-The effects of spatial variations in species richness on food-web structure
-mostly aligned with those from the temporal trend analysis, except for average
-trophic level. We found a direct negative effect of species richness on
-connectance both using data and model simulations (resp. $r_\delta =$
-`r rdsp$ct$r` and `r rdm$ct$r`, Fig. \@ref(fig:std)a), on average trophic level
-(resp. $r_\delta =$ `r rdsp$tlvl$r` and `r rdm$tlvl$r`), but a direct positive
-effect on redundancy (resp. $r_\delta =$ `r rdsp$red$r` and `r rdm$red$r`).
-Species richness had an indirect positive effect of species richness through
-community biomass, which added up to strong total negative effects on
-connectance in empirical data and simulations (resp. $r_\delta =$
-`r rtsp$ct$r` and `r rtm$ct$r`) and positive on redundancy (resp. $r_\delta =$
-`r rtsp$red$r` and `r rtm$red$r`). We found that
-species richness had a total positive effect on average trophic level in
-bioenergetic model, in agreement with temporal trends (resp. $r_\delta =$ `r rtm$tlvl$r`),
-but a total negative effect in spatial variations (resp. $r_\delta =$ `r rtsp$tlvl$r`).
+Spatial analyses, either using empirical data or the bioenergetic food web
+model, largely aligned with temporal trends (Fig. \@ref(fig:std)a and S3),
+showing consistent positive effects of species richness on community biomass and
+of community biomass on average trophic level and redundancy. Species richness
+also exhibited a direct negative effect on connectance and a positive effect on
+redundancy, mirroring temporal patterns. However, spatial and temporal analyses
+diverged in their effects of species richness on average trophic level, with
+spatial data showing a negative effect and temporal trends indicating a positive
+one. Detailed statistical effects and comparisons are provided in the Appendix.
 
@@
 We implemented three secondary extinction simulation scenarios on the empirical
-metaweb defined as a food-web containing all the trophic species found across
-all sites in the empirical data. This was to access a second line of inference
-about whether top species were drivers of biomass and structure patterns (see
-section 4.2). When species are removed in a sequential order beginning by the
-highest trophic levels, connectance, average trophic level, and redundancy
-decreased (purple lines, Fig. \@ref(fig:std)b). On the other hand, removing low trophic level
-species first increases connectance and average trophic level, but do not affect
+metaweb defined as a food web containing all the trophic species, i.e. the fish
+species subdivided in size classes added to their resources, found across all
+sites in the empirical data. This was to access a second line of inference about
+whether top species were drivers of biomass and structure patterns (see section
+4.2). When species are removed in a sequential order beginning by the highest
+trophic levels, connectance, average trophic level, and redundancy decreased
+(purple lines, Fig. \@ref(fig:std)b). On the other hand, removing low trophic level species
+first increases connectance and average trophic level, but did not affect
 redundancy (yellow lines, Fig. \@ref(fig:std)b). In turn, random species extinction sequence
-had little effect on food-web structure (black line, Fig. \@ref(fig:std)b). These results, in
-tandem with our empirical analyses above, suggest that top consumers play a
-disproportionate role in driving the changes in food web structure that we
-report.
+had little effect on food web structure (black line, Fig. \@ref(fig:std)b). These results,
+in conjunction with our empirical analyses above, suggest that top consumers
+play a disproportionate role in driving the changes in food web structure
+reported.
 
@@
 std_cap <- paste0( "a, Direct and total effects of community biomass and species
-  richness trends on food-web structure trends. Standardized coefficients (r)
+  richness trends on food web structure trends. Standardized coefficients (r)
   derived from the temporal, spatial, and bioenergetic model Structural Equation
@@
 
-We found remarkable variability in the estimated temporal trends in biomass,
-species richness and three metrics of food web structure in riverine fish
-communities across more than 400 locations throughout France. Those contrasted
-situations were instrumental to evaluation the association between biodiversity
-temporal changes and food-web structure temporal changes.
-
-Via a combination of SEM modelling, simulations and more specific assessment of
-robustness to identify guild/tropho-species drivers, we found, across temporal,
-space-for-time and simulations that (1) average trophic level is consistently
-positively related to changes in total biomass; (2) connectance is consistently
-negatively related to changes in species richness; and (3) redundancy covaries
-positively with community biomass and species richness. We also found (4) a
-weak relationship between species richness and average trophic level that varied
-by temporal versus space-for-time approaches. Additionally (5) we found evidence
-for a significant role of top predator species in driving these patterns. Here
-we discuss these patterns and their implications in more depth.
-
-We found that species richness scaled positively with community biomass.  Our
-result was consistent across our temporal, spatial and theoretical simulations
-and is in-line with previous analysis across space in stream communities
-[@woods_testing_2020; @danet_species_2021] and in grasslands, salt marshes and
-forests [@hector_plant_1999; @tilman_biodiversity_2014; @wu_relationship_2015;
-@li_relationship_2018; but see @grace_integrative_2016].   These empirical data
-collectively align with theory showing that food-web diversity can increase
-biomass by stimulating primary production and resource uptake
+Our findings reveal several key patterns: (1) temporal trends in species
+richness were positively associated with trends in community biomass; (2)
+temporal trends in community biomass were positively linked to trends in
+connectance and average trophic level; (3) temporal trends in species richness
+were negatively associated with trends in connectance but only weakly related to
+trends in average trophic level; and (4) both community biomass and species
+richness trends were positively associated with trends in trophic pathway
+redundancy. Additionally, we found that (5) top predator species play a
+significant role in driving these patterns. Importantly, these temporal
+relationships were largely consistent with patterns observed across spatial
+gradients, both in empirical data and in simulations from a bioenergetic food
+web model. In the following discussion, we explore these findings in the context
+of food web assembly theory and Biodiversity-Ecosystem Functioning theory, and
+consider their broader ecological implications.
+
+We found that community biomass scaled positively with species richness, a
+pattern consistent across our temporal, spatial, and theoretical analyses. This
+result aligns with previous studies in fish communities [@woods_testing_2020;
+@danet_species_2021] as well as in grasslands, salt marshes, and forests
+[@hector_plant_1999; @tilman_biodiversity_2014; @wu_relationship_2015;
+@li_relationship_2018; but see @grace_integrative_2016]. These empirical
+findings are supported by theory, which suggests that food web diversity
+enhances biomass by stimulating primary production and resource uptake
 [@schneider_animal_2016; @wang_biodiversity_2018; @wang_intraguild_2019;
-@nie_will_2023] and Biodiversity-Ecosystem Functioning theory where the loss of
-species richness and biomass predicts impaired ecosystem functioning
-[@loreau_biodiversity_2001]. These data and theory firmly indicate that loss of
-biodiversity per se (e.g. species richness) can lead to overall loss of biomass
-in many ecosystems and mitigating actions that increase biodiversity can lead to
-an increase in community biomass.
-
-Our results also show that food-webs that have undergone a biomass decline
-experienced significant structural changes marked by a loss of top trophic
-levels species and a decreased connectance. These results can be linked with the
-energetic and trophic biogeography theories [@lindeman_trophic-dynamic_1942;
-@gravel_trophic_2011], which posit that the presence of high trophic level
-species is limited by the productivity and the amount of energy available
-[@lindeman_trophic-dynamic_1942, @takimoto_ecosystem_2008; @post_ecosystem_2000;
-@post_long_2002]. Thus, our results suggest a decrease in community biomass can
-limit the amount of resource available to sustain high trophic level species,
-while increase in community biomass may translate in more resources available
-for high trophic level species [@takimoto_ecosystem_2008; @post_ecosystem_2000].
-
-Biodiversity-Ecosystem Functioning theory offers an alternative causal
-explanation, indeed the presence of higher trophic level species can decrease
-niche overlap among producers and then increase productivity and community
-biomass [@schneider_animal_2016; @wang_biodiversity_2018; @wang_intraguild_2019;
-@nie_will_2023]. The positive association of connectance with community biomass
-was weaker than for average trophic level, which might be related to the
-contrasting effects of connectance, negative or positive, on productivity
-previously reported in theoretical models [@nie_will_2023;
-@wang_intraguild_2019; @thebault_food-web_2003; @poisot_trophic_2013;
-@schneider_animal_2016]. While increasing connectance between herbivores and
-plants has been reported to either increase or decrease productivity
-[@thebault_food-web_2003; @poisot_trophic_2013; @nie_will_2023], increasing
-connectance within carnivores having generally a positive effect on productivity
-because higher connectance can decrease top-down control and allow biomass to
-accumulate across trophic level [@wang_intraguild_2019; @schneider_animal_2016].
-
-Species richness was negatively associated with connectance, confirming previous
-results [@dunne_network_2006], and was suggested to be the results of
-limitations of predator generality [@dunne_network_2006]. The effects of species
-richness changes on the average trophic level were more contrasted and twice
-lower in strength than the effects of community biomass. The direct effect of
-species richness on average trophic level being null, or negative considering
-temporal or spatial and theoretical models. When accounting for the indirect
-effect of species richness on community biomass, temporal and theoretical
-analysis indicates changes in species richness are positively associated with
-changes in average trophic level. Those contrasted effects of species richness
-on average trophic level can be related to the results of our extinction
-simulations where the removal of top trophic level species had much less impact
-on average trophic level than on connectance and redundancy. This discrepancy in
-space and time is likely due to the strong assumption that variations in space
-reflect differences in assembly stages of ecological communities and then mirror
-their temporal assembly/disassembly trajectories. Spatial gradients reflect
-aggregated dynamics over a longer timescale including a far number of
-processes including high species turnover and differences in ecosystem
-productivity along spatial gradients that are not captured by species richness
-[@post_ecosystem_2000; @post_long_2002].
-
-Altogether, our results then suggest community biomass changes in space might be
-a good surrogate to infer assembly and disassembly of food-webs in time, but
-that it is probably not always the case for species richness. Furthermore, it
-suggests that species richness increase and decrease were less clearly linked to
-specific changes in top trophic levels than community biomass. Species richness
-temporal trends could be more linked to changes in the redundancy of trophic
-roles in the food-webs, such as it has little effect on food-web structure
-itself but increases its community biomass. This interpretation aligns with the
-insurance hypothesis [@yachi_biodiversity_1999; @loreau_biodiversity_2021], such
-as species richness and associated redundancy in species roles can increase
-ecosystem stability by buffering the impacts of perturbations
-[@sanders_trophic_2018].
-
-Our study also demonstrates that redundancy of trophic pathways in food-webs are
-positively associated to both community biomass and species richness changes, so
-as declines in community biomass and species richness triggers a loss in the
-proportion of redundant links in food-webs, while increases in community biomass
-and species richness over time results in the increase in the proportion of
-redundant links in food-webs. Redundant links are the trophic links that can be
-removed with triggering secondary extinctions [@allesina_who_2004;
-@bodini_using_2009], such a higher proportion of redundant interactions increase
-robustness of food-webs to perturbations [@allesina_functional_2009]. It
-suggests that declines in community biomass and species richness result in a
-decline of food-web robustness to further perturbations. The positive link
-between redundancy and biomass is consistent to previous theoretical results
-showing that higher redundancy in trophic pathways could be associated with a
-decrease in complementarity within trophic species which in turn can reduce
-top-down effects and stimulate biomass productions [@wang_biodiversity_2018;
-@wang_intraguild_2019], and also give opportunity for compensatory dynamics
-which in turn increase robustness following extinctions
-[@staniczenko_structural_2010].
-
-We aimed to expose the relationships among three metrics of food web structure,
-community biomass and species richness. Our results, derived from a larger and
-extensive temporal and spatially resolved dataset, align with multiple bodies of
-theory and deliver consistent results across multiple methodologies. In an era
-of rapid anthropogenic driven change impacting directly the biodiversity of
-communities, these relationships are vital to our capacity to predict and
-mitigate effects. For example, our results suggest that community biomass
-changes are associated with changes in the presence and biomass of top
-predators, in agreement with two bodies of theory. Energetic theory which
-assumes that food-web maximum trophic level are mainly limited by the amount of
-energy available in lower trophic levels and Biodiversity-Ecosystem Functioning
-theory which assumes that the presence of higher trophic levels is the cause of
-higher productivity and total biomass. In contrast, species richness changes
-seem to be linked to changes in the upper and lower part of the food-webs.
-Importantly, temporal and spatial analysis using empirical fish food-webs are
-largely in agreement with theoretical simulations, which highlight the potential
-generality of the food-web assembly rules that we report. The study finally
-highlights that increases in community biomass and species richness brings
-robustness to food-webs by increasing the proportion of redundant trophic links.
-Altogether, our results suggest that assessments of food-web structure,
-community biomass and richness, which may be more feasible than direct
-estimation of function, may deliver much needed indicators of functional decline
-and metrics thus for the efficacy of mitigation strategies.
+@nie_will_2023] and by Biodiversity-Ecosystem Functioning theory, which predicts
+that species loss reduces community biomass [@loreau_biodiversity_2001]. Our
+results reinforce the idea that declines in species richness can lead to reduced
+biomass across ecosystems, highlighting the potential for conservation actions
+that promote species richness to also enhance community biomass.
+
+Our results also reveal that food webs experiencing biomass declines undergo
+significant structural changes, including the loss of top predators and reduced
+connectance. These findings align with energetic and trophic biogeography
+theories [@lindeman_trophic-dynamic_1942; @gravel_trophic_2011], which posit
+that the presence of high-trophic-level species is constrained by the
+availability of energy and resources [@lindeman_trophic-dynamic_1942,
+@takimoto_ecosystem_2008; @post_ecosystem_2000; @post_long_2002]. Thus, a
+decline in community biomass may lead to insufficient resources to sustain top
+predators, while an increase in biomass could provide the necessary energy to
+support these species [@takimoto_ecosystem_2008; @post_ecosystem_2000].
+Alternatively, Biodiversity-Ecosystem Functioning theory suggests that the
+presence of higher trophic levels may reduce niche overlap among producers,
+enhancing productivity and community biomass [@schneider_animal_2016;
+@wang_biodiversity_2018; @wang_intraguild_2019; @nie_will_2023]. The
+relationship between community biomass and connectance is less clear, with a
+weaker positive association compared to average trophic level. Previous
+theoretical studies have reported contrasting effects of connectance on
+productivity [@nie_will_2023; @wang_intraguild_2019; @thebault_food-web_2003;
+@poisot_trophic_2013; @schneider_animal_2016]. For instance, while increased
+connectance between herbivores and plants can either enhance or reduce
+productivity [@thebault_food web_2003; @poisot_trophic_2013; @nie_will_2023],
+greater connectance among carnivores generally boosts productivity by reducing
+top-down control and allowing biomass to accumulate across trophic levels
+[@wang_intraguild_2019; @schneider_animal_2016].
+
+Our study demonstrates that temporal trends in community biomass and species
+richness are positively associated with the proportion of redundant trophic
+pathways in food webs. In other words, declines in community biomass and species
+richness lead to a loss of redundant links, while increases in these factors
+result in greater redundancy. Since redundant links are those that can be
+removed without triggering secondary extinctions [@allesina_who_2004;
+@bodini_using_2009], our findings suggest that declines in community biomass and
+species richness reduce food web robustness to further perturbations
+[@allesina_functional_2009]. The positive effect of community biomass on
+redundancy aligns with theoretical predictions: higher redundancy can reduce
+trophic complementarity within species, weaken top-down control, and promote
+compensatory dynamics, thereby enhancing robustness following extinctions
+[@staniczenko_structural_2010]. Similarly, the positive effect of species
+richness on redundancy supports the insurance hypothesis
+[@yachi_biodiversity_1999; @loreau_biodiversity_2021], where greater species
+richness and functional redundancy buffer ecosystems against perturbations,
+increasing stability [@sanders_trophic_2018].
+
+Furthermore, our results highlight the disproportionate role of top
+trophic-level species in maintaining redundant links within food webs. This
+pattern is consistent with previous empirical studies showing that top predators
+are often the most generalist and highly connected species
+[@montoya_ecological_2006; @montoya_press_2009]. Consequently, disturbances
+affecting these top predators are likely to have the greatest impact on overall
+community stability [@montoya_press_2009]. These findings underscore the
+importance of preserving top predators and maintaining species richness to
+safeguard food web robustness and ecosystem stability.
+
+Species richness was negatively associated with connectance, consistent with
+previous findings and likely driven by limitations in predator generality
+[@dunne_network_2006]. In contrast, the effects of species richness on average
+trophic level were more nuanced and considerably weaker than those of community
+biomass. Direct effects of species richness on average trophic level were either
+negligible or negative, as observed in temporal, spatial, and theoretical
+models. However, when accounting for the indirect effects of species
+richness—mediated through changes in community biomass—temporal and theoretical
+analyses revealed a positive association between species richness and average
+trophic level. These contrasting effects may be explained by our extinction
+simulations, which showed that the removal of top trophic-level species had a
+much smaller impact on average trophic level than on connectance. This suggests
+that while species richness influences food web structure, its effects are more
+pronounced on connectance than on average trophic level dynamics.
+
+We found strong agreement between our temporal and spatial analyses, as well as
+with predictions from food web theory and Biodiversity-Ecosystem Functioning
+research. This suggests that spatial comparisons of generic topological food web
+properties and biodiversity metrics may serve as reasonable surrogates for
+predicting temporal trends—supporting the validity of the space-for-time
+substitution in both empirical data and bioenergetic food web models. However,
+this agreement did not hold for the relationship between weighted average
+trophic level (hereafter “average trophic level”) and species richness. This
+discrepancy may arise because average trophic level incorporates both food web
+topology and biomass distribution, which are influenced by dynamic processes
+such as bottom-up and top-down control. These processes likely require
+additional information about species metabolism and productivity
+[@brose_allometric_2006; @barbier_pyramids_2019]. This interpretation is
+supported by the fact that our spatial analysis accurately predicted the
+temporal association between community biomass and average trophic level.
+
+Our study provides compelling evidence that biodiversity trends are profoundly
+reshaping food web structure. By linking these patterns to
+Biodiversity-Ecosystem Functioning and food web theory, we demonstrate that
+widespread biodiversity declines likely have significant and detrimental
+consequences for ecosystem functioning and stability in the face of future
+perturbations. These findings suggest that assessments of food web structure,
+community biomass, and species richness—which are often more feasible than
+direct measurements of ecosystem functions—could serve as valuable indicators of
+functional decline and metrics for evaluating the efficacy of mitigation
+strategies. Importantly, our study also highlights critical avenues for future
+research, stemming from its limitations. For instance, integrating food web
+metrics into conservation planning will require understanding how they relate to
+other facets of biodiversity, such as the presence of non-native species, and
+drivers of biodiversity changes, including habitat degradation
+[@danet_past_2024] and climate change [@bonnaffe_warming_2024]. Ultimately, our
+work aims to bridge the gap between Biodiversity-Ecosystem Functioning and food
+web theory, fostering greater integration with research on biodiversity changes.
 
@@
 
-We used a monitoring of freshwater fishes conducted all over France and
-conducted by the Office Français de la Biodiversité (OFB). The sampling
-protocols were standardized since 1995 and a complete description of the
-sampling process can be found in @danet_species_2021. The fishes are sampled
-using electrofishing all across the streams in shallow streams and over the bank
-by boat in deeper streams. All the fishes are counted and the bodysize of fishes
-are recorded for a sample of them, enabling the estimate the distribution of
-individual bodysize by species for each sampling [@bonnaffe_comparison_2021;
+We used a monitoring of freshwater fishes conducted all over France by the
+Office Français de la Biodiversité (OFB). The sampling protocols were
+standardized since 1995 and a complete description of the sampling process can
+be found in @danet_species_2021. The fishes are sampled using electrofishing all across the
+streams in shallow streams and over the bank by boat in deeper streams. All the
+fishes are counted and the body size of fishes are recorded on a sample of
+individuals, enabling to estimate the distribution of individual body size by
+species for each sampling [@bonnaffe_comparison_2021;
 @danet_species_2021].
 
-We selected the sites that have been monitored at least 10 years on the
-1995-2018 period, with the same sampling protocol over time. We selected
-one sampling a year by site. In each site, we ensured low temporal heterogeneity
-in sampling period by selecting sampling that were performed in the same period,
-leading to a mean standard deviation of sampled month in each site of three
-weeks [@danet_species_2021]. Those steps lead to the selection of
-`r nb_st` sites (Fig. \@ref(fig:matmet), Table S1).
+We selected the sites that have been monitored for at least 10 years in the
+1995-2018 period, with the same sampling protocol over time. We selected one
+sampling per year by site. In each site, we ensured low temporal heterogeneity
+within the sampling period by selecting samplings that were performed in the
+same period, leading to a mean standard deviation of sampled month in each site
+of three weeks [@danet_species_2021]. Those steps lead to the selection of
+`r nb_st` sites (Fig. \@ref(fig:matmet)a, Table S1).
 
@@
 
-We first inferred the body mass of each fish individual considering an allometric
-law, $B_i = 0.01 \times l_i^{3.03}$, $B_i$ being the biomass expressed in gram and $l_i$ the
-body length of the individual $i$ expressed in millimeters [@froese_cube_2006]. Then the
-biomass of each species and community biomass were obtained by summing the body
-mass of individuals. Finally, the biomass was reported to the sampled surface
-(in $m^2$) to account for sampling effort.
-
-## Food-web inference
-
-We inferred food-web structure in two steps [@bonnaffe_comparison_2021;
+We first estimated the body mass of each fish individual with the allometric
+law: $B_i = 0.01 \times l_i^{3.03}$, $B_i$ being the biomass expressed in gram and $l_i$ the
+body length of the individual $i$ expressed in millimeters [@froese_cube_2006;
+@danet_species_2021]. Then the biomass of each species and community
+were obtained by summing the body mass of individuals. Finally, the biomass was
+reported to the sampled surface (in $m^2$) to account for sampling effort.
+
+## Food web reconstructions
+
+We reconstructed food web structure in two steps [@bonnaffe_comparison_2021;
 @danet_species_2021]: (1) we first computed the metaweb, describing the
 potential trophic interactions among all size classes species, (2) then we
-extracted each yearly snapshot of food-webs by extracting species size classes
-and their interactions according to their presence in a given sampling event.
+extracted yearly species size classes and their interactions according to their
+presence in a given sampling event, to establish a annual snapshot of food webs.
 
 We inferred the metaweb according to ontogenic diet data and body size
-[@gravel_inferring_2013; @@poisot_trophic_2013; @brose_predator_2019;
+[@gravel_inferring_2013; @poisot_trophic_2013; @brose_predator_2019;
 @bonnaffe_comparison_2021; @danet_species_2021]. The method is extensively
@@
 stream fishes changes along their life cycle or stage, therefore according to
-their body size. Each fish species was divided in nine size classes, named
-"trophic species", equally distributed in their observed body size range. Thus,
+their body size. Each fish species was divided in nine size classes, i.e.
+trophic species, equally distributed in their observed body size range. Thus,
 a trophic species is a group of individuals of the same species and size class
@@
 interactions are largely determined by predator-prey size ratio
-[@brose_allometric_2006]. We also added seven nodes present in the ontogenic
+[@brose_allometric_2006; @brose_predator_2019]. We also added seven nodes present in the ontogenic
 food diet database: detritus, biofilm, phytoplankton, zooplankton, macrophages,
 phytobenthos and zoobenthos.  The resulting metaweb contained 45 fish species
-divided into nine size classes plus 7 resource nodes, summing up to 412 nodes.
+divided into 9 size classes plus 7 resource nodes, summing up to 412 nodes.
 Consideration of size classes, i.e.  trophic species instead of species,
@@
 window.  The fish-resource trophic links were set between the trophic species
-and the resources nodes according to the food items of their size class.
+and the resource nodes according to the food items of their size class.
 Finally, the feeding interactions between resources were defined according to the
@@
 
-## Community and food-web structure
-
-At each site, yearly food-webs were described by their community biomass and
-species richness. Yearly food-web structure was described by their connectance,
+## Community and food web structure
+
+At each site, yearly food webs were described by their community biomass and
+species richness. Yearly food web structure was described by their connectance,
 describing the degree of generalism in a network [@dunne_network_2006;
-@delmas_analysing_2019]. It was computed as the ratio between the number of
-actual links and the number of potential links ($C = \frac{L}{S(S-1)}$, with $L$
-being the number of links and $S$ the number of trophic species). We also
-computed the average trophic level, weighted by the biomass of the trophic
-species. The trophic level of a trophic species was computed recursively as 1
-added to the mean trophic level of the preys that it consumes
-[@herendeen_ecological_2008]. We computed the number of redundant and functional
-links using the dominator tree approach [@allesina_functional_2009]. A species
-$i$ is a dominator of species $j$ if $i$ mediates the connection $j$ to basal
-resources such as the extinction of $i$ remove the connection of $j$ to basal
-resources. It is then to identify the set of trophic links that are essential to
-connect species to basal resources, i.e. functional links, and the
-redundant links. This method requires a single basal root in the food-webs. To
-do so, we added a basal dummy resource node to the empirical food-webs connected
-to biofilm and phytoplankton resource node. For food-webs generated from
+@delmas_analysing_2019]. Connectance was computed as the ratio between the
+number of actual links and the number of potential links ($C =
+\frac{L}{S(S-1)}$, with $L$ being the number of links and $S$ the number of
+trophic species). We also computed the average trophic level, weighted by the
+biomass of the trophic species. The trophic level of a trophic species was
+computed recursively as 1 added to the mean trophic level of the preys it
+consumes [@herendeen_ecological_2008]. We computed the number of redundant and
+functional links using the dominator tree approach [@allesina_functional_2009].
+A species $i$ is a dominator of species $j$ if $i$ mediates the connection $j$
+to basal resources such as the extinction of $i$ remove the connection of $j$ to
+basal resources. It is then to identify the set of trophic links that are
+essential to connect species to basal resources, i.e. functional links, and the
+redundant links. This method requires a single basal root in the food webs. To
+do so, we added a basal dummy resource node to the empirical food webs connected
+to biofilm and phytoplankton resource nodes. For food webs generated from
 theoretical simulations (see below), we added a resource node connected to all
 primary producers. We computed the set of dominator trees using the
-`dominator_tree()` function in `igraph` R package. We computed the number of
-functional links as the number of links in the resulting dominator tree of the
-food-web. We checked that the procedure reproduced the examples presented in
-@allesina_functional_2009. We then derived the proportion of redundant links in
-food-webs of empirical and theoretical simulations.
-
-## Temporal trends of food-web
-
-We modeled the temporal trends of food-web structure at each site ($Y_i$) using
-linear hierarchical model. Time was considered as the number of year since the
+`dominator_tree()` function from the `igraph` R package (Appendix B). We
+computed the number of functional links as the number of links in the resulting
+dominator tree of the food web. We checked that the procedure reproduced the
+examples presented in previous studies [@allesina_functional_2009, Appendix B].
+We then derived the proportion of redundant links in food webs of empirical and
+theoretical simulations.
+
+## Temporal trends of food web
+
+We modeled the temporal trends of food web structure at each site ($Y_i$) using
+linear hierarchical model. Time was considered as the number of years since the
 first sampling ($t = 0$) at each site. We accounted for the spatial structure of
@@
 5.10^-5)$), then their respective standard deviation were obtained by
-backtransforming the inverse scale parameter ($\sigma = 1 / \sqrt{\tau}$).
-Community biomass and species richness were logged transformed.
+back-transforming the inverse scale parameter ($\sigma = 1 / \sqrt{\tau}$).
+Community biomass and species richness were log-transformed.
 
@@
 Integral Transform (PIT) and Conditional Predictive Ordinate (CPO) to assess the
-quality of the model fit. We also computed the marginal ($R^2_m$)and conditional
+quality of the model fit. We also computed the marginal ($R^2_m$) and conditional
 ($R^2_c$) R-squared of the models following previous formulations
@@
 using mean BLUP values (Best Linear Unbiaised Prediction), then multiplied
-by 10 to get temporal trends by decade. For logged transformed biomass and
-species richness, we derived percentage change by decade by transforming the
-slopes ($\beta\prime = (e^{\beta } - 1) \times 100 \times 10$).
+by 10 to get temporal trends by decade. For community biomass and species
+richness which were log-transformed, we derived temporal trends in percentage
+change by decade by back-transforming the slopes ($\beta\prime = (e^{\beta } - 1)
+\times 100 \times 10$).
 
@@
 We assessed the validity of the space-for-time substitution hypothesis by
-comparing the relationships estimated among food-web structure in time to the
+comparing the relationships estimated among food web structure in time to the
 ones inferred in space. We used the same sites as in the temporal analysis,
-but we summarized temporal series of each station by the median value over time
-of each facet of food-web structure described above (Fig. \@ref(fig:matmet)).
+but we summarized the temporal series of each station by the median value over time
+of each facet of food web structure described above (Fig. \@ref(fig:matmet)).
 
@@
 
-We modeled the relationships among food-web structure, that is connectance,
+We modeled the relationships among food web structure indices, i.e. connectance,
 average trophic level, the proportion of redundant trophic links, and community
-biomass ($dB$) and species richness ($dR$) with Structural Equation Models. We
-modeled species richness as related to community biomass and food-web structure.
-In turn community biomass was related to food-web structure. We computed one
+biomass and species richness, with Structural Equation Models. We
+modeled species richness as related to community biomass and food web structure.
+In turn, community biomass was related to food web structure. We computed one
 structural equation model to assess the relationships among the temporal trends
@@
 [@murphy_semeff_2021]. Confidence intervals were obtained by bootstrapping the
-linear models 1000 times and computing adjusted bootstrap percentile interval
+linear models 1000 times and computing adjusted bootstrap percentile intervals
 (BCa), which are adjusted for the asymmetric distribution of resampling. The marginal
@@
 We simulated extinction sequences in the metaweb according to three scenarios to
-get expectations on how the food-web structure should change according to the
+get expectations on how the food web structure should change according to the
 addition and deletion of species and nodes. The scenario of extinction sequences
@@
 
-We used a bioenergetic food-web model to simulate the effects of community
-biomass and species richness changes on food-web structure. This food-web model
-lifts one of the limitation of our data, that is it includes the biomass of all
-the food-webs from primary producers to top predators. This model allows
+We used a bioenergetic food web model to simulate the effects of community
+biomass and species richness changes on food web structure. This food web model
+lifts one of the limitations of our data, that is it includes the biomass of all
+the food webs from primary producers to top predators. This model allows
 simulating complex communities because its parameterization depends mainly on
-species bodymasses. We first generated `r nfw` food-webs varying in species
+species bodymasses. We first generated `r nfw` food webs varying in species
 richness (range: `r s_range["min"]`-`r s_range["max"]`)
 and connectance (range: `r c_range["min"]`-`r c_range["max"]`) using the niche
-model algorithm, which reproduces food-web topology typically found in empirical
-food-webs [@williams_simple_2000]. We set species bodymasses ($M_i$) using a predator-prey
+model algorithm, which reproduces food web topology typically found in empirical
+food webs [@williams_simple_2000]. We set species bodymasses ($M_i$) using a predator-prey
 mass ratio of 100 ($Z$) [@brose_allometric_2006; @brose_predator_2019], such as $M_i =
@@
 metabolic rates ($x_j$), attack rates ($y_j$, set to 8 @delmas_analysing_2019),
-a functional response (F_{ji}), and assimilation efficiency ($e_{ij}$, set to
+a functional response ($F_{ji}$), and assimilation efficiency ($e_{ij}$, set to
 0.45 for herbivores and 0.85 for carnivores, @delmas_analysing_2019).
@@
 
-We simulated the dynamics of the `r nfw` food-webs across a gradient of global carrying capacity (K,
+We simulated the dynamics of the `r nfw` food webs across a gradient of global carrying capacity (K,
 range: `r k_range["min"]`-`r k_range["max"]`). The carrying capacity were
@@
 simulations for 5000 timesteps. At the end of simulations, we removed dead
-species and measured community biomass, species richness and food-web structure.
+species and measured community biomass, species richness and food web structure.
 If the final community contained disconnected producers (i.e. without consumers)
 or disconnected consumers (i.e. consumers without preys), we discarded them and
-run the simulations again with the same parametrisation. The simulations were
+run the simulations again with the same parametrization. The simulations were
 done using the Julia package `EcologicalNetworksDynamics.jl`
-[@lajaaiti_ecologicalnetworksdynamicsjl_2024]. Then we computed the community
-and food-web metrics at the last timesteps and analyzed the data with the same
-SEM than described above.
+[@lajaaiti_ecologicalnetworksdynamicsjl_2024]. Then, we computed the community
+and food web metrics at the last timesteps and analyzed the data with the same
+SEM described above.
 

### 2025-02-07 paper/appendix.Rmd
Minor edits: sent to Loubna & Willem for review

--- 2024-11-14 paper/appendix.Rmd
@@
 ---
-title: Appendix
-subtitle:
-author: Alain Danet, Loubna El Madouri, Maud Mouchet, Elisa Thébault and Colin Fontaine
-date: \today
+title: "Biodiversity temporal trends are reshaping food web structure and redundancy in riverine ecosystems"
+subtitle: "Alain Danet (a,b), Loubna El Madouri (a,c), Andrew P. Beckerman (b),
+Maud Mouchet (a), Colin Fontaine (a) and Elisa Thébault (d)"
+date: Supplementary Material
 output:
@@
 header-includes:
-   - \usepackage{natbib}
    - \newcommand{\beginsupplement}{\renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
@@
 number_sections: false
+csl: pnas.csl
 ---
@@
 library(nlme)
+library(igraph)
 
@@
 
+```{r}
+tar_load(c(semeff_tot, semeff_tot_ok))
+semeff_tot <- semeff_tot %>%
+  mutate(across(c(response, predictor), ~str_remove(.x, "mean_")))
+
+rdtps <- map(
+  setNames(
+    c("connectance", "w_trph_lvl_avg", "log_bm_std", "prop_redundant_links"),
+    c("ct", "tlvl", "bm", "red")
+    ),
+  ~ list(
+    bm = get_semeff_ci(resp = .x, term = "log_bm_std"),
+    r = get_semeff_ci(resp = .x, term = "log_rich_std")
+    )
+)
+rdsp <- map(
+  setNames(
+    c("connectance", "w_trph_lvl_avg", "log_bm_std", "prop_redundant_links"),
+    c("ct", "tlvl", "bm", "red")
+    ),
+  ~ list(
+    bm = get_semeff_ci(resp = .x, term = "log_bm_std", model = "spatial"),
+    r = get_semeff_ci(resp = .x, term = "log_rich_std", model = "spatial")
+    )
+)
+rdm <- map(
+  setNames(
+    c("Connectance", "Avg trophic level", "Biomass", "Redundancy"),
+    c("ct", "tlvl", "bm", "red")
+    ),
+  ~ list(
+    bm = get_semeff_ci(x = semeff_tot_ok, type = "Direct", resp = .x, term = "Biomass", model = "Theoretical model"),
+    r = get_semeff_ci(x = semeff_tot_ok, type = "Direct", resp = .x, term = "Species richness", model = "Theoretical model")
+    )
+)
+```
+
+```{r}
+ridtps <- map(
+  setNames(
+    c("connectance", "w_trph_lvl_avg", "log_bm_std", "prop_redundant_links"),
+    c("ct", "tlvl", "bm", "red")
+    ),
+  ~ list(
+    r = get_semeff_ci(resp = .x, term = "log_rich_std", type = "indirect")
+    )
+)
+ridsp <- map(
+  setNames(
+    c("connectance", "w_trph_lvl_avg", "log_bm_std", "prop_redundant_links"),
+    c("ct", "tlvl", "bm", "red")
+    ),
+  ~ list(
+    r = get_semeff_ci(resp = .x, term = "log_rich_std",
+      model = "spatial", type = "indirect")
+    )
+)
+ridm <- map(
+  setNames(
+    c("Connectance", "Avg trophic level", "Biomass", "Redundancy"),
+    c("ct", "tlvl", "bm", "red")
+    ),
+  ~ list(
+    bm = get_semeff_ci(x = semeff_tot_ok, type = "Indirect", resp = .x, term = "Biomass", model = "Theoretical model"),
+    r = get_semeff_ci(x = semeff_tot_ok, type = "Indirect", resp = .x, term = "Species richness", model = "Theoretical model")
+    )
+)
+rttps <- map(
+  setNames(
+    c("connectance", "w_trph_lvl_avg", "log_bm_std", "prop_redundant_links"),
+    c("ct", "tlvl", "bm", "red")
+    ),
+  ~ list(
+    bm = get_semeff_ci(resp = .x, term = "log_bm_std", type = "total"),
+    r = get_semeff_ci(resp = .x, term = "log_rich_std", type = "total")
+    )
+)
+rtsp <- map(
+  setNames(
+    c("connectance", "w_trph_lvl_avg", "log_bm_std", "prop_redundant_links"),
+    c("ct", "tlvl", "bm", "red")
+    ),
+  ~ list(
+    bm = get_semeff_ci(resp = .x, term = "log_bm_std",
+      model = "spatial", type = "total"),
+    r = get_semeff_ci(resp = .x, term = "log_rich_std",
+      model = "spatial", type = "total")
+    )
+)
+rtm <- map(
+  setNames(
+    c("Connectance", "Avg trophic level", "Biomass", "Redundancy"),
+    c("ct", "tlvl", "bm", "red")
+    ),
+  ~ list(
+    bm = get_semeff_ci(x = semeff_tot_ok, type = "Total", resp = .x, term = "Biomass", model = "Theoretical model"),
+    r = get_semeff_ci(x = semeff_tot_ok, type = "Total", resp = .x, term = "Species richness", model = "Theoretical model")
+    )
+)
+```
+
 \beginsupplement
+
+# Comparison of analysis in space and time
+
+We further assessed the consistency of the reported associations among temporal
+trends by implementing two additional analyses. We first tested if the
+associations among the temporal trends within sites was holding across sites,
+i.e. using spatial variations in food web structure rather than temporal changes
+over time (space-for-time hypothesis). Second, we performed theoretical
+simulations with a bioenergetic food web model to cross-reference our site and
+species specific empirical data on riverine fish with a more generalized
+representation of food web dynamics known to represent accurate relationships
+among our focal variables [@brose_allometric_2006; @eschenbrenner_diversity_2023;
+@danet_response_2024]. With those additional empirical and theoretical data, we
+assessed additional SEM models with the same structure as in Section 4.2.
+
+As in the temporal analysis, species richness had a positive effect on community
+biomass both in empirical data and in theoretical simulations (resp. $r_\delta
+=$ `r rdsp$bm$r` and `r rdm$bm$r`, Fig. 3a and S3). In both
+empirical data and theoretical simulations, community biomass had a positive
+effect on average trophic level (resp. $r_\delta =$ `r rdsp$tlvl$bm` and
+`r rdm$tlvl$bm`), and redundancy (resp. $r_\delta =$ `r rdsp$red$bm` and
+`r rdm$red$bm`), as in temporal analysis. We found weak evidence of a positive
+effect of spatial variation in community biomass on connectance in empirical
+data ($r_\delta =$ `r rdsp$ct$bm`) but strong evidence in theoretical
+simulations ($r_\delta =$ `r rdm$ct$bm`, Fig. 3a).
+
+The effects of spatial variations in species richness on food web structure
+mostly aligned with those from the temporal trend analysis, except for average
+trophic level. We found a direct negative effect of species richness on
+connectance both using data and model simulations (resp. $r_\delta =$
+`r rdsp$ct$r` and `r rdm$ct$r`, Fig. 3a), on average trophic level
+(resp. $r_\delta =$ `r rdsp$tlvl$r` and `r rdm$tlvl$r`), but a direct positive
+effect on redundancy (resp. $r_\delta =$ `r rdsp$red$r` and `r rdm$red$r`).
+Species richness had an indirect positive effect of species richness through
+community biomass, which added up to strong total negative effects on
+connectance in empirical data and simulations (resp. $r_\delta =$
+`r rtsp$ct$r` and `r rtm$ct$r`) and positive on redundancy (resp. $r_\delta =$
+`r rtsp$red$r` and `r rtm$red$r`). We found that
+species richness had a total positive effect on average trophic level in
+bioenergetic model, in agreement with temporal trends (resp. $r_\delta =$ `r rtm$tlvl$r`),
+but a total negative effect in spatial variations (resp. $r_\delta =$ `r rtsp$tlvl$r`).
+
+# Disantengling functional and redundant links
+
+Because species biomass are involved in trophic interactions, species losses can
+have cascading effects and trigger secondary extinctions [@dunne_network_2002].
+In the context of biodiversity crisis, assessing the robustness of ecological
+networks to species losses has been then a big question in Ecology. Previous
+research showed that food-web structure, such as connectance, increased
+robustness [@dunne_network_2002]. The idea is that more connected food-web will
+be more stable because they contain a large number of pathways convey biomass
+through the food-web. However, connectance as some limitations as a robustness
+metric, because each trophic link does not contribute equally to the robustness
+of an ecological network [@allesina_who_2004]. Trophic links can be categorised as
+functional or redundant, depending on their role in transmitting biomass through
+the food-web. Functional links are the set of links that is required to connect
+every species to the basal resource of the food-web, all of the other being
+redundant. Only functional links affect directly robustness, as their removal
+will trigger secondary extinctions. The removal of redundant links in turn do
+not directly trigger secondary extinctions, but makes the food-webs more fragile
+to further extinctions [@allesina_functional_2009].
+
+The identification of functional and redundant links is based on the use of
+denominator trees [@bodini_using_2009; @allesina_who_2004;
+@allesina_functional_2009]. Dominator trees allows to identify the set of
+trophic links that are essential to connect all the consumers to the basal resource, i.e.
+the functional links, and the redundant links, i.e. the redundant trophic pathways
+from basal resource to consumers. Pioneer papers explained the algorithm to
+compute the set of dominator trees and we refer to them for further
+information and examples [@bodini_using_2009; @allesina_who_2004;
+@allesina_functional_2009]. Here, we aim to show that while implementing this
+analysis could be difficult at the time, this algorithm is now widely
+available. In R, it is available in `igraph::dominator_tree()`. Below we show
+how the number of functional and redundant links can be  easily computed from R
+by replicating three examples presented in previous studies.
+
+```{r, echo = TRUE}
+compute_redundancy
+```
+
+Here is an example with the food-web displayed in appendix of
+@bodini_using_2009:
+
+```{r, echo = TRUE}
+# Get the food-web example from Bodini et al. (2009), Appendix 1 
+g <- get_bodini_graph_appendix()
+# compute reduncancy
+out <- compute_redundancy(g, root = "R")
+as.data.frame(out)
+```
+
+```{r}
+vertex_color <- "white"
+vertex_size  <- 40
+```
+
+We used this function to reproduce the three examples (Fig. \@ref(fig:examples)),
+which were displayed in the Fig. 1 and Appendix 1 of @bodini_using_2009, and
+in the Fig. 1 of @allesina_functional_2009. The table \@ref(tab:redun) displays
+the number and the proportion of functional and redundant links from those
+examples.
+
+```{r bod1}
+bodinifig1 <- get_bodini_graph_fig1()
+
+# Complete graph
+p_bodinifig1_all <- ~{
+  lg <- layout_as_tree(bodinifig1, root = "root")
+  lg[, 2] <- -lg[, 2]
+  plot(bodinifig1, layout = lg, vertex.color = vertex_color, vertex.size = vertex_size)
+}
+
+# Only functional links
+bodinifig1_dtree <- dominator_tree(bodinifig1, root = "root")
+p_bodinifig1_functional <- ~{
+  layout <- layout_as_tree(bodinifig1_dtree$domtree, root = "root")
+  layout[, 2] <- -layout[, 2]
+  plot(bodinifig1_dtree$domtree, layout = layout, vertex.color = vertex_color, vertex.size = vertex_size)
+}
+```
+
+```{r bod2, echo = FALSE, results = "hide"}
+g <- get_bodini_graph_appendix()
+
+# Complete graph
+p_bodiniappen_all <- ~{
+  lg <- layout_as_tree(g, root = "R")
+  lg[, 2] <- -lg[, 2]
+  plot(g, layout = lg, vertex.color = vertex_color, vertex.size = vertex_size)
+}
+
+# Only functional links
+dtree <- dominator_tree(g, root = "R")
+p_bodiniappen_functional <- ~{
+  lg <- layout_as_tree(dtree$domtree, root = "R")
+  lg[, 2] <- -lg[, 2]
+  plot(
+    dtree$domtree,
+    layout = lg,
+    vertex.color = vertex_color,
+    vertex.size = vertex_size
+  )
+}
+
+p_bodini <- plot_grid(
+  ggdraw(p_bodinifig1_all), ggdraw(p_bodinifig1_functional),
+  ggdraw(p_bodiniappen_all), ggdraw(p_bodiniappen_functional),
+  labels = "auto"
+)
+ggsave_multiple(
+  paste0("p_bodini", c(".png", ".pdf")),
+  plot = p_bodini,
+  path = here::here("figures"),
+  scale = 2.6,
+  units = c("mm"),
+  width = 80,
+  height = 80 * 1.5)
+```
+
+```{r all1, echo = FALSE, results = "hide"}
+allesinafig1 <- get_allesina_graph(diag = FALSE)
+
+p_allesinafig1_all <- ~{
+  lg <- layout_as_tree(allesinafig1, root = "0")
+  lg[, 2] <- -lg[, 2]
+  plot(allesinafig1, layout = lg, vertex.color = vertex_color, vertex.size = vertex_size)
+}
+
+# Only functional links
+allesinafig1_dtree <- dominator_tree(allesinafig1, root = "0")
+p_allesinafig1_functional <- ~{
+  layout <- layout_as_tree(allesinafig1_dtree$domtree, root = "0")
+  layout[, 2] <- -layout[, 2]
+  plot(
+    allesinafig1_dtree$domtree,
+    layout = layout,
+    vertex.color = vertex_color,
+    vertex.size = vertex_size
+  )
+}
+
+p_examples <- plot_grid(
+  ggdraw(p_bodinifig1_all), ggdraw(p_bodinifig1_functional),
+  ggdraw(p_bodiniappen_all), ggdraw(p_bodiniappen_functional),
+  ggdraw(p_allesinafig1_all), ggdraw(p_allesinafig1_functional),
+  nrow = 3,
+  labels = "auto"
+)
+ggsave_multiple(
+  paste0("p_examples", c(".png", ".pdf")),
+  plot = p_examples,
+  path = here::here("figures"),
+  scale = 4.0,
+  units = c("mm"),
+  width = 80,
+  height = 80 * 1.2)
+```
+
+(ref:example-cap) Reproduced examples of categorising functional links in
+food webs using `igraph::dominator_tree()` R function. Left columns (a, c, e)
+displays the complete food-web while right column displays food-web with the
+functional links only (b, d, f). (a,b): reproduction of Fig. 1 of
+@bodini_using_2009, (c, d): reproduction of appendix figures of @bodini_using_2009,
+(e, f): reproduction of fig. 1 of @allesina_functional_2009. Note that (e, f) is
+a bit different from the original, as noted by the authors, they could have
+removed further redundant links (i.e. $2 \to 5$, or $3 \to 5$).
+
+```{r examples, fig.cap = "(ref:example-cap)", out.height = "80%"}
+knitr::include_graphics(here::here("figures", "p_examples.png"))
+```
+
+```{r}
+examples <- list(
+  bodiniappendix = g,
+  bodinifig1 = bodinifig1,
+  allesinafig1 = allesinafig1
+)
+redundancy_examples <- map2_dfr(
+  examples,
+  list(bodiniappendix = "R", bodinifig1 = "root", allesinafig1 = "0"),
+  ~compute_redundancy(.x, root = .y), .id = "reference")
+```
+
+```{r}
+paper_replacement <- c(
+  bodinifig1 = "Bodini et al. (2009) Fig. 1",
+  bodiniappendix = "Bodini et al. (2009) Supp material 1",
+  allesinafig1 = "Allesina et al. (2009) Fig. 1"
+)
+
+redundancy_var_replacement <- function() {
+  c(
+    reference = "References",
+    functional_links = "Nb functional links",
+    redundant_links = "Nb redundant links",
+    total_links = "Nb links",
+    prop_functional_links = "Prop. functional links",
+    prop_redundant_links = "Prop. redundant links"
+  )
+}
+
+redundancy_examples %>%
+  select(reference, total_links,
+    functional_links, redundant_links,
+    prop_functional_links, prop_redundant_links
+  ) %>%
+  mutate(reference = paper_replacement[reference]) %>%
+  rename_with(~redundancy_var_replacement()[.x]) %>%
+  kable(
+    digits = 2,
+    row.names = FALSE,
+    label = "redun",
+    booktabs = T,
+    caption = "Computation of the number (Nb) of functional, redundant links, and
+    their proportion (Prop.) from previous published food-webs.",
+    ) %>%
+  collapse_rows(columns = c(1), valign = "top") %>%
+  kable_styling(latex_options = "scale_down")
+```
 

### 2025-02-07 paper/manuscript.Rmd
Minor edits: sent to Loubna & Willem for review

@@
 link-citations: true
-#csl: ecology-letters.csl
 #https://pkgs.rstudio.com/rticles/articles/examples.html
@@
 structure influence coexistence [@chesson_interaction_2008], ecosystem
-productivity [@thebault_food web_2003; @wang_biodiversity_2018], temporal
+productivity [@thebault_food-web_2003; @wang_biodiversity_2018], temporal
 stability [@danet_species_2021; @danet_response_2024;
@@
 of species richness and primary productivity using a bioenergetic model
-[@brose_allometric_2006; @lajaaiti_ecologicalnetworksdynamicsjl_2025]. These
+[@brose_allometric_2006; @lajaaiti_ecologicalnetworksdynamicsjl_nodate]. These
 simulations allowed us to evaluate whether theoretical predictions align with
@@
 great heterogeneity in the temporal trends at the site level (community biomass:
-from `r grbmn`% to +`r grbmx`% per decade, species richness: `r grrhn` to +`r
-grrhx`%, average trophic level: `r grtln` to +`r grtlx`, connectance: `r grctn`
-to +`r grctx`, redundancy: `r grln` to +`r grlx`, Fig. S1) which was effectively
-captured by the hierarchical model ( conditional R2 ranging from `r
-r2cond$log_bm_std` for community biomass to `r r2cond$log_rich_std` for species
-richness, Table S2).
+from `r grbmn`% to +`r grbmx`% per decade, species richness: `r grrhn` to
++`r grrhx`%, average trophic level: `r grtln` to +`r grtlx`, connectance:
+`r grctn` to +`r grctx`, redundancy: `r grln` to +`r grlx`, Fig. S1) which was
+effectively captured by the hierarchical model ( conditional R2 ranging from
+`r r2cond$log_bm_std` for community biomass to `r r2cond$log_rich_std` for
+species richness, Table S2).
 
@@
 connectance between herbivores and plants can either enhance or reduce
-productivity [@thebault_food web_2003; @poisot_trophic_2013; @nie_will_2023],
+productivity [@thebault_food-web_2003; @poisot_trophic_2013; @nie_will_2023],
 greater connectance among carnivores generally boosts productivity by reducing
@@
 drivers of biodiversity changes, including habitat degradation
-[@danet_past_2024] and climate change [@bonnaffe_warming_2024]. Ultimately, our
+[@danet_past_2024] and climate change [@bonnaffe_interaction_2024]. Ultimately, our
 work aims to bridge the gap between Biodiversity-Ecosystem Functioning and food
@@
 done using the Julia package `EcologicalNetworksDynamics.jl`
-[@lajaaiti_ecologicalnetworksdynamicsjl_2024]. Then, we computed the community
+[@lajaaiti_ecologicalnetworksdynamicsjl_nodate]. Then, we computed the community
 and food web metrics at the last timesteps and analyzed the data with the same

### 2025-02-19 paper/manuscript.Rmd
Incorporate Willem comments

@@
 
-Biodiversity changes are expected to profoundly impact ecosystem functioning and
-stability, yet empirical evidence remains limited. Bridging this gap requires
-aligning biodiversity trends with food web theory and Biodiversity-Ecosystem
-Functioning research, which provide strong predictions about the ecological
-consequences of biodiversity loss. Most insights rely on spatial comparisons of
-ecological communities, assuming they reflect temporal trends—a space-for-time
-substitution. Here, we analyze biodiversity and food web time series from over
-400 riverine fish communities across France (1995–2018) to evaluate how
-biodiversity trends reshape food web structure. We examine relationships among
-species richness, community biomass, and three key food web metrics:
-connectance, weighted average trophic level, and trophic pathway redundancy. We
-also test the space-for-time hypothesis using spatial gradients and a
-theoretical food web model. Structural equation models and robustness analyses
-reveal that declines in species richness strongly correlate with reduced
-community biomass, with top trophic-level species playing a disproportionate
-role in food web changes. Declining biomass leads to the loss of top trophic
-levels and decreased connectance, while species richness negatively correlates
-with connectance. Both biomass and species richness declines reduce trophic
-pathway redundancy, suggesting biodiversity loss undermines community robustness
-to future perturbations. Our findings align with food web theory and
-Biodiversity-Ecosystem Functioning research, support the validity of
-space-for-time approaches for basic food web metrics, and highlight the utility
-of food web metrics as indicators of ecosystem function and fragility.
+Biodiversity temporal changes are expected to profoundly impact ecosystem
+functioning and stability, yet large-scale empirical evidence remains limited. Bridging this
+gap requires aligning biodiversity temporal trends with food web theory and
+Biodiversity-Ecosystem Functioning research, which provide strong predictions
+about the ecological consequences of biodiversity loss. Most insights rely on
+spatial comparisons of ecological communities, assuming they reflect temporal
+trends—a space-for-time substitution. Here, we analyze biodiversity and food web
+time series from over 400 riverine fish communities across France (1995–2018) to
+evaluate how biodiversity temporal trends reshape food web structure. We examine
+relationships among species richness, community biomass, and three key food web
+metrics: connectance, weighted average trophic level, and trophic pathway
+redundancy. We also test the space-for-time hypothesis using spatial gradients
+and a theoretical food web model. Structural equation models and robustness
+analyses reveal that declines in species richness strongly correlate with
+reduced community biomass, with top trophic-level species playing a
+disproportionate role in food web changes. Declining biomass is associated with the loss
+of top trophic levels and decreased connectance, while species richness
+negatively correlates with connectance. Both biomass and species richness
+declines reduce trophic pathway redundancy, suggesting biodiversity loss
+undermines community robustness to future perturbations. Our findings align with
+food web theory and Biodiversity-Ecosystem Functioning research, support the
+validity of space-for-time approaches for basic food web metrics, and highlight
+the utility of food web metrics as indicators of ecosystem function and
+fragility.
 
@@
 changes over time relies on experimental and theoretical approaches. These
-approaches often depend on the critical assumption that spatial comparisons of
+approaches often rely on the critical assumption that spatial comparisons of
 ecological communities can serve as a proxy for temporal trends—a space-for-time
@@
 from our `r nb_st` fish communities with 10+ years of population dynamics
-spanning 1995-2018 over France (Fig. \@ref(fig:matmet)a-c). We implemented Bayesian hierarchical
-models to jointly estimate the temporal trends in these metrics. We found a
-great heterogeneity in the temporal trends at the site level (community biomass:
-from `r grbmn`% to +`r grbmx`% per decade, species richness: `r grrhn` to
-+`r grrhx`%, average trophic level: `r grtln` to +`r grtlx`, connectance:
-`r grctn` to +`r grctx`, redundancy: `r grln` to +`r grlx`, Fig. S1) which was
-effectively captured by the hierarchical model ( conditional R2 ranging from
-`r r2cond$log_bm_std` for community biomass to `r r2cond$log_rich_std` for
-species richness, Table S2).
+spanning 1995-2018 over France (Fig. \@ref(fig:matmet)a-c). We implemented
+Bayesian hierarchical models accounting for spatial variation at both
+hydrographic river basin and site levels to jointly estimate the temporal trends in these metrics. We found a
+great heterogeneity in the temporal trends at the site level
+(community biomass: from `r grbmn`% to +`r grbmx`% per decade, species richness:
+`r grrhn` to +`r grrhx`%, average trophic level: `r grtln` to +`r grtlx`,
+connectance: `r grctn` to +`r grctx`, redundancy: `r grln` to +`r grlx`, Fig.
+S1) which was effectively captured by the hierarchical model ( conditional R2
+ranging from `r r2cond$log_bm_std` for community biomass to `r
+r2cond$log_rich_std` for species richness, Table S2).
 
@@
 Thus, when communities experienced an increase, or decrease, in species
-richness, they also experienced a concomitant increase, or decrease, in
+richness, they also experienced a concomitant decrease, or increase, in
 connectance. In contrast, species richness temporal trends had no direct effects
@@
 direct and indirect positive effects ($r_\delta =$ `r rttps$red$r`). All
-together, it means that communities that have experienced species richness
+together, this means that communities that have experienced species richness
 declines over the last decades have decreased in average trophic level and
@@
 negative effect in total on connectance ($r_\delta =$ `r rttps$ct$r`, Fig.
-\@ref(fig:std)a). In contrast, species richness had no direct effects on in
+\@ref(fig:std)a). In contrast, species richness had no direct effects on
 average trophic level ($r_\delta =$ `r rdtps$tlvl$r`, Fig. \@ref(fig:sem)g), a
@@
 temporal association between community biomass and average trophic level.
+Importantly, this finding highlights that the relationship between
+biodiversity—biomass and species richness—and food web
+characteristics—connectance, trophic level, and redundancy—is not purely
+structural but also functional. Indeed, predictions of food web structure are
+most accurate when both structural (species richness) and functional (biomass)
+metrics are considered.
 
@@
 @danet_species_2021]. Then the biomass of each species and community
-were obtained by summing the body mass of individuals. Finally, the biomass was
+were obtained by summing the body mass of individuals. This resulted in a
+biomass score for the whole community of each site. Finally, the biomass was
 reported to the sampled surface (in $m^2$) to account for sampling effort.
@@
 a trophic species is a group of individuals of the same species and size class
-that are expected to share the same preys and predators because trophic
+that are expected to share the same prey and predators because trophic
 interactions are largely determined by predator-prey size ratio
@@
 functional links using the dominator tree approach [@allesina_functional_2009].
-A species $i$ is a dominator of species $j$ if $i$ mediates the connection $j$
-to basal resources such as the extinction of $i$ remove the connection of $j$ to
-basal resources. It is then to identify the set of trophic links that are
+A species $i$ is a dominator of species $j$ if $i$ mediates the connection of $j$
+to basal resources such that the extinction of $i$ removes the connection of $j$ to
+basal resources. It is then used to identify the set of trophic links that are
 essential to connect species to basal resources, i.e. functional links, and the
@@
 We modeled the temporal trends of food web structure at each site ($Y_i$) using
-linear hierarchical model. Time was considered as the number of years since the
-first sampling ($t = 0$) at each site. We accounted for the spatial structure of
-the data by adding random intercepts ($a$) and slopes ($b$) for the
-basin ($a_n$, $b_n$) and site ($a_{i|n}$, $b_{i|n}$) identity, site effects
-being nested in the basin one.
+linear hierarchical model which accounts for the hierarchical spatial structure
+of the data, i.e. the sites nested in hydrographic basins. Time was considered as the number of years since the
+first sampling ($t = 0$) at each site. $\alpha$ is the intercept and $\beta$ the
+slope estimating the temporal trends. The intercept and the slope parameters
+have a fixed ($\alpha_0$, $\mu$) part and a random part. We accounted for the
+spatial structure of the data by adding random intercepts ($a$) and slopes ($b$)
+for the basin ($a_n$, $b_n$) and site ($a_{i|n}$, $b_{i|n}$) identity, site
+effects being nested in the basin one.
 
@@
 Approximation) Bayesian inference with default uninformative priors
-[@rue_bayesian_2017]. The prior distributions for the fixed intercept and slope were
+[@rue_bayesian_2017]. The prior distributions for the fixed intercept ($\alpha_0$) and slope ($\mu$) were
 modeled as a flat normal distribution with a mean of zero ($\mathcal{N}(0,\, 1000)$).
@@
 The performance of the model was assessed visually by plotting the fitted versus
-the observed values (Fig. S5). We also visually inspected the Posterior
-Integral Transform (PIT) and Conditional Predictive Ordinate (CPO) to assess the
-quality of the model fit. We also computed the marginal ($R^2_m$) and conditional
+the observed values (Fig. S5). We also computed the marginal ($R^2_m$) and conditional
 ($R^2_c$) R-squared of the models following previous formulations
@@
 We extracted the temporal trends at each site from the hierarchical model
-using mean BLUP values (Best Linear Unbiaised Prediction), then multiplied
+using mean BLUP values (Best Linear Unbiased Prediction), then multiplied
 by 10 to get temporal trends by decade. For community biomass and species
@@
 of the estimated trends, i.e. the estimated slopes for the response and the
-explicative variables ($w_j = 1 / \sum{e_j}$, $w_j$ being the weight, and
-$s_{e_j}$ the standard deviation on the temporal trends of the variables).
+explicative variables ($w_j = 1 / \sum{s_j}$, $w_j$ being the weight, and
+$s_j$ the standard deviation on the temporal trends of the variables).
 
@@
 (BCa), which are adjusted for the asymmetric distribution of resampling. The marginal
-and conditional $R^2$ associated to the linear models of the SEMs were computed
+and conditional $R^2$ associated with the linear models of the SEMs were computed
 with the Nagelkerke method [@lefcheck_piecewisesem_2016, Table S4].
@@
 extinction sequences. For each simulation, we removed fish species/nodes that
-lost all their preys. We then computed the connectance, the average and the
-maximum trophic level after each extinction.
+lost all their prey and iterate this removal until all remaining species have at
+least one prey. We then computed the connectance, the average and the maximum
+trophic level after each extinction.
 
@@
 simulating complex communities because its parameterization depends mainly on
-species bodymasses. We first generated `r nfw` food webs varying in species
+species body masses. We first generated `r nfw` food webs varying in species
 richness (range: `r s_range["min"]`-`r s_range["max"]`)
@@
 model algorithm, which reproduces food web topology typically found in empirical
-food webs [@williams_simple_2000]. We set species bodymasses ($M_i$) using a predator-prey
+food webs [@williams_simple_2000]. We set species body masses ($M_i$) using a predator-prey
 mass ratio of 100 ($Z$) [@brose_allometric_2006; @brose_predator_2019], such as $M_i =
@@
 metabolic rates of the species ($x_i$) were then derived from allometric
-relationships between metabolism and bodymass empirically estimated
-[@brose_allometric_2006], such as $x_i = -0.314M_i^{-0.25}$.
+relationships between metabolism and body mass empirically estimated
+[@brose_allometric_2006], such as $x_i = 0.88M_i^{-0.25}$.
 
@@
 The primary producer biomass increase with a growth rate ($r_i$) of 1 and a
-logistic growth (eq. \@ref(eq:growth)), growth being limited by intraspecific
+logistic growth ($G_i$, eq. \@ref(eq:growth)), growth being limited by intraspecific
 ($\alpha_{ii}$, set to 1), interspecific ($\alpha_{ij}$, set to 0.5) competition,
 and carrying capacity ($K_i$, varying in the simulations). Primary producers
-loses biomass by being eaten by consumers at a rate that depend on consumer
-metabolic rates ($x_j$), attack rates ($y_j$, set to 8 @delmas_analysing_2019),
-a functional response ($F_{ji}$), and assimilation efficiency ($e_{ij}$, set to
-0.45 for herbivores and 0.85 for carnivores, @delmas_analysing_2019).
+lose biomass by being eaten by consumers at a rate that depend on consumer
+metabolic rates ($x_j$), attack rates ($y_j$, set to 4
+@lajaaiti_ecologicalnetworksdynamicsjl_nodate), a functional response
+($F_{ji}$), and assimilation efficiency which accounts for the fact that
+consumers assimilate better the primary producer biomass than the consumer ones
+($e_{ij}$, set to 0.45 for herbivores and 0.85 for carnivores,
+@lajaaiti_ecologicalnetworksdynamicsjl_nodate).
 
@@
 Consumers gain biomass by eating other species and lose biomass by being
-consumed and by metabolic loses ($x_i$, eq. \@ref(eq:cons)). The functional
+consumed and by metabolic losses ($x_i$, eq. \@ref(eq:cons)). The functional
 response (eq. \@ref(eq:holling)) of consumer feeding depends on the preference

### 2025-03-28 paper/appendix.Rmd
Begins to take final Colin's comments

@@
 title: "Biodiversity temporal trends are reshaping food web structure and redundancy in riverine ecosystems"
-subtitle: "Alain Danet (a,b), Loubna El Madouri (a,c), Andrew P. Beckerman (b),
-Maud Mouchet (a), Colin Fontaine (a) and Elisa Thébault (d)"
+subtitle: "Alain Danet , Loubna El Madouri, Willem Bonnaffé, Andrew P. Beckerman,
+Maud Mouchet, Colin Fontaine and Elisa Thébault"
 date: Supplementary Material
@@
 
-# Comparison of analysis in space and time
-
-We further assessed the consistency of the reported associations among temporal
-trends by implementing two additional analyses. We first tested if the
-associations among the temporal trends within sites was holding across sites,
-i.e. using spatial variations in food web structure rather than temporal changes
-over time (space-for-time hypothesis). Second, we performed theoretical
-simulations with a bioenergetic food web model to cross-reference our site and
-species specific empirical data on riverine fish with a more generalized
-representation of food web dynamics known to represent accurate relationships
-among our focal variables [@brose_allometric_2006; @eschenbrenner_diversity_2023;
-@danet_response_2024]. With those additional empirical and theoretical data, we
-assessed additional SEM models with the same structure as in Section 4.2.
-
-As in the temporal analysis, species richness had a positive effect on community
-biomass both in empirical data and in theoretical simulations (resp. $r_\delta
-=$ `r rdsp$bm$r` and `r rdm$bm$r`, Fig. 3a and S3). In both
-empirical data and theoretical simulations, community biomass had a positive
-effect on average trophic level (resp. $r_\delta =$ `r rdsp$tlvl$bm` and
-`r rdm$tlvl$bm`), and redundancy (resp. $r_\delta =$ `r rdsp$red$bm` and
-`r rdm$red$bm`), as in temporal analysis. We found weak evidence of a positive
-effect of spatial variation in community biomass on connectance in empirical
-data ($r_\delta =$ `r rdsp$ct$bm`) but strong evidence in theoretical
-simulations ($r_\delta =$ `r rdm$ct$bm`, Fig. 3a).
-
-The effects of spatial variations in species richness on food web structure
-mostly aligned with those from the temporal trend analysis, except for average
-trophic level. We found a direct negative effect of species richness on
-connectance both using data and model simulations (resp. $r_\delta =$
-`r rdsp$ct$r` and `r rdm$ct$r`, Fig. 3a), on average trophic level
-(resp. $r_\delta =$ `r rdsp$tlvl$r` and `r rdm$tlvl$r`), but a direct positive
-effect on redundancy (resp. $r_\delta =$ `r rdsp$red$r` and `r rdm$red$r`).
-Species richness had an indirect positive effect of species richness through
-community biomass, which added up to strong total negative effects on
-connectance in empirical data and simulations (resp. $r_\delta =$
-`r rtsp$ct$r` and `r rtm$ct$r`) and positive on redundancy (resp. $r_\delta =$
-`r rtsp$red$r` and `r rtm$red$r`). We found that
-species richness had a total positive effect on average trophic level in
-bioenergetic model, in agreement with temporal trends (resp. $r_\delta =$ `r rtm$tlvl$r`),
-but a total negative effect in spatial variations (resp. $r_\delta =$ `r rtsp$tlvl$r`).
-
-# Disantengling functional and redundant links
+# Disentangling functional and redundant trophic pathways
 
@@
 
+## References {-}
+
+<div id="refs"></div>
+
+\pagebreak
+
+# Supplementary results: comparison of analysis in space and time
+
+We further assessed the consistency of the reported associations among temporal
+trends by implementing two additional analyses. We first tested if the
+associations among the temporal trends within sites was holding across sites,
+i.e. using spatial variations in food web structure rather than temporal changes
+over time (space-for-time hypothesis). Second, we performed theoretical
+simulations with a bioenergetic food web model to cross-reference our site and
+species specific empirical data on riverine fish with a more generalized
+representation of food web dynamics known to represent accurate relationships
+among our focal variables. With those additional empirical and theoretical data, we
+assessed additional SEM models with the same structure as in Section 4.2 (see
+main text, Fig. 2a).
+
+As in the temporal analysis, species richness had a positive effect on community
+biomass both in empirical data and in theoretical simulations (resp. $r_\delta
+=$ `r rdsp$bm$r` and `r rdm$bm$r`, Fig. 3a and S3). In both
+empirical data and theoretical simulations, community biomass had a positive
+effect on average trophic level (resp. $r_\delta =$ `r rdsp$tlvl$bm` and
+`r rdm$tlvl$bm`), and redundancy (resp. $r_\delta =$ `r rdsp$red$bm` and
+`r rdm$red$bm`), as in temporal analysis. We found weak evidence of a positive
+effect of spatial variation in community biomass on connectance in empirical
+data ($r_\delta =$ `r rdsp$ct$bm`) but strong evidence in theoretical
+simulations ($r_\delta =$ `r rdm$ct$bm`, Fig. 3a).
+
+The effects of spatial variations in species richness on food web structure
+mostly aligned with those from the temporal trend analysis, except for average
+trophic level. We found a direct negative effect of species richness on
+connectance both using data and model simulations (resp. $r_\delta =$
+`r rdsp$ct$r` and `r rdm$ct$r`, Fig. 3a), on average trophic level
+(resp. $r_\delta =$ `r rdsp$tlvl$r` and `r rdm$tlvl$r`), but a direct positive
+effect on redundancy (resp. $r_\delta =$ `r rdsp$red$r` and `r rdm$red$r`).
+Species richness had an indirect positive effect of species richness through
+community biomass, which added up to strong total negative effects on
+connectance in empirical data and simulations (resp. $r_\delta =$
+`r rtsp$ct$r` and `r rtm$ct$r`) and positive on redundancy (resp. $r_\delta =$
+`r rtsp$red$r` and `r rtm$red$r`). We found that
+species richness had a total positive effect on average trophic level in
+bioenergetic model, in agreement with temporal trends (resp. $r_\delta =$ `r rtm$tlvl$r`),
+but a total negative effect in spatial variations (resp. $r_\delta =$ `r rtsp$tlvl$r`).
+
 # Supplementary figures {-}
@@
   structure by site estimated from the Bayesian models using Best Linear
-  Unbiaised Prediction (BLUP). Species richness and biomass temporal trends are
+  Unbiased Prediction (BLUP). Species richness and biomass temporal trends are
   reported in percentage change per decade. Dashed red line and solid black line
@@
 rand_sim_cap <- paste0(
-  "Simulations of (b) nodes extinctions in the metaweb according to three
+  "Simulations of trophic species extinctions in the metaweb according to three
   scenarios: random extinction sequence (grey dots), extinction sequence by
@@
   trophic level. The black line represents the average prediction of a GAM
-  linear model for the 50 random extinction sequences."
+  linear model for the 50 random extinction sequences. Please note that the
+  results are qualitatively similar that when considering species (see Fig. 3b,
+  main text) instead of trophic species."
 )
@@
 
-```{r ext, fig.cap=rand_sim_cap}
+```{r ext, fig.cap=rand_sim_cap, out.width = "100%"}
 tar_load(figSext)

### 2025-03-28 paper/manuscript.Rmd
Begins to take final Colin's comments

@@
 title: "Biodiversity temporal trends are reshaping food web structure and redundancy in riverine ecosystems"
-subtitle: "Alain Danet (a,b), Loubna El Madouri (a,c), Andrew P. Beckerman (b),
-Maud Mouchet (a), Colin Fontaine (a) and Elisa Thébault (d)"
+subtitle: "Alain Danet (a,b), Loubna El Madouri (a,c), Willem Bonnaffé (d), Andrew P. Beckerman (b),
+Maud Mouchet (a), Colin Fontaine (a) and Elisa Thébault (e)"
 date: "Research report"
 output:
+  bookdown::pdf_document2:
+    fig_caption: true
+    keep_tex: true
+    toc: false
   officedown::rdocx_document:
@@
 
-(d) Sorbonne Université, CNRS, IRD, INRAE, Université Paris Est Créteil, 15
+(d) Department of Biology, University of Oxford, Oxford, United Kingdom
+
+(e) Sorbonne Université, CNRS, IRD, INRAE, Université Paris Est Créteil, 15
 Institute of Ecology and Environmental Sciences of Paris (iEES-Paris), Paris,
@@
 
-- Keywords: food web structure, biodiversity changes, redundancy, biodiversity &
-  ecosystem functioning
-
-# Abstract (229 / 250 words max)
+- Keywords: food web, biodiversity changes, redundancy, ecosystem functioning,
+  vulnerability
+
+# Abstract {-}
 
 Biodiversity temporal changes are expected to profoundly impact ecosystem
-functioning and stability, yet large-scale empirical evidence remains limited. Bridging this
-gap requires aligning biodiversity temporal trends with food web theory and
-Biodiversity-Ecosystem Functioning research, which provide strong predictions
-about the ecological consequences of biodiversity loss. Most insights rely on
-spatial comparisons of ecological communities, assuming they reflect temporal
-trends—a space-for-time substitution. Here, we analyze biodiversity and food web
-time series from over 400 riverine fish communities across France (1995–2018) to
-evaluate how biodiversity temporal trends reshape food web structure. We examine
-relationships among species richness, community biomass, and three key food web
-metrics: connectance, weighted average trophic level, and trophic pathway
-redundancy. We also test the space-for-time hypothesis using spatial gradients
-and a theoretical food web model. Structural equation models and robustness
-analyses reveal that declines in species richness strongly correlate with
-reduced community biomass, with top trophic-level species playing a
-disproportionate role in food web changes. Declining biomass is associated with the loss
-of top trophic levels and decreased connectance, while species richness
-negatively correlates with connectance. Both biomass and species richness
-declines reduce trophic pathway redundancy, suggesting biodiversity loss
-undermines community robustness to future perturbations. Our findings align with
-food web theory and Biodiversity-Ecosystem Functioning research, support the
-validity of space-for-time approaches for basic food web metrics, and highlight
-the utility of food web metrics as indicators of ecosystem function and
-fragility.
-
-# Significance (118 / 120 words max)
+functioning and stability, yet large-scale empirical evidence remains limited.
+Bridging this gap requires aligning biodiversity temporal trends with food web
+theory and Biodiversity-Ecosystem Functioning research, which provide strong
+predictions about the ecological consequences of biodiversity loss. Most
+insights rely on spatial comparisons of ecological communities, assuming they
+reflect temporal trends—a space-for-time substitution. Here, we analyze
+biodiversity and food web time series from over 400 riverine fish communities
+across France (1995–2018) to evaluate how biodiversity temporal trends reshape
+food web structure and community functioning. We examine relationships among
+species richness, community biomass, and three key food web metrics:
+connectance, weighted average trophic level, and trophic pathway redundancy. We
+also test the space-for-time hypothesis using spatial gradients and a
+theoretical food web model. Structural equation models and robustness analyses
+reveal that declines in species richness strongly correlate with reduced
+community biomass, with top trophic-level species playing a disproportionate
+role in food web changes. Declining biomass is associated with the loss of top
+trophic levels and decreased connectance, while temporal changes of species
+richness negatively correlates with those of connectance. Both biomass and
+species richness declines reduce trophic pathway redundancy, suggesting
+biodiversity loss undermines community robustness to future perturbations. Our
+findings align with food web theory and Biodiversity-Ecosystem Functioning
+research, support the validity of space-for-time approaches for basic food web
+metrics, and highlight the relevance of food web metrics as indicators of
+ecosystem function and fragility.
+
+# Significance {-}
 
@@
 for predicting and mitigating human impacts on ecosystems. This study provides
-comprehensive evidence on how biodiversity changes are reshaping food web structure using
-an extensive dataset of riverine fish communities. We demonstrate that changes
-in species richness and community biomass consistently alter trophic levels,
-connectance, and the redundancy of feeding relationships. Our findings show how
-energetic constraints and biodiversity-ecosystem functioning mechanisms jointly
-shape food web assembly and disassembly. Importantly, we show that declining
-biodiversity reduces the redundancy of trophic pathways, potentially making
-communities more vulnerable to future perturbations. These results suggest that
-food web structure metrics could serve as valuable indicators for monitoring
-ecosystem health and evaluating conservation strategies.
-
-# Introduction (487 words)
+comprehensive evidence on how biodiversity changes are reshaping food web
+structure using an extensive dataset of riverine fish communities. We
+demonstrate that temporal changes in species richness and community biomass
+consistently correlate with altered trophic levels, connectance, and the
+redundancy of feeding relationships, suggesting energetic constraints and
+biodiversity-ecosystem functioning mechanisms jointly shape food web assembly
+and disassembly. Importantly, we show that declining biodiversity reduces the
+redundancy of trophic pathways, potentially making communities more vulnerable
+to future perturbations. These results suggest that food web structure metrics
+could serve as valuable indicators for monitoring ecosystem health and
+evaluating conservation strategies.
+
+# Introduction
 
@@
 @thebault_food-web_2003; @schneider_animal_2016; @dunne_network_2002;
-@sole_complexity_2001; @allesina_functional_2009; @montoya_press_2009; @sanders_trophic_2018]. However,
-research on biodiversity changes remains largely disconnected from studies
-examining their ecological impacts, primarily due to a lack of simultaneous
-temporal data on biodiversity and food web dynamics [@danet_species_2021]. As a
-result, much of our understanding of the ecological consequences of biodiversity
-changes over time relies on experimental and theoretical approaches. These
-approaches often rely on the critical assumption that spatial comparisons of
-ecological communities can serve as a proxy for temporal trends—a space-for-time
-substitution—when direct temporal data are scarce. To advance our understanding
-of the ecological consequences of biodiversity changes, it is essential to
-investigate how these changes are reshaping food web structure in natural
-settings.
+@sole_complexity_2001; @allesina_functional_2009; @montoya_press_2009;
+@sanders_trophic_2018]. However, research on biodiversity changes remains
+largely disconnected from studies examining their ecological impacts, primarily
+due to a lack of simultaneous temporal data on biodiversity and food web
+dynamics [@danet_species_2021]. As a result, much of our understanding of the
+ecological consequences of biodiversity changes over time relies on experimental
+and theoretical approaches [@loreau_biodiversity_2001; @loreau_ecological_2022;
+@thebault_food-web_2003; @dunne_network_2002; @sole_complexity_2001;
+@allesina_functional_2009]. These approaches often rely on the critical
+assumption that spatial comparisons of ecological communities can serve as a
+proxy for temporal trends—a space-for-time substitution—when direct temporal
+data are scarce [@damgaard_a_2019]. To advance our understanding of the
+ecological consequences of biodiversity changes, it is essential to investigate
+how these changes are reshaping food web structure in natural settings.
 
@@
 yearly food web structures [@danet_species_2021; @bonnaffe_comparison_2021], we
-investigate how temporal biodiversity trends reshape food web metrics such as
-connectance, weighted average trophic level, and the proportion of redundant
-trophic links (hereafter “redundancy”). Linking these findings to established
-theories of Biodiversity-Ecosystem Functioning and food web dynamics, we address
-three key objectives: (i) documenting how temporal biodiversity trends reshape
-food web structure, (ii) connecting these changes to ecosystem functioning and
-food web theories, and (iii) assessing the validity of the space-for-time
-substitution assumption in the context of biodiversity and food web structure
-changes.
+address three key objectives: (i) documenting how temporal biodiversity trends
+reshape food web structure, (ii) connecting these changes to established
+theories of food webs and Biodiversity-Ecosystem functioning relationships, and
+(iii) assessing the validity of the space-for-time substitution assumption in
+the context of biodiversity and food web structure changes.
 
@@
 @bodini_using_2009; @montoya_press_2009; @sanders_trophic_2018]. For instance,
-keystone predators can regulate dominant competitors, preventing competitive
-exclusion and maintaining species richness [@heithaus_predicting_2008;
-@johnson_rarity_2007; @estes_trophic_2011]. Similarly, food webs with higher
-trophic levels are associated with greater ecosystem productivity
-[@wang_biodiversity_2018; @schneider_animal_2016; @wang_biodiversity_2018;
+keystone predators can regulate dominant competitors, preventing
+competitive exclusion and maintaining species richness [@heithaus_predicting_2008;
+@johnson_rarity_2007; @estes_trophic_2011]. Similarly, food
+webs with higher trophic levels are associated with greater ecosystem
+productivity [@wang_biodiversity_2018; @schneider_animal_2016;
 @wang_intraguild_2019; @nie_will_2023] and community stability
@@
 perturbations [@dunne_network_2002; @allesina_who_2004; @bodini_using_2009;
-@allesina_functional_2009; @sanders_trophic_2018]. Understanding how
-biodiversity changes reshape ecological networks is therefore essential for
-quantifying and mitigating anthropogenic impacts on ecosystems.
+@allesina_functional_2009; @sanders_trophic_2018]. Understanding how biodiversity changes
+reshape ecological networks is therefore essential for quantifying and
+mitigating anthropogenic impacts on ecosystems.
 
@@
 against perturbations and environmental changes [@yachi_biodiversity_1999;
-@loreau_ecological_2022]. Finally, biodiversity-ecosystem functioning theory
-suggests that species richness promotes community biomass through niche
-complementarity [@loreau_biodiversity_2001]. In food webs, the presence of
-higher trophic levels reduces niche overlap among producers, further boosting
-productivity and biomass [@schneider_animal_2016; @wang_biodiversity_2018;
-@wang_intraguild_2019; @nie_will_2023]. Together, these mechanisms highlight how
-biodiversity changes can alter trophic link distribution, robustness, and
-ecosystem functioning.
-
-To achieve these objectives, we analyzed temporal trends in species richness,
-biomass, and food web structure across `r nb_op` community samplings (Fig.
-\@ref(fig:matmet)a-c, Table S1). Using structural equation modeling (SEM), we
-inferred the relative effects of biomass and species richness trends on food web
-metrics, as well as the effect of species richness on biomass (Fig.
-\@ref(fig:matmet)d). We also conducted a robustness analysis on the meta-food
-web (comprising all trophic species and their interactions) to identify species
-extinction scenarios that could explain observed variations in food web
-structure. To test the space-for-time hypothesis, we compared temporal findings
-with spatial gradients using two approaches: (i) replicating our temporal
-analysis using median biodiversity and food web metrics across sites (Fig.
-\@ref(fig:matmet)c & e), and (ii) simulating food web dynamics across gradients
-of species richness and primary productivity using a bioenergetic model
-[@brose_allometric_2006; @lajaaiti_ecologicalnetworksdynamicsjl_nodate]. These
-simulations allowed us to evaluate whether theoretical predictions align with
-our empirical data, which are limited to fish biodiversity.
-
-```{r}
-fig_mat_cap <- paste0("Methodological Approach: (a) We analyzed ", nb_st, "
-  stream fish communities in France, each monitored for at least 10 years. (b)
-  For each site and sampling event, we reconstructed food webs using a metaweb
-  based on ontogenetic diet information and predator-prey body size ratios. (c)
-  We computed temporal trends and median values for community biomass, species
-  richness, connectance, average trophic level, and redundancy at each site. (d)
-  We then assessed relationships among these food web descriptors over time and
-  (e) across spatial gradients.")
-```
-
-```{r matmet, fig.cap=fig_mat_cap, out.width="100%"}
+@loreau_ecological_2022; @danet_response_2024]. Finally, biodiversity-ecosystem
+functioning theory suggests that species richness promotes community biomass
+through niche complementarity [@loreau_biodiversity_2001]. In food webs, the
+presence of higher trophic levels reduces niche overlap among producers, further
+boosting productivity and biomass [@schneider_animal_2016;
+@wang_biodiversity_2018; @wang_intraguild_2019; @nie_will_2023]. Together, these
+mechanisms highlight how biodiversity changes can alter trophic link
+distribution, robustness, and ecosystem functioning.
+
+To investigate how temporal biodiversity changes correlate with changes in food
+webs, we analyzed temporal trends in species richness, biomass, and food web
+structure across `r nb_op` sampling events from `r nb_st` fish communities (Fig.
+\@ref(fig:matmet)a-c, Table S2). Using structural equation modeling (SEM), we
+inferred the relative effects of biomass and species richness temporal trends on
+trends of food web metrics, as well as the effect of species richness trends on
+biomass trends (Fig. \@ref(fig:matmet)d). Following a classical approach of
+network analysis [@dunne_network_2002], we also analyzed the robustness to
+species extinction of the meta-food web (comprising all trophic species and
+their interactions) to identify species extinction scenarios that could explain
+observed variations in food web structure. To test the space-for-time
+hypothesis, we compared temporal findings with spatial gradients using two
+approaches: (i) replicating our temporal analysis using median biodiversity and
+food web metrics across sites to remove temporal trends (Fig. \@ref(fig:matmet)c
+& e), and (ii) simulating food web dynamics across gradients of species richness
+and primary productivity using a bioenergetic model [@brose_allometric_2006;
+@lajaaiti_ecologicalnetworksdynamicsjl_nodate]. These simulations allowed us to
+evaluate whether theoretical predictions align with our empirical data, which
+are limited to fish biodiversity.
+
+(ref:fig-met-cap) Methodological Approach: (a) We analyzed `r nb_st` stream fish
+communities in France, each monitored for at least 10 years. (b) For each site
+and sampling event, we reconstructed food webs using a metaweb based on
+ontogenetic diet information and predator-prey body size ratios. (c) We computed
+temporal trends and median values for community biomass, species richness,
+connectance, average trophic level, and redundancy at each site. (d) We then
+assessed relationships among these food web descriptors over time and (e) across
+spatial gradients.
+
+```{r matmet, fig.cap="(fig-met-cap)", out.width="100%"}
 knitr::include_graphics(get_mypath("figures", "mat_met.png"))
@@
 
-Our food web reconstruction delivered `r nb_op` annual estimates of species
-richness, biomass, connectance, weighted average trophic level, and the
-proportion of redundant trophic links (hereafter “redundancy”, see Appendix B)
-from our `r nb_st` fish communities with 10+ years of population dynamics
-spanning 1995-2018 over France (Fig. \@ref(fig:matmet)a-c). We implemented
-Bayesian hierarchical models accounting for spatial variation at both
-hydrographic river basin and site levels to jointly estimate the temporal trends in these metrics. We found a
-great heterogeneity in the temporal trends at the site level
-(community biomass: from `r grbmn`% to +`r grbmx`% per decade, species richness:
-`r grrhn` to +`r grrhx`%, average trophic level: `r grtln` to +`r grtlx`,
-connectance: `r grctn` to +`r grctx`, redundancy: `r grln` to +`r grlx`, Fig.
-S1) which was effectively captured by the hierarchical model ( conditional R2
-ranging from `r r2cond$log_bm_std` for community biomass to `r
-r2cond$log_rich_std` for species richness, Table S2).
-
-```{r}
-sem_cap <- "(a) Structural equation models linking the temporal trends of
+Our food web reconstruction delivered `r nb_op` annual estimates of species richness,
+biomass, connectance, weighted average trophic level, and proportion of
+redundant trophic links (hereafter “redundancy”, see Appendix 1,
+Fig. S1, Table S2) from the `r nb_st`
+sampling sites with 10+ years of community dynamics (Fig. \@ref(fig:matmet)a-c). We used
+ontogenic food diet data at the species level and individual fish body size to
+reconstruct trophic species food webs, i.e. at the size class species level (See
+Methods). We implemented Bayesian hierarchical models accounting for spatial
+variation at both hydrographic river basin and site levels to jointly estimate
+the temporal trends in these metrics (see Methods). We found a great
+heterogeneity in the temporal trends at the site level (community biomass: from
+`r grbmn`% to +`r grbmx`% per decade, species richness: `r grrhn` to
++`r grrhx`%, average trophic level: `r grtln` to +`r grtlx`, connectance:
+`r grctn` to +`r grctx`, redundancy: `r grln` to +`r grlx`, Fig.
+S2) which was effectively captured by the hierarchical model (conditional R2
+ranging from `r r2cond$log_bm_std` for community biomass to
+`r r2cond$log_rich_std` for species richness, Table S3).
+
+(ref:sem-cap) (a) Structural equation models linking the temporal trends of
 biodiversity and food web structure. Dashed and solid arrows display
 respectively negative and positive the standardized slope coefficients, their
-widths being proportional to the absolute values of the coefficients.. The
+widths being proportional to the absolute values of the coefficients. The
 standardized slope coefficients and their associated 95% confidence intervals
-obtained by bootstrapping are displayed along the path. R2 displays the marginal
+obtained by bootstrapping are displayed along the path. $R^2$ displays the marginal
 R-squared of the linear models. (b to h) Direct bivariate relationships derived
@@
 relationship estimated with the SEM. The distribution of the site temporal
-trends are displayed in Fig. S1. All the effects are reported in Table S3.
+trends are displayed in Fig. S2. All the effects are reported in Table S4.
 Average trophic level is weighted by the biomass of the trophic species.
-Redundancy is the proportion of redundant links."
-
-```
-
-```{r sem, fig.cap = sem_cap, out.width = "100%"}
+Redundancy is the proportion of redundant links.
+
+```{r sem, fig.cap = "(ref:sem-cap)", out.width = "100%"}
 tar_load(p_sem_tps_file)
@@
 
-These temporal trend estimations at the site level were the input to our SEM,
-allowing us to evaluate the direct effect of the temporal trends of species
-richness and community biomass on the temporal trends of food web structure, the
-direct effect of  species richness temporal trends on the temporal trends of
-community biomass, and the indirect effect of species richness temporal trends
-on the temporal trends in food web structure through community biomass. We
-detected a strong positive effect of species richness temporal trends on the
+These temporal trend estimations at the site level were the input to our SEM
+which accounts for uncertainties in trend estimation (see Methods). It allows us
+to evaluate the direct effect of the temporal trends of species richness and
+community biomass on the temporal trends of food web structure, the direct
+effect of species richness temporal trends on the temporal trends of community
+biomass, and the indirect effect of species richness temporal trends on the
+temporal trends in food web structure through community biomass. We detected a
+strong positive effect of the temporal trends in species richness on the
 temporal trends in community biomass ($r_\delta =$ `r rdtps$bm$r`,
 Fig. \@ref(fig:sem) a and b, $r_\delta$: standardized slope coefficient, [95%
-CI], Table S3). This indicates that communities with decreasing, or increasing,
+CI], Table S4). This indicates that communities with decreasing, or increasing,
 species richness over time experienced a concomitant decrease, or increase, in
@@
 
-We also find a positive effect of the temporal trend in community biomass on the
+We also find positive effects of the temporal trend in community biomass on the
 temporal trends of connectance, average trophic level, and redundancy (resp.
@@
 in connectance, average trophic level and redundancy. To assess whether top
-trophic level species were driving those relationships, we additionally looked
+trophic level species were linked to those relationships, we additionally looked
 at the temporal trends in the number and the proportion of piscivorous species.
-The temporal trends in community biomass were positively associated with both
-the temporal trends in the number and proportion of piscivorous species (Fig.
-S2a). Then, communities with increasing biomass have an increase in average
-trophic level, in the number and proportion of piscivorous fishes (or
-reciprocally for decreasing biomass), suggesting that temporal trends in
-community biomass are driven by high trophic level fishes.
+The temporal trends in community biomass were positively associated with the
+temporal trends in both the number and the proportion of piscivorous species
+(Fig. S3a). It suggests that high trophic level fishes are strongly linked to
+temporal trends in community biomass.
+
+HERE
 
@@
 Spatial analyses, either using empirical data or the bioenergetic food web
-model, largely aligned with temporal trends (Fig. \@ref(fig:std)a and S3),
+model, largely aligned with temporal trends (Fig. \@ref(fig:std)a and S4),
 showing consistent positive effects of species richness on community biomass and
@@
   Models. Points and lines display the estimated effects and their confidence
-  intervals at 95\\%. Values are displayed in Table S3, R-squared in Table S4, and
+  intervals at 95\\%. Values are displayed in Table S4, R-squared in Table S5, and
   the visualization of the bivariate relationships for the spatial and
-  bioenergetic model SEMs are displayed in Figure S3. Average trophic level is
+  bioenergetic model SEMs are displayed in Fig. S4. Average trophic level is
   weighted by the biomass of the trophic species. Redundancy is the proportion
@@
   metaweb scale. Similar results were obtained with trophic species (i.e. node)
-  extinction (Fig. S4).")
+  extinction (Fig. S5).")
 ```
@@
 of three weeks [@danet_species_2021]. Those steps lead to the selection of
-`r nb_st` sites (Fig. \@ref(fig:matmet)a, Table S1).
+`r nb_st` sites (Fig. \@ref(fig:matmet)a, Table S2).
 
@@
 The performance of the model was assessed visually by plotting the fitted versus
-the observed values (Fig. S5). We also computed the marginal ($R^2_m$) and conditional
+the observed values (Fig. S6). We also computed the marginal ($R^2_m$) and conditional
 ($R^2_c$) R-squared of the models following previous formulations
@@
 baseline and temporal trends in community structure were much higher than the
-ones found for hydrographic basin (Table S5).
+ones found for hydrographic basin (Table S6).
 
@@
 and conditional $R^2$ associated with the linear models of the SEMs were computed
-with the Nagelkerke method [@lefcheck_piecewisesem_2016, Table S4].
+with the Nagelkerke method [@lefcheck_piecewisesem_2016, Table S5].
 
 All the statistical models displayed low multicollinearity (Variance inflation
-factors < 3, Table S6). We visually inspected the residuals of the linear
+factors < 3, Table S7). We visually inspected the residuals of the linear
 models.

### 2025-04-10 paper/manuscript.Rmd
Update manuscript with Colin and Elisa comments

@@
 
-HERE
-
 The total effect of the temporal trends in species richness on the temporal
@@
 `r rdtps$ct$r`, Fig. \@ref(fig:sem)f) and a positive indirect effect via changes
-in the temporal trends in community biomass ($r_\delta =$ `r ridtps$ct$r`).
-Thus, when communities experienced an increase, or decrease, in species
-richness, they also experienced a concomitant decrease, or increase, in
-connectance. In contrast, species richness temporal trends had no direct effects
-on trends in average trophic level ($r_\delta =$ `r rdtps$tlvl$r`, Fig.
-\@ref(fig:sem)g), but a positive indirect effect via changes in the trends of
-community biomass ($r_\delta =$ `r ridtps$tlvl$r`), which
-adds up to a total positive effect of species richness temporal trends on
-average trophic level ($r_\delta =$ `r rttps$tlvl$r`, Fig. \@ref(fig:std)a).
-Temporal trends in species richness had a strong total positive effect on the
-trends in redundancy (resp. $r_\delta =$ `r rdtps$red$r`, `r ridtps$red$r`), via
-direct and indirect positive effects ($r_\delta =$ `r rttps$red$r`). All
-together, this means that communities that have experienced species richness
-declines over the last decades have decreased in average trophic level and
-redundancy but increased in connectance. Conversely, those that experienced
-species richness increases have increased in average trophic level, redundancy,
-but decreased in connectance.
-
-The effects of species richness were more complex, because species richness in
-this model has indirect effects on food web structure through community biomass.
-Species richness had a direct negative effect on connectance ($r_\delta =$
-`r rdtps$ct$r`, Fig. \@ref(fig:sem)f), a positive indirect effect through
-community biomass ($r_\delta =$ `r ridtps$ct$r`), so that species richness had a
-negative effect in total on connectance ($r_\delta =$ `r rttps$ct$r`, Fig.
-\@ref(fig:std)a). In contrast, species richness had no direct effects on
-average trophic level ($r_\delta =$ `r rdtps$tlvl$r`, Fig. \@ref(fig:sem)g), a
-positive indirect effect through community biomass ($r_\delta =$
-`r ridtps$tlvl$r`), which adds up to a positive total effect of species richness
-temporal trends on average trophic level ($r_\delta =$ `r rttps$tlvl$r`, Fig.
-\@ref(fig:std)a). Species richness temporal trends had direct and indirect
-positive effect on the temporal trends in redundancy (resp. $r_\delta =$
-`r rdtps$red$r`, `r ridtps$red$r`), which added up to a strong positive effect
-($r_\delta =$ `r rttps$red$r`).
+in the temporal trends in community biomass ($r_\delta =$ `r ridtps$ct$r`). Thus, when
+communities experienced an increase, or decrease, in
+species richness, they also experienced a concomitant decrease, or increase, in
+connectance. In contrast, the total effects of the temporal trends in species
+richness on the temporal trend of both trophic level and redundancy were
+positive (resp. $r_\delta =$ `r rttps$tlvl$r`, `r rttps$red$r`, respectively,
+Fig. \@ref(fig:std)a). The total positive effect on the temporal trend of
+trophic level resulted from a combination of negative direct and positive
+indirect effect while the effect on the temporal trend of redundancy resulted
+from both positive direct and indirect effects (Fig. \@ref(fig:std)a). All together, this
+means that communities that have experienced decline in species richness over
+the last decades have decreased in average trophic level and redundancy but
+increased in connectance. Conversely, those that experienced species richness
+increases have increased in average trophic level, redundancy, but decreased in
+connectance.
+
+## Spatial association between biodiversity and food web
 
@@
 showing consistent positive effects of species richness on community biomass and
-of community biomass on average trophic level and redundancy. Species richness
-also exhibited a direct negative effect on connectance and a positive effect on
-redundancy, mirroring temporal patterns. However, spatial and temporal analyses
+of community biomass on average trophic level and redundancy. Across space,
+sites with higher fish biomass on average had food webs with higher connectance,
+redundancy and average trophic level than sites with lower fish biomass. The
+theoretical model predicted similar relations, with a particularly strong
+positive association between total biomass and average trophic level across
+modelled food webs. Species richness also exhibited a direct negative effect on
+connectance and a positive effect on redundancy, mirroring temporal patterns.
+Both modelled food webs and local fish communities characterized by greater
+species richness on average showed higher average biomass and food web
+redundancy, and lower connectance. However, spatial and temporal analyses
 diverged in their effects of species richness on average trophic level, with
@@
 
-We implemented three secondary extinction simulation scenarios on the empirical
-metaweb defined as a food web containing all the trophic species, i.e. the fish
-species subdivided in size classes added to their resources, found across all
-sites in the empirical data. This was to access a second line of inference about
-whether top species were drivers of biomass and structure patterns (see section
-4.2). When species are removed in a sequential order beginning by the highest
+To investigate whether top species were drivers of biomass and structure
+patterns (see section 4.2), we implemented three secondary extinction simulation
+scenarios on the empirical metaweb defined as a food web containing all the
+trophic species, i.e. the fish species subdivided in size classes added to their
+resources, found across all sites in the empirical data (See Methods). When
+trophic species were removed in a sequential order beginning by the highest
 trophic levels, connectance, average trophic level, and redundancy decreased
-(purple lines, Fig. \@ref(fig:std)b). On the other hand, removing low trophic level species
-first increases connectance and average trophic level, but did not affect
-redundancy (yellow lines, Fig. \@ref(fig:std)b). In turn, random species extinction sequence
-had little effect on food web structure (black line, Fig. \@ref(fig:std)b). These results,
-in conjunction with our empirical analyses above, suggest that top consumers
-play a disproportionate role in driving the changes in food web structure
-reported.
-
-```{r}
-std_cap <- paste0( "a, Direct and total effects of community biomass and species
+(purple lines, Fig. \@ref(fig:std)b). On the other hand, removing low level
+trophic species first increases connectance and average trophic level, but does
+not affect redundancy (yellow lines, Fig. \@ref(fig:std)b). In turn, species
+extinction at random had little effect on food web structure (black line, Fig.
+\@ref(fig:std)b). These results, in conjunction with our empirical analyses
+above, suggest that top consumers play a disproportionate role in driving the
+changes in food web structure reported.
+
+(ref:fig-std-cap) a, Direct and total effects of community biomass and species
 richness trends on food web structure trends. Standardized coefficients (r)
@@
 Models. Points and lines display the estimated effects and their confidence
-  intervals at 95\\%. Values are displayed in Table S4, R-squared in Table S5, and
+intervals at 95%. Values are displayed in Table S4, R-squared in Table S4, and
 the visualization of the bivariate relationships for the spatial and
-  bioenergetic model SEMs are displayed in Fig. S4. Average trophic level is
-  weighted by the biomass of the trophic species. Redundancy is the proportion
-  of redundant links. b, Effect of species extinctions on the structure of the
-  empirical metaweb according to three scenarios. In the Decreasing and
-  Increasing scenarios, species were ordered by their trophic level and removed
-  from the metaweb starting respectively from the highest and lowest trophic
-  level. Species were removed in a random sequence (50 sequences, grey dots) for
-  the random scenario, the black line displaying the average predicted by a GAM
-  linear model. For the extinction sequence, the average trophic level was not
-  weighted by the biomass of species as this information is not available at the
-  metaweb scale. Similar results were obtained with trophic species (i.e. node)
-  extinction (Fig. S5).")
-```
-
-```{r std, fig.cap=std_cap, out.width = "100%"}
+bioenergetic model SEMs are displayed in Figure S4. Average trophic level is
+weighted by the biomass of the trophic species. Redundancy is the proportion of
+redundant links. b, Effect of species extinctions on the structure of the
+empirical metaweb according to three scenarios. In the Decreasing and Increasing
+scenarios, species were ordered by their trophic level and removed from the
+metaweb starting respectively from the highest and lowest trophic level. Species
+were removed in a random sequence (50 sequences, grey dots) for the random
+scenario, the black line displaying the average predicted by a GAM linear model.
+For the extinction sequence, the average trophic level was not weighted by the
+biomass of species as this information is not available at the metaweb scale.
+Similar results were obtained with trophic species (i.e. node) extinction (Fig.
+S5).
+
+```{r std, fig.cap="(ref:fig-std-cap)", out.width = "100%"}
 tar_load(p_sem_tot_ext_sp_file)
@@
 connectance and average trophic level; (3) temporal trends in species richness
-were negatively associated with trends in connectance but only weakly related to
+were negatively associated with trends in connectance and only weakly related to
 trends in average trophic level; and (4) both community biomass and species
 richness trends were positively associated with trends in trophic pathway
-redundancy. Additionally, we found that (5) top predator species play a
+redundancy. Additionally, we found evidence that (5) top predator species play a
 significant role in driving these patterns. Importantly, these temporal
@@
 gradients, both in empirical data and in simulations from a bioenergetic food
-web model. In the following discussion, we explore these findings in the context
-of food web assembly theory and Biodiversity-Ecosystem Functioning theory, and
-consider their broader ecological implications.
+web model. In the following, we discuss these findings in the context of food
+web assembly theory and Biodiversity-Ecosystem Functioning theory, and consider
+their broader ecological implications.
 
@@
 pattern consistent across our temporal, spatial, and theoretical analyses. This
-result aligns with previous studies in fish communities [@woods_testing_2020;
-@danet_species_2021] as well as in grasslands, salt marshes, and forests
-[@hector_plant_1999; @tilman_biodiversity_2014; @wu_relationship_2015;
-@li_relationship_2018; but see @grace_integrative_2016]. These empirical
-findings are supported by theory, which suggests that food web diversity
-enhances biomass by stimulating primary production and resource uptake
+result aligns with previous studies on fish communities across space
+[@woods_testing_2020; @danet_species_2021] as well as grasslands, salt marshes,
+and forests [@hector_plant_1999; @tilman_biodiversity_2014;
+@wu_relationship_2015; @li_relationship_2018; but see @grace_integrative_2016].
+These empirical findings are supported by theory, suggesting that food web
+diversity enhances biomass by stimulating primary production and resource uptake
 [@schneider_animal_2016; @wang_biodiversity_2018; @wang_intraguild_2019;
-@nie_will_2023] and by Biodiversity-Ecosystem Functioning theory, which predicts
-that species loss reduces community biomass [@loreau_biodiversity_2001]. Our
-results reinforce the idea that declines in species richness can lead to reduced
-biomass across ecosystems, highlighting the potential for conservation actions
-that promote species richness to also enhance community biomass.
-
-Our results also reveal that food webs experiencing biomass declines undergo
-significant structural changes, including the loss of top predators and reduced
-connectance. These findings align with energetic and trophic biogeography
-theories [@lindeman_trophic-dynamic_1942; @gravel_trophic_2011], which posit
-that the presence of high-trophic-level species is constrained by the
-availability of energy and resources [@lindeman_trophic-dynamic_1942,
-@takimoto_ecosystem_2008; @post_ecosystem_2000; @post_long_2002]. Thus, a
-decline in community biomass may lead to insufficient resources to sustain top
-predators, while an increase in biomass could provide the necessary energy to
-support these species [@takimoto_ecosystem_2008; @post_ecosystem_2000].
-Alternatively, Biodiversity-Ecosystem Functioning theory suggests that the
-presence of higher trophic levels may reduce niche overlap among producers,
-enhancing productivity and community biomass [@schneider_animal_2016;
-@wang_biodiversity_2018; @wang_intraguild_2019; @nie_will_2023]. The
-relationship between community biomass and connectance is less clear, with a
-weaker positive association compared to average trophic level. Previous
-theoretical studies have reported contrasting effects of connectance on
-productivity [@nie_will_2023; @wang_intraguild_2019; @thebault_food-web_2003;
-@poisot_trophic_2013; @schneider_animal_2016]. For instance, while increased
-connectance between herbivores and plants can either enhance or reduce
-productivity [@thebault_food-web_2003; @poisot_trophic_2013; @nie_will_2023],
-greater connectance among carnivores generally boosts productivity by reducing
-top-down control and allowing biomass to accumulate across trophic levels
-[@wang_intraguild_2019; @schneider_animal_2016].
-
-Our study demonstrates that temporal trends in community biomass and species
-richness are positively associated with the proportion of redundant trophic
-pathways in food webs. In other words, declines in community biomass and species
-richness lead to a loss of redundant links, while increases in these factors
-result in greater redundancy. Since redundant links are those that can be
+@nie_will_2023], and by Biodiversity-Ecosystem Functioning theory, which
+predicts that species loss reduces community biomass
+[@loreau_biodiversity_2001]. Our results bring a temporal dimension to these
+findings using long-term trends in empirical data, and clearly exemplify that
+declines in species richness goes along with a reduction of biomass in
+ecosystems. Conversely, our result also indicates that conservation actions
+promoting species richness should also promote community biomass.
+
+Our results also reveal that food webs experiencing biomass and/or species
+richness declines undergo significant structural changes, including the loss of
+top predators and a reduction of connectance. These findings align with
+energetic and trophic biogeography theories [@lindeman_trophic-dynamic_1942;
+@gravel_trophic_2011], which posit that the presence of high-trophic-level
+species is constrained by the availability of energy and resources
+[@post_ecosystem_2000]. Thus, a decline in community biomass may lead to
+insufficient resources to sustain top predators, while an increase in biomass
+could provide the necessary energy to support these species
+[@takimoto_ecosystem_2008; @post_ecosystem_2000]. Further,
+Biodiversity-Ecosystem Functioning theory suggests that the presence of higher
+trophic levels may reduce niche overlap among producers, enhancing productivity
+and community biomass [@schneider_animal_2016; @wang_biodiversity_2018;
+@wang_intraguild_2019; @nie_will_2023]. The relationship between community
+biomass and connectance is less clear, with a weaker positive association
+compared to average trophic level. Previous theoretical studies have reported
+contrasting effects of connectance on productivity [@nie_will_2023;
+@wang_intraguild_2019; @thebault_food-web_2003; @poisot_trophic_2013;
+@schneider_animal_2016]. For instance, while increased connectance between
+herbivores and plants can either enhance or reduce productivity
+[@thebault_food-web_2003; @poisot_trophic_2013; @nie_will_2023], greater
+connectance among carnivores generally boosts productivity by reducing top-down
+control and allowing biomass to accumulate across trophic levels
+[@wang_intraguild_2019; @schneider_animal_2016]. Interestingly, our theoretical
+model predicts overall a positive relation between total biomass and
+connectance, which contrasts with the negative relation found recently by
+another complex allometric food web model [@nie_will_2023], but this relation is
+far weaker than the strong positive relation between total biomass and average
+trophic level.
+
+Our study suggests that declines in community biomass and species richness
+are associated with a loss of redundant trophic links, while their increase
+results in greater redundancy. Since redundant links are those that can be
 removed without triggering secondary extinctions [@allesina_who_2004;
 @bodini_using_2009], our findings suggest that declines in community biomass and
-species richness reduce food web robustness to further perturbations
-[@allesina_functional_2009]. The positive effect of community biomass on
-redundancy aligns with theoretical predictions: higher redundancy can reduce
-trophic complementarity within species, weaken top-down control, and promote
-compensatory dynamics, thereby enhancing robustness following extinctions
-[@staniczenko_structural_2010]. Similarly, the positive effect of species
-richness on redundancy supports the insurance hypothesis
+species richness might reduce food web robustness to further perturbations
+[@allesina_functional_2009]. Such positive effect of species richness on
+redundancy would then further support the insurance hypothesis
 [@yachi_biodiversity_1999; @loreau_biodiversity_2021], where greater species
 richness and functional redundancy buffer ecosystems against perturbations,
-increasing stability [@sanders_trophic_2018].
-
-Furthermore, our results highlight the disproportionate role of top
-trophic-level species in maintaining redundant links within food webs. This
-pattern is consistent with previous empirical studies showing that top predators
-are often the most generalist and highly connected species
-[@montoya_ecological_2006; @montoya_press_2009]. Consequently, disturbances
-affecting these top predators are likely to have the greatest impact on overall
-community stability [@montoya_press_2009]. These findings underscore the
-importance of preserving top predators and maintaining species richness to
-safeguard food web robustness and ecosystem stability.
-
-Species richness was negatively associated with connectance, consistent with
-previous findings and likely driven by limitations in predator generality
+increasing stability [@sanders_trophic_2018]. Furthermore, our results highlight
+the disproportionate role of top trophic-level species in maintaining redundant
+links within food webs. This pattern is consistent with previous empirical
+studies showing that top predators are often the most generalist and highly
+connected species [@montoya_press_2009; @montoya_ecological_2006]. Consequently,
+disturbances affecting these top predators are likely to have the greatest
+impact on overall community stability [@montoya_press_2009]. These findings
+underscore the importance of preserving top predators and maintaining species
+richness to safeguard food web robustness and ecosystem stability.
+
+Species richness was negatively associated with connectance, which is consistent
+with previous findings and likely driven by limitations in predator generality
 [@dunne_network_2006]. In contrast, the effects of species richness on average
@@
 negligible or negative, as observed in temporal, spatial, and theoretical
-models. However, when accounting for the indirect effects of species
-richness—mediated through changes in community biomass—temporal and theoretical
+models. However, when accounting for the indirect effects of species richness —
+mediated through changes in community biomass — our temporal and theoretical
 analyses revealed a positive association between species richness and average
-trophic level. These contrasting effects may be explained by our extinction
-simulations, which showed that the removal of top trophic-level species had a
-much smaller impact on average trophic level than on connectance. This suggests
-that while species richness influences food web structure, its effects are more
-pronounced on connectance than on average trophic level dynamics.
+trophic level. This suggests that while species richness influences food web
+structure, its effects are more pronounced on connectance than on average
+trophic level dynamics.
 
@@
 topology and biomass distribution, which are influenced by dynamic processes
-such as bottom-up and top-down control. These processes likely require
-additional information about species metabolism and productivity
-[@brose_allometric_2006; @barbier_pyramids_2019]. This interpretation is
-supported by the fact that our spatial analysis accurately predicted the
-temporal association between community biomass and average trophic level.
-Importantly, this finding highlights that the relationship between
-biodiversity—biomass and species richness—and food web
-characteristics—connectance, trophic level, and redundancy—is not purely
-structural but also functional. Indeed, predictions of food web structure are
-most accurate when both structural (species richness) and functional (biomass)
-metrics are considered.
+such as bottom-up and top-down control. Indeed, biomass distribution across
+trophic levels depends on  species metabolism and productivity which in turn
+control the strength of top-down and bottom-up processes
+[@brose_allometric_2006; @barbier_pyramids_2019].
 
@@
 consequences for ecosystem functioning and stability in the face of future
-perturbations. These findings suggest that assessments of food web structure,
-community biomass, and species richness—which are often more feasible than
-direct measurements of ecosystem functions—could serve as valuable indicators of
-functional decline and metrics for evaluating the efficacy of mitigation
-strategies. Importantly, our study also highlights critical avenues for future
-research, stemming from its limitations. For instance, integrating food web
-metrics into conservation planning will require understanding how they relate to
-other facets of biodiversity, such as the presence of non-native species, and
-drivers of biodiversity changes, including habitat degradation
-[@danet_past_2024] and climate change [@bonnaffe_interaction_2024]. Ultimately, our
-work aims to bridge the gap between Biodiversity-Ecosystem Functioning and food
-web theory, fostering greater integration with research on biodiversity changes.
+perturbations. These findings suggest that assessments of food web
+structure—based on metaweb reconstruction like in the present study—, added to
+more classic metrics of community biomass, and species richness could serve as
+valuable indicators of functional decline and metrics for evaluating the
+efficacy of mitigation strategies. Finally, our study also highlights critical
+avenues for future research. For instance, integrating food web metrics into
+conservation planning will require understanding how they relate to other facets
+of biodiversity, such as the presence of non-native species, and drivers of
+biodiversity changes, including habitat degradation [@danet_past_2024] and
+climate change [@bonnaffe_interaction_2024].
 
@@
 individuals, enabling to estimate the distribution of individual body size by
-species for each sampling [@bonnaffe_comparison_2021;
-@danet_species_2021].
+species for each sampling [@bonnaffe_comparison_2021; @danet_species_2021].
 
@@
 same period, leading to a mean standard deviation of sampled month in each site
-of three weeks [@danet_species_2021]. Those steps lead to the selection of
-`r nb_st` sites (Fig. \@ref(fig:matmet)a, Table S2).
+of three weeks [@danet_species_2021]. Those steps lead to the selection of `r nb_st` sites (Fig.
+\@ref(fig:matmet)a, Table S2).
 
@@
 We first estimated the body mass of each fish individual with the allometric
-law: $B_i = 0.01 \times l_i^{3.03}$, $B_i$ being the biomass expressed in gram and $l_i$ the
-body length of the individual $i$ expressed in millimeters [@froese_cube_2006;
-@danet_species_2021]. Then the biomass of each species and community
-were obtained by summing the body mass of individuals. This resulted in a
-biomass score for the whole community of each site. Finally, the biomass was
-reported to the sampled surface (in $m^2$) to account for sampling effort.
+law: $B_i = 0.01 \times l_i^{3.03}$, $B_i$ being the biomass expressed in gram
+and li the body length of the individual $i$ expressed in millimeters
+[@froese_cube_2006; @danet_species_2021]. Then the biomass of each species and
+community were obtained by summing the body mass of individuals. This resulted
+in a biomass score for the whole community of each site. Finally, the biomass
+was reported to the sampled surface (in $m^2$) to account for sampling effort.
 
@@
 
-We inferred the metaweb according to ontogenic diet data and body size
+We built the metaweb according to ontogenic diet data and body size
 [@gravel_inferring_2013; @poisot_trophic_2013; @brose_predator_2019;
-@bonnaffe_comparison_2021; @danet_species_2021]. The method is extensively
-described in @bonnaffe_comparison_2021 and @danet_species_2021. The food diet of
-stream fishes changes along their life cycle or stage, therefore according to
-their body size. Each fish species was divided in nine size classes, i.e.
-trophic species, equally distributed in their observed body size range. Thus,
-a trophic species is a group of individuals of the same species and size class
-that are expected to share the same prey and predators because trophic
-interactions are largely determined by predator-prey size ratio
-[@brose_allometric_2006; @brose_predator_2019]. We also added seven nodes present in the ontogenic
-food diet database: detritus, biofilm, phytoplankton, zooplankton, macrophages,
-phytobenthos and zoobenthos.  The resulting metaweb contained 45 fish species
-divided into 9 size classes plus 7 resource nodes, summing up to 412 nodes.
-Consideration of size classes, i.e.  trophic species instead of species,
-improves inference of trophic interactions [@jennings_weak_2001].
+@bonnaffe_comparison_2021; @danet_species_2021; @bonnaffe_interaction_2024]. The
+method is extensively described in @bonnaffe_comparison_2021 and
+@danet_species_2021. The food diet of stream fishes changes along their life
+cycle or stage, therefore according to their body size. Each fish species was
+divided in nine size classes, i.e. trophic species, equally distributed in their
+observed body size range. Thus, a trophic species is a group of individuals of
+the same species and size class that are expected to share the same prey and
+predators because trophic interactions are largely determined by predator-prey
+size ratio [@brose_allometric_2006; @brose_predator_2019]. We also added seven
+nodes present in the ontogenic food diet database: detritus, biofilm,
+phytoplankton, zooplankton, macrophages, phytobenthos and zoobenthos. The
+resulting metaweb contained 45 fish species divided into 9 size classes plus 7
+resource nodes, summing up to 412 nodes. Consideration of size classes, i.e.
+trophic species instead of species, improves inference of trophic interactions
+[@jennings_weak_2001].
 
@@
 
-The feeding interactions among fishes were based on the body size ratio
-between predators and preys. We defined the predation window of a
-piscivorous trophic species as 3% to 45% of its midpoint
-[@mittelbach_ontogeny_1998; @claessen_impact_2002; @hart_handbook_2008].  A
-trophic link was defined between the piscivorous trophic species and all the
-trophic species whose midpoint in body size range was included in the predation
-window.  The fish-resource trophic links were set between the trophic species
-and the resource nodes according to the food items of their size class.
-Finally, the feeding interactions between resources were defined according to the
-literature [@allan_stream_2007; @hart_handbook_2008].
+The feeding interactions among fishes were based on the body size ratio between
+predators and preys. We defined the predation window of a piscivorous trophic
+species as 3% to 45% of its midpoint [@mittelbach_ontogeny_1998;
+@claessen_impact_2002; @hart_handbook_2008]. A trophic link was defined between
+the piscivorous trophic species and all the trophic species whose midpoint in
+body size range was included in the predation window. The fish-resource trophic
+links were set between the trophic species and the resource nodes according to
+the food items of their size class. Finally, the feeding interactions between
+resources were defined according to the literature [@allan_stream_2007;
+@hart_handbook_2008].
 
@@
 @delmas_analysing_2019]. Connectance was computed as the ratio between the
-number of actual links and the number of potential links ($C =
-\frac{L}{S(S-1)}$, with $L$ being the number of links and $S$ the number of
-trophic species). We also computed the average trophic level, weighted by the
-biomass of the trophic species. The trophic level of a trophic species was
-computed recursively as 1 added to the mean trophic level of the preys it
-consumes [@herendeen_ecological_2008]. We computed the number of redundant and
-functional links using the dominator tree approach [@allesina_functional_2009].
-A species $i$ is a dominator of species $j$ if $i$ mediates the connection of $j$
-to basal resources such that the extinction of $i$ removes the connection of $j$ to
-basal resources. It is then used to identify the set of trophic links that are
-essential to connect species to basal resources, i.e. functional links, and the
-redundant links. This method requires a single basal root in the food webs. To
-do so, we added a basal dummy resource node to the empirical food webs connected
-to biofilm and phytoplankton resource nodes. For food webs generated from
-theoretical simulations (see below), we added a resource node connected to all
-primary producers. We computed the set of dominator trees using the
-`dominator_tree()` function from the `igraph` R package (Appendix B). We
-computed the number of functional links as the number of links in the resulting
-dominator tree of the food web. We checked that the procedure reproduced the
-examples presented in previous studies [@allesina_functional_2009, Appendix B].
-We then derived the proportion of redundant links in food webs of empirical and
-theoretical simulations.
+number of actual links and the number of potential links $C = \frac{L}{S(S-1)}$,
+with $L$ being the number of links and $S$ the number of trophic species). We
+also computed the average trophic level, weighted by the biomass of the trophic
+species. The trophic level of a trophic species was computed recursively as 1
+added to the mean trophic level of the preys it consumes
+[@herendeen_ecological_2008]. We computed the number of redundant and functional
+links using the dominator tree approach [@allesina_functional_2009]. A species
+$i$ is a dominator of species $j$ if species $i$ mediates the connection of
+species $j$ to basal resources such that the extinction of i removes the
+connection of $j$ to basal resources. It is then used to identify the set of
+trophic links that are essential to connect species to basal resources, i.e.
+functional links, and the redundant links. This method requires a single basal
+root in the food webs. To do so, we added a basal dummy resource node to the
+empirical food webs connected to biofilm and phytoplankton resource nodes. For
+food webs generated from theoretical simulations (see below), we added a
+resource node connected to all primary producers. We computed dominator trees
+using the `dominator_tree()` function from the `igraph` R package (See Appendix
+for details). We computed the number of functional links as the number of links
+in the resulting dominator tree of the food web. We checked that the procedure
+reproduced the examples presented in previous studies
+[@allesina_functional_2009, Appendix]. We then derived the proportion of
+redundant links in food webs of empirical and theoretical simulations.
 
@@
 We modeled the temporal trends of food web structure at each site ($Y_i$) using
-linear hierarchical model which accounts for the hierarchical spatial structure
+a linear hierarchical model which accounts for the hierarchical spatial structure
 of the data, i.e. the sites nested in hydrographic basins. Time was considered as the number of years since the
@@
 Approximation) Bayesian inference with default uninformative priors
-[@rue_bayesian_2017]. The prior distributions for the fixed intercept ($\alpha_0$) and slope ($\mu$) were
-modeled as a flat normal distribution with a mean of zero ($\mathcal{N}(0,\, 1000)$).
-Prior distributions for the Gaussian error $\epsilon_{i|n, t}$ and the random
-effects were modeled as a log gamma distribution with
-shape and inverse scale parameters ($\mathcal{G}(s, \, \tau) = \mathcal{G}(1, \,
-5.10^-5)$), then their respective standard deviation were obtained by
-back-transforming the inverse scale parameter ($\sigma = 1 / \sqrt{\tau}$).
-Community biomass and species richness were log-transformed.
+[@rue_bayesian_2017]. The prior distributions for the fixed intercept
+($\alpha_0$) and slope ($\mu$) were modeled as a flat normal distribution with a
+mean of zero ($\mathcal{N}(0,\, 1000)$). Prior distributions for the Gaussian
+error $\epsilon_{i|n, t}$ and the random effects were modeled as a log gamma
+distribution with shape and inverse scale parameters ($\mathcal{G}(s, \, \tau) =
+\mathcal{G}(1, \, 5.10^-5)$), then their respective standard deviation were
+obtained by back-transforming the inverse scale parameter ($\sigma = 1 /
+\sqrt{\tau}$). Community biomass and species richness were log-transformed.
 
@@
 
-We extracted the temporal trends at each site from the hierarchical model
-using mean BLUP values (Best Linear Unbiased Prediction), then multiplied
+We extracted the annual temporal trends at each site from the hierarchical model
+using mean Best Linear Unbiased Prediction (BLUP) values, then multiplied
 by 10 to get temporal trends by decade. For community biomass and species
@@
 Overall, we found that standard deviation attributed to site effects in both
-baseline and temporal trends in community structure were much higher than the
+baseline (i.e. the intercept) and temporal trends in community structure were much higher than the
 ones found for hydrographic basin (Table S6).
@@
 comparing the relationships estimated among food web structure in time to the
-ones inferred in space. We used the same sites as in the temporal analysis,
-but we summarized the temporal series of each station by the median value over time
+ones inferred in space. We used the same sites as in the temporal analysis, but
+we summarized the temporal series of each station by the median value over time
 of each facet of food web structure described above (Fig. \@ref(fig:matmet)).
@@
 average trophic level, the proportion of redundant trophic links, and community
-biomass and species richness, with Structural Equation Models. We
-modeled species richness as related to community biomass and food web structure.
-In turn, community biomass was related to food web structure. We computed one
+biomass and species richness, with Structural Equation Models. We modeled
+species richness as related to community biomass and food web structure. In
+turn, community biomass was related to food web structure. We computed one
 structural equation model to assess the relationships among the temporal trends
@@
 of the estimated trends, i.e. the estimated slopes for the response and the
-explicative variables ($w_j = 1 / \sum{s_j}$, $w_j$ being the weight, and
-$s_j$ the standard deviation on the temporal trends of the variables).
+explicative variables ($w_j = 1 / \sum{s_j}$, $w_j$ being the weight, and $s_j$
+the standard deviation on the temporal trends of the variables).
 
 The coefficients of the Structural Equation Models were computed with
-PiecewiseSEM R package [@lefcheck_piecewisesem_2016]. The coefficients were
-standardized and the confidence intervals were computed with semEff R package
-[@murphy_semeff_2021]. Confidence intervals were obtained by bootstrapping the
-linear models 1000 times and computing adjusted bootstrap percentile intervals
-(BCa), which are adjusted for the asymmetric distribution of resampling. The marginal
-and conditional $R^2$ associated with the linear models of the SEMs were computed
-with the Nagelkerke method [@lefcheck_piecewisesem_2016, Table S5].
-
-All the statistical models displayed low multicollinearity (Variance inflation
-factors < 3, Table S7). We visually inspected the residuals of the linear
+PiecewiseSEM R package [@lefcheck_piecewisesem_2016]. The coefficients were standardized and the
+confidence intervals were computed with semEff R package [@murphy_semeff_2021]. Confidence
+intervals were obtained by bootstrapping the linear models 1000 times and
+computing adjusted bootstrap percentile intervals (BCa), which are adjusted for
+the asymmetric distribution of resampling. The marginal and conditional R2
+associated with the linear models of the SEMs were computed with the Nagelkerke
+method [@lefcheck_piecewisesem_2016, Table S5].
+
+All the statistical models displayed low multicollinearity (Variance Inflation
+Factors < 3, Table S7). We visually inspected the residuals of the linear
 models.
@@
 get expectations on how the food web structure should change according to the
-addition and deletion of species and nodes. The scenario of extinction sequences
-were related to the trophic level of the species/nodes. In the decreasing and
-increasing scenario, we removed species/nodes in decreasing, resp. increasing
-order, of their trophic level, i.e. respectively beginning by the highest and
-lowest trophic level. In the random extinction sequence, we built 50 random
-extinction sequences. For each simulation, we removed fish species/nodes that
-lost all their prey and iterate this removal until all remaining species have at
-least one prey. We then computed the connectance, the average and the maximum
-trophic level after each extinction.
+addition and deletion of species (results presented in Fig. 3b) and trophic
+species (results in Appendix), i.e. species subdivided in size classes. The
+scenario of extinction sequences were related to the trophic level of the
+species/trophic species. In the decreasing and increasing scenario, we removed
+species/nodes in decreasing, resp. increasing order, of their trophic level,
+i.e. respectively beginning by the highest and lowest trophic level. In the
+random extinction sequence, we built 50 random extinction sequences. For each
+simulation, we removed fish species/nodes that lost all their prey. We then
+computed the connectance, the average and the maximum trophic level after each
+extinction.
 
@@
 
-We used a bioenergetic food web model to simulate the effects of community
-biomass and species richness changes on food web structure. This food web model
+We used a bioenergetic food web model to simulate the relations between
+community biomass, species richness and food web structure. This food web model
 lifts one of the limitations of our data, that is it includes the biomass of all
-the food webs from primary producers to top predators. This model allows
-simulating complex communities because its parameterization depends mainly on
-species body masses. We first generated `r nfw` food webs varying in species
+species in the food webs from primary producers to top predators. This model
+allows simulating complex communities because its parameterization depends
+mainly on species body masses. We first generated `r nfw` food webs varying in species
 richness (range: `r s_range["min"]`-`r s_range["max"]`)
@@
 relationships between metabolism and body mass empirically estimated
-[@brose_allometric_2006], such as $x_i = 0.88M_i^{-0.25}$.
+[@brose_allometric_2006], such as $x_i = 0.88 \times M_i^{-0.25}$.
 
@@
 
-The primary producer biomass increase with a growth rate ($r_i$) of 1 and a
+The primary producer biomass increases with a growth rate ($r_i$) of 1 and a
 logistic growth ($G_i$, eq. \@ref(eq:growth)), growth being limited by intraspecific
@@
 and carrying capacity ($K_i$, varying in the simulations). Primary producers
-lose biomass by being eaten by consumers at a rate that depend on consumer
+loose biomass by being eaten by consumers at a rate that depend on consumer
 metabolic rates ($x_j$), attack rates ($y_j$, set to 4
 @lajaaiti_ecologicalnetworksdynamicsjl_nodate), a functional response
-($F_{ji}$), and assimilation efficiency which accounts for the fact that
+($F_{ji}$), and assimilation efficiency accounting for the fact that
 consumers assimilate better the primary producer biomass than the consumer ones
@@
 Consumers gain biomass by eating other species and lose biomass by being
-consumed and by metabolic losses ($x_i$, eq. \@ref(eq:cons)). The functional
+consumed and by metabolic loses ($x_i$, eq. \@ref(eq:cons)). The functional
 response (eq. \@ref(eq:holling)) of consumer feeding depends on the preference
@@
 
-We simulated the dynamics of the `r nfw` food webs across a gradient of global carrying capacity (K,
-range: `r k_range["min"]`-`r k_range["max"]`). The carrying capacity were
+We simulated the dynamics of the `r nfw` food webs across a gradient of global
+carrying capacity ($K$, range: `r k_range["min"]`-`r k_range["max"]`) to
+represent variation in space of productivity. The carrying capacity were
 standardized according to the number of producers and interspecific competition
 ($K_i = \frac{1 + \alpha_{ij} (S - 1)}{S}K$) to prevent changes in productivity
-due to system size [@ives_stability_2000; @loreau_species_2008]. We ran
-simulations for 5000 timesteps. At the end of simulations, we removed dead
-species and measured community biomass, species richness and food web structure.
-If the final community contained disconnected producers (i.e. without consumers)
-or disconnected consumers (i.e. consumers without preys), we discarded them and
-run the simulations again with the same parametrization. The simulations were
-done using the Julia package `EcologicalNetworksDynamics.jl`
+due to system size and complementarity among producers [@ives_stability_2000;
+@loreau_species_2008]. We ran simulations for 5000 timesteps. At the end of
+simulations, we removed dead species (biomass < 10^-6) and measured community
+biomass, species richness and food web structure. If the final community
+contained disconnected producers (i.e. without consumers) or disconnected
+consumers (i.e. consumers without preys), we discarded them and run the
+simulations again with the same parametrization. The simulations were done using
+the Julia package `EcologicalNetworksDynamics.jl`
 [@lajaaiti_ecologicalnetworksdynamicsjl_nodate]. Then, we computed the community

### 2025-04-10 paper/manuscript.Rmd
Review abstract, Significance statement and appendix 1

@@
 
-Understanding how biodiversity loss affects ecological communities is crucial
-for predicting and mitigating human impacts on ecosystems. This study provides
-comprehensive evidence on how biodiversity changes are reshaping food web
-structure using an extensive dataset of riverine fish communities. We
-demonstrate that temporal changes in species richness and community biomass
-consistently correlate with altered trophic levels, connectance, and the
-redundancy of feeding relationships, suggesting energetic constraints and
-biodiversity-ecosystem functioning mechanisms jointly shape food web assembly
-and disassembly. Importantly, we show that declining biodiversity reduces the
-redundancy of trophic pathways, potentially making communities more vulnerable
-to future perturbations. These results suggest that food web structure metrics
-could serve as valuable indicators for monitoring ecosystem health and
-evaluating conservation strategies.
+Current rates of biodiversity loss raise urgent concerns about ecosystem
+functioning and stability, yet how biodiversity trends directly impact these
+critical processes remains unclear. For instance, food web &
+Biodiversity-Ecosystem Functioning research delivered strong predictions
+about the ecological consequences of biodiversity loss. Using an extensive
+dataset of riverine fish communities, we link biodiversity trends to temporal
+changes in food web structure. We demonstrate that temporal changes in species
+richness and community biomass consistently associate with altered trophic
+levels, connectance, and the redundancy of feeding relationships. We found that
+declining biodiversity reduces trophic pathway redundancy, likely increasing
+ecosystem vulnerability to perturbations. Our findings suggest that food web
+structure metrics could serve as valuable indicators for monitoring ecosystem
+health and guiding conservation strategies.
 

### 2025-04-10 paper/manuscript.Rmd
citation fix

@@
 proxy for temporal trends—a space-for-time substitution—when direct temporal
-data are scarce [@damgaard_a_2019]. To advance our understanding of the
+data are scarce [@damgaard_critique_2019]. To advance our understanding of the
 ecological consequences of biodiversity changes, it is essential to investigate

### 2025-04-16 README.Rmd

@@
 
-<!-- README.md is generated from README.Rmd. Please edit that file -->
-
-```{r, echo = FALSE}
-knitr::opts_chunk$set(
-  collapse = TRUE,
-  comment = "#>",
-  fig.path = "README-",
-  eval = TRUE 
-)
-
-mypath <- rprojroot::find_package_root_file
-source(mypath("R", "misc.R"))
-data_dir <- mypath("data")
-
-library(tidyverse)
-library(magrittr)
-library(jmotif)
-```
-# Analyse desassembly and assembly processes in fish communities
-
-<!-- badges: start -->
-<!-- badges: end -->
-
-The goal of this project is to analyze the links between the biomass dynamics
-and community structure dynamics.
-
-## Data
-
-data about communities are located in `data` folder.
-
-```{r load dataset, include = FALSE}
-myload(community_metrics, op_analysis, dir = data_dir)
-community_metrics %<>% left_join(select(op_analysis, opcod, station, date))
-```
-
-```{r}
-ts_biomass  <- community_metrics %>%
-  select(station, date, biomass) %>%
-  mutate(station = as.character(station)) %>%
-  group_by(station) %>%
-  arrange(date) %>%
-  nest()
-
-ts_biomass %<>%
-  mutate(
-    zts = map(data, function(x) znorm(x$biomass, threshold = 0.01)),
-    paa = map(zts, ~paa(., 3)),
-    sax = map_chr(paa, ~series_to_string(., 3))
-  )
-```
-
-```{r}
-pattern_dist <- ts_biomass %>%
-  group_by(sax) %>%
-  summarise(count = n()) %>%
-  arrange(desc(count))
-ggplot(ts_biomass, aes(x = sax)) +
-  geom_histogram(stat = "count")
-
-filter(pattern_dist, count > 10)
-```
-
-```{r}
-test <- ts_biomass %>%
-  filter(sax %in% c("cba", "bbb", "cab", "abc", "acb", "bca", "bac", "cbb")) %>%
-  group_by(sax) %>%
-  sample_n(10) %>%
-  mutate(
-    paa2 = map2(data, zts, function (x, zts) {
-      cbind(x[,1], zts)
-  }),
-    id_sta = as.character(seq(1,n()))
-
-  ) %>%
-  unnest(paa2)
-
-ggplot(test, aes(x = date, y = zts)) +
-  geom_line(aes(color = id_sta)) +
-  facet_wrap(~ sax)
-
-```
+# Assembly/Disassembly of food-web according to changes in species richness and community biomass

### 2025-04-16 paper/appendix.Rmd

@@
 
-Because species biomass are involved in trophic interactions, species losses can
-have cascading effects and trigger secondary extinctions [@dunne_network_2002].
-In the context of biodiversity crisis, assessing the robustness of ecological
-networks to species losses has been then a big question in Ecology. Previous
-research showed that food-web structure, such as connectance, increased
-robustness [@dunne_network_2002]. The idea is that more connected food-web will
-be more stable because they contain a large number of pathways convey biomass
-through the food-web. However, connectance as some limitations as a robustness
-metric, because each trophic link does not contribute equally to the robustness
-of an ecological network [@allesina_who_2004]. Trophic links can be categorised as
-functional or redundant, depending on their role in transmitting biomass through
-the food-web. Functional links are the set of links that is required to connect
-every species to the basal resource of the food-web, all of the other being
-redundant. Only functional links affect directly robustness, as their removal
-will trigger secondary extinctions. The removal of redundant links in turn do
-not directly trigger secondary extinctions, but makes the food-webs more fragile
-to further extinctions [@allesina_functional_2009].
+Species losses can trigger cascading extinctions by disrupting trophic
+interactions [@dunne_network_2002]. To assess ecological network robustness,
+researchers often examine food web connectance — the proportion of possible
+trophic links that are realized. While higher connectance generally increases
+stability by providing multiple pathways for biomass flow, not all links
+contribute equally to robustness [@allesina_who_2004].
 
-The identification of functional and redundant links is based on the use of
-denominator trees [@bodini_using_2009; @allesina_who_2004;
-@allesina_functional_2009]. Dominator trees allows to identify the set of
-trophic links that are essential to connect all the consumers to the basal resource, i.e.
-the functional links, and the redundant links, i.e. the redundant trophic pathways
-from basal resource to consumers. Pioneer papers explained the algorithm to
-compute the set of dominator trees and we refer to them for further
-information and examples [@bodini_using_2009; @allesina_who_2004;
-@allesina_functional_2009]. Here, we aim to show that while implementing this
-analysis could be difficult at the time, this algorithm is now widely
-available. In R, it is available in `igraph::dominator_tree()`. Below we show
-how the number of functional and redundant links can be  easily computed from R
-by replicating three examples presented in previous studies.
+Trophic links can be categorized into two types based on their role in
+maintaining food web integrity. Functional links are those essential for
+connecting all species to basal resources — their removal directly triggers
+secondary extinctions. In contrast, redundant links provide alternative pathways
+but are not strictly necessary for maintaining basic connectivity. While the
+loss of redundant links doesn’t cause immediate extinctions, it reduces the
+network’s resilience to future perturbations [@allesina_functional_2009]. This
+distinction makes quantifying redundancy crucial for predicting ecosystem
+vulnerability.
+
+To identify functional and redundant links, we employed dominator trees
+[@bodini_using_2009], a graph-theoretic approach that maps the minimal set of
+connections required to link all consumers to basal resources. Though once
+considered a niche tool, dominator tree algorithms are now readily accessible
+through common packages like R’s `igraph::dominator_tree()`. Below, we demonstrate
+this method by replicating classic examples from the literature.
+
+For implementation, we used a custom `compute_redundancy` function to quantify
+functional and redundant links. As an example, we applied this to the food-web
+from Bodini et al. (2009, see Appendix 1 therein), showing how easily these
+metrics can be derived from network data.
 
@@
 ```
-
-Here is an example with the food-web displayed in appendix of
-@bodini_using_2009:
 
@@
 
+Figure \@ref(fig:examples) provides visual comparisons between complete food-webs
+(left panels) and their functional-link subsets (right panels), reproducing key
+results from three seminal studies [@bodini_using_2009;
+@allesina_functional_2009]. The accompanying Table \@ref(tab:redun) summarizes
+the proportion of redundant links in these systems, highlighting how dominator
+trees can simplify robustness assessments.
+
 ```{r}
@@
 ```
-
-We used this function to reproduce the three examples (Fig. \@ref(fig:examples)),
-which were displayed in the Fig. 1 and Appendix 1 of @bodini_using_2009, and
-in the Fig. 1 of @allesina_functional_2009. The table \@ref(tab:redun) displays
-the number and the proportion of functional and redundant links from those
-examples.
 
@@
 
-(ref:example-cap) Reproduced examples of categorising functional links in
-food webs using `igraph::dominator_tree()` R function. Left columns (a, c, e)
-displays the complete food-web while right column displays food-web with the
-functional links only (b, d, f). (a,b): reproduction of Fig. 1 of
-@bodini_using_2009, (c, d): reproduction of appendix figures of @bodini_using_2009,
-(e, f): reproduction of fig. 1 of @allesina_functional_2009. Note that (e, f) is
-a bit different from the original, as noted by the authors, they could have
-removed further redundant links (i.e. $2 \to 5$, or $3 \to 5$).
+(ref:example-cap) **Functional link identification using dominator trees**. Left
+panels show complete food-webs, while right panels display only functional
+links. (a,b) reproduce @bodini_using_2009 Figure 1; (c,d) recreate their
+Appendix example; (e,f) replicate @bodini_using_2009 Figure 1 (with minor
+differences noted in the original text, they could have
+removed further redundant links, i.e. $2 \to 5$, or $3 \to 5$).
 

### 2025-04-16 paper/cover_letter.Rmd

---
author:
- On behalf of all the authors, Dr. Alain Danet
opening: Dear Editor in Chief and Associate Editors,
closing: Sincerely yours,
fontsize: 10pt
return-address:
- Dr. Alain Danet
- School of Biosciences
- The University of Sheffield
- Western Bank, S10 2TN, Sheffield, UK
output:
  linl::linl:
    keep_tex: true

letterhead: ./misc/letterhead.png
signature: /home/alain/Documents/Administration/signature.pdf
letterhead-y-offset: 0pt
letterhead-scale: .7
colorlinks: false
---

```{r, results = "hide", include = FALSE}
Sys.setlocale("LC_TIME", "C")
```

Please find enclosed our manuscript entitled *“Biodiversity temporal trends are
reshaping food web structure and redundancy in riverine ecosystems”*, which we
submit for consideration in *PNAS*.

In the midst of the current biodiversity crisis, understanding the ecological
consequences of biodiversity changes is critical for designing and implementing
effective conservation policies. This is especially urgent in freshwater
systems, which are among the most threatened ecosystems globally. While
biodiversity temporal trends have been widely documented, their impacts on
ecosystem functioning and stability remain poorly understood. Conversely, food
web and Biodiversity-Ecosystem Functioning research have provided robust
theoretical and experimental predictions on how biodiversity loss affects
ecosystem productivity and stability. For instance, food web structural
properties such as connectance and average trophic level are predicted to
strongly influence ecosystem productivity, while the presence of redundant
trophic pathways is linked to robustness against species extinctions. However,
aligning these predictions with empirical data from natural settings remains
challenging, as it requires simultaneous temporal data on biodiversity and food
web structure, which are rarely available.

We address this challenge here and reveal several effects of biodiversity
temporal trends on food web structure and function in riverine fish communities.
Using a unique dataset of over 400 fish community time series from multiple
hydrographic basins across France, we reconstructed food web structures for each
sampling event using individual body size, ontogenetic diet data, and predation
size windows. We then related changes in biodiversity (community biomass and
species richness) to changes in food web structure (connectance, average trophic
level, and the proportion of redundant trophic pathways). Our results reveal
that declines in species richness are associated with losses in community
biomass, while declines in community biomass are linked to reduced connectance
and average trophic level. We also found that top trophic-level species play a
disproportionate role in driving these trends. Importantly, declines in both
community biomass and species richness are associated with a reduction in the
proportion of redundant trophic pathways, suggesting weakened ecosystem
robustness to future perturbations.

Our study provides a large-scale perspective on how biodiversity trends reshape
food web structure in freshwater ecosystems, offering critical insights into the
ecological consequences of biodiversity loss. Our findings align with
predictions from food web and Biodiversity-Ecosystem Functioning research and
are supported by spatial analyses and bioenergetic food web modeling, which
validate the use of space-for-time substitution in this context. These results
underscore that widely reported biodiversity changes across taxa and ecosystems
likely have profound impacts on ecosystem functioning and resilience.

As *PNAS* has been at the forefront of research on biodiversity changes and food
web structure, we are confident that our study will interest the journal’s broad
readership and stimulate new perspectives on the ecological consequences of
biodiversity loss. The methods we developed to reconstruct food webs and
quantify redundancy using graph theory metrics will be of particular interest to
researchers across multiple disciplines. Additionally, this study provides
valuable insights for freshwater scientists and conservation practitioners,
offering the first comprehensive analysis of how biodiversity changes reshape
food web structure and integrating the fields of biodiversity change, food web
ecology, and Biodiversity-Ecosystem Functioning.

The enclosed manuscript has been approved by all authors and has not been
published or submitted elsewhere. We have had no prior discussions with a *PNAS*
editor regarding this work.

We suggest the following experts as potential editors and reviewers for their relevant expertise:

- Editorial Board members:
  - Power, Mary
  - Hastings, Alan
  - Marquet, Pablo A.
- NAS members:
  - Stephen R. Carpenter
  - Peter B. Reich
  - Sandra Lavorel
  - Marten Scheffer
  - Gene E. Likens
  - Lisa A. Levin
- Qualified referees (name & email link, institution, expertise):
  - [Shaopeng Wang](shaopeng.wang@pku.edu.cn), Peking University (expertise in Biodiversity-Ecosystem Functioning in food webs)
  - [Mary O’Connor](oconnor@zoology.ubc.ca), The University of British Columbia (expertise in the effects of biodiversity changes on ecosystem functioning)
  - [Jennifer Dunne](jdunne@santafe.edu), Santa Fe Institute (expertise in the effects of biodiversity loss on food web structure)
  - [Antonio Bodini](antonio.bodini@unipr.it), Universita di Parma (expertise in food web alteration and graph theory)
  - [Mike Heithaus](CASEdean@fiu.edu), Florida International University (expertise in the ecological consequences of top predator removal)

Thank you for considering our submission. We look forward to the possibility of
contributing to *PNAS*.

### 2025-04-16 paper/method_figure.Rmd

@@
 ```{r}
-library(drake)
+library('targets')
 library(tidyverse)
+library('magrittr')
+library(cowplot)
 
@@
     filter(station %in% st) %>%
-    dplyr::select(station, year, network) %>%
-    unnest(cols = c(network))
+    dplyr::select(station, year, network)
 
-  ## Compute metrics:
-  net %>%
+  if ("data.frame" %in% class(net$network[[1]])) {
+
+   net <- net %>%
+    unnest(cols = c(network)) %>%
     dplyr::select(year, from, to) %>%
@@
     )
+  } else {
+
+    net <- net %>%
+    arrange(year) %>%
+    group_by(year) %>%
+    rename(adj_mat = network) %>%
+    mutate(
+      troph = map(adj_mat, ~NetIndices::TrophInd(.x)),
+      obs_troph_level_vector = map(troph, function (x) {
+	TL <- x$TL
+	names(TL) <- rownames(x) 
+	return(TL)
+	})
+    )
+  }
+
+  return(net)
+
 }
@@
 ```{r}
-myload(metaweb_analysis, dir = get_mypath("data"), envir = environment())
-
+tar_load(metaweb_analysis)
 my_species_color <- set_color_species(
@@
 ```{r}
-loadd(rigal_classification, com_data, op_data)
+tar_load(c(com_data, op_data, com_analysis_data))
 op_data %<>%
   mutate(year = as.integer(year))
-myload(community_metrics, dir =
-  "~/Documents/post-these/mnhn/fishcom_biomass_dynamics/data", envir =
-  environment())
 
-community_metrics %<>%
+ti <- com_analysis_data %>%
+  group_by(opcod) %>%
+  summarise(sp_vector = list(setNames(biomass, species))) %>%
+  left_join(dplyr::select(op_data, station, opcod, year, surface))
+
+com_data %<>%
     left_join(dplyr::select(op_data, station, opcod, year))
-ti <- rigal_classification %>%
-  filter(variable == "bm_std") %>%
-  unnest(classif)
-first_st <- ti %>%
-  filter(shape_class == "decrease_constant") %>%
-  arrange(linear_slope)
 
-tes <- map(first_st$station[1:12], ~plot_dyn_web(
-    com = community_metrics,
+tar_load(gaussian_pred_station_tps10)
+tr10 <- gaussian_pred_station_tps10 %>%
+  select(response, station, mean) %>%
+  pivot_wider(names_from = "response", values_from = "mean")
+
+first_st <- tr10 %>%
+  arrange(log_bm_std)
+
+tes <- map(first_st$station[12:24], ~plot_dyn_web(
+    com = ti,
     sem_df = NULL,
@@
 ```{r}
+last_st <- tr10 %>%
+  arrange(desc(log_bm_std))
 
-last_st <- ti %>%
-  filter(shape_class == "increase_constant") %>%
-  arrange(linear_slope)
-
-tes <- map(last_st$station[1:12], ~plot_dyn_web(
-    com = community_metrics,
+tes <- map(last_st$station[13:24], ~plot_dyn_web(
+    com = ti,
     sem_df = NULL,
@@
 ```{r}
-st <- first_st$station[4]
-st[2] <- last_st$station[13]
+st <- first_st$station[20]
+st[2] <- last_st$station[16]
 names(st) <- c("decreasing", "increasing")
@@
 ```{r}
-myload(network_analysis, dir =
-  "~/Documents/post-these/mnhn/fishcom_biomass_dynamics/data/classes", envir =
-  environment())
+tar_load(c(net_analysis_data, net_data))
+load(here::here("data", "classes", "network_analysis.rda"))
 network_analysis %<>%
@@
   station = st[1],
-  selected_years = NULL,
-  node_color = NULL, scale_node_size = 0.06,
+  selected_years = c(1995, 2005),
+  node_color = NULL, scale_node_size = 0.02,
   par_options = par(mar = c(0,0,0,0)),
-  log_abun = TRUE
+  log_abun = FALSE 
 )
-g <- plot_grid(plotlist = map(p, ggdraw), nrow = 3)
+g <- plot_grid(plotlist = map(p, ggdraw), ncol = 2)
 
@@
   g,
-  nrow = 3,
-  ncol = 4,
+  nrow = 1,
+  ncol = 2,
   base_height = 4,
@@
 tes <- plot_dyn_web(
-    com = mutate(community_metrics, year = ymd(year, truncated = 2L)),
+    com = mutate(ti, year = ymd(year, truncated = 2L)),
     sem_df = NULL,
@@
 tes2 <- plot_dyn_web(
-    com = mutate(community_metrics, year = ymd(year, truncated = 2L)),
+    com = mutate(com_data, year = ymd(year, truncated = 2L)),
     sem_df = NULL,
@@
 ```{r}
+tar_load(full_data2)
 tps_ct_dec <- full_data2 %>%
@@
 
-```{r}
+```{r, eval = FALSE}
 # get a station that represents the results
@@
 ```{r}
-color_tes <- map(dec_representative$station,
+color_tes <- map(st[1],
   ~set_color_species(
-  node_list = community_metrics %>%
+  node_list = ti %>%
   filter(station == .x) %$%
@@
 )
-names(color_tes) <- as.character(dec_representative$station)
+names(color_tes) <- as.character(st[1])
 
-tes <- map(dec_representative$station, ~plot_dyn_web(
-    com = community_metrics,
+tes <- map(st[1], ~plot_dyn_web(
+    com = ti,
     sem_df = NULL,
@@
 
-names(tes) <- as.character(dec_representative$station)
+names(tes) <- as.character(st["decreasing"])
 plot_grid(plotlist = tes)
@@
 ```{r}
-
-st_decreasing <- dec_representative$station[3]
+st_decreasing <- st["decreasing"]
 
@@
   labs(color = "Species", fill = "Species") +
-  theme(legend.position = c(.2, .8), legend.direction = "horizontal")
+  theme(legend.position = c(.2, .9), legend.direction = "horizontal")
 
@@
   ncol = 1,
-  base_height = 6.6,
-  base_asp = 1.2
+  base_height = 4,
+  base_width = 7
   )
 ```
+
 ```{r}
-v_colors =  viridis(n = 2, begin = 0.5, end = 1)
+tar_load(c(net_analysis_data, net_data))
+load(here::here("data", "classes", "network_analysis.rda"))
+network_analysis %<>%
+  left_join(dplyr::select(op_data, opcod, station, year)) %>%
+  filter(!is.na(opcod))
+
+p <- get_network_temporal_plot(
+  net_list = network_analysis,
+  station = st[1],
+  selected_years = c(1995, 2005),
+  node_color = color_tes[[st[1]]], scale_node_size = 0.05,
+  par_options = par(mar = c(0, 0, 0, 0)),
+  log_abun = TRUE 
+)
+g <- plot_grid(plotlist = map(p, ggdraw), ncol = 2)
+
+save_plot(
+  get_mypath("figures/decreasing_biomass_network.pdf"),
+  g,
+  nrow = 1,
+  ncol = 2,
+  base_height = 4,
+  base_width = 4)
+
+p2 <- get_network_temporal_plot(
+  net_list = network_analysis,
+  station = st[2],
+  selected_years = NULL,
+  node_color = NULL, scale_node_size = 0.06,
+  par_options = par(mar = c(0,0,0,0)),
+  log_abun = TRUE
+)
+g2 <- plot_grid(plotlist = map(p2, ggdraw), nrow = 4)
+
+save_plot(
+  get_mypath("figures/increasing_biomass_network.png"), g2,
+  nrow = 4,
+  ncol = 4,
+  base_height = 4,
+  base_width = 4)
+```
+
+```{r}
+v_colors =  viridisLite::viridis(n = 2, begin = 0.5, end = 1)
 names(v_colors) <- c("tps", "sp")
 
-tps_dec_inc <- map(c("log_bm_std", "log_rich_std", "ct_ff", "w_trph_lvl_avg", "piel_bm"), # 
+tps_dec_inc <- map(c("log_bm_std", "log_rich_std", "ct_ff", "w_trph_lvl_avg"), # 
   ~plot_temporal_variable_lm(st = st_decreasing, var = .x, col_median =
@@
 )
-theme_get()$text
 ```

### 2025-04-17 paper/manuscript.Rmd
Last few edits + adding Acknowledgments and data/code repo

@@
 header-includes:
+  - \usepackage{amsmath}
   - \usepackage[left]{lineno}
@@
 Bridging this gap requires aligning biodiversity temporal trends with food web
-theory and Biodiversity-Ecosystem Functioning research, which provide strong
-predictions about the ecological consequences of biodiversity loss. Most
-insights rely on spatial comparisons of ecological communities, assuming they
-reflect temporal trends—a space-for-time substitution. Here, we analyze
-biodiversity and food web time series from over 400 riverine fish communities
-across France (1995–2018) to evaluate how biodiversity temporal trends reshape
-food web structure and community functioning. We examine relationships among
-species richness, community biomass, and three key food web metrics:
-connectance, weighted average trophic level, and trophic pathway redundancy. We
-also test the space-for-time hypothesis using spatial gradients and a
-theoretical food web model. Structural equation models and robustness analyses
-reveal that declines in species richness strongly correlate with reduced
-community biomass, with top trophic-level species playing a disproportionate
-role in food web changes. Declining biomass is associated with the loss of top
-trophic levels and decreased connectance, while temporal changes of species
-richness negatively correlates with those of connectance. Both biomass and
-species richness declines reduce trophic pathway redundancy, suggesting
-biodiversity loss undermines community robustness to future perturbations. Our
-findings align with food web theory and Biodiversity-Ecosystem Functioning
-research, support the validity of space-for-time approaches for basic food web
-metrics, and highlight the relevance of food web metrics as indicators of
-ecosystem function and fragility.
+theory and Biodiversity-Ecosystem Functioning research, both of which provide
+strong predictions about the ecological consequences of biodiversity loss. Most
+insights on those consequences currently rely on spatial comparisons of
+ecological communities, assuming they reflect temporal trends—a space-for-time
+substitution. Here, we analyze biodiversity and food web time series from over
+400 riverine fish communities across France (1995–2018) to evaluate how
+biodiversity temporal trends reshape food web structure and community
+functioning. We examine relationships among species richness, community biomass,
+and three key food web metrics: connectance, weighted average trophic level, and
+trophic pathway redundancy. We also test the space-for-time hypothesis using
+spatial gradients and a theoretical food web model. Our structural equation
+models and robustness analysis reveal that declines in species richness strongly
+correlate with reduced community biomass, with top trophic-level species playing
+a disproportionate role in food web changes. Declining biomass is associated
+with the loss of top trophic levels and decreased connectance, while temporal
+changes in species richness negatively correlates with changes in connectance.
+Both biomass and species richness declines reduce trophic pathway redundancy,
+suggesting that biodiversity loss weakens community robustness to future
+perturbations. Our findings align with food web theory and
+Biodiversity-Ecosystem Functioning research, support the validity of
+space-for-time approaches for basic food web metrics, and demonstrate the
+relevance of food web metrics as indicators of ecosystem function and fragility.
 
@@
 
-Current rates of biodiversity loss raise urgent concerns about ecosystem
-functioning and stability, yet how biodiversity trends directly impact these
-critical processes remains unclear. For instance, food web &
-Biodiversity-Ecosystem Functioning research delivered strong predictions
-about the ecological consequences of biodiversity loss. Using an extensive
-dataset of riverine fish communities, we link biodiversity trends to temporal
-changes in food web structure. We demonstrate that temporal changes in species
-richness and community biomass consistently associate with altered trophic
-levels, connectance, and the redundancy of feeding relationships. We found that
-declining biodiversity reduces trophic pathway redundancy, likely increasing
-ecosystem vulnerability to perturbations. Our findings suggest that food web
-structure metrics could serve as valuable indicators for monitoring ecosystem
-health and guiding conservation strategies.
+Rates of biodiversity loss raise urgent concerns about ecosystem functioning and
+stability, yet how biodiversity trends directly impact these critical processes
+remains unclear. For instance, food web & Biodiversity-Ecosystem Functioning
+research has delivered strong predictions about the ecological consequences of
+biodiversity loss but lack of empirical assessment. Using an extensive dataset
+of riverine fish communities, we link biodiversity trends to temporal changes in
+food web structure. We demonstrate that temporal changes in species richness and
+community biomass consistently associate with altered food web structure. We
+found that declining biodiversity reduces trophic pathway redundancy, likely
+increasing ecosystem vulnerability to perturbations. Our findings suggest that
+food web structure metrics could serve as valuable indicators for monitoring
+ecosystem health and guiding conservation strategies.
 
@@
 
-(ref:fig-met-cap) Methodological Approach: (a) We analyzed `r nb_st` stream fish
+(ref:met-cap) **Methodological approach**: (a) We analyzed `r nb_st` stream fish
 communities in France, each monitored for at least 10 years. (b) For each site
@@
 
-```{r matmet, fig.cap="(fig-met-cap)", out.width="100%"}
+```{r matmet, fig.cap="(ref:met-cap)", out.width="100%"}
 knitr::include_graphics(get_mypath("figures", "mat_met.png"))
@@
 redundant trophic links (hereafter “redundancy”, see Appendix 1,
-Fig. S1, Table S2) from the `r nb_st`
+Fig. S1, Table S1) from the `r nb_st`
 sampling sites with 10+ years of community dynamics (Fig. \@ref(fig:matmet)a-c). We used
@@
 
-(ref:sem-cap) (a) Structural equation models linking the temporal trends of
+(ref:sem-cap) **a**, Structural equation models linking the temporal trends of
 biodiversity and food web structure. Dashed and solid arrows display
@@
 obtained by bootstrapping are displayed along the path. $R^2$ displays the marginal
-R-squared of the linear models. (b to h) Direct bivariate relationships derived
+R-squared of the linear models. **b** to **h**, Direct bivariate relationships derived
 from the structural equation model. Points display the temporal trends at each
@@
 
-(ref:fig-std-cap) a, Direct and total effects of community biomass and species
-richness trends on food web structure trends. Standardized coefficients (r)
-derived from the temporal, spatial, and bioenergetic model Structural Equation
-Models. Points and lines display the estimated effects and their confidence
-intervals at 95%. Values are displayed in Table S4, R-squared in Table S4, and
-the visualization of the bivariate relationships for the spatial and
-bioenergetic model SEMs are displayed in Figure S4. Average trophic level is
-weighted by the biomass of the trophic species. Redundancy is the proportion of
-redundant links. b, Effect of species extinctions on the structure of the
-empirical metaweb according to three scenarios. In the Decreasing and Increasing
-scenarios, species were ordered by their trophic level and removed from the
-metaweb starting respectively from the highest and lowest trophic level. Species
-were removed in a random sequence (50 sequences, grey dots) for the random
-scenario, the black line displaying the average predicted by a GAM linear model.
-For the extinction sequence, the average trophic level was not weighted by the
-biomass of species as this information is not available at the metaweb scale.
-Similar results were obtained with trophic species (i.e. node) extinction (Fig.
-S5).
+(ref:fig-std-cap) **a**, Direct and total effects of community biomass and
+species richness trends on food web structure trends. Standardized coefficients
+($r_\delta$) derived from the temporal, spatial, and bioenergetic model
+Structural Equation Models. Points and lines display the estimated effects and
+their confidence intervals at 95%. Values are displayed in Table S4, $R^2$
+in Table S5, and the visualization of the bivariate relationships for the
+spatial and bioenergetic model SEMs are displayed in Fig. S4. Average trophic
+level is weighted by the biomass of the trophic species. Redundancy is the
+proportion of redundant links. **b**, Effect of species extinctions on the
+structure of the empirical metaweb according to three scenarios. In the
+Decreasing and Increasing scenarios, species were ordered by their trophic level
+and removed from the metaweb starting respectively from the highest and lowest
+trophic level. Species were removed in a random sequence (50 sequences, grey
+dots) for the random scenario, the black line displaying the average predicted
+by a GAM linear model. For the extinction sequence, the average trophic level
+was not weighted by the biomass of species as this information is not available
+at the metaweb scale. Similar results were obtained with trophic species (i.e.
+node) extinction (Fig. S5).
 
@@
 Overall, we found that standard deviation attributed to site effects in both
-baseline (i.e. the intercept) and temporal trends in community structure were much higher than the
-ones found for hydrographic basin (Table S6).
+baseline (i.e. the intercept) and temporal trends in community structure were
+much higher than the ones found for hydrographic basin (Table S6).
 
@@
 computing adjusted bootstrap percentile intervals (BCa), which are adjusted for
-the asymmetric distribution of resampling. The marginal and conditional R2
+the asymmetric distribution of resampling. The marginal and conditional $R^2$
 associated with the linear models of the SEMs were computed with the Nagelkerke
@@
 species in the food webs from primary producers to top predators. This model
-allows simulating complex communities because its parameterization depends
+allows simulating complex communities because its parametrization depends
 mainly on species body masses. We first generated `r nfw` food webs varying in species
@@
 
+# Data, Materials, and Software Availability
+
+The raw data used for the analysis are available on Zenodo:
+https://zenodo.org/records/5095656. The raw fish database is public and
+available on Zenodo: https://zenodo.org/records/8099409. The manuscript and the
+supplementary materials are written in Rmarkdown, i.e. combining code and text,
+and are available on github:
+https://github.com/alaindanet/fishcom_biomass_dynamics. We further implemented a
+code pipeline using the targets R package to ensure that the code, the data, the
+figures, the manuscript and the results are up to date.
+
+# Acknowledgments
+
+We are indebted to the OFB for providing the database, and we thank the numerous
+people who contributed to the fish records. We thank Dr Katherine Assersohn for
+her constructive feedback on the study. AD, LEM, MM, CF, and EL have received
+support from by the ANR project ECOSTAB (ANR-17-CE32-0002) awarded to EL. AD and
+APB have received support from the Natural Environment Research Council under
+grant agreement no. NE/T003502/1 awarded to APB.
+
 # References  {-}

### 2025-04-17 paper/appendix.Rmd

@@
   kbl(
-    caption = "Summary distribution of community metrics and fish monitoring variables.",
+    caption = "Summary distribution of community metrics and fish monitoring
+    variables. Q1 and Q3 are the first and third quartiles of the
+    distributions.",
     booktabs = T
